\chapter{Wednesday, Decembeer 23rd -- 3:00 AM}

%%% The encounter
Jeff clutched at his daughter's hand, then thought better of it and knelt beside her, hugging her protectively against his side.  She was still sobbing from the pain and rush of heat.

``Justin?  Justin, is that you?'' he called out.

There was a rustle from over by the far doorway, the one that led out into what would have been the backyard.  There was a form standing, shown only by the dull yellow of far away street-lights against clouds.

Perhaps standing was the wrong word.  From his vantage point on the foundation, kneeling next to his daughter, he could see that it was Justin, but his son was\ldots{}floating?  Hovering? His feet were flat, a scant few inches above the ground, but he wasn't touching anything else to keep him from resting on the ground.

``Justin!'' Jeff called again.  ``Come home, Justin.  It's daddy.  Come home with dad.''

Hesitating once more, he tried, ``Justin?''

``Os\'e.''

The voice that came from where his son stood was more than just his son.  It was as though Justin had whispered the word, but along with that in chorus with the boy was a voice far deeper, far older, speaking perfectly in time with him.

``O-Oh say?'' Jeff stammered.

``Os\'e,'' the voice repeated, layered above Justin's.  ``I am.  I am Os\'e.''

``Justin, come on, bud,'' Jeff pleaded.

Kayla interrupted, shouting, ``Give us back Justin!  Give me back my brother, Os\'e!''

There was a laugh, and with that horrible sound, a flush of warmth that rose up through father and daughter, starting in their feet and rising through their bodies, singeing hair and robbing them of their breath.

``What would you give, little girl?''  The voice sounded proud, jovial.  ``You have given me your blood.  Your father gave his blood.  You gave me your will, your trials, your tears.  It was not enough.  What would you give?''

Jeff coughed and gasped through the heat.  Kayla, recovering more quickly, lept from her father's arms and raced toward where Justin stood.

There was a sharp crack, and Jeff winced instinctively.  He cried out, ``Kayla!  Kayla honey, are you okay?''

His daughter was sitting on the floor, her knees drawn up to her chest and her face buried in her arms.  Unhurt, but silent and unmoving.  Jeff crawled forward toward her cautiously, unsure of what had transpired in that briefest of moments that he had looked away, though he knew time was different here.

Kayla nodded against her arms, her shoulders shaking with quiet sobs.

``You have nothing to give,'' the voice purred above Justin's hoarse whisper.

``I\ldots{}I'd give myself in a heartbeat for my son,'' Jeff offered, his voice clouded with emotion.

``No.''  The answer was flat, final.  There was no disputing that this would be unacceptable.  Justin -- Os\'e -- continued after a moment, as though he could not help but gloat, ``This battle is not your own, old man.  It is long past the time you could have made \textit{that} offering.''

Jeff was crying.  He was crying and burning, bleeding and struggling to see.  He felt anger, felt afraid, felt dirty, desparate, and in pain.

``There is nothing you can give.''  The voice was purely Os\'e's now.  ``This is beyond you.  There is nothing you can offer, though I have collected almost all of my toll.  He is mine-''

``No!'' Jeff shouted, sobbing.  ``No,'' he said once more, struggling to control his breath.

``He is mine,'' the voice asserted, growing in volume.  ``He has always been mine.  If I were to leave you now, he would forever be mine.  There is only one payment, and it will be mine.''

For the first time, Justin's form shifted in the dark.  His hands, previously hanging limply at his sides, moved up to his waist and slipped within the pockets of his hoodie. From it, he removed a small object, only a bit larger than a hand.

The hand clutching the object dropped, and the light reflected from the clouds caught it just enough for Jeff to make it out.

A gun.

``Justin!  Justin Justin Justin!'' Jeff cried, pleading.  ``Justin, bud, come on.  Come on, let's just talk.  Justin!''

There was no doubt of intent.

``The only thing that can be given,'' the voice purred.  ``Is everything.''

Justin's hand lifted the gun in one smooth, sure movement, and placed the muzzle of the barrel against his right temple.

``Everything.  And more.''

Justin's finger pulled the trigger.

\secdiv
%%% The suicide

A sharp report -- more of a bang than a roar, from that palm-sized pistol -- muffled by hair, skin, bone, and soul.

It was shocking just how quickly everything happened after that.

Kayla, who had been watching through wide, sobbing eyes, had let out a shrill scream and backed quickly across the room, scooting along her backside and clawing at the dirty cement of the foundation with her hands.

Jeff let out an anguished cry and crumpled onto the cold floor.

Justin's body was jerked against the side of the door frame, his feet finally leaving the position where they had been, a few inches above the floor of the house.  It fell in a disorganized heap, alternating between stiffness and relaxedness without rhythm on the floor, something slower than twitching, but still without conscious effort.

``No!  No no no no,'' Jeff cried, scrabbling along the floor and tearing his fingernails against the roughness of the concrete below him.  He raced over to his son's body and gathered it up into his arms.  Still warm, still warm\ldots{} ``No no no no no,'' he continued, a quiet litany of grief as he clutched his son to his chest.

There was a lot of blood, a stupendous amount of blood.

\secdiv
%%% The demon departs

\begin{quote}
  More, ever more.
\end{quote}

The voice was a shadow of what it once was, barely audible, almost solely within Jeff's head.

\begin{quote}
  Do not ever forget.  Always more.
\end{quote}

If there was more, it was drowned out by Jeff's sobs and shouts as he rocked with his son held half within his lap, Kayla's screams and tears as she wrapped her arms up over her head and curled into a tight ball.
