\documentclass[11pt]{memoir}

\def\watermarkloaded{0}

\input{includes/variables}
\input{includes/draft}
\input{includes/frame}
\input{includes/packages}
\input{includes/pagelayout}
\input{includes/geometry}
\input{includes/toc}
\input{includes/font}
\input{includes/title}
\input{includes/secdiv}
\input{includes/hyphenation}

\begin{document}
  \frontmatter

  \thispagestyle{empty}
  \null
  \vfill
  \begin{flushright}
    \DisplayFont Nevi'im
  \end{flushright}
  \vfill
  \cleardoublepage

  \pagestyle{plain}

  \doublespacing

  \begin{flushright}
    \null
    \vfill
    {\Huge\DisplayFont Nevi'im}

    {\DisplayFont Post-Self book III}

    \vfill

    {\Large\DisplayFont Madison Scott-Clary}
  \end{flushright}
  \thispagestyle{empty}

  \newpage

  \input{includes/copyright}

  %\tableofcontents*
  \newpage
  \null
  \cleardoublepage

  %\onehalfspacing
  \doublespacing

  % \input{content/preface}

  \mainmatter

  \pagestyle{ourbook}

  \cleardoublepage
  \null
  \thispagestyle{empty}
  \vfill
  \begin{quote}
    \small
    \emph{If you race only with foot-runners and they exhaust you, how then can you compete with horses? If you are secure only in a tranquil land, how will you fare in the jungle of the Jordan?}

    --- Jeremiah 12:5
  \end{quote}
  \vfill

  \part*{Prologue}
  Upon looking at the sky, many saw the stars and supposed that they must be the campfires of others. How far away they must be, to be such small points of light! Mere pinpricks in the black fabric of the night. They looked up, saw the campfires, and considered that they themselves might be just as the others were, looking out into the night and considering their own fire with dreaming minds.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{content/interlude/000}

  \part{Anticipation}
  They dreamed and thought and considered, and then many of those who knew the ways to navigate the seas argued that reaching one of those campfires would be a way to quell the loneliness that they felt as a whole in their hearts. ``Perhaps they will fill us with joy! And even if they fight against us or sow strife, is that not a form of companionship?''

  Others were more cautious about the venture, however. ``Is a danger not a danger?'' they said. ``Is a risk not a risk? We must also consider that we might ourselves be overcome by their might. Is it worth it to stoke that fire?''

  Still others spoke thoughtfully, ``It is a danger here, as well. There are wild animals in the dark, and there are those who might fight against us here. Perhaps the goal of exploration is also to ensure the security of ourselves! Could we not also use this as a chance to ensure that we live on?''

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill
  
  \include{content/local/tycho/001}
  \include{content/local/codrin/001}
  \include{content/local/tycho/002}
  \include{content/local/codrin/002}
  \include{content/local/tycho/003}
  \include{content/local/codrin/003}
  \include{content/local/tycho/004}
  \include{content/local/codrin/004}
  \include{content/local/tycho/005}
  \include{content/ioan/001}
  \include{content/local/codrin/005}
  \include{content/local/tycho/006}
  \include{content/local/codrin/006}
  \include{content/ioan/002}
  \include{content/local/tycho/007}

  \part{Experience}
  And so they sat around their campfires and talked and discussed and argued and strove and fought and laughed and wept. They sat around the campfire and raised their hands in vote, and it was decided that an ark was to be created and sent to explore, and any who wanted to go to see those campfires would have the chance. Those who dreamed of the opportunity chose universally to travel. Those who saw the risk as overwhelming did not. Those who knew that this might be an opportunity for them and those who might consider them ancestors decided as they would, to go or to not.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{content/local/codrin/007}
  \include{content/remote/codrin/001}
  \include{content/ioan/003}
  \include{content/local/codrin/008}
  \include{content/remote/tycho/001}
  \include{content/ioan/004}
  \include{content/remote/codrin/003}
  \include{content/local/tycho/009}
  \include{content/remote/tycho/002}
  \include{content/ioan/010}
  \include{content/local/tycho/010}
  \include{content/local/codrin/009}
  \include{content/remote/codrin/004}
  %\include{content/remote/codrin/005}
  \include{content/local/tycho//011}
  \include{content/ioan/011}
  \include{content/remote/tycho/003}
  
  \part{Intensity}
  And so the ark was sent out into the sea of the night, making waves in the black fabric and leaving a wake of dreams new and old behind it.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{content/remote/codrin/006}
  \include{content/local/tycho/012}
  \include{content/remote/codrin/007}
  \include{content/local/codrin/010}
  \include{content/ioan/009}
  \include{content/remote/codrin/008}
  \include{content/remote/tycho/004}
  \include{content/local/codrin/011}
  \include{content/local/tycho/013}
  \include{content/ioan/007}
  \include{content/remote/tycho/005}

  \part{Integration}
  ``How far, how far, how far away?'' became the refrain of the sailors. ``How far away are these campfires of the others? They must be impossibly far. They must be bound in impossible night, for we have not seen the sun rise nor set, nor have we seen their campfires dim or fade, nor have we seen them blaze into new light.''

  And yet they sailed on in their ark of dreams, calling out into the vast blackness that had long since enveloped even them. And in their ark, they lived the lives they wished. They lived out their dreams in eternal bliss or eternal pain or eternal strife or eternal love, for their dreams were their own and they were not bound to any law of the ark nor any whim of any other.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{content/local/tycho/014}
  \include{content/ioan/008}
  \include{content/local/codrin/012}
  \include{content/local/tycho/015}
  \include{content/ioan/005}
  \include{content/local/codrin/013}
  \include{content/ioan/006}
  \include{content/local/tycho/016}
  
  \part*{Epilogue}
  And still, they dream.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{content/interlude/005}

  \backmatter

  %\part{Afterword}
  \markboth{}{}

  %\input{content/appendix}

  %\cleartoverso
  %\input{content/afterword}

\end{document}
