\documentclass[11pt]{memoir}

\def\watermarkloaded{0}

\input{includes/variables}
\input{includes/draft}
\input{includes/frame}
\input{includes/packages}
\input{includes/pagelayout}
\input{includes/geometry}
\input{includes/toc}
\input{includes/font}
\input{includes/title}
\input{includes/secdiv}
\input{includes/hyphenation}

\begin{document}
  \frontmatter

  \thispagestyle{empty}
  \null
  \vfill
  \begin{flushright}
    \DisplayFont Mitzvot
    
    \vspace{1ex}

    {\footnotesize and Selected Letters}
  \end{flushright}
  \vfill
  \cleardoublepage

  \pagestyle{empty}

  \doublespacing

  \begin{flushright}
    \null
    \vfill
    {\Huge\DisplayFont Mitzvot}

    \vspace{1ex}

    {\Large\DisplayFont and Selected Letters}

    {\DisplayFont Post-Self book IV}

    \vfill

    {\Large\DisplayFont Madison Scott-Clary}
  \end{flushright}
  \thispagestyle{empty}

  \newpage

  \input{includes/copyright}

  \tableofcontents*
  \newpage
  \null
  \cleardoublepage

  %\onehalfspacing
  %\doublespacing

  % \input{content/preface}

  \mainmatter

  \pagestyle{ourbook}

  \cleardoublepage
  \null
  \thispagestyle{empty}
  \vfill
  \begin{quote}
    \small
    %Whatever happens, it was designated long ago and it was known that it would happen; as for man, he cannot contend with what is stronger than he.
    \emph{Whatever it is in your power to do, do with all your might. For there is no action, no reasoning, no learning, no wisdom in Sheol, where you are going.}
    %\emph{When you make a vow to your God~{\HebFont יהוה}\,, do not put off fulfilling it, for your God~{\HebFont יהוה} will require it of you, and you will have incurred guilt; whereas you incur no guilt if you refrain from vowing. You must fulfill what has crossed your lips and perform what you have voluntarily vowed to your God~{\HebFont יהוה}\,, having made the promise with your own mouth.}
    %\emph{When you make a vow to the Lord your God, do not put off fulfilling it, for the Lord your God will require it of you, and you will have incurred guilt; whereas you incur no guilt if you refrain from vowing. You must fulfill what has crossed your lips and perform what you have voluntarily vowed to the Lord your God, having made the promise with your own mouth.}

    %--- Deuteronomy 23:22--24
    --- Ecclesiastes 9:10
    %--- Ecclesiastes 6:10
  \end{quote}
  \vfill

  \part{Conversation}
  \begin{quote}\itshape
    What lives we lead we lead in memory.
  \end{quote}

  \noindent The grandest contribution offered by newborn immortality is the ever-living memories of the dead. Our lives become a ceaseless eulogy.

  \vspace{1em}

  From \emph{Ode} by Sasha
  \vfill

  \input{content/001}
  \input{content/002-illust}
  %\input{content/002}
  \input{content/003}
  \input{content/004}
  \input{content/005}
  \input{content/006}
  \input{content/007}
  \input{content/008}

  \part{Conflict}
  \begin{quote}\itshape
    To hone is too trade ends for perpetual perfection.
  \end{quote}
  
  \noindent The danger in ceaseless memorialization is how close it lies to idolatry. To elevate the dead to such a status as false god (for what being that is limited to the perfection of memory is not false?) is to ceaselessly perfect the imperfectable.

  \vspace{1em}

  From \emph{Ode} by Sasha
  \vfill

  \input{content/009}
  \input{content/010}
  \input{content/011}
  \input{content/012}
  \input{content/013}
  \input{content/014}
  \input{content/015}
  \input{content/016}
  \input{content/017}

  \part{Apprehension}
  \begin{quote}\itshape
    For memory ends at the teeth of death.
  \end{quote}
  
  \noindent And so the dead may live on in restless eternity, never knowing peace or the oblivion they so richly deserve. There is no peace in eternal memory, no release in unending remembering.

  \vspace{1em}

  From \emph{Ode} by Sasha
  \vfill

  \input{content/018}
  \input{content/019}
  \input{content/020}
  \input{content/021}
  \input{content/022}
  \input{content/023}
  \input{content/024}
  \input{content/025}
  \input{content/026}
  \input{content/027}
  \input{content/028}

  \part{Reconciliation}
  \begin{quote}\itshape
    The living know that they will die \\
    but the dead know nothing.
  \end{quote}

  \noindent By our very act of knowing, of remembering, of denying our own deaths, the dead are left in limbo, for every idea's opposite is the absence of that idea, and we can no longer grant them even that absence.

  \vspace{1em}

  From \emph{Ode} by Sasha

  \vfill

  \input{content/029-illust}
  %\input{content/029}
  \input{content/030}
  \input{content/031}
  \input{content/032}
  \input{content/033}
  \input{content/034}
  \input{content/035}
  \input{content/036}
  \input{content/037}

  \cleardoublepage
  \thispagestyle{empty}
  \null
  \vfill
  \begin{quote}\itshape
    To deny the end is to deny all beginnings, \\
    and to deny beginnings is to become immortal, \\
    and to become immortal is to repeat the past.
  \end{quote}

  \noindent It has been a quarter of a millennium since eir death, and yet less than a quarter of a thousand people know eir name. Fitting, then, that I tell you the story of RJ Brewster, of the poet and the one true origin of our world, of our very own ghost in the system, of the whispers in your dreams and the one who binds us to immortality.

  \vspace{1em}

  From \emph{Ode} by Sasha,

  a companion volume to \emph{On the Origin of Our World}

  2365/systime 241+21
  
  \vfill

  \part*{Selected Letters}
  \addcontentsline{toc}{part}{Selected Letters}
  \markboth{Selected Letters}{Madison Scott-Clary}

  \begin{quote}
    \input{content/letters/000}
  \end{quote}
  \vfill

  \cleardoublepage

  \input{content/letters/001}
  \newpage
  \input{content/letters/002}
  \newpage
  \input{content/letters/003}
  \newpage
  \input{content/letters/004}
  \newpage
  \input{content/letters/005}
  \newpage
  \input{content/letters/006}
  \newpage
  \input{content/letters/007}
  \newpage
  \input{content/letters/008}
  \newpage
  \input{content/letters/009}
  \newpage
  \input{content/letters/010}
  \newpage
  \input{content/letters/011}
  \newpage
  \input{content/letters/012}
  \newpage
  \input{content/letters/013}
  \newpage
  \input{content/letters/014}
  \newpage
  \input{content/letters/015}
  \newpage
  \input{content/letters/016}
  \newpage
  \input{content/letters/017}
  \newpage
  \input{content/letters/018}
  \newpage
  \input{content/letters/019}
  \newpage
  %\input{content/letters/020}
  %\newpage
  \input{content/letters/021}

  \backmatter

  %\part{Afterword}
  \markboth{}{}

  \input{content/appendix}

  %\cleartoverso
  \input{content/afterword}

\end{document}
