

\null
\vfill

\begin{verse}[1.01\textwidth]
  A measure of grain\\
  and a measure of water ---\\
  spring's own time and heat

  Air carries the scent\\
  of myriads of lives spent\\
  on summer's warm breath

  Crumb and density,\\
  warmth buried beneath crisp crust ---\\
  autumn's crackling leaves.

  Loaves and loaves and loaves\\
  baked for comfort in the cold ---\\
  winter calls for stores.
\end{verse}

\vfill

\newpage

\null
\vfill

\begin{verse}[1.01\textwidth]
  Leaves fall, grass withers,\\
  and I step back to witness\\
  winter's frozen form.

  Half an hour's silence,\marginnote{Physical therapy after surgery involves half an hour of stillness.}\\
  body relaxing slowly,\\
  letting springtime in.

  A season to stretch,\\
  then one to learn everything ---\\
  summer's exploring.

  What will autumn bring?\\
  Maturity? Strength? Wisdom?\\
  Dry heat and cool nights?
\end{verse}

\vfill

\newpage

\null
\vfill

\begin{verse}[1.01\textwidth]
    Seven flies circle,\\
    Trimmers chatter down the block:\\
    The hum of summer.

    \vin I listen, silent, waiting,\\
    \vin Breathing in sun and out shade.

    Fig leaves like fingers\\
    paw feebly through still hot air\\
    and come up with naught.

    \vin Too early for fruit to droop,\\
    \vin we must wait past midsummer.
  \end{verse}

  \begin{verse}[1.01\textwidth]
    And I walk until\\
    all I can hear is the wind\\
    among the fir trees.

    \vin Summer breezes bear away\\
    \vin all the choices of years past.
  \end{verse}

  \begin{verse}[1.01\textwidth]
      Drink deep of death-thoughts\\
      as the day dies with a yawn ---\\
      the year starts to fade.
  \end{verse}

  \vfill

  \newpage

  \null
  \vfill

  \begin{verse}[1.01\textwidth]
      Arctic fox's den,\\
      adorned with flowers and snow:\\
      garden in winter.\marginnote{Arctic foxes, due to both their housing arrangements and dining habits, tend to have their dens bedecked in flowers, even in winter.}
  \end{verse}

  \vfill
