\subsection{---}

\begin{verse}[1.01\textwidth]
Saturday is for mechanics.\\
Sunday is for terror.\\
Monday is for acceptance.\\
Tuesday is for purging.\\
Wednesday is for anxiety.\\
Thursday is for sleep.\marginnote{Surgery was Thursday, May 11, 2018.}
\end{verse}

\newpage
\null
\vspace{1cm}
\subsection{---}

\begin{verse}[1.01\textwidth]
When I am asleep,\\
The world changes around me.\\
In spring, I am changed.
\end{verse}

\newpage
\subsection{---}

\begin{verse}[1.01\textwidth]
I'm no good at images, only words,\\
and yet for days after surgery,\\
as anesthesia and countless\\
\vin milligrams, milliliters, millions of\\
drugs leave my system,\\
I'm lousy with visions,\\
each lousy with meaning.

I lay in bed, unable to move,\\
struggling to keep my eyes open;\marginnote{Every seven minutes, I would press the button to give me another drip of morphine. Even after drifting off, I would try to stay on it.}\\
I know that if I close them,\\
\vin I'll be lost, I'll be lost, I'll be\\
mired in waking dreams,\\
coherent visions with all the logic\\
of that paler side of consciousness.

Perhaps the veil here\\
is still too thin and vague,\\
the pool too clear, the monsters too scary\\
\vin too lean, too mean, too hungry, or\\
perhaps I was too close to death\\
to come away totally unscathed,\\
too close to completely survive.

\newpage
\null
\vspace{0.01em}

\vin It's as though, laying here,\\
\vin stinking of hospital,\\
\vin I'm seeing emotions play out,\\
\vin \vin Scene after scene, scene after scene,\\
\vin anxiety shown in heaps of discarded entrails,\\
\vin hope in the ceaseless ratcheting of gears,\\
\vin determination in the marching of feet.

If I were an artist, perhaps\\
I could hope to touch these images,\\
but as it is, every word falls short,\\
\vin too vague, too inexact, too tight to\\
hope to explain something so vast\\
by the very act of attempting to reproduce;\\
I can only hint from the margins.

That poetry can accomplish what prose cannot\\
in its economy of motion\\
is attractive to me, here in recovery ---\\
\vin so tired, so tired, so tired --- so\\
maybe I can hope to express the dire import\\
of these visions dancing behind closed lids,\\
or at least remind myself on rereading.

\newpage
\null
\vspace{0.01em}

Even now, a week out,\\
I'm starting to lose touch with the visions,\marginnote{I think that perhaps it was not the anaesthesia, but the morphine that was causing these visions.}\\
I can almost touch them if I squint,\\
\vin lie real still, don't move now, but\\
even then, a shadow of the substance\ldots{}\\
I'm starting to consign to memory\\
that which was probably memory to begin with.
\end{verse}

\newpage
\subsection{---}

\begin{verse}[1.01\textwidth]
It is two hundred miles between what I expect and what I want.\marginnote{From home to the hospital, it is a 202 mile drive.}\\
Two hundred long strides that seem impassible from one direction,\\
\vin and from the other a day's short drive.

It is nine and a half hours between question and answer.\marginnote{The length of my surgery.}\\
A half hour of jazz, nine hours of sleep, a scant second of perspective,\\
\vin and I can only traverse in one direction

It is eleven inches between who I was and who I am.\marginnote{The length of the penis before, plus the depth of the neovagina afterwards.}\\
Ten of those inches are pain, the eleventh is numb,\\
\vin There's pleasure to be had in there, I'm promised.

It is twelve years between what I want and what I get:\marginnote{I started questioning my gender at 20, had surgery at 32.}\\
Ten years of remembering who I will become, two years running,\marginnote{At 22, I started to come out to myself. At 30, I began transitioning in earnest.}\\
\vin Eight days dreaming.
\end{verse}

\newpage
\subsection{---}

\begin{verse}[1.01\textwidth]
What have you changed?\marginnote{Orignally intended to be a ritual incantation.}\\
\vin \emph{My mind}\\
What changed you?\\
\vin \emph{Nothing}\\
What became of it?\\
\vin \emph{I am not who I was}

What have you changed?\\
\vin \emph{My name}\\
What changed you?\\
\vin \emph{The word}\\
What became of it?\\
\vin \emph{I am called who I am}

What have you changed?\\
\vin \emph{My looks}\\
What changed you?\\
\vin \emph{The light}\\
What became of it?\\
\vin \emph{I am seen as I am}

What have you changed?\\
\vin \emph{My chemistry}\\
What changed you?\\
\vin \emph{The substance}\\
What became of it?\\
\vin \emph{My form is my own}

\newpage
\null
\vspace{0.01em}

What have you changed?\\
\vin \emph{My body}\\
What changed you?\\
\vin \emph{The knife}\\
What became of it?\\
\vin \emph{I am shaped how I am}

What have you changed?\\
\vin \emph{Nothing}\\
What changed you?\\
\vin \emph{I was accepted}\\
What became of it?\\
\vin \emph{I accepted myself}

What have you changed?\\
\vin \emph{Everything}\\
What changed you?\\
\vin \emph{Everything}\\
What became of it?\\
\vin \emph{I became who I am}
\end{verse}
