\begin{verse}[1.01\textwidth]
Her hair is tied with a ribbon\\
\vin Saying ``This is not for you.''\marginnote{Mark Z. Danielewski's \emph{House of Leaves}}\\
She wears a pendant of stamped brass\\
\vin Saying ``Non sum qualis eram.''\marginnote{Ibid.}\\
``I have been a hero since birth,''\marginnote{\emph{shagta ursangmen}, from Shulgi, king of Ur.}\\
\vin She tells herself,\\
\vin \vin As though that will somehow\\
\vin \vin \vin Explain her scars.

She pierced her own ears,\\
\vin But did a shit job of it.\\
Her tattoos tease around\\
\vin the edges of her identity.\\
Her bones are ley-lines,\\
\vin She tells herself,\\
\vin \vin Strung with symbols\\
\vin \vin \vin Heady with meaning.

She has a certain ``fuck you'' inflected\\
\vin ``Je ne sais quoi'' about her.\\
Her clothes bespeak\\
\vin carefully constructed laziness.\\
``I've got my own style,''\marginnote{Playfully named \emph{frumpcore}.}\\
\vin She tells herself,\\
\vin \vin While doing all she can\\
\vin \vin \vin To not be seen.
\newpage
\null
\vspace{1cm}

She studied order through science\\
\vin and found it chaotic.\\
She studied chaos through music\\
\vin and found it inviable.\\
``I'll work with words.''\\
\vin She tells herself\\
\vin \vin She'll write a book,\\
\vin \vin \vin Or publish stories.

She wanted to be a bus driver\\
\vin when she grew up.\\
Then a linguist, then a biologist,\\
\vin Then a composer, a conductor.\\
She never wanted to be\\
\vin What she became;\marginnote{Read: a girl.}\\
\vin \vin The irony of which\\
\vin \vin \vin Is not lost on her.
\end{verse}
