\hypertarget{douglas-hadje-2325}{%
\chapter{Douglas Hadje — 2325}\label{douglas-hadje-2325}}

Douglas found it strange that, over the next several days, the conversations that he had with May Then My Name and Ioan had amounted to little more than chitchat.

It wasn't that it was unpleasant in any way. May Then My Name had a delightfully weird sense of humor and, though he originally found it difficult to understand, given the text-only nature of the medium, an undeniable sense of empathy that made him immediately feel comfortable around her.

Ioan, too, had proven to be fascinating to talk to. Ey was, as May Then My Name had suggested, the type who spent much of eir time up in eir head, the result of which were statements that were as insightful as they were easy to understand. He liked the writer immediately. The two together could be hilarious, informative, somber, and comforting all in one conversation.

They were also very clearly in love with each other, which Douglas found odd, for some reason, given how often they referred to each other simply as coworkers. Ioan, especially, seemed either completely unwilling to acknowledgement or simply had not internalized it on eir side.

Ah well. It was an interesting fact, at least, in that when Douglas had interacted with couples before, he had often felt like\ldots well, not a third wheel, particularly, so much as someone who simply did not understand the social dynamic at hand. Not so with them.

As enjoyable as all of the conversations were, however, and as much as he was beginning to understand sys-side life, he seemed to gain little in the way of actual knowledge.

At this point, however, his duties had diminished almost to almost nil, and he had little else to do. Within the year, he suspected that he'd be off looking for another job, hopefully still station-side.

So here he was, sitting on his bed, reading until either May Then My Name or Ioan pinged him.

Tonight, it was Ioan.

\textbf{Ioan Bălan:} Good evening, Douglas. Let me know when you're around.

\textbf{Douglas Hadje:} I'm around! How are you, Ioan?

\textbf{Ioan:} I'm doing well. And yourself?

\textbf{Ioan:} And by the way, it's just me, tonight. May has fallen asleep.

\textbf{Ioan:} All of her, actually. It's like the planets aligning sometimes. A bit of blessed quiet.

\textbf{Douglas:} I'm alright. Was actually just waiting up to hear from you. Things are pretty boring with no further launch stuff to do.

\textbf{Douglas:} Is May Then My Name loud in person?

\textbf{Ioan:} Oh, not really, actually. She's just very

\textbf{Ioan:} Hmm.

\textbf{Ioan:} Intense, is maybe the right word? She doesn't chatter all of the time or run around or anything. Usually, she's just working, come to think of it, and she does all of her work up in her head. She'll have good conversations with me or with you, walk around, clean or cook, which I realize makes her sound very domestic, which isn't really the case. Those are just things she enjoys.

\textbf{Ioan:} But the whole time that she's doing those things, she's intense. Her expression, her personality, her words, her smile, her laugh, her eyes.

\textbf{Ioan:} That's one of those things that always strikes me as funny. You know, the whole thing about how eyes are just spheres, not actually emotive.

\textbf{Ioan:} But hers are intense.

\textbf{Douglas:} The intensity comes through even in text, so I believe you. So it's nice having a break from that intensity?

\textbf{Ioan:} Yeah, basically. It's nice when we sleep. The time before we head to bed is much calmer. Just a lot of talking and such. She's a very physically affectionate person, which I was very much not used to when she moved in.

Douglas laughed, considered his options, shrugged, and typed his response.

\textbf{Douglas:} That also comes through in text, in a way. You two sound like a cute couple.

\textbf{Ioan:} Huh.

\textbf{Ioan:} You know, I'd never really considered that.

\textbf{Ioan:} `That' meaning both being a couple and that such could come through in text.

\textbf{Ioan:} I don't know that we are, actually.

\textbf{Douglas:} ``Don't know''?

\textbf{Douglas:} Shit, I'm sorry, I didn't mean to presume.

\textbf{Ioan:} I also don't know that we aren't, either. Sometimes the question will come up in my mind and I'll wonder about it a little, but it always slips away and then I'm back to organizing my pen collection or whatever May accuses me of.

\textbf{Douglas:} But you've never talked with her about it?

\textbf{Ioan:} No.~Same problem as mentioned above. Every time I think of asking she's already asleep or too busy or I'm out on an interview as \#Tracker and then it just slips my mind.

\textbf{Ioan:} You can't be a couple without agreeing that you are, right? So maybe that means we aren't? It's above my pay grade.

\textbf{Douglas:} Do you want to be?

\textbf{Ioan:} I definitely don't know that! Not super comfortable continuing to talk about this, though.

\textbf{Douglas:} No problem.

\textbf{Ioan:} Needless to say, she's intense. The whole damn clade is.

\textbf{Douglas:} The Ode clade, was it?

\textbf{Ioan:} Yes. Or the Odists if you want something shorter.

\textbf{Douglas:} Can you tell me more about them? They sound fascinating, and I've always wondered.

\textbf{Ioan:} I can tell you a little bit. It's more on her to answer the details. They can be tight-lipped about the weirdest things.

\textbf{Douglas:} Of course. I'm eager to know, but don't want to pry.

\textbf{Ioan:} So, the Ode clade is very old. They've been around for ages. There are quite a few of them. I did a bunch of work with one of them named Dear, Also, The Tree That Was Felled about twenty years back, and that's how I got to know them. We've had an on-again-off-again working relationship.

\textbf{Ioan:} Though, now that I think about it, one of my forks — my only real cocladist — has found emself in a romantic relationship with Dear.

\textbf{Ioan:} You have to understand, though, every single Odist I've met (except maybe one, who isn't around anymore) has been completely and utterly charming, so maybe it's just a them thing.

\textbf{Ioan:} Anyway, They're all incredibly strange, is what I'm saying.

\textbf{Ioan:} Another incredible thing about them is that they are, to a one, incredible magnets for strange goings on. I guess that's part of being strange, but even so, every one of them has this incredible story about these events that have happened around them. I don't think it's a conscious thing, necessarily. Just by virtue of their intensity, they intense happenings, or intense friends, or intense reactions from those around them.

\textbf{Ioan:} For example — and this is public information here, now, I don't know if it ever made it phys-side — it was one of them who discovered (or at least was public about) the fact that those who live sys-side can't ever actually forget things. Instead of simply publishing some sort of report or studying the reality of it, he adopted the persona of a biblical teacher and organized an entire scavenger hunt to try and get the rest of the clade interested.

\textbf{Douglas:} That sounds incredibly dramatic.

\textbf{Ioan:} Agreed!

\textbf{Ioan:} I was going to say that they're not really dramatic, just intense, but it's definitely both.

\textbf{Douglas:} Can you tell me about their names? They all seem similar to the snippets of poetry that May Then My Name kept sending me.

\textbf{Ioan:} They're all really strange, I can certainly say that, but they're also a very, very touchy subject for them, enough that Qoheleth, the aforementioned Odist who did the scavenger hunt, the one I mentioned isn't here anymore, was assassinated for trying to divulge some information about their names.

\textbf{Douglas:} Assassinated?!

\textbf{Douglas:} That's a thing that can happen, sys-side?

\textbf{Ioan:} Unfortunately, yes. It's rare, thankfully. There are viruses of a sort that interrupt the sys-side mind enough to cause it to lose coherency and just sort of disappear.

\textbf{Ioan:} You told us you still have implants and rigs out there, right? It's like when your avatar crashes, except it's your personality instead.

\textbf{Douglas:} That's absolutely horrifying. I'll go ahead and add that to the bucket of fears right alongside nuclear and biological warfare.

\textbf{Ioan:} Again, they're not at all common, and they by convention have to be tied to a physical object. Any time that someone has considered designing ones that aren't or which are more widespread, there's an incredible backlash. Happens once every twenty years or so.

\textbf{Douglas:} That's not super encouraging, but I'll try not to let it get to me.

\textbf{Ioan:} Well, let's change the subject, then, just to keep it from being anxiety-inducing. I know that May will ask this, so, when do you think you'll upload?

\textbf{Douglas:} Hah, well, I guess she would. I was thinking within a year.

\textbf{Douglas:} My duties are all wrapping up all at once, it feels like, so, maybe when they tell me to get planet-side.

\textbf{Ioan:} I have a suggestion, if you're interested.

\textbf{Douglas:} Oh?

\textbf{Ioan:} Upload on the one-year anniversary of the launch.

\textbf{Douglas:} Why?

\textbf{Ioan:} The Odists are total suckers for symbolism. If you do it on Launch day, May will lose her damn mind.

\textbf{Ioan:} In a good way, I mean. You'll get to see it, I'm sure. It's quite the spectacle.

\textbf{Douglas:} It's not a bad idea, actually. I'll pester the commission to ensure that I'm up here for that.

\textbf{Ioan:} Really? You're seriously considering it?

\textbf{Douglas:} If you had left the planning up to me, I'm not sure I'd ever do it. I'd just keep on cycling and worrying and living up in my head, but give me a little push, and I'll make it happen.

\textbf{Ioan:} I believe it. Keep me in the loop!

\textbf{Douglas:} Should I tell May or keep it a surprise?

\textbf{Ioan:} Can you keep it a secret for the next six months or so?

\textbf{Douglas:} Sure, I guess.

\textbf{Ioan:} Great. Please do. I want to see her go nuts.

\textbf{Ioan:} Strange question: you say that you don't start projects without a little push, but you also said that you applied for the launch director position on a whim.

\textbf{Ioan:} Are you sure there was no push for you to apply?

\textbf{Douglas:} Huh.

\textbf{Douglas:} I\ldots will have to think on that and get back to you.

\textbf{Douglas:} Why do you ask?

\textbf{Ioan:} Well.

\textbf{Ioan:} I'm not sure I can tell you without compromising some agreements on my end.

\textbf{Ioan:} With May and the other Odists, I mean.

\textbf{Ioan:} I'll make sure May tells you at some point, though, alright?

\textbf{Douglas:} Sure.

\textbf{Douglas:} I mean, it sounds complicated, but like you say, they're a complicated group.

\textbf{Douglas:} I'll think about it, though, see if I can remember anything.

\textbf{Ioan:} Thanks!

\textbf{Ioan:} May's all sacked out in bed, so I think I'll go join her.

\textbf{Ioan:} Goodnight, Douglas. Sleep well, and keep in touch!

Douglas made his goodbyes and then stretched out on his own bed, still grinning at the idea of Ioan sharing a bed with May and still not knowing whether or not they were in a relationship.

He turned the lights off and rolled enough to pull his covers over him. It'd be early to fall asleep, but it's not like he had much else to do, so he might as well do the same.
