\hypertarget{douglas-hadje-2325}{%
\chapter{Douglas Hadje — 2325}\label{douglas-hadje-2325}}

\textbf{May Then My Name Die With Me:} Douglas

\textbf{May Then My Name:} Douglas Douglas Douglas Douglas Douglas Douglas Douglas Douglas Douglas Douglas Douglas

\textbf{May Then My Name:} Mister Douglas Hadje, Master of Spaceflight and Doctor of whatever the hell your degree is in, call on line one.

\textbf{May Then My Name:} Oh, whatever. Just let me know when you get this!

It took a moment for Douglas to compose himself when he returned to his terminal after yet another evening of sitting in the Pollux control tower, now largely remade into an observation bubble, despite the increased gravity. It was quiet, it was dark, it was calm, and there was nothing to see except the same Earth-rise-moon-rise cycle every thirty seconds or so.

So, when he returned back to his room to a series of messages that felt loud, bright, raucous, it took a moment for his mind to adjust.

\textbf{Douglas Hadje:} My doctorate is also in space flight. I did my thesis on booster stress in reusable launch vehicles.

\textbf{Douglas:} Now, how may I help you?

\textbf{May Then My Name:} That is just \emph{fantastically} boring, my dear.

\textbf{Douglas:} Oh, it was boring as hell. I'll send it to you sometime.

\textbf{May Then My Name:} If you would like.

\textbf{May Then My Name:} I will not read it.

\textbf{May Then My Name:} Also, hi. Good evening. Have a good day?

\textbf{Douglas:} That was also boring as hell. I keep going for walks or trying to read or whatever, but there's only so much here to keep myself interested when I based most of my life on my job.

\textbf{May Then My Name:} That does not sound healthy.

\textbf{Douglas:} Can confirm: not healthy.

\textbf{May Then My Name:} Well, fucking upload already.

\textbf{May Then My Name:} We can go out for drinks and build up your tolerance again, or you can go walk some place that has a horizon. Ioan took me on a hike a while back, we can take you there.

\textbf{Douglas:} Before long. Probably within the year, actually.

\textbf{May Then My Name:} !!!

\textbf{May Then My Name:} Good! Excellent! I will look forward to the day.

\textbf{Douglas:} I'll keep you apprised, then. Where's Ioan today?

\textbf{May Then My Name:} Ey is here, but in heads down mode. It can get frustrating sometimes, because when ey gets in that mindset, ey will not be able to fork effectively. If ey does, the fork will just spend all of eir time whining about not being at work.

\textbf{Douglas:} Like me, huh?

\textbf{May Then My Name:} You said it, not me.

\textbf{May Then My Name:} Anyway, I called you up to ask you about something that you have mentioned a few times so far. Do you have it in you to answer some questions?

\textbf{Douglas:} Sure, why not. My first meeting is in the afternoon, tomorrow, and it's just a weekly safety briefing. Talk my ear off! I could use the distraction.

\textbf{May Then My Name:} Yes, you certainly could.

\textbf{May Then My Name:} You mentioned that there had been sabotage attempts. We were surprised when we heard that initially, but it had been in the middle of some other conversations that we did not want to derail, so we have been holding onto it until a time when there was not much else going on. Can you tell us about those?

\textbf{Douglas:} Oh, sure.

\textbf{Douglas:} There were two big ones and one small one. You heard the small one, which was that tech knocking me off the edge of the torus. The other techs out there with us tackled him and tied him up in his own tether to bring him back into the station. One of them suggested just ripping off his suit there, but it was a reaction out of anger, and it's hard to stay angry out in space, so they did the right thing.

\textbf{Douglas:} He was brought inside, taped to a chair (there used to be a security station for when the torus was a hotel, but it was repurposed at some point), and then confined to quarters until the next shuttle could come pick him up.

\textbf{May Then My Name:} How did he even get in there to begin with?

\textbf{Douglas:} As far as I could tell, just lying really well. It was his second EVA, so there wasn't exactly much time to suss out if there was anything up with him.

\textbf{Douglas:} It's weird, though. You have to have an MSf to even do EVAs here, and even just getting into that program, not to mention getting a job out here, requires a lot of psychological testing and the like. He must have been pretty good at lying.

\textbf{May Then My Name:} You said that he was sent back to Earth and charged. What were the charges? How did that work?

\textbf{Douglas:} I don't know too much about it, honestly. I know he was charged with attempted murder and there was a whole flurry of articles about how the case was groundbreaking as the first attempted murder in the vacuum of space. He was convicted, then probably sentenced to jail.

\textbf{May Then My Name:} What does jail look like?

\textbf{Douglas:} Depends on where you are and what you did. I think for something like attempted murder, he was just put in sim for a while, unable to back out.

\textbf{May Then My Name:} Really? What a nightmare.

\textbf{Douglas:} It's not like he's just put in a sim of a jail cell to rot or anything. As far as I know, it's just a tightly regimented day, most of it in a solitary sim, the rest in a shared sim with other prisoners.

\textbf{May Then My Name:} Not able to back out, though. Even the thought of that makes me feel ill.

\textbf{Douglas:} Why? Aren't you kind of in that state right now?

\textbf{May Then My Name:} When you upload, you will see how the comparison fails. But it is terrifying because I am old enough to remember the lost.

\textbf{Douglas:} That virus or whatever that was getting people stuck in the 'net? Didn't that hit Michelle?

\textbf{May Then My Name:} Yes. Remember when I talked about how she had 80\% bad days? That is why.

\textbf{Douglas:} Oh, shit. Yeah, I can see how that'd be terrifying, then.

\textbf{May Then My Name:} On to brighter subjects, then. You mentioned bigger sabotage attempts.

\textbf{Douglas:} Much brighter.

\textbf{Douglas:} Well, one of them was here station-side, and one was back planet-side. The one up here was when one of the mechanics (who don't need an MSf) had smuggled up some type of plastic explosive in their luggage. I think it was actually the fabric lining of the case, something where thin strands of explosive were coated in plastic and woven just like one normally would. It was powerful enough and its target small enough, that even just that suitcase lining would have been enough to do the trick.

\textbf{Douglas:} They tore out the lining, rolled it into a rope, and wrapped it around a portion of the launch strut extrusion factory. It was about six years back, and the arms were already about 2800km long, so if the explosion had wound up actually causing enough damage, the stress of the arm would have torn the station apart, and likely taken the System with it.

\textbf{May Then My Name:} WHAT

\textbf{May Then My Name:} That seems like an awful important thing to not know as the sys-side launch director, Douglas.

\textbf{Douglas:} It was all hushed up by security (brought back up after my little incident on EVA). I wasn't allowed to tell you. Sorry, May Then My Name.

\textbf{May Then My Name:} Did they give you a reason for keeping it from us?

\textbf{Douglas:} They said it had political undertones because of the articles of secession. ``No other governmental entity shall declare war on or attempt to destroy the System.''

\textbf{May Then My Name:} They considered it an act of war?

\textbf{Douglas:} I guess so. If it was an act of war, then the System could retaliate. I'm sure they told someone over there who needed to know

\textbf{May Then My Name:} Then why are you telling me now?

\textbf{Douglas:} Well, our conversations are off the record, now. Besides, if I'm going to upload soon, it's also relevant to me in the same way it is to you.

\textbf{May Then My Name:} Well, alright. How were they caught?

\textbf{Douglas:} That's the weird thing. They turned themselves in. The cloth bomb had been in place for about a month, I guess, and they grew a conscience in that time, so they brought security over, admitted to what they'd done, defused the bomb, and let themself be sent back planet-side.

\textbf{Douglas:} Which actually brings me to the other big sabotage attempt. Apparently, they were working with a collective who were really unhappy with the launch overall, so there was also a suicide bombing at a launch facility during a tour which I guess was intended to take out the control room before it could be used for the next supply run.

\textbf{Douglas:} Cloth bomber struck a deal with the government for a lighter sentence (probably like my attacker received) for acting as an informant and ratting out the organization before the rest of the planned bombings could take place.

\textbf{May Then My Name:} Less immediately threatening to us, but still, that is terrible. Do you know why this collective (is this like a group, or is there a deeper meaning?) felt so strongly against Launch?

\textbf{Douglas:} Yes, a collective is a group of people who have decided to lose as much of their unique identity as they can to live as singular facets of a shared identity.

\textbf{May Then My Name:} Ioan will be fascinated to hear. Why is that?

\textbf{Douglas:} It actually started around a fictionalized account of forking. They sometimes called themselves clades, but the name never stuck. It's kind of a weird love/hate relationship with the System that they have. They love it enough to try and emulate it in their social groups, but they also loathe the idea of uploading and a lot of other things that go along with the System.

\textbf{Douglas:} de, on the launch commission, is a member of a much more liberal collective. Still will never upload, but really seems to take pride in their job.

\textbf{Douglas:} So I think it was some of that hatred that was at play. They hated the lack of control that is inherent in the System. They hated all that went into Secession, how it made the System this political entity. They hated Launch because, by phys-side collaborating with sys-side, it was a sign that we were equals. They felt that the System has been interfering with phys-side politics ever since Secession. They hated the System for lots of reasons.

\textbf{May Then My Name:} Do a lot of people phys-side think that the System is interfering with politics?

\textbf{Douglas:} Not really, no. There was a kerfuffle around it when uploading was incentivized that essentially no one remembers except for boring people like me who had to study it. There have been a few gripes here and there as other large political changes happened, like when governments merged or recessions hit. When things like that happen, I think a lot of people instinctively look for a boogeyman to pin it on, and the System is pretty convenient because it's not like you all can fight back, so you all turn into shadowy figures behind the politicians.

\textbf{May Then My Name:} Oh, that bit is definitely true.

\textbf{Douglas:} Yeah, figured as much. You all up there steepling your fingers and talking in hushed tones about how you're going to do everything from crash the economy to hire Michelle Hadje's distant ancestor specifically to work on your nefarious plot.

\textbf{May Then My Name:} Yep, got it in one.

\textbf{May Then My Name:} I am glad that none of these were successful on the scale that they had hoped. We do not know what happens to us if the System breaks. There have been a few instances of discontinuity over the centuries, but we don't see them except that systime jumps ahead. Were the System to explode in some fiery spectacle, we would just stop.

\textbf{May Then My Name:} Theologians and mystics have been disappointed to find no answers in what comes after death when one quits, so we are as in the dark as you are.

\textbf{Douglas:} Maybe a bit less, because at least one possibility of what comes after death for us is living sys-side.

\textbf{May Then My Name:} This is true! We are ghosts up here, haunting silicon and whatever else makes up the physical elements of the System these days.

\textbf{Douglas:} You may as well be ghosts, as far as people think planet-side. There have been various attempts at casting uploads in the light of ancestor worship in some places. I have no idea how those who are worshipped sys-side feel about being asked for courage or a healthy crop or whatever.

\textbf{May Then My Name:} I would be honored, personally. I have no one to haunt after two centuries but you. I am afraid that you are stuck with me.

\textbf{May Then My Name:} All I can do is bother you on a terminal, though, so I suppose that I am not that bad of a ghost.

\textbf{Douglas:} You're a pretty good ghost, I'd say. I'm looking forward to meeting you in person some day.

\textbf{May Then My Name:} I will beg you once more: please come join us soon. I know you said within a year, but if you do not live up to that promise, so help me God, I will move into your implants and never let you sleep again.

\textbf{Douglas:} Don't worry! I promise. You'll see me within the year. I've already put in word with both the launch commission and the clinic here, and they're fine having me stick around station-side until I can upload, so it's already (loosely) scheduled.

\textbf{May Then My Name:} !!!

\textbf{May Then My Name:} I am eager to meet you, Douglas Hadje, Master of Spaceflight and Doctor of Other Boring Shit!

\textbf{Douglas:} Goes both ways, May Then My Name Die With Me of the Ode clade.

\textbf{May Then My Name:} Excellent, excellent.

\textbf{May Then My Name:} Now, I should head off. Ioan is coming up for air from eir writing, so I am going to go chase em around the house, frothing like I am rabid.

\textbf{Douglas:} Have fun, say hi for me, don't stay up too late.

\textbf{May Then My Name:} Yes, father.

\textbf{May Then My Name:} Bye!

Douglas leaned back from his terminal and stretched his arms up toward the ceiling, leaning back in his chair.

Every time he talked with Ioan and May, he was once again faced with the realization that he had hardly needed Ioan to convince him at all. The two were the first people he could call friends that he'd had since school. Beyond that, though, something about May Then My Name seemed as though she was simply built to be liked, as though, whenever he talked with her, he had no choice but to like her.

It wasn't quite charisma, as, whenever he tried the word on for May Then My Name, it carried far too many implications of manipulation, and the last thing he could picture her doing was being manipulative.

She was weird, yes. Goofy, even. But there was nothing about her that was calculating or cold.

\emph{One more walk around the station,} he thought. \emph{Then I'll get to bed. January can't come soon enough.}
