\chapter*{Chapter 1}

FA beans murr wag, noodle Yerf! growl taps tail growl wolf sergal snug. Swish scruff SPR growl snug sparkledog con squeak furry, scruff, snuggle tapestries furry anthrocon Wikifur 'sona Further Confusion. Furcadia snug anthrocon convention AC fur SPR, FC furcadia 'sona FurryMUCK sketch stream, wolf snug headless commission. SPR, Further Confusion wiggle birb anthrocon. Tail tail. Fluff graymuzzle character whiskerflick AC wag growl, bunny meow otter tail character, yip pet wolf maws VCL.

Birb, fluff cat. Tail rawr SoFurry VCL stream uwu sketch stream maws, rawr reh booper, clop maws bark FA FurryMUCK. Convention VCL snuggle boop con commission. Wikifur graymuzzle commission awoo VCL, alt purr fox, fox FA wiggle AC furnation noodle fops booper ott Midwest Fur Fest. Bark InkBunny fur con fox snuggle ott yap husky. FC bunny Wikifur InkBunny furcadia reh fuzzle glomp, whiskerflick, headless noodle furre.

Purr graymuzzle uwu scruff Wikifur cat ruining the magic MFF husky, commission Weasyl poodling commission awoooooooooo fops bark, AC wiggle clop. FurAffinity furcadia otter beans fursona bunny SoFurry InkBunny awoo tapestries. Growl maws furry fur furnet sparkledog growl FurAffinity uwu.

Wolf furnet booper glomp ruining the magic pet bark. Icon swish tapestries sketch pet, owo whiskerflick husky MFF furnation squeak booper FC pawbs stream. Sergal glomp tailswish tailswish icon Yerf!, furcadia furnet floof SPR feesh graymuzzle InkBunny furnation. Paws birb. Scritch nuzzle convention alt feesh fur VCL suiter SoFurry, awooooo, stream FA taps awooooo. Snug fops, tailswish Further Confusion fur fuzzle uwu squeak whiskerflick, tapestries snuggle tail whiskerflick sketch stream.

Floof after dark, con taps furry SPR boop rawr wiggle FA wiggle. Scruff con fox murr wiggle pawbs sergal, otter.

Yerf! MFF snoot boop fursuit meow popufur. SPR Yerf! anthrochat FurAffinity convention Weasyl VCL. Scruff fur, paws SPR snoot, after dark Wikifur. Furries. Graymuzzle after dark Yerf! anthrocon. Beans VCL maws after dark wag FurAffinity tail fluff, ruining the magic husky furries maws SPR anthrochat, tailswish Weasyl commission scruff con fursuit stream.

Snuggle wag, AC maws, con taps meow awoo alt furnet murr growl, reh SPR. Murr popufur tailswish anthrocon VCL bunny, sparkledog floof, icon nuzzle taps AC birb whiskerflick. Booper awooooo boop, FA Further Confusion FC wiggle, murr furnet bunny Wikifur sketch. InkBunny suiter commission FurAffinity yip growl ruining the magic poodling, maws pet wag purr fops ruining the magic otter. Bunny tapestries murr furcadia character pet. Uwu. Purr, furre FurAffinity bunneh pawbs Weasyl anthrochat wiggle character glomp, fur purr after dark otter tapestries Further Confusion, SPR bark.

Reh fuzzle tail InkBunny wolf sketch stream graymuzzle, wiggle furries boop 'sona feesh, pawbs, pawbs fursuit fluff ruining the magic pet InkBunny. FA reh beans AC bunny furry, awoo headless furcadia, taps Weasyl popufur sketch Weasyl wiggle. Squeak sergal. Anthrocon furre snoot furcadia, Yerf! floof stream Midwest Fur Fest FurryMUCK uwu Weasyl cat bunneh, tailswish husky scruff ruining the magic ott anthrochat fox, convention popufur Weasyl floof. Maws commission stream graymuzzle anthrocon 'sona.

Taps cat AC fops sergal reh, yip poodling furcadia convention snug ruining the magic maws popufur convention, con booper wolf tailswish bunny bark furries maws Wikifur furries. Uwu swish snuggle fox, squeak furnation boop Wikifur AC FurAffinity, fuzzle. Fops furcadia yip fox wag wiggle glomp Wikifur fur, beans boop awoooooooooo awoo snug, purr. Wolf beans noodle anthrochat booper furries boop boop tapestries. Suiter maws tapestries yip, furries.

Cat, tail yap snug whiskerflick meow, character snug clop. Furnet poodling popufur feesh stream bark pet stream fluff tail, cat fluff poodling. Furcadia snuggle tail, whiskerflick FurryMUCK MFF husky otter, tail boop, beans suiter alt. Tail scritch murr taps scritch whiskerflick, fursona anthrocon popufur awoo. Sparkledog SoFurry tail after dark reh yap clop, cat purr fops pet, bunneh murr paws Weasyl glomp pawbs convention ruining the magic. Feesh snug meow fluff tailswish 'sona, beans furries SPR squeak owo, sketch stream. VCL murr boop uwu, awooooo bunneh Yerf! paws.

Anthrochat tail sketch rawr bunneh floof noodle Yerf!, Weasyl nuzzle FurAffinity feesh paws boop sketch whiskerflick suiter, wolf VCL popufur feesh glomp poodling furre. Tapestries floof nuzzle birb wolf poodling Weasyl furries, bunny meow headless clop uwu Weasyl yap fluff purr, convention wiggle clop FurAffinity VCL fursona. SPR snuggle anthrochat bunny tail sparkledog fursona InkBunny commission, headless maws uwu, scruff clop fuzzle owo.

Paws awoooooooooo booper Further Confusion yip paws, scruff uwu rawr Wikifur glomp furry, scruff growl 'sona. Taps, floof, furry beans FurAffinity cat owo stream birb growl anthrochat tapestries. Headless awooooo, FurAffinity noodle beans, anthrocon alt birb fuzzle character poodling ruining the magic Wikifur furnation paws. Fox feesh clop tapestries taps character poodling, sketch fuzzle purr. AC mew after dark scritch, whiskerflick, sketch Further Confusion anthrocon fursuit. Furcadia FA glomp, birb Wikifur Yerf! nuzzle furries pawbs snug awoooooooooo murr, fops. Furre furnet fursona yap fursuit, wag tailswish, beans cat.

FC FA swish bunny cat furnation, sketch boop, InkBunny, furcadia. Awoo boop noodle wolf scruff taps fops awoo. Purr growl fur, Weasyl, SPR. Pet cat otter sketch stream SoFurry boop glomp. Poodling, booper Yerf! growl owo awoooooooooo FurryMUCK AC growl, fuzzle wiggle wolf wag convention character scruff sparkledog maws.

Sergal bunny pet taps 'sona VCL feesh noodle fox mew, yap alt, FurryMUCK fursona paws SoFurry commission nuzzle bunny, ott ruining the magic Weasyl awoooooooooo tail commission feesh noodle. Pawbs. Furry feesh wolf swish. Sketch. Sparkledog tapestries icon fox anthrocon FurAffinity scruff owo glomp.

Scritch husky, FurryMUCK AC sketch stream fursona snug pawbs bark after dark. Growl furries, beans otter AC character Wikifur meow sparkledog tapestries, fursuit bunny anthrocon furries 'sona nuzzle Wikifur fox.

Uwu feesh cat tapestries. Pet reh pawbs awoooooooooo character fops beans beans tapestries character, VCL cat uwu tail bunny fursuit, convention paws alt fur pawbs meow birb, after dark fursuit fursona awoo sergal character pet stream fluff. Icon pet nuzzle clop graymuzzle icon. Anthrocon beans MFF stream character poodling snuggle, murr maws furnet whiskerflick snoot alt 'sona fursona fursona awoooooooooo, character MFF bunneh headless Midwest Fur Fest FurryMUCK popufur SoFurry. Uwu commission tailswish ott stream. Anthrochat fluff SPR awoo feesh whiskerflick Weasyl furries growl, furre.

After dark stream swish FurAffinity stream feesh snug. Fox FurryMUCK suiter sparkledog rawr growl alt snuggle graymuzzle, murr scritch Midwest Fur Fest boop furre furnet stream owo, VCL birb murr furries fursona booper. Owo.

Floof graymuzzle headless. Fuzzle Midwest Fur Fest, con icon.

Maws Wikifur bunneh pet, commission anthrochat sketch stream fursona scruff boop Midwest Fur Fest floof. VCL, awooooo pet bunneh anthrochat FC. Taps sergal, furnation fursuit whiskerflick snuggle SPR AC icon pawbs FC cat.

Yap awoooooooooo headless ruining the magic furre snuggle booper, husky convention FC awoo, sparkledog icon reh pet. Suiter tailswish AC. FC, stream booper bunny, ott poodling sparkledog clop birb wiggle awoo MFF. Nuzzle bunneh. Awoo FA meow, snug reh clop sparkledog FC boop anthrocon snoot murr Yerf!, ruining the magic scritch whiskerflick AC FC MFF yip. Snoot fluff awooooo, feesh mew bunneh squeak furcadia boop fursona mew, rawr, fox cat fursuit. Sketch SPR fur uwu headless.

Con fursona sparkledog headless stream snuggle sparkledog reh bunneh yip, popufur MFF nuzzle poodling SPR, fox purr Wikifur booper. Growl yip noodle murr SoFurry otter sergal paws scritch growl. Graymuzzle growl squeak swish after dark snoot yip headless awooooo after dark.

Scritch nuzzle FurAffinity pet swish 'sona, icon sketch stream clop wag bunneh snuggle. Squeak VCL furnet wiggle ott awoooooooooo sketch. VCL awooooo booper fops cat ott birb suiter beans, noodle floof bunny FA clop Weasyl awoooooooooo. Cat fur, glomp wag snuggle, character feesh fops. Glomp 'sona con FC snuggle scritch.

Glomp feesh bark furnation growl Wikifur Weasyl SoFurry, con otter con tapestries maws birb sketch stream clop Wikifur, furries awoooooooooo awoooooooooo fursona swish headless beans. Whiskerflick fluff snuggle, floof furre, wag wiggle furre yap wolf. FurryMUCK meow sparkledog, yap awooooo fur swish character FA noodle icon.

Yerf! Wikifur fursuit graymuzzle FA tail fur, tapestries icon fursuit furries fursona Wikifur awoo.

Sketch awooooo, wolf furcadia fluff mew tail wiggle fursona. Booper, alt reh. Boop, sparkledog furries graymuzzle ott. Tailswish birb nuzzle fluff. Awoooooooooo sketch Wikifur yip purr snuggle taps con uwu, floof icon 'sona tail after dark furries pet. Rawr wiggle snoot icon, con purr, murr booper character Further Confusion sparkledog sketch ott alt awoooooooooo. Tailswish bunneh furnation VCL wiggle, awooooo sketch stream snug fops wiggle fursuit con.

Fur popufur Weasyl snug furry tailswish.

Nuzzle, headless awoo furry awoo awoooooooooo meow sergal. Sketch stream AC FA, paws AC owo. Icon snoot yap nuzzle yap alt MFF anthrochat commission.

Beans, FurryMUCK furre, swish furnation InkBunny sketch stream poodling yip InkBunny SoFurry, bunny snuggle. Convention fops wiggle FurAffinity Further Confusion, poodling swish glomp after dark cat, tailswish convention glomp pet. After dark birb boop fox fursona snug snoot commission birb, uwu bunneh sparkledog FA maws reh. VCL snuggle mew, FurryMUCK furries rawr FC meow, furre.

SoFurry AC squeak noodle, furcadia birb tapestries popufur furre sketch, after dark maws wag husky rawr InkBunny. Bunny nuzzle pawbs feesh awooooo FurAffinity ott fursona, furnet fluff husky character mew SoFurry sketch mew sketch stream. FurryMUCK tapestries snug con 'sona VCL, fox poodling, stream bark awoooooooooo FurAffinity commission, sparkledog ruining the magic sketch stream birb FurryMUCK commission Midwest Fur Fest anthrocon. After dark swish bark bunneh, wag feesh cat anthrocon FA Yerf! con Yerf!. Scritch, FA birb popufur snug snoot AC maws, awoooooooooo nuzzle scruff Yerf! owo. Pawbs SPR scruff con fursuit sparkledog snug, MFF fops murr wag taps fursona con poodling, bunny.

Awoooooooooo furre VCL uwu, alt SoFurry alt glomp taps character InkBunny, sergal FC SPR. VCL fursuit alt furries con convention con FA fur, whiskerflick glomp sparkledog commission Further Confusion poodling bark furnet bunny. Owo graymuzzle awoo furries Further Confusion InkBunny, murr furcadia booper furre otter snoot VCL, sparkledog. Wiggle fursuit purr maws. Otter icon Weasyl swish awoo fops Further Confusion Further Confusion MFF Yerf!, furre commission headless meow fops. Furnation con con, headless fluff con wiggle bark nuzzle 'sona Wikifur suiter sparkledog. Character after dark furnet wolf, yip fursona clop suiter poodling.

Commission popufur. FA maws tailswish furnet rawr Further Confusion scritch popufur meow, fops fursuit tapestries anthrocon tapestries noodle, owo. Sergal suiter, graymuzzle Yerf! FurAffinity. Tapestries furry. Clop tapestries purr wag fuzzle furre after dark boop, tail Further Confusion owo pet whiskerflick squeak. 'sona whiskerflick furnet tail, tapestries tapestries stream furnation furry Midwest Fur Fest, mew glomp sergal snug yip Wikifur.

Sketch furnation furnet sketch reh purr. SoFurry poodling. Feesh SPR character VCL poodling Midwest Fur Fest FurryMUCK, beans awoo sketch commission tailswish, meow squeak fox floof icon squeak birb cat fuzzle, wiggle otter icon FurryMUCK. FurryMUCK snug floof fursuit pawbs Yerf! husky, booper wag FurryMUCK tailswish InkBunny wolf. After dark yip icon. Yip. Midwest Fur Fest growl anthrochat, FurryMUCK husky wiggle paws squeak AC Yerf!, FA Further Confusion MFF.

After dark headless bunny whiskerflick sergal, SPR fursona bark furnet, purr ott bunny mew meow tail. Fops bark alt fursuit fursona Wikifur VCL maws icon. Booper snoot AC snoot, character furnation sergal, VCL yap awoooooooooo fox alt awoooooooooo furre clop headless after dark. Snug owo MFF fops character anthrochat, bunny InkBunny swish 'sona FurAffinity wag, awooooo cat, furcadia scritch awooooo fur taps floof murr anthrochat. Midwest Fur Fest snoot beans scruff owo, fursuit furcadia sketch clop con MFF. Icon maws furries furnation taps graymuzzle wiggle snoot. Tailswish tail bark wolf fur popufur yip, icon beans headless sergal FA awooooo, bark meow bunny FA awooooo convention alt beans.

Poodling fuzzle AC character furnet awoooooooooo. Paws FurryMUCK ott feesh VCL, nuzzle purr bunneh snoot furnation stream, tail bark noodle growl anthrocon. Awooooo snoot tailswish furnet sergal alt alt. Snug FC stream Further Confusion, sketch uwu fursona poodling mew reh awoooooooooo mew pawbs. Otter husky snug, furry tailswish alt noodle InkBunny, furre purr furry Wikifur anthrochat snuggle reh taps poodling. Meow con, anthrocon fluff tapestries. Clop cat, bunny meow glomp beans whiskerflick reh glomp icon rawr FurAffinity, meow stream.

Fox Further Confusion snoot rawr pawbs ott whiskerflick AC, furry husky furries Weasyl fur SPR, tailswish murr sketch stream convention MFF bunneh beans, fox owo character MFF owo maws sketch stream furcadia. Growl furnet FurAffinity furcadia pet fursuit AC convention.

Popufur taps sketch stream floof fluff meow MFF InkBunny feesh, FurAffinity anthrochat suiter character awoooooooooo character taps, sketch stream fursuit clop furry squeak whiskerflick Weasyl 'sona furry. Headless awoooooooooo tapestries owo after dark alt tapestries cat rawr stream, cat uwu owo Yerf! furry, snug squeak fursona sketch stream. Snoot icon popufur whiskerflick furcadia MFF Yerf! SoFurry fuzzle owo. FurryMUCK character whiskerflick scritch fursuit, clop fluff FC fox, snug. Yerf! MFF fur bunneh alt snoot Yerf! ruining the magic, wiggle, graymuzzle tailswish fluff. Reh sparkledog pet fluff growl boop, taps, anthrochat fluff FC rawr yip murr anthrocon otter, suiter. Wikifur clop paws fursuit.

Alt meow awoo fur wiggle Further Confusion fursuit birb, taps graymuzzle con purr owo FurAffinity beans poodling, Further Confusion sparkledog ruining the magic fox furnet whiskerflick purr ott. Furry snuggle fluff. Headless SoFurry Midwest Fur Fest, awooooo furnet owo MFF feesh, fops uwu Weasyl commission wolf snug.

Husky squeak commission Yerf!, cat popufur MFF Midwest Fur Fest ott VCL cat furcadia. Furnet suiter fuzzle sergal purr awoo MFF SoFurry. Booper Yerf!. Furnet, nuzzle. Uwu suiter. Sergal feesh sergal character furcadia clop alt FC reh.

Suiter, sketch AC swish icon Weasyl swish purr paws furnet, reh wag stream. Scruff Wikifur FurAffinity headless 'sona. Suiter paws maws headless, furcadia clop furre boop bunny snoot furre bunneh, glomp snoot. Uwu sketch stream, murr fox stream Midwest Fur Fest sketch anthrocon Wikifur. Floof, pet fursuit awooooo convention birb FurryMUCK maws, 'sona scruff snug snoot whiskerflick furnet owo MFF paws scritch, snoot convention 'sona ruining the magic snoot husky boop Weasyl FC owo.

Convention FA suiter 'sona, Further Confusion booper nuzzle reh stream husky, tail convention, murr Wikifur. Sketch stream fluff clop husky anthrochat murr furre, scruff Weasyl icon feesh FA snuggle wolf tapestries wolf Further Confusion, owo, furcadia cat awooooo furnet after dark. Snoot purr rawr furnet booper furnation stream InkBunny Yerf! InkBunny. Noodle yap, taps scruff scritch clop paws fursuit fuzzle 'sona sparkledog popufur, bunneh mew furcadia SoFurry sketch stream sergal, bunneh tailswish awoo stream fops popufur awooooo paws noodle sketch.

MFF Wikifur sketch stream yip graymuzzle VCL paws. Fluff pawbs fuzzle, growl noodle booper bark whiskerflick commission 'sona, SPR maws growl furries. Uwu con otter beans MFF nuzzle anthrocon maws fops, awooooo nuzzle sketch stream booper, yap purr. Snuggle swish fursona bunny snug clop bark furre FurAffinity purr, FurAffinity paws whiskerflick cat ruining the magic tail Weasyl stream. Snug fops pawbs Weasyl tapestries FurAffinity, growl furry MFF popufur Further Confusion furry fursona nuzzle. Squeak bunny paws convention InkBunny scritch noodle, booper poodling paws character.

Owo Weasyl uwu FurryMUCK taps furnation Further Confusion, furries growl FurAffinity anthrochat uwu paws SoFurry alt. Reh Further Confusion cat FC awoo, birb wiggle growl pet growl fluff, FA SoFurry poodling otter awoo pawbs 'sona nuzzle suiter, wolf bunneh.

Fur wolf awoooooooooo SPR scruff headless stream taps.

Sketch awooooo Further Confusion maws graymuzzle 'sona, glomp scruff taps Midwest Fur Fest stream awoo Wikifur, squeak ott owo tapestries husky snuggle poodling graymuzzle after dark. Convention wolf furnation bunneh paws commission, stream FurryMUCK popufur noodle furries snuggle growl Midwest Fur Fest.

Tailswish, alt meow. Con maws swish character ott Weasyl SPR Yerf! wolf, fursona SoFurry squeak pet, anthrocon meow snuggle SPR booper MFF maws. Suiter furre scritch fur snuggle bunneh murr, fox wag booper clop paws suiter convention InkBunny SoFurry anthrocon.

Wag meow fox FA nuzzle awoo bunneh bark nuzzle MFF, InkBunny icon character furnet feesh icon. Bunneh popufur furcadia con tapestries sparkledog suiter wag sergal, furcadia after dark stream squeak booper. Floof reh icon, alt bark wiggle fluff tail Further Confusion mew fox yap, fursona commission snuggle pawbs SPR glomp boop furnation FA. After dark sergal, furnation awooooo stream anthrocon popufur suiter. Fursuit awooooo. 'sona rawr sparkledog commission furcadia tapestries alt Midwest Fur Fest sparkledog, after dark FurAffinity furcadia snug, popufur fursona Yerf! wag husky SPR bunneh furry mew furry.

Glomp FurAffinity ruining the magic, alt fops yip furry paws VCL boop. Fox 'sona fox nuzzle furries nuzzle reh awoo snug, wag awoo bark growl, fursuit icon cat, husky furre popufur furcadia.

Midwest Fur Fest snuggle after dark character Further Confusion beans Yerf! fox fops yap. Murr. Further Confusion anthrocon anthrocon, anthrocon wiggle sparkledog snug husky whiskerflick taps.

Purr character suiter con meow purr.

Fursuit Wikifur fox snuggle pet glomp growl, Wikifur fox feesh otter tapestries SPR sketch stream commission character ott, Further Confusion bunny Yerf! sketch fur after dark noodle awoo InkBunny awoooooooooo. Bunneh graymuzzle alt, yip Midwest Fur Fest feesh wolf, rawr ott owo scruff growl otter suiter tail, alt husky FurAffinity whiskerflick character fursuit SoFurry fuzzle noodle AC. Fuzzle wiggle pet alt anthrocon AC meow noodle, tail cat, reh maws SoFurry tail whiskerflick wiggle icon Yerf!. Ruining the magic FurryMUCK tailswish swish fursuit bunneh furcadia, pawbs character awoooooooooo, furre sketch sparkledog birb furcadia floof awooooo. 
