\section{--- \textit{February, 2017}}

\begin{verse}
I see your past in cross-processed film,\\
in blown-out colors and over-saturation.

\vin You told me all about it, told me grand stories:\\
\vin you were going to go back in time and save the world.

I see your past in yellows and browns,\\
in umber and sienna and amber, in a younger sun.

\vin You sat and told me how --- and you were always sitting ---\\
\vin you thought past-you dreamt of a future less complicated than today.

I see your past through film-grain and vignette,\\
with a thick white border, space on the bottom to write.

\vin You told me how you learned so many imperfect things,\\
\vin in so many less than ideal ways, always at inopportune times.

I see your past in architectural drawings of unrealized buildings,\\
in paperback covers reaching towards heaven, in trillions of words.

\vin You figured past you dreamt of, not perfection,\\
\vin but a world unconstrained by so many failures.

I see your past with no me in it,\\
and wonder if past-you dreamed of us.
\end{verse}
\newpage

\section{--- \textit{February, 2017}}

\begin{verse}
Resuscitating ancient coins in class, we learned,\\
takes a toothbrush and olive oil.\\
Slow, steady strokes across, around...\\
soft bristles dislodging soil\\
one speck at a time.\\
But no one that day was nearly as blessed,\\
seeing a coin shine through\\
at the end, full relief brightly expressed,\\
as I was to see you smile.
\end{verse}
\newpage

\section{--- \textit{February, 2017}}

\begin{verse}
When you arrive,\\
the whole world gets slow.\\
Sluggish, amber-colored air\\
mellows lively conversations.\\
Everyone stops, marvels,\\
turns eagerly toward you;\\
and there are no complaints\\
about warming our faces in the sun.
\end{verse}
\newpage

\section{--- \textit{February, 2017}}

\begin{verse}
We fit together in the strangest ways\\
and seem to seek new seams to savor.\\
Such joins are hardly perfect,\\
thread tugging fabric unevenly\\
unless it's reinforced over and over again.\\
We seem to seek new seams to savor,\\
and, weak though they are,\\
revel in the imperfect unevenness of joining.
\end{verse}
\newpage

\section{--- \textit{February, 2017}}

\begin{verse}
"Comrade" would I call you,\\
and "brave," and "fierce" and "true".\\
"Lovely" have I called you,\\
and hope but to live up to\\
the example which you set for me.

So, comrade, onward, ever onward.\\
I know I cannot hope to offer\\
much but word on cloying word,\\
dull rhymes I strain to proffer:\\
small flowers, small gifts, camaraderie.
\end{verse}
\newpage

\section{--- \textit{February, 2017}}

\begin{verse}
Complementary, clashing anxieties.\\
Dull clamor of intersecting feelings.\\
Need, desire, craving, even jealousy.\\
Worry, fear, care, prayerful fretting.\\
Love, lust, friendship, a need to share.\\
Emotions on emotions on emotions,\\
and, often, comfortable silence.
\end{verse}
