\documentclass{memoir}
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont{Gentium Book Plus}
\begin{document}
\section*{Group edit time!}

Alright, it's time for the final group edit! Here's what we're going to do: each of us will read our story as well as the story before and after ours (for the first and last stories, wrap around to the last and first) and look for the obvious spelling and grammar mistakes that aren't part of the style. Do the same for bios at the end.

Please also keep an eye out for the following:

\begin{itemize}
  \item Curly quotes that are mismatched (e.g: ''Oh no!'' or ``This apostrophe isn`t right.'').
  \item Space on either side of dashes and ellipses (e.g: ``Uh oh --- I mean\ldots{} no.'').
  \item Section dividers where they should be or missing section dividers.
  \item Missing or extra diacritics.
\item Awkward page breaks---if your PDF reader has a `dual/two-up' layout, turn that on---you may need to specify `open odd', `center first page', etc. so that the title page is on the right-hand side. Otherwise, keep in mind that page numbers are on the outside corners; widows/orphans that aren't on a page \emph{turn} are less bad than those on a page turn. For more info, there's a whole \emph{\href{https://writing.drab-makyo.com/layout-and-design/}{presentation}} if you want to know more.
  \item Awkward ends of chapters---that is, a chapter ending that has just one or two lines at the top of a page.
  \item Awkward hyphenation (I like to avoid names, but some of them are just long and it'll happen).
  \item Missing punctuation at the end of a paragraph.
  \item Indented paragraphs after a section divider.
  \item Extra/missing paragraph or line breaks.
  \item Suggestions for a different order of the stories
\end{itemize}

I think I've gotten most of the typesetting stuff, but if you find any of these, write them down in \emph{\href{https://docs.google.com/document/d/15Nxm2nm1xkqlmeFr-Nmw2E1KVGYrnD0w5vPffdfcRUU/edit?usp=sharing}{the edits document}} on the page dedicated to the story with the page number (the one at the bottom of the page, not the number of pages from the start of the PDF). Please finish this by October 15 if possible. I don't imagine any of these changes will change the page-count, but that's the deadline we've given to the cover artist.

Have at it!
\end{document}
