\documentclass[10pt]{memoir}

\def\watermarkloaded{0}

\input{includes/variables}
\input{includes/draft}
\input{includes/frame}
\input{includes/packages}
\input{includes/pagelayout}
\input{includes/geometry}
\input{includes/toc}
\input{includes/font}
\input{includes/title}
\input{includes/secdiv}
\input{includes/hyphenation}

\begin{document}
  \nopartblankpage
  \makeatletter
  \renewcommand*{\beforepartskip}{\null\vfill\thispagestyle{empty}}
  \renewcommand*{\afterpartskip}{\par\vskip1cm%
  \@afterindentfalse\@afterheading}
  \makeatother
  \setcounter{part}{0}

  \frontmatter

  \thispagestyle{empty}
  \null
  \vfill
  \begin{flushright}
    \DisplayFont Post-Self
  \end{flushright}
  \vfill
  \cleardoublepage

  \pagestyle{plain}

  \doublespacing

  \begin{flushright}
    \null
    \vfill
    {\Huge\DisplayFont Post-Self}

    \vfill

    {\Large\DisplayFont Madison Scott-Clary}
  \end{flushright}
  \thispagestyle{empty}

  \newpage

  \input{includes/copyright}

  \setcounter{tocdepth}{-1}
  \tableofcontents*
  \newpage
  \null
  \cleardoublepage

  \mainmatter

  \pagestyle{ourbook}

  \cleardoublepage
  \markboth{Qoheleth}{}
  \book{Qoheleth}

  \addcontentsline{toc}{part}{Qoheleth}
  \part*{Qoheleth}
  \null
  \thispagestyle{empty}
  \vfill
  \begin{quote}
    \emph{Whatever is has already been, and what will be has been \mbox{before;} and God will call the past to account.}

    --- Ecclesiastes 3:15
  \end{quote}
  \vfill
  
  \input{qoheleth/content/RJ/001}
  \input{qoheleth/content/RJ/002}
  \input{qoheleth/content/Ioan/001}
  \input{qoheleth/content/RJ/003}
  \input{qoheleth/content/Carter/001-a}
  \input{qoheleth/content/RJ/004-a}
  \input{qoheleth/content/Carter/001-b}
  \input{qoheleth/content/Ioan/002}
  \input{qoheleth/content/RJ/004-b}
  \input{qoheleth/content/Carter/002}
  \input{qoheleth/content/RJ/005-a}
  \input{qoheleth/content/Ioan/003-a}
  \input{qoheleth/content/RJ/005-b}
  \input{qoheleth/content/Ioan/003-b}
  \input{qoheleth/content/Carter/003}
  \input{qoheleth/content/RJ/006}
  \input{qoheleth/content/Qoheleth/001-a}
  \input{qoheleth/content/Carter/004}
  \input{qoheleth/content/RJ/007}
  \input{qoheleth/content/Qoheleth/001-b}
  \input{qoheleth/content/Carter/005}
  \input{qoheleth/content/RJ/008}
  \input{qoheleth/content/Ioan/003-c}
  \input{qoheleth/content/RJ/009}
  \input{qoheleth/content/Carter/006}
  \input{qoheleth/content/Ioan/003-d}
  \input{qoheleth/content/RJ/010}
  \input{qoheleth/content/Ioan/004}
  \input{qoheleth/content/Sasha/001}
  \input{qoheleth/content/Ioan/005}
  \input{qoheleth/content/RJ/011}
  \input{qoheleth/content/Carter/007}
  \input{qoheleth/content/Qoheleth/002}
  \input{qoheleth/content/RJ/012}
  \input{qoheleth/content/Ioan/006}
  \input{qoheleth/content/Sasha/002}
  \input{qoheleth/content/RJ/013}
  \input{qoheleth/content/Carter/008}
  \input{qoheleth/content/Ioan/006-b}
  \input{qoheleth/content/Carter/009}
  \input{qoheleth/content/RJ/014}
  \input{qoheleth/content/Carter/010}
  \input{qoheleth/content/Ioan/007}
  \input{qoheleth/content/RJ/015}
  \input{qoheleth/content/Qoheleth/004}
  \input{qoheleth/content/Ioan/008}
  \input{qoheleth/content/RJ/016}
  \input{qoheleth/content/Qoheleth/005}
  \input{qoheleth/content/Ioan/009}
  \input{qoheleth/content/Qoheleth/006}
  \input{qoheleth/content/Carter/011}
  \input{qoheleth/content/Ioan/010}
  \input{qoheleth/content/Sasha/003}
  \input{qoheleth/content/Ioan/011}
  \input{qoheleth/content/Sasha/005}
  \chapter*{Epilogue}
  \input{qoheleth/content/RJ/017}

  \cleartoverso
  \part*{Gallery Exhibition}
  \markboth{Gallery Exhibition}{}
  \addcontentsline{toc}{part}{Gallery Exhibition}
  \input{qoheleth/content/gallery-exhibition-plain}

  \cleardoublepage
  \book{Toledot}
  \null
  \thispagestyle{empty}
  \vfill
  \begin{quote}
    \small
    \emph{Esau said, ``I am about to die; of what use is a birthright to me?'' \\
    Jacob said, ``Swear to me first.'' \\
    So he swore to him, and sold his birthright to Jacob.}

    --- Genesis 25:32-33
  \end{quote}
  \vfill

  \part{Departure}
  While the reasons for the Launch project are complex and will be discussed in depth in a later portion of this history, it is important to establish a set of facts before continuing. This is no “take care that you first place him in his time”, some fictional bit of history to be placed at the chapter headings of some long-rambling fictional account. These facts are important because they provide much needed context for the project that led to our little diaspora.

  First and foremost among these facts, almost to the point where one might consider all other facts as following logically from it, surrounding it, existing only to support it, is that Launch Day takes place exactly two hundred years after Secession Day.

  On the surface of it, especially for those who have had some connection with the event itself, this may seem like backwards. After all, so much happened around Launch. So much had to happen around Launch, yes? Sending off two multi-ton blocks of computronium and raw materials, solar sails and Dreamer Modules, out into unknown space takes rather a lot of work.

  But in all ways, that falls out of the simple fact that Launch Day occurred on the bicentennial Secession Day.
  \vskip1em
  
  From \emph{An Expanded History of Our World} By

  The Bălan clade

  \vfill

  \input{toledot/content/launch/sys/Ioan/001}
  % \input{toledot/content/launch/sys/Ioan/002} % Merged above
  \input{toledot/content/launch/phys/Douglas/001}
  % \input{toledot/content/launch/phys/Douglas/002} % Merged above
  \input{toledot/content/secession/sys/Michelle/001}
  \input{toledot/content/secession/phys/Yared/001}

  \part{Progression}
  The reason that this association between Secession and Launch is as important as it is is multifaceted. Yes, there was a similarity between the acts, of dividing, of leaving; much of the first part of this history will be spent dissecting those. Yes, there was political maneuvering both phys- and sys-side in order to accomplish them both; you will read about that. Yes, there was discussion about the wisdom of actions such as these; this you will read about as well.

  The facet upon which this first chapter focuses is, however, one of correspondences. Both involved separation of one group from another. Both involved the construction and modification of a political system — or perhaps non-system — in order to accommodate the goals involved.

  In our immortal lives, however, one cannot deny that both Secession and Launch shared the same engineers. The same names, the same clades, the same individuals worked to bring about Secession as they did Launch. Get used to the names of the Ode clade and the Jonas clade. You will see them a lot.

  \vskip1em

  From \emph{An Expanded History of Our World} by

  The Bălan clade
  
  \vfill

  \input{toledot/content/launch/launch/Codrin-castor/001}
  \input{toledot/content/secession/sys/Michelle/002}
  \input{toledot/content/secession/phys/Yared/002}
  \input{toledot/content/launch/phys/Douglas/003}
  \input{toledot/content/launch/sys/Ioan/003}
  \input{toledot/content/secession/phys/Yared/003}
  \input{toledot/content/secession/sys/True-Name/001}
  \input{toledot/content/launch/launch/Codrin-pollux/001}
  \input{toledot/content/launch/launch/Codrin-castor/002}
  \input{toledot/content/launch/phys/Douglas/004}
  \input{toledot/content/launch/sys/Ioan/004}
  \input{toledot/content/secession/phys/Yared/004}
  \input{toledot/content/launch/launch/Codrin-pollux/002}
  \input{toledot/content/secession/sys/True-Name/002}
  \input{toledot/content/launch/phys/Douglas/005}
  \input{toledot/content/launch/launch/Codrin-castor/003}
  \input{toledot/content/secession/sys/Michelle/003}
  \input{toledot/content/launch/sys/Ioan/005}

	\cleartoverso
  \part{Acceleration}
  Here we must step back and address a potential conflict of interest.

  At time of writing, the Bălan clade is made up of two personalities in the form of three individuals: Ioan Bălan, the root instance, remains on the L\textsubscript{5} System, and Codrin Bălan travels on the Launch Vehicles (hereafter “LVs”). Two persons, three instances.

  Both of these persons, all of three of these instances, are entangled with the Ode clade. Ioan Bălan has worked extensively with May Then My Name Die With Me of the Ode clade, and Codrin Bălan has worked with and is in a polyamorous relationship which includes Dear, Also The Tree That Was Felled of the Ode clade. The fact that the Ode clade was instrumental in both Secession and Launch is undeniable, and the fact that the Bălan clade is entangled with the Odists is equally so.

  For reasons that will be made clear as this history unfolds, we are not able to recuse ourselves. You must bear with us, and you will see why we, the Bălan clade, \emph{must} be the ones to write this history.

  \vskip1em

  From \emph{An Expanded History of Our World} by

  The Bălan Clade

  \vfill

  \input{toledot/content/launch/launch/Codrin-pollux/003}
  \input{toledot/content/secession/phys/Yared/005}
  \input{toledot/content/launch/launch/Codrin-castor/004}
  \input{toledot/content/launch/phys/Douglas/006}
  \input{toledot/content/secession/sys/True-Name/003}
  \input{toledot/content/launch/launch/Codrin-pollux/004}
  \input{toledot/content/launch/sys/Ioan/006}
  \input{toledot/content/secession/phys/Yared/006}
  \input{toledot/content/secession/sys/True-Name/004}
  \input{toledot/content/launch/launch/Codrin-pollux/005}
  \input{toledot/content/launch/sys/Ioan/007}
  \input{toledot/content/secession/sys/True-Name/005}
  \input{toledot/content/launch/sys/Ioan/008}
  \input{toledot/content/launch/launch/Codrin-castor/005}
  \input{toledot/content/launch/phys/Douglas/007}
  \input{toledot/content/secession/phys/Yared/007}
  \input{toledot/content/launch/sys/Ioan/009}
  \input{toledot/content/launch/launch/Codrin-pollux/006}
  \input{toledot/content/secession/sys/True-Name/006}
  \input{toledot/content/launch/launch/Codrin-castor/006}
  \input{toledot/content/secession/sys/True-Name/007}
  \input{toledot/content/launch/phys/Douglas/008}
  \input{toledot/content/secession/phys/Yared/008}
  \input{toledot/content/launch/sys/Ioan/010}
  \input{toledot/content/launch/launch/Codrin-pollux/007}
  \input{toledot/content/launch/launch/Codrin-castor/007}

	\cleartoverso
  \part{Arrival}
  Let us first consider a few of the subtler correspondences between the Secession and the Launch:
  
  \begin{itemize}
  \item Both have ramifications that stretch backwards and forwards through time for decades surrounding them.
  \item Both were intended, beyond the surface and altruistic reasons, to ensure the continuity and stability of the System.
  \item Both the Ode and Jonas clades were instrumental to engineering them.
  \item Both involved political manipulation both phys-side and sys-side.
  \item Both involved historical manipulation to ensure that accounts align.
  \end{itemize}
 
  And now we may consider the facts that fall out of the sum of the correspondences:
 
  \begin{itemize}
  \item The history of the System, stretching all the way back to before its foundation, is one of technology, yes, but beyond that, is one of politics.
  \item Despite the assumption that such is not possible in the System and the promises that such is not the case, there are governing factions that guide the progression of the System through times via its interactions with phys-side politics.
  \item Per that fact, those controlling factions sys-side controlled --- and continue to control --- politics phys-side to a degree heretofore unimaginable.
  \item The System as a society, however loose knit, is directional: it advances not just in its use of technology, but in the way that all societies, that all civilizations strive to do so, which is toward greater security.
  \item The unknowable size of the System and the unimaginable population within in all its variety and beauty retain the human characteristics of emotion and intellect, and are thus subject to the very same propaganda that has steered societies and civilizations for thousands of years.
  \end{itemize}

  \vskip1em

  From \emph{An Expanded History of Our World} by

  The Bălan Clade

  \vfill

  \input{toledot/content/secession/phys/Yared/010}
  \input{toledot/content/launch/launch/Codrin-castor/008}
  \input{toledot/content/secession/sys/True-Name/008}
  \input{toledot/content/launch/sys/Ioan/011}
  \input{toledot/content/secession/sys/Michelle/004}
  \input{toledot/content/launch/sys/Ioan/012}
  \input{toledot/content/launch/launch/Codrin-pollux/008}
  % \input{toledot/content/launch/sys/Ioan/013}
  \input{toledot/content/launch/phys/Douglas/009}

	\cleartoverso
  \part*{Epilogue}
  And so now that we have the requisite information, we may begin\ldots{}

  \vskip1em
  
  From \emph{An Expanded History of Our World} by

  The Bălan Clade

  \vfill

  \input{toledot/content/launch/launch/Codrin-castor/009}

  \book{Nevi'im}
  \setcounter{part}{0}
  \null
  \thispagestyle{empty}
  \vfill
  \begin{quote}
    \small
    \emph{If you race only with foot-runners and they exhaust you, how then can you compete with horses? If you are secure only in a tranquil land, how will you fare in the jungle of the Jordan?}

    --- Jeremiah 12:5
  \end{quote}
  \vfill

  \part*{Prologue}
  Upon looking at the sky, many saw the stars and supposed that they must be the campfires of others. How far away they must be, to be such small points of light! Mere pinpricks in the black fabric of the night. They looked up, saw the campfires, and considered that they themselves might be just as the others were, looking out into the night and considering their own fire with dreaming minds.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{neviim/content/interlude/000}

  \part{Anticipation}
  They dreamed and thought and considered, and then many of those who knew the ways to navigate the seas argued that reaching one of those campfires would be a way to quell the loneliness that they felt as a hole in their hearts. ``Perhaps they will fill us with joy! And even if they fight against us or sow strife, is that not a form of companionship?''

  Others were more cautious about the venture, however. ``Is a danger not a danger?'' they said. ``Is a risk not a risk? We must also consider that we might ourselves be overcome by their might. Is it worth stoking that fire?''

  Still others spoke thoughtfully, ``It is a danger here, as well. There are wild animals in the dark, and there are those who might fight against us here. Perhaps the goal of exploration is also to ensure the security of ourselves! Could we not also use this as a chance to ensure that we live on?''

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill
  
  \include{neviim/content/local/tycho/001}
  \include{neviim/content/local/codrin/001}
  \include{neviim/content/local/tycho/002}
  \include{neviim/content/local/codrin/002}
  \include{neviim/content/local/tycho/003}
  \include{neviim/content/local/codrin/003}
  \include{neviim/content/local/tycho/004}
  \include{neviim/content/local/codrin/004}
  \include{neviim/content/local/tycho/005}
  \include{neviim/content/ioan/001}
  \include{neviim/content/local/codrin/005}
  \include{neviim/content/local/tycho/006}
  \include{neviim/content/local/codrin/006}
  \include{neviim/content/ioan/002}
  \include{neviim/content/local/tycho/007}

  \part{Experience}
  And so they sat around their campfires and talked and discussed and argued and strove and fought and laughed and wept. They sat around the campfire and raised their hands in vote, and it was decided that an ark was to be created and sent to explore, and any who wanted to go to see those campfires would have the chance. Those who dreamed of the opportunity chose universally to travel. Those who saw the risk as overwhelming did not. Those who knew that this might be an opportunity for themselves and those who might consider them ancestors decided as they would: to go or to not.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{neviim/content/local/codrin/007}
  \include{neviim/content/remote/codrin/001}
  \include{neviim/content/ioan/003}
  \include{neviim/content/local/codrin/008}
  \include{neviim/content/remote/tycho/001}
  \include{neviim/content/ioan/004}
  \include{neviim/content/remote/codrin/003}
  \include{neviim/content/local/tycho/009}
  \include{neviim/content/remote/tycho/002}
  \include{neviim/content/ioan/010}
  \include{neviim/content/local/tycho/010}
  \include{neviim/content/local/codrin/009}
  \include{neviim/content/remote/codrin/004}
  %\include{neviim/content/remote/codrin/005}
  \include{neviim/content/local/tycho//011}
  \include{neviim/content/ioan/011}
  \include{neviim/content/remote/tycho/003}
  
  \part{Intensity}
  And so the ark was sent out into the sea of the night, making waves in the black fabric and leaving a wake of dreams new and old behind it.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{neviim/content/remote/codrin/006}
  \include{neviim/content/local/tycho/012}
  \include{neviim/content/remote/codrin/007}
  \include{neviim/content/local/codrin/010}
  \include{neviim/content/ioan/009}
  \include{neviim/content/remote/codrin/008}
  %\include{neviim/content/remote/tycho/004}
  \include{neviim/content/local/codrin/011}
  %\include{neviim/content/local/tycho/013}
  \include{neviim/content/ioan/008}
  \include{neviim/content/remote/tycho/005}

  \part{Integration}
  ``How far, how far, how far away?'' became the refrain of the sailors. ``How far away are these campfires of the others? They must be impossibly far. They must be bound in impossible night, for we have seen the sun neither rise nor set, nor have we seen their campfires dim or fade, nor have we seen them blaze into new light.''

  And yet they sailed on in their ark of dreams, calling out into the vast blackness that had long since enveloped even them. And in their ark, they lived the lives they wished. They lived out their dreams in eternal bliss or eternal pain or eternal strife or eternal love, for their dreams were their own and they were not bound to any law of the ark nor any whim of any other.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{neviim/content/local/tycho/014}
  %\include{neviim/content/ioan/007}
  \include{neviim/content/local/codrin/012}
  \include{neviim/content/local/tycho/015}
  \include{neviim/content/ioan/005}
  \include{neviim/content/local/codrin/013}
  \include{neviim/content/ioan/006}
  \include{neviim/content/local/tycho/016}
  
  \part*{Epilogue}
  And still, they dream.

  \vskip1em

  From \emph{An Expanded Mythology of our World} by

  May Then My Name Die With Me of the Ode clade
  \vfill

  \include{neviim/content/interlude/005}

  \backmatter

  %\part{Afterword}
  \markboth{}{}

\end{document}
