\hypertarget{ioan-bux103lan-2346}{%
\chapter{Ioan Bălan — 2346}\label{ioan-bux103lan-2346}}

Ioan,

I must admit, I'm really not sure what to say about all of this. Thank you for waiting until you have a substantial amount to send to me, at least. Dear threw a little tantrum about about this ``We have received messages over the last few days'' bit, but I appreciate having an initial digest to work with so that I'm not left a fretting mess (as you say you were) by the simple news that, oh look, aliens! I threatened to bundle it up in blankets until it was immobile for a few hours, though, and it calmed down. I may do so anyway.

Four races! Five thousand years! One language! Have you learned any of that, yourself? How is May then My name taking it? You mention True Name, but have you heard from any other Odists? Any other friends? If the System is anything like Pollux, people are talking about little else.

The news broke over here much as it sounds as though it has done on the L5 System: with tightly controlled excitement.

There is no doubt that the powers that be continue their work across all three Systems, but it's always fascinating to see. The amount of bafflement was outweighed by the amount of excitement. The excitement also outweighed the amount of fear. Everyone's eager for every scrap of news that they can get.

How much of the delay in sending word to us was due to True Name and her friends? I imagine she had words about the first message, at least, but a whole week's worth of messages feels like a good deal.

No matter, though. We're all eagerly awaiting every little snippet that we can get from you. I know that you won't get this for another, what, seven days? Eight? And that seven or eight days from when you sent it! I know you won't get it for a few weeks, but please know that you're free to pass on information directly from here on out! We'll be learning plenty from the news we're allowed to see over here, anyway, so any juicy tidbits in addition to that will be greatly appreciated.

I am continually confronted with the ways in which we have diverged. May Then My Name and Dear\#Castor mentioned how upset they were by the idea of time manipulation, but my Dear\ldots well, it did not seem pleased with the idea, but its reaction was not nearly so visceral. It simply got a sour look on its face and said \emph{``I do not like the idea of a place where I cannot fork. Can you imagine a place so boring?''}

\textbf{BĂLAN CLADE-EYES-ONLY MATERIAL FOLLOWS}

The last few years have seen a drastic reduction in the amount of times that Dear has `overflowed'. I don't know if ey's been passing on every instance from Castor, or if you have been passing on every letter in turn, but it sounds like the same is true of Dear\#Castor as well, for which I'm thankful.

I'm sorry to hear about May Then My Name, though. Discussion of `cracks showing' always seems to crop up whenever one of our loved ones goes through a rough period such as this, and your news spurred a conversation between the three of us plus Serene, and despite the relative quiescence of Dear's symptoms, such as they are, we have noticed an uptick of oddities in Odists over here, as well. Not just Odists, of course, but a few of the older clades. Hell, a Jonas even went haywire a few weeks back.

Still, I'm happy to hear that everyone's tallies are lining up well: far fewer old clades over here are experiencing such symptoms than feared after the publication of \emph{Perils}, for which just about everyone is happy. No one wants to deal with an impending burden of insanity on one's two hundredth birthday, so to hear that it's only a fraction and that maybe there's something that can be done (or so we hear; has there been news of psychotherapy as a treatment over there? I've been hearing whispers) has kept the population at large from freaking out. I imagine you have it worse, though, given the relative skew towards dispersionistas on the LVs; I bet early taskers are freaking out.

Either way, Ioan, I am concerned for you and your partner. Our lives are informed by trauma, and the trauma that we hold in particular leads to a sort of conservatism that is particularly focused on our loved ones. I know that you want nothing more than to see May Then My Name continue to thrive, and I know that seeing her struggle is incredibly painful as it touches on the roots of those very same traumas. I know that the two of you will make it through alright, but, as this is in the clade-eyes-only section, do remember to keep yourself safe. You have Douglas. You have A Finger Pointing. You have Carolyn (who you'll have to tell me more about, sometime; she sounds fascinating). When you need, nudge May Then My Name to her support network and lean on yours when you need.

\textbf{IOAN BĂLAN INDIVIDUAL-EYES-ONLY MATERIAL}

The following is in strict confidence with you and you alone, Ioan.

I don't know how much of Codrin\#Castor and my messages between each other that you've read, or if that would even have helped, but watching the slow individuation of a loved one is an experience unique even from watching oneself individuate. The Dear I am in love with feels much like the Dear I fell in love with decades ago, and yet slowly the Dear on Castor begins to feel like a stranger to me.

Dear\#Castor sounds so much more conservative — in its approach to life, of course, rather than that of the division of the Odists — than what I've grown used to. The prairie remains the same. The house remains the same. Codrin\#Castor's struggles with agency and directedness in life feel as unfamiliar to me as you have mentioned. You have taken control of your life as I have taken control of my own, each in our own way. To put this on the Odists feels at once unfair, unfortunate, and totally accurate. May Then My Name has changed you in so many irreversible ways, just as Dear changed me so many years ago. Changed you, too, for when we merged and then diverged, you were no longer the same Ioan that remained behind. You were the type of Ioan who \emph{could} fall in love with May Then My Name in the first place.

So when Dear gave up the prairie and dragged Serene over to build out our little world into something grander, a place more well-rounded than just flat plains, we were both ready because, hey, this was Dear, right? So we built out our world. And then that spur-of-the-moment shift redirected our lives in unforeseen ways. With the acceptance of variety, Serene moved in to continue her work, and then her elliptical orbit passed through our lives for a while before she drifted away again.

I am not ashamed of having wound up, for that one short year, in a relationship with two members of the same clade. None of us are, not even Dear, it promises. It's not shame that keeps me from telling those on Castor about this. It is the completely alien nature that those who feel as though they ought to \emph{be} us interact with the world that leads to such. I do not feel as though I am able to tell Codrin\#Castor about what happened because to do so feels like explaining the alien to someone who really, truly, in all ways ought to know. Ey ought to be able to feel the same things that I feel, correct? Ey ought to also love Serene, oughtn't ey? Ey must, for ey is me, is ey not?

And yet ey is not. I cannot bring up our relationship with Serene because Codrin\#Castor — that is, specifically me\#Castor — does not have the same thoughts around intraclade romantic relationships that I do, and by virtue of the direction that the Odists steered us (or, as feels more accurate, crashed headlong and heedless) we are now completely different in that way.

The Dear that I live with has, in comparison to Dear\#Castor, relaxed and moved on to an approach to life that is far more laid back. As a result, we \emph{all} have, me included.

Also, as an internal postscript, I should note that we are all still deeply in love with Serene, and she with us, so please do not misconstrue the past tense above, but good Lord. Two foxes in the same house? Never again.

This is the end of the private content of the letter. Please redact this in its entirety should you pass my thoughts on to Castor.

\textbf{END IOAN BĂLAN INDIVIDUAL-EYES-ONLY MATERIAL}

\textbf{END BĂLAN CLADE-EYES-ONLY MATERIAL}

I am settling in quite well at the university and they are as excited as I am to receive the inevitable dump of information that comes from Artemis. It is a librarian's dream. I have seen quite the bump in my reputation, oddly enough, just by having my cocladist's name attached to the project over on Castor. No complaints, but honestly, what is a librarian to do with reputation?

Pass on our love to May Then My Name and tell her that we are all incredibly happy to hear that there is no more news of broken noses in this letter.

Codrin\#Castor, know that you've got us backing you as well. The world lies before you and is not nearly so black and white as it might seem. Search for those shades of gray that allow you to take a step forward.

It's been more than twenty years (or forty, if you count splitting from you, Ioan), and it still feels incredibly weird talking myself up, doesn't it? If nothing else, take it from yourself that it's possible.

Cheers,

Codrin\#Pollux

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Codrin,

Wonderful as always to hear from you. This will, of course, reach you long after the point where I could answer any pertinent questions about Artemis that I have not already done so by forwarding on what I've learned, myself. The amount of updates quickly got to the point where it didn't feel worth it to try and summarize them at all, so you're getting them all. Besides, you can summarize as well as I.

I'm curious about how things are working out over there with True Name and the leadership. We haven't heard anything yet from Castor about how she's doing over there, but it's always good to get a fuller picture of how things are going when they are, yet again, involved in something enormous.

Hell, on that note, how is the sentiment overall? There's been a lot of chatter, and, on the night of the announcement, we had to cancel a performance due to how excited everyone was. A Finger Pointing was quick to capitalize this, and went on a tear of digging up every single production that she could find about aliens to start scheduling. When she found a relative paucity of such, she started digging into sci-fi, including going all the way back to R.U.R. I have, of course, been contracted to write one for the occasion, and I've been doing so with what information that I can.

As to other Odists, we are in regular communication with A Finger Pointing and several from her stanza as a matter of course, and we've also been keeping up with End Waking, who I know you have not met, but who I promise is a delight to be around in his own coarse, woodsy way. I'll get Carolyn to send you a letter, too. I've certainly talked you up enough to her.

At time of writing, there is only a small amount of news. The talks will have started by now, but the last bit of clade news that we received from Castor was more about mechanics. They have decided to ensure that there is no radio communication between the DMZ and Artemis just for safety's sake, so all communication between those tagged \#Artemis and those tagged \#Emissary is done through an instance Codrin has tagged \#Assist. \#Assist will transit the border between LV and DMZ and exchange notes with \#Artemis then send them to Artemis itself via radio. It all sounds very convoluted, but I'm sure they have their good reasons for it.

I'll pass on the snippets of secondrace language that I've received so far. Codrin promises that the grammar and dictionary will be forthcoming, but says that True Name has suggested that any large messages from Artemis be sent after a thorough evaluation. I can't tell if that means an evaluation of their contents or an evaluation of the Artemisians' intent.

\textbf{BĂLAN CLADE-EYES-ONLY MATERIAL FOLLOWS}

\textbf{CODRIN BĂLAN\#POLLUX INDIVIDUAL-EYES-ONLY MATERIAL FOLLOWS}

This is in confidence.

It was interesting hearing the story of your triad (is it still a triad? I was unable to parse whether Serene is still part of your little polycule, though it does sound as though there is a healthier distance between you all now) in your words. Serene actually contacted us a few months back to pass on the story, herself, also in confidence. She made us promise to keep it to ourselves, even from you. I pinged her with the fact that your letter contained this information to make sure that I could confirm this with you, and she said yes.

I found the whole story as she told it to be terribly fascinating. There was a brief twinge of surprise at the idea of an intraclade relationship, but it was not the first that I've heard of since Launch. They're hardly common back here, but neither are they unheard of. Still, this is the closest that we've been to one. No friends, even, just right into our own clades.

It sparked a long, drawn out discussion between May, Douglas and I, actually. Less, I think, because there was any chance of that between the three of us than because Douglas is hungry for essentially every bit of information about the clade that he can get his hands on — though, May being May, she would leap at the chance to get closer to Douglas, but the most he seems comfortable with from anyone is friendship and physical affection (he will pet May for hours if she'll let him, and she always does).

On my end, I was mostly interested in May's thoughts on the matter as, except for a drunken (very drunken) night with A Finger Pointing, the two of us together have at most friendly relationships with any other Odist. We've not talked about that night with anyone else, either, and hardly even with each other. When I brought it up, both May and A Finger Pointing laughed at me and told me to ``get the fuck over it'' because apparently that's just how theatre nerds are.

However, when I asked May about it directly, she confided in me (and again, the anxious part of me compels me to note that I have permission to share this) that several decades back, she was nudged toward another Odist (one from the first stanza, though she did not specify which) by True Name, and a fork of her remained in a relationship with them for some time, and perhaps they are still together. May does not know. When pressed as to how this worked, she said that the instance who began that relationship was ``no longer me''. I did not ask further.

Either way, it's something of a relief to be able to talk about this openly (or, well ``openly'') with you. Keeping a secret about one's own cocladist from them is uncomfortable.

That digression aside, I take well your meaning about the divergence of Castor and Pollux. I see the divergence in you two, and while it has mostly just been an interesting fact to consider at times, occasionally it becomes very pertinent very quickly. I have often admired the ways in which you moved beyond the Bălans of old. It's nice to see proof that we can own our lives — which is not to say that I don't feel that about myself, but in contrast to \#Castor's current malaise, it comes in stark contrast.

I don't know how Dear would take a nudge from you, and it certainly isn't my place, but I do plan on helping Codrin over there however I can. I've been discussing this with May as well, and we are brainstorming suggestions for new paths for em. I don't think that ey could manage hopping right into life in academia as you have, both because of the differences in the university between the two LVs as well as the differences in your histories over the last few decades.

I also want to discuss this with May as well, though I will await your permission. I do not think that she is at as much risk of conservatism as it sounds like Dear\#Castor is, but there have been several conversation between us now regarding the directions that the clade that I'll speak to in normal clade-eyes-only.

Ah well, I'll keep you up to date either way.

\textbf{END CODRIN BĂLAN\#POLLUX INDIVIDUAL-EYES-ONLY MATERIAL}

While I'm sure that another Odist has already passed on this information, you should know that two Odists have quit recently, May One Day Death Itself Not Die and I Do Not Know, I Do Not Know, leaving behind no forks. The Ode is now ninety-seven.

May and Bathe In Dreams were there at the end, and this has led to an increased sense of urgency when it comes to the clade approaching their affliction. To that end, May and Bathe In Dreams are getting in touch with a psychologist recommended from folks on Castor (the Sarah Genet mentioned in the messages I've been forwarding) to discuss paths forward.

These events took place during May's aforementioned difficult spell, which led to it being prolonged to nearly a week. She has made it through, and my nose remains intact despite getting tackled, as usual. She has recovered well, but this, in combination with some of the news from Castor which you also will have received before this, has me more worried for her than usual. She may be a little terror, but she is my little terror.

Can you do me a favor when you get a chance, and let me know how True Name\#Pollux is doing in this respect in particular? Doesn't need to be anything too in-depth, but, well, she is a part of this as always, and clearly there is something going on with her here.

\textbf{END BĂLAN CLADE-EYES-ONLY MATERIAL}

Pass on my love. I miss you and yours.

Ioan Bălan
