Things were less hectic at my dad's, owing of course to the fact that no one had recently lost their job.  Christmas dinner proved to be more turkey, which was excellent as usual, as well as a few beers on everyone's part.  Thusly inebriated, my dad, Jenny, and I got into a discussion about relationships, particularly after I mentioned the strain I had felt between my mom and Jared.  Both of them offered their support, which I knew I wouldn't pass on in order to avoid any awkwardness.  Both also congratulated me on how well my relationship with Kris seemed to be going, and as my gift for Christmas, my dad gave me another three hundred dollars in order to help out both with the trip later during break as well as for during the semester.

Figuring I would stay down in Colorado Springs until the New Years party, I typed up a flyer on a whim --- ``New computer?  New troubles?  Call for help!'' was the gist of it --- and posted it on a few lightpoles around the town where I figured i might get a few hits.  As it turned out my services were indeed needed, and my current pricing undersold one or two other businesses that were trying to do the same thing, so I wound up making another hundred and eighty dollars, though none of the appointments lasted longer than an hour.  I spent a bit of time stringing cable and setting up new wireless routers, but most of my time by far was spent introducing people to their new computers.  I gained a new respect for the technophobes: I knew of no other class of people that was so obstinate against learning something new.  I was continually confronted with furrowed brows and hesitant answers as I tried to explain the vagueries of email.  This served to reaffirm my choice of study in college.  If I had gotten stuck doing this for the rest of my life, I would've lost faith in humanity.

Money was money, though, and gas prices were on the climb, so those extra six hours of my time I was sure would prove to be quite useful in getting me around the state for fun and profit.  Nearly a thousand dollars in my bank account was sure to help out during school, because I surely didn't plan on spending all of that during break.  Money in the bank certainly felt nice, though so I figured I would go ahead and follow advice and get a job during next semester if I was able, in order to start earning enough in order to support myself should funding get cut off or cut back sometime in the future.

Come New Years, though, I drove around and took down all of the signs.  Not even twenty bucks an hour would keep me from the possibility of going to see Kris.  I was starting to miss her dearly by this point, and the concept of the drive to Boulder in the snow was not going to stop me from making my way up there.  I left the house by noon, figuring that would get me up north before the party started, just in case Kris and I wanted to do something before hand.  If not, I could always putter around the town and check it out until the time when I could go and see her.

Leaving early turned out to be a good idea.  I had apparently forgot that I wouldn't be the only one driving to a New Years party on new years, because it seemed as though everyone who had a car was on the road and trying to go from one town to the next.  I got stuck in traffic in Denver for a little while before I could make my way onto the turnpike between Denver and Boulder.  More traffic just outside Boulder, of course.  By the time I got to the city, I figured I'd only be ten minutes early, though, so I gave Kris a call to let her know that I would be there on time.  She sounded breathless and excited.

By the time I parked, nearly half a block away from their house, it was dark and the party was apparently just about to start.  I walked quickly up to the house and, before I even made it onto the lawn, the door opened and Kris, decked out in a button up black shirt and that same dress I had seen her in the first time I met her, bounded out to greet me with a hug.

``Oof, hey!''  I laughed, ``Hope I'm not under-dressed''  I had neglected to ask, and aimed for somewhere between casual and formal with khaki slacks slacks (Wal-Mart) and a blue-jean colored button up shirt (Kohl's)

``Nah, you look fine.  Like a dork, but fine.''  She grinned and tugged at my fake-denim shirt.

``Gee, thanks a lot, dear,'' I rolled my eyes.

``Whatever, Cor,'' she said, leaning to kiss me on the cheek.  ``Come on, it's friggin' cold out here.''

We piled into the warm, yellow light of the living room and shut the door behind us.  I was greeted with a hug and a handshake, respectively, by Kris' mother and father, who introduced me to the other couple that had gotten there a little earlier.

``There's snacks and small food in the kitchen,'' Kris' mother was saying.  ``We invited quite a bit of people, so if you guys need to duck downstairs, feel free.  We figured there'd be a few bored kids about, so we set the basement up as a retreat from boring adulthood.''

I smiled and nodded, ``Thank you, Mrs. Careen.''

She smiled back, ``I'd tell you to call me Kathy, dear, but I know you probably won't.''

Her husband laughed and whacked me on the shoulder, ``Well, Kristal did say that he was polite and chivalrous, didn't she?''

I felt my ears redden then arched to the side when Kris pinched at me.  ``Cory's nice, don't you two go about trying to ruin him,'' she said, standing with arms akimbo.  ``Better polite than Dante, right?''

Kathy rolled her eyes and walked back into the kitchen, shaking her head.  ``Ain't that the truth, kiddo,'' James said.

``Dante?''  I had a guess, but I still felt decidedly out of the loop.

``Ex,'' Kris said, shaking her head before I could ask any further.  ``Come on,'' she instructed.  ``Lets go pick up some food.  Mom's a good cook, and their friends all brought a bunch of food.''

Indeed, Kris' mom was a very good cook.  There was daal, an Indian lentil stew; spanikopetes, Greek spinach and cheese pastries; rolls; cookies with what looked to be jam spread in a pattern on top of them; and several different loaves of bread that all looked to be different flavors.  I piled some of everything on my paper plate along with a styrofoam cup of the daal.  The other couple had brought baked beans speckled with chunks of hotdogs, which I stayed away from at all costs.

Since everyone seemed to be gathering in the livingroom, Kris and I made our way back out there together and found ourselves a spot on the love seat, spending our time eating while the `adults' made small talk and laughed at lame jokes about work and politics.

Finally, Kris turned more towards me and started up our own conversation.  ``So how was the last week?  Only got to talk to you once.''

``Yeah, sorry 'bout that,'' I said, washing down a bite of spanikopeta with a spoonful of lentils.  ``Family stuff and all.  It was good.  Made a bit more money, so I'm set for the rest of break and into the semester,'' I said carefully, unsure of weather I should bring up the trip bluntly.

Kris nodded, but her mom surprised us by asking, ``What do you do for work over break?''

``Oh,'' I shrugged.  ``Fixing computers for people.  I made almost two hundred in the days after Christmas just helping people set up their new computers.''

``Are you studying computer science in school?'' asked the husband of the couple whose names I couldn't remember.

I shook my head, ``Music education.  I decided I didn't like computers enough to make it my job.''

A Significant Look passed between the couple, and the wife said, ``The market for computers has stopped booming anyway, I think.''

``Well, I don't know,'' began her husband.  ``Quantum's doing fine, seems like.''

As the discussion continued between the couple, soon enveloping Kris parents, continued, it became clear that my becoming involved in the discussion was an anomoly best forgotten.  I shrugged and smiled at Kris, who grinned and patted my knee.  I'd never understand group dynamics, I thought.

``How 'bout your break?'' I asked, reaching back to the original topic.

``Oh, it was fine.''  Kris sipped at a glass of water, food resting in her lap.  ``Was good to see the family again, I suppose.  Kinda good to be back home, you know?''

I laughed and nodded, ``Yeah, felt good to be back up in the mountains.  They make the world seem a lot smaller, unlike the plains.''

``Yeah.  When I got back home, it almost felt like the Flatirons were going to tip over and crush me.  Had a semester out with no real hills to speak of.''

And so it continued.  I told Kris about the troubles going on at my mom's while Kris related stories about her grand parents' visit as couples arrived, one or two with teens sulking behind them that brightened up as soon as they saw Kris.  I was introduced to everyone in turn, and remembered no one's name.  I was a little too focused on the pleasure of being introduced as Kris' boyfriend.  Every time, it gave me a small twinge of pride.

Things finally started to pick up at around eight or nine that evening.  There were, by my count, twenty three people at the party now, plus myself.  Kitchen table had filled up with food and I did my duty of keeping it out of the mouths of starving children in Africa.  Even one semester in college had taught me to never pass up free food.

The crowd had fractured into several small conversational groups.  It seemed as though five or six people would gravitate towards one or two people that would spend the most time talking just so that they could nod their heads and smile at strategic moments.  Unable to fathom the group dynamics involved, I turned into one of those head-nodders and just followed Kris around, getting into one or two small polite conversations about school or my relationship with Kris, but spending most of the time just hanging by her side, glass of juice in hand (while Kris had mentioned that we would get a glass of champagne at midnight, her parents were decidedly against underage drinking; I was starting to feel bad about drinking as much as I did at such an early age, anyway).

When the group seemed to reach the maximum amount of fracturing it could withstand, there was something of a unanimous, tacet decision amongst the younger demographic to migrate downstairs to the promised den.

A second round of introductions went around, now that we were a little more used to seeing each other around the house, and those in highschool still were not under the careful eye of their parents.  There was more laughing, too, as we sat around, some on a futon couch and some on the floor, the TV on to some random movie more for the ambiance of a television than for us to watch.

``So, Dante?'' I asked Kris when the younger group had started to fracture much as the older crowd had.

Kris shook her head and looked down at her drink, ``It's a long story.''

I checked my phone and shrugged, ``Well, we have three hours until midnight, so time's not an issue.''  I hastened to add, ``Of course, if you don't want to talk about it, that's okay.  I was just curious.''

``No,'' she wavered, then seemed to make up her mind.  ``Nah, now's as good a time as any.  We leaned back against the wall next to a book case where we sat on the floor, each with our legs stretched out in front of us and crossed at the ankles.

``This isn't too public or anything, is it?''  Everyone else seemed to be clustered in little groups of two and three near the TV, but I figured I'd ask for sanity's sake.

Kris gave half a smile and shrugged, ``Wouldn't have started if it was.  Anyway, yeah, Dante.  I went out with him for a few years during high school.  He was my first boyfriend.  You're my second, by the way.  We hit it off pretty well when we met.  He was sarcastic and funny, I was weird and funny.  Neither of us were really all that popular.  We hung out a lot in the halls in high school and people watched, even when we were supposed to be in class.  Open campus and all that.  And you should've seen our highschool.  Not a right angle in sight, all these acute and obtuse things that were supposed to, like, break us out of the mold of thinking in the box or something.  Of course, the walls were all bare concrete that had vertical stripes gouged in them.  It made the place look like a prison.  There were even rumors that the place was designed by a guy that designed nothing but prisons.

``Anyway, so yeah.  We wound up hanging out more and more and then just sort started going out.  It was kinda funny.  We never talked about it or anything.  We just sorta started going out without talking about it.  My parents were okay with it, though I got the feeling they didn't really like him.  You saw the way my mom reacted earlier.  They later told me they thought he was something of a deadbeat who didn't seem to be going anywhere in life.  I agree now.  He works at some sandwich shop near the school.  Never graduated.  Got his GED a semester before he would've.

``I liked him, though, and he liked me.  He was fun to talk to and make fun of all the stupid kids with.  He let me try pot for the first time, and I had my first real drink with him, and tried cigarettes too, though I didn't like either of those then.  Still don't like tobacco.''  She cleared her throat and took a small swallow of her juice, ``Anyway.  Things were fun and all that, and we would lay around outside or inside and just sort of talk.  We talked a lot.  Lot more than us, by the way.  Trying to get you to talk more.''

I laughed and slipped my arm around her shoulders for a brief hug.

``We never had sex, though.  We would talk about it and sometimes, I would feel him, you know... reacting to it when we would lay together, but I would chicken out every time.  He would start touching me or something.  My breasts or whatever, sometimes would try to put his hand down my pants, but I would always start feeling really dirty and stop him.  He was always pretty cool with that, though.

``Then, one day we ditched out of school early and went over to his place and got stoned.  I mean, like, totally fucked up, completely wasted on his crazy strong weed he had.  It knocked me down pretty bad.  I could only lay on his bed and pet his cat while I stared at the ceiling, watching it sort of breathe at me.  I felt like I couldn't move.  Dante lay with me and just kept kind of talking.  I don't remember what he said actually meaning anything, just sort of mumbling words.  I remember it turned into kind of a drone and I felt like it was sort of lulling me somewhat.''

Her face turned red and her voice got quieter.  ``Then he just kinda... undressed me.  I was wearing a skirt like this and a guy's button up shirt.  He just kinda sat up and took them off.''  Her face went still and stony, reminding me of my talk with Jamen weeks ago.  ``I couldn't do anything.  I couldn't stop him.  I couldn't really think of anything to say, and it just kind of felt like I was sitting on the edge of the bed, watching.  He just put a condom on and went at it, you know?  I just felt like I was sitting there, watching him screw me, and I wasn't moving at all.  Just staring at the ceiling, you know?''

I held one of her hands in my own and she gave it a little squeeze in return.  Her story had a rehearsed quality to it despite all the repitition, and I felt as though she had practiced itin order to tell it with the minimum of emotion required.  All I could do was stare and wonder at the stillness of her voice.  I would've been sobbing.

``So yeah.  He finished and just went back to smoking.  I slowly came down from being as high as I was.  I just got dressed again and left.  He was sitting on his computer and didn't even really look up at me and I didn't look at him.  Just put myself back together and walked home.

``Our relationship ended there.  We just kind of stopped talking to each other from that point on.  I didn't tell anyone what had happened, and I assumed he didn't either.  I still wonder about that.  I kind of get the feeling he was just as embarassed about the whole thing as I was.  I don't think he was acting as himself.  And before you say anything, I'm not making any excuses.  I've watched the same thing happen twice before to my friends, and each time, they kept it all quiet like I did, but I could tell from the start that the boys had planned the whole thing out like that.  They'd go and gloat about it to their friends and it'd turn into a big deal and the girl would be crying in the bathroom all the time.''

Kris faltered and shrugged, breaking her still mask and giving me another half smile, ``That's about it, I guess.  Didn't trust myself to have another boyfriend until I knew I was ready.  And our first time... well, I was kinda drunk, you know.  It showed me that it could be nice, you know?''

All I could do was nod.  My little spat with Chris seemed like so little now, after hearing that.  I squeezed her hand in mine again and leaned over to kiss at her temple.  I kept my face near hers and murmurred to her the only thing I could think of saying, ``Wow... thanks for trusting me enough to share...''

She laughed a little and tilted her head away from me as if I was tickling her ear with my breath.  ``I thought I might just make something up, but I figure if I can't trust you, I can't trust anyone.''  She finished her drink and set the cup aside so that she could lean in against me.

``You two are pretty cute together.''

I blinked and looked up to see one of the other kids --- Alan, I think his name was --- grinning down at us from where he had just come down the stairs, lugging a plate of snacks.  Kris smiled up at him bashfully and I couldn't think to do anything but copy her.

He laughed and shook his head sitting down on the office chair nearby, ``Didn't know you had a boyfriend, Kris.  Meet him at school?''  He added quickly, ``Sorry if I'm interrupting something, just let me know...''

Kris shook her head and sat up straight again, the both of us just sitting at the base of the wall like we had been.  ``You're fine.  Yeah, met Cory in one of my classes.''

Alan smiled and nodded, ``You're up at CSU, right?  How is it way up there?''

I shrugged, ``It's alright.  Flat.''

He laughed.  ``How is it people wise?  Pretty conservative?''

``Yeah,''  Kris said.

``Not as bad as Colorado Springs,'' I added.  ``Not by a long shot.''

He nodded and took a drink, though the gesture looked staged, what with the cup in his left hand.  I saw why pretty quickly.  Showing the little rainbow chain-link bracelet around his wrist.  Smooth, I though.  

I nodded towards his wrist, ``Definitely more friendly than the Springs.''

Alan blushed despite his little act, or perhaps as part of it.  ``Oh... yeah, I would hope so.''  He leaned in a little closer and lowerd his voice somewhat, ``You bi?''

I blinked.  Gay-dar?  I always thought it was a bit of a hoax, but every now and then someone would guess about me and I would question it.  With both of them looking at me I shrugged, ``I... well, I guess so.''

``Kinda struck me as a gay guy,'' Alan said quietly.

``Thought I was until I met Kris...'' I smiled slightly.

He nodded and sat back in his chair, picking at his food.  He seemed to have regretted bringing the whole thing up, now for some reason.  We sat in silence for a bit, while I thought about what I had done to give my sexuality away.  I was hardly effeminate, and I hadn't done anything to give it away.  Hell, the last guy I had looked at in any sort of attractive way was, I was ashamed to admit, Jamen.

``Funny how things work,'' Kris said after a bit.  She looked thoughtful in a decidedly cold sort of way.

``Oh?'' Alan looked taken aback.

``Just gender and all.  Seems to mean an awful lot to people,'' she said quietly.

``I didn't mean...'' he began.  ``No, I mean you guys really are cute together, didn't mean to insult...''

I smiled in what I hoped was a disarming manner, ``Well, I guess it does mean a lot to some people, but it's not always the deciding factor.  I'm happy with Kris, even though it was a big change.''

Both smiled at me and nodded.  I relaxed a little, not realizing that I had been so tense to begin with.  Man, I thought, even with people who didn't know me, it was like coming out all over again.

``Gender means rather a lot to me,'' Alan shrugged, blushing.  ``Don't think I could go out with a girl... no offense or anything.''

Kris laughed, ``None taken.  I don't think I could go out with a girl, either.''

``Don't have to worry about losing you to your roommate, then,'' I joked.

``God, no.''  She laughed, ``Erin's got her boy, remember?  Don't think you have to worry about either of us.''

Alan grinned at the two of us.  ``So it's pretty friendly up there and all?'' he asked, trying to get back onto the topic he had started.

``Yeah, it's fine.  It's more conservative, but it's hard not be liberal on a college campus, know what I mean?  There's a pretty big community on campus there.  They've got a student services office and everything.''

``Ah, alright,'' he nodded.  ``I was thinking about going there for vet medicine, but was kinda worried.''

I shrugged, ``Don't think you need to be.  It's a good school and a cool place.  Not that bad.''

The conversation wandered on from there, the three of us discussing the relative merits of mountains and plains, and how that changed things such as what type of bike you wanted to buy.  It took me several minutes to realize that we were our own little group fractured away from the whole, that Kris and I had been for quite a while now.

I was just in the process of digging in my pocket for my phone when Kris' dad called down the stairs, ``Hey!  Guys!  Come on up!  Ten minutes to go!''

Upstairs, they had a TV on a wheeled cart and had moved it to the little dining room nook.  Almost all of the adults were gathered in the dining area, kitchen, and back end of the living room.  It was hot and muggy up stairs from so many bodies and so much food heating the room up.  The French doors had been opened and one or two adventurous people were even standing outside, cooling themselves off by standing in the three feet of cement free of snow left by the overhang of the roof.  The cool air did feel pretty good, and I gravitated toward the open door with Kris in tow.

The TV was tuned to one of the local news stations so that we could watch the ball drop as, Kris' mom explained to me after finding us, was a tradition in the family and had led to parties like this.  I had never really paid attention to such things, so I stayed inside the house to watch.  I was tall enough to see over most of the people milling in the dining room, and the TV was set back a little ways.  Kris wandered over and leaned back against my front, so I hugged my arms around her middle as he watched the show and listened to the adults chatter.  I caught her parents smiling at us from across the room out of the corner of my eye.  I smiled back sheepishly and they looked away, back at the TV.  Kathy leaning over to whisper something in her husband's ear.  A quick glance showed that they were holding hands.

Finally, with a minute left, Kris' father reached into the fridge and got out several bottles of champagne, and looking behind him, I saw a couple of rows of plastic champagne flutes lined up on the counter.  The bottles where handed to what I assumed were a few trusted accomplices who all made their way outside.

``Ten!  Nine!  Eight!'' we counted along with the TV.  Those outside tore the foil off their individual bottles.

``Seven!  Six!  Five!'' the wire cork baskets were untwisted with thumbs held over the corks.  I held Kris a little tighter against my front.

``Four!  Three!  Two!  One!''  And finally, drowning out the sound of the corks popping, ``Happy New Year!''

A cheer went up around the room and Kris twisted about in my arms and leaned up to give me a kiss.  I returned it, keeping it chaste, conscious always of being surrounded by a good number of other people.  Finally, she settled back onto her heels and draped her arms around my neck, ``Here's to doing this again next year.''

I smiled wide enough that I was sure she would call me a dork as always, but she just leaned in closer to rest her head on my shoulder while those in the room half sang, half mumbled Auld Lang Syne along with the music from the TV.  We stayed like that for several minutes until Kris' mom tapped her on the shoulder to separate us while her father pressed a plastic glass of champagne into my left hand, shaking my right firmly.

He leaned in close to say quietly near my ear, ``Thank you for making my daughter so happy.''

I bowed my head in response and tried to hide behind my sparkling wine as I took a sip.  He whacked me lightly on the shoulder and moved away through the crowd, his wife in tow.

We spent another hour or so upstairs, picking at the now cold food and talking with a few of the other guests.  People seemed to be leaving in a steady stream, and by one o'clock, there were only three other guests left: a couple and their son, Alan.  Kris' mother seemed to be anxious to see them off and hinted at such by starting to clean up around the house, but the father was in a discussion with James and didn't look to be wrapping it up.  Kris, Alan, and I followed Kathy around, helping to clean up while Alan's mother stood next to her husband and occasionally shot us an apologetic look.

Finally, Alan's father seemed to get the hint, and within five minutes, gathered up his son and wife and found his way back to the car.  The four of us remained alone in the living room, just standing and trying to digest the silence and emptiness of the house.

``Alright, guys,'' Kathy smiled to us after a bit.  ``Thank you for your help.  I'm done in, though, we'll get the rest in the morning.''

I nodded and suddenly felt awkward standing there with Kris and her parents, knowing that I was then supposed to sleep over but not knowing the protocol.  Was I supposed to follow Kris downstairs?  If so, was that futon meant for me while Kris slept in her own bedroom?  If I was to share a bed with her, was it meant to be chaste?  Sleeping with our clothes on?

Everyone else seemed to pick up on the awkwardness as well, and Kris finally let out a nervous laugh, which we all followed along with.  

``Well, sorry about that,'' Kris' mom said.  ``Cory, I can't ask you to sleep on the couch with anything, but, uh... there's an extra set of blankets and pillows in the linen closet in the downstairs bathroom...''

``Mom!''  Kris was bright red and looked horrified.

``Yeesh, relax, Kristal,'' James laughed.  ``Someone had to broach it.  Just don't stay up too late, alright?  Keep it quiet down there.''

``Dad!''

I had to remind myself to close my mouth.  Everyone was flushed bright red and stood around for another moment before Kristal's parents left for their own bedroom, laughing and shaking their heads, talking amongst each other, something about growing up quickly.

``Jesus, parents,'' Kris said, sounding exasperated.

I could only nod in response.

``Well, whatever.  They're weird.  C'mon, Cor.''

We made our way back downstairs and instead of turning toward the den kept going straight to a door that had been shut for most of the evening.  Kris apologized preemptively for the mess and let me follow her in.  The room was cozy and she still had a bunch packed away in boxes, but her bed was set up nicely with a green comforter and blue pillow cases.  She sat on the edge and I stood leaning against the door jam, looking over the room.

Kris finally laughed and leaned forward to grab at my hand and pull me over to her.  I stumbled and grinned down to her as she sat on the bed, towering over her.  She hugged her arms around the backs of my thighs and rested her head against my belly.  I brushed my fingers through her hair once or twice before leaning away from her, embarassed at the beginnings of an erection.

I sat next to her on the bed and tugged my shoes off and set them next to the dresser before leaning in to kiss at her cheek.  I smiled, ``Awkward.''

She laughed and wove her fingers with mine.  ``Yeah, I know.  I keep feeling like they're going to like, barge in or that they've got a stethoscope on the floor above us.  Oh well.''

I nodded and sat still for a little, finally relaxing from the evening.  ``I'm friggin' beat from this evening.  You cool with bed?''

Kris nodded and stood up to kick her own shoes off next to mine and to turn off the light.  Left in the dark, the only light being the clock and a vague yellow glow coming from the window well of her one window, I lay back on her bed.  My girlfriend's bed, I though, amazed that this still was so surprising to me.  I heard Kris shuffling about in the dark, apparently as blinded as I was.  I felt her fingertips brush against my knee and giggled.  The fingertips traveled quickly up my thight and passed hesitantly over the crotch of my slacks before finding my stomach, then sliding off to the bed beside me.  I felt that hand push down into the mattress as she put her weight into it.  I let out a quiet grunt as she lifted herself up onto the bed, swung one leg over mine, and straddled my hips.

I set my hands on her sides and felt her lean over until her nose bumped into my cheek.  We shared another kiss before she pulled back.  ``Thank you for coming, Cor.  And for listening.  Earlier, I mean.''

I nodded, nose brushing against her own.  ``Of course.  Thanks for having me over.''

She kissed me again and I rubbed my hands against her hips, not even trying to hide my body's reaction to hers.  She shifted her weight all to one hand and slipped the other between us to fumble with my belt, getting it unbuckled and tugging it from around my waist.

Our paranoia about her parents lead to our moving slowly and quietly, which changed everything about the experience, made it all the more special.  It was nearly three by the time we fell asleep, both still wearing our shirts in case one of her parents were to check in on us.  More than the quiet sex or the fear of being caught, however, I remembered our last exchange before sleep.

``Cor, you know I really like you,'' she had murmurred.

I nodded, ``You know I like you too.''

She chuckled quietly and was silent for a bit.  Then, ``Just wanted to say that.''

``Mm.''

``Not going to say `I love you' until I know I mean it for real.''

I had been on the verge of dozing off, but that woke me up.  I nodded and hugged her a little tighter, her back against my front.

``I hope you understand.''

``I do.''  I swallowed, thinking of how quickly I told Chris that I loved him.  ``I'll do the same.''

She nodded, and we lay together.  Finally, and I can't be sure she really said this because I was nearly asleep by that point, she whispered, ``But the more I think about it, the better it gets.''
