\hypertarget{a-theory-of-attachment}{%
\chapter{A Theory of Attachment}\label{a-theory-of-attachment}}

A cool, pale blue lightness sitting just behind her sternum, Sélène made what she promised herself would be a quick pass through the kitchen

She brushed her fingers along the edges of cabinet doors. Each one was opened and inspected, leaving her standing on tiptoes to peer in those above the counters. Nothing but cups and glasses, plates and bowls, cutting boards and pots and pans and trays and dishes. All clean and neatly stacked.

Each cabinet was carefully left ajar. The vixen had perfected the art of finding the balance point that would leave them open before the weight of the door on the hinge would close them, without simply leaving them all the way open. The barest crack.

The fridge bore her inspection patiently, door held open as she inspected along each of the shelves, gently moving well organized bottles to check between each of them. The freezer was equally patient as the vixen lifted containers of leftovers and trays of uncooked meats. Doing her best to avoid glancing at the back walls of either, she pressed the doors shut to keep the fridge from endlessly breathing cold out into the kitchen. Just to be sure, she opened them again, savoring that clean snap of the magnetic seal pulling away from the body of the fridge, then gritting her teeth in frustration as closing the door offered no such tangible reward.

The oven yawned out to her, empty. The oven was easy, because it had a light that turned on while open, and off when closed. The fridge did, too, but the oven had its pristine glass door through which she could observe the light cycling. The stove had similar lights which, the associate at the hardware store assured here, were connected directly to the burners. Even so, she touched each cook-top surface gingerly to test for warmth, turned all the burners on, then off again.

On a whim, the drawers were next. Thankfully, most of those were empty, and the rest mostly so. The underside of the silverware tray was inspected with care.

That coolness in her chest ticked up in intensity, a little pang, as she held the drawer partly open. Anxiety into fear. A cool, blue, perfectly smooth and perfectly round fear just behind her breastbone, snaking tendrils out along her limbs.

Down on her knees with tail bristled out, Sélène eased open the cabinet door and peered up toward the underside of the drawer, ensuring that there was nothing between the drawer's underside and the cabinet, and that the drawer sides didn't reach the underside of the counter, that there was a gap.

The pang continued to grow with an implacable intensity, arteries as avenues to carry it throughout her body. Pressing visions of cramped quarters and unassailable darkness, of not enough space and not enough air, of the sheer uncaring of one's surroundings.

So she checked the rest of the drawers.

Finally, swallowing as best she could, Sélène stood in the center of the kitchen. She fished her phone out of her pocket, and thumbed the screen on. Turning a slow circle, she took a panorama of the kitchen.

She waited for the panorama to stitch itself together, then pulled it up and inspected it carefully, scrolling along its length.

Cabinet. Cabinet. Fridge. Cabinet. Doorway. The barest hint of a figure.

Her head jerked up and she let out a shriek at the sight of her husband standing at the entrance to the kitchen, tired smile on his muzzle. Her phone dropped from her paws and she clutched at her chest, that cool ache replaced with hot embarrassment.

Aiden stepped forward quickly and lifted up her phone careful to touch only the edges, and deposit it back into her paw. ``Sorry, Sélène, I should've stepped in more. May I hug?''

Sélène laughed breathlessly, inspecting her phone and tucking it back into her pocket. ``Yes, sorry! Of course!'' She leaned into her husband's open arms, breathing that familiar scent. ``Are you okay?''

The taller fox --- much taller, which Sélène quite enjoyed --- tucked his muzzle over her head and nodded against her. ``I'm fine, it's alright,'' he murmured. ``You going to head into work today, sweetheart? You only have one from-home day left this week.''

``I think so, yeah. Feeling pretty good today, actually.'' That cool ache sat in her chest, where it didn't grow any, yet somehow made it's presence all the more known. The cold of anxiety tickled along her ribs, threatening to make a liar of her.

She had to ask. She had to. Just ask. She just had to ask. ``You sure you're alright?''

The pang subsided.

Aiden leaned back and nodded where she could see him, then leaned in again to touch his cheek to hers --- the closest she could stand to affection around her face. ``Fine, love. I'm doing okay.''

Sélène returned the touch and nodded, silently promising that thin pang of fear that Aiden meant to say ``I'm fine'', rather than a grouchy ``\emph{fine}'', that her husband was just tired, not tired of her.

``I'd like to head out soon, is that alright?''

``Mmhm, I just need to grab my bag. Need to pack.''

Aiden nodded. ``It's by the door. Check your phone, it's already packed.''

Her ears twitched to attention, smile brightening. Sure enough, just before the pano of the kitchen was a photo of the inside of her shoulder bag. Laptop, all her pens, an empty book of blank paper she never could bring herself to write in, and an umbrella.

``Alright, just a quick look. Let's head out before I get lost again,'' she waved vaguely at the cabinets, ignoring the cool blue sensation of doubt traveling down her arms, little flares arcing out from the anxiety in her chest. She could \emph{see} the cabinets were open. She didn't need to check. She didn't need to check. She could see. She didn't need to--

Aiden seemed to pick up on her hesitancy and set his paws on her shoulders, ``Come on, bag's all packed, love.''

Sure enough, it was packed.

\secdiv{}

The ride to work was about a four, she decided. She'd had better days, but this was far from her worst, even though her morning had been a seven, approaching an eight out of ten on her arbitrary scale of badness. Most of the time, she was able to look out the window at the passing traffic, and the rest of the time, she was able to distract herself with her phone. The app she used for her federated feeds gave a satisfying click every time she pulled down from the top to refresh it.

Aiden talked to her about his upcoming day throughout the drive in his calm, soothing voice. That was the second best thing she loved about him: his words seemed to instill a sense of the proper temperature. Not the cool-to-cold obsession, nor the heat of frustration or embarrassment.

He put up with her, too; that was the best thing about him.

That was one thing that always calmed her. All of the things that made her life difficult, all those obsessions and rituals, they all didn't feel like so much work when she thought about Aiden and the way he cared about her. She could ask him if he was alright a million times, and he would always say yes. If he was upset about work or money, he would say that he was okay, and then explain his frustrations.

Everyone else moved so much faster than he did, so haphazardly. There was so much noise and so much movement. So many ways for things to go wrong, so many missed opportunities to make sure someone else was okay.

She'd gotten her job to let her work from home three days a week just to make sure she could get enough of a break to be productive. It had taken a doctor's note, but it had worked, and she'd kept her job.

That note was humiliating.

The medical industry solemnly swore that Sélène Kelly was off her rocker, utterly crazy, completely bonkers, that madness rode her like so many ticks. All so she could get three days at home to stay productive.

The diagnosis had been fine. Her family dealt with her getting steadily worse over the years, and when they finally got her in, hearing ``obsessive-compulsive disorder'' confirmed that \emph{they} were not crazy, she was. She'd resented them right up until her first dose of the emergency sublingual anxiolytic. It had made her sleepy, but it had made her mind quiet. It had quelled so many of those cold pangs of anxiety.

She remembered thinking before nodding off that night, ``Fine, okay, it \emph{is} just me.'' It had been depressing, but it knocked her resentment of her family down a few notches.

Aiden one-upped all of her family's care: he'd fallen in love with her, he said, whether or not she checked all the cabinets to ensure that no one was stuck, slowly starving to death. He'd gotten her more than just meds, he'd gotten her therapy. A doctor who was working with her on a steady program of exposure: \emph{``Next time you're in the kitchen, walk in, take a glass from the cabinet, pour yourself a glass of water, and walk out. Think about how that feels.''} Little steps, over and over. Her family tried to hide her, Aiden tried to help her.

And he'd gotten her more than just meds and therapy, he'd gotten her him.

By the time they'd stopped at her office, just outside the front door, the day had been knocked down from a seven, to a four, to more like a two. A brush of cheeks, two I-love-yous, and one are-you-alright, and she was off to work.

\secdiv{}

``You're picking, love.''

Sélène jolted to awareness, realizing just how much she had zoned out. She pinned her ears back, massaging the fur on her wrist in an attempt to cover the frayed patch where she'd been digging with her claws, trying to root out a bump she'd thought she felt under her skin. ``Uh, sorry, Aiden. Are you okay?''

The fox smiled and turned off the engine, pulling the parking break up with a series of sharp, satisfying clicks. He looked exhausted ``I'm alright. Work was\ldots{}it was a long day. Eight appointments, two meetings, no lunch. I'm starving, can we get inside and whip something up?'' His expression of excitement was transparently false.

``Mmhm, I'll make us something quick,'' she said, giving him her best goofy grin in return. ``Microwave. I promise.''

Sélène felt lucky she was actually able to pull off a seamless dinner, even if it meant relying on microwaved leftovers. She loved to cook, but sometimes, reducing the friction her brain seemed intent on pushing into the act was what the night called for. Ovens and stoves are fraught with needs, dangers, anxieties. The more tired Aiden was, the less she wanted her personal idiosyncrasies to intrude on him, or on them.

They settled into their respective sides of the couch with their plates, and set the TV to droning. It was Sélène's night to choose, so the result was a documentary. Aiden had put his foot down early on and specified that they would alternate nights of choosing programs to watch. That had soon after been amended to specify no repetitions of a program or movie within a month's span, when Sélène watched the same documentary four times in two weeks. Old habits from university turned coping mechanisms.

Tonight was some investigative journalism piece about missing people. It wasn't particularly interesting to Sélène, but the narrator's voice was nice.

Sélène finished faster than Aiden, but she always did. All of her anxieties around correctness and proper fit and safety, and somehow none of them ever involved food. Chow's chow.

``Sweetheart,'' Aiden murmured, setting his plate to the side. ``Can you pet?''

The vixen straightened up and set her phone to the side, nodding eagerly. ``Of course. Are you alright?''

``Mmhm, I'm alright. Is it okay if I lay down?''

Sélène nodded and shifted from her half-curled position to a proper sit as Aiden shifted and turned, settling back to lay his head in her lap.

\emph{``It's exposure therapy, just like with the kitchen,''} her therapist had said. \emph{``All of these are just means of exposing yourself to the biggest stressors and triggers in a careful and controlled way.''}

Aiden had come in with her that day. For a while, they had had group sessions once a month with her usual therapist, \emph{``so that you can learn to be whole together.''} The phrase had made Sélène roll her eyes, but there was no denying the utility of the sessions.

\emph{``So she should just touch me?''} Aiden had asked.

\emph{``If you two would like, yes. Just a simple touch, a way to interact with fur deliberately.''}

\emph{``Would you like that, Aiden?''}

He had grinned at that, she remembered, and nodded eagerly. \emph{``I always loved that feeling as a kid, but thought it was childish to ask for it.''}

Her therapist had smiled and nodded encouragingly. \emph{``Just petting, then. No picking, no grooming, no inspecting. And no goals, this isn't a sexual exercise.''}

There had been a tense silence at that. Her therapist had looked between them, then offered, \emph{``That can be a separate exercise. For now, there should be no goal to the act other than exposure and being close to one another. It should be a comfortable way for you to work on your coping mechanisms around the picking.''}

And so Sélène set to petting, brushing her claws lightly through Aiden's fur, combing lazy rows into it, fingertips tracing around the base of her husband's ears. Her day had gone well enough that there wasn't any tugs this way or that on her anxiety. No tugs this way or that on Aiden's fur.

The narrator's voice droned on through the second half of the documentary, and neither fox noticed when it stopped and looped back to the loading screen. The motions of the vixen's petting had become hypnotic for them both: Aiden had nodded off, and Sélène wasn't far behind.

\secdiv{}

When Sélène received her work-from-home permission letter, it had been a joy and a relief. Getting the letter had been humiliating, as had the request from HR. They had been so positive about it, so supportive, and so clueless. Lots of ``we just need to make sure'' and ``we want you to be safe, but also present''.

She \emph{was} present. She was just \emph{too} present.

Work had known this when hiring her, too. She had made it clear in her cover letter when applying, and had repeated it (and repeated it, and repeated it) during the interview. Aiden had had to talk her through a night of anxious pacing and had even requested she turn her phone to net-only mode so that she wouldn't be so tempted to call and reassure her potential employers, yet again, that she had OCD but was willing to do everything she could.

\emph{``We are happy to welcome you to the team with the position of junior editor,''} the acceptance letter had said. \emph{``We are eager to help you achieve all that you can in your work life. Please see HR about additional accommodations during orientation.''}

And they did try. She was the cubicle furthest from the kitchen. They special-ordered her a desk which was a simple, flat table with no pesky drawers or cabinets. They provided her with a laptop --- paid for in installments direct from her paycheck --- instead of a desktop. It came pre-loaded with all the stuff she'd need, as well as some stuff she didn't, but found useful anyway. The time-sensitive monitor dimming software was nice, so she left that on, and she used the timed-break software to dictate when she could check her feeds.

It just hadn't been quite enough. Nothing ever was, with OCD, perhaps by its very definition.

Her cubicle being so far away from it hadn't necessarily kept her from the work kitchen. There had been several instances of her getting caught prowling through the cupboards. Caught by coworkers she didn't know well enough to explain \emph{why} she she had to leave the cabinets open.

She got a get-well-soon card addressed to her husband after she called to check on Aiden on every break and several times besides. She had accepted the card as gracefully as she could, stammering out a lie about a death in the family.

The worst had been when HR had called her in one day for a meeting. It was a toss-up as to who was more anxious, her or the fretful mouse saying, \emph{``This is totally confidential, but one of your coworkers has been concerned about the appearance of your fur, and has asked me to pass this on.''} On the printout she was given were several domestic abuse hot-lines.

That's when she'd asked about working remote.

Friday was a work-from-home day. It was always a bit of a relief for both her and Aiden. It was time away from all of the awkwardly shaped stresses of the office for her, a time with the more familiarly shaped stresses of home. And it was a time for Aiden to relax, drive as he pleased, go eat out. He had once admitted that he would, on occasion, duck over to a nearby coworker's home to join him and his wife in cooking a gloriously uncomplicated meal.

When Sélène had first set up this arrangement with her employer, she had imagined that remote days would be far easier than working from the office.

She was half right. At first, it had been much easier. The fact of just how terrifying driving was --- there was doubtless some helpful exercise her therapist would come up with --- combined with the completely uncontrolled and uncontrollable nature of the office weighed her down and left her anxieties scrabbling for purchase.

Home was where all the particulars lived, however, and so home housed all of her particular anxieties. After a week of trying to work from the living room, Aiden helped her move her setup to the breakfast bar in the kitchen. It was a less-than-ideal solution, but, on bad days, she would at least be quick about checking the cabinets.

Home is where her grooming kit was --- something Aiden made sure she never brought to the office. Picking and over-grooming was a problem, but one that could be solved eighty percent of the way by just not having access to grooming implements. Her claws were only so good, after all.

Home is also where it felt okay to check her feeds. She began using the ergonomics software that timed her breaks in earnest, putting her phone in the living room and only checking it when the software told her to put a break. Or at least trying to.

Some days, days like today, it felt like the only anxiety remote days solved was that which surrounded driving.

Sélène knew the uptick in anxiety was due to the upcoming Saturday. An anxiety that seemed to veer wildly between ``very good'' and ``oh no''.

Work was obscured by a constant cloud of half-formed fears. Her thoughts were obscured by subtle corruptions, with so much \emph{un}-rightness, \emph{un}-wellbeing. Her view was filled with cabinets thrown wide open, the oven door hanging slack in an unchanging yawn. And still she felt that trapped feeling, that fear of being locked in total darkness, too cramped to move, air too thick to breathe.

When her break timer went off, she skittered through the kitchen, pausing only to make sure that the cabinets on the other side of the breakfast bar were still left open, and dashed out into the living room to grab at her phone. Anything to scratch one of those myriad itches. Anything for some breathing room.

By the time she had curled on the couch, she'd already gotten her phone unlocked and her feeds open. There was nothing before her but her phone and the cushions at the back of the couch, nothing behind her but an empty room. She'd curled with her head toward her end of the couch, since she knew she'd have to call Aiden if all she could smell was him at his end.

One news item. Fluff story about mod shops.

Two social updates. High school friend posting a selfie (not a good one, could see up his nose), and Malina talking about food.

Her tail, already bottlebrushed and full of nervous twitches, nearly jerked her off the couch in a rush of excitement. She cursed and scooted herself further onto the couch, slipping a paw back to brush along her tail, to calm the fur.

Sélène tapped `favorite' on the post and flipped over to her messaging window with Malina.

\texttt{{[}2:03 PM{]} Sélène\textgreater{} Hey you. What's cooking?}

The vixen winced. That had a different meaning, didn't it? What's cooking, what's \emph{cooking}. What's cooking? What \emph{is} cooking? Hey, what's cooking, sexy?

She growled to herself and tamped down her clamoring anxieties. Malina was endlessly patient. Had been from day one. Last thing Sélène wanted to do was let her anxieties spill over onto the badger.

\texttt{{[}2:04 PM{]} Malina\textgreater{} Casserole! I made some marshmallows yesterday, too. Alright if I bring those with tomorrow? I was going to surprise you, but figured I should probably ask.}

Tension drained from her as the chill of stress melted into a pleasant embarrassment. A flush of warmth within her ears. A goofy smile. Where Aiden was calm, collected, and supportive, Malina was kind, warm, and earnest. Both did wonders to calm her.

\texttt{{[}2:04 PM{]} Sélène\textgreater{} You make marshmallows?}

\texttt{{[}2:04 PM{]} Malina\textgreater{} Yup, they're really easy. Just sugar, corn syrup, gelatin, and whatever flavor you want}

Sélène grinned to her phone. She had no idea why it was surprising to her that people, not just machines, made marshmallows. It fit Malina perfectly.

\texttt{{[}2:04 PM{]} Sélène\textgreater{} That's cool. What flavor?}

\texttt{{[}2:05 PM{]} Malina\textgreater{} Lime. Sound good to you?}

\texttt{{[}2:05 PM{]} Sélène\textgreater{} Sounds excellent.} She paused, then tapped at the keyboard to add, \texttt{I'm really nervous, but really excited.}

\texttt{{[}2:05 PM{]} Malina\textgreater{} Me too. I've been thinking about it all morning. I've never been on a date}

Sélène's grin grew wider and the flush within her ears grew warmer.

\texttt{{[}2:05 PM{]} Sélène\textgreater{} Wait, never?}

\texttt{{[}2:06 PM{]} Malina\textgreater{} Well, I mean I've been on dates, yeah, but never a DATE date. Like, one that was agreed upon as a date ahead of time}

\texttt{{[}2:06 PM{]} Sélène\textgreater{} Oh. Me neither, come to think of it. Aiden and I would go out and whatever, and then just suddenly -boom-, in a relationship. I don't think either of us said `date'.}

\texttt{{[}2:07 PM{]} Malina\textgreater{} *laughs* yeah? I suppose that makes sense. You sure Aiden is okay with this?}

\texttt{{[}2:07 PM{]} Sélène\textgreater{} He says he is every time I've asked. He says it'll be good for me, but I worry.}

\texttt{{[}2:08 PM{]} Malina\textgreater{} I know. We'll keep talking about it, though}

\texttt{{[}2:08 PM{]} Sélène\textgreater{} Yeah.}

A comfortable pause, and then a thrill of chill anxiety behind her breastbone, a splash of blue mood.

\texttt{{[}2:09 PM{]} Sélène\textgreater{} You alright?}

\texttt{{[}2:09 PM{]} Malina\textgreater{} Doing great!}

The chill faded again. There was a soft, pleasant chime from the kitchen. Sélène grumbled.

\texttt{{[}2:10 PM{]} Sélène\textgreater{} Break time's up, I gotta get back to work. You working tonight?}

\texttt{{[}2:10 PM{]} Malina\textgreater{} Yeah. I traded shifts so I could get tomorrow off}

\texttt{{[}2:10 PM{]} Sélène\textgreater{} Good. You sure you don't want to go to Book and Bean for our date?}

\texttt{{[}2:10 PM{]} Malina\textgreater{} *laughs* QUITE sure. Last thing I want to do is go on a date where I work}

\texttt{{[}2:11 PM{]} Sélène\textgreater{} Fine, fine. Have fun, and I'll see you tomorrow.}

\texttt{{[}2:11 PM{]} Malina\textgreater{} Can't wait! \textless{}3}

The chime was growing louder and more insistent in the kitchen, but Sélène clutched her phone in her paw for a moment longer, smiling at that little heart at the end of Malina's last message.

\secdiv{}

The rest of the day had passed with relative ease. The conversation with Malina had broken a lot of cycling trains of thought. Not all of them, but enough that she didn't get interrupted by her compulsions. She was at the point where, as her therapist put it, she could acknowledge the obsession, recognize it, and\ldots{}well, not let it go, not this time, but at least set it at the periphery where she could keep an eye on it..

All the same, Sélène found herself spending as much time listening intently for Aiden's car as she did working.

When she finally heard it, the relief was palpable.

Levering herself up from her stool at the breakfast bar, Sélène saved her work and swung the lid of the laptop shut, stood, and stretched. She padded toward the front hallway and waited for her husband.

Aiden perked his ears and smiled to be greeted at the door. ``Hi sweetheart. Everything okay?''

``That's my line.'' The vixen grinned and leaned in for a hug. ``And yeah, I'm doing okay. A bit stressed, I suppose. Are you alright?''

Slipping his arms around her, Aiden leaned into brush his cheek against his wife's. ``Mm, very good. Good end to the week, glad to be home.''

Aiden felt secure to her. Safe. A warm and solid presence for her to lean in against, different from Malina. Steadier, perhaps, more familiar; less exciting, but pleasantly so. ``Glad you're home, too,'' she purred. ``You sure you're alright?''

``Very much so. Alright if I come in and get changed?''

Sélène canted her ears back and laughed. ``Uh, sorry. Suppose I'm a bit in the way, huh?'' She tightened her hug for a moment, then ducked back into the kitchen, letting her husband pass.

By the time Aiden joined her in the kitchen, she already had a pot of water coming to a boil, and cubes of chicken sizzling in a pan. Chicken and pasta was simple enough, clean enough, to make it an easy meal for her to deal with when she was up to cooking. Despite the day being something of a mess when it came to stress, she was feeling good enough after talking with both Malina and Aiden that she figured she'd try to work on engaging with the kitchen.

``Smells good, sweetheart. Chicken?''

``Mmhm.'' She flipped each cube of chicken precisely before tipping the box of dried pasta into the water and giving it a stir. ``Wanted to cook something for you tonight.''

Aiden padded beside her, murmuring, ``Thank you, dear, that means a lot. May I hug?''

Sélène splayed her ears, hesitating for a moment before shaking her head. ``Um, let me get to a better point, then I can. You alright?''

The fox nodded and slipped around the corner to sit on one of the stools. ``Alright. And yeah, I'm good. Feeling lovey, is all.''

``Let me finish, then,'' Sélène grinned. ``And then I'll get all lovey with you.''

Aiden laughed and nodded, watching her cook.

Simple or not, the chicken and olive oil smelled good to Sélène. Nothing special, taste-wise, but the homeyness was attractive. Chicken and noodles, some oregano and rosemary, some salt and pepper, and a --- very generous --- grating of Parmesan over the top.

Once Sélène got the food dished, leftovers boxed, and pots into the sink, they migrated to the couch with their bowls of food and ate quickly and quietly, both apparently too hungry to talk. No TV, just some music, a playlist Aiden queued up.

``Alright,'' Sélène said, once Aiden had finished and set his bowl aside. ``Lovey time.''

The fox laughed. ``Alright. A hug and some pets?''

Sélène nodded happily and leaned into Aiden for a comfortable hug, each turning toward the other on the couch. After some affectionate cheek-rubs, her husband shifted about until he was sitting cross-legged facing her, muzzle dipped down and ears perked. Sélène obliged and reached up to brush soft pawpads over the ears.

``Mm. Thank you, love.''

She nodded and stroked along Aiden's ears from bases to tips a few times, then set to sifting fur through her claws. Confronting the kitchen by cooking, confronting the picking by brushing through dry fox fur. For as twitchy as the morning was, she felt a little proud with her engagement with this evening.

Plus, Aiden's little happy purrs and content sighs made her feel accomplished.

``You excited about tomorrow, sweetheart?''

Sélène nodded and brushed her fingers back through Aiden's fur, ruffling it up before combing it straight again. ``Anxious, but excited, yeah. You sure you're alright with it?''

Aiden nodded. ``I'm sure. It'll be good for you. And Malina's nice.''

A twinge of cool unquiet struggled against a warm flush within her ears, but she nodded all the same. ``She is.''

``I'd be surprised if you didn't think so,'' Aiden laughed, flicking his ears against Sélène's paws. ``You're picking a bit, love. Would you like to talk about something else?''

Sélène tugged her paws back quickly from there they had dug through Aiden's fur. ``Uh, sorry. No, this is okay. Are you alright?''

``Mmhm. Maybe just pet my ears?''

``Alright.'' Sélène went back to stroking the velvety triangles. ``And yeah, I'm excited. Still a little surprised that you're alright with me going on a date with someone else, but happy all the same.''

Aiden finished another one of those content sighs before replying. ``I love you dearly, Sélène, but I know how much Malina means to you. She's good for you, she's fond of you, you're cute when you're together. It works.''

Sélène kept her bashfulness to herself as best she could, and focused on the feel of her husband's soft fur.

\secdiv{}

The bus ride to the 13th Street Plaza was uneventful in all ways except for how much Sélène fretted about the date to come. She pulled out her phone, refreshed her feeds, put the phone away.

Ten seconds later, and her phone was already back in her paw. A swipe down on the page, that satisfying click, no new items. She put the phone away with a conscious effort. She had promised herself she wouldn't text Aiden more than once during the whole date, unless she needed or wanted a ride home. She desperately wanted to text him now, but was doing her best to save that option for later.

Malina greeted her at the stop. The badger looked kind and cozy and happy, enough that a good chunk of Sélène's anxiety was transmuted into proper excitement.

She bounced off the bus and straight into a hug, ``Hi you!''

``You made it,'' Malina laughed. ``Good to see you. Been all nervous here at the bus stop. `What if she doesn't come?' I feel like a dorky teenager all over again.''

Sélène grinned. ``Yeah, I was all fidgety, too. You alright?''

``Mmhm. Excited, is all.'' Malina leaned back from the embrace and grinned. She held up a small paper bag. ``I'm sorry to say that I ate a bunch of them earlier, but I brought some marshmallows for you.''

``I'll admit that I've never had a homemade marshmallow,'' Sélène admitted, peeking into the bag, then reached in to grab one. ``They're square! What's the white stuff?''

Malina reached in to grab one as well. ``Cornstarch. Keeps them from sticking together.''

Sélène sniffed at it carefully. It smelled sweet, with a hint of citrus and what she could only describe as chalk. She figured the last was probably from the cornstarch, so she took a cautious bite and chewed. It was\ldots{}well, a marshmallow. But it was fresher than any she'd ever had, far more flavorful and less cloying. The lime was delightful, almost as an afterthought. A bit of brightness that added without overwhelming.

``'oh-ee thit!'' She laughed a puff of cornstarch and struggled to chew the rest of the marshmallow, swallowing to say more clearly, ``Holy shit, Malina. That's good!''

Malina grinned as best she could around her own marshmallow, a dusting of cornstarch on her muzzle. One she was able, she laughed. ``Glad you like, dear. Come on, let's walk a bit before real food. We can save the other two for dessert.''

The 13th Street Plaza had begun some decades before when the courthouse lawn and the road in front of it had been redone to fix the water main. The city had decided that in order to keep the shops there open for business, they would turn the two blocks to either side of the courthouse into a pedestrian mall. It was an attempt at turning the utility fix into something that benefited the city.

It had worked, after a fashion. Due to the traffic problems, 12th and 14th had to be reworked down the line, but the plaza had become an institution. It was anchored on one end by a record and video store, and on the other by The Book and the Bean, a coffeeshop in front that faded seamlessly into a bookstore in back and the second floor above it.

On a warm fall weekend like this, the street was full of folks of all sorts enjoying the evening: lounging on benches, poking in and out of shops, watching buskers and jugglers. Several of Sawtooth's homeless and itinerant population were parked, as usual, on the lawn of the courthouse. Come eight or nine, the security guards and police would start ushering them off, but until then, everyone seemed cozy just where they were.

Down the center of the plaza, Malina and Sélène strolled side by side, talking. Malina described her old job at a CPA office and how it went from comfortable and familiar to awkward and, at times, frightening when a coworker disappeared. How she'd left for a simpler life to work at The Book and the Bean. About the split with her husband that followed. About her love of food and cooking.

Sélène mostly listened. The excitement and nervousness had settled down to the comfortable glow she felt with the badger, with the added gloss of giddiness that came with the capital-D Date. It was comfortable around Malina, there was little she wanted to add.

``Antica Roma sound good for dinner?''

Sélène nodded, ``I've only been once. Sounds good to me.''

Malina grinned and nodded, letting Sélène stand in front of the restaurant while she went inside to get their name on the list.

\texttt{{[}5:53 PM{]} Sélène\textgreater{} Hi Aiden! You okay?}

\texttt{{[}5:53 PM{]} Aiden\textgreater{} Doing great, love. Everything going well with Malina?}

\texttt{{[}5:53 PM{]} Sélène\textgreater{} Really good. She's getting us on the list at Antica Roma, otherwise just talking.}

\texttt{{[}5:54 PM{]} Aiden\textgreater{} Good, sounds good to me. You two have fun!}

\texttt{{[}5:54 PM{]} Sélène\textgreater{} Will do. You alright?}

\texttt{{[}5:54 PM{]} Aiden\textgreater{} I'm good, sweetheart. Have a good evening!}

``Half an hour!''

Sélène jolted and grinned sheepishly to the badger, pocketing her phone. ``Oh! Okay, sounds good. You alright?''

Malina tilted her head. ``I'm fine, don't worry about me. How about you? Hope I'm not stressing you out.''

The vixen splayed her ears and shook her head. ``I'm fine. Sorry.'' She bit her tongue a moment, holding back another are-you-alright. ``I'm good.''

They turned and continued on their slow stroll down the plaza. Antica Roma was directly in front of the courthouse. Cozy and pricey. Definitely date material.

``You sure you're alright, dear? You got quiet.''

``Uh, sorry. I'm fine.'' She laughed breathlessly. ``Sorry. Are you\ldots{}uh, sorry.''

Malina tilted her head and gave the fox a nudge with her elbow, her concerned smile inviting Sélène to continue.

``I was just going to ask if you were alright, but I'd already done that.'' She scuffed at the back of her neck with her paw. ``That's\ldots{}one of my things, I guess.''

Malina's expression softened. ``A compulsion?''

Sélène nodded and gave an apologetic shrug.

``Well, I'm just fine,'' the badger smiled, leaned in, and gave the fox a kiss to the cheek.

Sélène froze, fur bristling.

``Shit, I'm sorry if that was--''

``R-really nice.'' Sélène giggled, ears pinned back. That giddiness swelled within her. ``That was really nice.''

It was Sélène's turn to pick up the conversational lead as they continued to meander east. She talked about the various compulsions and the obsessions and anxieties that drove them, about her struggles with relationship-rightness and need to repeatedly ask Aiden --- and, lately, Malina --- if they were alright. She talked about her therapist and attachment styles and the exposure therapy that was part of her work. She talked about the problems with touches to her face.

Malina, for her part, listened attentively up until the end. ``I'm sorry about the kiss, I didn't know.''

Sélène shook her head insistently. ``It really was nice, Malina. I just have a bit of trouble with it, is all. I\ldots{}hmm. Here. Like this.''

She skipped ahead a pace and turned so she could face Malina, took the badger's paws in her own, and leaned forward to brush her cheek in against Malina's own black-white-gray cheek, feeling the coarser fur against her own.

``Thats, um,'' she murmured, smiling bashfully. ``That's my kiss.''

Malina went from looking startled to grinning widely in a heartbeat, leaning in to give another rub of the cheek in return. ``You are adorable, Sélène, you know that?''

The vixen huffed and stamped her foot, shaking her head.

Slipping one of her paws free, Malina started to walking again, Sélène falling into step beside her, ears hot with embarrassment and excitement.

\secdiv{}

Malina drove Sélène home after dinner.

Sélène hadn't know Malina had a car, much less were the badger lived. After dinner, they'd walked down 13th, past The Book and the Bean for a few blocks, and suddenly, they were standing in front of a small townhouse and Malina was unlocking a car.

``Easy commute to work.'' Sélène carefully clambered into the badger's sedan. Old, serviceable, very clean.

Malina laughed. ``Yeah, I'm super close. I walk, but have the car for errands and such.''

The ten-minute ride was mostly quiet, otherwise. They had been talking nearly non-stop for well on five hours now, and their silence was comfortable. Sélène's mind was quiet, glowing. She reveled in the silence.

By the time they pulled up in front of Sélène and Aiden's house, the vixen could feel just how much the night and all the anxiety that led up to it had taken out of her. It was a cozy sort of exhaustion, the satisfying kind.

She sat in quiet for a moment after Malina put the car in park, then sighed contentedly. ``Thank you, Malina. Tonight was wonderful.'' She hesitated, then added, ``Would you like to come in? Say hi to Aiden?''

The badger shook her head. ``Not tonight. You look exhausted, and I have work in the morning.'' She shrugged, looking sheepish. ``Besides, I worry that'd be a little weird. Next time, perhaps.''

Sélène lay her ears back and nodded. ``Okay. Are you alright?''

Malina laughed and nodded. ``Wonderful, Sélène. Can I have another, er\ldots{}kiss before you go?''

The fox nodded once more, ears tilted back as if to hide her embarrassment. She leaned in and brushed her cheek in against Malina's, enjoying the familiar-yet-new sensation of it.

``Hey,'' the badger murmured as they lingered close. ``I have Wednesday off. Can I see you again after you get off work?''

Sélènea leaned across the center console to hug awkwardly around Malina, hungry for a bit more contact before heading inside. ``I'll ask Aiden, but I think so, yeah.''

With one last cheek-rub, she unbuckled and slipped out of the car.

Aiden met her at the door, smiling. He held the screen door open so that he could let Sélène in and wave to Malina out in the car. ``Have a good evening, sweetheart?''

Sélène bounced once or twice in a fit of residual excitement, ``Very good! You okay, Aiden?''

Her husband let the screen door shut and ushered Sélène further into the house so he could close the door proper. ``I'm fine, yeah. Look at \emph{you}, though, you're glowing,'' he laughed. ``May I hug?''

``Mmhm. Sorry, I can't help it,'' she purred, leaning into her husband's arms and rubbing her cheek up against his own. His fur was softer, warmer, more familiar than Malina's. She certainly \emph{felt} as if she were glowing.

Aiden returned the affectionate nuzzle and murmured quietly, ``No need to apologize. I'm happy for you, sweetheart. Did you invite her in?''

Sélène nodded and relaxed against her husband's front, tucking her muzzle up under his after the `kiss'. ``I offered, but she said she has work in the morning.'' After a moment, she added, ``She said she also would feel a little weird about it.''

``Mm, okay,'' Aiden said. ``Maybe it would have been awkward. Hopefully that's something that will change, though. Something we can work on.''

``Do you feel weird about it?''

``About her coming in?''

``Yeah.'' Sélène shrugged. ``Or about any of this, I guess.''

``A little,'' Aiden said. He leaned back from Sélène enough to meet her gaze. ``I'm happy for you, though, sweetheart. It will take some getting used to for all of us, is all.''

``I think I understand. Are you alright?''

Aiden nodded. ``I'm alright, love. It's good to see you happy. You look exhausted.'' He hesitated for a moment before asking, ``Would you be up for chilling on the couch for a bit before bed, though? I want to hear about your date, if you'd like.''

Sélène nodded and tightened her hug around Aiden briefly before relaxing. She padded quickly past the entrance to the kitchen so as to not get caught up in compulsions just yet, though she could feel the doubt and worry growing frostily within. She clambered up onto the couch and dug her phone out of her pocket instead. She'd checked her feeds in the car, so they should be empty, but the act of pulling down to refresh was a comforting thought.

Aiden laughed and followed after her, flopping back onto the couch. ``So,'' he lilted. ``How was your date?''

Sélène tilted her ears back as if to hide the warm flush of embarrassment. ``It was\ldots{}good.'' She laughed giddily and shrugged. ``It was good. We walked along the plaza. Ducked in to say hi to her friends at Book and Bean, ate dinner at Antica Roma.''

Aiden grinned, nodded, and made little urging gestures with his paws, as if drawing more story out of his wife.

``We talked a bit about her and where she is in life.'' Sélène fiddled with her phone, pulling to refresh over and over, just for the sound of the click. ``And we talked about me, and the compulsions. Like why I ask if she's alright, or you're alright, and why it's hard to have my face touched.''

``Oh?'' Aiden perked up. ``Did she kiss you, then?''

Sélène's ears went from being just tilted to fully pinned back. ``W-well,'' she stammered. ``She did. I um\ldots{}I showed her what works instead of that.''

Aiden nodded and opened his mouth to speak, before being cut off frantically by Sélène.

``Are you alright? Is that alright?''

Her husband held up his paws to forestall any further questions. ``It's alright, I promise. I'm really happy for you.'' He laughed and added, ``Sweetheart, you're adorable.''

Sélène smiled nervously and bowed her head. ``Uh, thank you.''

``Of course, love.'' Aiden held his paws out, offering. Sélène relaxed, set her phone in her lap, and rested her paws in his.

``Are you sure you're alright, Aiden?''

The fox brushed his thumbs over the soft-furred backs of his wife's paws. ``I think so, yeah.''

Sélène winced, more at the words than the touch. ``\,`Think so'?''

``Mmhm. I'm really happy for you. I was just thinking,'' he trailed off, shrugged, and pushed ahead. ``I was just thinking, the kiss is probably something only the two of us had ever done, until tonight.''

Sélène shivered and nodded. Without any direction for her nervousness, without anything to obsess over other than her relationship-rightness with Aiden, she felt trapped, frozen in an icy block of anxiety. ``Is that okay?''

Aiden nodded. ``It is, sweetheart. Like I said, it's something for us to work on. It's new, not bad, and I'm trying to change to make it work.''

The vixen nodded, struggling to find an outlet for that energy. She couldn't meet her husband's eyes, and was unwilling to lose the contact of his paws holding hers for anything so silly as grabbing her phone. Her tail was already bristled out between her and the arm of the couch.

``Hey. Sélène, look here,'' Aiden said. When she pointed her muzzle at him without making eye contact, he lifted her paws in his, and gave them a rub of his cheek, a `kiss' to their backs. A gesture he'd never done before. ``Look at me, sweetheart.''

At that, she did make eye contact. She felt on the verge of tears, without fully understanding why. Aiden was so reassuring, so loving; and she was so terrified of losing him. Aiden was smiling so kindly, and she could barely keep from crying.

``May I hug?''

Sélène nodded, and let Aiden draw her into his arms. They brushed cheeks a few times, before she just wound up resting against him. She managed to keep from crying outright, but at the expense of some sniffles.

``Tell me something good about your evening,'' Aiden murmured, after Sélène had calmed down.

She thought for a moment. ``I think\ldots{}that I was able to open up, I guess. I can talk \emph{about} stuff with people, but only really engage with you two.'' She hesitated, then added, ``If that makes sense.''

She felt Aiden nod above her. ``Yeah. Talking can take a lot out of you, if you're not engaging.''

``Mmhm.''

``And did you come up with any plans for another date?''

``She suggested maybe Wednesday. She said she had it off.''

``Go.''

Sélène jolted at the word, and Aiden laughed. ``I mean, go on the date. Not go away or anything.''

``Really?''

Aiden nodded again. ``Definitely. Go. I want you to experience more of that, and I want us both to get more comfortable with this. All three of us, I suppose.''

``Okay.'' Sélène bit at the side of her tongue, realized what she was doing, and forced herself to stop. ``And you're alright?''

``I'm alright, sweetheart.''

\secdiv{}

Sunday was a calm leisurely day for the pair.

Aiden cooked brunch --- Sélène was hopeless when it came to eggs --- while Sélène picked out songs she thought were interesting and tried to explain why to Aiden. Later, they walked to the park at the end of the block and made their way through the Frisbee golf course. Neither played, but it was low-key exercise, and comforting for Sélène to walk each hole from start to finish.

Later, Aiden ran to get groceries while Sélène wrote on some of her personal projects.

That night, they watched two movies, having each picked one.

The sheer normalcy of the day helped to dampen Sélène's lingering anxiety, keeping the day from going above a four. She liked Malina a lot. Maybe even loved her, who knew. But the things that she shared with Aiden she could never share with the badger. She and Malina could watch movies, but it would never be the same as watching movies with Aiden.

Throughout the day, it never felt right to bring up in conversation, though. Neither she nor Aiden talked about the night before, nor the upcoming Wednesday. It didn't feel like a closed topic, so much as something that was comfortable to wait on.

It only came up again on Tuesday night, when it came to setting up logistics. It was Aiden that brought it up first.

``Do you know what you two are doing tomorrow night?''

Sélène looked up from her phone. She'd spaced out during whatever Aiden had picked to watch after dinner. Chatting with Malina, no less. ``She suggested dinner at her place.''

Aiden nodded. ``Do you want to me to drop you off on the way home from work?''

``Oh! That would work.'' Sélène sat up. ``Would that be okay?''

``Of course, sweetheart.''

Sélène picked at the fur on her wrist. There was a slight bump just on the top of the bone, perhaps a small scar from picking earlier. She'd already worried a small bald-patch in the fur. ``You sure that's alright?''

``Mmhm, I'm sure.'' Aiden held out one of his paws for hers.

She transfered her phone to the other and let her husband take her paw. She smiled bashfully, ``Sorry, I was picking.''

Aiden lifted her paw, turned her wrist upward, and leaned to brush his cheek over it. ``A kiss to make it better.''

Sélène giggled happily and moved her phone to the armrest of the couch so she could lean in closer, and return the kiss in turn, brushing her cheek in against his. ``You're a dork.''

He laughed and gave her paws a gentle squeeze in his own. ``I love you too, sweetheart.''

She squeezed his paws back before tugging free, grabbing her phone once more and squirming around to lean back against him. ``Alright, let me tell Malina, then, before I lose my nerve.''

Shifting to let her get more comfortable against him, Aiden rested his arm up along the back of the couch, making a show of watching the movie. Sélène was protective of her phone, but Aiden always went out of his way to show he wasn't shoulder-surfing.

Once she'd finished and gotten the okay from Malina and set her phone back down in her lap, Aiden tilted his muzzle enough to brush it against one of his wife's ears. ``You've been doing really good the last few days, you know that?''

Sélène tensed at a frisson and flicked her ears against Aiden's muzzle. ``Tickles,'' she mumbled, then nodded. ``Yeah, it's been good.''

``Any particular reason why?''

``I think--'' Sélène hesitated while she dug for words. ``I think just having a direction to put energy.''

``Good, yeah.'' Aiden gave her ear another nuzzle before leaning down to put a kiss --- a proper one, rather than a cheek-rub --- atop her head.

Hunching her shoulders and splaying her ears to the sides, Sélène tucked herself in closer to her husband, paws folded together so she could pick at her wrist again.

``Sorry, sweetheart. Bit too much?'' Aiden lifted his muzzle clear of the area to let Sélène scrub at the spot with her paw.

``Uh, a little.'' Realizing what she was doing, she reached up to tug Aiden's arm along the back of the sofa down along her front so that she could focus on petting rather than picking. ``Sorry. Are you alright?''

Aiden let his arm be claimed, carefully snaking it partway around his Sélène in a sort of hug. ``Mmhm, I'm fine.''

The two sat quietly, letting the rest of the show play out until the credits.

``I love you, Aiden.''

``Mm? I love you too, sweetheart.''

``I think I forgot to say so earlier,'' Sélène murmured sleepily. ``Thank you for putting up with your nutball wife.''

Aiden turned enough to give her a fond cheek-rub. ``Of course, love, that's my job. Let's get you to bed so you can be all rested for tomorrow.''

\secdiv{}

Work often colors the perception of days of the week. Sélène, for instance, had three quarters of her meetings on Wednesdays. It was her day of drudgery. The one day she wasn't allowed to work from home. There was a project sync-up, an editorial staff meeting, a project lottery, and a one-on-one with her direct supervisor.

Best case, Wednesdays felt like less-productive workdays. Sélène would sit in her spot by the door and try to pay attention to the staff meeting. As junior editor, she wasn't eligible for the project lottery, but she might be working with someone who was. She'd talk through progress on her own project with the team during the sync-up, then she and Jeff, her manager, would hash out the details. Jeff always seemed vaguely puzzled by Sélène, but she got her work done, at home and at the office, so he rarely complained.

Worst case, she'd be a jittery mess. She'd play with her phone, or pick at spots on her arms. She'd fret over Aiden. She'd fret over home. One week, she seriously considered buying a net enabled camera for the house so she could keep an eye on things, then had to run to the restroom and wash her face to clear thoughts cameras and stoves and cabinets.

This Wednesday was seemingly neither of these. It was apart from other Wednesdays in some intangible way.

She was going to have her husband drop her off at her girlfriend's house tonight.

She kept repeating that over and over inside her head, trying to make the shapes fit. \emph{Work. Husband. Girlfriend. Husband\ldots{}driving me to girlfriend. And it's a good thing?} Very good.

She'd never had a giddy Wednesday before.

``Sélène? You okay? 'Bout done here.''

She snapped her head up, smiling apologetically to the coyote. She brushed her fur down on her wrist. ``Sorry, Jeff.''

``It's okay. Stressful day?''

``No.'' Sélène thought for a moment. ``Well, yes, but not at work. Date tonight.''

Jeff racked his notes against the desk. ``That sounds good. Where are you and Aiden headed?''

Sélène halted halfway out of her chair.

Shit.

``Uh. We're\ldots{}'' She struggled to come up with something, feeling suddenly more on the spot than she probably was. All that she could think of was the truth. ``We're going to someone's for dinner.''

True enough.

``Oh, well, have a good one,'' Jeff said, smiling quizzically as Sélène skittered out of his office.

She managed to make it through the rest of the day without incident, but perhaps only by dint of her sticking to her cubicle as much as possible. She spent half her time there working, and the other half daydreaming and digging at the spot on her wrist. That little bump she'd found had been a focal point ever since, and she'd already picked it clean of fur. There had to be something there. Splinter, ingrown fur, or something.

As early as she could manage without attracting attention, Sélène made her way out to the front of the building, camping on one of the benches normally used by smokers during their breaks.

Fall had treated Sawtooth well, this year. There had been a few chill days, but no freezes yet. It had remained unremarkably comfortable. The sort of weather you never think about. The sort of weather that was only ever ``nice'' in conversation.

It \emph{was} nice, too, so Sélène sat and waited outside for Aiden. Enjoying the non-conditioned air, relative quiet, and natural light.

The sun warmed the dark fur of her paws as she brushed her claws through fur, half-conscious of searching for any other perceived imperfections. The rest of her dreamed of Aiden and Malina, and the different sensations of their cheeks against hers.

``Sweetheart?''

Sélène yelped and jumped to her feet. ``Aiden! Sorry!''

The fox laughed and held out his arms to offer a hug. ``It's okay! It's okay. Spacing out?''

``A little,'' Sélène gasped. She got her breathing under control and un-bushed her tail with a few brushes of her paws before leaning into Aiden's arms. She brushed her cheek up against his. ``Sorry. You alright?''

``I'm alright,'' he said, tightening the hug for a moment. ``How're you?''

Sélène relaxed against her husband a bit longer, enjoying the solidity of him. ``I'm good. Weird day, spent most of it up in my head.''

The fox nodded, gave her a squeeze, then guided her back to his car. ``Good weird? Stressful weird? Your paws and arms are all ruffled.''

``Good weird, mostly.'' Sélène brushed her paws down over her arms, realizing she'd gone after more than just that spot on her wrist without realizing it. ``Better than I look, I guess. Are you alright?''

Aiden waited to respond until they'd both clambered into the car. ``I'm alright. Long day, but a pretty good one. Going to meet up with Aaron from work, grab dinner with him and his wife while you're out. You excited?''

``Yeah. It's been going through my head all day. You sure you're okay driving me?''

``I already am,'' he laughed.

Sélène tilted her ears in a flush of embarrassment. ``Right. But to Malina's?''

Aiden nodded.

``Alright.'' She picked at her thumb briefly, then forced herself to stop. ``This feels a little goofy, I guess.''

``What?'' he laughed. ``Driving my wife to a date with her girlfriend? I guess it is. It was on my mind all day, too. I'm still happy for you, though.''

Smiling nervously, Sélène brushed her fingers along her arm, finding bits of fur she tugged out of order and straightening them out as best she could. She kept finding new bumps and spots begging to be picked. Eventually she just gave up. ``I hope it goes well. Been looking forward to it.''

``It will sweetheart, I'm sure of it.''

``Just hoping I don't get all weird about her kitchen cabinets or whatever, is all.''

``If so, do you think you could ask to put on a show or something?''

``Mmhm.'' Sélène grinned to her husband. ``She's got your taste in movies.''

``So, good movies, then?'' Aiden laughed. ``Maybe we could do a double date or something, sometime. A\ldots{}one-and-a-half date.''

The vixen grinned. ``That might be fun. Is that something you'd be up for?''

Aiden hesitated. ``Down the road, perhaps.''

Sélène's smile faded. ``Okay. You alright, Aiden?''

He nodded. ``Yeah. Just hit by the realization of how strange and new this feels, still. I'm trying, though. Maybe we ought to all get together soon, just so we can\ldots{}I don't know, be around each other. See how we work.''

``That'd be good.''

They drove in silence for another few minutes, until they made it onto east 13th street. Aiden rested his arm down on the center console, paw up, and murmured, ``You're picking, dear. Want to hold my paw?''

Sélène squirmed and clenched her paws into fists, then relaxed them again and rested her paw in his. ``Sorry, Aiden.''

She still felt itchy those last few blocks, still felt as though her skin were imperfect beneath her fur. Dirty. She focused on just resting her paw in her husband's, on the feeling of his pads against hers. She imagined she could trace every line across his them, feel every perfection of his and each imperfection of hers.

Aiden smiled over to her, then nodded up the street. ``This it, here?''

``Oh! Already.'' Sélène smiled. ``Yeah, the one with the green car out front.''

The car slid smoothly up to the sidewalk in front of the townhouse. Aiden had to reclaim his paw to shift into park, but quickly returned it. ``Have a good evening, okay, sweetheart? Message if you need a ride back.''

Sélène gave his paw a squeeze once she got it back, leaning over to brush cheeks with her husband. ``Mm, alright. Can I leave my bag with you? Um, and are you okay?''

Aiden laughed and nodded. ``I'm good. I'll get your bag home safe and sound. Now go, have a good time,'' he said, tugging his paw free so he could shoo his wife out of the car.

``Alright, alright.'' Sélène beamed, leaned in for one more cheek-rub, then slipped out onto the sidewalk. ``Love you.''

``Love you too, sweetheart.''

The vixen closed the car door behind her and made her way up to the stoop. She knocked, and once Malina opened the door, waved back over her shoulder to her husband.

``Hey you.'' The badger grinned.

Sélène smiled back and leaned in to brush her cheek against Malina's. ``Hi. Long time no see.''

``It's been ages,'' Malina laughed, opening the door further. ``Days, even. Come on in, dinner's already ready, so no need to prep anything.''

She followed after Malina, slipping into the entryway, swishing her tail out of the way, and closing the door behind her.

Malina's place is bright and spacious. A simple place, clean and orderly, the room was larger than she would've expected, though perhaps that was due in part to the way the kitchen was an open corner of the room. Kitchen, dining room, and living room provided a veritable landscape of a room.

It was very Malina.

``Your place is beautiful.''

Malina nodded. ``I like this place. Cyril never did, so I lucked out on that end of things when we split. Come on in, though, make yourself comfortable.

Sélène followed the badger as she trundled in to the kitchen. The sight of all of those cabinets, clearly visible from anywhere in the great room, made Sélène's arms itch all over again. ``Didn't realize how big this place was. Never seen a kitchen this exposed to the rest of the house.''

``It's nice, isn't it?''

``Mm.'' So many cabinets. So many drawers.

\emph{Stop it, Sélène.}

``I can duck in and out of the kitchen whenever I want,'' Malina said proudly. ``Suits me, I guess.''

The fox forced herself to stop gritting her teeth and smiled, ``That it does. Smells nice in here, too.''

``Chicken and pasta sound okay?''

``Sounds wonderful,'' Sélène laughed. ``My favorite, actually. Good guess.''

Malina tapped at her temple with a claw. ``Smart folk, badgers. Read it in your future.''

``Read?''

``Dumb joke. I do tarot readings on the side.''

``Really?'' Sélène blinked. ``I mean, I guess it fits. Madame Malina with a wicked pack of cards.''

``I'm no clairvoyant, more like something between a therapist and a mom.'' Malina laughed and shook her head, ``I did make us food, though. Ready to eat now?''

The two ate at the dining room table, though the `dining room' was simply a handy spot next to the kitchen.

After some waffling, Sélène took the seat facing away from the kitchen, though she regretted it soon after. It felt as though the cabinets were watching over her shoulder. Too much anxiety, too much blue.

Still, the food was very good, and not at all how she would've made chicken and noodles. Malina had cooked the chicken to be quite spicy in the barest hint of a sauce, and the noodles were tossed with peppers and vegetables. Looming kitchen or not, Sélène cleaned her plate. The badger was a wonderful cook.

They talked about their day, though Malina did most of the talking. All Sélène could manage was to say that she'd been nervous all day. Malina filled in for her, talking about deciding what to cook, running into people at the store, peeking in at The Book and The Bean to say hi.

From anyone else, Sélène would've glossed over all of this as polite chatter, but it was comforting, coming from the badger. Her voice was soothing, her words reassuring. She had a kind sense of humor, and could get Sélène laughing without anyone being the butt of a joke except perhaps herself.

The conversation flowed from the day to broader topics, and as Malina swept the dishes off to the sink, Sélène talked about her work, and what had gone into finding a job that would work with her as well as this one did. They wafted over to the couch --- much to Sélène's relief --- and slouched together. Sélène kept talking, about school and finding ways to live and work, and about meeting Aiden.

``You're a very lucky, fox, Sélène. You and Aiden fit together so well.'' The badger smiled kindly at the vixen's embarrassment before carrying on. ``I mean this in the nicest way, but I think he needs someone to care for, and you need someone to care for you. It's a good fit.''

``Thank you.'' She looked down at her paws and shrugged. ``I guess if I'm honest, it wasn't until I admitted to myself that I couldn't do things alone that I started doing better. I never did well as a kid, and no one knew what to do about it, so they just left me alone.''

``\,`They'?''

Sélène gave a dismissive wave of her paw. ``Mom and older sister. Mom was unpredictable, Marguerite was just mean.''

``Yeesh, childhood's hard enough as is, without that.'' Perhaps sensing the tension in the fox, Malina shifted the subject. ``\,`Marguerite'? Is your family French?''

``Oh goodness no,'' Sélène laughed. ``We're from here, via the east coast, and I think England before that. Mom was crazy, though, and really wanted to have been from France. `Sélène' isn't even really a French name, not like `Selena' or `Celine'. My mom thought the extra accent made it sound more French, but now I just mean `lunar'. She lived in a fantasy.''

Malina gave the fox an appraising look. ``You don't look much like a moon, dear.''

``I'd hope not.'' Selina grinned.

The badger slipped her arm around Sélène, gently tugging the fox toward her. Sélène squirmed to get her tail out of the way and let herself be guided until she was leaning back against Malina, and Malina back against the arm of the couch.

``You are looking kind of pocked and cratered, though,'' Malina murmured, brushing fingers along the scuffed up and pocked fur on Sélènea's arm.

``Sorry. I was picking, I guess.'' Sélène massaged at a tuft of fur on the back of her paw self-consciously. The badger was comfortable and comforting, but that didn't stop the desire to dig at her fur.

``It's alright, dear. You don't need to apologize.'' The badger fussed a dull claw through another of those tufts, then paused. ``I should have asked. Is this alright? Me touching where you were picking?''

``It's okay, yeah. If I try to do it now, I'll find what I was picking at and start doing it again.'' Sélène tilted her head enough to get a peripheral glance of Malina, a pale blue flare of anxiety tickling along her spine. ``Sorry. I mean\ldots{}sorry. Are you alright?''

Malina met Sélène's head-tilt with her own, brushing cheek to cheek. ``Shh, I'm alright, dear. Let me take care of you,'' she murmured, setting about grooming along one of Sélène's forearms. She worried her claws through the fur around each spot, straightening it out to lay flat again.

The sensation of being fussed over and cared for made Sélène feel small, young. It was some combination of intimate and caring, that touched on both the parts of her that needed affection and the parts that needed attention. It calmed her and made her anxious at the same time.

``You're still all tense,'' Malina said. ``You sure this is okay?''

The vixen nodded, ``It's okay. I just\ldots{}still kinda anxious, I think.''

Those attentive paws continued their work of grooming down her arms as the badger brushed her cheek to Sélène's. ``If you need to pick at something, you can pick at my fur.''

Sélène buzzed past possible responses --- ``that's not how it works'' and ``it doesn't feel good, I don't want to do that to you'' and ``are you alright?'' --- and just did her best to settle against Malina and enjoy the touches. \emph{It's exposure therapy, maybe,} she thought desperately. \emph{I'm being present without engaging in the compulsion.}

``This is nice,'' she mumbled.

``To be touched? Or groomed?''

She shrugged. ``Both, I guess.''

Malina nodded and brushed her fingers down over the fox's left arm, having mostly sorted out the rough patches, and moved on to the right. ``When I first met you, when you started coming to Book and Bean, I'd see you with your arms or neck like this, and I thought you were sick, like your fur was falling out.''

``Thankfully not,'' Sélène giggled.

``And once I knew what was up, I guess I wanted to sit you down and help you groom.''

``Like this?''

``Well, I figured it was more likely we'd sit at a table all professional like.'' Malina laughed. ``That I get to do it with you in my arms is certainly beyond anything I imagined.''

Sélène tilted her ears back, feeling them flush along the insides. She shifted herself more comfortably against Malina, thankful for a partner larger than herself, even if only by a few inches. ``That's the nicest bit,'' she purred, brushing her free paw along the badger's arm.

Neither seemed keen to move after all the grooming that could be done had been done. Malina hugged her arms comfortably around Sélène's middle, while Sélène brushed and petted through their fur, an echo of the grooming she'd just received. They shared brushes of the cheeks and soft, content noises and familiar scents.

``Should we start the movie?''

``Mm.''

Neither moved from their spot on the couch. Neither moved at all, other than Sélène's claws tracing lazy lines through Malina's arm-fur and Malina's paw scrunching up a pawful of Sélène's shirt to brush her knuckles through belly-fur.

After a minute, they both laughed.

``Guess not, huh?'' Malina said.

Sélène stretched a little at the tickle of claws in fur. ``We seem to be doing okay without. You alright?''

Perhaps sensing Sélène's ticklishness, or perhaps for her own reasons, Malina ducked her paw beneath the shirt she'd scrunched up to pet through fur more directly. ``I'm okay, dear. This alright?''

The vixen relaxed again, without the ticklishness keeping her tense. ``Mmhm, mostly just around my face and arms that I pick.''

``Not just where,'' Malina said, stroking through soft fur. ``But me touching you like this. Petting. Is that okay?''

Sélène nodded, relaxing back against the badger and brushing her fingers through coarser black-white-gray fur. Her ears and cheeks were flushed warm, giddiness making her breathing pick up. ``Very okay. It feels nice.'' She giggled quietly and added, ``Feel anxious, still, but the good kind of anxious.''

Malina laughed, ``Isn't that just `excited'?''

``Excited, yeah,'' Sélène said, after a moment's thought. ``Excited and warm.''

Rubbing her cheek to Sélène's, Malina broadened the reach of her touches, hiking Sélène's shirt up a little further to comb her fingers through more fur. ``You are warm, at that. And soft. Is this okay?''

``Mmhm.'' Sélène felt as though she as thinking through a layer of cotton, her thoughts and feelings coming through softer, warmer, more rounded than they would have otherwise. The sensation of Malina's fingers brushing and stroking through the mussed up fur beneath her shirt added to this muzziness with each pass.

She stretched almost luxuriously, careful not to melt out of range of the badger's wide paws. It was unusual for her to relax under touch, rather than tense up. Even when the touch felt good, it usually brought with it tension, if not anxiety. She was keen to enjoy what she could.

``When we started to get closer,'' Malina murmured, muzzle resting against Sélène's cheek. ``I would think a lot about how soft you must be.''

Sélène perked an ear up. ``Soft?''

Malina nodded, smoothing out the fur under her paw. ``Even when you were picking, your fur looked so much softer than mine. Or Cyril's, for that matter.''

Sélène laughed.

``I'd think about that a lot. Just kind of daydream.''

``And?''

Malina tilted her head. ``And what?'' she murmured, putting both paws to work petting over Sélène's belly and sides.

The fox squirmed at the touches, and Malina paused. ``S'okay, little ticklish. Am I as soft as you daydreamed?''

The badger nodded and shifted her paws back toward Sélène's belly. ``I think so, yeah. You're not pillowy soft or whatever, but your fur is way softer than mine.''

Sélène brushed her own pawpads along the backs of Malina's paws and up her forearms a ways. Her fur was far coarser than a fox's, but no less pleasant to touch. ``You thought about that a lot, didn't you?''

Malina nodded again, whiskers brushing against Sélène's cheek. ``I thought about \emph{you} a lot, dear. I was sweet on you for a long time, there.''

Tilting her head back, Sélène did her best to rub her cheek against Malina's, murmuring, ``I'm pretty sure that went both ways.''

She languidly lifted her arms to try and loop them loosely around the badger's shoulders. It was a bit too much of a stretch, but she made it far enough to comfortably reach Malina's nape, which she set about combing with her claws.

She could feel Malina shiver behind her in response to the touches, hear a growl and a chuff. She quickly lifted her paws. ``Sorry. You alright?''

``Mmhm.'' Malina's arms tightened around Sélène, one paw slipping around the fox's waist and the other slipping up beneath her shirt, wandering perilously close to her chest. It was a kind grip, but a possessive one. ``Bit of a tender spot, there.''

Sélène held still in the badger's arms, tense and quiet. ``In a good way?''

``In a good way.''

Relaxing again slowly, Sélène delicately set her paws back down on the badger's scruff, petting slowly through the fur. ``Are you\ldots{}uh, is this okay?''

The growl came out as more of a rumble this time. ``This is okay. I'm alright, dear.''

Sélène relaxed back against the badger, trying to get back to that warm, cotton-muffled space. It was easy to do. So easy to relax into comfort like this around Malina. So warm and so far removed from the chill anxiety of obsession.

It took another moment or two, but they both settled down again. Malina resumed her petting, ruffling, combing, and grooming with one paw on Sélène's belly and the other just above that, inching her shirt up higher and higher.

For her part, Sélène combed and stroked down over the scruff of the badger's neck, gently at first, and then a bit more firm, listening and responding to the pleased sounds.

They murmured quiet things to each other. An is-this-alright here and a you-can-do-that-more there. Through careful negotiations, their touches moved from comfortable to sensual, from aimless to focused. Each explored the ways in which the other moved, found ticklish spots and avoided them, found pleasurable spots and gravitated toward them.

Sélène learned that if she combed her claws from the base of Malina's skull down to the base of her neck, she could get a thrill out of the badger, a shudder and another of those chuffs. She used this sparingly, knowing full well that too much touch left one tingly.

She also learned that she arched up when Malina's paws brushed up over her chest, cupping a breast. She learned that Malina enjoyed such responsiveness, that the pads of the badger's paws were pleasantly coarse, that an embrace could be both tender and possessive. It all added to a pleasurable current of warmth flowing through her.

That current stole time from her. It took logic and caution. It lowered defenses and raised sensitivity. It was a smooth sense of pleasure that arced from behind her sternum to the center of her abdomen. Smooth and alluring, it made her want more, and the more she got the more she wanted. It was panic inverted. It was desire.

By the time the badger's other paw dipped down over her belly to tug at the drawstring to her pants, Sélène was lost to that current.

She gave herself up to Malina.

Malina, who was so comforting a presence, who had so sure a touch, who seemed to know just what Sélène needed.

Malina, who learned quickly how to draw a moan from Sélène, who knew to shift her focus before a touch got to be too much, who responded to Sélène as readily as Sélène responded to her.

Malina, who seemed to know just how intensely that desire moved within Sélène, who knew how to track it --- its rise, its plateau, its crest --- and who held Sélène tightly to her as the vixen cried out and shookm when the desire crashed down into a sudden rush of pleasure.

And as each wave of warmth and ecstasy passed, Malina kept Sélène held comfortable and safe.

Sélène brought her arms down to simply hold onto Malina's arm. The warmth within her faded and was replaced by that soft, cottony feeling magnified ten times over. She could feel a touch of anxiety, a touch of shame peeking in, but it was muffled, distant, barely visible behind the comfort and calm.

``Is this alright, love?'' Malina's voice was soft, low. She sounded as though she were in the same comfortable dream as Sélène.

Sélène purred. ``Wonderful.''

The two sat in silence, Malina hugging around Sélène's middle and Sélène hugging Malina's arms to her front.

\secdiv{}

Sélène must have dozed off, or at least gotten close to it, as she jolted suddenly awake at the feeling of her phone buzzing against her thigh.

``Your vibrating,'' Malina mumbled, sounding about as asleep as Sélène had been.

Squirming, the vixen struggled to free the phone from her pocket. She blinked and squinted as the screen swam into focus. ``Nine thirty, yikes,'' she mumbled, and pawed at the message notification from Aiden.

\texttt{{[}9:32 PM{]} Aiden\textgreater{} Having a good time, sweetheart?}

Sélène furrowed her brow

\texttt{{[}9:33 PM{]} Sélène\textgreater{} Wonderful!}

\texttt{{[}9:33 PM{]} Aiden\textgreater{} Glad to hear! Would you like me to pick you up tonight, or will Malina drive?}

``Shit.''

Malina yawned. ``Everything alright, dear?''

Logic seemed to be making its way back in fits and starts. Late. She needed to be back home tonight. Aiden had to come pick her up, or Malina had to drive her.

``Shit.'' She squirmed until she could sit up straight, tugging her tail around to her side. ``Um. Sorry. Are you alright?''

The badger, nodded. ``Sleepy, but alright. Is everything okay?''

``I need to be back home soon.'' She bit at the side of her tongue and winced. ``Aiden is wondering whether he should drive or you.''

Malina shrugged, yawned once more, and smiled to Sélène. ``I can drive, if you give me a bit to stretch and wake up.''

``Sorry, Malina. I hope it's not\ldots{}I lost track of\ldots{}are you alright?''

``I'm alright, love.'' The badger leaned in for a kiss, seemed to remember herself, and rubbed her cheek to Sélène's. ``It's no trouble. Sorry I dozed off there. It got late, didn't it?''

Sélène settled down at the `kiss', returning the cheek-rub and smiling bashfully. ``A little, yeah. I think I dozed off, too.''

Malina nodded. ``Well, alright. I'll get ready. Do you want to take any of the chicken home with you?''

Stretching and twisting at the waist, Sélène winced at tense muscles and cool anxiety, then nodded. ``If you'd like. It was wonderful, and I bet Aiden would like some.'' She hesitated a moment, before asking, ``May I use your bathroom before we leave?''

``Mmhm, first door on the right, dear.''

Sélène padded off and locked herself in the restroom, which was, thankfully, as spotless as the badger's kitchen. She had made the judgment between urgency and anxiety, factoring in the admonition to urinate after sex and the likelihood of cabinets, and\ldots{}

She could feel herself starting to spiral, She felt ashamed. She felt sticky and unappealing and dirty. She felt like she'd intruded and had done something horrible.

She tamped it down as best she could. The night had been good. Spectacular, really. The last thing she needed was for it to be painted blue with worry.

All the same, she quietly eased open the cabinets under the sink, settling down on her knees to peer into the darkness.

On finishing up actually using the restroom, she tugged her phone out and swiped over to Aiden's messages.

\texttt{{[}9:37 PM{]} Sélène\textgreater{} Malina will drive. Home in a bit.}

\texttt{{[}9:37 PM{]} Aiden\textgreater{} Okay, see you soon}

Sélène padded back to the great room and smiled sheepishly to Malina. ``Sorry. I'm about ready. Are you alright?''

Malina beamed. ``Wonderful. Come on, dear, let's get you home.''

\secdiv{}

The drive back was quick and quiet. Both Sélène and Malina seemed lost in their own thoughts, and while she couldn't speak to Malina's, Sélène's swirled in a figure eight around how nice the evening was and how she would even begin to talk about it with Aiden.

The ride wasn't nearly long enough to sort out either, and by the time they stopped in front of home, Sélène could feel the anxiety coming on in icy pangs. It made her chest tight and her fingers tingle.

``Tonight was wonderful, dear. Thanks for coming over,'' Malina rumbled. ``I hope you had fun, too.''

Sélène nodded. ``Very much so. You sure you're alright?''

``I'm alright, dear, promise. Enjoy the rest of your night, and lets see about getting together soon. Friday or Saturday work for me.''

The fox nodded again and picked at a spot on her wrist. ``I'll ask Aiden. And you're sure--'' She cut herself off and shook her head. ``Sorry. Um, kiss before I head off?''

They brushed cheeks and smiled to each other, exchanging their goodbyes before Sélène slipped out of the car and padded up to the stoop, clutching her little container of leftovers.

As before, Aiden was waiting at the door with a smile. He waved to Malina and held the screen door open for his wife. Sélène ducked inside quickly. The night felt crisp and chilly. She wasn't sure how much of that was actually the case, though, and how much was just her anxiety robbing her warmth.

``Hi sweetheart. How was your--'' Aiden paused in the act of leaning forward to brush cheeks with Sélène. His nose twitched and his ears canted back. ``Uh\ldots{}date went well, I'm assuming?''

Sélène's own ears perked up, and then flattened back as she realized that her husband could smell her. He could smell Malina.

He could smell what they had done.

Her body tensed up as she tried to make herself smaller, tried to hide without moving. The chill blue of anxiety froze to a bright, frozen white of outright panic, and Sélène began shivering. ``I'm s-sorry Aiden\ldots{}I-- W-we just\ldots{}'' She swallowed. ``Are you alright?''

``I'm\ldots{}'' Aiden frowned, then shook his head. He straightened his back and squared his shoulders. ``I'm okay, I think.'' He furrowed his brow, seemed to master some complex emotion, and said, ``I know you're stressed, sweetheart, but can we talk?''

Sélène could barely move, and certainly couldn't speak. So calm was Aiden usually, that this reaction felt like an slap to the face. Almost literally: her cheeks were burning, and she could barely get any air. She nodded as best she could.

Aiden's shoulders sagged and his expression softened. ``Oh, love, I'm sorry. You look terrified.'' He frowned, ``And you're barely breathing. Come on, let's go sit on the couch, and we can talk.''

When Sélène didn't move, he gingerly took her by the elbow, guiding her over to her spot on the couch. Sélène sat on the edge of the cushions and set the container of leftovers on on the table by the couch. Her muscles felt tight and ready to launch; this wasn't just panic, it was an adrenaline spike that robbed her of thought, corrupted vision and hearing and touch.

Aiden sat in his spot and looked down at his paws thoughtfully. After a moment, he spoke. ``So, when we first started talking about this, we talked about sex right away, and I agreed that it'd be fine. We agreed, I mean.''

Sélène stared at her paws as well, watching her pick at that spot on her wrist. She kept her ears pinned back. ``I remember, yeah,'' she whispered.

``And I think--'' He cut himself off and appeared to be turning the rest of the sentence over in his head. ``I think I'm still okay with it.''

Sélène nodded. Unable to shift her gaze, she could only see her husband out of the corner of her eye. ``\,`But'?''

Aiden sighed. ``\,`But', yeah. But I'm a little upset over how soon it happened, I guess.''

``Second date?'' Sélène murmured.

``I guess. Or maybe it'd be more accurate for me to say that I'm upset over how easy it seems to have been.''

Sélène nodded. She kept watching herself pick and pick at that one spot. It seemed like it was happening to someone else. Or maybe that something was doing it to her, and she had no control over it. The madness rode her, and it hurt.

``We've not had the best of luck with sex,'' Aiden continued. ``And I'm okay with that, I really am. It's pretty far down on the list of things I need out of our relationship.''

A silence followed this (pick pick, each pick seemingly closer to excising some foreign object or dull-cornered sin), until Sélène nodded and said, ``But it is on there.''

``Yeah. It is on there.'' Aiden shifted on the couch, to face Sélène more directly (pick pick pick, each dig of her claws sending a bright spark of pain into her wrist, a magnesium flare to blind her). ``And we agreed that you liked Malina for different reasons than me, and that you still loved me. And I know it's not a race, but I feel left behind all the same.''

The last of Aiden's words came out in a rush, and Sélène could see his muzzle drop after he finished. The conversation seemed to be taking a toll on him. ``I'm sorry, Aiden--'' (pick pick, pick pick, almost there, almost to tearing loose whatever was under her skin, whatever taint of evil) ``I love you so much, and\ldots{}and--''

``Sweetheart-- oh jeez, hold on.'' Aiden scrambled up from the couch and dashed off to the kitchen.

Sélène sniffled, unable to see through the tears, but she heard Aiden trot back and felt the coarse texture of a paper towel press to her wrist.

``No.~Hold still, Sélène,'' Aiden mumbled, tightening his grip as she tried to tug her paw back. ``Here, wipe your other paw here--'' he guided her paw to one bit of towel then hander her a separate one. ``--and then you can wipe your face with this one.''

Sélène struggled to follow the directions, some remote part of her confused as to the sudden halt in the conversation. She fumbled with a a bit of paper towel Aiden put in her paw, lifting it to wipe at her eyes and nose.

``Oh, uh\ldots{}shit.'' She whined quietly, more tears immediately filling her eyes. ``I'm sorry, Aiden, I didn't mean\ldots{}I mean, are you alright?''

Aiden folded his long legs and sat cross-legged before her, pressing a paper towel, wet with blood, to the spot on Sélène's wrist. ``Hush, love, I'm alright. I know you didn't mean to.''

She held the paper towel to her face and stifled a sob, struggled to keep from totally breaking down. ``Im-important c-conversation and here I am making a mess.''

Aiden laughed. ``It's okay, sweetheart. Really. Lemme look.''

She wiped her face again as Aiden dabbed at the stinging spot on her wrist before peeking under the paper towel. ``Oh, that's not as bad as it looked. Must've just nicked something.''

Sélène struggled to smile at her husband. ``I'm sorry. Are you alright, Aiden?''

``Mmhm, I'm alright.''

``I'm sorry.'' Sélène pawed at her face again with the paper towel. She had been picking on her right paw, too --- she felt clumsy and awkward using the towel with her left. ``I promise I'm not, uh\ldots{}not trying to beg off.''

Aiden laughed. ``I know, sweetheart.''

``I, uh\ldots{}are you sure you're alright?''

``I am.'' Aiden leaned forward and brushed his cheek over her wrist, paper towel and all. ``Kiss to make it better.''

It was Sélène's turn to laugh, though it sounded strangled to her ears.

``I'm sorry things got stressful there, but--'' He shrugged. ``I don't know. I love you, Sélène, and I trust you through all this. I just got a bit upset, I suppose, because it felt like I wasn't getting all of you.''

Sélène nodded. ``I'm sorry, Aiden. If you want, we can try and do more.''

Aiden tilted his head. ``I won't say no to that, of course, but I don't want to push you. I know sex can make you feel gross.''

Wiping at her face, Sélène was a little surprised that she'd managed stopped crying. ``Yeah, I'm sorry,'' she mumbled. ``We can maybe work on that, though.''

``I'd like that, sweetheart.'' The fox bowed his head for a moment. ``Though I was also wondering if you had thoughts on if I branched out some, myself.''

Sélène sat up straighter, turning over the idea in her mind. She knew she could not, in any circumstances, get by without Aiden. And yet she made a less than idea partner in so many ways. Now, however, she was also getting help from Malina, so maybe she wouldn't need to lean so heavily on her husband for support. It only made sense.

It only made sense, that is, except for all of the ways it ground up against her problems with relationship-rightness.

For Aiden to be not getting all he needed from her made her feel like a failure. It was a horrific condemnation, and she could barely consider the full idea in her mind, only peek at it sidelong.

It made her feel monstrous and demanding, that she should seek love and support, and yet feel so bad letting Aiden do the same.

``Love?''

Sélène snapped to and shook her head to clear it. ``Sorry, Aiden. Are you\ldots{}uh, I mean, sorry.'' She closed her eyes and forced herself to collect her thoughts. ``What were you thinking?''

Aiden shrugged and peeked under the makeshift bandage. What he saw must have looked alright, as he nodded and wadded up the paper towel. ``I didn't have anything particularly in mind.''

Sélène looked down at her wrist. It didn't look bad at all, but she'd need to wash and bandage it proper so she wouldn't pick the scab, as she knew she would.

``Only, I've been talking with my coworker--''

``Aaron?'' Sélène blinked in surprise.

``Mmhm. He's the one I go get lunch with some days. I've been talking with him, and he says he and his wife do okay\ldots{}er, playing around with others to get what they need, and it got me thinking, is all.''

Confused as she was, Sélène had to smile. A bashful Aiden was a rare sight.

``I guess that's what I was thinking of. You mean the world to me, sweetheart, and I don't think I could manage a--'' He cut off, swallowed and shook his head. ``Another relationship. I'm happy for you and Malina, but I don't think I could do the same.''

This was a whole new take on it, then. Sélène struggled to make that fit in her picture of things, to see how life would be. Her and Aiden. Her and Malina. Aiden without anyone, but\ldots{}something. But having sex with friends? Swinging?

She laughed, and Aiden tilted his ears back. ``I'm sorry, Aiden. I just remembered the term `swinger' and laughed, is all.''

Aiden looked confused, then broke out in a grin. ``It is pretty ridiculous.''

``Is that sort of what you were thinking?''

He nodded. ``Not a relationship, but\ldots{}uh\ldots{}''

``Sex?'' Sélène immediately shook her head. ``That sounds bad, sorry. Um\ldots{}sexual fulfillment?''

Aiden nodded again, more emphatically. ``Yes! That's a good way to put it.''

Sélène shrugged and smiled. ``I can go along with that, I think. Maybe something to try out, like us trying with me and Malina?''

``I suppose, yeah.'' He frowned. ``Would you still be willing to work on our own sex life, too?''

``I would, yeah.''

``I would really like that, sweetheart. The playing around thing is one thing, but I don't really want to use it to\ldots{}I don't know. I don't want to use it instead of fixing our relationship''

Sélène winced and nodded. ``I really am sorry, Aiden. I didn't mean to. I didn't mean to hurt you.''

Aiden slipped his paws up into Sélène's. ``I know you didn't, sweetheart. You're right that it did-- that it does hurt, but I'm still not totally sure why. Maybe I just accepted things intellectually without understanding them. It's hard, Sélène.''

Clutching at her husband's paws helped keep Sélène from picking, so she held on, even if she felt a little gross with what blood was left in her fur. ``Hurting you is the last thing I want, Aiden.''

``I know, love. I trust you fully, in that.'' He gave a lopsided grin and added, ``I'm not actually sure you'd be able to lie or hurt me intentionally.''

Sélène giggled and shook her head, ``I have my tells, don't I?''

``Mmhm.''

``So,'' she sighed. ``I want to try and make things better. And I don't want to hurt you again.''

Aiden nodded. ``And I want to see you happy, too. I don't want you to stop seeing Malina or anything. I just--'' He toyed with her fingers for a moment before apparently finding the right words. ``I need to make this work in my head that you and Malina are more compatible than you and I, in some ways.''

Sélène splayed her ears. It wasn't really something she could argue against. Whether or not the sex had been a fluke, it was true on a very base level. If Aiden was her rock, the steadying force in her life that kept her going, Malina seemed to be her blanket, her pillow, her means to relax and rest from too much energy.

``What should I do?''

Her husband frowned, looking down to her paws rather than up to her face. ``That's a hard one, Sélène. I don't think either of us can make long term decisions with what little we know, now.''

She nodded and squeezed his fingers in hers.

When he did finally look up to her, the pain and anxiety in his face startled her. ``Can you give me some time though, sweetheart? It may not be fair of me to ask, but can you and Malina at least hold off on sex for a little bit? I'm trying, I'm--''

Unable to respond, Sélène slid off the couch and down onto her knees in front of where Aiden was sat on the floor. She tugged his paws toward her and guided his arms around her shoulders, before leaning in to hug around him in turn. The position was awkward and she felt surprisingly stiff from all the stress, but she wanted --- needed to be closer.

Aiden seemed to need the closeness as much as she did, as the hug he gave her was tight and shaky.

It took what felt like several minutes before Sélène was able to speak, and then only hoarsely. ``Oh, Aiden, of course, of course.''

Loosening his grip, Aiden rubbed his cheek against Sélène's firmly. ``I love you so much, sweetheart, and I want to be fair. I'm just having a hard time, is all.''

Sélène nodded, adding another cheek-rub as she did so. ``Do you want me to call things off with Malina?''

Aiden leaned back from the hug, letting Sélène sit back on the floor as well, though he kept her paws in his. ``No, sweetheart. Not at all. Just slow down a bit, for me. Let me get used to this.''

``Of course,'' she murmured. ``The last thing I want to do is to hurt you.''

``I know, love.'' He lifted her paws and brushed his cheek against them, then seemed to remember the wound on her wrist and smiled apologetically. ``Sorry. Are you alright?''

``It's alright. It stings, but isn't bad.'' She paused, then picked up the thread again. ``Still, do you want me to hold off on any more dates with her for a while, too? Would that help any?''

Aiden shook his head. ``No, that's alright. In fact, more would probably be better, so I can get used to things faster.''

He looked exhausted. \emph{She} was exhausted. Work, a date, sex, an argument, blood, love. Sélène felt like she lived in a soap opera. She winced as she struggled to stand, helping Aiden up shortly after. then it was time for a proper hug, with no leaning forward or awkward angles. Aiden really was her pillar, her anchor.

``Malina wanted to meet up Friday or Saturday, would you like me to cancel?''

Aiden was quiet for a few seconds, then he smiled and brushed his cheek against hers in another soft kiss. ``Do you think she'd like to have dinner over here?''

``The three of us?''

Aiden smiled and nodded. ``The three of us.''
