\hypertarget{centerpiece}{%
\chapter{Centerpiece}\label{centerpiece}}

``Hey E,'' Aaron mumbled, the cat nudging the turn signal lever up to make his way toward the right lane.

``Mm?'' Erin peeked up from her book to see how far they'd made it into their journey. Still about twenty minutes. She lowered her gaze once again.

``Put any more thought into the idea of a donor?''

Slinking lower into the passenger seat, Erin gave a half-hearted shrug. ``Not really any more than before. Just want someone we know already and who we trust. Don't want to go to a bank.''

Aaron nodded and settled back into his seat as they made their way onto the highway. ``Anyone you can think of, minkypie?''

Erin caught herself about to shrug again and shook her head instead, ``Only really know a few other minks out there---the Redstones from work, and there's that Matthew guy from your office\ldots{}Matthew Lederer, was it?---and I don't know if they swing or not. Come on, though,'' she laughed. ``Figure out something sexier to talk about. We're supposed to be getting psyched for a night of debauchery, not figuring out sperm donor paperwork.''

Erin and Aaron had been one of those couples that had been insufferably cute when dating. When they'd been friends, they'd been teased about it enough, but when it turned to romance, it all seemed a bit much.

It was the names that got most people, of course. They'd react in a few very predictable ways when they found out that the couple had homophonic names. Most folks would gush over how adorable it was, asking how they referred to each other when alone, what they'd name their children if they could have any, and so on, The rest seemed to fall into two camps: those that would ask, ``doesn't that get confusing or weird in conversations?'' and those that would make some lewd comment about sex, whether referring to threesomes or whether they'd ever played with another Aaron or Erin or something like that

The answers were all fairly straight forward, too, especially after several years of being asked the same questions. They would say that they called each other by their names like regular folks; they'd joke that if they had kids, they'd name them Erin and Aaron; they'd say that conversations were made easier when eye contact signaled which individual was being talked to; they'd say their sex life was private but give a wink.

Below the surface, though, were the more intimate truths. In private, they really only used each other's first initials, going by E and A respectively. They'd done the threesome thing quite a bit, actually, and even once with another Erin, it had been really rather nice, and they were looking forward to seeing her again tonight. And perhaps the most intimate truth was just how sore a subject parenthood was for the two of them, how much being an interspecies couple got in the way.

Aaron laughed and nodded. ``Alright, alright,'' he said. ``You looking forward to being a useful mink tonight, then?''

Despite all the planning and negotiation that had gone into tonight, despite all the times she'd heard it before, being called a `useful mink' right before the first night in far too long where she really would be useful had Erin squirming in her seat, ears pinned back against her head.

The cat in the the driver's seat laughed, ``I'll take that as a yes, then. Tell me what you're looking forward to most, then.''

``Being\ldots{}being useful.''

``Mm, so it's more the serving others than the bondage?''

Erin felt her tail start to frizz out, something she could never seem to help when agitated. A fact that Aaron was always keen to exploit. ``Mmhm\ldots{}mink wants to be useful more than anything.''

``More than anything?'' Aaron asked, risking a glance away from the road to grin at his wife. ``More than the pleasure of the act, you just want others to use you to feel good?''

If his goal had been to make her flustered, Aaron was succeeding. If it had been to get her more worked up, it was also very, very much succeeding. ``Yeah,'' she began, voice thick with embarrassment. ``Yeah, I want\ldots{}I want people to come away feeling fulfilled, I want to be a tool to help them feel that way.'' The mink thought for a moment longer before adding, ``The sex is good too, you know I'll enjoy that, but being useful is what I want.''

Aaron nodded. ``Not to drag us back to where we were, but is that part of why you want to be a mother so badly?''

``Mmhm, at least a little part of it. It feels like the strongest, highest, and, well, purest form of being useful.''

``Well, that makes sense,'' Aaron said with a chuckle. ``So\ldots{}''

``\,`So\ldots{}' what?'' Erin sat up within her seat. ``What are you planning?''

``Nothing, nothing!'' Unable to lift his paws from the steering wheel, the cat did his best to imply a disarming gesture with his shoulders. ``Only, I was wondering, what if you got to be useful at a party like this one, and that led to a child?''

The mink in the passenger seat sat, mouth open, for a moment before finding the words to respond, ``You\ldots{}you're sure you're not planning anything?''

``Promise. No plans, or we'd be negotiating a hell of a lot harder.''

``Well, I\ldots{}I don't know.'' Erin realized that she was fiddling too much with her book, bending the pages, so she set her bookmark in place and slipped the paperback into her bag. ``It would be a lot to process. But I'm pretty sure all of it would be good.''

Aaron grinned toward the road, making his way over to the rightmost lane once more---they were just about to the end of the freeway stint of the trip, Erin guessed, so probably just a few minutes left. ``Well, alright then. So if we wind up at a party like this and there just happens to be another mink there-''

Erin cut him off with a quiet whine, her tail bristled from base to tip and swishing against the back of the seat. ``A! Come \emph{on}!''

The cat's grin turned to a laugh. ``What do you mean, `come on'? You'd love it, you said so. You'd love to be a Centerpiece and come away with motherhood, I know you would! And you know I'm game, too.''

Brushing furiously at her tail in an attempt to soothe her nerves, Erin let a stony silence fall, fighting to sort out a turbulent mixture of embarrassment, arousal, and that longing she'd always associated with her drive towards motherhood, biological imperative and otherwise.

Erin's silence and Aaron's grin lasted the next few minutes until they parked at the curb before a squat, suburban ranch house.

Aaron turned off the car and tugged up the parking break, leaning over to kiss his wife on the cheek, ``Sorry if that was too far, E.''

When Erin didn't respond, he reached for her paw, twining fingers with her. Looking back up to her face, he was surprised to see a bashful smile there.

``No, was just thinking,'' she murmured. ``I \emph{would} love that.''

The cat's grin snapped back into place almost immediately, along with the start of a quiet purr. He leaned over to give another quick kiss before slipping his paw away and swinging wide the driver's side door. ``Come on, then, grab the bin and let's get inside, catch up with folks.''

\secdiv{}

\noindent Those who travel among the play parties, orgies, and swing groups often think of themselves as being sexually liberated.

However, they'll all be the first to admit that the time before the play party begins can be the most awkward part. Milling around with a plastic cup of too-sweet spiked punch in one paw and a little plate of store-bought cookies in the other sometimes made it feel a little too much like a social function put on by a group of employees.

The hosts of this party, another couple that Erin and Aaron had known for a few years now, two ferrets named Elise and Joan, had set up a few things to help alleviate that feeling, though there's not much that could make it go away entirely. For every bowl of chips or plate of cookies, there was a bowl of condoms (with several different sizes present) or lube packets (silicone or water based). The cooler of drinks, normally holding just beers and sodas, also contained a few drinks made from stronger things. Small, printed signs listed the rules (play safe, wear clothes outside, and so on) near every doorway. The plans for segueing from ``party'' to ``play'' involved strip poker.

Despite all of the effort, there was still some difficulty in loosening up. This was due in no small part, Erin suspected, to anticipation for later. Even the most sexually liberated could be in the time leading up to sex.

Thankfully, as Centerpiece, she had little to worry about, in that sense. For her, the start and end to the night were clearly delineated. No strip poker for her. It would start when she was bound, gagged, and blindfolded, and it would end when she tapped out or was set loose, whichever came first. That would come soon, and the gear was all in the bin that Aaron had dragged in and set in the living room next to the neatly decked mattress that would be her spot for the night.

``First things first,'' Aaron said, once Erin had gotten a drink. ``Lift your chin.''

Erin did as she was told, letting her husband deftly swing a collar up around her neck and fasten it in front. Although she couldn't see the collar, she knew what it looked like---black nylon webbing with some yellow nylon woven into it to spell `TOY' along the back and a tag saying the same in front. Feeling the weight of it around her neck, the slight constriction of her fur beneath it, Erin tensed up and swished about, her short, rounded ears canted back.

``Finish your drink, minkytoy,'' Aaron continued, waiting for the mink to down the rest of her soda before clipping a leash to the D-ring at her throat.

When the cat gave an experimental tug, Erin felt herself jerked forward an inch or two by the collar at back of her neck. Beyond that, though, she felt that latent arousal that had been dwelling within her the last few days finally begin to assert its presence, felt sub-space start to surround her like a warm blanket.

Her husband grinned at the obvious change and leaned in close enough to whisper to her, ``Mm, cozy there, pet?''

Ears pinned back, Erin gave a bashful nod.

``Going to be a good pet tonight?''

Nod.

``Still comfortable with this?''

Another nod, more vigorous this time.

``Going to be useful for everyone tonight, no matter what?''

Erin let out a low mewl, tucking her muzzle down toward her chest and hunching her shoulders as though she could hide her embarrassment that way. ``Yes owner,'' she murmured, tail lashing this way and that. ``Will be useful.''

Aaron grinned haughtily and wound the leash around one of his paws a few times, giving another little tug to help reinforce his position over her. ``Good mink. Let's go see who you're going to be useful for, then.''

Erin felt like they into a feedback loop of power dynamics. The more dominant that Aaron got in showing her off to the party's other attendees, the more submissive she felt. The more submissive she acted, the more that seemed to egg Aaron on. Before long, he was encouraging her to spin and show off, to curtsy, to make small confessions to the other attendees.

This was one of the other things that Elise and Joan did to loosen up their guests. Each party---and there were several a year---included one guest who would be the Centerpiece. The Centerpiece had become a coveted role in the circles that attended this party, one that had to be applied for ahead of time.

And it was indeed a role to play. The Centerpiece was the one who had to start moving the atmosphere from party to play while the two ferrets tended to more mundane things such as maintaining snack levels and ensuring that the rules were followed. Once the atmosphere had shifted, the Centerpiece (almost always a known sub, but once or twice, a more dominant figure had surprised the group by serving) was to become literally that: a fixture at the center of the party, immobile. A figure to be discussed or a toy to be used in a public fashion.

Although this was Erin's first time being the Centerpiece, the role fit her naturally. Elise had leaped at the chance to feature the mink for the party. To have a willing critter who was already a well-known sub (and already quite knowledgeable in bondage) made the hostesses' jobs easier and the party more fun.

By the time they had made the rounds of the patio, Erin knew that she had done well. The timbre of the party had shifted according to plan, the curtains had been drawn, and the game of strip poker had already begun in the den. The mink was buzzing with a mixture of arousal and pleasurable embarrassment, along with a base note of that nearly primal need to please.

Which is precisely when her smirking owner and husband tugged on her leash to get her to look up, saying, ``And this is Matthew. Matthew Lederer. I believe you've met.''

Erin found her gaze sliding up along the slinky form before her, hidden by a half-unbuttoned dress shirt, to the soft features of the other mink. He was sleek and well groomed, whiskers bristled as if caught in the middle of searching for an intriguing scent. As everything from the earlier conversations clicked into place, she found herself tense at the end of the leash.

Another mink.

And here she was, smelling of arousal and desire: the Centerpiece, the offering to the party.

Matthew's mind seemed to be going through some similar calculation, as his gaze shifted from shock through bemusement to hunger, grinning at the slender mink-toy being presented to him by the cat, giving an appraising glance over the rims of his glasses.

Erin watched him turn to face her husband, ``Good to see you here, buddy! And yeah, I believe we have.'' That grin widened, showing the mink's pointed teeth. ``Wasn't expecting to be so lucky in my choice of toys for tonight.''

Looking positively smug, Aaron tapped the tip of his wife's nose with the end of the leash, nodding. ``Mmhm. Was my turn to bring the Centerpiece. Just about to go get her all trussed up. But here, stand up straighter, minkytoy.''

Able only to muster a soft mewl, Erin nodded and stood up straighter, her tail flitting about erratically.

``The Centerpiece should greet all her guests while she still can. Go on.''

Erin nodded and leaned in to give the other mink an embrace and a whiskery, bashful kiss to the side of his muzzle. ``W-welcome\ldots{}''

Matthew returned the kiss with a grin, seeming to pick up on some of Aaron's bravado. ``Thank you, ah\ldots{}'' he reached a paw up to lift the tag on the smaller mink's collar to read it. ``Thank you, toy. I'm sure I'll be most welcome indeed.''

\secdiv{}

\noindent ``I thought you said you didn't have anything planned,'' Erin said, still shivering from the mix of humiliation and arousal as she tugged her shirt off.

Aaron, already nude, looked up from where he had been rooting in the bin of bondage gear, ``I didn't, E, I promise. I didn't even know he was coming until he showed up just then.''

Erin nodded, anxious. She slipped shyly out of the last of her clothes and knelt, nude, on the mattress.

``Do you want me to call in Elise? We can tap out, if it's uncomfortable, or Elise can ask him to not interact with you as the Centerpiece.''

The mink felt herself flush beneath her fur, whiskers bristling. ``Mmnf\ldots{}'' she managed, then, ``N-no. I mean, now I'm all curious. I've\ldots{}never been with another mink before, after all.''

Aaron grinned and sat down on the edge of the mattress, holding a pair of soft, locking bondage cuffs and a snap hook connector---two lobster clasps joined by a strip of nylon with a D-ring situated in the middle---for binding them together. ``Oh, so you're eager, then, toy?''

Erin squirmed at the pet name. She hadn't quite left sub-space, hadn't wanted to, and so the words played readily into that. ``I\ldots{}maybe,'' she admitted, squirming tensely.

The cat's grin widened as he turned and crawled over the mattress to her, muzzle tucking in against her cheek, his paws working to fasten one of the locking cuffs around her wrist. ``Toy sure \emph{smells} eager,'' he breathed.

Tilting her cheek to her owner's muzzle and lifting both of her paws to offer her wrists to him, Erin whined quietly in return. ``Can't help it,'' she mumbled, her breathing picking up.

``I imagine not.'' Aaron continued slipping the other cuff onto the mink's other wrist, making a show of checking the locked status of each before attaching the connector to the exposed D-rings of the cuffs, effectively locking Erin's paws together. Although cuffs were a common accessory for her, she always got a thrill out of having them put on by someone else.

``Hopefully not too obvious?'' she asked.

``This is a play party, E, it's kind of expected,'' Aaron said. The cat's laugh made Erin lay her ears all the way back. He tugged on the strap connecting her cuffs together pulling her up onto her knees and then onto all fours, his paw pinning the snap connector to the mattress. The laugh turned into a low growl as Aaron murmured, ``And besides, toy, everyone noticed.'' With a soft nip to her ear, he lowered his voice further to a soft purr, adding, ``Everyone.''

Any distance Erin had managed to gain from the sexual dynamic to ask about plans was quickly obliterated with the firm treatment and teasing words. She quickly found herself back in that cozy submissive space, her paws clutching at the sheets of the mattress, held only as far apart as the cuffs would let them. ``Was toy useful?''

Dragging the tote of gear closer, Aaron nodded, his voice muffled slightly by the fact that he couldn't hold back a purr. ``Very useful. You got everyone up and moving. Lots of needy looks when we left to get ready.'' The cat brought up another snap connector and with an insistent push, nudged Erin's shoulders down until her chin nearly touched her paws, clipping this connector between the D-ring on her collar and the one on the first snap connector, leaving the mink with her backside hiked up and exposed. ``But you're only just getting started, minkytoy. You're going to be very, very useful by night's end, aren't you?''

Erin nodded, her breathing quick and shallow in anticipation. She could smell her own arousal quite strongly, now, as well as that of Aaron, a scent she was well accustomed to. ``Yes owner,'' she panted, breaths tinged with a whine.

There was a bit more fumbling in the bin before Aaron lay a few more items out in front of her, close enough to see but not touch. A ring-gag. A blindfold. A small remote control type device. A bowl of condoms. Two laminated signs---one with rules, the other with a space for tallying just how the mink had been useful. A marker to go with the signs.

Kneeling before her, Aaron took the blindfold in one paw and the gag in the other and leaned in closer. The familiar scent of the cat's arousal was filling Erin's nostrils, his stiff shaft dead center in her gaze, but, again, just out of reach. The scent of him was overpowering the scent of herself, but she could feel that burning arousal in her belly, feel the cool air against her groin, caressing warm and slick flesh.

``Even that mink? Matthew?'' the cat asked. It was hard for Erin to pick apart whether her owner was purring or growling, or perhaps a little bit of both. ``Are you going to be a useful toy for him, too?''

Erin felt her fur bristle, that perennial reaction to humiliation no longer restricted to just her tail, but creeping up her spine to her neck and ears, heckles raising. ``I will,'' she whimpered. ``I'll be usef-\emph{nngh!}''

She was cut off quickly. She'd been so focused on Aaron's words and the sight of his arousal in the center of her tunnel-vision that she hadn't noticed the paw with the ring gag.

With one deft movement, the cat had taken advantage of her open muzzle to slip the gag in place, wedging her muzzle open with the ring of stiff rubber. His fingers quickly traced the straps of the gag to their ends, Velcro straps that looped around her collar to hold the gag in place.

``I know you will, toy,'' the cat growled---and it definitely was a growl this time. A commanding, possessive, domineering growl that ensured she knew her place.

Erin could only whine and pant, huff and whimper. She nodded shakily, as much as the straps restraining her neck to her wrists would allow.

Those teasing growls continued as Aaron set up, clearly leaving the blindfold in his paw until last so that she would be forced to watch. ``I wonder if toy will be able to tell it's him,'' he said. ``By shape or by noise. Or maybe he'll lean forward and whisper to you how he's taking you. Maybe he'll just scruff the toy. I bet his teeth are sharp.''

Whimper, pant, squirm. Erin couldn't manage a whole lot more, as she watched her owner set up the signs. ``Please use condoms; no damage; Centerpiece will use buzzer to tap out'' read one. ``Cum count: In sex---In muzzle---In fur'' read the other, the pen laid neatly at its base.

``Maybe it'll trigger something in you,'' Aaron said. He picked up the remote control and gave its single button a quick press, the small box emitting a surprisingly loud buzzing noise, annoying by design. Slipping the buzzer into Erin's paw, he leaned in closer to continue, ``Maybe your body will know him by his species. Maybe you'll know what it is that you're missing out by him using a condom with you, by being that close to having his kits.''

A more drawn-out whine this time, low and needy, as her owner sought out and tickled each and every one of her kinks in turn.

She was gone. Totally lost in sub-space. And he was driving her deeper and deeper.

``Press the button, toy.''

Shaking, Erin fumbled with the remote, getting the button aligned under her thumb before pressing it. She got a loud buzz in response.

``Good. Don't forget that, toy.'' Aaron grinned and reached once more into the tote of gear. ``I'll watch when I can, but I have my own fun planned tonight.''

With that, Erin watched as the cat stood, making as if to open the door for everyone, letting the play of the Centerpiece begin, still murmuring, ``Maybe toy will find herself needing him, hmm? Craving that mink within her, fitting so nicely like only another mink can. Maybe some day you \emph{will} wind up with his kits.''

The cat paused and turned back, looking as if he'd just remembered something. Erin noticed the blindfold left in his paw and squirmed against the bed, knowing that the sensory deprivation would only serve to drive her deeper into Useful Mink territory.

Aaron knelt before her once more and lifted the blindfold, then set it to the side and instead lifted his other paw. In it was a safety pin, something from the emergency sewing kit in the gear tote. Holding his paws deliberately within her gaze, Aaron opened the safety pin, exposing the sharp point. With his free paw, he reached down to grab one of the wrapped condoms from the bowl.

``And who knows,'' he said, grinning widely as he drove the point of the pin through the package, the condom inside, and clear through out the other side of the package. ``Maybe he'll get this one.''

The condom dangled briefly from the safety pin directly before Erin's eyes. She watched, unable to speak even if she hadn't been gagged, as the cat slid the needle-thin pin from the condom and massaged it with his finger-pads, leaving it looking intact and unmolested. He then tossed it almost casually into the bowl of condoms, mixing them up lazily with his paw. Aaron closed the safety pin and dropped it back into the tote with a small rattle.

Realizing that she had been holding her breath, Erin let out a gasp and a shaky moan before swallowing dryly, making a soft \emph{glk} noise with the gag in the way. She could feel Aaron hesitating, watching her for any sign that she would need to back out.

Her mind was reeling, her breath coming in ragged pants, her arousal out of control, her body coursing with what felt like electricity. But she gave a slight nod of consent.

Her last sight was of Aaron grinning as he reached down to fasten the blindfold over her eyes, clipping that, too, to the collar so that it couldn't easily be removed. Sight gone, she could only rely on touch, scent, taste, sound.

The rustle of Aaron standing, the feel of the mattress shifting beneath her.

``Remember your buzzer, toy.''

Footsteps.

The scent of her owner's arousal fading, the scent of her own taking over.

The sound of the door.

Traces of other scents, other people, other species, other arousals.

Voices, soft applause.

And Aaron's voice, ``The Centerpiece is ready.''
