\subsection*{I}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:} \\
      Unnerving

      \textit{Expect:}\\
      anxiety
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      A hundred geese overhead --- \\
      \vin A thousand --- \\
      \vin \vin A million ---
    \end{verse}
    % parcolumns treats verse weird. This is the best way to get a linebreak in the middle of the verse
    \begin{verse}
      Heady scent of premonition. \\
      Acrid tang of ill omens. \\
      Portents.\\
      Too much meaning \\
      \vin In too small a space.
    \end{verse}
  }
\end{parcolumns}

\subsection*{II}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:} \\
      Noise-Cancelling Headphones

      \textit{Expect:}\\
      auditory aberrations
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      Geese are a byproduct of laminar shear stress \\
      \vin Of two layers of phantasmagorical\\
      \vin \vin Newtonian fluids, \\
      \vin Which is why they’re often seen on a plane. \\
      A thin, sort-of Truth \\
      \vin From a sort of thin layer \\
      \vin \vin geese chromatography.
    \end{verse}
  }
\end{parcolumns}

\newpage

\subsection*{III}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Eldrich

      \textit{Expect:}\\
      red tint to vision; hot flashes
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      As the dove bears the olive branch, \\
      \vin so to the goose bears the wand \\
      \vin \vin that withers all it touches. \\
      A wand of nightshade, \\
      \vin Core of tainted silver. \\
      A wand of obscure origin, \\
      \vin The goose surely stole it. \\
      Malice begets malice.
    \end{verse}
  }
\end{parcolumns}

\subsection*{IV}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Beyond Comprehension

      \textit{Expect:}\\
      confusion; nausea; sweating; racing pulse
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      We know not the transgression, \\
      \vin the origin - \\
      We know not the punishment, \\
      \vin only the terror.
    \end{verse}
  }
\end{parcolumns}

\subsection*{V}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Excruciating

      \textit{Expect:}\\
      pounding heart; tunnel vision; racing thoughts; black outs; blood pouring from ears
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      Geas \\
      \vin Wing \\
      \vin \vin Dark \\
      \vin \vin \vin Horizon
    \end{verse}
  }
\end{parcolumns}

\subsection*{VI}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Terrifying

      \textit{Expect:}\\
      tinnitus; piloerection; shortness of breath; uneven gait
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      I'd rather owls.\\
      Owls, as though geese were turned inside out,\\
      \vin made less evil.\\
      Still portentous,\\
      \vin Still momentous,\\
      \vin Just less terrifying.\\
      Owls are okay.\\
      I can think about owls.\\
    \end{verse}
  }
\end{parcolumns}

\subsection*{VII}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Uncomfortable

      \textit{Expect:}\\
      subdermal itching; formication
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      Life within a comfortable grid.\\
      Parallel lines\\
      \vin Interrupting narrowing circles\\
      \vin Of birds in flight.\\
      Travel in straight lines.\\
      Turn at right angles.\\
      Trace the roof of your mouth\\
      \vin With wet tongue.
    \end{verse}
    \begin{verse}
      I’m not afraid of geese anymore\\
      \vin Because I can step on them now.\\
      I’m big enough.
    \end{verse}
  }
\end{parcolumns}

\newpage

\subsection*{VIII}
\begin{parcolumns}[colwidths={1=0.3\textwidth}]{2}
  \colchunk{
    \begin{flushright}
      \textit{Geese Level:}\\
      Birds

      \textit{Expect:}\\
      birds
    \end{flushright}
  }
  \colchunk{
    \begin{verse}
      Ritual thinking\\
      \vin Driven by geese ---\\
      \vin By lines, by grids, by food ---\\
      \vin By numbers and neat delineation.\\
      And I'm left with questions:\\
      \vin Why are they so portentous?\\
      \vin Why the anxiety?\\
      Or maybe:\\
      \vin Did I take my meds this morning?
    \end{verse}
    \begin{verse}
      Failing that,\\
      \vin Can I just have the comfort of prayer\\
      \vin Or the ecstasy of signs\\
      \vin \vin Without the bleak paranoia\\
      \vin \vin Over circling birds?
    \end{verse}
  }
\end{parcolumns}
