\chapter{How Many?}

``Oh for pete's sake, quit fretting,'' Andrew chided, bumping his elbow against Ian's as they crowded into the too-narrow seats. Neither of them were all that skinny anymore, and Andrew was bordering on fat, to Ian's stocky.

Ian closed his eyes and gritted his teeth, focusing on wedging himself in between the window and his boyfriend, counting up slowly through the numbers as he absentmindedly slipped the buckle around his waist.

``Sorry, Ian. I know it's probably harder for you than for me. Like\ldots{}twice as hard, or was it three times\ldots{}'' Andrew continued, a slight smile twisting the corners of his mouth.

Ian had to smile as well, caving to his partner's wiles and leaning over to place a kiss on his cheek. ``I'm just happy you're coming with, really. I can't promise I won't be freaking the whole time, but at least there will be wolves to come back to in the evenings.''

Andrew grinned, ``Damn right there will! No gallivanting off with weasels for me. Just sitting in the room, twiddling my thumbs, waitin-''

Ian kicked Andrew's foot under the airline seats before settling down against the side of the wall of the plane. ``You get plenty of fox time, don't you worry. Rei's there with his whole group of friends. I'm not going to leave you hanging or anything.''

``I know, I know. You've told me a few times. I swear you have all your bases covered, just relax and promise me you'll have a good time.''

``I'll\ldots{}I'll try. I promise I'll try.''

Ian jumped as there came a steady, barking sound beneath their feet, clutching earnestly at the arm rests as though he might actually leap to his feet, though the plane was taxiing steadily to the runway.

``Hey, hush,'' Andrew soothed. ``Don't worry, it's a normal sound. Just\ldots{}just make sure you count, and you'll be fine, promise.''

Ian nodded. He edged his hands from where they were grabbing at the seat to mock stretch, feeling the sweat coating his palms. Dragging his palms along his jeans from knees to waist, he did his best to calm down and simply let his hands rest, adopting the attitude of someone who wasn't terrified of what was to come, as if that would keep him calm.

It didn't.

Once the engines started to spin up, Ian went rigid, his whole body tensing from head to foot. He deliberately edged his hands back to the armrests, only to find his right hand intercepted by Andrews. Holding gratefully onto both his boyfriend and the plane, he closed his eyes and began counting.

``One, two, three,'' he mouthed silently, tracing the outline of each number in his mind as he counted up. ``Four, five\ldots{}'' The plane began to shake, his eyes went from merely closed to clenched shut. ``Six, seven, eight, nine,'' he continued, feeling himself sink back into his seat with the acceleration, feeling Andrew's hand getting coated with the sweat from his own. ``Ten\ldots{}eleven\ldots{}''

``Keep counting,'' Andrew urged quietly, leaning his bulk toward Ian so that the other could feel the comforting touch all the way from fingertips up to shoulder.

Ian's lips stopped moving, but he kept up the ritual in his head, tracing the numbers, drawing them with a saturated brush on imaginary paper in his mind, from eleven on up. By the time he reached seventy, the plane had gone airborne and made its first little dip after takeoff. By the time he reached one hundred, they were climbing steadily out of Portland International, and he felt more settled than he had during take-off. Just to be sure, however, he began counting once again, starting over at one. It was one of the rules: never count above one hundred.

Andrew, well accustomed to the ritual, relaxed his grip on Ian's hand when he felt him settle down next to him. He knew how much internal strife the anxiety caused, and he knew that it had a half life, decaying exponentially into the ground state, something just slightly more anxious than what he supposed he would consider his own `normal'. Being a hand to grab as needed was one of the roles he played.

\secdiv{}

It took seventeen counts of one-hundred to make it through the flight. The nice part about flying, Ian knew, is that by the time one was at cruising altitude, the plane seemed to morph from a trap into simply a cramped, tube-shaped room. The view out the window turned from horrifying evidence of their speed to something like a tapestry being drawn slowly beneath him. At that point, height seemed to matter less because it was outside his brain's ability to grasp.

The counting came up primarily during take-off, landing, and any turbulence -- twice there -- as well as the stolid progress of the flight attendants down the aisle-way. They were seated just aft of the wings on this flight, which afforded Ian plenty of time to watch the cart of drinks make its way row by row down the aisle, and he found himself counting -- twice again -- out of habit as he fretted about what to order to drink, knowing that he'd fail to be understood when the time came.

``Rum-and-coke,'' he answered, well rehearsed, when the attendant finally made it to him. There was no fall, no muttering or mumbling, nothing exploded, just a quiet response.

The flight attendant accepted his card as he reached past Andrew, knowing that the alcohol would likely calm him in the short term at the expense of the long term.

Andrew knew this too, and murmured to him as his plastic tumbler of ice was prepped, ``You sure, hon? I suppose we land late enough we can take it easy\ldots{}''

``Or stop and get another drink before dinner,'' Ian joked, accepting the cup, can, and tiny bottle of rum.

Andrew thought for a minute, then shrugged, ``We probably could, at that. Vacation Rules.''

Vacation Rules meant different things to Andrew than it did to Ian. For Andrew, it meant a relaxation of the stringent ways in which he kept himself, letting the excess that had led to his belly creep into other areas of his life. For Ian, it was another ritual in and of itself, a way to follow up ever action one took with ``but we're on vacation'' as a means of alleviating the inner tension that went along with his anxiety.

This particular vacation had come with all sorts of extra rules for both of them. Andrew and Ian had made it to plenty of different conventions in the past, both together and separate, but this was the first time both would be going to the same convention with Rei also there. They'd talked through the procedures involved in visiting a shared third partner plenty of times in the past, but only in the last few months had it involved a third partner involved only with one of the two.

It's not that Rei and Andrew didn't get along. They got along fine. They just never seemed to connect on the same level that Rei and Ian had, and they both had seemed happy with that.

Even as Ian counted his way through the plane's choppy descent into Colorado, he felt giddy, as well as nervous. Going through the process of getting close with Andrew, going through the outings-with-friends that slowly turned into dates, had felt natural, but this was something wholly different.

He was going to a Convention! To go on a Date! With someone he \emph{Liked}!

It was all so explicit.

He had only made it up to about thirty-eight or so by the time the plane touched down once more, and was still gripping Andrew's hand in his own. He couldn't stop now, though, so even though Andrew turned to face him, he held up a hand to signal the wait as he made his way through the rest of the numbers before finally settling back into his seat, turning to smile sheepishly at his boyfriend.

``So, um\ldots{}about that second drink?''

\secdiv{}

The couple managed to make it all the way to the hotel without stopping, despite the rising panic on Ian's part, checking his pockets repeatedly to make sure that he hadn't misplaced his phone, wallet, or keys -- the all-important keys with their little vial of emergency pills. No matter how thoroughly he convinced himself that he had everything that he needed, the results would slowly fade into is-it-a-dream-land, and he'd begin questioning his judgement again.

He kept his mouth shut, though, and mostly just clutched at Andrew's hand, letting himself be led to the shuttle, to the hotel, to the front desk, to their room, before finally letting his guard down.

``Hey,'' Andrew said quietly, resting his hands on Ian's slumped shoulders and guiding him into a hug. ``We made it. We don't have to do anything else tonight, except maybe get that drink. That sound good?''

Ian leaned tiredly into the hug, slipping his arms around his boyfriend's waist and holding himself close for a moment, just nodding.

``Need a shower or anything?'' Ian asked after a moment.

Andrew shook his head.

Ian nodded and pulled out his phone, quelling the feeling of being sweaty, being caked with sweat, being coated with grime, dirt and grease, grease so thick it showed through his clothes, enveloped them, darkened and then made them translucent, coating him in-

``Ready hon?''

Ian nodded, relaxing his grip on his phone long enough to text Rei to tell him where they would be before stuffing the phone into his pocket. ``Yep, let's go,'' he chirped, striding to the door before another cycle had the chance to start up.

They made their way down the hallway to the stairs, thankful for the low floor as the elevators were already starting to back up with fur-clad congoers. Elevators were usually okay for Ian, except late at night, and except for glass elevators. Since there would doubtless be late nights at the con and since this hotel had glass-walled elevators overlooking an atrium, they'd specifically requested a lower floor when booking, and had been pleasantly surprised by a room on the second floor.

As they trooped tiredly down the stairs, Ian thought for a moment before pulling out his keys and unscrewing the vial containing his medications.

``Think you'll need that?'' Andrew asked.

``Think I already do.''

Andrew nodded a little and continued on to the landing before pausing to let Ian catch up.

He carefully split one of the small tablets in half and placed one of the halves beneath his tongue, the learned reaction to the taste bringing an almost immediate sense of calm, however superficial.

``Gonna be okay taking that with a drink?''

``I should be, yeah,'' Ian responded. ``If anything, it'll just make me sleepy, and sleepy is an okay way to be.''

Andrew brushed his hand down over Ian's back and nodded, ``Well, just keep an eye on yourself. Yap if you need anything.''

``Yap!'' Ian grinned. ``Like that?''

He followed Andrew down the rest of the steps, yapping as he planted his foot on each one. The meds hadn't even started to kick in yet, but he knew they would, and knowing that was enough to lift his spirits to the point where he was actually looking forward to the bar, to seeing Rei.

Rei was shockingly easy to spot at the bar. He wasn't remarkable in his build, but having bleach-blond hair made him stick out in a sea of dark.

``There he is. There he is!'' Ian exclaimed and bounded ahead of Andrew. He took the steps up to the bar -- a group of two and a group of three separated by a small landing (five was a perfectly acceptable number) -- and called out, ``Rei!''

The man with the blond hair shot upright and pocketed his phone quickly. ``Ast! Is that you?'' he asked, meeting Ian -- or Ast, as he knew him -- in a quick, firm hug. ``Jeez, it's good to see you!''

The two regrouped into a more comfortable, less hasty hug, leaning in against each other and simply spending a moment holding tight. The sound of a shutter clicking brought Ian back to attention and he turned his head quickly to see Andrew grinning from behind his phone, holding it up to take another picture.

``H-hey!'' Ian stammered.

Rei laughed and grinned, ``You must be Andrew. Gonna have to send me those pictures.''

Ian felt himself flush, biting back a stinging retort and simply tucking his head back over Rei's shoulder, thankful that they were about the same height. He focused instead on counting. He didn't need a hundred, but he made sure to hold the hug until fifteen. Three and five were particularly auspicious.

Slipping away from Rei, Ian gestured to Andrew, ``Um, let me formally introduce you two. Andrew, Rei. Rei, this is Andrew.''

They shook hands, then seemed to think better of it and hugged before settling into stools around the bar table, Andrew picking up where Ian left off. ``Ast's told me a lot about you, too. Good to finally put a face behind the name. And hey, I like your hair.''

``Hah, thanks. Yeah, it feels like I already kind of know you.'' Rei said, rubbing at the back of his neck. ``I uh\ldots{}I hope it isn't too weird meeting up with your boyfriend's partner. I don't want to\ldots{}like, impose or anything.''

Andrew shook his head and put his hands up disarmingly. ``No, trust me, it's fine. We've had this talk so many times just between the two of us, it's good to put it into practice.''

The tinkling of glasses breaking behind the group drew their attention, and they turned to see a young woman in paws and a tail rush to clean up a small flood of drink from the table. Ian saw her cut herself on a piece of broken glass, feeling the glass slice into his own flesh within his mind, and winced, swiveling back to face his own table, clasping his hands together in front of himself to keep himself from forcing both Andrew and Rei to turn away, second-hand embarrassment running deep.

Ian had realized how close he was to panicking and had taken the brief, calm interaction between his two partners to clutch at the edge of the table for dear life and work on calming himself. Breathe, slow, calm, chill, breathe. Simple one-syllable words said in order to restore a sense of balance within himself. Finally, he stood, paced in a quick circle behind his chair and shook his hands to dry the sweat from his palms, before settling back onto the stool and grinning sheepishly at Andrew and Rei.

``Sorry,'' he said breathlessly. ``I'm really excited. Um\ldots{}hi!''

Rei looked a touch taken aback, but Andrew laughed. ``Long flight, we're both a little on edge. Seen the waitress around here? I think a drink might do all of us good.''

Rei smiled warily, but nodded to someone behind Andrew, catching the eye of the server.

``Help you gents?'' the man asked, whisking a cocktail napkin down in front of each of them with practiced ease.

``What beers do you have?'' Andrew asked.

The server rattled off a list. The only one that seemed to ring a bell outside of the standard macrobrews was some craft beer, so Andrew ordered that.

Ian tore his gaze off of the table and managed to order a rum and coke. He focused on not fiddling with his napkin too much as Rei ordered a mojito.

Once the server went back over to his station to put in the order, Ian rested a hand on both Andrew's and Rei's knees. Forcing himself into a calmer composure, he smiled between the two of them, ``Really glad we could make it, and really good to finally see you, Rei.''

Andrew simply smiled back, but Rei leaned in to kiss Ian on the cheek, ``You okay there, fox? You seem pretty on edge. Rough flight?''

Ian swallowed hard and quelled the sense of unbalance of only being kissed on one cheek. He focused on the swelling warmth inside his chest, the first sign that the anxiolytics were kicking in. ``Uh, well, yeah. I'm just really anxious. Like, most of the time. I'm sorry, it sometimes comes out in strange ways.''

Rei reached a hand over and brushed it down Ian's back before resting it on the chair behind him, ``No, it's okay! I just wasn't sure what was up, is all.''

``I type better than I talk,'' Ian admitted. ``And I talk better if I'm pacing.''

Andrew leaned over and knowingly placed a kiss on Ian's other cheek, helping to restore balance, ``Hey, don't worry about it, hon. We're all just animals here, no need to worry about how you talk.''

Ian was sure that he was blushing red. Bright red, cherry red, fire-engine red, beet red, turning purple, lips blueing, struggling for air, hypoxic. No, none of those. Just blushing, he smiled and gave the knee under each of his hands a gentle squeeze, murmuring, ``Just really glad.''

Once the drinks arrived, Ian felt that he could relax. The warmth within his chest swelled slowly and was augmented by the addition of the rum in his drink. Conversation eased for him, and he felt himself opening up both to Rei and Andrew. His two lovers shared an occupation as software developers and had plenty to talk about when Ian's stories of online goings-on flagged. He felt comfortable sitting between them, watching someone dressed as a cat flirt with someone who was dressed for something other than the convention, who may not actually have been a part of the convention, but was willing to humor the cat.

Balance became less of a pressing concern as the meds took firmer hold, but even so, as Andrew and Rei chatted about computers, Ian revelled in the feeling of love flowing out from himself and into himself evenly from both sides.

\secdiv{}

As the night wore on, through at least two more rounds, Ian settled into a very comfortable spot between Andrew and Rei. The medication he'd taken had filled his head with the softness of cotton and soothed the jagged edges of his anxiety, leaving him feeling almost languid in combination with the alcohol. He contented himself with touching each of his partners, sometimes evenly, sometimes not, enjoying the slight thrill of the lack of symmetry.

By the time he started to feel as though he was nodding, he had his hands entwined with Andrew's and Rei's both.

``Hey, I'm fading, guys,'' Andrew murmured. He'd always been something of a lightweight when it came to drinking. ``Mind if I call it? You two can totally keep up or do whatever.''

Rei nodded, ``Sure, I've had about my fill of these stools, anyway. Do you\ldots{}um, do you mind if I steal Ast for a little while?''

Ian felt the blush begin to return as his partners talked about him so plainly.

Andrew laughed, ``Sure, go ahead, as long as that's okay with you, hon. You guys should spend some time together.''

The blush deepened, but Ian nodded and said, ``Yeah, I'd like that. I'll be back tonight, okay?''

Nodding and leaning in to give him a light kiss, Andrew smiled, ``You, sir, need to have a good evening, don't fret any. You know where I'll be and how to get in touch. Have fun, you two.''

Andrew sauntered off and left Ian with Rei, the both of them sitting in silence for a moment longer.

Finally, Rei offered shyly, ``Would you like to head up to the room? Not, like, for anything, just some place quieter? Roommates should be out still.''

Ian squeezed Rei's hand in both of his own. ``Yeah, let's do that. I'm a little buzzy, and it's a little loud down here.''

Rei nodded and moved to settle the tab, covering all three's drinks over Ian's protests, before standing. The two smiled at each other and, before his sleep-, medication-, and alcohol-addled mind had the chance to talk him out of it, Ian stood quickly and leaned to give Rei a soft kiss, more of a smooch than anything.

Rei looked a little startled, but smiled all the wider, slipping his arm around Ian's back and gently guiding him out of the bar, the two talking softly about how good it was to finally have the chance to meet.

``So,'' Rei said as the door to the room shut behind them. ``How'd you and Andrew meet, anyway? I mean, I know how we met\ldots{}''

Ian laughed and settled onto the bed that Rei led him too, leaning back onto his hands. ``We actually met outside of furry, at school. Our campus had a GLBT Student Services office, and we both met there, though I think it only took us a couple of days to figure out that we were both into the furry thing. He's been in it a lot longer than I have.''

Rei slipped his messenger bag off of his shoulder and set it down atop a hard-shell suitcase as Ian talked, chatting about how he and Andrew had started dating by default, but found themselves more than compatible.

Rei slipped up onto the bed behind Ian, carefully settling himself on the bed with his legs to either side of his partner's waist. He leaned back onto one of his own hands before carefully drawing Ian toward his front, letting him rest half in his lap, half against his slender front.

Ian fretted for a moment about letting his weight rest against Rei before remembering Andrew's admonition. He had fallen silent when his partner had drawn him close like that, and eventually he managed to relax, murmuring affectionately, ``Weasels are slinky.''

Rei chuckled and placed a kiss atop Ian's head, replying, ``It's in the job description. We can't help it.''

Sighing quietly at the kiss, Ian settled both of his hands on Rei's arm around his front and made himself cozy. Everything felt warm, comfortable. There wasn't the same safe feeling he felt with Andrew, but he figured that would come in time. For now, he was content to rest against his lover, asking quietly, ``How do you feel about tonight? I hope it wasn't too, you know\ldots{}awkward.''

Rei appeared to think for a moment, then shrugged. ``It was good. I mean, I've talked with Andrew some, too, it's not like we don't have anything to talk about or anything.''

``But it wasn't weird with me being affectionate with both of you?'' Ian fidgeted, ``Wasn't weird when I kissed him?''

Rei shook his head. ``No. I'm happy to have the time with you now, but I still really enjoyed the evening.'' He paused for a moment, then asked, ``Did the evening make you anxious?''

Ian shook his head drowsily, hiking himself up a little further onto the bed so that he could rest more comfortably against Rei, ``Not really, no, just wanted to make sure. I took meds before meeting you in the bar.''

Squeezing him a little tighter against his front, Rei nodded silently.

Ian lay for a little bit longer, but eventually sat up, turned to face his partner, and leaned in to kiss him once more, more thoroughly this time. Rei carefully brought both arms up around Ian's shoulders and guided him down to the bed as he lay flat on his back.

Ian shifted up along Rei's front, careful to match movements and stay close. He made sure to set his elbows down to either side of Rei, resting most of his weight on them. The kiss lingered a little longer before parting with the two looking quietly at each other.

``I'm not crushing you, am I?'' Ian asked quietly.

``Hush, fox,'' Rei laughed, taking a cue from Andrew. ``Don't fret.''

\secdiv{}

Ian edged his way as quietly as he could into his room, finding it totally dark.

``Mmm, good evening, hon?'' he heard from the blackness, letting the door shut quietly behind him.

Ian nodded before realizing that Andrew wouldn't be able to see him, even if he had his eyes open. ``Mmhm, just some cuddling, was nice,'' he murmured, kicking his shoes off and tugging his shirt up over his head.

``Yeah, you weren't gone all that long.''

He blushed at the implication. Had he been gone longer\ldots{}but no, that was anxiety talking. Anxiety that was growing sharper edged as time went by -- the medication was starting to wear thin.

``C'mere, hon,'' Andrew murmured from the bed. ``I'm up now.''

Ian slipped out of his pants and down to his briefs, sitting for a moment on the edge of the bed. He could still feel Rei's warmth in his arms by its absence, still catch the faint scent of him in his hair. And yet, here was his boyfriend of the last six years.

Shaking his head to clear the confused tangle of thoughts, he tugged the covers up and slid beneath them alongside Andrew. He leaned in to kiss his partner three times, softly on the lips, before turning his back to him and nestling snug against his front. This is where he belonged. There was belonging with Rei, too, but this is where he was meant to be.

Andrew's arms slipped comfortably around his chest in the dark, pulling Ian warmly against his front, the soft breaths against the back of his neck raising small bumps from there all the way down his arms. ``Shh, just relax,'' came the whispered words against his neck.

Ian did his best to follow his boyfriend's suggestion, settling and relaxing within his grip by conscious effort. Andrew was warm behind him, belly pressed to the small of his back and hips pressed to his backside. He'd apparently been woken during quite the dream as the firm ridge within his boxer-briefs nudging along Ian's rear attested.

He stayed quiet, stayed still, stayed relaxed. This is where he belonged. His own erection strained at the front of his underwear, pent up after an evening of closeness with his other partner and still no release.

One of Andrew's hands wandered sleepily down over his front, brushing over freshly-shaved skin to trace a delicate fingertip along that tented fabric, ``Mmm, definitely didn't get up to much, did you, fox?''

Ian melted into his boyfriend's arms and let out a quiet moan. For all his anxiety and all the obsession over being in control, letting Andrew control things completely during sex was one of the only times he could truly let go.

With a deft hand, Andrew hooked both his underwear and Ian's down past their hips in one smooth motion, exposing his own arousal to slip stiffly along his partner's backside. ``Wolf wants inside his fox,'' he growled quietly. ``And fox needs his wolf.''

The sex was not gentle, though it was quiet, both of them aware of being in a strange room, in a strange bed, and not wanting to make too much noise. After a minute or two of firm grinding, underwear found its way to the floor and the lube had been snagged from the nightstand, and Ian felt himself spread wide by his partner.

The two moved in time, working from a few cautious initial thrusts to a steady rhythm with Andrew holding Ian to his front with one arm while the other hand clutched at his hip, tugging him back to meet his eager thrusts. The feeling was both familiar and titillating. Ian quelled a pang of regret as he felt himself leave streaks of slick precum along the underside of the sheets, the feeling of his erection being dragged across them almost enough to get him off as it was.

Finally, he felt those familiar fingers curl around his shaft and squeeze, stroking shakily as the thrusts became more urgent, less rhythmic. Ian began counting his breaths as they started to catch in his throat. He only made it to twenty-seven before he felt Andrew grind firmly against him from behind and let out a gasp, and only to thirty-three before he felt his own cock pulsing in his boyfriend's hand, waves of pleasure pushing through him and washing any thoughts of numbers out of his mind.

Once his climax had petered down to a dribble within Andrew's hand, Ian let out a long moan and relaxed back against his lover. Andrew had cupped his hand in front of Ian's shaft to catch most of the mess that he'd made, and before Ian could object, he wiped the slick mess up along Ian's clean-shaven front, leaving a smear of seed in a vertical swatch up to his neck. Hands clutched him close, and Andrew growled in his ear, ``Marked my fox. You smell of sex, and wolf''

Ian let out a sound, almost a whimper and tensed rigidly against Andrew's front, hands balling up into fists at the combination of erotic teasing and the feeling of being dirty.

``Mine now,'' Andrew murmured, then leaned in to kiss three times at the back of Ian's neck. ``Go, shower. I know you need to, love.''

The rush of relief at being given explicit permission to clean came through as a shudder when Ian relaxed against Andrew's front, pausing for a moment before carefully slipping free of the embrace and turning to kiss him firmly. ``Love you,'' he sighed, very nearly a moan, and slipped out of bed to go clean up.

\secdiv{}

Saturday morning started out slowly. Andrew and Ian had spent the hour or so after Ian's shower talking about the night past and hadn't gotten to sleep until late. By the time they made it out of bed, Andrew needed a shower, and Ian felt as though he did too, so they wound up showering together. That ate another hour of time, though Ian felt it was time well spent.

They didn't even really make it out of their room until late in the morning, partly because Andrew kept teasing Ian about the night before, brushing fingertips down over his front right where he'd smeared that slick mess the night before and making Ian squirm at the touch.

This playful attitude kept up all the way down the stairs and out of the hotel before Ian remembered about Rei. There hadn't been any plans around breakfast, though, and he sheepishly left his phone in his pocket. They had all weekend to spend together, and doing something as simple as going and getting coffee with Andrew shouldn't be that big of a deal.

They strolled leisurely through the crowds of begoggled and betailed folks in the lobby, making their way out through the doors and down the street to the coffee shop, also visibly filled with the furry crowd. They could spy no less than three tails in the line of five waiting for drinks, and several others who might be congoers as well throughout the seating area.

The settled in a corner table next to a window, Ian keeping his back to the wall so that he could see both out the window and into the room.

``I know I got a little wound up last night, but how was your evening?'' Andrew asked, splitting his breakfast burrito in half to let it cool.

Ian blushed and polished his silverware on his napkin, ``Not much more than I said, really. Got all cuddly, kissed a little, talked about you and I. It was a good evening.''

Andrew laughed and forked bite of burrito into his mouth, nodding and chewing, huffing slightly to cool the bite. ``That's good, though. I'm really happy for you,'' he said, once he could speak again.

Focusing on cutting his burrito into sixteen bite-sized pieces (four was important, but square numbers more so), Ian nodded and took the time to formulate a response. ``Yeah. I mean, I feel good about the way things went\ldots{}er, are going well. I feel really safe with you, and I think I'm learning to feel that way with Rei as well.''

Ian tried not to notice as Andrew haphazardly cut off another bite of burrito, ``Can you unpack that a little?'' he asked. ``I mean, I'm glad you feel safe and all, but I\ldots{}well, I guess I want to make sure you keep feeling that way.''

Ian shrugged and nodded, taking the first bite of his burrito and chewing thoughtfully, counting as he went. ``I guess, like, it's a two way thing. I feel like I can be myself around you and you accept and work with that, and vice versa. We each have our idiosyncrasies and the other knows how to make\ldots{}that\ldots{}work. Sorry.''

``For what?''

``I ran out of words.'' Ian frowned, fumbling over his own thoughts for a moment. ``We work with each other, rather than against each other. We don't focus on the thing the other might like, we focus on just being happy, and it works out. I don't honestly know if Rei and I are there yet, but I want to see if we can be,''

Andrew nodded thoughtfully as he chewed on his burrito, washing it down with a coffee drink as he stared out the window. ``I think I get it, yeah. It's safe because it doesn't have much friction, and you're finding the way to um\ldots{}.interact with Rei, cold as it sounds, without that friction?''

Ian nodded and worked his way through the first half of his burrito before polishing off a quarter of his coffee. He thought for a moment before adding, ``I wish he were here. Rei, I mean. I wish we could all have this conversation together.''

``Why didn't you invite him?'' Andrew asked, concerned. ``He's more than welcome, you know that.''

Ian flushed, then rubbed his hands over his cheeks, then his eyes. ``I thought about it, I just didn't know if he was awake.'' The excuse sounded lame, even to his own ears.

``I think it's good stuff, though, have you talked about this with him?''

Ian shook his head and focused on finishing his own burrito in eight smooth motions.

\secdiv{}

\begin{quote}
Rei: Hey, what's up foxy?

Ast: Hi weasel. Sorry I was out most of the morning. At the dealer's den, wanna join?

Rei: In friend's panels. Join later? Dinner?

Ast: Erf, forgot about panels, sorry. Dinner sounds good. Hotel or out?
\end{quote}

The lack of reply vexed Ian as he made his way through the Dealer's Den, mentally noting the artists he liked and their positions within the ballroom, planning a future route. He did want to keep up with Rei, this was their time together, but he felt unable to assert himself even enough to ask which panels he was in. He could guess, maybe, by looking at the schedule, but the thought of showing up unannounced presented itself as a jagged corner of anxiety in an otherwise smooth mood.

These corners had been getting out of control, today. It was like some square -- or no, some pointed star rotating within him with the points of the corners catching on his soul as though at the hem of a fraying cloth, tugging and pulling at loose threads as he wound his way through the crowds. There wasn't any way for him to keep moving without invoking some ritual or another, whether it was counting to some unattainable number or holding still long enough for his subconscious to catch up.

Ian loathed the fact that there was some sort of medication he needed in order to function within the world around him, and he avoided it at all costs. Cons, or any open, public space, however, seemed to demand such things of him, and there was little he could do to escape it.

``I won't need it,'' he sub-vocalized. ``I can take it later when I can lay down. I won't need it. I can make it through this.''

The affirmations had little impact on the part of his brain that kept repeating, ``You're visible, you're known, they know you, they can see you, they know how guilty you are, they know what you've done to Rei, how you've betrayed Andrew, they've seen the filth, they know, you're visible\ldots{}''

He shook his head, trying to clear his mind. It was just the inner critic, he thought, shouting down all the other parts of his personality. He just needed to calm that part of himself, bring the meeting back to order.

Ian found himself standing outside the dealer's den, facing out the windows of the hallway with his hands over his ears.

``I gotta stop,'' he told the glass. ``It needs to stop. I need to stop it.''

How he found himself by the elevators, or why, he never knew. Ditto the trip up to the second floor: there was simply no memory of what had happened, beyond the feeling of hands on his shoulders, guiding him out of the tiny box into an empty hallway, limitless placards, hungry doorways.

His mind was filled with numbers. One, two three, four, five six, six\ldots{}did he get three already? One, two\ldots{}

``Two\ldots{}one eight,'' he repeated to himself. ``Two\ldots{}two nines\ldots{}two one eight.''

The simple math problem calmed him enough to allow him to recognize the placards next to each door before him, and he found himself counting up by twos until he reached the door that proclaimed itself. Two. One. Eight.

Retrieving his wallet was easy, but managing to get the key-card into the slot required to open the door less so. He found himself confronted with a monumental task, weighted down with years of emotion, the actions of his own history, and the incredible importance of what it would mean if he were to open the door. Would they all come tumbling out? It wouldn't mean anything to open the door. It would mean everything if he opened the door.

``Open it,'' he mumbled, pressing his forehead to the door, eyes angled sharply down to the lock. ``Open it.''

He slipped the card in. The simple electronic shuffle of the lock cycling was almost a let down. Rei? No. Andrew?

Ian collapsed into the room, the door having provided less resistance than he was expecting. As the door clicked shut, he found himself on all fours, then knees and elbows in front of it. Two. Two nines. Two one eight. Two three four, one two, two times four. Two one eight.

Bed?

The thought was distant, but it seemed to resonate with his elbows and knees. Something something lay down something. The words didn't really line up in his head. Andrew. Rei. The things that made him feel safe. If he could only lay down with Andrew and Rei\ldots{}

\secdiv{}

``Oh jeez, I'm sorry, hon,'' came the voice from at least a mile away.

``Mmnuh?'' Ian asked.

Andrew climbed into bed with his partner, laying on top of the covers before him His hands fumbled down along Ian's sides in search of that key ring with its all-important vial.

``Hot,'' Ian mumbled. Andrew laughed.

With the key-ring in hand, Andrew unscrewed the vial and fished out a whole tablet of the blessed benzo and, with minimal effort, slipped it into Ian's mouth. ``Hey, just relax,'' he mumbled, leaning up to kiss on Ian's forehead. ``Everything's fine, fox, Just relax.''

Ian wasn't sure when the blur of torrid panic gave way to simple rest, nor even when his boyfriend's voice really faded in and out, and when it was simple hallucination. He welcomed that cool sensation, though, and sunk down into it.

\secdiv{}

Ian woke later that evening to find himself laying down between two sets of hips, the thicker of the two he recognized almost immediately as Andrew's, and on further investigation, he realized Rei was on the other side of him. The TV was playing softly in the background.

``Hey, um,'' he mumbled, licking his lips to clear the dry mouth that seemed to occupy all of his attention. ``Hi.''

Both Rei and Andrew smiled down to Ian, and he basked briefly in the glow of their attention.

``Hey,'' Andrew said. ``We got pizza. Just pepperoni. Want some?''

Sitting up in bed made Ian feel the cottony softness that the medications brought to him still filling his mind. He nodded sleepily and accepted a paper plate with a slice of admittedly pretty good-looking pizza from Andrew. He leaned first to the right to kiss his boyfriend on the cheek, then to the left to kiss Rei in the same spot on the other cheek, ``Thanks. Um, sorry about all that.''

``It's fine!'' Andrew promised.

``And sorry I didn't get to see you much until tonight, Rei,'' Ian offered. ``I kinda panicked.''

Rei grinned and hugged his arm around Ian's shoulders, ``It's okay, really. We've got tonight and the rest of this weekend.''

Ian relaxed into his partner's side and focused on eating. Pizza was less than ideal, but it sated the hunger that had cropped up as he slept, though sleep wasn't quite the right word for the fugue of deep anxiety. It was tasty, but simply difficult to decide how best to eat it. He could make it about halfway through with single, even bites, but then had to proceed boustrophedon along the thicker portion of the slice until he got to the crust, which he could break up into four pieces and eat one at a time.

Knowing that he wasn't up for leaving the room again that night, Ian settled into bed between his two partners. Watching TV at a convention wasn't really what anyone wanted, but being able to spend time with loved ones was certainly worth it. They managed to find some movie to leave on quietly in the background and settled in to talking, then into cuddling, with Ian feeling safe between Andrew and Rei.

As the night went on, the trio slipped further down into bed until they were lying flat, Rei spooning up behind Ian with his arms wrapped around him, Ian hugging those arms to his front as he nuzzled and kissed with Andrew.

As the cuddling grew in intensity and sensuality, Rei bit gently down on Ian's shoulder, right where it met with his neck, getting a quiet moan out of his partner.

``Uh-oh,'' Andrew grinned. ``You found one of his buttons. Keep it up, and make sure to get the other side, too.''

Rei held his grip a little longer before kissing at that spot, then along the back of Ian's neck, to bite gently on the other shoulder.

The fact that both of his partners were taking control of him in such a way had Ian blushing bright red, not least of which because he was also intensely aware of his arousal, as well as that of Rei pressed firmly to his backside. The gentle biting continued along his shoulders and neck as Rei pressed firmly to him with a gentle rocking motion.

Andrew shifted some in front of Ian, slipping one hand down to cup over his boyfriend's tented jeans as he reached back with the other to snag the plastic bag that held the condoms and bottle of lube they had brought along to the con. The biting on his neck stopped as Rei looked up, curious.

Ian's eyes widened, ``H-hey\ldots{}''

``Shh, it's okay, just relax, fox,'' Andrew murmured, passing the bag over Ian to Rei, who took it cautiously. ``You two should have some fun, it feels like you're already on your way.''

Ian chewed on the inside of his cheek for a moment, then nodded. ``Can you\ldots{}can you stay? Is it alright if he stays, Rei?''

Andrew thought for a moment, then nodded, ``I'll stay if you want, if it's okay with Rei.''

Rei had been quiet throughout the exchange, holding himself still against his partner and clutching the plastic bag in one hand. ``Um\ldots{}If you'd like, sure. I'll admit I've never done anything in front of someone else, much less my partner's partner.''

Ian felt flustered, but clutched one hand on either of his partners, unable to meet either of their gaze. His blush seemed to be consuming his face with its heat, but he could feel his shaft pulsing stiffly against Andrew's hand still lingering on his crotch.

After a few more moments of stillness and silence, Ian worked up the courage to stammer, ``T-take your fox?''

Rei let out something akin to a quiet growl and gave another firm grind of his hips to Ian's, biting down on his shoulder once more, more firmly this time, before rolling free to extract a condom and the lube from the bag. Andrew did his part in helping by unfastening the button to Ian's pants, slipping the zipper down and helping his boyfriend scoot both pants and briefs down to his knees, freeing his erection from the confines.

Leaving himself mostly clothed as well, Rei managed to unroll the condom down along his own shaft and coat it thoroughly with the slick lube. That accomplished, he rolled himself back to face Ian, leaning away from him enough to peer down his front as he worked the tip of his cock up against, then very carefully into his lover.

Ian, for his part, clutched tightly to Andrew, burying his face against his boyfriend's shoulder and letting out a soft moan as he felt Rei slide into him. Rei felt thinner inside of him than Andrew did, but longer as well, and the whole experience was almost jarring, in a pleasant sense. He felt connected, emotionally and physically, to both of the people he treasured most.

Edging himself forward until his hips were pressed firmly to Ian's bare backside, Rei let out a shaky breath. He slid his hands up under Ian's shirt and inched the fabric up until he could help his partner out of the garment, breaking his grip on Andrew only momentarily.

Thus exposed, he dragged his fingernails down over the skin of Ian's back, grinning as the back arched to the touch.

As they relaxed, the two settled into a slow and comfortable rhythm. Ian rocked gently with each of Rei's thrusts into him as he held his upper body close to Andrew. Rei, confident in the red scratch-marks along Ian's back, settled his hands on his partner's hips to hold them still as he moved within him. Andrew contented himself with kissing gently along Ian's forehead while his hands busied themselves with his boyfriend's own stiff arousal, caressing along it in time with the thrusts.

Ian focused on counting along with his breaths. He made it a point during sex to breathe steadily and evenly. Four counts in, hold for one count, four counts out, hold for one count. He knew that the definition of a `count' changed as he got more worked up, but it was important that he remain consistent.

They didn't speak much, and the TV was too low to make make out, and so the only sounds were the gentle sounds of sex: quiet affirmations, gentle rustling, and the occasional sound of Rei's hips meeting up with Ian's rear after a particularly hard thrust. Andrew coaxed Ian on with gentle cooing, while Rei murmured, ``My fox,'' under his breath.

The feeling of belonging, of being taken by both his partners in a way, touched Ian both emotionally and physically. Usually, it took him longer to get off than Andrew, but tonight, his body seemed to rush toward climax. He didn't even have a chance to count his breaths before he felt the familiar surge of pleasure, spurt after spurt of his cum coating Andrew's hand, wrist, and front.

``Mmm, goodness,'' Andrew murmured into his ear. ``There you go, good fox\ldots{}''

Ian whimpered and shivered through his orgasm, tilting his head up to kiss Andrew firmly on the lips, something he couldn't easily do during climax in their usual set of positions.

Rei, sensing his partner's climax, redoubled his efforts, picking up the pace of his thrusts and clutching all the more firmly at Ian's hips. It didn't take too much longer -- only twelve more shaky breaths by Ian's count -- before Rei pressed himself firmly forward one last time, leaning forward to bite down on Ian's shoulder as pleasure overtook him.

Spent, the partly clothed couple simply held themselves still and worked on catching their breath. Ian could feel Rei's chest heaving against his back beneath the soft fabric of his t-shirt, reveling in the comfort of being held twice over as he rested his head back down against Andrew's chest.

``Mmm, two good animals,'' Andrew hummed softly, holding himself still as his boyfriend relaxed into calmer breathing and relaxation.

Ian held himself still as long as he was able. The corners of his anxiety were starting to make themselves felt once more, spurred on primarily by the sensation of his semen starting to cool in the room's air, making him feel coated and dirty. Even so, it was nice to be held by both partners and share in the moment while he could.

Finally, the need to be clean overrode the coziness, and he murmured quietly, ``I need to go get cleaned up, can I get up real quick?''

Rei peeked questioningly over Ian's shoulder to Andrew who nodded his assent. Both of them disentangled from their lover and let him slip carefully out of bed and shuck his pants the rest of the way before making his way off to the bathroom.

``\ldots{}just needs to be clean, nothing wrong\ldots{}'' Ian overheard Andrew explain before he shut the door, keeping his embarrassment to himself as he started the water running for the shower.

A scant minute or so later, he heard the door to the bathroom open. Someone washed their hands thoroughly followed by a bulk settling onto the closed lid of the toilet. Peeking out from behind the shower curtain, he saw Andrew sitting there, rubbing his face in his hands.

``You okay, wolf?'' Ian asked quietly, soaping his hands up for another round of trying to clean himself of the slick lube.

``Yeah. I'm okay. I don't know if that was really what I needed, but I'm happy for you.''

Ian stood in silence for a moment until he was done soaping and rinsing. Finally, he replied, ``I'm sorry, I just\ldots{}I just wanted you both there, I guess. It was very nice to feel.''

``Yeah, no, I get that.'' Andrew sighed, ``You're just my fox, you know? I could accept you and Rei as an intellectual thing before now, but that just kind of made me internalize it\ldots{}a little more forcefully than I was expecting.''

Ian nodded and ran his hands down over his body, checking for any hint of slickness from lingering spots of lube before realizing that Andrew couldn't actually see him. Rather than replying right away, he shut the water off and grabbed a towel, drying himself in the tub. Once he was mostly dry, he folded the towel neatly in quarters and slid the shower curtain back, laying the folded towel on the floor in front of the toilet before daintily stepping out.

``I'm your fox, wolf, and nothing's ever going to change that,'' he murmured, settling himself down onto his knees and resting his hands on his partner's knees. ``You and Rei play different roles in my life, and nothing is supplanting anything that was there before.''

Andrew nodded and took one of Ian's damp hands in his own and smiled tiredly. ``Promise?''

``Promise,'' Ian murmred, leaning up to kiss his partner on one cheek, then the other. He stood to dry the rest of the way with a smaller towel.

``Hey Ian?''

``Yes, wolf?''

Andrew paused for a moment. ``How many? How many roles do you think you need filled?''

Ian draped the smaller towel around his shoulders and thought for a second. ``I don't have an answer for that, hon. I just know you're the first, and will always be.''

Andrew stood again, level with Ian so that he could kiss him gently on the lips. ``And you'll always be my fox?''

Ian nodded, smiled.

``Come on, then,'' Andrew rumbled. ``I left Rei out there to clean up. Thanks for yapping, though.''

``Yap!''

Andrew smiled, more earnestly this time.

Ian let Andrew precede him out of the bathroom. He thought for a moment, smiled, and hung up his towel. Anxiety quelled, he headed back out into the room, to both his partners.
