\documentclass{article}

\usepackage{hyperref}
\usepackage{graphicx}

\begin{document}
\title{Tarot: An Informal Self-Experiment}
\author{Matthew Scott}
\maketitle

\section{Introduction}
Tarot is a game of correspondences.  Rather than aiming to strictly
'divine' the future, we look for correspondences between the cards laid
out before us and the rest of our lives - how this card relates to our
past, what this card means in the present, and using that card to divine
a new path through life.  Tarot can change the way we act, can help us
search the depths of our subconscious and memories to help explain the
events of the past, and will show us new ways to work with the future,
ways that we would never have thought of before without some outside
influence, doing so all while being impersonal, keeping our deepest
secrets, and never telling a soul about these correspondences.

I got interested in Tarot through various sources.  In my exploratory
high school years, I had a few friends and a few relationships with some
brilliant people with diverse interests, and a few of them showed me
different aspects of tarot at different points in my career.  Despite
having two very scientific and skeptical parents, I developed something
of an interest in occult systems such as Tarot and wound up frequenting
a bookstore catering to those interests in my home town.  

At one point, while purchasing my first deck of my own, I was offered a
free reading with my own deck of cards from an established cartomancer
at the bookstore.  The reading proved to be one of the most powerful
experiences in my life up to that point.  From then on my interest grew
further, leading to many more purchases of decks and books, as well as
further research online and in libraries in Tarot as well as other
occult systems.  To this day, many of my readings still follow the same
general plan as that original one so many years ago.

I have not forgotten my heritage, though, and the respect for the more
commonly accepted sciences ingrained in me by my parents.  I thus
decided to embark on a bit of an informal self-experiment, following the
guidelines of the scientific method to test how working with the Tarot
as a tool to explore deeper within myself might change the way I
perceive the world around me, alter the way I act by forcing me to think
through situations in a different way.  This experiment also acts as a
bit of a slice-of-life diary, with each reading providing a view of
what's going on in my life at the time - the issues that are concerning
me, and all the hopes and fears that have built up to that point.

%%%%%
\section{An Informal Self-Experiment}

%%%%%
\subsection{Questions}
\begin{itemize}
	\item How does tarot work?
	\item How does learning to work with the tarot affect a person?
	\item Does mindfully working with the tarot generally lead to a different method of dealing with events in the past?
	\item Does mindfully working with the tarot generally lead to a different consideration of the future?
	\item How does working with the tarot affect the way a person deals with events and their position in time?
	\item How does the conscious application of a defined set of archetypes change the way a person deals with a situation?
	\item How does the person respond to such questions as these above being applied to them?
\end{itemize}

What I aim to learn from this experiment is basically what would happen
by changing a part of my life.  I don't want to see into the future,
necessarily.  Rather, I would like to become more cognizant of the
present, to take the past into account, and to integrate all levels of
myself into my day-to-day life: conscious, subconscious, and
unconscious.  While the questions listed above are the specific ones,
the more general overview would be this: if I were to consciously try to
change my outlook on life through the use of this tool, what would
happen?  What would change about me as a person, not just the path my
life was taking?

%%%%%
\subsection{Observation}
\begin{quote}
We come to the notion that the Tarot works precisely because it makes no
sense.  The information exists.  Our unconscious selves already know it.
What we need is a device to act as a bridge to conscious perception.
\cite{pollack97}
\end{quote}

The modern Tarot deck is made up of 78 cards - there are 56 minor arcana
and 22 major arcana cards.  All of these cards represent different
archetypes, or general ideas about different aspects of life, humanity,
and the self.  More than simply divining the future, one my seek out
correspondences between situations at hand, in the past, or possibly in
the future through these archetypal images, laid out within the
framework of the cards and how they relate to each other.  One can
utilize a 'spread', a pattern in which to lay the cards with each of
their positions holding a predetermined meaning so as to deepen the
meanings of each card.  Just as frequently, however, one may let the
cards, the reader, or the querent determine the positions of those
cards, divining meanings for them as the reading progresses.

There are many different views on Tarot.  By far, the overwhelming
majority of people in todays world put little or no stock in divination
of any sort, and would just as soon leave any introspection in the hands
of those with 'Ph.D' tacked on the ends of their names.  Of those whose
opinions do not favor Tarot, there are further divisions: some may have
humored a cartomancer and had a reading done for themselves and disliked
it for one reason or another, having been scared by it; some may have
difficulty thinking of those who deal in such things as actively harmful
frauds; and everything in between.  On the other side, of course, there
are those who see the cards as a window into the future, those who use
them strictly for introspection, those who use them for various magical
purposes, and, again, everything in between.

This document is hardly meant to be a dissertation on the cards
themselves, nor the varied opinions on their meanings or acceptance in
the world today.  For further information, please look up the
information in the bibliography, as others can surely tell those stories
far better than I.  My aim is only to explore the way that the cards can
influence life.  When I began college, I saw that those around me
weren't focused on growing or changing, and in fact, many had remained
the same person that their parents had molded them into years back,
simply refusing to change.  Not only did that idea of changing who I am
in however subtle a fashion appeal to me, I felt that allowing this
change instead of stagnation would mean that I was actively working to
make myself a better person and doing my best to better the lives of
those around me.

%%%%%
\subsection{Hypothesis}
I feel optimistic about this experiment.  I have rarely ever taken an
active role in the way my life changes, and I think that by guiding it
in this small way, I can improve the way that I deal with what happens
to me, improving the integration of new information in order to become a
better person as a whole.  I also expect that, by being more easily able
to comprehend the world around me and the people in it in reference to
my own worldview, I will be able to affect those around me in a
possitive manner, in effect, being a better person for them.

%%%%%
\subsection{Procedure}
My goal is to do 78 readings of the Tarot with the goal of at least one
reading per day.  For each reading, I will gather information about the
background of the situation, the layout of the cards and the disposition
of the deck, and finally, an analysis of the cards and the reading,
including the effect that the reading had on me as a person.  These
readings will be mostly for myself in my day-to-day life, but I will
also attempt to read for others as well, recording the way the reading
made me feel and any insights that will be applicable in my own life.

When the 78 readings are completed, I will attempt to analyze the
information from the collected write-ups of the readings, looking for
changes over time in the way I interacted with the world around me and
how I felt as a whole.  These trends will be described in as much depth
as possible in order to explore how the conscious utilization of the
Tarot to change my life truly affected me and, hopefully, those around
me as well.

%%%%%
\section{Experimental Data}
\subsection*{Preliminary Introduction}
As these readings are very personal in nature, I feel the need to
introduce myself before just jumping right into portions of my life,
lest they make no sense at all.

I was born Matthew Joseph Scott in January, 1986 to Donna Karr and Ron
Scott, two engineers with the minds of scientists.  I was raised a
skeptic and an atheist.  Life was uncomplicated: everything that could
be explained, was, and anything that couldn't was set aside as an
unknown until it could be explained with no further thoughts on the
matter.  Of course, when you tell a young child not to do something,
that's a very effective way to invite them to do it in secret if
possible; I was told not to concern myself with the unexplainable
matters of religion, mysticism.  Thus it was that I began acquiring my
secret stash of information on all of those subjects, beginning with a
King James bible given to me by a camp counsellor, working up to a
modest library of books dealing with topics ranging from the ``big five''
religions and reiki to the history and use of drugs.  I have already mentioned a
little about my introductions to Tarot.

That leads to me today, August 13, 2008: I am a student in the music composition program
at Colorado State University in Fort Collins, Colorado.  After trying
(and failing) to be a biochemist, I've accepted that I make a far better
musician and publisher than a scientist, but the need to explain, to
experiment, and to experience the world around me remains.

To lend even more specifics to the situation, I was only recently
accepted into the composition program after spending nearly four years
in music education, finding myself disillusioned with the American
public education system.  This means that my four years of paid tuition
promised by my dad are up, and I must begin paying for my own tuition
from my earnings.  I work at the campus library as technical support,
and I am currently dealing with some problematic homophobia from my boss
and coworkers there.  On top of that, just a few months ago, I underwent
a very difficult breakup with my boyfriend at the time.  I ``rebounded''
onto another friend of mine, but as soon as we started getting close to
each other, he had to move down to Denver, Colorado, an hour's drive
away.  

It was this combination of stressors that lead me to look into
creating my own change in life.  This jumble of emotions and ideas is
what I am right now, and I want see what I can make of that by being
more mindful of my life, guiding it where I can, and becoming a better
person, using the Tarot as a tool.

%included files, one for each reading
\include{data8-13-08}
\include{data8-14-08}
\include{data8-17-08}
\include{data8-18-08}

%%%%%
\section{Analysis}
The analysis of this experiment will be written when all data is
collected, in order to more properly answer the questions posed.
%answer questions with experimental data

\bibliographystyle{apalike}
\bibliography{biblio}
\end{document}
