``This,'' Thomas declared in a reverent tone.  ``Is Salvia divinorum.''

I blinked up from my computer.  ``What?''

``Salvia!'' he repeated, dropping his backpack unceremoniously and flopping down onto his bed.  ``It's a hallucinogen, I guess, but it's legal.  Got it at a head shop just off campus.''

I twisted myself around in my chair.

Thomas laughed, ``I knew that would get your attention.  Couldn't get you any shrooms, sorry, but I figured this is the next best thing.''

``Hey,'' I grinned.  ``And it's legal, too.  Thanks for thinking of that.''

Thomas nodded and pulled a ziplock bag smaller than a matchbook from the plastic bag and frisbeed it across to me.  It was labelled with a hand-written sticker saying `S. div. 20x 1.1g 15-'.  All it contained what looked to be a dried up leaf crumpled up into flakes.  I pinched it dubiously between my fingers. ``Looks like oregano.''

``Well,'' Thomas countered.  ``If it is, I'm out fifteen dollars.  Oh well.''

``So what's it do, then?''

``Well, it's a hallucinogen, like I said.  Makes you kinda... see shit and have all sorts of grand thoughts.''  He brightened up, ``Here, give it back.  Tell you what.  I'll try it and tell you what it's like.''

I laughed and tossed the baggie back to Thomas, ``Well, okay.  If you freak out, I'm getting out of here and denying everything.''

Thomas nodded, so I set myself as away on instant messengers and IRC.  ``The cool part,'' he explained, shifting himself to sit cross legged on the floor, reaching hand underneath his bed for the shoe box of drug paraphenalia I knew he kept there.  ``The cool part is that it only lasts, like, five minutes or sorather than, like, six hours for shrooms or acid.''

I nodded a little and shifted onto the floor as well so we'd be level with each other.  ``Well, what is it, exactly?''

``Leaves off some plant.  They told me at the shop that you need to smoke a fuck ton of the plain leaf, so they sold me some extact.  I got twenty ex stuff, since that was the most concentrated they sold, and I figured that'd be better.''  He worked as he spoke, picking a glass pot pipe out of the box and examinging it.  He seemed to be pondering emptying it out, but after looking at the tiny size of the flakes of Salvia, he seemed to change his mind.  Resting the pipe on one of his knees, he opened the tiny baggie with his fingers and delicately pinched a small amount into the bowl of the pipe.  If he had laid all of the peices flat on a table, it probably would've only taken up the area of a dime.

Closing the bag, he cradled the pipe in his palm, digging his lighter out of his pocket with his free hand.  ``So if I freak out or something, which I probably won't, just, like, keep me quiet for ten minutes or so, I should be good.''

``Thanks for the reassurance,'' I muttered sarcastically.  My palms were sweating enough to leave damp patches on my knees where they rested.  I had been bugging Thomas about trying hallucinogens every since I found out just how much he was into drugs, but he had always just waved me off, complaining that such things were difficult to procure.

``Alright,'' he muttered, taking a few deep breaths and letting his shoulders drop as he relaxed.  Finally, he brought the stem of the pipe up to his lips and, holding the lighter to the plant material in the bowl, drew the smoke in deep.  His hands started to shake as he set the pipe down quickly on the upturned lid of the shoebox, dropping his lighter into his lap as his eyes screwed shut.  He held the smoke for about twenty seconds before coughing it out like a bubble of cloud.

He collapsed back against the edge of his bed while his right hand grasped the frame of it, keeping him from sliding down onto his side.  ``Nnnnnn,'' he said, nodding and smiling to me.  The smile turned into a grin, the grin to a snicker, and the snicker burst into gales of laughter, startling me.  Holding himself up like that, he laughed and laughed and laughed.  The laughter went on for probably a minute and a half before finally slowing down, dropping nearly an octave to his low, stoned chuckle that I was so used to.

After another thirty seconds or so, he leaned his body forward in a slow swinging motion to rest his forearms on his knees, propping himself up.  He swayed slightly in this position, another half a minute passing by before he shifted his arms so that his elbows rested on his knees and he could prop his chin up on his fists.  

``W-weird,'' he drawled.

``What the hell was that, Thomas?''  I realised I was clutching the denim of my jeans in my fists and relaxed my hands, wiping the perspiration off on my thighs, ``What happened?''

``Dunno, man,'' he smiled beatifically.  ``Dunno.''

I let him sit there for a few minutes while he seemed to sober up.  Finally, he shook his head and lit a stick of the incense, opening the window and moving sluggishly to drop a towel along the base of the door, something we had forgotten to do earlier.  Finally, he continued, ``I felt like the earth tilted down and to the left and that something was really, really funny, but I never knew what.''  He swallowed drily and grabbed a Mountain Dew out of the fridge before returning to his spot on the floor.  ``Lot shorter than I thought.  How long did it last?''

``Uh... about three minutes, I'd say,'' I smiled.  This didn't sound like a hallucinogen, but it did sound resonably fun.  Thomas' reaction to the drug relaxed me some.

``Holy fuck,'' he laughed, drinking about a third of the soda in one go.  ``Felt like ten, fifteen seconds.  Cool.''

We sat for a few minutes, Thomas finishing his drink and me fingering the hem of my shirt.

Finally, he tossed his bottle toward the trash, missed horribly, and chuckled.  ``Still kinda stoned feeling.  Wanna try?''

I took a shaky breath and nodded, watching as he reloaded the bowl with a small pinch of the Salvia.  I took the offered pipe and lighter and sat for a few moments, holding them in my lap and looking down at them.  I shook my head finally and, before I lost my nerve, brought the stem of the pipe to my lips, inhaling the smoke deep as Thomas had done.

The Salvia burned quickly and there was surprisingly little smoke, though the smoke was parched and hurt my throat.  Holding it in despite the sting, I quickly set the pipe and lighter down in front of me on the floor.  I held the smoke for what I guessed was a count to thirty before huffing it out at once, feeling a bubble of amusement rise in my chest.  Breathing out the smoke, I felt like I had blown myself backwards.  This was kind of funny, I thought.

The amusement froze in my chest and I felt gravity turn beneath me, the ground suddenly sinister.  I reached out and clawed at my mattress, tugging feebly at my sheets as I was pulled inexorably down onto my side with gravity trying to suck me under the bed.  There was a persistant rhythmic sound, like someone hyperventillating on the consonant `t', a little less than twice per second, maybe a hundred beats per minute.  More than the sound, the rhythm was a sensation --- something dry and rasping was stroking against the inside of the back of my skull, feeling rather like strokes of a cat tongue.

My eyelids stuttered close as time slowed.  I felt as though I was watching a video game on a slow computer, the framerate of my eyelids covering my vision having to be redrawn several times a second.

Terror.  The rhythm became my existence for what seemed like a short eternity, and I felt compressed on all sides as though I was being smothered with very soft weights.  I couldn't move.

Terror.  The weight began to lessen and it felt as though each of those rhythmic pulses was a gash of reality peeking through into my mind.  Some reality more real and raw than I had ever experienced.

Terror.  Memories of words and snippets of conversation flipped through my mind during the dark phases between the flashes of reality.  What must've been the bed frame was digging into my side, but the word `monster' flashed before my eyes in the dark and I felt as though I was being eaten.

Terror.  I struggled to sit up as my eyes open and light bled into my my brain.  I saw everything not as objects, but as borders; the edge of the fridge was just a line separating a black area from an off-white area.  There was a man-shaped blend of colors leaning near to me.  I nodded at this strange thing knowingly.

Terror.  I crawled from my spot on the floor and up onto my bed, where gravity pulled me definitively down onto my back.  I watched from within as, without the bed eating me, everything became internalized.  I felt as though I was just an area, myself, that my ego was defined by a border.

Terror.  The border ruptured as I watched and I convulsed as my straining self rushed out of my body.  It felt as though I was dying.  Everything about me was getting lost in a universe of lights.

Terror subsiding.  I suddenly realized that this didn't hurt, that dying didn't feel bad.  I had simply lost my concept of self.

Relax.  I wasn't a person any more, I was a part of humanity.  Purer, brighter, lighter, more innocent than a person.  Every other part of humanity seemed connected and close by.  I must be coming down, I thought comfortably.  The sense of self-ness was returning, and memories were starting to come back.  The rhythm decrescendoed into a sense of waves.  Relax.  Kris wandered into my thoughts and I smiled.  This was a person I felt affection for.  This was a very puzzling thought, one that I couldn't quite wrap my mind around.  I couldn't define affection, nor my feelings for Kris.

The Salvia gravity relented enough for me to sit up in bed and I looked around the room.  Thomas was sitting in the center of the room now, pipe and lighter in hand.  I waved at him and he burst out laughing.  He said something, but my ears were buzzing to loudly for me to hear.  Finally, I twisted a little, stretching out my back and shaking my head.

Another minute or so and Thomas and I were talking again.  I felt, as Thomas had said, a little stoned.  It wasn't a happy sort of stoned --- it wasn't emotional at all.  I just felt slow and sluggish.

``That shit must've just rolled over on you, man.''

I laughed, ``What happened?''

``Well, you set the pipe down pretty quickly and frowned, then you sorta laughed out the smoke.  You said `whoa' and fell over onto your side.  You just sorta lay there for a bit, shaking your head occasionally.  Then you, like, flipped out and climbed up onto the bed and lay down there, breathing all fast.''  He shrugged and passed me one of his sodas from the fridge, ``After a few seconds you said `huh' a few times and started to relax.  You were tense as fuck for a while there.  I was going to ask you what was up when you sat up and waved at me.''

I laughed again and nodded, drinking some of the Mountain Dew down gratefully, letting it cool my throat.  It tasted like soda water, for some reason.  ``Weird as hell.  Felt like gravity shifted for me, too, and pulled me onto my side.''  I grinned, ``I thought the bed was eating me so I climbed up onto it.''

Thomas laughed too, ``Fuckin' trippy.''

I tapped out the rhythm on my leg, explainging, ``It felt like it was trying to eat my thoughts or something, licking at my mind about this fast.  It was better when I got on the bed but I felt, like... uh... I don't know.  Like I couldn't define myself or me or I anymore.''

``Ego-death,'' Thomas nodded.  ``Had that when I did shrooms.  Was fun.''

``Was fucking scary as hell,'' I corrected him.  ``Though after a bit I guess I kind of accepted it.  That's when I started coming down.''

Thomas nodded and leaned back against his bed, dropping the Salvia and pipe back into the box before nudging it under the bed again.  The room smelled like Nag Champa still, so I figured he had burned a little more of the incense.  ``Fuckin' trippy,'' he muttered again, shaking his head and lumbering over to his desk where he started up his laptop.  I shifted myself off of my bed and over to my own computer, shaking the mouse to wake it back up since it seemed that Thomas had other things to do.

I checked to see if Kris was online.  She wasn't, so I left myself set as away and opened up a text editor, figuring I'd write out my thoughts.

I sat for a few minutes staring at the blank screen.  The windows still looked to me like how I had perceived the room in my moment of terror, as more border than anything substantial.  Finally, I begun writing, haltingly and pausing often to think and stare at my screen.

\vspace{1em}\begin{sloppypar}{\ttfamily
HOW I BRIEFLY WENT CRAZY 

or 

MAKE ME ONE WITH EVERYTHING

My roommate gave me some salvia and told me to smoke it.  Being the open-minded individual I try to be, I decided I'd go ahead, despite the risk of seeming like a druggie, something I worry about a lot more than I probably should.  I watched my roommate try before I did, figuring I would get an idea of what happened.  He laughed like a crazy man for about three minutes, and in another minute, he was back to his normal stoner self, saying that he didn't know what he was laughing about.  Seemed fun enough.

There were three levels to the trip, and I'll go through each in turn.

ACTUAL:

This is what happened outside of the trip.  Most of this was found out second-hand from my roommate, who was watching the whole process.  I smoked a tiny pinch of 20x salvia extract (note to self: look this up later) and held the smoke for several seconds.  I put the pipe down while I was holding the smoke and frowned, then laughed the smoke out.  I proceeded to say `whoa' and tip over onto my side, where I layed still except for occasionally shaking my head.  Eventually, I seemed to freak out, then climbed back up onto the bed where I stayed tense before finally relaxing.  I sat up after a bit and waved at my roommate, who laughed.  By then, I was just about down.

PHYSICAL:

Everything was as described up until the time I laughed.  I blew out the smoke and thought I was blowing myself backwards, but then it felt like gravity was shifting beneath me and despite trying to stop myself, I fell over onto my side, pulled there by gravity.  I remember closing my eyes and watching it like that scene from Tron where the protagonist is traced into the computer program, but that's all I remember for a little bit.  Except for the rhythmic pulse I heard and felt against the back of my head.  With the frame digging into my back, it felt as though I was being eaten by the bed, so I crawled up on top of it to get away.  This was one of the scariest things I had ever felt, so I stayed tense in bed until I started to come down, relaxing and feeling more comfortable.

MENTAL:

Mentally, I spent most of the time terrified of what was happening.  After I thought the bed was eating me, I looked around and lost the concept of space, seeing borders of things instead of the things themselves.  I climbed back into bed and experienced what my roommate called ego-death.  I felt like I was disappearing as a person and simply part of a larger whole of everything.  It seems cliche now, but I felt like I was starting to become one with everything, and it was terrifying.  Finally I started to accept it, and that's when I started to come down from everything.

=====

So what does it all mean?  I know I shouldn't look for meaning in the random misfirings of the brain on drugs, but the whole experience of ego-death was startling and felt extraordinarily deep.  It makes me feel that I would be a fool to not take anything from this experience.  I know that I'll be digesting this whole thing for a long time to come.  It has sobered me up to the raw truth embedded in reality, and I'm starting to see everything in a whole new light.  When I was coming down, Kris came to mind and I felt like I was seeing my affection for her from some sort of objective standpoint.  I don't know how to explain it, but it felt as though it was just sort of a fact of who we were as people.  Not destiny, just that that's how we were made to react towards each other.

I guess the net experience from the salvia is that everything was put into perspective.  All of the terror and all of the weird physical and visual anomalies were just static produced by this foreign substance coursing through my body.  The truly valuable part was the kernel of truth I gleaned from the matter.  It showed me that my interactions between myself and others are always on the terms of me being a person, and of them being sort of projections from myself.  Ego-death showed me how much deeper things really could be.  It would be terrifying, but being able to experience someone as a truly separate entity as my sense of self dissolved would, I think, get me much closer to them in the long run.  It brings to mind some experimenting that Kris and I could do, though I'm not sure that plumbing the depths of fear is something you really want to plan on doing with someone you like.}\end{sloppypar}\vspace{1em}

I saved the file with some sort of innocuous name that I hoped I would remember, leaning back in my chair and listening to Thomas playing music on his laptop, staring out the window instead.  Now that I was down from the experience, I didn't feel so objective about my affection for Kris anymore.  I felt incredibly strongly to be honest, almost as though I needed to see her right now.

I opted for a little bit of restraint instead and made my way back over to my bed so that I could sprawl out on my back comfortably, thinking of Kris, of all that had transpired in the last few weeks, and of how little gender really meant.  When one ignored the dissonance created by acting contrary to what was expected by the self and others, it was liberating.  It felt honest, truthful, and it made me happy.

But I had been finding, of course, that there are always consequences of dissonance, and those chaotic consequences stretched farther and wider than I would ever be able to predict.
