\hypertarget{michelle-hadjesasha-2124}{%
\chapter{Michelle Hadje/Sasha — 2124}\label{michelle-hadjesasha-2124}}

Michelle Hadje mastered the urge to vomit.

She knew that could change this. Change all of these things from so many dreams that pressed in against. She knew that she could will them away, or perhaps spring for a fork that would simply\ldots not have them. She had enough reputation, by now, but fork a dozen times over. Some perks came with being on the council, after all.

But she didn't, and she was not quite sure why.

At one point, she had entertained the idea that it was out of a need to keep some part of herself tied to the her of eight years ago, the panicked and wild-eyed woman who had scrimped and saved all that she could to get a one-way ticket into the System. Perhaps she needed to keep some tenuous connection to the Michelle left so changed by getting lost that year on year become madness on madness.

But that wasn't quite it. Perhaps, instead, she felt as though she wasn't worth it. She hadn't been able to save her friends, not in the end, and it was only by dint of luck that she managed to survive the years after that terrible day her mind was wrapped in on itself and all her thoughts and all her dreams were mirrored back upon her. Perhaps she deserved these bouts of lingering disconnection, dissociation, derealization, depersonalizeation.

That wasn't it either, though. She may sometimes feel the weight of responsibility, but thoughts as gloomy as that came only when she was feeling particularly peaky.

Lately, her best guess as to why she kept this madness draped around her was the slew of memories of RJ that hit her at unexpected intervals. She could feel em, sometimes, as a ghost, perhaps, or a wish, a dream, but then that feeling would disappear and she'd be left with despair and the urge to vomit and the flickering of herself.

Michelle.

Sasha.

Michelle.

Sasha.

That last hypothesis encompassed much of the previous two, and would explain why the looming tenth anniversary of the founding of the system seemed to make it all the worse. Ten years since the founding, eleven years since RJ disappeared, giving emself up to the act of creation.

Ah well. She had lingered long enough outside the coffee shop, so she swallowed down her rising gorge and mastered a few waves of shifting form, skunk fur and human flesh fighting for dominance. The skunk form won today, anthropomorphized to a comforting degree, sitting just shy of cartoonish. It would do. She would be Sasha for the meeting.

The Council of Eight, for all its high status and demand, met in incognito in unassuming, downtempo sims rather than some conference room or grand palace. The eight of them would trickle into the sim over the course of a few hours, set up camp on a hilltop or in a cafe, enjoy the ambiance, and then set up a cone of silence to discuss business. They had been noticed once or twice, but never hounded and certainly not attacked.

Debarre and user11824 were there already, slouching before their coffees in comfortable silence. Both looked up and waved to her when she entered, so she requested a mocha and joined them around the table.

``Hey Mi--er, Sasha. Hows tricks?'' Debarre asked.

``Tricksy, as usual.'' She smiled wanly. ``How about you two?''

user11824 shrugged. His features were nondescript to the point where Sasha doubted that he even needed to work at being incognito. Eyes simply slid over him without pausing. ``Bored. Boring. Bored.''

``How are you bored? There's always too much to do.'' Laughter came from behind her, followed by a friendly touch to the shoulder. Jonas, on the other hand, was perilously handsome and friendly with a casual ease that left all feeling envious.

``Yeah. Boring shit.''

Jonas slid into the seat next to Michelle, coffee in hand. There were a few minutes amiable chatter as the other four octarchs trickled in: two well-dressed women, one well-dressed man, and one slouching form of indeterminate gender (and occasionally species) that looked more like a discarded pile of rags than anything.

Sasha blinked, and a cone of silence spread around the table. The proprietor raised an eyebrow, but made no other move to acknowledge it.

``So,'' she began, rubbing her paws over her face. ``I know we just had a meeting, so I am sorry for stealing you all again, but I have a thing to ask of you all. A question, for sure, but it may morph into a favor, depending on the answer.''

``Boring one?'' user11824 asked.

Sasha forced a tired chuckle and wobbled one of her paws over the table. ``Maybe. Probably. Most things are boring to you.''

He rolled his eyes. More chuckles around the table.

Swallowing down another wave of Michelle washing across her body, she continued. ``I would like to create ten forks to delegate responsibility. Would that be okay?''

Jonas frowned. ``That'd be pretty expensive.''

``Would it be worth the expenditure?'' the pile of rags rasped.

Sasha quelled the instinct to shrug again, nodding instead. ``I think it would be. At least, temporarily. At least for the next year or so. I will shift my role to a more managerial one, acting as consensus builder for my clade. I would not gain any more say in votes.''

``Would you take on additional responsibility, then?''

``I can. I am always happy to do my share of the work, and if that share increases ten-fold while I shift to a consensus point, I will be okay with that.''

Debarre gave a lopsided smile. ``If it's simply about more hands on the ground, I see no problem with it. It's your reputation to spend, and\ldots{}'' He hesitated, smile fading to something more serious, and continued. ``And if it helps you out, then it's probably for the best. I'm sorry Sasha, but you look like hell.''

She forced herself to keep tears out of her voice. ``I feel like hell, if I am honest. I will ensure none of the forks have\ldots all this.''

Nods around the table. The woman spoke up. ``I'm comfortable answering your quest with a `yes'.''

They went around the table, and none of the others said contradicted the first vote. Sasha slouched in relief, letting her control slacken and her form blur for a few moments.

``Does that answer mean that you have a favor to ask?''

She nodded to Debarre. ``A two-part favor. I would like some help delegating to my forks, if we have ten things that need doing, and then I would like a week off.''

Jonas laughed. ``You're allowed a vacation, Sasha. Go for it. I'm sure we can all find something for your new clade. The Hadje Clade?''

``The Ode Clade.''

Debarre stiffened in his seat, frowned. Sasha did her best to maintain her tired mien, keeping her gaze on Jonas.

``No clue what that means, but hey, Michelle-slash-Sasha of the Ode Clade it is.''

``Do we applaud? Is this exciting?'' user11824 asked. He looked honestly befuddled, and Sasha admitted that she could use a life so bound by boredom that excitement could go unnoticed.

``It's exciting for me. I get to sleep in.''

Laughter around the table.

The pile of rags shifted, rasping its words. ``Are we comfortable with this as a general rule? Perhaps we would all benefit from a fork here and there to help us out.''

``Can we come up with a mechanism for tracking hands on the ground, as you so eloquently put it?''

Sasha nodded eagerly to the sharp dressed man. ``Please. It is not my intention to take over work just so I can do more things my way.''

``And we'll have to be careful not to overextend our reach. There being only the eight of us kind of limits our capabilities by necessity.''

``We can be open about it, set limits for ourselves. Maybe no more than ten per council member.''

``It might be handy to fork further for personal reasons down the line,'' Sasha said, carefully avoiding Debarre's gaze. ``I can think of a hundred things I would like to do.''

The weasel's frown deepened.

``Sounds fair enough. I figure we've all got personal lives outside this,'' one of the women said.

``Yeah, boring ones.''

``You're such a drag. Take up fishing or something. Then you can be bored with purpose.''

``I've got a stack and a half of trashy novels to plow through.''

``There's some changes I've been meaning to make. Maybe I can even figure out how to make it like a real demolition process, too. Putting a sledgehammer through drywall? Exquisite. Simply exquisite.''

The chatter continued around the table. Sasha focused on her mocha, studiously avoiding Debarre's searching gaze.

The cone of silence was dropped, and council members left at their own pace until only Sasha, Jonas, and Debarre left.

``So, what's the deal with the clade name? And why are you two being so weird around each other?'' Jonas asked.

There was a moment's silence, then Debarre murmured, ``You tell him.''

``A friend of mine — of ours — wrote this poem, an ode, and I was thinking that I would name the instances after lines from it. A hundred lines, ten stanzas. That gives me ten first lines to start with, and I can go from there.''

Jonas shrugged. ``Well, fair enough. You didn't answer why you two got all weird, though.''

``Complicated stuff. Both Sasha and--''

``We were both among the lost,'' Sasha interrupted, shooting Debarre a warning glance.

Jonas held his hands up to forestall further conversation. ``This is between you two. You can share what you want when you've got it sorted out.''

Debarre nodded sullenly. Sasha looked down at her paws.

``While we're on complicated subjects, I have an admission to make.'' Jonas looked sheepish. ``I have a small clade of my own on the side. All for personal stuff, of course.''

Debarre tilted his head, then laughed. It was an earnest laugh, full-throated, and Sasha realized that Jonas had said precisely the right thing to cut through the tension.

``Do you have some equally stupid clade name?'' Sasha said, grinning.

``Oh, just the Jonas Clade. I'm going to keep forking as long as I have reputation, so we've been naming ourselves with syllables. There's plenty enough of those. I'll stay Jonas Prime, but there's already a Ku, Ar, and Re Jonas.''

``Fucking nerd.''

Jonas batted his eyelids at Debarre. ``Thank you. I try.''

After a bit more chatter, Debarre made his goodbyes and left the sim.

Sasha and Jonas tacitly agreed to go for a walk down the street. The sim was of a comfortable, small town plaza, so it was a pleasant enough walk. They made their way to a central fountain and, while Jonas sat on the rim and watched, Sasha dumped hunk after hunk of reputation to create her ten forks. They alternated between looking like Michelle and looking like Sasha. Each introduced herself in turn.

``I Am At A Loss For Images In This End Of Days of the Ode Clade.''

``Life Breeds Life But Death Must Now Be Chosen.''

``Oh, But To Whom Do I Speak These Words.''

And on down the list of first lines. Eventually, a crowd of eleven stood near the fountain, in front of a bemused Jonas.

``So, what next?''

``What is next is that I get assignments from the council and then take a fucking vacation. I plan on sleeping for at least three days straight.''

Jonas laughed. ``I wholeheartedly endorse this course of action. One of you want to take on an assignment today?''

After a short conversation, one of the Michelles stepped forward. ``Sure. What kind of assignment?''

``Which one are you again?''

``The Only Time I Know My True Name Is When I Dream.''

Jonas winced. ``Got something shorter I can call you? Even if only in informal settings?''

She laughed. ``Oh, sure. Let us go with `True Name'.''

``Much better! Alright, your assignment is to work with me on the individual rights conversation.''

``Is that heating up?''

``Yeah, there's some real grade-A stupidity going on out there.'' Jonas paused to wave to the rest of the Ode Clade, which left the sim en masse. ``Lots of this and that about how software can't be an individual blah blah blah. One particularly vile shithead suggested that if we wanted to be treated as individuals, we would need to contribute to society as equals with those still in the embodied world. He suggested we could split the system and dump individuals into flight computers and software rigs and other expert systems to run those so that they wouldn't have to.''

True Name frowned. ``What a dick. Is that kind of opinion common out there? I am still coming off the mount of work that was the reputation market.''

``Not so common now, but those voices are getting louder by the week.''

``Damn.''

``Damn indeed. Thankfully, those aren't the only voices. The DDR still has a good number of folks who remember the lost and just how fucked up it was for whole-ass people to be dumped into nothingness, and that sounds awfully similar to becoming a glorified flight sim.''

``But that is on the DDR. Do we get votes? Do we even have access?''

``We do not, no. What we do have is the ability to communicate.''

"Propaganda, you mean.

Jonas smiled, nodded. ``Propaganda.''

``I did pretty well in debate class.''

``Good, we'll have need of that. And you can write, too. Your proposals are a thing of beauty.''

``Oh? A joy for ever? Its loveliness increases?''

Jonas looked blank.

True Name laughed. ``Never mind. Let us go change some minds.''
