\hypertarget{youre-gone}{%
\chapter{You're Gone}\label{youre-gone}}

{
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\subsubsection*{Sunday, March 30}\label{sunday-march-30}

\emph{1:39 PM Markus\textgreater{}} Doctor Maura told me I should start
journaling when this whole crazy process started. She said it would keep
me grounded, let me set milestones of memory, some BS like that.

\emph{1:40 PM Markus\textgreater{}} I told her I'd give it a think and
then promised myself I'd forget about it.

\emph{1:40 PM Markus\textgreater{}} But now, you're gone.

\emph{1:40 PM Markus\textgreater{}} You're gone.

\emph{1:40 PM Markus\textgreater{}} Oh god.

\emph{1:40 PM Markus\textgreater{}} You're gone.

\subsubsection*{Monday, March 31}\label{monday-march-31}

\emph{12:10 AM Markus\textgreater{}} I made it home from the hospital a
few hours ago. My hand hurts. My heart hurts. So much paperwork to let
someone go.

\emph{12:11 AM Markus\textgreater{}} They say I'll have to sign more
tomorrow, and that I should get a lawyer.

\subsubsection*{Tuesday, April 1}\label{tuesday-april-1}

\emph{7:12 AM Markus\textgreater{}} I keep expecting you to still be
here.

\emph{7:12 AM Markus\textgreater{}} It's not trite, like it sounds like
when others say it.

\emph{7:13 AM Markus\textgreater{}} Not like I'm expecting you to come
around the corner or come through the door.

\emph{7:13 AM Markus\textgreater{}} More like

\emph{7:13 AM Markus\textgreater{}} You're still at the hospital.

\emph{7:13 AM Markus\textgreater{}} You're still just at chemo.

\emph{7:13 AM Markus\textgreater{}} You're out of the house.

\emph{7:14 AM Markus\textgreater{}} You lost your phone.

\emph{7:14 AM Markus\textgreater{}} I guess that's trite.

\emph{7:18 AM Markus\textgreater{}} Though I turned off your phone.

\emph{7:18 AM Markus\textgreater{}} I could hear it vibrating every time
I messaged.

\emph{7:28 AM Markus\textgreater{}} Couldn't tell if that made me feel
sad or stupid, or both.

\emph{7:32 AM Markus\textgreater{}} Both, I think.

\subsubsection*{Wednesday, April 2}\label{wednesday-april-2}

\emph{2:30 PM Markus\textgreater{}} You made it to the funeral home.

\emph{2:30 PM Markus\textgreater{}} In one piece.

\emph{2:30 PM Markus\textgreater{}} Hah hah.

\emph{2:48 PM Markus\textgreater{}} Nice skunk working with me there is
irked that I keep texting.

\emph{2:49 PM Markus\textgreater{}} Just showed him this.

\emph{2:50 PM Markus\textgreater{}} He got quiet and smiled and said,
``You can keep texting.''

\emph{2:50 PM Markus\textgreater{}} Feeling slightly less stupid, but no
less sad.

\emph{3:08 PM Markus\textgreater{}} Cremation and all that goes with it
is expensive.

\emph{3:08 PM Markus\textgreater{}} I mean, not super expensive. Cheaper
than the other stuff.

\emph{3:08 PM Markus\textgreater{}} But we didn't really plan this well.

\emph{3:09 PM Markus\textgreater{}} Oh god.

\emph{3:09 PM Markus\textgreater{}} I almost made a suggestion.

\emph{3:09 PM Markus\textgreater{}} Oh god.

\emph{3:28 PM Markus\textgreater{}} You're gone.

\subsubsection*{Thursday, April 3}\label{thursday-april-3}

\emph{10:02 AM Markus\textgreater{}} You came home in a plastic bag in a
box.

\emph{10:02 AM Markus\textgreater{}} Lol

\emph{10:08 AM Markus\textgreater{}} this is dumb

\emph{10:08 AM Markus\textgreater{}} cryinf ovef a bvox

\emph{3:43 PM Markus\textgreater{}} Service Friday 4pm call Maru dad mom
mil Jenna Jeff Selene flowers 664-1140

\emph{3:43 PM Markus\textgreater{}} \ldots{}

\emph{3:44 PM Markus\textgreater{}} Thought you should know, I guess.

\emph{3:44 PM Markus\textgreater{}} Kick me from beyond the grave if I
start using this as a notepad.

\emph{3:44 PM Markus\textgreater{}} I know you would, too.

\subsubsection*{Friday, April 4}\label{friday-april-4}

\emph{9:51 PM Markus\textgreater{}} Okay.

\emph{9:51 PM Markus\textgreater{}} So.

\emph{9:51 PM Markus\textgreater{}} You know I hate your mom.

\emph{9:52 PM Markus\textgreater{}} I think that's supposed to be some
Thing, that a husband must hate his wife's mom.

\emph{9:52 PM Markus\textgreater{}} But you know that, because I'm
pretty sure you hated her too.

\emph{9:53 PM Markus\textgreater{}} I mean, you never said so to my face
or anything, but you did all you could not to be in the same room as
her.

\emph{9:53 PM Markus\textgreater{}} (I know you hate your stepdad)

\emph{9:53 PM Markus\textgreater{}} *hated

\emph{9:53 PM Markus\textgreater{}} fuck

\emph{9:54 PM Markus\textgreater{}} sorry

\emph{9:54 PM Markus\textgreater{}} \ldots{}

\emph{9:56 PM Markus\textgreater{}} sorry

\subsubsection*{Saturday, April 5}\label{saturday-april-5}

\emph{12:21 AM Markus\textgreater{}} Anyway, that bitch was there at
your service.

\emph{12:21 AM Markus\textgreater{}} Of course she was, I mean.

\emph{12:21 AM Markus\textgreater{}} But I call her a bitch because she
was.

\emph{12:22 AM Markus\textgreater{}} She made it sound like I killed
you.

\emph{12:22 AM Markus\textgreater{}} She said if her daughter had
married another cat, it would've been fine.

\emph{12:23 AM Markus\textgreater{}} But no.

\emph{12:23 AM Markus\textgreater{}} You married me.

\emph{12:23 AM Markus\textgreater{}} And I don't know how, but somehow
it became my fault that you died.

\emph{12:24 AM Markus\textgreater{}} We went from crying together over
supermarket snack trays to terse arguments in surprisingly little time.

\emph{12:24 AM Markus\textgreater{}} She thought that if she'd married a
cat, she would've had kids and a happier life.

\emph{12:25 AM Markus\textgreater{}} I don't know where the cancer came
in, but she was convinced that this was somehow the cause of it.

\emph{12:26 AM Markus\textgreater{}} Marry a coyote? Get cancer.

\emph{12:26 AM Markus\textgreater{}} I mean, duh.

\emph{12:26 AM Markus\textgreater{}} She really wanted grandkits.

\emph{12:26 AM Markus\textgreater{}} (didn't tell her about the
ligation. You never did, so I promised I wouldn't)

\emph{12:26 AM Markus\textgreater{}} Anyway.

\emph{12:27 AM Markus\textgreater{}} I'm really upset.

\emph{12:27 AM Markus\textgreater{}} The service wasn't meaningful. It
was boring.

\emph{12:27 AM Markus\textgreater{}} Your mother aside, I think that's
the most upsetting thing.

\emph{12:27 AM Markus\textgreater{}} Your service was boring.

\emph{12:27 AM Markus\textgreater{}} I got home at nine or whatever, and
I just sat on the bed.

\emph{12:28 AM Markus\textgreater{}} I fell asleep in my nice clothes.

\emph{12:28 AM Markus\textgreater{}} Now I'm sitting on the bathroom
floor waiting for the water to heat up, and it's already hot, but I'm
still on my phone, just like you hate.

\emph{12:28 AM Markus\textgreater{}} *hated

\subsubsection*{Sunday, April 6}\label{sunday-april-6}

\emph{10:10 AM Markus\textgreater{}} Thank you for leaving a will.

\emph{11:12 AM Markus\textgreater{}} Met with MiL again, this time with
lawyers.

\emph{11:12 AM Markus\textgreater{}} Thank you for leaving me
everything.

\emph{11:12 AM Markus\textgreater{}} Even your ashes. Your mom hated
that most, I think.

\emph{11:13 AM Markus\textgreater{}} You left me with all of our debts,
but you left her with nothing.

\emph{11:13 AM Markus\textgreater{}} Surprised I don't feel
self-righteous or whatever. Just resolute. I didn't ``win''. If anyone
won, it was you.

\emph{11:14 AM Markus\textgreater{}} But if I'd had to cede to your mom
and stepdad that would have hurt.

\emph{11:16 AM Markus\textgreater{}} Thank you.

\subsubsection*{Monday, April 7}\label{monday-april-7}

\emph{2:18 PM Markus\textgreater{}} I formed your ashes into a rock by
mixing them with water and baking until they got hard, and then I
skipped it across the university pond.

\emph{2:19 PM Markus\textgreater{}} Kidding.

\emph{2:19 PM Markus\textgreater{}} I know you asked for that.

\emph{2:19 PM Markus\textgreater{}} I also didn't dump your ashes out in
the parking lot of your office.

\emph{2:20 PM Markus\textgreater{}} I didn't dump them in the plaza
fountain or flush them down a toilet at your office, either.

\emph{2:21 PM Markus\textgreater{}} Sorry. All your last wishes gone to
waste.

\emph{2:24 PM Markus\textgreater{}} I took your ashes and drove up into
the hills, because I decided this wasn't for you, it was for me.

\emph{2:25 PM Markus\textgreater{}} I'm sorry.

\emph{2:27 PM Markus\textgreater{}} I drove up into the hills until I
got to one of those pull-aside rest stops, and I walked down to the
river there, and I just sat for a bit and cried.

\emph{2:27 PM Markus\textgreater{}} And I wasn't thinking.

\emph{2:28 PM Markus\textgreater{}} And I cut open the bag of ashes and
scooped a few pawfuls of water in there and mixed it up to a sort of
smoothie consistency.

\emph{2:29 PM Markus\textgreater{}} And I poured it out on the river
bank.

\emph{2:29 PM Markus\textgreater{}} And I kinda mixed and kneaded and
massaged it into the river mud.

\emph{2:29 PM Markus\textgreater{}} And I just kinda cried and gave you
up bit by bit.

\emph{2:30 PM Markus\textgreater{}} The water would splash up on the
banks and I just let you be carried away bit by bit.

\emph{2:30 PM Markus\textgreater{}} Until there was nothing left but a
messy spot on the shore.

\emph{2:30 PM Markus\textgreater{}} And I washed my paws.

\emph{2:30 PM Markus\textgreater{}} And it was super cold.

\emph{2:30 PM Markus\textgreater{}} And I only had my jeans to dry my
paws on, so I just sat there like an idiot.

\emph{2:30 PM Markus\textgreater{}} Crying and puffing into my paws to
try and warm them up.

\emph{2:31 PM Markus\textgreater{}} You'll be proud to know that it was
disgusting.

\emph{2:31 PM Markus\textgreater{}} there's you all over that river bank

\emph{2:31 PM Markus\textgreater{}} and all over my paws

\emph{2:31 PM Markus\textgreater{}} and stuck in my fur

\emph{2:31 PM Markus\textgreater{}} and probably on my muzzle

\emph{2:31 PM Markus\textgreater{}} and the steering wheel of the car

\emph{2:31 PM Markus\textgreater{}} and the doorknib

\emph{2:31 PM Markus\textgreater{}} asnd your all over now

\emph{2:32 PM Markus\textgreater{}} and i thought I was saying goodbye

\emph{2:32 PM Markus\textgreater{}} and your still here

\emph{2:32 PM Markus\textgreater{}} i miss you

\emph{2:32 PM Markus\textgreater{}} i love you

\subsubsection*{Tuesday, April 8}\label{tuesday-april-8}

\emph{12:01 PM Markus\textgreater{}} Okay.

\emph{12:01 PM Markus\textgreater{}} So.

\emph{12:01 PM Markus\textgreater{}} Not only was that a mess, but it
was apparently illegal.

\emph{12:03 PM Markus\textgreater{}} I slept and feel better, and now
I'm giggling like an idiot over the fact that I did something meaningful
to me, and it turned out I was breaking the law the whole time. You're
not supposed to scatter ashes in water.

\emph{12:03 PM Markus\textgreater{}} (And even if it were legal, there's
probably a better way to do it than what I did.)

\emph{12:04 PM Markus\textgreater{}} So there you have it. I thought I
was going to snub your goofy wishes but your idiot husband wound up
going along with them all the same.

\subsubsection*{Wednesday, April 9}\label{wednesday-april-9}

\emph{9:41 AM Markus\textgreater{}} Back at work today.

\emph{9:41 AM Markus\textgreater{}} Everyone was nice.

\emph{9:41 AM Markus\textgreater{}} Calm.

\emph{10:21 AM Markus\textgreater{}} And I do feel better, PS. I think I
got more out of that than I can put into words.

\subsubsection*{Thursday, April 10}\label{thursday-april-10}

\emph{4:54 PM Markus\textgreater{}} I miss you, sweetheart.

\emph{4:54 PM Markus\textgreater{}} I remember when you got diagnosed
and we both had a good cry over it, but then it all turned out to be so
boring after that.

\emph{4:55 PM Markus\textgreater{}} It was hard having that hang over us
both, I know, but it all got routine

\emph{4:56 PM Markus\textgreater{}} Awful, but routine

\emph{4:56 PM Markus\textgreater{}} And then things got better.

\emph{4:56 PM Markus\textgreater{}} Until they didn't.

\emph{4:56 PM Markus\textgreater{}} Everything got so bad so quickly.

\emph{4:56 PM Markus\textgreater{}} Your mom didn't even come and see
you.

\emph{4:56 PM Markus\textgreater{}} Oh well.

\emph{4:58 PM Markus\textgreater{}} Starting on the rest of your will
and such tonight.

\emph{5:20 PM Markus\textgreater{}} Looks like you just left me
anything.

\emph{5:20 PM Markus\textgreater{}} Which is good.

\emph{5:22 PM Markus\textgreater{}} When my sister died, everything was
a mess, because she had two wills.

\emph{5:23 PM Markus\textgreater{}} Neither had been updated.

\emph{5:24 PM Markus\textgreater{}} Oh god, and her husband and my
parents were a mess trying to figure things out with the house and title
and stuff.

\emph{5:24 PM Markus\textgreater{}} Renting is making things easier.

\emph{5:24 PM Markus\textgreater{}} And your ``everything to Markus''
will.

\emph{5:24 PM Markus\textgreater{}} Your mom's pissed.

\subsubsection*{Friday, April 11}\label{friday-april-11}

\emph{6:43 PM Markus\textgreater{}} Okay, your mom's -really- pissed.

\emph{6:43 PM Markus\textgreater{}} She says that a lot of your stuff is
rightfully hers.

\emph{6:44 PM Markus\textgreater{}} I've yet to find anything that could
rightfully be called hers.

\emph{6:46 PM Markus\textgreater{}} She wants to go through your desk
with me, and I don't know what to say to her. She says she's got books
and papers that are hers in there, and I don't know what to do about
that.

\emph{6:46 PM Markus\textgreater{}} I wish you were here to tell her
off.

\emph{6:48 PM Markus\textgreater{}} She keeps sending me messages in all
caps that are half about your stuff and half about how I'm the wrong
species, and that you deserved a cat who would take care of her and give
her grandkits. She says I'm garbage and disreputable and that I
tarnished the reputation of your family.

\emph{6:48 PM Markus\textgreater{}} Which I don't get.

\emph{6:48 PM Markus\textgreater{}} You guys aren't famous

\emph{6:48 PM Markus\textgreater{}} \emph{Forwarded message from Xiuying
(Lee Mom)} GARBAGE YOUR GARBAGE I CANT BELIEVE YOUD KEEP ME FROM MY
DAUGHTER

\emph{6:48 PM Markus\textgreater{}} \emph{Forwarded message from Xiuying
(Lee Mom)} You took our name and DRAGGED IT THROUGH MUD YOU TOOK LI AND
DRAGGED HER THROUGH MUD GIVE ME WHATS MINE

\emph{6:49 PM Markus\textgreater{}} Though I guess I did drag you
throuugh the mud.

\emph{6:49 PM Markus\textgreater{}} Har Har

\emph{6:50 PM Markus\textgreater{}} I don't know what she means about
keeping you from her.

\emph{6:50 PM Markus\textgreater{}} I thought I knew what hatred felt
like, but damn, Lee.

\emph{6:50 PM Markus\textgreater{}} How did so sane a cat come from so
crazy a family?

\emph{6:52 PM Markus\textgreater{}} I was going to go through your
clothes first, because those felt like they'd be easy, but I'm going to
go through your desk instead.

\subsubsection*{Sunday, April 13}\label{sunday-april-13}

\emph{9:03 AM Markus\textgreater{}} There is literally nothing in your
desk of interest.

\emph{9:04 AM Markus\textgreater{}} I took all our bills and boxed up
everything and gave it to your mom.

\emph{9:05 AM Markus\textgreater{}} Seriously. You had some notes
printed out about research, two planners, and 12 blank books.

\emph{9:05 AM Markus\textgreater{}} I counted.

\emph{9:05 AM Markus\textgreater{}} I swear to god, Lee. I miss the hell
out of you, but 12 blank books?

\emph{9:06 AM Markus\textgreater{}} I just kept your laptop.

\subsubsection*{Monday, April 14}\label{monday-april-14}

\emph{4:21 PM Markus\textgreater{}} Your mom's yelling at me again.

\emph{4:21 PM Markus\textgreater{}} She wants to go through my papers
now, too. And my books?

\emph{4:22 PM Markus\textgreater{}} I love you and miss you so much. You
were always so good at telling her to go away. She won't listen to me at
all.

\subsubsection*{Tuesday, April 15}\label{tuesday-april-15}

\emph{3:53 PM Markus\textgreater{}} Your stepdad is meeting with me
after work.

\emph{3:53 PM Markus\textgreater{}} We're meeting at a coffee shop,
don't worry.

\emph{5:23 PM Markus\textgreater{}} WHAT THE FUCK WHAT THE FUCK

\emph{5:24 PM Markus\textgreater{}} Your stepdad was nice enough, we
talked about memories of you. He said he knew about your feelings toward
him, and that he wished he'd done better by you.

\emph{5:24 PM Markus\textgreater{}} But then I got home and YOUR MOM HAS
BEEN IN OUR APARTMENT

\emph{5:25 PM Markus\textgreater{}} I guess I got home faster than they
thought, but I think your stepdad was keeping me occupied while your mom
BROKE INTO OUR PLACE

\emph{5:26 PM Markus\textgreater{}} I ran into her in front of the
building and she started yelling and hollering at me, and I was so
confused.

\emph{5:26 PM Markus\textgreater{}} She said I was hiding your stuff
from her and that she would be calling her lawyer.

\emph{5:28 PM Markus\textgreater{}} AND THEN SHE HIT ME

\emph{5:28 PM Markus\textgreater{}} SHE SLAPPED ME

\emph{5:29 PM Markus\textgreater{}} I yelled that I was going to call
the police when Jun screeched up in a car and she jumped in and drove
off

\emph{5:29 PM Markus\textgreater{}} What the FUCK

\emph{5:30 PM Markus\textgreater{}} I'm calling the cops to get her away
from here

\emph{5:58 PM Markus\textgreater{}} They took a report and said to call
again if she shows up, that way they can talk with her, and worst case,
then I can get a restraining order.

\emph{5:59 PM Markus\textgreater{}} She trashed our bookshelf and dug
through our closets.

\emph{6:00 PM Markus\textgreater{}} I don't think anything's missing.
It's just a mess.

\emph{6:00 PM Markus\textgreater{}} The cop took a report, though.

\emph{6:00 PM Markus\textgreater{}} Don't know how she got a key.

\subsubsection*{Wednesday, April 16}\label{wednesday-april-16}

\emph{11:03 AM Markus\textgreater{}} Now she wants your laptop.

\emph{11:03 AM Markus\textgreater{}} I had it with me at coffee even.

\emph{11:04 AM Markus\textgreater{}} I don't have the password, though,
no idea what she'd do with it.

\emph{11:32 AM Markus\textgreater{}} I think I may destroy it.

\subsubsection*{Friday, April 18}\label{friday-april-18}

\emph{11:03 PM Markus\textgreater{}} I miss you so much, Lee.

\emph{11:04 PM Markus\textgreater{}} I think it's really starting to hit
me.

\emph{11:04 PM Markus\textgreater{}} You're gone.

\emph{11:04 PM Markus\textgreater{}} You're dead.

\emph{11:04 PM Markus\textgreater{}} You're never coming back.

\emph{11:05 PM Markus\textgreater{}} Your mom went quiet, and now I'm
finally starting to digest this.

\emph{11:08 PM Markus\textgreater{}} I wish I could take your place.

\emph{11:08 PM Markus\textgreater{}} I wish I were dead.

\emph{11:08 PM Markus\textgreater{}} I wish I was gone.

\emph{11:11 PM Markus\textgreater{}} Oh god.

\emph{11:11 PM Markus\textgreater{}} I keep getting stcuk crying and

\emph{11:11 PM Markus\textgreater{}} its so hrad to keep going sometimes

\emph{11:11 PM Markus\textgreater{}} i want to die without yowue

\emph{11:12 PM Markus\textgreater{}} oh god

\emph{11:12 PM Markus\textgreater{}} lee

\emph{11:12 PM Markus\textgreater{}} oh god

\subsubsection*{Saturday, April 19}\label{saturday-april-19}

\emph{12:44 AM Markus\textgreater{}} I miss you

\subsubsection*{Sunday, April 20}\label{sunday-april-20}

\emph{2:21 PM Markus\textgreater{}} I can't believe you set your
password to that!

\emph{2:21 PM Markus\textgreater{}} I could spank you for that, miss
prissy whiskers.

\emph{2:21 PM Markus\textgreater{}} You're such a dork \textless{}3

\subsubsection*{Monday, April 21}\label{monday-april-21}

\emph{1:02 AM Markus\textgreater{}} Lee

\emph{1:02 AM Markus\textgreater{}} Lee I'm so sorry

\emph{1:02 AM Markus\textgreater{}} I'm so sorry

\emph{1:02 AM Markus\textgreater{}} I'm reading it now

\emph{9:20 AM Markus\textgreater{}} stayed home

\emph{9:21 AM Markus\textgreater{}} cant stop crying

\emph{9:21 AM Markus\textgreater{}} sorry

\emph{9:21 AM Markus\textgreater{}} im so sorry lee

\emph{4:11 PM Markus\textgreater{}} I could kill him

\emph{4:11 PM Markus\textgreater{}} I WOULD fucking kill him right now

\emph{4:28 PM Markus\textgreater{}} I would destroy him and your mom for
all they've done if I could

\subsubsection*{Tuesday, April 22}\label{tuesday-april-22}

\emph{12:31 AM Markus\textgreater{}} I won't

\emph{12:31 AM Markus\textgreater{}} But I could.

\emph{12:31 AM Markus\textgreater{}} I'm sorry Lee

\emph{12:41 AM Markus\textgreater{}} I wish I could go back in time and
help you.

\subsubsection*{Wednesday, April 23}\label{wednesday-april-23}

\emph{6:43 PM} Lee sent you a file ``should-I-pass.txt''

\emph{6:43 PM Markus\textgreater{}} Sorry, wanted that on my end, so I
sent it from your account.

\emph{6:48 PM Markus\textgreater{}} Apparently your account expires
after six months inactivity.

\emph{6:48 PM Markus\textgreater{}} I wonder if I should keep logging on
once a month to keep it active?

\emph{6:49 PM Markus\textgreater{}} Or

\emph{6:49 PM Markus\textgreater{}} Maybe I should let it expire

\emph{6:49 PM Markus\textgreater{}} And set that as a date to let you go

\emph{6:49 PM Markus\textgreater{}} Oh god Lee

\emph{6:52 PM Markus\textgreater{}} oh god

\emph{6:52 PM Markus\textgreater{}} i miss you

\emph{6:52 PM Markus\textgreater{}} you made me whole

\emph{6:57 PM Markus\textgreater{}} don't want to tgo on weifthout oyu

\emph{6:57 PM Markus\textgreater{}} sdf

\emph{7:20 PM Markus\textgreater{}} sorry

\subsubsection*{Friday, April 25}\label{friday-april-25}

\emph{5:10 PM Markus\textgreater{}} I'm calling your mom and Jun today.

\emph{5:11 PM Markus\textgreater{}} I'm going to invite them over this
weekend and confront them.

\emph{5:12 PM Markus\textgreater{}} You're right in that it's just a
document. No signature, no verification.

\emph{5:12 PM Markus\textgreater{}} Biot I need to do right by yuo/ i
miss yuo, and i want to do right by you

\emph{5:12 PM Markus\textgreater{}} you tolfd me not to fight

\emph{5:12 PM Markus\textgreater{}} and i wont

\emph{5:12 PM Markus\textgreater{}} im just goin to tell thm i know

\emph{5:12 PM Markus\textgreater{}} tey need to know that someone else
knowds

\subsubsection*{Saturday, April 26}\label{saturday-april-26}

\emph{11:01 AM Markus\textgreater{}} Your mom and Jun are coming over
tomorrow.

\emph{11:01 AM Markus\textgreater{}} I think I'm going to just tell them
plain and simple, what I found.

\emph{11:02 AM Markus\textgreater{}} I hate them. I loathe them.

\emph{11:03 AM Markus\textgreater{}} But I owe it to you to not make it
a big fight.

\emph{11:03 AM Markus\textgreater{}} Not on my part, at least.

\emph{11:03 AM Markus\textgreater{}} If they get angry, whatever. I'm
just going to read it.

\emph{11:03 AM Markus\textgreater{}} Most of it.

\emph{11:03 AM Markus\textgreater{}} Read it and watch and make sure
they understand that I know.

\emph{11:08 AM Markus\textgreater{}} I'm starting to second guess this.

\emph{11:18 AM Markus\textgreater{}} Like, obviously I'm upset, and
obviously you wanted me to know that your parents are awful.

\emph{11:18 AM Markus\textgreater{}} But I'm starting to second guess
what I'll get out of this.

\emph{11:19 AM Markus\textgreater{}} Even when I said I wouldn't make it
a big fight, I was still coming at it from a vengeance standpoint.

\emph{11:19 AM Markus\textgreater{}} I wanted to hurt them.

\emph{11:20 AM Markus\textgreater{}} Still do.

\emph{11:20 AM Markus\textgreater{}} I just don't think that's totally
right.

\emph{2:18 PM Markus\textgreater{}} I thought about it more, and I think
I still need to share what you wrote.

\emph{2:19 PM Markus\textgreater{}} It'll hurt them, and it'll probably
hurt me more than it already has.

\emph{2:19 PM Markus\textgreater{}} But I don't think any of us will be
able to start grieving with the current state.

\emph{2:19 PM Markus\textgreater{}} \ldots{}I'm going to call Dr Maura.

\emph{2:48 PM Markus\textgreater{}} I wasn't expecting her to get back
to me, but she actually picked up her phone on the first ring.

\emph{2:48 PM Markus\textgreater{}} I don't know why that strikes me as
weird.

\emph{2:49 PM Markus\textgreater{}} We talked for a bit about what I
should do.

\emph{2:40 PM Markus\textgreater{}} I told her about the letter you
left. She agrees I should share with your parents, if only to give
closure, like I said before.

\emph{2:50 PM Markus\textgreater{}} She says she's worried about me and
wants to talk more soon.

\emph{2:58 PM Markus\textgreater{}} I told her about this, too.

\emph{2:58 PM Markus\textgreater{}} About sending you messages, even
though you'll never respond. Just talking to you.

\emph{3:00 PM Markus\textgreater{}} She says it can be a healthy coping
mechanism, but only to a point, and that I shouldn't lean on it too
much, or I won't stop grieving.

\emph{3:00 PM Markus\textgreater{}} Makes sense.

\emph{3:01 PM Markus\textgreater{}} I promised I'd let your account
expire, and would do my best to start moving on sooner than that.

\emph{3:02 PM Markus\textgreater{}} We also talked about getting through
grief in stages. She says there are a few different lists of `stages of
grief', but that they're all just loose guidelines.

\emph{3:03 PM Markus\textgreater{}} She says it sounds like I'm going
through some healthy stuff, but that she wants to meet again to make
sure I keep going.

\emph{3:05 PM Markus\textgreater{}} She says that things could wear me
out and make me depressed, or that things could be super easy and I
could finish all the work I need to do, and realize you're truly gone
and get depressed.

\emph{3:05 PM Markus\textgreater{}} I countered that I was depressed
now, but I'm not sure about that anymore. I think I'm sad, and that
depression will come soon.

\emph{3:06 PM Markus\textgreater{}} I'm sad, Lee.

\emph{3:06 PM Markus\textgreater{}} I'm sad and I'm tired and I want you
back.

\emph{3:06 PM Markus\textgreater{}} I'm sitting on the floor waiting for
the shower again. My tail's fallen asleep. I'm gonna go before you get
mad, even if that isn't possible.

\emph{3:07 PM Markus\textgreater{}} I don't care if that's me grieving
in an unhealthy manner or anything, I'm going to go before you get mad.

\emph{3:07 PM Markus\textgreater{}} I'll try to only write again after
things with your parents.

\subsubsection*{Sunday, April 27}\label{sunday-april-27}

\emph{4:05 PM Markus\textgreater{}} This is weird

\emph{4:21 PM Markus\textgreater{}} Taking a break, this is still weird.

\emph{5:33 PM Markus\textgreater{}} WHAT THE FUCK, LEE

\emph{5:33 PM Markus\textgreater{}} THE POLICE JUST ARRESTED YOUR MOM

\emph{5:33 PM Markus\textgreater{}} What the FUCK

\emph{5:43 PM Markus\textgreater{}} Gave the police my report.

\emph{5:43 PM Markus\textgreater{}} What the fuck.

\emph{5:46 PM Markus\textgreater{}} Okay, writing this all down before I
forget.

\emph{5:47 PM Markus\textgreater{}} We met at that same coffee shop I
met Jun at before. The Book and the Bean. It's got a bookstore in the
back, I think we've been there before.

\emph{5:47 PM Markus\textgreater{}} Only this time, Jun looked sincerely
upset and sorry.

\emph{5:47 PM Markus\textgreater{}} Like

\emph{5:48 PM Markus\textgreater{}} I don't know how to put it. He
looked upset for me, not at me?

\emph{5:48 PM Markus\textgreater{}} And your mom looked extra pissed.

\emph{5:48 PM Markus\textgreater{}} And I don't know what happened, like
maybe they got into a fight before getting here?

\emph{5:49 PM Markus\textgreater{}} So we were really quiet and Jun was
looking down at his paws a lot and your mom was glaring at me a lot and
I was tired.

\emph{5:49 PM Markus\textgreater{}} I hate coffee, but I got a mocha or
whatever, because Lee, I've just been so tired.

\emph{5:50 PM Markus\textgreater{}} this isn't helping, i'm sorry.

\emph{5:50 PM Markus\textgreater{}} i miss yuo

\emph{7:32 PM Markus\textgreater{}} Sorry, I'll try again and get more
to the point.

\emph{7:33 PM Markus\textgreater{}} So the more I thought about what I
had planned, the less I really wanted to go through with it. So I tried
to just sit there and talk with your parents about you and all the good
time and stuff.

\emph{7:33 PM Markus\textgreater{}} I tried earnestly to patch things
up, but your mom just told me she remembered things differently.

\emph{7:34 PM Markus\textgreater{}} And it was stupid, because I could
tell Jun was sad.

\emph{7:34 PM Markus\textgreater{}} After everything.

\emph{7:34 PM Markus\textgreater{}} After everything in your letter and
after the dumbass break-in attempt and everything.

\emph{7:34 PM Markus\textgreater{}} He was sad.

\emph{7:35 PM Markus\textgreater{}} He would smile a little at a memory
I brought up, then look off away from your mom like he wasn't going to
cry.

\emph{7:35 PM Markus\textgreater{}} And then your mom would get huffy,
and he'd nod at her, and go back to looking at his paws.

\emph{7:35 PM Markus\textgreater{}} I don't know.

\emph{7:36 PM Markus\textgreater{}} I feel like he's as exhausted as I
am, but for different reasons.

\emph{7:36 PM Markus\textgreater{}} So we took a little break because I
felt like he and I were headed for a different conversation than your
mom.

\emph{7:36 PM Markus\textgreater{}} So we got some more coffees and
such.

\emph{7:36 PM Markus\textgreater{}} And I just kinda buckled down and
did it.

\emph{7:36 PM Markus\textgreater{}} Before, when I was feeling more
vengeful, I thought maybe I'd print off some copies and hand it to them
all formally and wither them under my glare or whatever.

\emph{7:37 PM Markus\textgreater{}} But I just sat down and told them
about the file and how I found it.

\emph{7:37 PM Markus\textgreater{}} How you'd written it to me, and
locked your computer with a password for me.

\emph{7:37 PM Markus\textgreater{}} oh god haha

\emph{7:37 PM Markus\textgreater{}} fuck

\emph{8:01 PM Markus\textgreater{}} I'm supposed to keep it together to
finish this.

\emph{8:02 PM Markus\textgreater{}} How you always called me `crazy
face' but only over text because it sounded silly to say.

\emph{8:02 PM Markus\textgreater{}} And how you set that as your
password, and addressed the letter to me.

\emph{8:03 PM Markus\textgreater{}} (I didn't tell them I called you
`prissy whiskers' in return.)

\emph{8:03 PM Markus\textgreater{}} And I told them what the letter was
about.

\emph{8:04 PM Markus\textgreater{}} And as I started to talk about all
that your dad had done and all that your mom and Jun did to cover it up
I started to loosen things up

\emph{8:04 PM Markus\textgreater{}} And I started to feel lighter.

\emph{8:04 PM Markus\textgreater{}} And I started to wake up.

\emph{8:04 PM Markus\textgreater{}} And your mom started looking strange
and scared.

\emph{8:04 PM Markus\textgreater{}} And Jun was actively crying now

\emph{8:05 PM Markus\textgreater{}} and don't know

\subsubsection*{Monday, April 28}\label{monday-april-28}

\emph{12:03 AM Markus\textgreater{}} Sorry

\emph{12:03 AM Markus\textgreater{}} And then I started talking about
your mom and her attempts to cope and how she blamed you, and she lost
her mind.

\emph{12:04 AM Markus\textgreater{}} It was like something snapped.

\emph{12:04 AM Markus\textgreater{}} That sounds cliche, but it's true.
Like, she was gripping the table tight and all set to pounce, and
whatever tension was in her muscles snapped violently and she threw the
table.

\emph{12:05 AM Markus\textgreater{}} It sounds so fucking ridiculous to
say it now, hah

\emph{12:05 AM Markus\textgreater{}} It was scary as hell then, though.
She threw the whole table to the side and then threw her coffee cup
(empty) at my face and then hit Jun with her purse.

\emph{12:06 AM Markus\textgreater{}} And I thought she was done because
everyone was shocked and staring at us.

\emph{12:06 AM Markus\textgreater{}} But then she started shrieking and
ran to the book shelf we were sitting by and started throwing books at
us.

\emph{12:06 AM Markus\textgreater{}} (paperbacks don't hurt that much,
but hardcovers do)

\emph{12:06 AM Markus\textgreater{}} And Jun seemed to snap out of it
too and jumped up to grab her.

\emph{12:07 AM Markus\textgreater{}} He grabbed her around the middle
and sort of lifted her up and turned around so that he was between us.

\emph{12:07 AM Markus\textgreater{}} This is dumb, but it was sorta like
when I'd pick you up when you were being a fuss and carry you off to
bed, laughing.

\emph{12:07 AM Markus\textgreater{}} So I guess that runs in the family
in a creepy sort of way.

\emph{12:07 AM Markus\textgreater{}} Anyway.

\emph{12:07 AM Markus\textgreater{}} Jun got her turned around and
hauled her outside, hollering at us to call the ambulance on the way
out.

\emph{12:08 AM Markus\textgreater{}} And the badger at the bar already
had the police on the phone, so she added something about an ambulance.

\emph{12:08 AM Markus\textgreater{}} And then the police were there and
the fire truck because they're the first responders.

\emph{12:08 AM Markus\textgreater{}} And they fucking handcuffed your
mom and put her in the back of the cruiser.

\emph{12:08 AM Markus\textgreater{}} And no one was hurt, so the fire
truck left

\emph{12:08 AM Markus\textgreater{}} And the police came in and started
taking reports as Jun and I and the badger started picking up the books
and putting them back.

\emph{12:09 AM Markus\textgreater{}} And all the while your mom was
alternating between sobbing and throwing a hissing fit in the back of
the cop car.

\emph{12:09 AM Markus\textgreater{}} And then I gave my report, and then
Jun did

\emph{12:10 AM Markus\textgreater{}} And I just kinda waved at him and
left while he was giving his report.

\emph{12:10 AM Markus\textgreater{}} Because how awkward of a goodbye
would that have been?

\emph{1:21 PM Markus\textgreater{}} I met with Dr.~Maura today, and we
talked about the weekend a lot.

\emph{1:21 PM Markus\textgreater{}} She says that she thinks I did the
right thing, and that this is a turning point in our relationship

\emph{1:22 PM Markus\textgreater{}} our=me and your parents

\emph{1:22 PM Markus\textgreater{}} And she said that it's time to work
on letting you go.

\emph{1:23 PM Markus\textgreater{}} She said that it's not because my
relationship with you has changed, or if it has, it's gotten stronger.
She says that it's important that I use the energy I've had when it came
to your parents and your estate and put it to work on myself.

\emph{1:23 PM Markus\textgreater{}} And I told her how tired I was and
she smiled and said that I felt better after giving the letter to your
parents because that was the first bit of letting you go.

\emph{1:24 PM Markus\textgreater{}} And I think she's right.

\emph{1:24 PM Markus\textgreater{}} I think I'd been holding you close
to keep you safe from what I perceived as danger.

\emph{1:24 PM Markus\textgreater{}} Rightfully so!

\emph{1:24 PM Markus\textgreater{}} But your mom was right in that I was
keeping you from her, to some extent, and largely at your request.

\emph{1:24 PM Markus\textgreater{}} So I think I need to start working
on that.

\emph{1:24 PM Markus\textgreater{}} I'll never forget you

\emph{1:25 PM Markus\textgreater{}} And I'll never stop loving you

\emph{1:25 PM Markus\textgreater{}} and i'll never stop missing you

\emph{1:25 PM Markus\textgreater{}} but she's right

\emph{1:35 PM Markus\textgreater{}} I need to start working on myself,
too.

\subsubsection*{Wednesday, May 1}\label{wednesday-may-1}

\emph{9:38 PM Markus\textgreater{}} I gave it a break for a day and
spent yesterday cleaning the apartment.

\emph{9:40 PM Markus\textgreater{}} Well, after work. I'm back there
full time, and that's starting to feel normal again.

\emph{9:40 PM Markus\textgreater{}} But after, I tore down your desk and
turned it into a bookshelf, best I could.

\emph{9:40 PM Markus\textgreater{}} Not sure how long that will last. I
want to set up my gaming rig there, just to piss you off \textless{}3

\emph{9:44 PM Markus\textgreater{}} Anyway, I'm going to keep doing this
less and less.

\emph{9:44 PM Markus\textgreater{}} This texting you.

\emph{9:44 PM Markus\textgreater{}} I already threw away your phone and
wiped your laptop.

\emph{9:45 PM Markus\textgreater{}} So I don't have access to your
account anymore, and it'll expire.

\emph{9:45 PM Markus\textgreater{}} (and yes, I did try `crazy face',
but you hadn't changed it, which is good, miss prissy whiskers.)

\emph{9:45 PM Markus\textgreater{}} So\ldots{}

\emph{9:45 PM Markus\textgreater{}} I'll contact you in a week and see
where things go from there.

\subsubsection*{Tuesday, May 7}\label{tuesday-may-7}

\emph{6:11 PM Markus\textgreater{}} I

\emph{6:11 PM Markus\textgreater{}} shit, tomorrow

\subsubsection*{Wednesday, May 8}\label{wednesday-may-8}

\emph{7:58 PM Markus\textgreater{}} I was going to text you yesterday
because I got a call from Jun.

\emph{7:59 PM Markus\textgreater{}} Your mom was released that same
weekend, of course, but she got charged and had to go do a trial or
something and has community service and therapy.

\emph{7:59 PM Markus\textgreater{}} And Jun sounded like he'd perked up
some, too.

\emph{8:00 PM Markus\textgreater{}} So we talked about you and sort of
had the conversation that we were going to have without your mom.

\emph{8:00 PM Markus\textgreater{}} You know, memories and good stuff
and rebuilding bridges.

\emph{8:01 PM Markus\textgreater{}} And he said that he'll probably be
getting a divorce from your mom after the letter (I emailed it) and
coming to realize just how much your mom was after him as well as you,
keeping you in her service and using anxiety as a tool.

\emph{8:01 PM Markus\textgreater{}} So that was good.

\emph{8:02 PM Markus\textgreater{}} Or maybe not good, I imagine
divorces suck.

\emph{8:18 PM Markus\textgreater{}} Anyway, it's been a week of caring
for myself.

\emph{8:18 PM Markus\textgreater{}} I did move the gaming rig.

\emph{8:18 PM Markus\textgreater{}} Sorry not sorry.

\emph{8:19 PM Markus\textgreater{}} And I started putting the stuff that
was yours but worth keeping into a few boxes, which are now in my
closet, and the rest of your stuff is gone.

\emph{8:20 PM Markus\textgreater{}} Well, there's probably more, but
it's gone.

\emph{8:20 PM Markus\textgreater{}} And hell, I miss you, Lee.

\emph{8:22 PM Markus\textgreater{}} Until next week \textless{}3

\subsubsection*{Wednesday, May 15}\label{wednesday-may-15}

\emph{5:07 PM Markus\textgreater{}} I met with Dr Maura again today.

\emph{5:07 PM Markus\textgreater{}} It was REALLY good.

\emph{5:07 PM Markus\textgreater{}} We were talking a lot about the
stages of crisis and such.

\emph{5:07 PM Markus\textgreater{}} Which we've done before, of course.

\emph{5:08 PM Markus\textgreater{}} And my role in it all.

\emph{5:08 PM Markus\textgreater{}} How it's sometimes my choice to move
between stages.

\emph{5:08 PM Markus\textgreater{}} Like, I can park myself in
depression for a while.

\emph{5:09 PM Markus\textgreater{}} Or anger, or bargaining, or
whatever.

\emph{5:09 PM Markus\textgreater{}} I could just stay there because it's
easier to stay than moving on.

\emph{5:09 PM Markus\textgreater{}} Not that those stages aren't
necessary!

\emph{5:10 PM Markus\textgreater{}} Just that it takes effort to leave
them when you're ready.

\emph{5:10 PM Markus\textgreater{}} And I'm trying.

\emph{8:22 PM Markus\textgreater{}} We were pretty spot on in terms of
music tastes, you know that?

\emph{8:22 PM Markus\textgreater{}} Going through your library.

\emph{8:22 PM Markus\textgreater{}} Sorry not sorry \textless{}3

\emph{8:28 PM Markus\textgreater{}} We could've made a rockin' band, you
know?

\emph{8:28 PM Markus\textgreater{}} Miss Prissy Whiskers and the Crazy
Faces.

\emph{8:28 PM Markus\textgreater{}} Though that sounds like an old punk
band.

\emph{8:28 PM Markus\textgreater{}} And we seem to have done mostly
prog.

\emph{8:28 PM Markus\textgreater{}} \ldots{}

\emph{8:29 PM Markus\textgreater{}} And neither of us played any
instruments

\emph{8:29 PM Markus\textgreater{}} So maybe not a good band.

\subsubsection*{Thursday, May 16}\label{thursday-may-16}

\emph{12:38 AM Markus\textgreater{}} i miss you

\emph{12:38 AM Markus\textgreater{}} i love you

\emph{8:22 AM Markus\textgreater{}} Sad night last night.

\emph{8:23 AM Markus\textgreater{}} Taking Maura's words to heart.

\emph{8:23 AM Markus\textgreater{}} Going to choose to go to work.

\emph{8:23 AM Markus\textgreater{}} Choose to get better.

\emph{8:23 AM Markus\textgreater{}} Holding off until tomorrow, if I
can.

\emph{11:01 PM Markus\textgreater{}} This needs to stop.

\emph{11:12 AM Markus\textgreater{}} I think it's time.

\subsubsection*{Friday, May 24}\label{friday-may-24}

\emph{6:58 PM Markus\textgreater{}} I miss you, Lee.

\emph{6:58 PM Markus\textgreater{}} I always will, and I'll always love
you.

\emph{6:58 PM Markus\textgreater{}} But you're gone.

\emph{6:59 PM Markus\textgreater{}} You're gone now, and I'm working to
find a way to live with that.

\emph{6:59 PM Markus\textgreater{}} I've been slowly washing the
apartment of your presence.

\emph{7:03 Markus\textgreater{}} Not that you'll be gone entirely, of
course. I have your picture in a few places.

\emph{7:03 Markus\textgreater{}} But I got rid of all the stuff that was
-yours-.

\emph{7:03 Markus\textgreater{}} and washed the bedding several times.

\emph{7:04 PM Markus\textgreater{}} To get rid of the smell of you.

\emph{7:06 PM Markus\textgreater{}} Christ, this is hard.

\emph{7:07 PM Markus\textgreater{}} Good, in the long run, I hope, but
hard.

\emph{7:18 PM Markus\textgreater{}} I'm not done grieving or mourning.

\emph{7:18 PM Markus\textgreater{}} Not by a long shot.

\emph{7:18 PM Markus\textgreater{}} But I'm working on it. I'm working
on finding a way to accept that you're gone.

\emph{7:21 PM Markus\textgreater{}} Not to forget you, but, tacky as it
sounds, honor you.

\emph{7:21 PM Markus\textgreater{}} I'm working on getting to that
stage.

\emph{7:21 PM Markus\textgreater{}} So.

\emph{7:21 PM Markus\textgreater{}} I'm going to start journaling.

\emph{7:21 PM Markus\textgreater{}} And delete your contact.

\emph{7:21 PM Markus\textgreater{}} Though I saved our messages.

\emph{7:21 PM Markus\textgreater{}} And write for myself, and not for
you.

\emph{7:21 PM Markus\textgreater{}} With Dr.~Maura's blessing.

\emph{7:22 PM Markus\textgreater{}} And, hopefully, yours.

\emph{7:22 PM Markus\textgreater{}} I love you.

\emph{7:22 PM Markus\textgreater{}} I miss you.

\emph{7:22 PM Markus\textgreater{}} I always will.

\emph{7:22 PM Markus\textgreater{}} But you're gone.

\emph{7:22 PM Markus\textgreater{}} And you're not at the store.

\emph{7:23 PM Markus\textgreater{}} Or at chemo, or still sick at the
hospital.

\emph{7:23 PM Markus\textgreater{}} You're gone.

\emph{7:23 PM Markus\textgreater{}} And it's time for me to work on
that.

\emph{7:24 PM Markus\textgreater{}} So goodbye, Lee.

\emph{7:24 PM Markus\textgreater{}} Sleep well, miss prissy whiskers.

\emph{7:24 PM Markus\textgreater{}} Crazy face, out.

} % parindent
