%%%%%
\chapter*{AwDae — 2112}

AwDae slowly picked emself up off of the floor, staggering to eir feet.

Ey was standing, swaying, in the middle of a long row of lockers. And then ey was sitting again. Ey didn't feel weak, but the shock of being in the tech booth and theater sim, and then suddenly being back in high school was taking its toll on eir wits.

Ey swiped eir paw from left to right in front of emself to bring up the usual menu. Only, no menu came up. There was nothing in this sim, if sim it was. No global menu, no ACLs, no control.

Panic crested again.

AwDae felt behind emself, reaching for that sense of reality outside of the sim, that cool breeze of the tangible that should be at eir back. It \emph{was} there. Ey could feel it. A cool breath of air on the back of eir neck, but muffled. There was something keeping em from reaching for it, touching it. A thin barrier. A membrane. A sheet of keeping em trapped within the sim.

And then, with a jolt of pain driving like a spike down the back of eir neck and along eir spine, it was gone.

Throughout all of the practice runs, the endless training on the rig that had gone into eir education, that feeling had only come up a scant handful of times. It was the feeling of being forcibly disconnected from the rig through the manual expedient of removing the contacts from the cradles in which they rested. It was the shock of being brought to reality from out of a sim with no disconnection. It was the rush of eir exocortex dumping its core. It was panic made tangible, halfway between electricity and the feeling of missing one's step on the last stair.

With that, AwDae should've found emself back in the tech booth, trying to figure out what strange loop the theater had gotten itself into that would have frozen eir rig.

The lockers never wavered, though, and now ey found emself stuck in eir old high school school with no contact to the world outside of whatever this place was.

Ey screamed.

Ey didn't know how long ey screamed, how many times. Ey didn't know how long ey cried or beat eir fists against the lockers. Ey didn't know where ey was.

Lost.

Lost like so many others.

Lost like Cicero.

Or perhaps Aeneas, Odysseus.

Eventually, ey cried emself out. Eventually, eir tail went numb and eir feet fell asleep.

\emph{Nothing for it.} Ey wobbled to eir feet, kicked off ill-fitting shoes, and began to trudge.

Ey walked slowly down the halls, memories coming back in a wash. Realities blurred effortlessly. Realities of the embodied world. Realities of online life.

Nails on feetpaws clicking against the tile, following the math wing to the student center, a cavernous space that acted as a terminus for all of the different hallways, each hosting a different subject. They spread away from the cavernous room like limbs, a giant insect clutching at the earth.

Neither halls nor hub had ever seen a fox. They were supposed to be home to students. To students and teachers and staff. To humans. To anyone, not some lone half-beast.

Inside the student center, AwDae sat down and tried to reach towards reality once more. Ey sagged, rolling onto eir side in eir increasingly frustrated attempts to pull away from the contacts, though that shock of pain suggested those in reality had pulled em away.

Frustration, anger, fear. Hopelessness. Terror. All simmered within em, working up to a boil as ey tried increasingly harder.

Finally, ey gave up and, hastily brushing at the tears staining eir cheeks, slipped out of eir suit jacket as well. Why keep it?

Ey swished eir tail to the side, and lay flat on eir back on the cool terrazzo floor. Ey pulled eir suit jacket up over eir face and buried eir muzzle in the soft lining. With paws holding the cloth to eir face, ey deliberately let the tears come. Willed them too. Forced. Screamed and begged. Anything for release from the tension building up.

It was a few minutes before ey peeled the coat from eir face and stood back up once more. Exhausted, ey slipped eir arms back into the sleeves of the coat, letting it drape awkwardly from eir shoulders, unbuttoned, fill fitting around eir slim frame. Ey bent down to roll up the cuffs of eir slacks to keep them from bothering eir feet.

It was in the middle of the second cuff that ey realized the absurdity of the motion. In the theater sim, ey didn't have a body, and when ey `woke' in eir normal sim, ey was dressed only in the clothes ey had on when ey went to bed. Usually nothing. Ey disrobed before disconnecting more out of habit than anything.

Why was ey still in eir tux? Did ey even have a tux in eir wardrobe?

AwDae puzzled over this for a moment longer before completing the act. Something to look into later. For now, ey needed to find eir way out. Find eir way back out. Or, failing that, at least one thing ey could complete. One task to complete. Something to make em feel less powerless in the face of it all.
