%%%%% XXX do we really need a split here?
\chapter*{AwDae — 2112}

The sim was startlingly complete.

Perhaps. Ey had been in London a few years, and before that, on the coast at university. Was it complete? Was it accurate? Despair lay around the corner: the thought that the chances of em being able to compare the sim and reality vanishingly small.

In fact, the only thing that seemed to have changed was AwDae emself.

AwDae's curiousity won out. y had made eir way back to the school's auditorium. It was exactly as ey had left it all those years ago. Trudging up the few steps toward the entrance, ey feared that it would be locked. Missing. Somehow erased from existance, such that it had never been there in the first place.

But the door swung easily beneath eir paw and eir nails clicked against the lower portion of the sound guard in the doorway, leading em into a dimly lit auditorium.

The house lights were at quarter, the stage lit only by utility lights from the back. All the same, it was enough for em to find eir way to the small sound booth. A counter with a light --- off. A bank of sliders and knobs --- all zeroed out.

AwDae brushed eir fingerpads along the lower lip of the soundboard. The screws were exactly where ey remembered.

Swishing eir tail out of the way to, ey sat on the stool in front of it. Ey reached a paw up past the master sliders, just around to the back of the board, where ey found the power switch.

Click.

Nothing happened, so ey reached a little further back, finding the power strip for the booth itself, and toggled the switch on that. The board let out a satisfying pop of recognition as it came to life. The brief surge of power echoed throughout the room as speakers awoke. The theater uncoiled, purred to em, just as the one back in London had done\ldots{}what? Three hours back? Five?

Ey fumbled with the booth light, finding the ancient dial switch to wash the unlit portions of the booth in lazy red light. Light illuminated a thin layer of dust covering the board and booth in a matte coating, and countless motes already disturbed. The only breaks in the coating were where eir fingers had brushed the dust away, leaving black slicks.

So familiar. So many dreams. Dreams of flawless performances of breathtaking beauty. Nightmares of feedback and missing equipment.

Acting on a dream, ey slowly brought the master volume up to the spot ey still remembered from so long ago, turned the gain to mid on mic one, and brought the slider up slowly.

Blinked.

A soft hiss filled the hall. The channel was open.

\emph{That doesn't mean anything,} AwDae thought. \emph{Could be anything plugged into the snakehead in the pit. A line with a powered mic, a wireless receiver. Hell, a fault in the system.}

All the same, it was something. Something in this seemingly abandoned hulk of memory was turned on, something else besides emself was making noise.

Ey was about to head down to the pit to check on the snakehead, the terminus for all of the microphone cables or wireless receivers that stretched up to the board, when ey caught sight of a sheet of paper, folded in quarters, tucked between the side of the board and the wall of the booth.

AwDae plucked the paper free and unfolded it, then held it under the red light of the booth lamp to get a closer look at it.

There, in tiny print, was a good chunk of the content of the vcard ey had created earlier that morning to add to Sasha and Debarre's deck. Cicero's DDR ledger, containing transactions that comprised votes made, bounties collected, and comments posted.

A note, though. Doubly weird. The paper didn't act like a normal vcard. No menu, no ACLs ey could sense. And yet the closer ey looked at the paper, the more the data seemed to unfold, fractally nested and apparently infinitely deep.

Ey blinked, and the moment passed. The note once more contained only tabulated transactions.

Frowning, AwDae refolded the note and stuck it into eir trousers' pocket. A small scrap of the outside world stuck in this elaborate fantasy.
