\chapter{Chapter 1}

``Alright, everyone, it's midnight, time to start packing up,'' Johansson called.  ``Ross, we're short one, can you start pulling together all of the mics?  RJ will help you get them sorted.''

``Mmm,'' RJ offered through the sound system.  He was busy putting the theatre to bed, and couldn't spare more than a meager few syllables to the rest of the cast and crew, though he knew that he'd need to help Ross out.  ``Get a headset, Ross, so I don't have to talk through the speakers.''

The theatre purred quietly to him, relaxing and unwinding around him after the tenseness of running rehearsal.  RJ and the room let out a soft, long-held breath together, feeling muscles and wires relax, nerves and current disentangle themselves from the task at hand.  Speakers signed off and went to bed one by one through RJ's gentle attentions, as the virtual board set about the task of returning to neutral, all of the gain knobs orienting themselves, then all of the monitor knobs, the sliders, the whole system ticking as it cooled down, minus the channel he'd need to keep open to Ross.

``Hey boss, got a headset.  Where do you want me to start?''

``Grab the lead, first,'' RJ murmured through the open channel.  ``Then Sarah and Catherine, they've got the nice mics.  They should have a tiny number painted on the costume side that matches up with their box.  All of the boxes are stacked in the pit, by the front wall, you should be able to get them out in one load, though be careful taking them back.''

``Got it, heading down to the pit now.''

RJ left the channel on just in case, though the soft sounds of breathing and the occasional curse as Ross bumped his head on the pit cover were distracting, while he set about going through his notes with the sleepy theatre for the next night's rehearsal, the last one before they went live.  He knew the show better than most of the cast, since he had to learn everyone's lines, plus a few cues when he'd have to take care not to pick up any of the sound effects.  Gun-shots and the like.

The theatre's job was to simply work with RJ and the lighting crew, responding to their knowledge of what was going on in the play, while RJ and Caitlin's job, as sound and lights, was to respond to the stage manager's near encyclopedic knowledge of the play as well as of the house.  All sound was under RJ's jurisdiction, including managing communication between the hands, the manager, and himself and Caitlin.

They were all as ghosts in this, even the theatre.  Their job was one that should be totally invisible to the audience, because it would only become visible if they fucked up.  No one wanted to fuck up.  Even the theatre seemed to feel a sense of pride in doing its job and doing it well.

RJ soothed the room with a gentle cooing and reluctantly started the process of pulling back, closing the channel with Ross and putting all of the headsets to bed last of all, before he slipped back from the interface, blinking as he adjusted to seeing the cavernous hall with his own eyes once more as his fingers slipped from the contact points and he leaned back from the headrest.

He shook his head to clear it and stood up, stretching, before ambling from the tech booth down the stairs towards the stage, letting gravity carry his lanky form down two steps at a time.

Ross was down there standing still and staring at the floor, muttering agitated questions into the headset.

``Hey bud, I'm here.  The house is sleeping now.  I'll help get the rest of the mics and the headsets.''

Ross jumped, then looked embarrassed as he tugged the headset off his head, ``Sorry, was wondering where you'd gone.  I just heard a beep.''

``Yep, signing off from above.  Did you get all the mics gathered up?''

``Oh! Yeah, that's what I was trying to tell you.  I wasn't sure what to do next.''

It only took about ten minutes for RJ and Ross to get the last of the sound gear settled, gathering the headsets from all of the hands and socketing them into numbered chargers against the wall.  Everything would sleep tight until the next night on sound's end.

Caitlin and Sarai, the stage manager, joined them and the rest of the hands, sitting on the edge of the pit cover as they unwound from the tenseness of rehearsal.  The actors slowly getting out of their dress to clump together on the stage, unwilling to leave their beloved platform just yet.

``Gather `round, children'', a voice boomed from out in the darkened audience, lights still hovering around one quarter until the troupe left for the night.

``Yes, Mister Johansson'', one of the actors recited back, getting a tired laugh out of everyone.

``Good job, I think we're nearly there.  Still, we need a bit more polish.  No flubbed lines, and mostly relaxed, but Sarah, you gotta loosen up.  It's not Shakespeare, it's a modern play, you can chill out.  Crew, you guys got a little sluggish toward the end.  I know it's late, but so are our shows.  Don't work yourselves too hard, but keep on top of things, okay?''

RJ, Sarai, and Caitlin murmured their assent while the rest of the hands nodded, one or two looking sheepish.

``Tomorow night, back here at five.''

``Aw, come on, that early?'' RJ asked,

``Yep, five.''  Johansson grinned wryly.  ``There's a school production that winds up around then and I want you all back here to make sure we still have a theatre around then, okay?''

There was a bit more grumbling, but RJ knew they'd be there on time -- it wasn't too much of a stretch.

``Back to base, then.  Go get some rest tonight, and I'll catch you all tomorrow.  Remember, you can drink tonight, but tomorrow night, \textit{Das is streng verboten}.''

The company laughed and started to disperse, the tech leads lingering on the pit cover for a little while longer as they worked on reorienting themselves to the real world, limited by two eyes, two ears, two hands.

Eventually, RJ made his way out onto the chill of the street, pulling his thin water proof gloves on to keep the contacts on the middle joints of his fingers dry and clean.

At midnight on a week day, there wasn't too much going on outside of those visiting the pubs to catch up with their friends after work, though by the time that midnight had rolled around, those who were left were the harder drinkers.  The idea of a warm pub and one quick pint before heading home tugged at him, but the pull of home was much stronger tonight than that of beer.

He trudged instead up to the northwest corner of Soho to Oxford Circus, where he could catch the Central line up to Benthal Green, and walk the few blocks from there to his flat, stopping only to pick up a take-away carton of curry and rice from one of the more trustworthy shops along the way.

Once home, he slipped out of his jacket and welcomed the warmth of his little flat after the damp chill of London outside.  His cat trotted up to him eagerly, twining around his feet.  A little ginger thing of a few years that he had rescued from a friend who was moving deeper into the city, she was the only one to share his space with him after his last flatmate had left for somewhere cheaper.

``Hey Prisca, let me set my shit down before I get you food.''

An eager meow followed him to the kitchen, where he set down his take-away and scooped a cup of dry food into a fresh dish, setting it down for the delicate cat.

He thumbed his phone with the contacts on the thumb-pads of his glove to start music playing, some of the stuff that reminded him of his dad, to go along with the curry that reminded him of his mom.

Dinner was no more or less exciting than usual, RJ eating alone at the kitchen table with the carton spread out before him to reveal the orange curry and soggy samosa that had come with it.  He left his gloves on just to be sure -- no sense in having to clean his contacts more than he'd already need to after a long day's rehearsal.

The draw of his workstation was a lingering presence in a corner of his mind, tugging at him, inviting him on toward where he knew he could finally relax for the day, but he knew that he probably ought to finish all of his routine before he delved back in.

He scooped the last of the curry into a little plastic container for the next day's lunch, promising himself that he'd cook an additional pot of rice before heading out in the afternoon so he'd have more calories to keep himself running. Clean up was as easy as tossing the container into the compost bin along with all of the others.  Cooking much more than rice was for times other than crunch time.

He finally allowed himelf to sit down at his workstation, relaxing into the familiar curves of the chair, peeling his gloves off one by one.  Even with the draw so close to him, he took his time.  First, he picked up Priscilla and stroked her smoothly from ears to tail a few times until she started purring up a storm, informing her that, in fact, she was the prettiest kitty.

Once the cat had settled into his lap and curled into a small crescent, he set about cleaning the contacts on his hands with lint-free paper and rubbing alcohol.  Those done, he wiped down the headset as well, removing the negligible residue of sweat and skin oils that had collected on the soft, padded headrest where his forehead would lay, held inches away from the miniscule cameras that would track his face.

His gear was more elaborate than the stuff in the tech booth at work that he shared with Sarai and Caitlin, and he had paid dearly for it, as well as for the contacts on his fingers, and the countless other tiny gizmos placed throughout his body -- the small interferites that took over his optic and auditory nerves when he was connected, the NFC connections implanted just under his hairline and their ramifying tendrils that tied him into his work, all of the painful work down his spine that helped him more fully experience the connection.

With all of his connections and gear cleaned, RJ finally felt at ease enough to pop open the lid on his workstation.  The screen, nearly vestigial when he was inside, served as an interface to boot or, if needed, to troubleshoot problems with the rig.  He quickly keyed in his passphrase and then rested his right hand on the curved pad, feeling his fingers find the subtle grooves that would hold his hand in place, the connection from his contacts was the other half of his two factors of authentication, and the system signed him on, displaying the spinning earth surrounded by a jauntily tilted ring that was the omnipresent logo of the `net.

``Gonna head in, Prisca,'' he spoke to his cat, stroking the fingers of his left hand over her ears, fingering the soft, velveteen folds for a moment.  ``I'll be back in a bit.''

With that, he brought his left hand up and set it into the cradle of the pad designed especially for it.  Tilting his head against the headrest, feeling the comforting touch of cool plastic against his forehead and the little twinge of recognition from the NFC controllers, he nudged the button beneath his right thumb.  The workstation went into immersive mode as RJ delved in, a soft hum of a cooling fan picking up to handle the waste heat of his rig.

He could no longer hear it.
