\chapter*{Chapter Three}
\addcontentsline{toc}{chapter}{Chapter Thre}

As RJ slid his hands from the pads and leaned back from the headrest, he let out a full-fledged yawn, startling even Priscilla across the room with the sound and the stretch.  He stumbled up out of his seat and over toward the still-purring cat, stroking over her ears once more as she butted her head up against his hand, his mind whirling with a mix of work, of Cicero's disappearance, and of school with Sasha.

``I'm wiped, Prisca,'' he informed the cat, who simply purred louder.

Smiling, he peeled his shirt off over his head and slipped out of his jeans, knowing that tomorrow's dress rehearsal would mean full dress for everyone and makeup for the actors.  He'd have to make sure his suit was clean, or he'd be in trouble.  For now, though, as it neared two, he focused mostly on making sure the door was locked and the lights were out before stumbling over to bed.

As he flipped the screen down on his workstation to signal for it to go to sleep and wandered over to his bed, he couldn't get Sasha and all of her talk of high school, gone these last fifteen years now, out of his head.  Even as he climbed into his narrow bed and pulled the comforter over him to ward off the chill of the night, he was replaying scenes from school, back in the US, through his head, a worn out film, dim and scattershot, but still laced with emotion.

He and Sasha had tried dating early on.  Later, after a few weeks of it not going anywhere, they had both admitted that they had felt pressured into having a relationship in school.  Good boys and girls fell in love with other good boys and girls, pretended they didn't have sex, and went out to the movies together.  They had continued the trend of going to movies, and later to live performances, together, but the relationship had petered out, rather than ending in some climactic fashion.  Sasha had gone on to have a string of other relationships, some earnest and some not, some more intense than others -- a string that remained unbroken, if tonight's conversation was any clue -- but RJ had stopped there.

The social pressure to date throughout high school was only equaled in intensity by RJ's apathy toward the whole scene.  He'd felt the occasional twinge of romantic attraction, and to other students of all genders, but the expectation of sex that went along with the idea of a relationship so put him off that he had instead buried himself in his school work.  He did well in some courses and not as well in others, but on the things that he enjoyed, he dumped all of his effort.  He had gotten started early on in working the school's older sound board in their theater, running sound for plays, concerts, and assemblies, quickly earning the trust of the other tech crew and the school staff and faculty, rising to lead sound tech within a year.

Computer class had captivated him as well, and for his sixteenth birthday, his parents had surprised him with the implants that would be needed for full interfacing with a workstation.  To be honest, it hadn't been too much of a surprise: his father was an engineer and his mother a fairly forward-thinking person, and they had promised him the procedure eventually.

It was a simple afair that took place in an outpatient office, involving self-guided implants that had largely installed themselves.  The worst part had been the itching.  It was bearable on his hands and along his spine, where the implants breached the surface of his skin, because at least he could scratch (though he had been cautioned to try not to), but the worst had been the NFC pads in his forehead and the interferites embedded even deeper, providing an itch that no scratching would ever reach.

Sound and the interface had taken up all of his energy throughout school, leaving little time to worry about the social stigma that went along with not having a relationship.  He was simply the nerdy sound kid who knew more about computers than even the teachers.

Training on the interface was a daily task that he had applied himself to with gusto.  It hadn't always been fun, of course, but by the time he'd reached that age, he was starting to understand the idea that work put into a craft was a good way to get more out of it.  That he had found furry around then was another thing that kept him going, working and improving at the art of interfacing with his workstation in a way that felt natural to him and came off as natural to others on the `net.  He moved effortlessly through the Crown Pub and a few other choice spaces, slowly crafting the primary persona that he used when interacting with others, the cross fox known as AwDae.

It was then that he and Sasha had really started connecting, for it was her that introduced him to the community.  They started hanging out more, talking more, and, especially, building a network of friends together.  Dating hadn't worked out for them, what with RJ slowly coming into his identity as asexual and more and more androgynous over the years, while Sasha remained fairly sexual and interested in guys much more masculine than him.  All the same friendship had seemed almost natural.

The training had culminated in an offer to go into interactive sound technology at a rather prestigious university out on the east coast.  It meant leaving Sasha and a few other close friends behind along with his family, but it also meant that he would be at the forefront of a new technology used in production of both films and live work.  In fact, the field was so new that his own studies at the university helped fuel the change in theater tech work, his dissertation, what was meant to be his capstone project, being eventually published and spread around the world.

He had continued to work at the university for a while, as they were one of the few places around with both a theater and the technology to back it up in such a way that he had helped create.  He had considered continuing his studies beyond where he had, but the draw of the theater was what focused him most, rather than strictly academia, or even limiting himself to college theater.

The call from London, had come less than a year after he graduated.  Would he like to help start a tech-savvy theater group in town?  The pay would be slow to start, but the troupe had a loose collection of apartments he could stay in.  He would have full run of the sound department.  When could he start?

That conversation had taken some convincing, when it came to his parents.  They were pleased, to be sure, but they also felt that London was fairly far away, even though still in the western bloc.  He made his promises that he'd come and visit every now and then between shows or when an understudy would take a show for him.

Burying himself deeper into the covers and the mattress, leaving enough room for Priscilla to join him later, RJ thought more about what had come up between him and Sasha before.  When they'd Lost Cicero, it was a blow to them all.  Getting Lost was not something that happened often, only a couple dozen recorded cases to date, but among those who were counted among the Lost, a disproportionate amount of them were those who were heavy users of the integration technology.  It was a risk, everyone had assumed, just as was travel.  Something could always happen.

All the same, it was an intense sensation to feel it hit so close to home, and it reminded RJ of just how much he relied on the integration technology, not only for work, but for a large part of his social life.  He enjoyed the company of the troupe just fine, and often accompanied them out for drinks and the like, but his heart truly lay among the friends he'd made on the `net.  His friends being on the `net meant more use of his contacts, and more use of his contacts meant more risk.

It was risk for all of them.
