\chapter*{Chapter Four}
\addcontentsline{toc}{chapter}{Chapter Four}

Doctor Carter Ramirez rubbed her face into her hands, ground her palms against her eyes until she saw stars, before finally slicking her hair back.  She had put it up into a bun earlier that day, but there were plenty of flyaway hairs, as there always were.

She felt out of her league.  Everyone did, here on her team, but that didn't stop the fact from wearing on her.  It's not that there was no support from on high to help with the Lost, because there was.  It's not that there was no one else trying, because there was there, too.  It's that no one seemed to take it all that seriously.  It was a thing like addiction, or plane crashes, or suicide.  Something to look at, to study long enough to say ``Ah, \textit{this} is happening now,'' and then set aside like some work of art which was only good enough to be a conversation piece.

People admitted that the phenomenon of getting Lost was happening, but only in as much as it didn't affect that many people.  A simple number to point to.

She wasn't the last one left in the lab, by any stretch, but it had reached that point of the night where collaboration had stopped and everyone was butting their head against their own individual problems, toiling in silence.  She put down her tablet and pressed down the display on the workstation that she had been assigned for this project, sending it to sleep.  It had also clearly reached the point of the night where she wouldn't be getting anything else done.

It was as though the brains of the Lost were just elsewhere, just dreaming on some level, but there was no sense to it, no rhyme or reason to why such a thing would happen to the patient.  Some of her team were working on pulling together all of the facts about the population that they could, from demographics to physical stature, searching for clues.  The neuroscientists were digging into what was going on within the brain, and what few scans they had from before someone had gotten Lost.  Their two pet lawyers (thankfully not present) were digging into both the legal status of the Lost as well as doing what they could to procure under health information law from patient medical histories.

And Carter was supposed to tie it together.

Or, that was her stated goal.  The university medical center had grudgingly provided space and funding for the project in an attempt to win some much-needed kudos, but she was starting to doubt just how much the UMC even wanted her to continue.  As manager, she had been met with hurdle after hurdle in trying to make any progress in the case as soon as she started to venture outwards.  It was as though the advisory board had given her all the data that it was willing to give, and any more might put those kudos it was receiving at risk.
