\chapter*{Chapter Five}
\addcontentsline{toc}{chapter}{Chapter Five}

RJ allowed himself to sleep in until nearing 11 that morning, given that tonight was the last night of dress rehearsals.  Many other members of the troupe held part time jobs during the day, and he had been known to offer his services as consultant during times like these.  Even so, with all that he did, he made enough to not have to worry about holding down more than the one job

As it was, on days when they had nighttime rehearsals, he felt no compunctions about sleeping in.  There was nothing to be up for, and with only the `net to keep him occupied in the mornings, he felt little need to get moving.

It was Priscilla who has woken him up, butting her head against his cheek and purring loudly to him.  The more insistent the cat got, the less he was able to ignore her intrusions on his admittedly banal dreams.

He finally trudged out of bed and refilled his cat's water and food dishes, giving her the requisite morning pets to keep her happy.  That done, he scooped her litter box and made himself a pot of tea.  He sat at the tiny kitchen table, sipping from his oversized mug and watching the late morning traffic from his window, primarily composed of business traffic, with the occasional mother with child in tow.

% Stops for food, thinks of Cicero and checks on contacts from cards

% Heads to theater

% First half of the night goes smoothly

% First notices that the room feels smaller, then less responsive to control, then silent; finally tries to pull back and winds up just looking up from a board at his HS auditorium
