\chapter*{Chapter One}
\addcontentsline{toc}{chapter}{Chapter One}

``Listen, Ramirez, I'm just not sure if you-''

``No.  Come on, Sanders, just hear me out.''  Carter sighed and settled her weight against the edge of her desk, taking a slow breath to buy herself some time and organize her thoughts.  ``I'm just saying that we ought to look into social connections between the patients so that we can see if there's some factor that's tying these occurrences together.  With that under our belt, we may be able to formulate a better theory of what's going on here, even neurologically.''

Sanders hung his head and then shrugged, ``It's just that you're talking about a social vector here, Carter.  Not only do we have very little data to go on, but there's no indication that this is something passed from one person to another.  All of the data suggests random-''

``Sanders,'' Carter said sternly.  ``I know how the project works.  I know the data.  There's a lot of questions still left in the air.  I'm not suggesting that getting Lost is something that is transferred from one person to another like some sort of virus.  I'm merely suggesting that we might find shared factors within a social realm as well as the physiological.''

Sanders glared at Carter, who stood her ground.  As the lead of the research team, she could tell Sanders to do whatever she wanted him to.  There was no reason for her not to, as well, since she was plugged into all of the teams that he was distanced from.  He may be lead of the neurochem side, but Carter was lead of basically everyone except the grantors.

Eventually, Sanders caved with a shrug, turning his back on Carter and bowing his head towards his own team.

``Look, Sanders,'' Carter said, following after him.  ``You're a fantastic doctor, and I really respect that, I really do.  I'm not pulling labor away from the neurochem team, I'm merely suggesting that we add a social angle to our attack here.''

Sanders held up his hand, gave another noncommittal shrug, and walked over to his workstation.

Carter rolled her eyes and turned back to the remaining team.  ``We've got a hunch on the social front: there's a few patients who are involved in the furry subculture, and there's distinct ties between them.  They're loose ties, sure, not everyone knows everyone else, but they \textit{are} there.  Let's timebox half a day to chase down these ties and see just where they lead.  If they lead nowhere, fine.  If we can find a way to tie them together, then we find out all of the ways that the web ramifies.  Worst case, half a day is spent tracing along the web, but best case, we find a way to tie these cases together that lets us predict -- and then interrupt -- future cases.  Got it?  Catch you at lunch.''

Carter sighed after her speech and wandered over to her desk.  Rather than sequester herself in an office, she had taken a desk among the team, four foot cube walls separating each, even if they were made of glass.  There wasn't much room for an office in the repurposed classroom, all the same, but the deliberate attitude with which she had chosen to join everyone in equal conditions had endeared her to some of the more stubborn of the crew.  On the other hand, the lawyers were badly out of their element.  Ah well.
