\chapter*{Chapter Two}
\addcontentsline{toc}{chapter}{Chapter Two}

AwDae slowly picked emself up off of the floor, staggering to eir feet in the middle of a long row of lockers. Ey hardly felt weak, but the shock to the system of being in the tech booth and theater sim, and then suddenly being back in high school was taking its toll on eir wits.

Ey swiped eir paw from left to right in front of emself to bring up the menu. Only, no menu came up. There was nothing in this sim, wherever it was. Ey had no ACLs, and there was no global menu.

Beginning to panic, AwDae felt behind emself, reaching for that sense of reality outside of the sim that should be at his back. It was there, ey could feel it like a cool breath of air on the back of his neck, but there was something keeping em from being able to get to it. A thin barrier, a membrane, like a sheet of plastic that kept him trapped within the sim.

And then, with a jolt of pain through the back of eir neck and down along eir spine, it was gone.

Throughout all of the practice runs and training on the workstation that had gone into eir education, that feeling had only come up a small handful of times before. It was the feeling of being forcibly disconnected from the workstation through the manual expedient of removing the contacts from the cradles in which they rested. It was the shock of being brought to reality from out of a sim with no disconnection.

And with that, AwDae should've found emself back in the tech booth, trying to figure out what strange loop the theater had gotten itself into to freeze eir workstation. The lockers never wavered, though, and now ey found emself stuck in eir old school with no contact to the world outside of the sim, or whatever this\ldots{}place was.

The lockers were enough to tip em off, but sims -- if that's what this was -- could contain any details, so ey started to walk slowly down the halls, memories coming back in a wash as ey made eir way along the hallway, nails clicking aginst the tile, following the math wing to the student center, a cavernous open area that acted as a terminus for all of the different hallways, each one hosting a different subject. They spread away from the cavernous room like limbs, a giant insect clutching at the earth.

Once inside the student center, AwDae sat down once more and tried to reach towards reality once more, rolling onto eir back in eir increasingly frustrated attempts to pull away from the contacts, even though that shock of pain suggested those in reality had pulled em back.

Frustration, anger, fear: all simmered within em, working up to a boil as ey tried increasingly harder. Finally, ey gave up and, hastily brushing tears from eir eyes, slipped out of eir jacket, swished eir tail to the side, and lay flat on eir back on the cool terrazzo floor. Ey pulled eir tux jacket up over eir face and buried eir muzzle in the soft lining, paws holding the cloth to eir face as ey deliberately let the tears come, seeking any kind of release from the tension building up inside of em.

It was a few minutes before ey peeled the coat from eir face and managed to stand back up once more. Ey tiredly slipped eir arms back into the sleeves of the coat, letting it rest on eir shoulders once more and drape, unbuttoned, around eir slim frame. Before continuing, ey bent down to roll up the cuffs of eir slacks to keep them from bothering eir feet.

It was in the middle of the second cuff that ey realized the absurdity of the motion. In the theater sim, ey didn't have a body, and when ey `woke' in eir normal sim, ey was dressed only in the clothes ey had put on when ey went to bed, though usually ey remembered to disrobe before disconnecting, more out of habit than anything.

Why was ey still in eir tux, then?

AwDae puzzled over this for a moment longer before completing the act, setting it aside as something to look into later. For now, ey needed to find eir way out. Find eir way back out.

\secdiv

The sim was startlingly complete.

In fact, the only thing that seemed to have changed was AwDae emself.

AwDae's curiousity had wone out, and ey had made eir way back to the school's auditorium, exactly as ey had left it all those years ago. Trudging up the few steps toward the entrance, ey feared that it would be locked, but the door swung easily beneath eir paw, and eir nails clicked against the lower portion of the sound guard in the doorway, leading em into a dimly lit auditorium.

The house lights were at a quarter, and the stage was lit only by utility lights from the back. All the same, it was enough for em to find eir way to the small sound booth, a counter with a light, off, and a bank of sliders and knobs, all zeroed out.

AwDae brushed eir fingers along the lower lip of the soundboard, swishing eir tail out of the way to take a seat on the stool in front of it. Ey reached a paw up past the master sliders, just around to the back of the board, where ey found the power switch. Click.

Nothing happened, so ey reached a little further back, finding the power strip for the booth itself, and toggled the power on that. The board let out a satisfying pop of recognition as it came to life, the brief surge of power echoing throughout the hall as the speakers woke up. The theater was purring to em, just as the one back in London had done earlier that night.

Ey fumbled with the light to get it on, washing the unlit portions of the booth in red -- red being the least obtrusive from the visible spectrum in a dark room -- and exposing a thin layer of dust covering the board and booth in a thin, matte coating. The only breaks in it were where eir fingers had brushed the dust away, leaving black slicks amid the gray. Ey slowly brought the master volume up to the spot ey still remembered from so long ago, turned the gain to mid on mic one, and brought the slider up slowly.

A soft hiss filled the hall. The channel was open.

That didn't mean anything, AwDae told emself. There could be anything plugged into the snakehead in the pit. A line with a powered mic, a receiver, or hell, a fault in the system.

All the same, it was something. Something in this seemingly abandoned hulk of memory was turned on, something else besides emself was making noise.

Ey was about to head down to the pit to check on the snakehead, the terminus for all of the microphone cables or wireless receivers that stretched up to the board, when ey caught sight of a sheet of paper, folded in quarters, tucked between the side of the board and the wall of the booth.

AwDae plucked the paper free and unfolded it, then held it under the red light of the booth lamp to get a closer look at it.

There, in tiny print, was a good chunk of the content of the card ey had created earlier that morning to add to the deck. Cicero's DDR ledger, containing transactions that comprised votes made, bounties collected, and comments posted.

Frowning, AwDae refolded the note and stuck it into eir trousers' pocket, mulling over the small scrap of the outside world stuck in this elaborate fantasy.

\secdiv

The pit revealed little. There were twenty boxes set on a table in front of the snakehead. Twenty receivers for wireless mics. Twenty cables neatly velcroed together into a bundle, contracting from the boxes and expanding once more toward the dull grey plug box. From there, the cables were reduced to a simple five-per-row organization, arching up from the snakehead before bowing under their own weight, each a graceful arc.

All of the boxes on the table were dull, mute LEDs simple bumps on their surface. All but one, the first one. A piece of masking tape on its box marked with a simple `1'. That box had a single red light on the front, marking that it was powered on, and a single green light, marking that its corresponding mic was transmitting.

``Great,'' AwDae murmured. ``That lowers the position down to only half of the school.''

If it had been a wired mic, the search would have been over right as it started. The cable would've been plugged into the snakehead, and by following it until ey reached its end. There would be the mic.

And what?

There would be the mike, and ey would still be stuck in some stereotype of a nightmare, all dressed up for the high school performance and the auditorium completely empty. The fox barked a soft laugh at just how cliche the whole situation was, turning away from the receivers and resting eir weight against the edge of the table on which they were placed. Ey rested a moment there before hiking eir weight up onto the familiar surface, hearing the slight squeak of stressed metal from eir sudden burden.

AwDae swung eir legs back and forth, hearing the table creak and groan in time with the slow movements, the sound quiet, but in the dread silence of the auditorium, more than enough to fill the hall.

Ey stopped. The hall was pleasantly wet: not damp or anything, but int terms of echo, it had just the right amount (or, at least, as much as a high school auditorium was willing to muster). Had it been dry, the sound would've died away completely. The dryer a room, the closer it got to approaching an anechoic chamber, a room lined with material such that it would reflect zero sound.

Neither did the sound bounce back endlessly like an echo chamber.

AwDae knew this hall, even still. Ey knew the ways in which there would be pockets of good sound and bad sound throughout the seating. Ey knew the dead spots on stage where one's voice would fall flat if it weren't amplified. Ey knew how the stage was built rather like a horn, with the performers at the small end, so that their sounds were projected out toward the audience.

And yet, that slight echo of the squeaking of the table fading out had given em an idea. It was crazy, sure, but by this point, though ey hadn't admitted it in such terms to emself, if ey had gotten Lost, a crazy idea was better than none.

\textit{And}, a bitter portion of em reasoned, \textit{if getting Lost \emph{is} permanent like people say, I've got nothing to lose.}

The idea was this.

The squeal of feedback in an audio system is known to most everyone, and even those who have not heard it before know immediately that something is wrong when it crops up. It starts as a quiet hum in the background, but it doesn't take long before it can be understood as something originating in the system, rather than coming from the speaker or performer. From there, it builds on itself, feeding back into itself, until it quickly overwhelms all sound coming into it.

The idea is similar to the echo that AwDae had produced by making the table squeak beneath eir weight. Sound was picked up by the microphone, transmitted through the sound board, and then out into the room, amplified, through the speakers. However, the microphone was in the same room as the speakers.

If the microphone started to pick up sound from the speakers -- or, more commonly, the monitors: speakers placed at the front of the stage and pointed back toward the performers so that they could hear themselves on the otherwise acoustically dead stage -- then that sound would come out of the speakers and be picked back up by the microphone once more.

This was the feedback loop that was referred to. That would continue to build through further and further iterations, until the auditorium was filled with a roar of the one pitch the microphone had locked onto.

Obviously, microphones were still in use. They hadn't been abandoned because of this roar, as there were many different ways around feedback. One could angle speakers toward the audience, rather than the stage, for instance. Bodies were notoriously bad reflectors of sound, which is part of what made the stage so dead, acoustically. One could also not provide monitors, but that was cruel to one's performers. One could turn down amplification, but that defeated the purpose.

The solution, then, was gain.

Gain was the sensitivity of a mic. The simple adjustment was given a knob at the very top of the sound board, befitting its importance in the world of sound engineering. Turn the gain all the way down, and the mic was a dumb lump of metal. Turn it all the way up, and the mic picked up everything from the movement of the air to the slight hiss of the live sound system, leading to almost instant feedback.

If AwDae were to turn up the gain almost to the point of feedback, ey could try and make noise in various points throughout the auditorium. The more feedback ey generated, the more sound the mic was picking up. The more sound it was picking up, the closer ey was to it.

Eir possible locations for the mic hadn't been reduced from half the school, but eir chances would go up. If the mic was not in the auditorium, ey could turn the main system up and start venturing further afield with a door left open, allowing em to hear the theater hum like an alarm.
