\chapter*{Chapter Four}
\addcontentsline{toc}{chapter}{Chapter Four}

It took AwDae just under two hours to find the microphone.

The first hour was spent searching the auditorium thoroughly. Ey searched by walking around clapping and humming, then singing songs half-remembered from productions ey had helped with in the past. Ey would've whistled if it wasn't for the structure of a canid muzzle. There was no way eir lips would manage to pull that off.

Silence.

After an hour, venturing even into the overhead areas where sound wouldn't reach, ey gave up and took a break.

Taking the slip of paper with Cicero's transactions from eir pocket once more, ey scanned over the titles of the initiatives voted on. There was very little there to latch onto. Or, rather, there was way too much. AwDae couldn't manage to even boil down the table into any single sentence, much less something useful. The cat had apparently voted on just about everything, without taking any breaks.

Eventually, when the rows started to blur into one another, ey levered emself up from the auditorium seat ey had chosen. Ey refolded the paper and slipped it back into the pocket before checking on the board once more. Everything remained set as it was before the break.

Venturing outside the auditorium, AwDae had imagined ey would work in concentric circle away from the auditorium. This turned out not to be the best idea. The theater was nestled between two arms of the school which did not meet. That made their routine fairly artuous. Ey'd walk down one hallway, poke into classrooms, and make noise before moving on. When ey reached the end of eir circle, ey had to jog around the auditorium through the student center to go down the other hallway and do the same

Eventually ey gave up on the concentric circle plan and started working from north to south.  Ey worked through the entirety of one hallway, clapping and hollering, without hearing anything, before moving on to the area of the student center near the auditorium.

It was there that ey heard the first, faint hum.

At first, it had skimmed beneath eir attention, sounding rather like an echo from eir own voice in the cavernous space of the student center. When the open doors to the aduditorium caught eir eyes, ey tried once more, getting another faint hum that slowly died out as the space and air dissipated the tone.

It took another few minutes to find the microphone itself: a small bit of hardware resting delicately atop the door handle leading into the principal's office just to the northeast of the auditorium doors. It was surprising, in a way, that ey hadn't managed to trigger any feedback earlier, until ey realized eir mistake: ey would have to shout loud enough to be heard in the auditorium; without the speakers producing noise loud enough to make it back through the walls and reach the mic, there would be no feedback.

The door was labeled `Admin.', which was omminous. Although there was a head office at the front of the school, administration was where the principal and vice principals' offices were. It was one of those places that lingered in the mind of every student who had passed through the doors of the school. Getting called to the front office was usually bad enough -- a call from a parent!? -- but getting called to the admin office was worse still.

AwDae delicately picked up the microphone through mounting feedback before shutting it off, eir ears laid flat in an attempt to shut off the growing hum from the auditorium. The sound stopped a scant few moments after the mic was shut off, bouncing around the auditorium and the student center.

Ey pocketed the mic in eir trouser pockets and straightened back up, cautiously lifting eir ears once more. The school was once again silent. There was no hearing the hiss from out here in the student center. Remembering the position of the mic, AwDae wandered back over to the auditorium, turning the gain back down on the board and lowering the house volume. Ey even turned the mic back on and gave it a quick ``one-two'' to ensure that none of the speakers had been damaged.

\textit{This is a sim, and not even mine,} ey thought, ears tinted pink with a blush. \textit{What does it matter if a speaker blew?}

Ey shrugged it off after a moment. Habits were habits and there was no reason to break them now.

Wandering back to the admin office, tail swishing behind em, AwDae couldn't help but feel as though ey was trapped within a game, one of those first-person puzzle solvers that seemed to be forever popular. The fact that ey seemed to be receiving what amounted to clues while in an complex abandoned building only added to that.

Shaking eir head, ey turned the knob on the admin office and peeked carefully inside.

There were no traps, no jump-scares, just the six-sided room with its three doors on the opposite walls. One for the principal, and two for the vice principals. Taking the game metaphor to heart, ey started poking around the office where ey could, flipping through a datebook on the secretary's desk (empty) and rummaging through the drawers (office supplies). The waste baskets were empty.

Steeling emself for something shocking, with the game mentality still holding onto eir mind, ey tried each of the doors in turn.

It surprised AwDae that it wasn't the principal's office that opened, but one of the vice principals, though the name escaped em. The office was dark, but the lights responded to a touch on the pad, which ey sent to a comfortable level without being intimidating. Ey remembered being hauled into the room, all those years ago, with the lights all the way up, a gesture of power.

Rummaging through the desk revealed little of note. Rather than a planner on the desk, however, was a workstation; simple and, to eir eyes, ancient. It didn't respond to any of AwDae's interactions, though. Although how it would work, ey didn't know, ey had hoped that a connection like that might lead to a way back out of this mess.

The only other item on the desk was a scratch pad, and a pencil. They never seemed to go out of style. The pad contained a simple breakdown of costs, divided into departments, for the coming year. A simple three-column setup tallying subject, expense, and deductions from some number at the top which must be the classroom budgets. At the bottom of the page, was a final number, circled. Apparently, the administrator hadn't quite liked the result, for it was circled in dark, angry strokes.

AwDae flumped down in the chair at a bit of an angle, letting eir tail flop down between the arm rest and the chair's back so as to keep from crimping up uncomfortably. Tired, so very tired.

Ey rubbed eir eyes tiredly, brushing away the sandy grit of tears already shed. Ey was moving in this search with determination, occupying eir mind, specifically so that ey wouldn't collapse into a depression borne of hopelessness and despair. It occurred to em that getting Lost was the perfect prison: complete freedom, or nearly so (ey had already fantasized about jimmying open the other doors), with nothing to do. Nothing to dream, nowhere to go, nothing to know.

Ey would go mad without a task. Ey could create, but why create in these empty halls? What would ey even begin to create that would matter the worth of a damn? Ey would never be able to share it. Ey would only be able to spiral inwards. Endlessly.

All AwDae wanted to do was curl up in the chair. It was comfortable enough, ey could probably manage to get some sleep in.

Instead, ey rubbed eir eyes once more and leaned forward toward the desk, letting eir eyes focus on the columns of scratched digits and marks on the sheet of scrap before em. Mindlessly working through the sums in eir head simply for lack of anything else to do.

``Hmm, that's weird,'' ey murmured sleepily out of the corner of eir muzzle.

The numbers didn't add up. In fact, everything added up within its own row, it was simply as though a row were missing.

Ey yawned and stretched before holding the sheet of scrap up to the light. There were no erasures, whiteouts, or anything like that. There was just simply not enough information.

Finally, the fact that ey was holding onto a ledger, such as it was, dawned on AwDae. If ey was meant to be looking for clues, then\ldots{}

Ey hastily fished the previous clue out of eir pocket. The ledger of Cicero's DDR interactions.

It wasn't nearly so simple as the scratch paper. For instance, each referendum had three different types of interaction: a cost, a bounty (if that referendum was referred back to the house), and any number of comments made on the issue, and they were often out of order on the sheet, given Cicero's habit of voting on everything.

Ey wished for eir workstation more than anything, as this would make the task almost trivial. Having to do without, ey snagged the half-used pencil and the rest of the scrap and worked it out. Each cost and comment would be a debit, and each bounty would be a credit. One could also buy DDR credits through a mechanism that basically acted as an additional withholding on one's taxes, and there were two of those in there, ensuring that Cicero would have enough DDR credit to make what AwDae assumed was some scathing political rant on an upcoming high-stakes referendum.

Even so, with all that work, it was clear that even the section of numbers on the paper didn't add up. Once more, there was a missing interaction. Three missing interactions, rather: one vote's cost, one vote's comment, and one vote's bounty, at AwDae's best guess.

The problem was that one's DDR records were public -- they had to be, for the system to work -- and, unless it had been tampered with (something AwDae had to take into account), eir was a combination of 1,252,000 credits unaccounted for in terms of transactions. One million debit to the comment, a quarter of a million credit for bounty, and two thousand to the vote cost.

AwDae tore off the top sheet of scrap and, working faster this time, ran the numbers once more, only to receive the same result.

``Well, huh.'' Ey sat, stunned, for a little while longer before gathering eir notes and folding them together with the original clue and stuffing them into eir pocket. Ey couldn't create a deck here, but ey could sure take items with emself.

If this all had something to do with what was going on outside, where ey was counted among the Lost, that was all well and good. But, how would ey get that information back out.

It was probably too early to be thinking of such things. Ey wasn't going anywhere for the time being. Sleep was taking too strong a hold on em. Ey gave token consideration to where ey would be able to sleep before deciding on the auditorium. The fold-down seats were cushioned, but not very well. All the same, the place had a sense of home about it. Perhaps the day to come would help em learn more.
