\chapter*{Chapter Five}
\addcontentsline{toc}{chapter}{Chapter Five}

Carter hadn't meant to dodge her subordinate's question.  They truly did need to go in to eat.

The food was, as promised, delightful, and Carter made a mental note to come here more often for more good Vietnamese food.  That note, however, was filed by her mind and set aside so that she could work through the implications of what had been spilled to her by the tabloid.

She couldn't visit this RJ any more than she could fly out of the second story window here and back to her lab.  There were several factors keeping her from doing so.

First, and foremost, it was useless.  Her team didn't \textit{need} access to the Lost to do all of their work, because much of their vitals was provided as a real-time stream of data into the work group.  Besides, it had been proven that physical contact registered little, if at all, to the Lost.

Secondly, there would be people between her and RJ.  Not just doctors and nurses, but her own administration.  She would have to go through any number of people just to get access to some variables that likely wouldn't help her investigation at all, such as eye color or hair color.

Finally, there was the law.  Carter understood the purpose of WFHIPA: the Western Federation Health Information Protection Act.  Hell, she had voted on it, herself.  It was something she felt strongly about.  The tabloid had techincally breached that (though there was no culpability) by informing her that there was a good chance that one of the group they were studying was this RJ.

There was, however, nothing to stop her from going to a show in the next day or two.

Feeling very much the sleuth, she stuffed a small egg roll into her mouth with delight, savoring the taste of it.

Yes, she'd go to a show up in Soho.

\secdiv
