\chapter*{Chapter Six}
\addcontentsline{toc}{chapter}{Chapter Six}

Sleep did not come easily.

Auditorium seats, although padded, were not made for laying down on, and AwDae found that ey had to face toward the backs of the seats, or else eir tail would get crimped against them.  At first, the faint dusty smell of the seat fabric had inspired nostalgia, but it didn't last long.  Eventually, ey got up blearily and began pacing around the auditorium, looking for some way to get some rest that did not involve the seats.

Ey pondered pulling down one of the curtains and making a bed out of that, but, as ey did not know how to do so without ripping the curtain, ey was loath to do so.  They carried some of that same smell, as well.  Ey figured they would make a good last resort, if nothing else, and started exploring beyond the stage and auditorium.

The back door of the stage led out into the hall where all of the music classrooms were, and ey started cataloging additional places where ey could get rest.  The black fabric orchestra seats were a little promising, but ey hit paydirt in the theater classroom.

In the back of the room was the wardrobe area, which also housed rack upon rack of tuxes and identical dresses for the choir singers.  Nestled back behind all of these rows of clothing was an old sagging sofa.  There was zero reason for the room to contain a sofa, but as inexplicable as it was, AwDae wouldn't have been surprised if such a thing had existed in the school ey had attended.

Thanking the gods, or at least whoever had created this sim, ey flopped down onto the sofa.  Slightly musty smell aside, ey was asleep within minutes.

Sleep, while restful, brought intense dreams.  Dreams of twisting passages, corridors lined with lockers that looped back around on themselves, leading always into the same dim light of the student center.  And in the middle sat a menu, like the kind ey could get by swiping eir paw from left to right in any sane and sensible sim.  Every time ey got close to try and read the menu, though, it would slide closed once more, leaving only its shadow behind, an unexpected rendering mistake.

AwDae awoke feeling as though ey had drastically overslept.  Ey hadn't paid attention to when ey had gone to bed in the first place, but all the same, ey felt late.

The day before, with the shock of the transition and the need to explore the auditorium and school for the microphone, ey had never managed to make it outside of the school.  Ey felt silly for that now, and so after ey woke, ey started to plan a way out of the school to see how extensive the sim was.

It was customary to lock the doors of a building that did not lead anywhere in a sim.  For instance, although the Crown Pub did have bathrooms and fire escapes, all things to make it look authentic, the doors were simply locked.  Beyond them would have been nothing at all.  That was simply the extent of the sim.  There were much larger sims than the school itself, and much more intricate, as well.  AwDae couldn't be sure of the boundaries of the sim without exploring.

As ey walked toward the front doors of the school, figuring that those would be the most likely to lead anywhere, ey wondered about what was happening to emself back in reality.  Ey didn't feel hungry, and such things were usually translated in-sim -- after all, ey had still felt the need to sleep -- so something had obviously been done with eir body.

That train of thought led to the question of just how exactly ey had gotten Lost in a sim without being connected.  Obviously, plenty of time had passed, and certainly the crew hadn't left em just sitting on eir workstation after ey had finally lost touch.  Even so, ey should've been pulled back when eir hands had been lifted from the cradles and eir head pulled away from the NFC headrest.  And yet here ey was.  Where was eir body, then?  Some hospital somewhere, insensate and tied to life support?

And if ey was in a hospital, where did this sim live?  A sim this size couldn't simply live in eir gear, with all of the mechanics ey had encountered so far: the fully functioning sound booth and mic, all of the papers in the office, the clothing ey had brushed eir hand across on the way to the couch.

No answers were forthcoming.  All ey had to go on was what was in front of him.

Ey stopped at the front door, staring at the panic bar.  Resigning emself to whatever happened when ey pushed it, ey leaned forward and rested eir paws against the smooth metal, claws clicking against the door itself, and gave a firm shove.

The door swung open and ey laid eir ears back and squinted into the bright sunlight beyond, holding the door open with one paw while the other shaded eir eyes.

Ey saw the cul-de-sac used by parents to drop their children off.  Ey saw the street beyond, and the set of townhouses that lined the street opposite the school.  Ey saw\ldots{}grey.  Ey saw fog.  Despite the very sunny day (ey had indeed slept in almost until noon), ey saw fog.

Fog, usually referred to fog of war or render distance, represented the furthest that the system was willing to render the sim away from the character.  It was occasionally also used as an invisible boundary, so AwDae could not be sure which it was.  That it was there in the first place, closing off the street in either direction about a hundred yards into the distance, though, confirmed that this was indeed a sim, and not just some artifact of eir subconscious.

Ey stepped out onto the sidewalk by the flagpole and stared, shoulders sagging and tail drooping.  There were no answers.  There was nothing for it but to keep looking.
