\chapter*{Chapter Nine}
\addcontentsline{toc}{chapter}{Chapter Nine}

Home was unlocked.

AwDae wasn't terribly startled by this fact.  Although the front door had always been locked when ey had been growing up there, the fact that this whole sim seemed oriented around clues led em to believe that ey'd be able to gain entry to eir old townhome.  On a whim, ey checked the other doors in the complex, and they were all locked, as expected.

Although ey had braced emself for it, there was still a surge of emotion and memory as AwDae stepped through the door and into the entryway of eir old home.  Ey could feel immediately that it was deserted, but all the same, ey felt as though eir mom could be just around the corner in the kitchen, prowling through the fridge, or eir mom's boyfriend laid out flat on the couch, snoozing in front of the TV running old science fiction shows.

It was silent, though, as silent as school had been.

AwDae shrugged out of eir backpack and set it down in the entryway, as ey had done countless times growing up, and paced into the common area, toenails clicking against the hardwood floor.  Ey kept eir eyes peeled for any sign of a clue like ey had been pointed toward back at the school.

The sensation quickly grew to be too much, and the fox sat down on the rug in front of the coffee table, where ey had sat to eat dinner countless times, watching whatever was on the TV.  It was one thing for the house to be so empty, and another thing entirely to be here as eir fox-self, but the two combined were quite overwhelming.  Ey felt eir breath coming in short and shallow, and eir sense of vision being slowly reduced to only what was in front of them.  Eir pulse felt elevated, no matter how still ey sat, and ey found it hard to concentrate on what ey was even supposed to be doing here.

The only thought that they could manage to pull up was, ``Is my pulse elevated offline, wherever that is?''

Ey let out a strangled sort of laugh, trying to picture some doctor's befuddled stare at the sudden signs of anxiety showing in their patient.

The laugh stopped quickly.

AwDae leaned forward onto eir forepaws, stretching eir legs out behind em to lay flat on eir belly on the oh-so-familiar rug, before rolling over onto eir side.  
