\chapter*{Chapter Eight}
\addcontentsline{toc}{chapter}{Chapter Eight}

That night, Carter dreamed of shadows.

And through it all, there was the river.  The muddy and sometimes stinking river.  The Thames which only seemed to generate affection that one might call `grudging' when she thought of it.  When she had first moved to London, it had been one of her best guides - the Thames was always vaguely downhill.

She strode aimlessly along the south bank of the Thames.  The constant renovation of the area had led to not just a single revival, but countless smaller revivals, as buildings were torn down and raised back up, plots of land chopped into smaller portions, buildings growing higher, never quite managing to match.  She passed towers, squat pubs, architecture new and old, but mostly new.  She passed people and crowds, buskers and food carts.  She walked beneath bridges, along railings, past tour boats gliding silently along the surface of the water.

And she passed shadows.

The shadows were like the people of the crowds, a little taller perhaps, but still like the people.  It was as though someone had cut a person-shaped hole out of space and blurred the edges so as to make it indistinct.

It wasn't particularly through prolonged observation, she just suddently seemed to be aware of the fact that the shadows were all behaving in the same way.  They were always following one of the people walking along the bank of the Thames with her.  Always just one person, never changing, never looking around at anyone else.  No one else seemed to see or notice these shadows except her.

She started tailing one of the shadowy figures, as unobtrusively as possible.  It was following a young black woman pushing a stroller, another young child walking at her side, with his hand curled loosely in the fabric of her pants, keeping her constantly in touch.

Carter felt as though she was struggling to keep up -- the harder she tried to keep up with the young mother, the slower she seemed to go.  She tried to call out, but her voice came out only as a whisper.  The shadow reached out it's hand.  The shadow's fingers slid through the woman's hair reaching for the base of her scalp.

Carter screamed, inaudible.

\secdiv
