\hypertarget{sasha-2112}{%
\chapter*{Sasha — 2112}\label{sasha-2112}}

Sasha clutched at the arms of her chair, white knuckled, before standing up.

That her relationship with RJ was so casual was working against her. She knew ey was in the UK, and that they worked at a theater, but for the most part, ey talked about other things. Ey talked about Cicero and Debarre. Ey talked about The Crown Pub. Ey talked about eir past and eir shared world, eir syncosm. Ey rarely got into the present and the embodied world, eir exocosm.

So she had been at something of an impasse, then, with no way to figure out just what had happened to lead to eir disappearance. There were rumors abound in the Crown Pub that ey was Lost, just like Cicero. She would have to admit that she had been the source of more than a few of them, given her guess that perhaps their combined work on figuring out what had happened when discussing Cicero might have been the inciting incident, somehow, to lead to this.

The thing that plagued her with doubts, however, was the sheer improbability of such a thing. How was it that thinking about, talking about, and working with data related to the Lost would lead to one getting Lost themselves? As far as she had read, there was absolutely no such correlation.

Perhaps it was that one who thought a lot about the Lost was more prone to getting lost? But no, that didn't make sense. Obviously there were the doctors, probably entire teams of people studying the cases, and as far as she could find, none of them had gotten Lost, themselves.

Perhaps it was something about the data? Still a dead end, she thought, as she had exactly the same data that RJ had had, as did a few other folks with whom she had shared the deck.

And perhaps ey wasn't Lost at all. There had been the show, of course. And while RJ had never disappeared during performances before, ey had certainly been quieter during her timezone.

No one else had seen em, though, which is what had raised alarms.

After the fact, she was embarrassed at how long it had taken her to think about simply searching eir name. After all, she was relatively privileged in that she had known em in school, and actually remembered eir legal name.

So it was that Sasha wound up reading the same article that Carter had found a few days earlier, confirming all her worst suspicions. She emailed Debarre the link first, the subject line simply the emoticon :/ — distressed as she was, she deleted the auto-corrected emoji and replaced it with the emoticon, feeling, somehow, that that better represented her despair. She considered passing the article around further, but thought better of it. It pulled too hard at her heart, and had left her sobbing when she first found it. Their relationship, brief as it was, had been one of the happiest of the lot she had been through. There was no ire in the way they had drifted from `item' back to simply friends.

The one upshot to finding the article had been the name of the group that RJ worked for.

Thus Sasha, pacing back and forth in front of her workstation, trying to work up the courage to hit send on the email she had drafted.

She had considered sending an email to the leader of the troupe, one Bernhard Johansson, but had decided against it, figuring that the man had far more on his plate running a play than anything, too much to bother responding to a request such as hers. Ditto Sarai Coen, who was listed as stage manager. If the play was still running, she figured both would be swamped.

She had settled instead on a Caitlin Fowler, who was listed as working the lights for the stage. Given all that RJ had told her about working in a theater, she would likely be both the closest to em and one of the least busy, if there were such a thing.

Sasha was just thankful that email addresses had been listed for the cast members. Not the crew, but given the pattern of first-name-dot-last-name-at-sttroupe-dot-co-dot-gb, she was hoping Caitlin's would follow suit.

\begin{quote}
Caitlin Fowler,
\end{quote}

the email still up on her screen read.

\begin{quote}
I apologize for writing to you somewhat out of the blue, but I am a friend of RJ Brewster who I believe works with the Soho Theatre Troupe, and I was wondering if you would be able to provide me with a bit more information about em. I am a friend from high school and remember em working with theater there, and talked with em daily on a sim online.

I know this is a long shot, and I hope this reaches you, and I hope that you are well, all things considered. If you get a chance to send me a note, I would greatly appreciate it. Both email and meeting in a sim would be fine.

Yours.

Sasha
\end{quote}

Sasha had deliberated over this short, two-paragraph email for an hour and a half, deleting and correcting — how much should she ask for? — should she reveal where they interacted? — how should she start the letter, and how should she finish it? Hell, how should she address herself? Her real name wasn't Sasha, though she often thought of herself that way, but she figured that, should they actually meet up in a sim somewhere, that would be the name that this Caitlin would see.

She ran quickly to her terminal and hit `send' before she second-guessed herself any further, and then\ldots{}

Oh, shit.

Now she realized her mistake, realizing that, if they \emph{did} meet up in a sim, Caitlin would be meeting up with an anthropomorphic skunk. Perhaps she had a human av stashed away somewhere, or she could buy one off the shelf real quick. It was seven thirty in the British Isles, she might have time before Caitlin woke up.

No luck. A scant two minutes had passed with Sasha fretting at her keyboard considering possibilities, before a ping alerted her to a new message.

\begin{quote}
OMG OMG we were hoping one of RJ's friends would contact us. We only know so much. Your sim or mine? Meet you in five. C.
\end{quote}

Sasha groaned. Far too little time to switch out an av for something a bit more\ldots{}presentable? A bit more human?

She was still grumbling as she delved in, setting her hands on the cradles and leaning into the headband of her workstation. Once in, she pulled up her in-sim email client and spoke quickly.

\begin{quote}
Caitlin,

Either is fine. Should warn you that I know RJ through furry, and may look weird. My address is @Sasha:of-all-stripes.fur\#home in case you want to meet here, or we can meet publicly.

Sasha
\end{quote}

The reply came in a matter of seconds, half a minute tops.

\begin{quote}
Sasha. Crown Pub? In case you want to tell others. That's what RJ always talked to me. We know about furry. C.
\end{quote}

Her relief was palpable, if incomplete. It would certainly be weird to actually interact with one of the tourists that drifted through that sim. She tapped one of the pre-written replies — ``Sure, see you there!'' — on her client, hoping that that would fit the appropriate levels of urgency that Caitlin seemed intent on, and then dashed over to her tport pad and swiped left, quickly selecting the top, most-visited option.

Caitlin was already there, and Sasha wasn't sure whether to be surprised or not that the woman had a custom avatar. She clearly was a fan of the past, with hair swept neatly to the side to reveal an undercut, a long, tank-top style tunic emblazoned with the word `heh.' running to mid thigh covering only leggings. Something from earlier in the century.

Sasha felt plain in her simple skunk av with baggy shirt and fisherman's pants, fashionable enough by today's standards.

``Caitlin?'' she said, voice raised.

The human waved frantically and ran over to her. ``Sasha, right? There a place we can talk? Anyone else you want to bring along?''

Sasha did a quick scan of the room, picking out Debarre sulking at the end of the bar. She ran over and tapped him on the shoulder. ``Someone who knows RJ is here, want to join?''

The weasel perked up at that, frowned, and nodded. ``Uh, sure. Do they know about Cice?''

``I don't know, but they might. They only said they know about RJ, and that the talked to em about this place.''

Debarre shrugged, then nodded again and slipped out of his stool, pacing after Sasha and nodding to Caitlin on his way to one of the empty booths.

The three settled onto the cushy seats, and there was a moment of silence before all three started talking at once, followed by another silence and some nervous laughter. Sasha gestured to Caitlin.

``RJ's Lost. It happened during a rehearsal.'' She frowned, a finger tapping at the scarred table between them. ``Should back up, though. How much do you know?''

``We read an article about em. Something from a tabloid. It just mentioned the Troupe, which is how I found you.''

Caitlin nodded, hesitated, then offered her hand to Debarre, who shook it cautiously. ``Sorry, I should introduce myself. I'm Caitlin, the lights tech for STT. I was there when\ldots{}when it happened.''

``Debarre,'' Debarre said, sounding gruff. ``Boyfriend's Lost, too. RJ, Sasha, and I were trying to figure out what happened.''

Sasha, fumbling some cards out of her pocket and duplicating them, added, ``We were exchanging a deck on Cicero, Debarre's partner. You don't have to do anything with them, but you might as well have a copy, too. And, hold on.'' The skunk swiped, tapped through menus, and created a new card titled `RJ Lost', and duplicated it twice, handing one each to Debarre and Caitlin. ``One for RJ as well.''

Caitlin swiped up the card and nodded, saying, ``Alright, so here's what I know.'' She tapped the card to add another to the deck and hit record. "RJ was working sound that night, last night of rehearsals, and started having trouble about halfway through. Ey went quiet on the mic, and then missed a cue or two before we noticed what was going on. We called a halt to the rehearsal and found em unresponsive at eir workstation. We pulled em back and hit the panic button and\ldots{}and nothing. Ey was gone and, even out of the station, eir implants indicated that ey was still inside.

``The cops and paramedics seemed to have a protocol for the whole thing, and ey was taken off to the hospital. It all happened so fast. Johansson — that's the director — met up with a woman from the university who said she was studying the Lost and had a talk with her. She said she had gotten information on em, but wanted more, so they talked for a bit. Her name was--'' Caitlin frowned and thought for a moment, then tapped the growing deck to add another card. ``Carter Ramirez. Remembered it was Spanish or something. Johansson mentioned your name, which is why I was so eager to meet up.''

``My name?'' Sasha said, incredulous.

``Yeah. Ey mentioned you. Hell, ey mentioned Cicero.''

At this, Debarre perked up, looking intently at Caitlin, who quailed under his gaze.

``Just that he was lost, I'm sorry. I don't know much beyond that.''

The weasel's shoulders slumped, and he nodded. ``Fair.''

``There's a lot of downtime, working tech. We all chat and\ldots{}hey, why did you contact me, anyway?''

``I figured you'd be the least busy. Plus, RJ said lights techs were always cool.''

Caitlin laughed, brushing her hair back. The motion seemed automatic, as her hair had hardly budged. ``It's true. Anyway, we talked. I don't actually know what more to tell you beyond that. The rest of our relationship was work. RJ was super focused on that, and didn't really chill with the rest of us when ey wasn't working. Ey had a cat, I know that.''

``Priscilla, yeah.''

Caitlin shrugged. ``Sure, I guess. I was hoping you could tell me more, actually.''

Sasha frowned and, on a whim, recounted much of her and RJ's history, all the way back to their relationship in high school. By the end, she was crying freely.

``I didn't know, I'm sorry. RJ never talked about relationships.''

``I think I was eir only one,'' Sasha sniffled. ``There weren't any others that I knew about, at least. Ey was kinda, uh\ldots{}aromantic, I guess.''

Caitlin nodded. ``That tallies, I guess. Listen, I gotta get going, though. I ran at this without really thinking, and your email ping woke me up. I don't know if I can, but I should try sleeping more before the show tonight.''

``No problem,'' Sasha and Debarre said in unison, then laughed together.

``No problem,'' Sasha repeated. ``Thank you so much for meeting up with us. And thank you for the name. I'll see if I can find this Dr.~Ramirez. Keep in touch, alright? And add to the deck if you find anything.''

Caitlin nodded. ``Will do. See you later.''

And with that, the woman signed off. It was generally considered rude to sign off in the middle of a public sim like this, but everyone was a bit jumpy, so the skunk and the weasel shrugged it off.

``Guess now we have another lead,'' Debarre said.

``Yeah. And if she's a big name researcher, I bet she knows about Cicero, too.''

At that, Debarre brightened, and the two spent the rest of the night talking.
