\hypertarget{sasha-2112}{%
\chapter*{Sasha — 2112}\label{sasha-2112}}

Sasha wanted to be pleased with the rapidity with which everything was taking place. It hadn't even been a week, and here was one of the lead researchers of the Lost getting in touch with her.

She wanted to be pleased. She wanted to believe that things were moving forward. Wanted more than anything to smell the lingering scent of fox and cat in the Crown Pub, just to know at they were there.

And yet, she wasn't. It was all wrong. Everything about all of this was wrong. There was no way that she would be able to forget that, despite feeling like things were actually getting done, she was still doing all of this for what was widely acknowledged to be a lost cause.

She began typing.

\begin{quote}
Dr.~Ramirez,

Wow, I'm glad you got back to me! I was not expecting that. I'm a little confused as to why, but I guess no sense in questioning it.

Do you have information on RJ and Collin? I'll gladly give what I can. They both were good people. RJ and I went to school together, and the three of us spent a lot of time together in sim. They would spend hours talking politics (mostly Collin yelling).

The last thing I got from RJ was this:

\begin{quote}
AwDae here. Looks like there's a lot going on in DDR activity (where'd you get this, Debarre?). Cicero was into a lot, and I'm not trying to go all conspiracy nut on you all, but do you think that maybe he got in too deep or something? Not saying someone tried to do it too him or anything, just that maybe the more one uses the net, the more likely it is to happen to them? I mean seriously, look at all of his votes, and his stash of credits! I'll keep poking at this after rehearsal.
\end{quote}

Do you have any idea what that might be about? I mean, I said Cicero was super into politics, but do you think RJ was onto something here?

I've copied Cicero's partner, Debarre (don't know real name, sorry!) and Caitlin Fowler from where RJ works.

Sasha
\end{quote}

The response was only an hour in coming. As with Caitlin, the response was short and to the point.

\begin{quote}
Sasha, all - @129822922:d.no.onehere.board\#default
\end{quote}

A throwaway user? The sense of wrongness intensified.

All the same, Sasha logged in and swiped her way over to the address Carter had provided.

As with most throwaway rooms, it was a cube measuring about five meters on a side, with a faint grid lining the floor, and as with most throwaway avatars, Carter was visible as a gesture at humanity. The lines of a face visible only enough to show hints of expressions. Average height. Gray skin. Androgynous hair.

``Sasha, I'm sorry for meeting you like this.''

The skunk shook her head. ``It's okay, I guess. Can you tell me why?''

``Will you accept \emph{because of a dream} as an answer?''

Sasha frowned.

``I suppose not.'' Carter hugged her arms around her middle, a gesture that felt distinctly out of place from the gray avatar. ``You mention, uh\ldots{}AwDae investigating DDR activity, as well as Collin's own involvement but--well, should we wait for others to show up?''

``I don't know if any of them are coming.'' She felt the tightness of panic in her chest intensify. ``I don't know where Debarre is, and I imagine Caitlin's show is on.''

The figure before her frowned. ``Right, I suppose so.''

Sasha pulled up her deck. ``I can take notes, perhaps,'' she allowed. ``I don't suppose you'll want ACLs with a throwaway.''

``No, probably not. Notes will have to do.'' Carter took a moment to compose herself, and then continued as she was saying before. ``You mentioned the relation to DDR, and we already know that Collin and RJ were friends. This is something we've been looking into with my group. The possibility of a social vector, I mean. It's gone poorly.''

``How do you mean, poorly?''

``Well, there was unexpected resistance within the team, and then shortly after taking this tack, the hammer came down from above saying we had to fire someone — someone not a neurologist — and shift our investigation to the neurological side.''

Sasha blinked. ``Are you suggesting you're being told to not look at social aspects?''

Despite the vagueness of the features on the avatar's face, the smile still carried the weariness heard in the tone of its voice. ``I suppose, yes. I had a dream about shadows following everyone and I guess I could say I'm a bit spooked. Too many coincidences in too short a time.''

``I'd chalk it all up to paranoia if I weren't feeling so anxious, myself.''

``Any particular reason why?''

``I, well.'' She brushed her paws down over the fur on her forearms, taking the moment to figure out a response. Any response. ``I don't know. Things are moving so quickly. I don't know how to explain. I met up with Caitlin and she told me a lot, and then I emailed you, and your two responses didn't do anything to assuage my fears.''

Carter nodded, didn't respond.

``But I don't know that anything you could have said beyond \emph{we fixed it, AwDae's awake} would have done anything but. Even your \emph{we're working on it} form letter was anxiety-inducing in its own way. I know you're working on it. I imagine a lot of people are.'' She hesitated, then added, ``But that doesn't really help to hear.''

``No, I imagine not.''

``And to then get another email saying that you wanted to talk things through outside the context of your work just added to my fears. Like, what could that possibly mean?''

``I'm sorry,'' the figure said dully. ``I really can't help in the context of work.''

``I know. I read up a bit on WFHIPA.''

``Yeah.''

The panic was slowly transmuting into anger. Sasha didn't like it, but felt powerless to stop the change. ``And now here you are in all gray talking about, what, conspiracy theories?''

``I'm sorry, Sasha. I really don't feel any better about this than you. I'm not the paranoid type, usually, but I think Sanders\ldots{}well, I suspect that one of my colleagues has motives that go beyond just his focus on neurochemistry. I think they go beyond just the university.''

Receiving more information tempered that anger. ``How do you mean?''

``Well, I said the hammer came down. It did so in the form of grantors threatening to pull funding from the project.'' Carter shrugged. ``And I believe that the research coordinator — that is, the university itself — was just passing along that message. I think the stress is coming from higher up.''

``Wait, grantors?''

``Yes. The project is hosted by the UCL, but is being funded from external sources. Grants, that sort of thing.''

``Who's writing the grants.''

Carter held up her hands. ``No clue. That's the thing. Why would the grantors throw their weight around, saying that we should follow specific lines of research? That's not their job.''

``Have you even published data that would suggest anything but a--'' Sasha dug for the term. ``Neurological cause?''

The figure stiffened. ``What?''

``I just mean AwDae got lost only a few days ago, and you said that ey was the reason you started looking at the social aspect, right?''

Carter began pacing. ``Right, yeah. And we haven't published anything along either front in that time. I can't say this is helping my paranoia any.''

``Do you think this coworker--''

``Sanders?''

``Do you think Sanders is, what,'' Sasha said, struggling to keep her voice in check. It seemed to want to simultaneously rise in panic and also sneer at the very suggestion. ``Some sort of shady government plant?''

``I gotta go,'' Carter said. ``Don't use the DDR for a while.''

Then she teleported away.

There were three small alarm bells, and Sasha found herself back in her home sim. The throwaway had been recycled.

``\emph{Fuck.}''
