It began, as many things in my life do, on the Internet.

This is, you must understand, before I had dived headlong into furry with enough zeal to turn me from a boy into a fox by way of dragon.  That would come later, but not too much later.

No, this is a year or so before I'd started getting into animal people on the Internet.  I had joined a site called, and I say this with a cringe, `Puberty 101'.  I cringe because, even though it was specifically designed to be a site for folks 20 and under to talk about romance, hormones, and sexuality, it was almost certainly a breeding ground for all of those monsters we heard about on the early days of the internet.  The pedophiles and the predators, eagerly waiting in this new extension of their beat-up white vans to offer us whatever passed for candy in exchange for vague sexual acts that would destroy us as children and land the perpetrators in jail.

It was later renamed GovTeen, thank goodness.

Nonetheless, there I was, signing in under the name \texttt{!xabbu} in order to quietly, carefully come out as bisexual, later as homosexual.  I was among my people, there.  I could go to one page on the forum and ask a question about Visual Basic, then go to another and find out that there were people like me who were Guys Who Liked Guys.

It's where I met Danny, a lovely, nerdy soul who would talk to me for hours on end about computers, about sex, about living in New York.  This sidled casually into dating in a way that struck me as absurd at the time.  Having been in my fair share of relationships by now, I know how often it is that a friendship turns into more.  We would call for hours at a time, talking about this or that, just being young and in love.

Eventually, I wound up coming out to my mom through the not-so-subtle tactic of leaving a book full of stories of folks about my age coming to terms with their sexuality on top of her stack of mysteries.  Scared shitless as I was, I did so right before heading down to stay the night with my dad; I couldn't bear to handle that as a face-to-face conversation with her.  She called me that night at my dad's to confirm that I was actually coming out to her, saying that we would talk the next day when I was back at her place.

Then I called Danny and cried over the phone with him.

It was a scant few months from that point in my life to the time when I discovered furry.  Danny and I eventually drifted apart --- our trajectories were never wholly in line, though I treasure everything about our time together, and will always miss him\footnote{Danny passed away in April of 2014, a fact I didn't learn until recently.  This is one hundred percent a footnote and totally tangential, but every time I remember this, want to tell someone and share a bit of the joy I had.}.

Furry was something that had never really jived with Danny.  He knew what it was, of course --- word travels, and all --- it just wasn't his thing.  When we drifted apart, he drifted into drugs and hacktivism (although that word had yet to come to exist at the time) and I drifted right into the waiting arms of furry.

Within furry, I started meeting folks right away.  Gone were the days of pining for a boyfriend on the GovTeen forums, I found myself hip-deep in a dating pool of folks with whom I could talk for hours about something that we both shared an interest in.

I promise I'm not just wandering.  I started this by saying it all began on the internet, and truly, it did.  I came into my own as a sexual person, a romantic person, and an adult through my interactions on the internet, and through 99\% of that time, furry was there as a large part of my life. Furry as a social fixture, furry as an integral part of the online experience for me.  Through furry, I came to a deeper understanding of love and relationships than I think I would have come to had Danny and I just stuck it out and found a way to work together.

I think that relationships within a subculture are going to be stronger than those bridging interests.  There was Danny, and later Matt, and in college there was Kayla, but in the end, the stress of dating across boundaries of identity such as that always became too much of a stress on the relationship to maintain.

With that thesis under my belt, I started to ask around to see what it is that draws furries to other furries --- or to other non-furries --- and how the fandom interacts with the ways in which we play out our relationships.  Does the fandom strengthen relationships?  Are relationships within the fandom harder to talk about outside the fandom?  What is it we get out of sexual and romantic relationships that can differentiate the two?

I really am in love with furry, have been for years, but it's worth taking a look at why, and the consequences of that relationship.
