``True Name,'' May said, interrupting the other skunk's tirade. ``Wait.''

Wrong footed, True Name frowned. ``What? Why? I do not--''

May held up her paw, a brief glance at the ceiling hinting at a sensorium message elsewhere.

Ioan frowned as well. Intuition told him the discussion they'd had earlier had gone beyond the hypothetical. ``May, are you sure--''

True Name jolted upright in her seat on the couch. ``What the fuck is--''

``Accept it,'' May said, and ey could see the force of her gaze boring into her cocladist. ``You must do this. You have to.''

Her face contorting with the strain of holding what must be a very large impending merge at bay without either remembering or forgetting it, True Name gasped. ``May\ldots{} May Then\ldots{} Why\ldots{}''

Eir partner's expression softened. ``Please, my dear. I think you need this. I think we all need this, if we are to move forward.''

The skunk nodded shakily, attempted a dry swallow, and then let the merge of End Waking's centuries of memories crash into her.

The change was immediate and more dramatic than ey'd expected. Ey had been expecting a shell-shocked look and maybe a few minutes of silence, but instead True Name's expression melted into a glazed, nearly stroke-like stupor. The glass of water she'd been clutching at but had yet to drink tumbled to the floor and, as all her muscles gave out at once, she began to slide off the couch.

``Shit. Shit! Ioan!'' May shouted.

Ey was already on eir feet and halfway around the table, thankfully in time to catch the skunk before she slid down into the pool of water on the floor. Ey managed to get eir arms under hers enough to hoist her up into the couch again while May ducked around to lift her feet so that they could lay her out on her back.

They both stared at the limp True Name.

``Fuck,'' eir partner murmured.

``What just happened?''

``One second,'' she said, waving away the spilled water so that she could kneel by her down-tree instance. There was a moment's hesitation before she brushed some of the skunk's longer head fur away from her face. ``Can you close your eyes?''

When True Name didn't respond, didn't move, May gently brushed her paw down to close them for her.

After lingering another moment, she stood slowly, took Ioan's hand in her paw and led em to the balcony. As soon as the door shut behind them, she burst into tears.

Ey guided her carefully to the bench swing to sit her down, letting her cry herself out against eir shoulder.

``I am sorry, my dear,'' she said when she could speak again at last. ``Really, truly sorry.''

Ey shook eir head, kissing her between the ears. ``You don't need to apologize to me. I'm more confused than anything. Was that your and End Waking's plan?''

She pressed closer to em. ``That was him merging back down, yes. I did not expect that, though,'' she said, and ey could hear that she was on the verge of crying once more. ``I never intended to hurt her.''

``Can you explain what happened, at least?''

She nodded, swallowing down that wave of tears as best she could. ``We are good at forking and merging. Very, \emph{very} good at it. I am pretty sure you know that, though.''

``Did something go wrong, then?''

``End Waking has not merged down in nearly two centuries. He has diverged quite far in that time, as is to be expected, which means the potential for conflicts.''

Eir frown deepened. Ey thought ey could tell where this was going. ``Aren't those usually just when memories don't line up, though?''

May gave the barest hint of a shrug against em. ``You have met her, and you have met him. Their viewpoints are almost diametrically opposed, yes?''

Ey nodded.

``Viewpoints are built atop a collection of memories. That they can share so many memories and yet have such different outlooks on the world and their actions is a subtler, but trickier sort of merge conflict.'' She paused, took a deep breath, then continued slowly. ``I pressed her to accept because I knew that she would accept the merge as smoothly as she always does if there was external pressure. She merged blithely and took on two hundred years of End Waking all at once. All of his memories. All of his penitence. All of his loathing for what he did, what she was so proud of.''

``And it was too much?'' ey asked.

Her face screwed up again as she nodded. ``I nuh-never wanted t-to hur-hurt her,'' May stammered as the tears started to flow once more.

Ey got eir arms around her again and held her close. A quick glance through the windows showed that True Name still lay on the couch, breathing shallowly.

``May, I want to ask you something,'' ey said, once she had calmed down some. ``And\ldots well, I think it'll probably make you cry again, but I want to make sure we stay open about this. I'm really not asking this to take a jab at you. Is that okay?''

She whined quietly, but nodded all the same.

Ey took a deep breath, keeping eir voice as gentle as ey could. ``I'm not upset with you, but I need to know since this is just getting weirder and weirder. Are you sure you didn't want to hurt her?''

There was a long silence before she replied, and ey could tell she spent much of it counting her breaths, one of the exercises that had worked best to ground her. At least she counted as best she could between sniffles.

``I think,'' she started, then cleared her throat. ``I know a part of me was acting out of vengeance.''

Ey nodded. ``We talked about that, yeah.''

``Right. I think that part was hoping that it would be a rough merge to knock her down a peg, yes,'' she said, then let out a shaky sigh. ``I did not think it would be this bad, though. I am really sorry, Ioan. I want to be a good person.''

Hugging her tightly to em, ey said, ``It's okay, May. You \emph{are} a good person, promise. Just that even good people feel resentment.''

She nodded, fell back into breathing exercises.

``And I believe you when you say you didn't want to hurt her. Both those--''

She elbowed em in the side. ``Right, yes, yes. Both can be true at once. You know we have the same therapist, right? She says the same things to me.''

Ey smiled, pleased to hear the humor in her voice. ``Sorry, May.''

She wormed her arms around em to give a tight squeeze. ``It is alright. You are just a nerd. Both of those things can be true, too.'' After a moment's hesitation, she asked more quietly, ``Can you see her? Is she okay?''

``She's rolled onto her side. Still breathing pretty quick.''

May nodded. ``Let us get back in and check on her, then. We may want to get her into bed. Being comfortable can make it easier.''

(They do, ey carries her, May stays by her side, Ioan leaves so she can apologize in private)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
