\subsection*{SakaraFox}
SakaraFox would tell you he’s from the mist-shrouded past some 12,000 years ago, but in truth he’s a railway worker and prose-fiction writer who hails from the West Country of the United Kingdom. With a keen interest in history, enough railway photos to fill a hard drive, and an insatiable appetite for Mesolithic prehistory, it’s recommended not to get him onto these subjects unless you’re happy to have your ears talked-off. It’s no surprise then that these make up the bulk of his writing, which mostly explores an ancient past which we often neglect. His work can best be found on FurAffinity, or followed on Twitter @Metro\_Fox for updates on the latest works and happenings. FurAffinity: furaffinity.net/user/metrofox2/

\subsection*{Utunu}
Utunu has been a video game developer since the mythical early '90s, and is fond of worldbuilding, linguistics, ancient history, fantasy, and Oxford commas. He's written a few short stories, and has received both a Cóyotl and Leo Award.

\subsection*{Huskyteer}
Alice "Huskyteer" Dryden's short stories have been published in and out of the furry fandom, and have won two Cóyotl Awards, two Ursa Major Awards and one Leo Award. She edited the Furry Megapack for Wildside Press, and in 2019 she was Guest of Honor at Fur the 'More 007: Furry Never Dies.

\subsection*{J.F.R. Coates}

\subsection*{NightEyes DaySpring}

\subsection*{Rose LaCroix}

\subsection*{Madison Scott-Clary}
Madison Scott-Clary is an author and technical writer living in the Pacific Northwest with her two dogs and her husband, who is also a dog. She's the author of the Post-Self cycle, a series of gender-weird, meta-furry sci-fi thrillers, and the Sawtooth books, collections of short stories from a small town in a flyover state. Her work can be found at makyo.ink

\subsection*{Kayodé Lycaon}
Kayodé Lycaon is a gregarious painted wolf living in the questionable habitat of southwestern Ohio. By day, he pretends to be a human, writing software. At night, his paws weave stories from threads spun from the fertile grounds of his imagination. You can find out more on his website, kayode.co

\subsection*{Rob MacWolf}
Rob MacWolf lives somewhere in North America waiting for the world to end. In the meantime he practices neo-paganism, writes poetry, and co-hosts the audiofiction podcast The Voice of Dog, at thevoice.dog.

\subsection*{Thomas ``Faux'' Steele}
Thomas "Faux" Steele is an author and attorney who has been creating short stories since 2015. He enjoys writing in many genres, including horror, science-fiction, fantasy, and adult contemporary. He specializes in descriptive stories with rich world-building whose written words render a painting in the reader's mind. His work has been printed in many anthologies, including FANG Vol. 7, Exploring New Places, and Beast Vol. 1 as well as many 'zines including \#OhMurr. In his free time, he's an avid coin collector and fancier of antiquities and fine art, almost all thrifted or picked from estate sales.

\subsection*{J.S. Hawthorne}
J.S. Hawthorne was raised in New England, but now lives in exile on Long Island, where she pretends to be a lawyer by day and might actually be three magpies in a trenchcoat. When she isn't writing either fiction or law, she mostly enjoys running more Dungeons and Dragons games than is strictly necessary and collecting books written by her friends. She promises she'll get around to reading them eventually, honest.

\subsection*{Haya Baru}
Born 3000 years too late to devote their life to the proud and noble art of extispicy under the tutelage of a state temple, Haya spends their free time reading history books, depressive 19th century philosophy, and gay romance novels instead. They have neither children nor pets, instead filling the resulting emotional void with an ever-growing conlang that was torn from the pages of an Akkadian language textbook. Although they work as a software developer, they plan to become a priest should the temple of Ištar ever return. If they ever undertake this momentous career change, they hope to revive the long-lost personality archetype of a smugly pious polytheist.

\subsection*{Pascal Farful}
Pascal Farful is an author, musician, fursuiter, railway enthusiast and photographer. At one point almost all of these occoured at once. He lives in a hollowed out volcano on the outskirts of the UK where Angels Pizza Company fear to tread.

\subsection*{Casimir Laski}
Casimir Laski is a writer, YouTuber, and literary critic from Virginia. He is the author of Winter Without End, a post-apocalyptic survival story told from the perspective of a dog, inspired by the animal stories he grew up reading. Additionally, he writes for Furry Book Review, and operates the YouTube channel Cardinal West, primarily devoted to discussion of literary xenofiction and western animation.
