The signs were everywhere, even young Kuveli could read them from beside the low-burning fire. It was much too dark to see the storm clouds forming overhead, but he knew without a doubt that they had come. He knew because they had swallowed the very stars and filled the air with a strange tension that made his fur stand on end.

A great dance was about to take place high over the steppe, and the mighty black reindeer, Peruvaan - spirit of the storm - had graced the young fox with the best spot at his fire.

Yet, Kuveli felt no joy at the prospect. In fact, his hackles were raised and his heart was pounding in his chest, like the thrumming hooves of a stampeding elk.

He was so fixated on the sky that his eyes were frantic as he sat in complete stillness. Kuveli didn't even notice how tight his grip had grown, his sharp, vulpine claws tearing holes into the patchwork animal skins that made up his simple skirt.

``Careful now, little bud,'' said a warm voice from beside Kuveli, a pair of large paws suddenly reaching over and gently holding his own. ``A grip like that could break rocks. You haven't hurt yourself, have you?''

The little fox turned toward the voice, seeing the familiar, doting smile of his older brother in the dim light of their fire. His icy-blue eyes, a feature the two shared, seemed to glow in the darkness. Those eyes were as sharp as the stone spear lying between them as they carefully looked over the younger fox for injuries.

``I'm fine-!'' Kuveli snapped, pulling back his paws and pouting. ``I just want to watch the storm, I wasn't doing anything.''

But in truth, he really was terrified. Kuveli so badly wanted to bury his face in his big brother's scruff. He wanted to feel a gentle arm around his head, and hear his brother tell him that it was all going to be alright, but\ldots{}what kind of a hunter would he be if he couldn't face his fears?

``Nothing except tearing holes in your clothes so I have to spend all tomorrow sewing patches on them. Making more work for me, right, brother?'' Sakara chuckled with a teasing smile, and ruffled Kuveli's head fur.

The young fox returned a timid growl and shook his head, at which point Sakara decided to escalate and wrapped an arm around his brother's shoulders, pulling him into a tight hug. Kuveli resisted for a moment, but quickly succumbed and welcomed the warmth of his brother's body against his cheek, and the beating of his brother's heart in his ear.

Kuveli couldn't deny the comfort he felt in moments like these. It was like being a kit again, swaddled in warm furs and listening to whatever stories Sakara could dream up. No responsibility, no worries, and no future to think about.

``I'll sew them back together; the shaman says I need the practice,'' Kuveli replied at length, breathing a sigh as he stared nervously at the shifting mass of black clouds.

``You know Sana means you need practice sewing wounds closed, not leggings, right?'' Sakara cocked his head at his brother, but Kuveli did not humour him. His mind was once again focused on the coming dance, his thoughts filled with dread of its deafening drums.

Letting out a huff of frustration, Kuveli pulled himself from his brother's arms and lazily slumped down in the grass. Sakara would never say it to his face, but he knew it nonetheless. He knew it from the way Sakara spoke down to him, and to the fates their shaman had foreseen. ``Coward.'' That's how Sakara saw him, forever his little ``rabbit-chaser'' no matter how many deer he slew, no matter how talented a hunter he became. It annoyed him to no end at times, when he so badly wanted to find his place like the rest of the kids his age.

He didn't even have a horse, unlike the rest of his tribe. They were a tribe of fierce riders after all, and it was nothing short of shameful for a Lentavohi like him not to have a horse of his own, especially when the others had ridden almost as long as they had walked.

``You will be like them in time, little bud,'' his brother would always say in his usual, soft-spoken voice. ``But this is your tenth summer, and you still have so many more to look forward to before you carry that burden.

``Enjoy what I never got to.''

That last part had always lingered in his mind. He knew his brother had lost his boyhood years when their ma and fah had passed away, not long after he had been born. It had to have been hard, but\ldots{}how was Sakara protecting him by coddling him away from his destiny?

Their shaman had always been good to the little fox. Even though he was only a few summers older than Sakara, the otter seemed to possess an impossible wealth of wisdom, beyond that of even the tribe's few elders.

And within all that wisdom, he had strangely always seen something in Kuveli. Something magical that he himself could not yet see.

Honestly, the prospect that he might be more than just an ordinary hunter scared him. The mere thought of it made him hunch over, like a great weight had been placed upon his shoulders, the weight of responsibility that he would carry with him if he walked this path. So much knowledge to memorise by heart, to be called upon at a moment's notice, else someone he cared for might be maimed or\ldots{}worse.

Sana had taught him some things already, using the wounds that presented themselves as the days went by. Cuts and scrapes mostly, and a few bad gashes, always smeared with honey to stop the bad spirits getting at them, followed by a boiled scrap of leather to wrap around the wound. But such paltry injuries could never have prepared him for the horror of broken bones.

Last winter, a hunter's horse slipped and crushed his leg. As a hunter himself, Kuveli thought he could stomach it, having gutted animals and extracted their bones for tools and marrow, but it wasn't the same.

When the bone pierces the flesh, and the victim is crying, screaming, begging for his soul to be free of the pain, it takes a whole different kind of nerve. Sana had done all the work himself, and yet the little fox still had to flee the horrific scene while choking back a disgusted gag.

Suddenly, Kuveli was shaken from his thoughts by an almighty boom and his eyes filled with a blinding flash.

By Äituri - their tribe's patron spirit - he had almost leaped out of his skin at the sound of it!

What few nerves he had left unfrayed were at their limit, his hackles raised, and his lips peeled back in an instinctive snarl.

Those wide, arctic blue eyes were utterly fixated on the gnarled finger of lightning that, in a fleeting moment, had come down and struck the steppe with the power of all the stampeding aurochs in the whole world.

The dance had begun.

All across the land would hunters and animals alike hear almighty Peruvaan, as he stomped his hooves to the rhythm of the drums and the chanting of earthbound shamans. No doubt his own tribe's shaman would be joining them, voiceless as he was, divining what he could from the rhythm of the storm god's dance.

It was strange, but deep in his heart Kuveli knew he wanted to join them. He wanted to don the antlers of the reindeer and paint lightning bolts on his calves, just to dance and sing to the rhythm of the storm until his voice was hoarse and his legs could no longer carry him.

``Oh, gods damn it,'' his brother's voice cut through his thoughts. The words puzzled Kuveli for a moment, looking to Sakara for answers and catching a glimpse of something just beyond the firelight. ``Stay here, bud, I've got to make sure Pekka doesn't break free again. I don't want to be chasing her to the ends of the world, again.''

Sakara jumped to his footpaws and brushed off his leggings, turning for just a moment to offer Kuveli a reassuring smile and a few pats on the head. He responded with a long, worried stare, but said nothing.

It was at that moment when something strange happened. Another bolt of lightning suddenly ripped the sky in two, but rather than fear Kuveli felt something else\ldots{}

His heart was still racing as fast as before, and his hackles were still raised in warning, but the primal fear that had eaten away at his heart and resolve was not there anymore. Instead he felt a familiar, yet, somehow, completely unknown strength. It was like the rush of the hunt, compelling him to move with haste, only it wasn't coming from within him.

Was it the storm?

Whatever it was, Kuveli felt a pit of dread forming in his stomach. If it was the storm then it was something not of this world, something\ldots{}magical.

In his brief time with the shaman he had learned just how dangerous the world beyond the veil could be, like the ways demons could poison wounds and slay innocents with invisible claws. How could he possibly face such horrors alone and without even the knowledge to see them?

Only, he wasn't alone. Not truly, anyway.

Prying his gaze away from the gathering storm, Kuveli watched as his brother quickly made towards their horse. The darkness was already swallowing him, the fire growing dimmer as the winds began to pick up and smother the starving flames. Kuveli knew in his gut that he had to follow his brother, it was the right thing to do.

Or was that merely a demon whispering in his ear, like those that had caused him so many night terrors when he was younger?

For a moment he remained still, stewing over the decision. His mind felt as though it were being torn at by the fangs of two hungry wolves: the wolf who wanted to stay, and the wolf who trusted his gut.

Gritting his teeth, Kuveli rose slowly, placing his fate into the paws of something far beyond his understanding.

He drew a shuddering breath and stepped towards the smouldering fire, where the dying embers hissed their final breaths. His leather pouch and a pair of brand new leather leggings lay beside the fire. He took them gingerly, slipping into the leggings and tying the pouch to his belt.

Then, instinctively, he laid a paw on his chest and pressed against something hard. His crude slate knife. It was swaddled in a leather sheath, which his brother had sewn into the shoulder strap that held up his skirt, so he could always keep it close. A good hunter never went anywhere without his knife, and if that's what he wanted to be, he wasn't going to forget about it now.

With that, Kuveli turned his head into the wind and made off in the same direction as his brother, catching a glimpse of his silhouette when another bolt of lightning cracked viciously overhead.

A sign, maybe, like Sana had once explained. But Kuveli refused to believe so.

The dirt and dust crunching beneath his bare pawpads quickly turned soft, as Kuveli entered the grass that towered almost a head above him. With each gust it rustled and swayed, moving like the waves of the great sea he had once visited, many turnings of the Moon ago. It would be easy to get lost here, and end up wandering in circles for spirits only know how long.

For a second he paused, a distant thoom making his stomach drop as he glanced about himself. Everything seemed to blur into an identical image, the wall of quivering grass indistinguishable from itself. He couldn't have lost his way already; he had only just begun.

But then, between the rumbles of thunder that shook Kuveli and the howling of the wind that bristled his fur, he heard a sound not of Peruvaan's dance.

A high-pitched scream carried to him on the wind, followed by a deluge of curses. It was Pekka and Sakara, arguing as they often did.

Steeling himself, Kuveli followed the sounds of their voices, brushing aside the brittle blades so parched of rain this summer - some merely crumbling at his touch - before he stumbled into another clearing.

A bolt of white snapped across the sky, illuminating the scene just long enough for Kuveli to make it out. Their horse, Pekka, was reared up on her hind legs and kicking wildly, her dapple-grey coat sparkling with dew. And standing bravely in her way - not even half the reared horse's height - with a length of rawhide rope tied around his waist, was the little fox's brother.

``Easy, girl!'' barked Sakara, his voice clearly strained as he clung to the rawhide rope - which Kuveli now realised was tied loosely around Pekka's neck at the other end.

Pekka landed with a thud, her heavy hooves kicking up a cloud of dust that sent Sakara into a hacking cough. But the huge mare wasn't done, as she kept bucking her head against the rope, huffing and snorting. Even grounded, Pekka still stood a head taller than his lanky brother.

``By Äituri, you're as bad as the boy!'' Sakara growled as he tugged back on the rope, still not noticing Kuveli. ``Since when does a big mare like you get so afraid of a little storm?''

``What did you-!?'' Kuveli yelled in retort, before throwing a paw over his agape maw. Had his brother really just said that? And behind his back too, when he thought Kuveli couldn't hear him. Did he speak of him like this around the other hunters too?

Kuveli let his paws fall to his side, his heart sinking as he stared across at Sakara, who was staring back with a shocked look in his wide, shining eyes. His brother of ten summers and ten winters, who he had always loved as his only flesh and blood. His brother who had raised him, made toys for him, taught him everything to know about life. The brother who had, and always would be, his entire world. And this was what he thought of Kuveli?

The pain the little fox felt was indescribable, like a knife had plunged into his back and pierced his heart, from which poured a flood of emotions all at once.

Anger. Hate. Sadness.

And most of all\ldots{}

Betrayal.

And then it overcame him, all at once. With a snarl, Kuveli marched towards his brother with purpose, spurred by the emotions swelling within him. Raising a clenched fist into the air, he yelled at Sakara with all the force his small frame could muster.

``I knew it! I knew you said things behind my back. I knew you told people I was just a scared little kit. That's why I still don't have a horse, or why they haven't invited me to hunt. You held me back, to `protect' me, isn't that it?''

``Kuveli\ldots'' exhaled the older fox at length, but he wasn't done.

``I won't let you hold me down anymore, now that I know,'' Kuveli said, sniffling as his eyes became heavy. Sakara was heartbroken as he watched his little brother's eyes fill with tears. ``I'll walk my own trail, chase the game I am destined to catch. I will listen to every drop of wisdom the shaman has, because he knows better than you.''

Stopping at an arm's length from Sakara, the little fox stared up at his brother's sullen features. His often perky expression had evaporated, his bright eyes now sunken and dulled, unable to look back at Kuveli, ears pinned back and shoulders slouched. The rope fell by the wayside, hanging slack between the horse and the fox, as Sakara timidly reached out.

``I'm sorry I hurt you, little bud,'' he mustered in a voice so full of defeat that Kuveli almost struggled to hear him. ``Please believe me, I meant nothing by it. I was just-''

A bright flash cut him off, followed by another deafening kaboom. Pekka squealed as if she had been driven feral, and bucked her head violently to the side. With this single motion, the rawhide rope snapped taut and Sakara was ripped off his feet as though he were little more than a leaf on the wind.

``Big brother!'' Kuveli sprang forward, reaching out in vain for any part of Sakara, left to watch in horror as he was dashed against the earth with a sickening crack.

A shrill scream sent a chill up the little fox's spine as Sakara curled up and gripped his leg, teeth grit as he writhed in the dirt, as a powerful rear hoof stomped down beside his head. The sight of it banished the inferno of emotion within Kuveli and, as he rushed towards Pekka, replaced it with something born purely of instinct.

``Please calm down, Pekka,'' the tiny fox pleaded as he threw himself at the colossal beast. Kuveli had never taken to horses like his tribemates, but he had always watched how they soothed their mounts, who often acted like oversized infants throwing a tantrum. ``You've hurt Sakara now, are you happy? Please just listen to me, listen to the sound of my voice and relax. It's only a storm. The spirits will not hurt us,'' he continued to beg through gritted teeth.

In the back of his mind, Kuveli heard a lone, dissenting voice. He could swear he almost heard it snicker as it teased, ``Like that ever calmed you, coward.''

It was certainly the voice of a demon. Kuveli had always suffered with demons, clawing at his dreams and filling his nights with terror, unless his brother was there to ward them off. They feared the strength of his soul. Clearly they thought he had a cowardly soul too. And they were fearless this time, whispering into his ears so openly. Something must have emboldened them, most likely the dance and the storm high above, which must have kept Äituri busy with her attendance.

And yet, as Kuveli pressed his cheek to Pekka's breast and listened to the thrumming of her mighty heart, he muttered prayers under his breath. He begged the almighty White Mare to come and drive away the storm, and promised he would leave her a great offering of amber for every day he went on living.

But it was no use.

Even as he kept trying to reassure the horse, stroking his paw gently along her neck and nose, down her chest, all the little fox could feel was tightly woven muscle and sinew.

Horses were beasts of pure strength, after all. As Pekka proved when she suddenly bucked her head to one side and took off like an arrow.

Surprised, Kuveli grabbed her neck, using his momentum to swing over her shoulder, legs kicking helplessly, clinging to her long, black mane for dear life.

Behind them, he heard the rope snap taut and a pained yelp as Sakara was hauled along behind them. The little fox just barely caught a glimpse of his brother with his arms over his face, trying to protect what he could before disappearing into the tall grass.

``STOP!'' he cried with all the strength he had left, his arms growing tired and his feet finding no purchase.

Thunder boomed overhead, growing in intensity, while the plains were illuminated under the constant lashing of white-hot bolts. Ahead Kuveli saw a forest lying directly in their path, the birch and pine trees naught but growing silhouettes in the darkness. And it filled him with dread.

A forest meant danger, with low-hanging branches just waiting to snatch him away or, worse, stray rocks and boulders hidden in the undergrowth, eager to split his brother's skull open.

Kuveli kicked his legs again, jamming his foot into Pekka's stomach, crying out for her to stop, pleading, praying, anything that might bring her to a halt. But before he knew it, they had arrived. Trees rushed by, grazing the hairs on his tail, one thorny bush even snagging on his back and tearing his flesh.

He screamed, the pain seizing his body, sapping the last of his strength. It was too much, he couldn't hold on anymore. His right paw slipped first, followed by the other.

He fell, and it felt like the whole world slowed down around him. The wind rushed through his fur and whistled in his ears. The foreboding figures of the trees stood over him, laughing. His heart was full of fear, regret even, as a single thought passed through his mind\ldots{}by the spirits, would those really be the last words he said to Sakara?

Kuveli didn't have to regret it for long, as the ground quickly rose to meet him. The last thing he remembered was the crunch as his muzzle bit the dirt.

\secdiv

\noindent A strange veil of wispy grey encompassed Kuveli, as he stood in the midst of what appeared to be a thick fog, the scent of petrichor filling his nostrils. It was so strong, stronger than after any rain storm he had ever experienced. And he could taste the distinct tang of blood filling his mouth and feel a dull ache throbbing along his muzzle as he looked about.

Something about this place wasn't right.

On a whim he glanced down at his footpaws, expecting to find the soft grass like always. But instead, as he looked down past his skirt, he felt his stomach drop as he stared into a swirling maelstrom of grey clouds, broken up by the odd flash of thunder.

Was he\ldots{}standing atop the storm?

There was no sight of the world far below, no breaks in the seemingly endless cloud cover. No, he wasn't above the storm at all - it all felt far too wrong - he was \emph{inside} the storm. Inside the very hall of Peruvaan.

At the thought of that name, there came another unsettling feeling, just like the energy of the storm from before. He felt as every strand of fur stood on end, lifting up his arms to see they had puffed up to twice their size, at least. What in the name of Äituri was happening!?

``She cannot answer you here, Kuveli,'' came a voice from behind that shook like thunder, and yet was strangely comforting.

The little fox felt compelled to turn and meet the voice. And so he did, slowly at first, eyes fixed on his footpaws, uncertain if he wanted to confirm his suspicion, but ultimately even he knew he could not simply hide beneath the covers. Kuveli had to face this, whether it scared him or not.

Lifting his gaze, Kuveli could hardly have said he was surprised by who was awaiting him. In this realm, at this moment in time, it could only have been one spirit among them all.

The Black Reindeer himself.

Peruvaan.

It was strange, actually. Not that he was witnessing an actual spirit, nor that this spirit had chosen to show itself. It was strange because\ldots{}Kuveli had never pictured him walking on two legs, like he and his people did. Two-legged prey did not exist after all, else they wouldn't eat them.

Come to think of it, did Peruvaan take offence to the hunting of his mortal kin?

Other than that, he was just as the stories described. His heavy coat of fur was charred-black, like the remnants of a tree that had been struck by lightning, except for his velvety-red antlers. He also wore a simple woven loincloth around his waist. Even the spirits appreciated modesty, it seemed.

And yet, in spite of his foreboding appearance, the spirit wore a broad smile, his features soft and welcoming, shoulders slack, relaxed. This supposed spirit of unknowable power seemed downright jovial.

``You seem afraid, young one. Please, come and sit by my fire,'' the voice rumbled, almost distant and distracted, making the clouds beneath Kuveli quiver. ``We have a lot to talk about.''

Gulping, Kuveli hesitantly stepped towards the manifestation as it moved aside - each hoofstep producing a bolt of lightning - revealing a mysterious fire pit that crackled with strange blue flames.

As he approached, he caught the spirit's gaze with his own, and looked right into his eyes. And by all the spirits, Peruvaan's eyes were magnificent, like black opals that sparkled with the light of a thousand, thousand stars. And just like the stars, they inspired in him a sense of awe like nothing he had felt before. A precious feeling only he and his brother shared on cold, clear nights in an open meadow.

His brother\ldots{}

``But Sakara is still out there, and he's hurt-'' Kuveli began, but a thunderous chuckle cut him off.

``How foolish you fleeting mortals can be,'' the spirit chuckled playfully, amused at Kuveli's plight, seemingly ignorant of the offence he might cause. ``I cannot merely pick up your brother and breathe life back into him, no, that would upset the balance. And we have worked ever so hard to preserve that.''

In that moment, as the laughter rang in his ears, Kuveli felt that familiar rush of strength rise up from within him. It coursed through his veins as he straightened his back and raised his voice to challenge a god.

``Fleeting mortals? So that's what you spirits do. You sit up here, laughing at our struggles, and stepping on us when we don't offer you enough of our precious winter supplies?'' the fox hissed, a foul snarl quickly taking the place of innocent curiosity as he hesitated to come any closer.

Only a few moments of silence passed, but it felt like an eternity as Kuveli grew to realise he'd made a mistake. He had rejected the hospitality of a creature that could flick him into the void, or simply torment him for the rest of his days.

What a foolish thing to do! How could he have allowed himself to act so childish at a moment like this?

It seemed his fears were confirmed as Peruvaan's once jovial features seemed to turn sour. The welcoming smile bent into a deep frown, and those all-knowing opal eyes seemed to simmer with an unknowable power.

``If that were so, do you think I would have graced you with the honour of sitting before my fire?'' the reindeer responded at length, lifting his nose and staring down at the fox, the clouds rumbling with the fury that surely bubbled within him. ``This is no small privilege, boy. Stronger shamans than you have gone mad in the presence of lesser spirits than I.''

``I am no shaman!'' Kuveli protested, throwing up his arms in frustration. ``Why must everyone insist that I am something I'm not?''

``Sana tells me you are, and I trust that otter more than most. Should I have to punish him? What about your Äituri or the many ravens who squawk on and on about your potential? Am I to tell them they are wrong?''

The fox was stunned into silence. He knew Sana? And by name no less! What business did Sana have knowing the spirit of storms by name, when he was a shaman of Äituri? Oh, but it was obvious. The spirits were like the mortals, in that they bickered and argued like a family, and gossiped like his brother when they ate night meal. The Horse Mother was no different, and Sana probably sought something from Peruvaan on her behalf.

``I was always destined to be a hunter. My brother is a strong hunter, as were my ma and fah before him, so I am destined to be a hunter too. It's the very blood that flows through me!''

``Do not lie to me,'' the reindeer stated dryly, raising an open palm to silence the fox. ``Is it not true that you never knew your parents? The winds tell me that they died long before you can remember. Your mother at your birth and your father-''

``My fah by his own paws,'' Kuveli muttered bitterly, wrinkling his muzzle and folding his arms. ``I don't see how this matters right now, when I might lose my brother too.''

Again, silence reigned for a time, interrupted by the odd rumble of distant thunder. It had grown in intensity since the reindeer had arrived, no doubt his anger being its source. Something inside Kuveli, a voice of reason, pleaded for him to cease his childish bickering, but to do so now was surely a sign of cowardice.

And he was done being seen as a coward.

Or so he thought, until he watched the spirit slowly reach behind his back and produce something frighteningly familiar. A carved wooden figure, with scraps of leather wrapped around its waist, and a face\ldots{}

It was his own visage! Perfectly resembling a toy which Sakara had carved for him many winters ago, to give him something to play with on those long winter nights. He had carved Pekka too, and himself, and even a deer for their little figures to hunt.

``Where\ldots? How did you get that!?'' Kuveli asked, his words stuttering. Unless the spirit really had meant what he said, that Kuveli meant more than he believed.

``Do you know why they say my fur is black like charred wood?'' the reindeer asked, sounding legitimately curious as he turned to regard the little vulpine doll with a distant gaze.

Kuveli nodded slowly, wrapping his arms around his chest as a tightness seemed to grip his body. Stranger still, the tightness seemed to match exactly where Peruvaan was holding the doll, the hefty muscles beneath his fur contracting as his grip tightened.

Then, there was a flash of red-hot fire in those cosmic eyes, and Kuveli saw\ldots{}no, he felt the rage rising up inside the spirit. It was like a phantom, a feeling that was there, and yet not quite. The feeling made his hackles rise as butterflies filled his stomach, his every fibre growing more and more anxious. He could feel something bad coming, almost like how he could feel a coming storm.

``Once, the spirit of fire fell in love with my dance. It watched, utterly mesmerised by me, the fire unable to help itself when it embraced me,'' the spirit explained, each word hesitant as Peruvaan recalled what must have been an unbearable memory. Kuveli saw his features contort as the almighty spirit gripped his arms, the pain clearly still lingering in his bones. ``And by thunder, did it burn so terribly. The spirit of fire hurt me, seared my flesh, charred my beautiful fur to be as black as the night. I cast off the fire with lightning, sending it down unto the mortal realm, but fire never forgives. It follows my dance wherever I go, seeking me and all who know me.''

Peruvaan paused and knelt down by the fire, holding the doll over the flames. As he did, the fox felt the heat wash over his own body, burning his bare paws and making him pant.

It was then that the reindeer turned to him, and stared him dead in the eyes with those beautiful, star-filled opals. But rather than awe, they now filled the little fox with dread.

``And now, it will follow you too, little one.''

With that, Peruvaan dropped the figure into the fire, the flames erupting to consume the little vulpine figure.

``Wait-'' Kuveli barked, but a sudden and intense burning engulfed his body, like the flames were licking at his fur. It felt like his flesh was boiling and dripping off his blackened bones, every nerve screaming with a pain like nothing he had ever felt before. Lifting his maw to let out a scream, he found that he had no voice, the flames having consumed his throat, and now all he could hear was the roaring in his ears.

All around him were flames, burning bright, consuming him like tinder. Fleeting glimpses of the reindeer spirit through the fire became rarer and rarer until, finally, the whole world seemed to twist into a swirling inferno as he writhed upon the floor.

The world of the storm spirit faded away.

He couldn't hold on anymore.

\secdiv

\noindent A rich, emerald light filled Kuveli's vision as his eyes flicked open, gasping for air as he floundered for a moment. Like a salmon plucked from the river, he thrashed around as if he had forgotten how to use his body. He grasped enough control to throw a paw over his head as a pounding headache sent spots across his vision.

But this headache quickly faded, leaving the fox to look upon the welcome sight of a rich, leafy canopy hanging overhead. No more lightning, no more Peruvaan, the sky beyond was a gentle blue speckled with soft, white clouds. The reindeer spirit must have moved on and taken its booming dance with it, leaving only sweet birdsong to fill the fox's sensitive ears.

For a while, he simply remained there. The fox's heart was still racing, and his body ached as if he had been trampled by an auroch. Granted, he did fall off a horse, and that wasn't much better. Though, the bed of crushed bracken beneath him was very soft, and he wasn't in much of a rush to get up. Just a few moments longer, to collect his thoughts and let the storm within his own mind calm.

Once he finally decided to rise, Kuveli looked about his surroundings with great care. Pekka might have still been around, just out of sight, but the forest here was too deep to tell. While the numerous birch and pine trees were spaced generously, there grew a wall of thick undergrowth between them. Bracken, buckthorn, and honeysuckle, the latter of which attracted more than a few fluttering moths and lumbering bumblebees, none of which seemed to pay him any mind. Why would they?

There was, however, a very obvious clue as to where Pekka had gotten herself. A great gash had been carved through the undergrowth, the earth beneath torn up and splattered across the flowers and birchbark, no doubt by his helpless brother being raked along the floor.

The gash also revealed a thick blanket of tinder-dry needles and pine cones, the refuse of a hot and dry summer. And although Kuveli saw no blood, he found himself no more at ease than before. He had seen, in his time with Sana, that one does not need to bleed to have their skull crushed or neck snapped.

``Äituri be merciful,'' he muttered, ``please let him be ok.''

The fox took a moment to brush the debris from his skirt, the patchwork of furs and leather torn up by the night's events. But his shoulder strap held firm and his knife was still sitting snugly in its sheath, at least as far as he could tell with a quick squeeze.

He also ran a thumb along his lip, lifting it up to his face to check for blood, which he could still taste on his tongue. There were flecks, but nothing substantial. It was probably nothing then, just bit his tongue in the fall.

With that, he practically leaped towards the trail, setting off at a brisk pace. There was no time to lose, not especially as a particular scent was tickling his nostrils. Through the sweet scents of clover and pine, almost overwhelming in their power, there was the distinctive odour of woodsmoke.

Through the forest he ran, as fast as his nimble footpaws would carry him. Although his body ached, he moved with great finesse, ducking beneath prickly branches and skipping over hidden roots that waited to ensnare him. Thankfully the trail was dead straight; Pekka, in her forever stubborn ways, clearly hadn't stopped to check if she was actually in danger.

Where was she now? Kuveli could not say. Horses always tended to return if they ever escaped, not content to stay far away from their food and a nice, dry bed.

Perhaps that's where she had gone. All the way back to camp, dragging Sakara's broken body along for the ride, so that the tribe might find it. Though, it seemed that he would not be so unlucky this time, as he rounded a sudden corner in the trail and felt something warm beneath his paw pads, followed by a pained yelp.

Kuveli tripped over his own feet as he staggered to a halt, barely catching himself on a tree as he whirled about to make sure his ears weren't deceiving him.

And sure enough, he saw a familiar coat of red, white, and grey fur lying in the grass, writhing weakly as he groaned in pain.

There was no word in the Lentavohi tongue that could describe the sense of relief he felt. It overwhelmed everything, casting the anger and the fear into a growing fire of hope that he sheltered within his heart. Without thinking, Kuveli scrambled to Sakara and threw himself upon the delirious pile of fox he called brother.

``I thought you were gone, big brother. Like I'd never see you again, ever,'' Kuveli bawled into Sakara's scruff, pressing his face tightly against the bigger fox's warm body as tears streamed from his eyes.

In his ears he could hear Sakara's heartbeat, strong as it ever was, followed by a grunt as the larger fox shifted slightly. Kuveli felt an arm around his back, squeezing him back, if only delicately. But it was enough to make the little fox sob and sniffle, letting out all the stress and worry that had weighed upon him and leaving only a grateful smile.

``You won't\ldots{}get rid of me that easily,'' Sakara wheezed, his voice hoarse, as he lifted his head with great difficulty. ``Famine, bears, frostbite,'' he murmured seemingly at random. ``I'll be feral if it's my own horse that kills me, after all I've lived through.''

Kuveli wrapped an arm under his brother's head, helping him to lift it. Yet he was heavier than the little fox had realised, and Kuveli started to look around for a place his brother could lean against, to regain his bearings.

But the touch of a paw stopped his searching, as his brother gently held the long, white fur on his cheek and began to rub it between his thumb and finger. Sakara's delirious features twisted with worry as he did.

``You're bleeding,'' he commented, bringing his paw between them to reveal a bloody finger.

Kuveli felt strange as he looked at his blood on his brother's fingertips, like colour-paste ready to be rubbed across someone's cheek or forehead. The hungry-fanged wolves from last night were back, to tear his mind in half, but they were different now. The one wanted to drag him somewhere where he let his brother worry over him as much as he clearly wanted to. Somewhere where finding Pekka and worrying about the smell of smoke were left to Sakara. The other was dragging him into a cloud of dark smoke.

But the second was the one that wore Kuveli's face. Like the toy Peruvaan had burnt.

Kuveli blinked away the confusion. ``Let me see, brother,'' he blurted out.

``But little rabbit chaser, if you're bleeding-''

``If I'm bleeding I can still walk. Can you?'' Kuveli snapped.

Sakara recoiled in surprise, but didn't try to stop him. He strangled a yelp into a long whine when Kuveli's paw touched his shin.

``I think,'' the little fox fought to keep his voice steady, ``your leg is broken. I\ldots'' What would the shaman do? ``I'll go find a splint.''

``Stay where I can see you, though!'' Sakara pushed himself up on his elbows. But that was stupid, Kuveli thought, as if there would be a usable splint lying in the mossy underbrush within a few paces, just waiting for him to put his hand on.

When he put his hand down in the mossy underbrush he felt something knobby and hard.

Kuveli stood up, holding the reindeer leg bone gingerly, and stared wide eyed at his injured brother.

``That should do,'' Sakara nodded as Kuveli approached. ``There're thongs in my pouch\ldots''

``You don't have your pouch.'' Kuveli frowned. It was probably somewhere back there in the forest, if not further. And himself with only his knife and his clothes-

Hastily, Kuveli began untying one of his new leggings from his belt before kicking it off. He unsheathed his slate knife as he picked it up, and carefully but as swiftly as he could, took the sharply-honed stone to the stitches.

Sakara tried to object but Kuveli cut him off. ``I'll stitch them back together tomorrow when we're safe. The practice will be good for me.''

But he hesitated when it came time to pick up the reindeer leg bone.

``What's wrong?''

``The\ldots{}it\ldots'' Kuveli grimaced at the bone lying beside his brother as if it might bite. ``Nothing's wrong!''

``Then what's so scary about a bone?'' asked his brother, ``Seems lucky to me, it's just what we needed. Here, I'll hold it while you tie it on.''

``I\ldots'' Kuveli hesitated. Surely it'd be fine if he didn't tell. Just help his brother, remember what he'd learned from Sana, wasn't that enough? ``I spoke with someone,'' he said anyway, ``last night. In the storm, after I fell off Pekka.''

``Someone looking for shelter?''

``No. IN the storm.''

Sakara looked at the younger fox for long enough that Kuveli had time to feel up and down his brother's shin. No crookedness or twisting as far as he could tell, Äituri had given them that much at least. ``You mean,'' the older fox finally said, ``you met Peruvaan?''

Kuveli nodded.

``Face to face?''

He nodded again.

There was a peculiar kind of expression he'd noticed, around Sana, around any shaman. The people who had it would have said it was respect. But Kuveli would have said it was more like fear, maybe even disgust, and that malicious voice was whispering that if he looked up now he'd see it in his brother's eyes.

But Sakara was only looking at the leg bone lying beside his own. ``Well, that makes this a good omen, then.''

``I don't know,'' Kuveli said, ``I think I might have made him angry.''

``You made Peruvaan angry?''

``I might have.''

Sakara threw back his head and yelped with laughter, until he winced at his leg and stopped. ``The spirit of dancing and celebration and drunkenness? The happiest god? The dancer who never stops? You made HIM upset?''

Kuveli's cheeks grew warm. ``He's not nothing but dancing! Lightning is dangerous and he can be too!''

``Well, I suppose you would know, little bud,'' Sakara had found his laughter again, ``the mysteries of the spirits! This mere hunter's never met one face to face, himself!''

``Lucky you, then,'' Kuveli grumbled as he began to lash the bone splint in place with what had until recently been his leggings. ``He wanted me to listen to some stories about fire, and it felt like I was being burned\ldots{}but I think he wanted me to listen more than I did.''

``About the fire?'' Sakara cocked his weary head.

``It was something about how fire always followed him\ldots''

Some of the details were hard to recall, but he was sure that had been the bulk of the details. The blue fire, the questions about his own past, his worthiness to be called a shaman.

And then the appearance of his own doll, which Peruvaan had burned while warning that-

Oh.

Kuveli's paws made haste to finish the splint and check it was tight enough. ``We need to go! We need to find Pekka! That's why he gave us a splint!''

``What's wrong with you, little brother?'' Sakara hauled himself up onto his good leg with Kuveli's shoulder for support. He made to pat the young fox's head, but Kuveli ignored him. The young fox's nose was in the air, his eyes were wide, and his ears were up for the faintest whisper, spirit or otherwise.

``Can't you smell it?'' he said.

``Smell what?''

``The fire that follows him.''

\secdiv

\noindent It was growing closer with each moment that passed, a veil of thick smoke clouding the skies overhead, its stench ever-present in the otherwise calm forest. It was a clear sign that the spirit of fire had found them, and like a pack of hungry wolves it had begun to stalk them, its flames eager to nip at their heels.

The foxes pressed on, shuffling through the thick growth with as much haste as their battered and broken bodies could summon, spurred by the oddly warm winds at their back. But already Kuveli knew it wasn't going to be enough, not with his brother's broken leg.

After every few dozen paces they were forced to stop, Sakara grimacing as he rested his back against the nearest tree and huffed with ragged breaths. Even if they had willow bark to dull the pain, it wouldn't have filled the aches in their empty stomachs and the stiffness in their bones. Kuveli found no use denying it, he too was utterly exhausted, but he couldn't allow himself to give in.

It felt like hours had passed, but he could not see the sun to tell, for they had delved so much deeper into the forest, following Pekka's trail, which had brought them to the top of a steep embankment.

Both foxes paused, looking down the relatively short drop into a gurgling stream. A fit hunter would have had no trouble traversing it, but with Sakara in such a state there was a real chance he could fall and do even more harm to himself.

What if he landed wrong and broke the splint? More time wasted making another splint. Time that they didn't have, as the fire spirit was surely gaining on them. His worry was proved when, as he glanced to the sky, Kuveli realised the smoke had descended towards them.

Something nattered frantically in his ear. A gut feeling, a spirit perhaps, was telling Kuveli just to go. Be like a hunter, be brave, and take a step into uncertainty.

Or be foolish, if it had been a demon that seeded the idea.

Either way their time was up and, thinking quickly, Kuveli put a tentative paw forward to begin down the slope. At the same time, he pulled on Sakara's arm, urging his brother to follow, but the bigger and - supposedly - braver fox was none too keen to risk the fall.

``Go on ahead,'' he gasped between breaths, one arm wrapped around his chest. ``I'll find a safer place to climb down and meet you, somewhere near the Salmon River.''

``Shut up,'' Kuveli snapped back, ``we won't lose each other again! I swear it upon my soul, may Äituri tear it from my body if we do.''

Sakara gulped, his brows knitted with worry as he quickly gave in, following Kuveli to the best of his ability.

``Since when did you get so righteous,'' he commented after a few moments, giving a forced chuckle. It was hardly convincing, and Kuveli could clearly hear the worry in his voice.

Even as positive as Sakara had always tried to be, the thought that they might very well still die was weighing heavy on him. Neither fox was ignorant of the danger, which, on top of their mounting exhaustion, only worked to fill them with a growing sense of dread as it picked away at their minds like the tapping of a crow's beak.

They traversed the slope at a frustrating pace, one footpaw after the other. Or, in Sakara's case, carefully sliding down the slope on his good paw at the pace of a snail. Though, it wouldn't be careful enough.

About half-way down Kuveli heard a yelp behind him, and in his panic he tried to turn and see only to lose his footing. The crusted mud that covered the ground gave way, seizing what little grip Kuveli had found and causing him to slam down hard on his side. His grip on Sakara was still firm, and as he landed, the little fox was then crushed beneath his brother's tumbling form, before they both rolled down the slope and landed in the stream with a splash.

The little fox gasped as the bitterly cold waters of the stream soaked into his fur and made his body prickle, as if he were being stabbed by dozens of tiny sewing needles.

In that moment he could understand why salmon were so keen to jump out of rivers, as he followed their example and scrambled over his groaning brother, splashing water everywhere as he clambered back onto dry land. He quickly turned and grabbed his brother by the fur, but froze in place as he laid his eyes upon a terrifying sight.

Smoke was pouring between the trees and swallowing the canopy above, carried overhead by wind, which had begun to pick up rapidly. It wasn't just the overwhelming smell now, but a distant crackling that banished the once comforting sounds of the forest, and a low, orange glow that seeped through cracks in the thick, choking wall of black.

By all the spirits, it was here. The fire spirit had come for them, at long last, and it wasn't wasting any time, as the menacing smoke rolled over the edge of the embankment and fell towards them. As it did, it seemed to pick up speed, like a predator seeing that its prey was vulnerable, and moving to make the kill.

``Get up,'' he screamed at his brother, ``it's already here, we have to go!''

Sakara looked up groggily, his tired and sunken face turning pale under the fur, his maw falling agape as he watched the smoke fall upon them. When Kuveli yanked on his fur again, he snapped out of his daze and stumbled up onto his good leg.

Pain shot through his features as, in his panic, he scraped and battered his broken leg while hauling himself up by Kuveli's shoulder. And, as soon as he was on his feet, they both began to run.

They could feel the heat at their backs, almost like the comforting embrace of a warm campfire, as if the fire spirit was trying to fool them into a false sense of safety. But foxes were too cunning for such trickery, and they kept running. Over roots and rocks, down slopes and along ditches, the stream shadowing the path they frantically cut through the overwhelming forest.

It should have been impossible, moving at such a pace through a forest that seemed untouched by even good game trails, but wildfire, it seemed, was a strong motivator. Though, as his paws beat the dry and brittle forest floor, Kuveli swore he could feel something else. Something like what he had felt when the thunder was booming overhead.

But it wasn't enough.

Sakara stumbled again, his arm slipping from around Kuveli's shoulders. Before the little fox could even turn and call his name, the smoke overcame them, turning the whole world black.

It burned his every sense, like Peruvaan's fire. His eyes screamed and watered, even as he screwed them shut. His nose and mouth filled with thick, suffocating smoke that caused him to cough violently, dropping to the floor where he found a brief respite.

Down there, all around him, he saw a fiery orange that was only growing brighter with each passing moment. The heart of the fire itself, ravenous for their flesh and souls. The sound was deafening, a rageful roaring like that of a great windstorm, louder than even the thunder.

Though, rather than run, Kuveli merely remained there. His mind was racing like never before, unable to think as the memory of Peruvaan's fire paralysed him. He could feel it, his flesh bubbling and boiling again, his fur charred, his bones rendered unto ash. It made him shudder as he lay there, eyes glazing over.

Terrified.

Until he heard another noise through the roaring smoke. Something animalistic and shrill, and yet\ldots{}familiar.

It was the whinnying of a horse.

By the mercy of Äituri.

Pekka.

A delirious smile came to Kuveli's muzzle. He rolled onto his stomach and began to crawl towards the sound, but it was hard. Fear still had its claws in his pelt, digging deeper into him the further he tried to run from it.

But he could feel that otherworldly strength growing within him. Like before, it was filling his veins, banishing the poison. Slowly, it brought him to his knees, and face-to-face with a force beyond reckoning: a terrified horse.

Kuveli put forth a paw, and behold, there was a halter for it to grasp. He hauled himself to his feet, leaned against Pekka's shivering flank for balance. ``Brother,'' he tried to yell and only croaked, ``can you ride?''

``I don't know,'' Sakara whispered as he scrambled astride the mare. ``I can't properly guide her with this splint on.''

``I'll have to do it, then.''

``Can you?''

``You just said you can't.'' Kuveli pulled himself up in front of Sakara. ``And actually try to hold on this time!''

Pekka needed little urging to make the best speed she could away from the fire. It wasn't her fastest, tired and frightened as she was, but it was quicker than an exhausted fox could crawl. Kuveli began to hope, as he felt the heat fade behind them and the smoke ahead thin, that they had escaped.

Then Pekka stopped, whickering and grumbling. They were atop a high riverbank, nearly a cliff, and below them limped a wide river, shallower than it should have been, yet still seething with upset. River spirits were malevolent and treacherous at the best of times, and this one would be angry - not only was it parched, but the fire spirits had spent all night blowing ash and cinders into it, just to rub it in.

They would have to go another way. But instead of urging Pekka along the river, Kuveli felt a thought come to him, unbidden, from where he couldn't say.

How had Purevaan escaped the fire spirit?

He had gone where it couldn't follow.

``Pekka,'' he growled in a voice it had never before occurred to him to use, ``trust me better than my stubborn oaf of a brother does.''

He pulled her head toward the cliff, and she responded. He could still feel her panicking beneath them, but she did as bidden.

``For Äituri's sake, jump!'' Kuveli yiped.

The flames reached the crest of the hill behind them, exploding between the trees before consuming them all together, gleefully certain their newest lovers were within reach.

Pekka reared, nostrils flared, and her hooves left the ground.

It felt like an eternity as they fell. Kuveli's stomach turned over as he lost his grip on Pekka. And then, his heart stopped as he felt his brother's grip slip from around his waist.

The cool muddy river water caught the three of them a moment later, its embrace surprisingly gentle. Like a reflection of the dull grey sky into which Peruvaan had once lept, leaving the fires, jilted and frustrated, behind.

Pekka was the first to make the opposite shore, as the river had borne them swiftly downstream to where the banks were lower. Its anger, apparently, was all against the fire spirit today, and it was only too happy to aggravate it by rescuing three weary and bedraggled morsels from its jaws. The mare plodded up the sandbank and then flopped to the ground, glaring daggers at the fox brothers as if daring them to try to make her get up again.

Nothing could have been further from their thoughts. Sakara and Kuveli lay on their backs on the sand, toes still in the water, panting grateful lungfuls of clean air.

``Is your splint still in place?'' Kuveli finally asked.

``Stubborn oaf of a brother?'' Sakara huffed.

``It's only fair,'' Kuveli retorted, ``but is your splint still in place?''

``It is,'' Sakara answered, ``but never mind that. What's Sana going to say when I tell him you reenacted the whole dance of Peruvaan?''

Kuveli the shaman blinked up at the clouds. The ash-smeared fox imagined they were laughing at him.

There they lay upon the bank for a long time, watching the fire consume the forest on the opposite river, raging at its loss. They stayed until dusk began to fall, and the canoes of a friendly otter tribe stopped to help them.

In the end, the forest would regrow. Twice as lush and twice as bountiful, just as it always did after every one of the fire spirit's tantrums, for as long as hunters had huddled in shelters and told stories about it.

And now, he had his own story too.

A story brought about by his own tantrum.

Only, unlike the fire, he had learned to be better.
