Ahbay awoke in the darkness with a feeling that now was the moment. The cheetah wasn't certain what it was that told him that, but as he lay there thinking, there was the sound of someone at his hut, and he knew immediately who it was before he could smell her or even see her. The light of the dying village fire gave her away and made her eyes shine with possibilities as Sizan pulled the flap over his hut's entrance aside.

``It is time. I knew this moment would come,'' she said softly, her long thin tail curling up in delight the only sign of her excitement. In the dark, her spots and markings were hard to make out, but her eyes were clear and bright even though it was a moonless night as they shone with possibilities.

He wanted to protest, to roll over his mat of grasses and tell her that her teaching and visions were all wrong, that the middle of the night, when even the most diehard of the hunters drunk on wine had fallen to the seduction of slumber, was no time for such nonsense, but it would be a lie. He could feel it himself that now was the time for him to complete his training. It was unnerving that he knew that, but something about tonight, something about this moment was right. The vision would be strong. When he first started, he'd only get a faintest inkling of when, but not anymore. He had begun to feel the currents of fate himself now, and all the doubts he had in the beginning had been laid bare.

``Is anyone even still awake?'' he asked, rising from his grass mat, setting the blanket he slept under aside.

``Not that I can tell, but then I think that is why now is the moment.''

The soothsayer rarely said something was correct or certain because so much of what she did was deal with the indistinct edges of life. To say anything was a specific thing was to commit in a way that prophecy did not. In the three years he'd trained with her, he'd noticed her way of always leaving the door open to something else, and he had come to understand that himself. The threads of fate were fickle at best, and to tell the weather tomorrow was one thing, to know and set the fate of another was a completely different task. The weather was easy; people were hard. Knowing the will of the gods? Impossible.

He dressed quickly in his loose pants. The night was cool, the wind coming off the distant mountains, but he did not bother with a shirt. Sizan wore her simple linen robe that fell from her shoulders, tied at the waist with a bit of hemp cloth. She waited for him outside, but her tail lashed back and forth.

``Should we go to the spring?'' he asked, curious.

``No, this is bigger than that.'' She turned toward her own hut. ``Come, we shall gaze into the darkness and from there you shall see.''

He nodded. Some visions came best in nature, others in his own bed. He followed her back to the hut and when she pulled the flap open, he entered. Sizan's hut had already been prepared, her sleeping mat picked up and set to the back. A single clay oil lamp was already lit in the room, and he took the seat on the far side.

Sizan let go of the flap and entered the hut, sitting down across from him. It was dark except for the lone lamp, and the light only barely illuminated her, except for her eyes. They glowed brighter at night than anyone else's in the village, although he could not tell if that was his imagination or a trick she played.

``Tonight, we shall journey. I will guide you on a vision that will take you further than any you have seen before. Are you ready?'' she asked.

He could feel his ears flick. ``As ready as I can be to answer the call.''

She nodded. ``The journey ends where it started, but you are no longer a kit in the eyes of the gods. You will be a seer, and the visions will be yours to interpret. Do you understand how much weight I am putting on you?''

``I do,'' he said.

She chuckled and her eyes sparkled. ``What was the first tenet I taught you?''

``Never look for your own fate.''

``Why?''

Ahbay cleared his throat. ``Because if you see your own fate, you will try and change it. That is the nature of who we are. We always want to fight against it.''

``And the second tenet?''

``If the gods show you your fate, accept it. Do not attempt to change it,'' he replied.

``Look at me, Ahbay, meet my eyes.''

He looked at the soothsayer, and in the faintest reflections in the dark, he saw himself, and then he saw himself looking back at her, with her reflection in her eyes, his eyes shining like hers. It had taken weeks to learn this simple technique, to grasp vision, and now it was almost effortless.

``The pull\ldots'' she started,

``\ldots is strong,'' he finished. ``This is the moment of my\ldots''

``\ldots of your\ldots'' she intoned with him,

``\ldots journey.'' they both said together.

Above them the day dawned bright clouds and sky, and around them the village spread out, or the land where the village was spread out, but it was different. The plants were different even though the land was roughly the same, but the mountains still stood in the distance.

The village was no more. Around them only scrubland and the distant mountains nearby.

``The vision has come,'' Sizan intoned in a voice that was not spoken yet heard. ``Behold!''

``Is this our future or our past?'' he asked.

``We might never know.'' She turned to gaze into the distance. They were alone in this wilderness by themselves, until suddenly they weren't. They could see dust rising up and as they watched, a half dozen leopards and tigers dressed in brightly colored fabrics equipped for war hurried toward a fate unknown. The men ran on, and the land sat, and then came a wolf shepherd with her goats, and when she was gone there was a path through the dry scrub toward a place beyond.

``Where does that lead?'' he asked.

She hesitated. ``I don't know, but it is your path to follow. Go, and tell me what you see,'' and then he was alone and yet not alone. She was gone, and yet he was still in the room with her. The oil lamp was in front of him, but he could see only the path that lay before him.

``Sizan?'' he called out to wilderness and in the hut.

``I am here. This is your path and yours alone,'' she said far away and yet right next to him. ``Go, the journey is here for you. I have taken mine many seasons back.''

He stepped out on the path and felt his paws touch the dirt with the grasses lining it tickling at his sides. He started walking. ``There's a road, and no, wait\ldots'' He saw huts, but huts much bigger than theirs, and these seemed made of stone and could hold two or three families.

``I see stone huts, but they're massive.''

``Go on.''

He walked toward the structures, and they only seemed to grow. What was a moment ago a few huts became many, and the roofs suddenly reached up toward the trees as the buildings grew.

``The huts are bigger.''

``You see the future,'' she called out.

``And there are so many of them, and people, all sorts of people\ldots'' He paused. The road has suddenly become flat and smooth and different, and then a wagon went by pulled by a horse on two legs, with people riding by, and then another, and another, and faster and faster and\ldots.

``There are wagons, so many wagons,'' he yelped in surprise. ``This is so much bigger than our village.''

``What you see is a city. I have never been to one, but down by the banks of the two great rivers you can find them. Keep going. The vision will tell you more.''

He wanted to call out. He wanted to scream, but there were things all around him. The stone huts reaching to the sky with pillars all around. People were shouting as a chariot passed by, a man draped in purple riding by, as a crowd cheered, leading what appeared to be prisoners. There was so much he didn't understand, so much he couldn't comprehend, as sounds from metal horns echoed in his ears and made them lay back.

``What do you see now?'' she called out, obviously aware he was in distress.

``I don't know. There are pillars of stone and men carrying blades.'' He paused and what had been a festival turned into a battle as steel clashed with steel as the city burned. People were dying, innocent people, and even in his vision, he could feel the smoke stinking in his eyes. He wandered the streets, but there were flashes of more people and battles.

``I see war, death\ldots'' he whispered, trying to make sense of it all.

``Stay with it. See to the end,'' she called out, a voice far away and yet right in front of him.

He tried to step down the path, to continue on, but it was overwhelming. Things shifted endlessly around him, and he could feel glimpses of emotions before they were gone. Things came faster and faster, people moving quicker and quicker in things he could only describe as wagons made of metal as the city grew, changed and died, when suddenly it all froze in a single moment. There was a deafening roar, and a mushroom of fire engulfed everyone and everything. The people in his vision vanished instantly, and everything was white hot and burning.

He hit the ground then, not the ground of the road or the path, or the strange world he had just seen, but the ground in Sizan's hut. He blinked, confused. ``It's all gone.''

She had leaned forward, still looking at him, concern on her face. ``What did you see?''

``I saw change, and growth, life and death, and then fire. There was a fire that consumed everything and everyone,'' he sobbed. ``That was the end.''

She frowned. ``Do you see a fire hotter than any you have ever seen that took everything away?''

He looked up at her, blinking back tears. ``Yes,'' he nodded. ``What does it mean?''

The soothsayer didn't say anything but sat back and took a deep breath. ``I had hoped you would not see that. I have had a vision like this before, with a pillar of flame of unimaginable power consuming all. I've seen it multiple times, actually.''

She was silent then, and he shifted, suddenly uneasy. ``And?'' he asked, still on the ground.

The soothsayer slowly ran a claw through the dirt, watching the way the earth parted. She looked up at him after a moment. ``I cannot be sure it is the same one I have seen. I cannot say for sure if that is the past or the future, or even our world. Parts of my visions have been so different than our lives I cannot understand them, but I believe the vision is of a distant future. Not only that, it changes. Sometimes there is the fire that consumes everything, and sometimes I float, with the balls of light of our ancestors above us so close that I must be in the heavens above, as the pillar of fire pushes me onward. When I see that, I feel joy. When I see it destroy the city, I feel pain.''

He picked himself off the ground. ``Are these connected?''

``Yes, but it took me a long time to realize they were.''

He was silent for a moment. ``What can I do with these visions?'' he asked.

She laughed bitterly. ``What can anyone do with a future or a past they have no connection to, living or dead?''

He was surprised by the intensity of her voice. ``I don't know. What can we learn from it?''

She looked back to the marking she made in the dirt. ``Perhaps very little, but perhaps that is my lack of understanding of the vision. The path goes on from here, but I am unable to draw this line forever toward the horizon, I am unable to follow it. You might not get much further than I have, but it is important we try.''

He felt so confused, so unsure. ``Why?''

``Why indeed. Why are our lives like they are? Is this how the gods intended for us to live, or are we destined for more, for something else? Could this all be the temptation of the darkness in war?''

She looked tired then, and he knew what she'd done. ``You broke the second tenet,'' Ahbay said.

Sizan looked up at him. ``I have tried to.''

``That's forbidden.''

``The gods have not shown me so much for me not to know. You saw how far in the future that is, yet you felt it, didn't you? The loss, the pain, that despair?''

He had. Before he'd seen small things or things not too far away, but this, this was beyond his sense of scale. It went beyond the mountains and kept going in a way he could not fathom.

``Why have you never told me about this?''

She looked up at him and her eyes were bright. ``I had hoped what I was taught was not wrong, so I taught it to you. I thought you might never see this far. I have spoken to others with the gift of sight, and none see this, and yet I know this vision lies before our great descendants when every last one of those of us alive today and our children and their children are looking down upon them. Who should worry about that? How could I say this vision was true either, without someone else seeing it?''

``But you know it to be true,'' he said. ``If you felt it like I have, you know it's out there.''

``Yes, but we control only the now,'' she responded.

A glimmer of thought came to him. ``And by controlling the now, we can control the future?''

She flashed a smile full of fangs as her tail lashed behind her. It wasn't a threat, but in great amusement. ``That's correct. You learn quickly, but now you see the dangerous power we have.''

He considered. ``I could stop things from happening that shouldn't happen.''

``That's true, but you could also stop things happening that should.''

``If I can see the vision again and it changes for the better, would that mean we have done the right thing?''

``One can only hope. Prophecy is a terribly imprecise thing. I have thought you having a vision like this was always a thing that could happen, but I by no means thought this was something that would happen. I was mistaken.''

He sat, tail lashing, and looked upon his teacher. ``You didn't have to hide this from me.''

She laughed. ``What would putting the burden of the future on you do when I don't know how to fix it?''

His eyes shone at the soothsayer in the dim light. ``Because we all must live. We must find a way. The gods ask us to.''

She smiled back. ``Indeed, they do.'' She took a deep breath and reached out to take one of his paws in each of his hands, the oil lamp burning between them. ``The call is still upon us, so come, let us journey into the dream again, and this time I will accompany you wherever the vision goes. Perhaps together, we can find a clue to aid our present.''

He nodded and took a deep breath and locked eyes with Sizan. ``Then let us go.''

She took a deep breath and spoke with a spark in her eyes. ``Call out to the path\ldots'' she intoned.

``\ldots and follow the fates,'' he replied.

``\ldots together we go,'' they intoned.

Once again the day dawned around them, and the sky opened up above them with a bright blue hue. In the distance the mountains waited, and the road lay before them. Sizan nodded to Ahbay, and together they started down the path to see what fate would show them.
