There was no such thing as silence. Even the quietest movement created a noise for sensitive ears to detect, and the forest was full of hundreds upon thousands of noises. Leaves rustled. Birds chirped. Twigs cracked underpaw. For ears as large as a hare's, those noises should have aroused suspicion, but the three by the stream that flowed through the forest didn't even twitch a nose.

The wolf in the shadows didn't care about the hares spotting him. He knew what their stronger senses were. Slowly, he crept. Keeping to the shadows. Avoiding the fallen leaves and branches. It wasn't long until he was almost at the edge of the trees. Their scent filled his nose, carried by the wind directly towards him.

There were three of them, crouched by the bank of the narrow stream, their backs turned to the wolf in the shadows. One laughed at a joke told by another.

Before they could spot him, the wolf pounced. Arms wrapped around the hare's body, twisting upon impact to drag the prey animal from his feet. Wolf and hare rolled and splashed into the stream, predator on top of prey.

The wolf poked his cold nose to the throat of the hare. ``Got you. I could have been any predator hunting you.''

White Tuft said nothing, though the other two hares started to giggle. The wolf's ears pinned back at the laughter. Had he gotten something wrong?

``Oh, Found Moon,'' Grey Ear said, nose twitching in amusement, even as the giggles died off. ``We heard you before you even set paw in the woods.''

Found Moon hadn't realised his ears could pin back farther. They did, and he slowly leaned back to release White Tuft from beneath him. ``You did?'' he whimpered softly, a whine coming to his voice in a way only a wolf could manage. ``I thought I was being really quiet.''

Wandering Star held out her hand to help White Tuft out of the stream. She did not offer Found Moon the same courtesy. ``Quiet for a wolf, maybe,'' she said, cocking a smile to the other hares.

``Then why did you let me jump you?'' Found Moon asked. He lowered his eyes, hunching his shoulders to lessen the height difference between himself and his adopted siblings.

``A wolf has to feel like a predator sometimes, or else their teeth start to fall out,'' Grey Ear said.

``Here, come and see what we've done with the nets,'' White Tuft said, distracting Found Moon before he could raise his voice in protest.

The wolf tucked his tail between his legs as he allowed White Tuft to lead him towards what the hares had been working on before his interruption. They had been weaving reeds into nets, creating a strong mesh that could be used to toss into the stream or the nearby lake to catch fish.

``We've tried a new way of weaving,'' White Tuft said. He took the partially completed net in both hands and tugged at a few of the segments. The reeds barely moved. ``This way should be a lot stronger, so we're not having to repair them all the time.''

``Yeah, but they take so much longer to make,'' Grey Ear grumbled. He slumped down on the bank, picking up one of the unfinished parts of the net. He started to weave a few strands together, using a fishbone needle to tease the reeds into a regular pattern. He didn't get far before dramatically sighing, his long grey ears draped against his shoulders.

Found Moon resisted the urge to shake the water from his fur as he crouched close to Grey Ear. ``Can you show me how? I'd like to learn.''

Wandering Star laughed. She pushed both hands against Found Moon's chest, making him topple into the stream again. ``A wolf's hands aren't delicate enough to weave a net like this. Just be happy with eating our catch.''

The wolf didn't resist the urge this time. He shook the water from his fur, his loincloth almost slipping off from the vigorous movement, with only a quick grab from his hand keeping it in place. His eartips blushed, but the hares either did not notice, or simply did not comment on it. ``I'm always thankful you catch fish for me,'' Found Moon mumbled, hoping to distract from his embarrassment.

``And because of that, we're never short of their bones,'' White Tuft said, grinning widely on her short muzzle. She tossed an empty basket towards the wolf, who clumsily caught it. ``If you're wanting to be useful, go and forage some food for us.''

``Make sure you don't get the poisonous berries this time,'' Wandering Star said.

``But do get those hazelnuts if you can sniff them out,'' Grey Ear added. He licked his lips.

Found Moon sighed. Not as dramatically as Grey Ear had. A smile touched his muzzle as he did so, tucking the reed basket beneath his arm. The hares, especially his three adopted siblings, helped to keep him fed in a tribe of herbivores. It was only fair that he helped seek out food for them, especially when his nose was able to detect some of their favourite foods hidden amongst the foliage.

Leaving the hares to the net, Found Moon returned to the forest. He hoped his hunt for berries and nuts was more successful than his failed stalking of his siblings. It could hardly go much worse.

Many years of experience had taught Found Moon what to forage for. He knew what hares liked to eat, what was good for them, and what was considered a rare delicacy. He ate little of it himself, with most of their diet disagreeing violently with his stomach and tongue.

The wolf's thoughts wandered as his paws did, meandering through the forest as he slowly filled the basket. His nose led him towards a small grove of hazelnuts, and he made sure to remember just where those trees grew. It wasn't just Grey Ear who adored them.

As he hunted for plants, Found Moon became aware of another scent on the wind. It was an unusual one, something that was both familiar and unknown at the same time, and he soon realised why. The scent on the wind reminded him of his own smell. There had been wolves here, though the scent was old. A few days at least. A concern, but not one that needed him to rush back to his siblings.

Found Moon remained vigilant for the wolves, each sense on alert, but he detected nothing but the stale, old scent. All the same, the presence of wolves disturbed him. There had been none in the area since\ldots{} well, ever since he had been found sixteen summers ago. He could only hope the wolves were merely passing through the area, because if they had come to stay, then the hares would be in great danger.

The light began to fail, the sky painted vivid orange. Found Moon made his way back to the stream, his arms laden with the heavy basket of food and his mind occupied with thoughts of the wolves. He heard his siblings long before he saw them, laughing and joking noisily with each other, with the occasional loud splash of water. They had not learned of the wolves, then.

Grey Ear was the first to notice Found Moon. The hare crowed in delight and bounded across to the wolf, saying nothing as he rummaged through the basket of food until he found a couple of hazelnuts. His eyes were bright as he quickly crunched his powerful teeth into them, ears aquiver as he closed his eyes.

The other two were slower, taking care to fold up the net and place it on top of a basket of their own, which had a few fresh fish at the bottom. Found Moon's stomach growled at the thought of food, a little weary after a long day foraging for the hares.

Wandering Star grumbled about a missing fishbone needle, lost in the mud and the fading light. Once, that would have been an unfortunate loss for the tribe, but with Found Moon's diet, they had a reason to keep catching fish. There was no shortage of fish bones now.

Grey Ear and Wandering Star bounded ahead, chatting loudly to each other as they picked their way through the well-worn trail that cut through the forest. The shadows grew long and dark around them. Any one of them could have contained a wolf, a danger to them that Found Moon could never truly represent. Even though his nose confirmed there were none around, he still worried.

``You seem distracted,'' White Tuft said, walking alongside the wolf. He, like all hares, walked with a bouncing gait. Even with his long ears and the way Found Moon hunched, he barely reached the wolf's shoulders.

Found Moon twitched his nose, unsure how much to say. He didn't want to panic the hare, but nor did he want to put them in danger by saying nothing. He kept his voice low, hoping that the two ahead were too distracted by their conversation to listen back. ``I thought I smelled some wolves while I was out there. An old scent, a few days at least.''

``I've heard nothing,'' White Tuft replied. His ears were perked, alert to their surroundings. ``If they're close, then they're much better than you at walking quietly. And no matter what the others say, you're almost as good as a hare at being silent.''

``Almost isn't good enough, though,'' Found Moon said, sighing.

White Tuft lightly shoved against the wolf. ``We're silent so we can survive. You don't have to worry about that. Nothing, thinking animal or not, is going to hunt a wolf.''

``Except another wolf. One who knows how to properly hunt,'' Found Moon muttered. He lowered his eyes and tucked his tail between his legs.

``We'll be careful,'' White Tuft said, resting his hand against the wolf's elbow. ``If we need to leave home again, we'll bring protection, and they're not going to be able to touch us inside the walls.''

Found Moon chanced a quick glance up. Through the trees, he could see the walls the hare spoke of. A massive wooden palisade that protected the homes inside, far taller than even the wolf. The thought of a pack of hunting wolves breaching the palisade did seem absurd to Found Moon, but he still worried.

Sanctuary was on top of a low hill, cleared of trees, though the forest continued almost entirely around the settlement. Many of those trees felled to make way for the settlement had then been used to construct the palisade, with the massive trunks bound together and anchored deep in the ground to provide a protective wall around the hill.

Two deep ditches ran around its perimeter, outside the palisade. Further logs were embedded on the inner bank of the ditches, jutting out with the ends whittled to sharp points. Any predator who dared to charge for Sanctuary would end in a bloody and painful way.

There was only one small entrance to Sanctuary, a narrow path that crested the ditches and into a small gateway through the palisade. Found Moon paused at the entrance, turning back to face the sun against the horizon. He held his claw-tipped fingers to his heart and muttered a quiet prayer, asking for the sun to return safely the next morning.

Found Moon followed his siblings into Sanctuary, the gate dragged open for their arrival, and pushed closed again once the wolf stepped inside. The gate was secured by a heavy log rolled into position, with four hares needed to move the fallen tree.

Nearly two dozen roundhouses dotted the summit of the hill, all loosely surrounding an open area at the highest point of the settlement. Around the edge of Sanctuary, just inside the palisade, grew the crops that supplemented the foraging, barley and corn grown throughout the warmer months to provide a surplus of food and other supplies for the hares to use.

Wandering Star embraced another hare who bounded out of one of the roundhouses to greet the returning group. Long Paw was their mother, short even for a hare, but capable of a glare that could quell even the mightiest predator. That glare was nowhere to be seen for the moment. Her nose twitched as she approached Found Moon, her eyes on the basket of food he carried.

``Come to the fire,'' Long Paw said, taking the basket from Found Moon's hands. ``The night will be cold, but the fire is bright and hot, and we have food already prepared for you all.''

Found Moon lifted his nose to the cool air. Smoke drifted on the breeze, coming from the massive bonfire lit in the very centre of Sanctuary, at the highest point. Most of the hares were already gathered around its base, preparing food or tending to the flames.

Guided by Long Paw, Found Moon made his way towards the edge of the fire. A few hares looked up at his arrival, ears flicking or noses twitching, but no vocal greeting was given.

Found Moon took a seat a little away from anyone else, a few paces from the edge of the fire. The heat bristled at his fur, keeping away the start of the evening's chill as the sunlight gradually faded from the sky. The first stars twinkled into life, spreading through the inky darkness above. It took all Found Moon's willpower to keep his eyes down, or else he would lose much of the night to stargazing.

Instead, the wolf focused on preparing the fish the hares had caught for him. Not only was it food, but he also needed to extract the delicate but useful bones, which would then be used by the tribe for tools. Wandering Star watched him from a short distance, her nose twitching. She always looked on the verge of saying something, but shut her mouth at the last moment every time.

Found Moon smirked. He knew what she was thinking. Usually she handled the delicate tasks, but like most hares, she didn't like handling meat. That was a task for the wolf, in spite of his big, clumsy hands.

A flint blade made short work of the fish, slicing through its scales and flesh with ease. He began to fill two stone plates; one for the flesh he planned to cook, and another for the bones intact enough to turn into tools. His progress was slow, and all around he could hear the hares feasting on the day's food. Only Wandering Star didn't eat, her eyes fixed on the wolf's work.

``You're getting better at that,'' Wandering Star said, once Found Moon had finished the entire catch.

Found Moon's smirk grew into a grin. He waggled his fingers at the hare. ``More useful than you think, aren't they?''

The hare giggled. ``I wouldn't say that. But you're more than just claw and muscle. Usually.''

Found Moon stuck out his tongue. His ears flicked back, a poor imitation of the expression and movement the hares possessed. As difficult as Wandering Star could be out in the wild, she was always relaxed and fun to be around in Sanctuary.

Wandering Star held out a hazelnut. ``Want to try one?''

Found Moon's tongue retreated into his mouth. ``Wh-what?''

The hare grinned. ``A hazelnut. Do you want one?'' The hint of a giggle came to her voice.

Instinct demanded that he wrinkle his nose and turn away, saying no. But he didn't. He hesitated. Then he shrugged. ``Alright. But only if you try some fish.''

Wandering Star's giggles stopped. She twitched her nose and stared at the fish Found Moon had prepared. ``Alright, I'll try it.''

Found Moon carefully picked out a small piece of fish and smoked it in the fire. Wandering Star watched on curiously, leaning over his shoulder with her nose twitching. She already had a couple of hazelnuts grasped tightly in her small hand.

Once the small sliver of meat was ready, Found Moon pulled it away from the flames. He presented it to Wandering Star, who stared at it uncertainly. Her nose wrinkled, and she reached out with one hand, only to withdraw again.

The wolf was aware of a number of eyes watching them. The attention of most of Sanctuary was upon them both. Wandering Star seemed to recognise the audience at the same moment, as her hand lashed out and grabbed the fish from the wolf. Before putting the meat in her mouth, she made sure to press one of the hazelnuts into Found Moon's hand.

``Ready?'' the hare asked.

In answer, Found Moon shoved the hazelnut into his mouth and attempted to chew. Instead, his teeth crunched down on the tough nut, splintering it into many jagged pieces that felt like they tore at his tongue and lips. He almost spat out the dry shards, but he looked up to see Wandering Star valiantly chewing, her nose wrinkled in disgust as she worked her jaw. If she could do this, then so could he.

With a great effort, Found Moon crunched and winced his way through the hazelnut, the taste like licking the bark of a tree trunk. He forced himself to swallow, then immediately grimaced and reached for the closest waterskin. He tried to ignore the raucous laughter that surrounded him.

``That was like eating rocks,'' he gasped, taking a mouthful of water and swilling it around. He couldn't taste any blood, but he couldn't be sure the nut hadn't torn open the soft flesh of his mouth.

``And that was like chewing on wet mud,'' Wandering Star retorted. She stuck out her tongue, but there was no trace of the fish left. She held one hand over her gut. ``How about I stick to my food, and you stick to yours.''

Found Moon shuddered. ``I think I can manage that.''

Wandering Star managed a grin, despite her twitching nose. ``I didn't think you'd actually do it. Perhaps we can still make a good hare out of you after all.''

White Tuft laughed loudly. He leaned over Wandering Star, his hands on her shoulders. ``Come on. We all love Found Moon, but I think it's clear he's a pretty awful hare,'' he said loudly. The firelight twinkled in his eye as he winked at the wolf.

More laughter rippled around the fire. This time, Found Moon didn't mind joining in. He knew exactly what he was, and never pretended otherwise. He didn't aim to be a hare. He was simply happy being a part of Sanctuary, wolf and all.

The night deepened, but around the fire the cold air of the darkness was kept at bay. No one was short of food, not the hares who shared amongst each other, nor the wolf who had the entire supply of fish to himself. Water was plentiful, from the spring that bubbled out from the ground, inside the walls of the palisade. And far above them, the moon's pale face gazed down upon it all, almost full.

Found Moon's eyes were naturally drawn to her cold light, a smile on his muzzle as he stared as though transfixed. He forgot everything around him, lost to that beautiful sight, ignorant of all other senses. At least, until someone elbowed him in the ribs. His attention snapped back to Sanctuary to hear the giggles of the hares.

``You should do your wolf thing,'' one of them cried out. Found Moon thought it might have been Grey Ear, but his head was still too full of thoughts of the moon to pay enough attention.

``What?'' Found Moon asked, his ears warming as they flicked back, almost flat against the top of his head. ``No, I shouldn't. It's\ldots''

Any protests were quickly drowned out. ``Go on. Do it,'' another hare shouted. And then a second, and a third. Soon, what felt like half the community demanded it of him.

Even with his ears growing hotter and his tail tucked against his legs, Found Moon acceded to their calls. He stood up to cheers, which quickly fell silent as he lifted his head and closed his eyes, feeling the moonlight on his face. He breathed in deep, turning his head slightly to avoid the worst of the smoke. Then he opened his eyes and gazed into the moon.

``Ao-ao-aaoooo!''

The rapid barks turned into a powerful howl, ripping itself out of his throat and calling to the untouchable moon. The fur on the back of his neck lifted, hackles rising as a surge of power flowed through his body, a feeling of joy and righteousness.

Half a dozen hares tried to join in, making little yipping noises that were poor imitations of Found Moon's powerful howl. The wolf arched his back and thrust his head up, unleashing another howl that easily drowned out anything the hares could muster.

Another howl responded. Distant. Quiet. Lupine.

A deathly hush fell on Sanctuary.

Suddenly the fire didn't feel quite so warm after all.

***

Found Moon woke early, beating the first of the sun's light. He rarely slept well at night, preferring instead to sit and stare at the stars, but after the distant howl the previous night, everyone had been keen to get back to the safety and security of the roundhouses, Found Moon included.

Smoke still drifted across the settlement, from the smouldering remains of the fire that had not lasted the night. The scent of charcoal settled on Sanctuary like a lingering bad dream, a reminder of the festivities that had been cut short.

Found Moon crawled out of the roundhouse, moving quietly so he didn't wake his siblings or adopted mother. The dried mud walls of the hut kept much of the night's chill out, but Found Moon still shivered as he shrugged off the nest of woven reeds and leaves that he used as a blanket.

As usual, few hares were awake before the sun. Only two guards stood watch by the gate, their backs turned to the roundhouses. Found Moon knew from experience that they could barely see anything in the darkness, but their ears were usually strong enough to detect any movement.

Found Moon shivered and hugged his arms close to his body. A strong wind blew, coming up from the gatehouse, rustling the grass and reed rooves as it whistled over Sanctuary and the summit of the hill.

The wolf slowly moved towards that summit, where he would get a better view of the first light of day. Already, the sky was beginning to pale pink towards the horizon. From inside the roundhouses, he could hear the hares beginning to stir. Their scents were masked by the haze of smoke, which also stung at Found Moon's eyes. The strong wind was playing havoc with the remnants of the fire. No one must have tended to it after the worries of the previous night.

A catch of sudden pain in his foot startled Found Moon. He yelped and stumbled forward, his eyes torn from the hazy sky to the ground underfoot. Small, dark stains splotched the earth.

Blood. The smoke had obscured the scent, but now he knew it was there, the tang of blood was all he could smell.

While his tired mind tried to reason why there was blood on the grass, Found Moon idly reached to pick at whatever had jabbed into his foot. He expected a sharp stone or broken sherd of pot. Instead, he found a tooth. Not a small, blunt one belonging to a hare. Sharp and curved, like his own.

His hand moved to his mouth, feeling around his jaw. None of his teeth were missing. ``Wolves,'' he whispered. He struggled even to get the word out around the lump in his throat, the fear that gripped his chest and made his body hot in terror. They had been here. Inside Sanctuary. They had spilled blood.

The word came to Found Moon's mouth again. This time, instead of a quiet whisper, it was a howling cry. ``Wolves! Wolves were here! Is everyone safe?''

Those hares that had not yet woken were roused by Found Moon's cry. They hurried from the huts, some already carrying flint knives and spears. There was no enemy to find, even as they clustered around Found Moon and the blood spilled on the ground. A nervous clamour grew as the hares demanded to know what had happened.

``Search all of Sanctuary,'' Long Paw said, speaking loudest of all. ``See if anyone is missing.''

A search quickly went out, covering the entire hill within the palisade. Found Moon hunted differently. Instead of hare, he sought the wolf who had come into Sanctuary. Using sight as much as nose, he tracked the small patches of blood that created a trail, following the path the wolf and its victim had taken through the settlement. A couple of interested hares mimicked his moves, but their eyes wouldn't be much use here.

The trail led away from the centre of the settlement, but it did not go towards the only entrance at the gate. That had been guarded all night. There would have been no way in or out for any wolves through there. Instead, the trail came to the palisade wall.

``Did they climb in?'' one hare asked, her voice a hushed and awed whisper.

Found Moon could see no other way. They must have climbed in, though craning his neck high enough to see the top of the wall made him. The wolves had not damaged the wall in any way.

The wolf put his hand on the massive wooden logs, once the trunks of towering trees. Any number of the small pockmarks and blemishes in the wood could have been caused by wolf claws as they clambered up the palisade. The small splatters of blood, however, had to be from a wounded hare carried by wolves.

Whispers spread through Sanctuary, all indistinct and merging into each other as Found Moon looked up. It must have been a dedicated wolf to climb so high, especially with a struggling hare. At least, Found Moon hoped the hare struggled. He would feel much better if that was the case, as it would mean no one had died. Not yet, anyway.

Those whispers began to converge, as more and more hares were identified as safe and present. Wandering Star and White Tuft were amongst them, but one name remained absent. One hare missing. Found Moon went cold, his claws digging into the hard wood of the palisade.

Grey Ear was gone.

``How did they get in?'' one hare asked.

``Do we build the walls higher?'' another added.

Found Moon's claws scratched through the wood. ``I need to get him back,'' he said through gritted teeth.

Silence rippled out through the hares, starting with those close enough to hear him. His words gradually spread back to those furthest away, leaving nervous silence in their wake.

``How?'' someone finally asked. Wandering Star, her voice cracked with tears barely held back.

Found Moon slowly turned to face the hares. A few held onto each other. Some hid behind ears flopped forward, with others unable to hold back tears. One of their number was gone, taken by wolves. By a predator like him.

One of the hares spoke before he could. ``How can you get him back?'' Bright Eye demanded. He was an elder of the village, his fur no longer possessing the lustre of youth, but his eyes remained as bright as his name suggested. ``Our precious Grey Ear is probably already dead, killed by a predator like you. What's to stop you from doing the same to us?''

Found Moon lifted his hands and stepped back, bumping against the palisade. ``I would never,'' he protested. He was glad that no other hares joined in with Bright Eye's accusation, but his ears still pinned back. He lowered his eyes, staring at the feet of the closest hares. ``I hope none of you feel I am a danger to you, that I might hunt you like these wolves have done. But I am still a wolf. I can use that to bring Grey Ear back.''

``How?'' Bright Eye challenged.

Found Moon didn't look up. ``I can track them, follow their scent. I can find where they're resting. I'm a wolf, they'll let me get close to them. Much closer than any of you could,'' he said slowly. His eyes lifted slightly, just enough to look to the necks of the nearest hares. ``I might even be able to convince them to go away and leave Sanctuary alone.''

``But how will you get them to listen to you?'' Long Paw asked, her voice gentle and soft, especially compared to the angry demands of Bright Eye.

The wolf's head dropped again. ``I don't know yet, but I have to try.''

``Then you'll need this,'' Long Paw said. She held out a spear, tipped with a flint head. The weapon was almost as tall as the hare, the shaft carefully carved from wood to give the vulnerable prey animals a better weapon against predators that might take a fancy to thinking animals.

Found Moon didn't take the offered weapon. ``They won't let me get close if I come with a weapon. Especially not a prey weapon,'' he said slowly. He stared down at his hands, rubbing one finger against a claw of the opposite hand. ``These are the only weapons a wolf will respect.''

``If it comes to a fight, you won't have a chance,'' Wandering Star said. She took the spear from her mother and turned it in her hands, prodding the butt of the weapon against Found Moon's chest. ``Take it.''

This time, Found Moon took it. He ran his hands down the long shaft. Then, with a surge of strength, he took the shaft just beneath the flint head and snapped it in two. A few hares gasped and stepped back as the wolf threw aside the broken shaft. He was left with the flint blade on barely a hand's breadth of wood left.

``Get me some reed,'' the wolf said gruffly. The shortened spear was light in his hand. He practiced a couple of thrusts into empty air. ``I can tie this to my loincloth. Keep it hidden.''

No one argued with the wolf. Found Moon didn't know if it was because they didn't dare, or that they had genuine hope that he could come back with Grey Ear. Or that they were glad to be rid of him. None of that mattered. He didn't care what they thought of him. He only cared what he thought of himself, and that meant trying. He had to try to get Grey Ear back.

It didn't take long to get the reed he needed. To the wolf's embarrassment, it was Long Paw who helped him secure the broken flint spear to the inside of his loincloth. His ears flushed hot, and he forced himself to stand still as the hare he considered his mother played around at his crotch. She secured the spear tip with reed, also using a small sheath of thick leaves to cover the sharp flint.

The gathered crowd of onlookers never once moved away, though a few did avert their eyes until his loincloth was put back in position. The extra weight of the spear made his clothing sit uncomfortably, but he knew he would feel better for its presence. He wasn't throwing himself at the wolf pack unarmed.

``You know you don't have to do this,'' Wandering Star said quietly. She stood back a couple of paces from her mother, with White Tuft by her side.

Found Moon couldn't quite meet her eyes. ``I must,'' he said. ``No matter what, I will bring Grey Ear back.''

Left unsaid was the fear that Wandering Moon would bring back Grey Ear already dead. Even worse, the thought that he would only bring back devoured remains. That would be better than doing nothing.

``Bring him home. Please,'' Long Paw said. Her lip trembled. Then she turned away.

Found Moon wanted to say something. Anything. But he didn't know what would make things better. He couldn't make promises he had no guarantee of keeping. He began to walk in silence, with his back straight and head held high. He tried not to think that this might be his last time in Sanctuary.

Finding Grey Ear was all that mattered.

***

Picking up the scent of the wolves was not difficult. They had made no effort to hide their tracks, running through the forest and leaving behind a trail of broken branches and obvious pawprints. There was no sign of blood, either on the ground or the leaves the wolves had pushed past. If they had Grey Ear, then he was likely not badly injured. Found Moon refused to think about it. He didn't want to give himself too much hope.

Forest eventually gave way to open plains, long grass rustling in the wind and undulating over the low hills stretching to the horizon. The weight of the trees hanging over his shoulders lifted, and the wolf felt a freedom surging through his mind and body that warred with the anxiety in his gut. He couldn't bring himself to be happy, but he did allow his legs to stretch, his strides lengthening as he sprinted in a way he could not do in the forest.

He was born to run in a way hares were not. Sure, they could outpace a wolf over a very short distance, but over more than a hundred strides, a hare could never hope to beat him. Of course, the wolves he hunted had that same freedom, that same strength. He could not hunt down the wolf pack in the wild. He would have to negotiate with them in their camp, wherever that was.

The scent of wolf grew gradually stronger. Each time the wind shifted it drew more of that unfamiliar yet intimate smell to his nose. Found Moon couldn't be sure if he was close to overtaking his quarry, or if their settlement was nearby. The wolves had to live somewhere close. It would be futile hunting too far out from a place where they could rest.

He heard the wolves before he saw them. The pack made no attempt to be quiet, speaking loudly amongst themselves, the exact nature of their words obscured by distance and the wind. They were hidden behind a low rise, so Found Moon cautiously climbed, trying to avoid making any noise himself. At least he was downwind of the wolves, so they would not be able to smell his approach.

Found Moon expected to see a settlement, like Sanctuary. The wolf pack did not live in such a place. They lived at the base of a hill, nestled in a valley, vulnerable to predators. No palisade protected them. Instead, they dwelt in a simple cluster of hideskin tents surrounding a firepit. The closest thing to defences they had were the mammoth tusks and ribs stacked around the largest of the tents.

At first, Found Moon couldn't find the hunting party. Brief worries that he had tracked the wrong wolves flared in his mind, but his pounding heart quickly calmed when he caught sight of them, already around the back of the tents. His blood boiled anew when he saw Grey Ear slung over the shoulder of one wolf. The hare moved, a futile twitch of bound limbs. He was still alive.

Found Moon crouched low as he tried to work out how to approach. He didn't want to recklessly charge forward without a plan in mind. He needed to wait, to be confident of what he needed to do and how to do it.

A hand to his back put all such thoughts from his mind. He froze, barely daring even to breathe. He could smell nothing. Hear nothing. To all his senses, he should have been alone.

If the hand hadn't been enough, the low growl was certainly realisation that he had attracted unwanted company. He struggled not to cower, to shrink lower to the ground. That was what a hare might do. Here, he had to be a wolf. A confident predator. Perhaps he should have swatted the hand away or growled back. He did neither. Frozen in fear, he waited for the other wolf to speak.

``Hunting outside your territory, little pup?''

The other wolf grasped Found Moon by the scruff, hauling him to his feet with unexpected strength. A tight grip held him in place, leaving any struggle futile. His feet dangled off the ground, the loose skin of his neck pulled tight and uncomfortable in the grip of the wolf. Slowly, Found Moon was turned, then thrown back to the ground.

He faced up, his eyes wide. Above him towered the first wolf he had ever seen up close. The predator was massive, covered in thick, shaggy fur plastered in mud and grime. That mud had masked the wolf's scent, hiding it beneath the smell of the land. Admiration briefly warred with fear, but all confidence and courage fled as the predator bared his teeth, exposing yellowed fangs flecked with traces of blood from his last kill.

``A mute, are you?'' the hunter asked.

Found Moon managed to shake his head. ``No, I can speak.'' He forced the words out from his muzzle, his voice pitched high in a near squeak.

The hunter sneered. ``So you can. Perhaps you can use your tongue to explain why you're in our territory.''

``I, uh\ldots'' Found Moon's eyes flicked to the side, struggling to focus on the hunter. His throat was dry. His tongue lashed at his lips, running over his sharp teeth. ``I need to\ldots''

``Out with it,'' the hunter snapped.

Found Moon swallowed his fear. He looked up, but he couldn't quite meet the hunter in the eyes. He settled for the dirty white fur of the wolf's throat. ``I want to see your chief.''

A wide grin broke out across the hunter's muzzle. He held out one hand to Found Moon, muddy claws gripping tightly against the flesh of the smaller wolf. ``Well, why didn't you say so before? I can take you to the chief. He just got back from a hunt.''

Found Moon immediately regretted the request. He did not like the predatory gleam in the hunter's eyes. Every instinct told him to run, to run fast and far away, back to Sanctuary if he could. But the hunter's grip on his wrist was too strong to break. Feeling like he was almost as much prey to these wolves as Grey Ear, Found Moon reluctantly followed the hunter towards the small village of tents.

They quickly gained attention. Sharp, eager eyes tracked their movement towards the tents. Found Moon had always felt a giant amongst the hares, with even the tallest of them barely coming up to his shoulder. He was just as short to these wolves as the hares were to him. His shoulders hunched, further diminishing his size as he cowered by the hunter's side.

Found Moon quickly lost sight of Grey Ear. He tried not to keep too focused on the hare, not yet. The wolf pack probably wouldn't treat him too kindly if they realised that he was after their prey. His thoughts raced, struggling to work out a way to free himself from the hunter's grip, and also to get away from the camp with Grey Ear alive. His foolish declaration that he would make it safely back to Sanctuary seemed a difficult challenge now.

There were more offerings and talismans around the edge of the largest tent. Strewn amongst the mammoth bones lay the remains of other hunts, as well as small trinkets of carved wood and chipped stone, likely stolen from thinking animals who had been preyed upon. The young wolf could see no evidence that the vicious pack made any tools or weapons of their own.

Found Moon was thrown to the ground in front of the large tent. He scuffed his knees against the coarse, dry dirt, and for a moment he thought his loincloth, weighted with the flint knife inside, was about to dislodge and expose himself in front of the pack. Fortunately, no such embarrassment happened, but before Found Moon could work out whether he was expected to stand or remain prostrate on the ground, another wolf emerged from the tent. Even from the size of his paws, Found Moon knew this wolf was bigger than any of the others he had seen in the camp. His head slowly lifted, higher and higher.

``Who is this?'' the massive chief growled. He nudged his foot against Found Moon's shoulder. There was little the smaller wolf could see, his vision dominated by the chief's muscular legs and loincloth.

``I'm not sure, Chief Ripper,'' the hunter said, from somewhere just behind Found Moon. ``I caught him skulking after our raiders.''

The chief sneered. ``Ah, a thief, then? A wandering outcast left to scrounge off the scraps of superior hunters?''

Found Moon opened his mouth to protest, then snapped it shut again. He would not get any opportunity to rescue Grey Ear by picking fights with the wolves, especially when all the advantages of size and strength lay with them. He bowed his head, ears folding flat. ``Yes. I came to learn from better hunters, so that I might provide for myself and my pack.''

A ripple of laughter spread through the watching wolves. Found Moon struggled to ignore them, his tail tucked low. He kept his eyes down, not looking any higher than the chief's knees. He was fully aware of the larger wolf's fierce gaze, like heat burning on the back of his neck.

``Why should we share our food with a pup who cannot hunt for himself?'' the chief asked, a deep snarl coming into his voice. A few drops of saliva dripped onto Found Moon's muzzle. The smaller wolf kept his hands on the ground, not daring to wipe it away.

``I do not come asking for food,'' Found Moon said quietly. He swallowed, his tongue feeling twice the size, his throat parched like he had not tasted water in days. ``I merely ask that I watch and learn. Please, give me until tomorrow night at least.''

The chief did not answer. Not immediately, though the dribbles of saliva continued to fall. His massive feet shuffled closer, the curved claws on each of his toes almost close enough for Found Moon to touch with his muzzle. They each looked a deadly weapon, far more perfect and precise than the jagged piece of flint hidden beneath his loincloth.

``You are fortunate,'' the chief finally said. A hefty hand closed around Found Moon's shoulder and dragged him back to his feet. The smouldering gaze of the chief's bright yellow eyes met his. ``Tonight is one of generosity. The moon will be full, and we must sing our praises to the spirits that guide it through the sky. You may join us for the night, and we shall see what tomorrow brings.''

Found Moon could barely stop his tail wagging. He didn't yet know how, but he would have a chance to save Grey Ear. The wolves were giving him that opportunity. He struggled to keep the emotion from his voice as he lowered his eyes. ``Thank you, Chief Ripper.''

The large wolf snorted in amusement. ``What is your name, pup?''

``Found Moon. My name is Found Moon.'' A ripple of laughter spread through the pack. Found Moon's ears reddened, his head and tail low. The wolves of the pack chuckled to each other, a few even repeating his name in mocking tones.

The chief did not join in the laughter, but a smile twisted at his muzzle. He held up his hand. Silence fell. ``Welcome, Found Moon,'' he said, somehow turning the name into a mocking insult. ``We trust you will enjoy our ceremony.''

Before Found Moon could question the chief, the massive wolf had turned away, barking orders to the pack. Found Moon backed away, making himself small as the wolves forgot about their mockery. The sun was beginning to sink towards the horizon, with the sky already starting to darken. The moon had not yet risen from beyond the forest, but the wolves seemed to know it was coming with a certainty that had not reached Found Moon.

The wolves prepared a space in the centre of the encampment, clearing away the tents closest to the blackened firepit. Meat came from seemingly nowhere, placed with reverence around the fire once it was lit. None of it seemed to be from thinking animals, though Found Moon couldn't be sure. All meat looked and smelled the same once it was skinned and prepared. A brief panic settled in his gut, fearing he might already be too late for Grey Ear, but as he moved around the camp, trying to keep out of the way, he caught scent of the hare. Fresh and alive. Held captive inside the chief's tent.

The pack ignored Found Moon, but for a few snide glances and avoidable bumps into his shoulder. It was more than a feast that they prepared. Grass was scraped away to bare dirt, with sticks and branches plundered from the forest to partition off a small square in front of the fire pit. Carved bones were deposited around the simple, ankle-high wall.

Then came the drums. Found Moon's eyes widened, his mouth hanging partially open, as three wolves dragged them from one of the tents. The bases of the drums were carved exquisitely from polished wood, with taut animal hide stretched over the top. Found Moon had no doubt they were stolen from elsewhere. He longed to approach the instruments and run his hands over them, but held himself back. He wasn't there to enjoy the ceremony. He needed to find a way to get Grey Ear to safety, but there was always at least one wolf with their eyes on him, or on the entrance to the chief's tent.

The first howl rang out just as the last light of the sun dipped below the horizon. The fur on the back of Found Moon's neck lifted. He looked to the western sky, holding two fingers to his heart. But he was the only one who looked to the dying light of the sun. He quickly turned, ears folded, as he looked to the opposite horizon with the others.

The pack stood in silence, all perfectly still. Darkness swathed the sky, even as the stars burned brighter. A cool wind rippled through Found Moon's fur, coming down from the hills that darkened the far horizon to his left, further away from Sanctuary and the forest.

Pale white light breached the horizon. The moon lifted from below the world, bright and full. And still the wolves waited. They breathed harsh and heavy, chests heaving as though they struggled to contain themselves.

The bottom edge of the moon rose above the tree line. Only then did the wolves unleash. As one, they each drew in a powerful breath, then let it all out in a cacophonous howl, keening towards the heavens with a strength of voice Found Moon could only admire. He longed to join in, but felt the chief's eyes on him, unsure if he was being warned to remain silent, or being judged that he did not add to the howl. He knew he would never match the sheer power the other wolves managed. His own howl was pitiful in comparison.

Three more times, the whole pack howled in unison, a chorus to welcome the moon to the darkened sky. Found Moon was so enraptured in the sound that he didn't even notice any of the wolves moving. Only when they began to beat their hands on the drums did he realise the pack moved anew.

Howls turned to dance and music. With one wolf to a drum, they hammered out a beat in perfect unison, their hands pounding against the taut skin. A fifth wolf kicked to the rhythm, his feet stirring up dust as he scuffed around the cleared space in front of the fire. His limbs and torso twisted with his lithe movement, loincloth swirling and bone talismans clicking against each other.

The pack circled around the firepit and cleared space, cheering on the dancing wolf and drummers. More and more joined in, swaying to the music and clapping their hands in time with the beat pounded out by the drums.

Found Moon lost track of the few faces he recognised. Both the chief and the hunter disappeared amongst the pack, the wolves all little more than darkened silhouettes in front of the bright firelight. Smoke obscured most scents, perfumed by the sap and oils of the burning wood, but the sounds more than made up for the dulled senses.

The rhythm of the drums was a heartbeat, invigorating the blood and fuelling the voice and movement of the pack. Feet scuffed and scraped against the ground. Hands clapped, palms together or against thighs. Wordless voices howled to it all, necks arched so their heads were turned to the spirits in the dark sky.

Found Moon's breath was taken away. He shivered, the cold wind cutting through the heat of the fire. He longed to be amongst the crowd of bodies, closer to the fire, a part of the pack. He wanted to dance with them, to sing and howl to the moon and the spirits, but their attention was all on the dancers. He was ignored, not part of the pack, not a part of the celebrations. Here, he was an outcast among his fellow species, just as much as he was among the hares.

A startled realisation pierced through his mind. It was like the smoke had hazed his thoughts, the pounding beat distracting him. He was not here to ingratiate himself with the pack. And nobody was paying any attention to him.

He had to take the opportunity. Found Moon tore his eyes away from the smoky celebration and padded around the light, keeping to the shadows and hoping the smoke was enough to mask his scent. He could barely see the chief's tent in the gloom beyond the fire, though the great mammoth tusks outside the entrance did cast dark shadows against the starlit sky.

Found Moon cautiously put his hand out, lightly brushing against one of the tusks. He had never seen one of the massive mammoths alive, though he had seen a corpse once. He could only imagine how majestic such a creature must look when rampaging across the steppe, but with a shake of his head he forced himself to ignore such fantasies.

He glanced back. The pack danced around the fire, clapping to the beat of the drums. Those who looked away from the firepit only did so to gaze at the moon. His tail twitched in excitement as he turned back to slip inside the largest tent, only to bump into something warm, heavy, and full of muscle.

The chief grabbed hold of Found Moon's wrist before the smaller wolf could escape. Claws pinched tight against flesh. Brutal strength dragged Found Moon back, out of the tent and into the firelight. Though the drums continued, the thumping feet of dancing wolves stilled.

To his horror, Found Moon realised he was not the only one in the chief's grip. As his feet dragged against the ground, hauled towards the fire, he caught sight of a shadow in Ripper's other hand. The dark shape of a hare, limp and unresisting.

Both Found Moon and Grey Ear were thrown to the ground, in the centre of the clearing by the firepit. The wolf rolled a couple of times, before coming to rest by the firewood. His heart thundered to the beat of the drums, which seemed louder to his ears now that they surrounded him.

Found Moon looked up at the ring of wolves. Their eyes gleamed. Teeth glistened. Predatory grins were masked onto their muzzles.

His knees and palms pained him as he struggled to his feet. No one approached him, or the hare lying curled like an infant by his side. The wolves all looked down on him, staring with those unblinking eyes and open jaws like he was a morsel of meat.

Standing on trembling legs, Found Moon tried to stare down the massive bulk of the chief. He could not manage it. He looked down as the chief barked in laughter.

``Why would our interloping visitor be sneaking into my tent to claim our prized meat?'' Ripper asked, his voice loud enough to drown out even the drums.

``I\ldots{} I\ldots'' Found Moon stammered, no answer coming to mind. Either he was trying to hunt and kill the hare, therefore betraying the hostile welcome he had received from the pack, or he was trying to rescue the hare, in which case he was not a wolf worth protecting. Not according to the pack. He knew there was no answer which would save him, and his throat closed over so he couldn't even speak the truth and suffer the consequences.

``Shall we perhaps show generosity?'' the chief asked, turning slowly on the spot to look around at his pack, before shifting his gaze upwards. ``After all, is it not the full moon? Why don't we give our friend a choice?''

Found Moon's heart sank, even before the gnashing howls of the pack rose to a terrifying crescendo. He struggled to swallow, his throat so dry. He almost tripped over his own heels.

Chief Ripper stepped forward, moving from the ring of wolves. He gestured down to the cowering hare. ``Go on, Found Moon,'' he said, again twisting the name into an insult. ``Take a bite. Kill your prey. You said you wanted help with hunting, so go ahead. You'll never have an easier kill.''

Found Moon's eyes darted down to Grey Ear, shivering but otherwise still, halfway between himself and the chief. He looked up again. He chewed on his lip and didn't answer.

The chief sneered. ``Perhaps I should make it a little easier for you,'' he said, taking another step towards Found Moon. ``Either you kill the hare, or I kill you. And then the hare.''

``I will not kill him,'' Found Moon said, the words ripped from his throat before he could hold them back. He trembled, feeling so small beneath the cruel smile of the chief.

``Of course you won't,'' the chief said, his voice quiet despite the howls from his pack, the beat of wolf hands on the drums. The brutish wolf smiled wider, showing his fangs, drooling saliva. ``A wolf comes into my territory, stinking of hare, bearing one of their names. And he has the temerity to lie to me, to try to steal my food? You don't even deserve the death I shall give you, mongrel.''

``Let us go,'' Found Moon said, voice shaking almost as much as his body.

The mocking laughter started with Ripper, but soon spread to the rest of the pack.

``Let you go?'' the chief asked. He extended one hand, claws glistening in the firelight. ``I shall enjoy looking up to your spirit when you take your place amongst the stars. It shall fill me with great amusement. Now, mongrel. Fight me and die like a wolf, however little you deserve that honour.''

Found Moon quickly glanced around. The wolf pack had him surrounded. There was no way to run, certainly nothing that allowed him to take Grey Ear with him. His only option was to stand and fight, to defeat the chief and get away then. He almost laughed. Ripper was so much bigger than him, more powerful in every way. His hand shook as he reached for his loincloth.

The chief laughed. ``Not that kind of fight, mongrel. I don't know what you do with those hares, but you will not win that way either.''

Found Moon struggled to ignore the raucous laughter, his ears low. He tugged free the flint blade and flicked aside the sheath. The sharpened stone felt pitiful and light in his hand, but it silenced some of the laughter.

Ripper sneered. ``Of course you would use the weapons of the hares. No matter. Nothing you wield is stronger than the fury of a true wolf,'' the chief growled. He lowered his head, bracing his feet against the dusty ground. ``Now, die.''

Found Moon slashed empty air, his knife passing harmlessly over Ripper's head. The chief slammed into the smaller wolf, shoulder against ribs. The impact stole the air from Found Moon's lungs. He fell back, scraping against the ground as the full weight of the chief pinned him down.

Once, twice, three times the closed fists of the chief pummelled against him, each sending a crack of pain through his body. A quick kick to the stomach momentarily dislodged the chief, giving Found Moon the chance to roll to the side. His chest and face ached. The taste of blood filled his mouth. Already, he could barely stand. He was going to die. It was as simple as that. He would die to the howl and laughter of wolves. Grey Ear would be next. The hare would not be able to escape. The hares of Sanctuary would know he failed. There would come a time when they would stop checking every dawn in the hope of seeing the pair return home.

Found Moon's grip almost slackened on his knife. What was the use in fighting? Why delay the inevitable? He stared down Ripper, taking a step back, but he did not raise his arms to defend.

Ripper's fist opened as he struck again. Claws slashed against Found Moon's shoulders and cheek, wetting his fur with crimson blood. A kick to the gut sent him sprawling to the ground again, by the feet of the onlooking wolves.

The chief prowled towards him, a savage gleam in his eye. Someone shrieked, a sound unlike anything a wolf could make. A shadow leaped across the fire. Grey Ear leaped onto Ripper's back, his small hands wrapped around the wolf's throat.

Ripper roared in anger and spun around, his fist grabbing Grey Ear by the shoulder and tearing the hare away. Grey Ear yelped as he was thrown to the ground, quickly gathered up again by another wolf. The hunter growled in triumph as he wrapped both arms around the struggling hare's body. The wolf glared directly at Found Moon as he pressed his muzzle to the hare's shoulder, teeth grazing against flesh.

Found Moon's blood boiled in his veins. His fingers tightened around the knife. It was one thing to know he was going to die; it was another to see the hunter threatening to kill his brother. The diminutive wolf snarled. If he had to die, then he would make something of it.

A smirk flashed across the muzzle of the chief. He bared his teeth and lunged again, claws swiping. They brushed through Found Moon's fur, but just missed his flesh. The smaller wolf slashed back, his adversary narrowly dodging the knife.

Grey Ear whimpered, falling still in the grip of the hunter's arms and jaw. Found Moon struggled to keep his focus on Ripper, his ears twitching to every quiet noise, barely audible over the wolves. Drums beat in time to his heart. Rage bright as the flames burned white hot through his blood, flowing red from his cheek.

Claws raked down Found Moon's side. He shrieked in pain and stumbled back, the agony extinguishing his anger. He panted and stumbled away but was pushed back again by the ring of wolves that surrounded the fighters.

His strength waned. He was in too much pain to think properly. All he could see was the massive bulk of the chief, fur nearly unblemished with blood. Found Moon staggered forward, only to be struck by a powerful punch to the jaw. His vision flashed white as he spun to the ground with a limp crash. Dimly he was aware of the wolves howling, but somehow, over all the noise, over the pounding in his head and the shriek of his thoughts, he heard a hare whispering his name.

``Found Moon, please get up\ldots''

Blinking furiously, Found Moon rolled onto his back. A dark shadow loomed over him.

Ripper lunged for the fallen wolf. Found Moon swung up with his right arm at the same moment. The flint knife sunk into flesh. It scraped against bone as it slid between the ribs. The handle pulsed in time with the beat of Ripper's punctured heart.

The larger, heavier wolf collapsed on top of Found Moon. Ripper breathed in, a death rattle as his hands weakly struggled to find the neck of his foe. ``You mongrel\ldots''

Found Moon pushed Ripper off himself once the chief fell still. He yanked his knife out, blood rushing from the incision as the flint pulled free. A deathly silence stilled the pack.

Though he could barely stand, Found Moon forced himself to remain upright. He staggered towards the hunter, his bloody knife lifted. ``Let him go,'' he growled.

The hunter obeyed, shoving Grey Ear away. The hare stumbled into Found Moon's waiting arm, pressing tight to his lupine brother. A couple of wolves hastily stepped away, clearing a route out of the ring. No one else moved. Found Moon wasn't sure if they even breathed, as though their own life had been stolen away with Ripper's.

The young wolf spat out a mouthful of blood. His throat felt dry despite the acrid tang coating his tongue. He struggled to speak. ``Sanctuary is my territory,'' he said, his voice raspy and pained. He had only the crackle of the fire to compete with. He doubted the wolves failed to hear him, even if they did not acknowledge he had spoken. ``Sanctuary is mine. As is the forests that surround it. You are not to encroach on my land. I have killed your leader. That means you must obey me. Do you understand?''

At first none answered. Found Moon snapped his jaws and growled. He pointed his bloodstained knife towards the closest wolf, to the hunter who had first captured him. ``Do you hear me?'' he barked.

The hunter bowed his head, looking to the ground. ``We hear you,'' the wolf said, his muzzle twisted into a bitter grimace.

The ring of wolves parted fully as Found Moon shuffled towards them. He leaned heavily on the hare at his side, blood still leaking from the wounds on his face and chest. His hand ached with how tightly he grasped the flint knife. But no wolf attacked him. None even looked at him, their eyes shifting away whenever he got close.

Turning his back on the pack was the hardest thing. He expected to feel claws any moment, but nothing came. No one approached. No one dared. He had killed their chief. A prey's weapon had done it. Not claws or fangs. A simple stone blade.

``You didn't have to come for me,'' Grey Ear said quietly.

Found Moon grunted in pain. ``You're my brother. I had to.'' His ears strained, turned back to ensure no one snuck up on them. He could hear nothing but the fire as it burned through the wooden fuel.

The hare fell silent again. Together, they limped slowly away from the pack's shelter, into the darkness of the night. It would be a long walk back to Sanctuary, especially injured as they both were. Starlight would guide the way, but before they reached the forest they would be exposed and vulnerable.

``Do you think it will be enough?'' Grey Ear said at last.

Found Moon risked a glance back. No one followed through the gloom. The fire continued to burn, but the celebration to the spirits and the full moon had turned silent. There wasn't even a mourning howl for the fallen chief. He had been slain by a prey's tool. Found Moon doubted there would be any respect left for Ripper. But to the one who had killed him, perhaps.

The hare didn't want doubts and uncertainty. Found Moon gently squeezed his arm around Grey Ear's shoulder. ``It will be enough,'' he said, managing a bloodstained smile to the darkness. ``We'll be safe now.''

It would be up to him to enforce that safety. He was a wolf, but the hares were his family. He could protect them, with claw or blade. No wolf would threaten his family again.

Sanctuary would be a haven for them all.
