The cave with no entrance was lit by a light with no source.

It was always the same, every time Sreki dreamt it. He would find himself there in the cave's centre, hyena paws on the soft sand. It was not the sand of the wide river Pindipindi, coarse and spattered with pebbles and sharp rocks, but rather the finer, silky sand of the sea. At least that's what Sreki assumed; he had never been to the sea.

It felt gentle on his paws, and he scuffed his feet in it, reveling in its caress. Yet, as with every time before, his eyes did not linger on the sand, and Sreki lifted his gaze to the cave surrounding him. It was small, with a ceiling and walls of rough grey stone. The walls curved sinuously around, such that some regions of the cave were blocked from view, but Sreki knew it did not extend far, even though he had not traversed the entirety of the cave himself.

Sreki felt safe here. But there was something waiting---a strangeness in the air around him that he could not define.

He assumed it was the pots.

They were where they always were, nestled haphazardly on the sandy floor. All were different---some large, some small, some made of odd materials, some with peculiar designs or emblazoned with unfamiliar glyphs---yet they were all there, all in the same spots. Perhaps two eights of them, all told; he hadn't counted. In the many nights before when Sreki had come to this place, he had walked among them, paws whispering on the sand. In his first visits, when the cave was new to his dreams, he had moved one or two of them, sliding them from their places or toppling them over. But the next time they were always back where they had been. It had felt wrong when he had done so, so he did not try again.

Sreki never bothered with the further recesses of the cave. A few of the pots knelt there in the shadows, but the closer ones called to him. They made his paws itch and his whiskers prickle. And with their summons, the frustration began.

Because each pot was stoppered with an immovable lid.

At first this was a curiosity. But it soon became more, as Sreki realised that no matter how hard he tried, they would not budge. He knew there was something inside, something for him and him alone, but it remained locked away behind unassuming lids. It became infuriating, and as always, his hold on the dreamcave shuddered and wavered and was lost.

\secdiv

\noindent ``Sreki, wake up!''

He clawed at the shredded tatters of the dreamcave as it drifted away, once again.

The pre-dawn light crept through the entrance of his hut, silhouetting Ruha's distinctive form, hyena ears perked forward with concern. Ruha lightly shook him.

``Sreki?''

``Ruha\ldots{} I\ldots''

``The dream again?'' Ruha's voice was soft, as if it tried to drape itself over the worry beneath, failing to hide it in its entirety. ``Your heart is a drum calling to battle.''

Sreki struggled to sit up, and the wisps of the dream scattered. Ruha squatted on his haunches next to him, and the touch of his paw on Sreki's face was gentle. It took several moments for the thud of his heart to settle, and he nodded.

``Have you spoken to Old Eye of it yet?'' Ruha inquired, tentatively.

``No,'' stated Sreki firmly. ``She thinks I'm a fool, a cub, a screamer at monkeys. Why should I?''

Ruha sighed. ``She's a shaman. She says there's something to you. If she felt she were just swinging at the wind she'd not be bothering with you.''

``And who would bother with me if she didn't?'' Sreki countered.

``You are so angry, Sreki. But please, do not throw your spears at me.''

Sreki's muzzle dipped, ashamed. ``I am sorry.''

Ruha pulled him into an embrace, and Sreki held tight.

``The hunt leaves soon,'' Ruha said.

Sreki released him, and looked him up and down. Ruha was naked, and there were but a few lines of clay upon his body. ``Where's your loincloth?''

``Here,'' Ruha replied, holding it up, along with a small bowl. ``I wanted you to help me prepare.''

``Seems Nyota has already drawn some of the reeds by the river. I scent her on you.''

``Just a few. Don't pout, Sreki. I love you as well, and I always have. Pindipindi will go dry and the reeds become dust before that changes.''

Sreki sighed and got to his feet, taking the bowl of white clay from Ruha's grasp. He began to paint upon Ruha's fur, letting the clay guide his fingers and flow on its own: the reeds to hide amongst the grasses, the waves to slip and evade, and the spears for striking true. Ruha grinned at Sreki as the last spear adorned his sheath. ``Thank you,'' Ruha said, and it was heartfelt.

Sreki smiled shyly, as he always did when Ruha spoke with such intensity, his words shining bright as the sun above the savanna.

``I must go,'' he added, apologetically, and Sreki nodded. Ruha tied his loincloth around his waist, turning to leave the hut.

``Ruha? Will you be here tonight? Or does Nyota have her claws in you?''

``I'll be here. Nyota knows you'll always be part of me, and I you. She accepts it.''

Sreki held those words close. It meant the cough and stutter of the choppy waves in his mind would calm, at least for a while.

\secdiv

\noindent ``Try again.''

Old Eye settled on her haunches, expectantly. The small cooking fire cast stark shadows across her scarred face as she watched the young hyena seated by her side. Sreki ignored her, his muzzle set in concentration.

\emph{I'm trying as hard as I can!}

Sreki's mind reached for the flames beneath the copper pot, its water bubbling. It felt like trying to grasp dust motes. He had no idea if he was even doing it the right way, and the flames wavered there, mockingly close. For all he strained, the fire might as well have been eights of strides away.

\emph{I'd have a better chance flinging a spear at that distance than persuading this flame but a few paws away. But then, that would imply I am invited to the hunts.}

He closed his eyes for a moment, trying and failing to calm himself. He knew Old Eye was staring at him. He wondered briefly how Ruha's hunt was going.

Sighing, he switched his attention to the pieces of wood within the fire, as they slowly and stoically gave way to the merry flicker of flames. Silently he spoke to them. They ignored him, as if he weren't there, as if his words weren't meant for them. The wood was as distant as a single stalk of grass on the savanna's expanse, and he needed to whisper to it and it alone.

His gaze flicked briefly to Old Eye. \emph{Of course she's looking at me}.

He moved to the water within the pot. It didn't listen either. \emph{Am I even doing this the way I'm supposed to? I have no idea!}

It bubbled there, but its world did not include him. He glared at the water angrily, his ears flat against his head, mentally groping for it. The bubbles of the water became the bubbles of his anger, and his paws itched with the desire to strike the pot and dash its contents over the earthen floor of the hut.

``!Sreki\ldots''

\emph{Gods, I hate how she says my name. I am not a cub any more!}

``!Sreki!'' Old Eye emphasised the click at the beginning, a warning to a wayward cub, and he turned and glowered at her. She met his scowl calmly and waited.

He studied her face---the left eye a vibrant emerald, alert and intense. The right\ldots{} well, a horrible scar split it like a chasm, a fur-less furrow that went from forehead to muzzle, and the eye itself lay there dormant, blind and milky-white. The power behind that gaze unnerved him, and her one eye easily conquered his two as he dipped his muzzle in submission. His flattened ears drooped as he felt the anger dribble away, flowing out of him almost as quickly as it had arisen.

``You push too hard. You're straining with a muscle you haven't yet found, in a limb you have no control over,'' Old Eye stated quietly, her voice tinged with sympathy.

Sreki nodded, eyes downcast, staring into his lap. He wore nothing but a simple covering of dark brown hide at his waist. \emph{I wish it were a hunter's loincloth. Like Ruha's. Or even Peshu's}, thought Sreki bitterly.

``Why do you think I say your name like that?''

Sreki stayed silent.

``Because in some ways you are still a cub. Yes, you have the height of one grown, the shape, even some of the muscle of the hunt. Even the heft beneath that loincloth, I'm to understand.''

Sreki felt his ears grow hot.

``But it is the impulsiveness, the stubbornness, the rawness. You are the chaos of the wind rustling the tall grasses, weaving this way and that way on a whim. Look at you. You throw a spear, and if it does not strike true, you toss the rest aside and storm back home.''

``I---'' he began.

``How do you think I lost my eye? Shall I tell you?'' Old Eye demanded.

He stayed quiet, curiosity and shame sparring for control.

It seemed the flash of that green orb faded somewhat, and Old Eye sighed resignedly. She seated herself on the dirt floor of the hut, arms crossed. Armour of soft hide covered her from breast to thigh, glyphs of her own devising carved and dyed across its surface. The rest of her was covered in tawny fur, spattered with dark spots, like all the tribe---yet hers had begun to grey in places. Much older than Sreki, perhaps, but still strong-jawed, and she held his curious orange eyes with her singular one.

``It was a challenge, simple as that,'' Old Eye said. ``I am not proud of it. Everything was a \emph{now} thing for me then. I did not wish to wait. Young and angry and impulsive and stubborn, much like you. I desired a place above me, a place I did not deserve. I brought my challenge to the village centre, to be seen by all, as is the way these things are done.''

Old Eye paused, and Sreki shifted uncomfortably. The silence grew, and Old Eye waited until it became heavy and threatening, like rain-thick clouds.

``Taori defeated me,'' Old Eye continued, and the tautness in the air broke. Sreki breathed out the breath he hadn't realised he held.

``The wound festered, as if my foolishness would not let it go. I lay as dead for eight and one days, but in the end I lived. Taori's spear took my eye and left wisdom in its place.''

She glanced over at the young hyena, who sat there with ears perked forward, attentive to every word.

``That's it. There is nothing more to tell. Taori won, and I lost. And here we sit.''

\emph{And here we sit.} Sreki looked down at the dirt floor between his paws. The silence grew again, needing to be filled. Uncertainty pricked at him, but he tried to ignore it, looking back towards the flames. They ignored him. So did the wood, mostly burned now. The water's boiling bubbles mocked him.

\emph{I cannot do this.} ``I cannot do this,'' he said, ashamed at the whine that snuck into his voice.

``Tcha!'' Old Eye spat, her patience lost. ``We'll get no further today. The hunt has likely returned and will need help preparing the kill. Go.''

\secdiv

\noindent The hut was eights of strides behind him, but Sreki could still feel his hackles bristling, pricked by anger and shame from the bite of Old Eye's words. Pushing it from his mind was hopeless---it was a fly that kept returning no matter how many times he waved it away. As he neared the village centre, he spotted some of the hunting party. By the time he was close enough to determine that Ruha was not among them, it was too late. His hackles rose further.

``!Sreki,'' said Peshu disdainfully, with the intonation of addressing a cub.

\emph{Of course it would have to be Peshu}, Sreki thought, and his fury rekindled. He glared over at the hyena who had spoken.

Peshu stood nonchalant, with the lazy posture of arrogant confidence. He was standing perhaps two eight-strides away, his spear leaning against his shoulder. Several others stood by his side with their huntleader, Tal, nearby. Peshu had seen the same seasons as Sreki but had clearly found his place in the hunt---he was tall and muscled, much like Ruha, and Tal herself had praised his youthful exuberance and skill. He'd won his hunter's loincloth several seasons back and used every opportunity to gleefully provide constant reminders of Sreki's lack.

Sreki, ears back and hot with anger, spat the words that bubbled up.

``Peshu. I don't see you carrying any kill. Did you miss?''

Peshu's eyes narrowed. ``Fool. The kills are already by the fire, being prepared. Don't want the \emph{cubs} to go hungry,'' he snarled, the emphasis making his meaning clear. ``And miss? I think not. I at least know how to use my spear,'' he added, then with a grin lifted his loincloth and grasped his genitals, making a show of shaking them in Sreki's direction. ``Unlike some. Or did Old Eye take pity on you and show you how it works?''

There were a few appreciative chuckles at the barb.

``Enough,'' Huntleader Tal admonished him, half-heartedly.

It took all Sreki's control to continue walking; the fury was boiling within him, the lid barely holding it contained. He knew the others could scent both his rage and his embarrassment---it seeped from him, colouring everything, like the blood spreading from a kill and staining the earth below.

Fortunately, Ruha wasn't far, squatting on his haunches as he helped others skin the carcasses. His face brightened when he saw Sreki, then his ears lowered. He set his knife down and walked to meet him.

``Sreki?''

``It is nothing. Just Peshu,'' Sreki said, failing utterly at hiding his fury. He could read Ruha's face---protectiveness, vicarious anger, sympathy. ``Do not worry, Ruha. It's downstream now.''

Ruha opened his mouth, then shut it again. He beckoned Sreki over, handed him a knife, and together they carved the kill.

The fire playfully fought the night, and the tribe gathered. The choicest bits, of course, went to the hunters themselves. Peshu had taken it upon himself to portion out pieces, which Sreki dreaded, for he saw it as another obvious opportunity for Peshu to mock him. Sreki sat between Ruha and Nyota; he assumed Ruha had planned it that way. Nyota was affectionate and pressed close, which surprised him. He waited with the two shielding him, walls on either side.

And waited. It was becoming uncomfortable. Nyota and Ruha both had theirs, and Peshu had begun with the cubs. Heat rose unbidden to his face, and he could feel the press of eyes upon him. The scent of Ruha's anger flowered.

``Peshu\ldots'' Ruha said, dangerously, a viper coiled.

All innocence and bright eyes, Peshu responded. ``More? I shall get you some in but a moment. The cubs are hungry.''

Nyota's paw rested on Sreki's leg in silent sympathy and support. It did nothing to cool the flames.

``Peshu. You have forgotten Sreki,'' Ruha said, each word emphatic and clipped, like the snap of a branch.

``I was getting to him---'' Peshu began.

``Now,'' Ruha declared.

``Peshu, enough,'' sighed Tal. ``This accomplishes nothing.''

Meat was tossed dismissively into the dust in front of Sreki. Enough to insult, not enough to challenge. The green of Old Eye's eye flashed at him across the fire. It was too much. Sreki stood, slowly, aware of all eyes upon him. He reached down for his portion, turned, and left.

He had made the walk back to his hut in silence and fury, and had drawn the hide across the entrance. But that didn't stop Ruha. Sreki watched him enter, eyes smouldering in the darkness as he lay on his bed of hides.

``Ruha\ldots'' Sreki said, his voice breaking.

``Shhh,'' whispered Ruha, laying down and holding him tightly.

``Nyota doesn't---'' Sreki started.

``Nyota wanted me to come, and so did I. She worries for you too, I wish you would see that.''

``Only because you and I are so close.''

``I don't think so. I think she sees what I see,'' Ruha said.

Sreki didn't argue. He kept quiet, and let Ruha's presence calm the chaos in his mind.

Later, as Ruha mounted him, thrusting then arching his back in release, Sreki was finally able to just \emph{be}. For Ruha was here. In that \emph{now}, he savoured it as much as he could, before the chaos returned.

For the first night in many, his sleep was dreamless.

He awoke cradled in Ruha's embrace. Dawn crept nearer, threatening. He wriggled closer, his rear rubbing against Ruha. The gold ring piercing Ruha's sheath, a hunter's reward, rubbed too, a reminder of who was a hunter and who was not. Sreki grew still, and Ruha woke.

Sreki was silent as he painted the lines---the reeds, the waves, the spears. But after the final spear, he pushed aside the glint of gold and beckoned Ruha forth, to be with him once more before he left on the hunt.

\secdiv

\noindent ``Where is your focus? You are a bird, flitting from branch to branch, thinking each branch is better,'' Old Eye snapped.

Her emerald gaze held him, and Sreki dipped his muzzle once more. The flames remained unmoved, the wood uninterested, and the water, not yet boiling, yielded not a ripple. She watched as his jaw clenched tightly in concentration and frustration. Muscles corded as Sreki strained, his will palpable. Yet nothing. She remained quiet as his anger kindled, and soon he was panting with the effort.

``It's there, you know.''

Sreki stopped, his breathing heavy, and scowled over at her. ``What?''

``It's there. Just beneath the surface. A fish about to breach. I can see it, feel it. It's like you're scrabbling for something just out of reach, is it not?''

Sreki's face answered for him.

``I had the same failing,'' Old Eye continued. ``I tried so hard\ldots{} I pushed and pushed\ldots{} but there is a subtlety. A caress instead of a strike. For each person, it is different. Most have only one small pocket of it that they can never touch. Others glow brightly, the vessels almost overflowing, begging to be opened.''

Sreki's confusion was plain.

``You, like me, have\ldots{} several vessels. I see fire. I see earth. I see wind. And another perhaps? It is hard to tell, like looking down into deep water. You may even exceed me---there were six for me, but it took me ever so long to open them. Each was difficult, each was a struggle, each was different. Even now they don't come easily. But you have them there. You just need to open them.''

Sreki grimaced bitterly, the fury of failure still hot within him, and it burst forth before he could tamp it down.

``I know! You keep telling me this, but it does no good. You push and push, but it does nothing. This is foolish. I should just take my spear and hunt with the rest.''

She cuffed him, hard. Her claws slashed across his muzzle and he yelped in surprise, his anger replaced by shock. His eyes were liquid orange hurt, and the words tumbled forth, the barrier lifted.

``Don't you think I know that? Don't you think I see these\ldots{} vessels?'' Sreki cried. ``They're \emph{there}, in that cave! Pots upon pots, strangely shaped, strangely coloured, lids tight. Just \emph{sitting} there, but I can see the glow\ldots{} \emph{feel} the glow. Each one beckons me and I tug and tug at the lids and they just \emph{sit} there and mock me. Night after night! In my dreams\ldots{} every dream\ldots{} they're there, waiting. Waiting for me to fail yet again. I \emph{try}, but I don't know how, and you keep telling me things I don't understand and pushing at me and---''

``Pots?'' inquired Old Eye, too softly.

Sreki didn't notice and continued on, tears flowing unchecked down the fur of his face, mingling with the blood at his muzzle.

``And I look at that fire,'' he sobbed, waving his paw in the direction of the small cooking fire nearby. ``And I \emph{see} its pot in that cave, and I pull at its lid. But it doesn't come off! I pull at it, and the glow makes my fur stand on end and my claws itch and my paws itch and there's something heavy and strange inside me and I feel it deep behind my sheath and I'm desperate, so desperate to open it, but it refuses! And there\ldots{} the water?''

He gestured at the contents of the cooking pot, its water still.

``I see its pot too! It's small and dark, almost black, rounded like a river stone, and it has what look like jagged marks on it, they're blue, and \emph{it} won't open either! I claw at the lids, but they're stuck.''

Old Eye stared at him with vivid emerald. ``A cave?''

``Yes! It's there every night now, in my dreams. There's no opening, it should be dark, but I can see clearly. The floor is covered in sand and pawprints, but I don't know if they're my pawprints, and all sorts of pots sit there, scattered about. Each one looks different, feels different, but they all pull at me, and I pull at them and shake them and try to get my claws beneath the lids, but I cannot. It's maddening! They won't budge.''

``How many pots?'' Old Eye's query was whispered, unnaturally calm, still water before a storm. Sreki's hackles rose then, and he paused, sobered and wary.

``I don't know, maybe four or five?'' he lied, now uncertain. \emph{Two eights, maybe more?} ``Some are hidden in the shadows, and I can't quite see them properly. It's hard to walk over to them, but they're there. I can't open \emph{any} of them. I hit them, I pull at the lids, but it is as if I am a newborn cub.''

``Why didn't you mention this before?'' she asked.

His eyes still wet with tears, Sreki stared sullenly at the shaman. ``What for? They're only dreams. It's probably because I'm just angry at\ldots{} failing every time I try with the fire. Or the wood. Or water. Or anything.''

Old Eye was silent, but he could sense her anger there. He opened his muzzle to continue, but she shook her head sharply, causing her bone earrings to rattle.

``You\ldots{} ah! You young males are all the same. No elegance, no subtlety, just brute force and unchecked rage. You can't just assault every problem you come across.''

Sreki looked chastened and embarrassed, and she continued on.

``These vessels are a puzzle to solve. Not something you just beat into submission. These pots of yours have lids, yes, but they are lids with a latch. It could be as simple as that. Just find that latch, and the lid comes off. A gentle push, a slight twist in just the right place, and it could open with ease.''

``Then how do I do that?'' he asked.

``I do not know,'' admitted Old Eye. ``As I've said, it's different for everyone. All I can do is guide you until you solve those puzzles. Once you have, I can help you direct the powers you uncover, and protect you from them if they prove too much. It can be dangerous when those lids come off; I can help you manage that and master it, once they do.''

\emph{Then exactly why am I here?} Sreki directed his gaze back towards the flames and said nothing, knowing his scent told of his frustration. And more.

The shaman was quiet too, watching him. A rumble of distant thunder interjected itself into the silence that hovered between them, and she shifted slightly, her head cocked, listening.

``A storm comes. It will be a bad one. Go, this day is done.''

\secdiv

\noindent The cave with no entrance was lit by a light with no source.

He had gone back to his hut, since it was only midday, and laid down on the hides to listen to the rain and wait for the hunt to return. \emph{I must have fallen asleep.} But knowing this changed nothing; the dreamcave remained. With each night, each visit, Sreki had become more aware of it. There was a part of him, always expanding, that realised he was within a place wholly inside the confines of his mind, yet even that knowledge could not touch how real it felt.

Again, he found himself standing in its centre, the sand warm beneath his paws. His ears pricked, and realisation dawned. \emph{There's something different.} He raised his eyes to scan the interior of the cave; the various pots were scattered about, where they always were. \emph{But the sound is different. Ah\ldots{} the storm.} He could hear it outside the cave---wherever `outside' might be. It was still distant and faint, with the occasional rumble. It did not matter; inside, Sreki knew he was safe, and he switched his attention to the familiar shapes of the pots upon the sandy floor.

Nearby was the small dark pot, the rounded one with the strange, jagged markings of blue. It stood upright, nestled there between two shallow mounds of sand, and Sreki went and crouched beside it. He gave a tentative tug at the lid, but it was stuck tight. Recalling Old Eye's words, he peered more closely, but there was nothing he could see that might speak to the lid's stubbornness. He tried a gentle push, a twist, a pull in a direction one might not expect---but it remained unmoved. He glared at the cobalt markings, but they meant nothing.

\emph{Keep calm.}

Leaving the dark one for the time being, he stood and went over to the next nearest pot---a smooth, tall, burgundy amphora, almost half his height, yet its lid was as small as his paw. There were small divots in the clay, as if it had been struck with a weapon, but it seemed as solid as all the rest. He tried the lid.

\emph{Of course it doesn't budge. Why would it?}

Sreki could feel the annoyance bubbling deep down inside. He pushed the lid---it was so thin, so small, it should be easy to move! Yet, nothing. Again he lifted, twisted, pulled, and pushed, trying every direction, begging and coaxing the lid to move. He could feel the fury begin---

But no. That was what he did every time, and he was no closer.

\emph{Calm.} He let the burgeoning anger ebb away, and the choppy waves and gusting winds of his mind settled. He held the calmness there, the quiet, as if he were nestled within Ruha's arms. That outside world, with its fears and its failures, could spin and slash, but it would not reach him here. Not through Ruha.

Slowly he reached for the lid. The placid waters of his mind pushed at it, and it shifted, ever so slightly. His heart leapt, and ripples started to form, so he let the quiet suffuse him until he was calm once more. Nudging the lid, it moved again, enough for a gap.

A brightness shone through, sudden and sharp, like the glint of sunlight reflecting from a speartip.

``Sreki,'' called a voice.

The light grew brighter, and to his dismay the dreamcave dissipated, flowing away like water through his fingers.

``Sreki?'' it called again, and he sat up as the hide curtain on his hut was pushed aside. Huntleader Tal stood there.

Her face told him everything, before she even spoke another word.

\secdiv

\noindent Sreki did not remember leaving his hut. But now he was here, accompanied by the entire tribe. The wind and rain swirled, plucking at his fur, but he barely felt it. It made the lighting of the pyre that much more difficult, and Old Eye was forced to step in and coax the flames to honour the fallen.

Detachedly, he felt the press of someone against his side. \emph{Nyota}, he thought, distractedly. He could scent her grief, and that of those gathered. There was immense sorrow within him too, but it was far away. He felt eyes upon him, wondering at him, but they no longer mattered.

Sreki remained still, expressionless, unable to speak. The insistent fire-flicker impinged briefly on his vision, so he raised his head to look upon Ruha one last time, before the flames took him away. He lay peacefully, almost asleep. Someone had placed a piece of hide over the crushed half of his skull; the part of his face still visible was as pristine as Sreki remembered.

It had been an errant hoof from a kudu, Tal had said. Ruha was killed instantly.

\emph{Ruha.}

He could feel his mind start to struggle, but he couldn't, not now. He tamped it down, he plugged the leaks.

The flames had long since obscured his view of Ruha, when he felt a paw on his arm, pulling him gently away to walk back to the village proper. Numbly he let himself be led.

``What is wrong with him? Has he gone simple?'' Peshu's voice.

``Silence, you fool.'' Old Eye.

Slowly, ever so slowly, Sreki turned to look at Peshu. The bubbling in his mind began to spin. He was at the centre, unmoving, but the sorrow and fury began to trace a path around him, swirling, a whirlpool with him as the nexus, pulling it all in, faster now, gradually focusing.

``Sreki? Come, let's go,'' Nyota said gently, and he turned blankly to walk with her. She took him to his hut, and obediently he lay upon his hides. She crouched there beside him, her eyes bright with the moonlight that slipped through the half-drawn curtain, but Sreki was silent. When she laid down by his side and held him close, a remote part of him noticed, but that was all.

``Sreki\ldots{} please speak to me,'' she whispered, her voice breaking. ``I'm alone too.''

He heard the words, but they came from far away. A conversation for someone else, not him. The words became tears, and he knew there was a part of him that wished her to stay, wished he could do something, but that part was shut away, buried deep within.

So Sreki neither spoke nor moved, only stared up at the roof of his hut, and eventually Nyota left and pulled the curtain closed.

He was alone. \emph{Ruha.}

\secdiv

\noindent The sand was warm beneath his paws.

It was louder now. The storm outside the cave was intense; the chaos of winds, the thunder and lashing of rain, the distant crack of branches as the gale swept over the land. But Sreki barely heard, as the whirl inside him grew.

Gradually the howl of the storm increased, whether the one within him or the one outside, Sreki could not tell, but he could feel his fur start to stand on end. A sharp crack and resounding thud made him jump, bringing him back to his surroundings, and a fine breath of stone dust fell from the cave's ceiling. With it came the familiar pull---a pull against the reality he was experiencing.

\emph{No, the dream needs to stay! I know I can open one! I was so close before\ldots{}}

Yet the calmness he had found before was lost, unattainable now. It lay beyond his reach, in Ruha's embrace.

He rushed over to a pot near one of the walls, stumbling briefly in his hurry. It was almost spherical, made of obsidian, with a lid that fit so closely and seamlessly it was almost invisible. Three parallel furrows were carved down it on one side, like the gouging of a huge beast's claws. Its glossy surface was hot to the touch, and he was convinced he could feel it thrum, ever so slightly. But its lid was as stubborn as the rest, refusing to yield to all of his desperate scrabblings.

\emph{Gods, open, curse you! If you had opened before, perhaps I could have gone on the hunt with Ruha! Perhaps I could have saved him!}

Frantically, he turned his attention to an asymmetrical pot of rich red ochre, leaning angled against the nearby wall. Elegant stripes of wood engraved with curved glyphs were embedded around its surface, and Sreki raced over to tug at its lid. It looked to not fit properly to begin with, it should only take a simple push! But it resisted, and his anger opened up bright-hot within him. He tore at the lid and it mocked him. The vortex within him drifted ever closer to its center, and something shifted inside him and he lost himself to the rage, hurling his fury at the pot even as the storm hurled its fury at the earth beneath. There was another sudden crack of fissured stone and a cloud of crumbled rock and dust fell from above, but he barely noticed. Reality stretched as the cave's ceiling opened to the sky and the lightning and the rain and the wind, and the whirl inside him grew brighter and smaller until it was nothing but an impossibly intense point. And everything went white.

\secdiv

\noindent Sreki awoke.

He was prone, face-down in the dirt just outside the entrance to his hut. It was dark and noiseless, the night sky brilliant with too many stars and untouched by clouds. \emph{The storm must have passed.} He staggered slowly to his feet and wiped the blood from his nose, the pots still sharp in his mind.

\emph{The cave. It opened.}

The realisation energised him, and he knew where he must go.

Shakily, he headed towards the hills abutting the village. The stars above him were wrong, and the hills themselves looked odd and too close, not the right shape, but the path that led him gradually upslope was familiar. Ahead the hills merged, coming together to form a craggy boundary that bordered his village opposite the river Pindipindi. The simple footing of the hard-packed dirt gave way to more rocky terrain, dotted with jutting stones and storm-broken branches. It looked slightly different, slightly wrong, slightly askew, like the path was not exactly as he remembered, but he was too focused on his destination to notice. The smell of wet air, damp leaves, singed wood, and the underlying smell of iron pushed at his muzzle---yet it was another, different sense that pulled him unerringly upwards. The pull grew irresistibly stronger, and his heart leapt at the unfamiliar silhouette of the stones ahead. Lightning-smell and the spicy scent of scorched rock touched him then, and he slowed to a stop in front of the fresh wound in the earth. It was a narrow fissure, more of a tear than a split, and Sreki quickly dropped to his haunches to peer over its lip.

It was strangely lit, a sourceless light that felt out of place, but he was too enthralled at the discovery to care. For there, in the dimness beneath, were the telltale curves of pots---many pots---\emph{the} pots---and Sreki wasted no time in wriggling his way through the opening. Sharp edges of newly fractured rock caught at his flesh, leaving red furrows in his fur, but he hardly noticed. He dropped down, landing crouched and silent in the soft sand of the cave from his dreams.

\emph{They're all here\ldots{} every last one of them.}

His panting breaths and thudding of his heart were loud in his ears as he slowly turned, gazing at all the pots just waiting to be opened.

There it was: that small dark one, the one with the jagged blue markings, exactly as he remembered. He moved towards it, resting a shaking paw on its lid. He held his breath and twisted; he felt it shift, and the lid toppled to the sand. His eyes could not see the blinding brilliance within, but his mind could, and the rush of it was a wind that filled his head, a gust of intense cold that burst open doors that he only just realised were there, blowing down the passageways beyond, and he felt his mind stretch with it.

He staggered back, shuddering, unable to process the new paths, the new way things now were, but exhilarated nonetheless. Gasping, he reached for the second pot, the tall burgundy one, and with a simple flick of a claw its tiny lid slid clear, and windows opened within him in a noiseless roar.

Torrents flooded his mind. It was as if the rains had come and swelled the rivers to bursting, and they overflowed their banks, making new paths. But floodwaters push everything else aside---any small blockade of trees or bushes gets shoved aside and away, and the water strengthens until it makes its own paths unrelentingly.

Of course, the stone---his stone---that was Ruha, that anchor, that safe haven he could cling to as the currents in his head grew wild\ldots{} Ruha was gone, and the river flowed unchecked.

It was so simple. All of it was. \emph{I must be careful,} some other part of him thought. Yet they were all here, they had been waiting for him all this time, for so long. And he knew how they opened. Even the ones in the darker recesses of the cave---he knew how to open those too. \emph{Just one more\ldots{}}

He flung the obsidian lid aside, and lightning and thunder broke the cave around him.

\secdiv

\noindent Sreki awoke, crumpled by his hut, blood pooled around his muzzle. He was in the same place where he had awoken earlier, just outside its entrance. The storm was full force around him, a violent swirl of rain and wind, and it took him several moments to get his bearings. The storm did not touch him, yet he could see distant trees being torn and broken by it. He had heard of these storms before, strange circular ones, the most dangerous, with the eye of safety within them. \emph{If I just keep within the eye\ldots{}}

\emph{The cave!}

Panicked, he looked towards the trail up the hillside\ldots{} but there was no need. His doors were still open, and the cave was there within him. Each pot was there, and the three he had opened poured their brilliance through him. He stumbled with the force of it. Deftly he slid the obsidian lid back on. It clamped snugly to its pot, and Sreki could think again. The rush of the other two still flowed, but he could handle it now.

\emph{Old Eye, I must show Old Eye.}

And then: \emph{Oh, Ruha. I wish I could show you too.}

He staggered towards the village centre, following the storm's eye as it roiled about him, absently wiping at the fresh blood that dripped from his muzzle.

Ahead, as the storm's front continued to move, he saw the torches in the village flicker out and the panicked forms of his hyena tribemates desperately making for their huts, only to be dragged sliding across the ground by the intensity of the gale. Sreki yelled at them to take cover, but they were too slow---one by one the storm hurled them aside, breaking them on the trees and rocks, the sickening crunch of each impact cutting short the terrified screams. Briefly he saw Peshu look his way, horror on his face, before he was simply torn in half.

\emph{Old Eye, I must get to her!}

Her hut was straight ahead, and he could barely make out her form at its entrance. Around her stones and trees and bodies hurtled by, yet she stood untouched, straining against it. She looked at Sreki then, her emerald eye locking onto him, and her face was full of shock and fear.

``What have you done?'' She did not shout it, yet he could still hear it above the deafening storm.

``I can open them, Old Eye!'' He pulled off the obsidian lid, and as it roared through his mind, he showed her what he could now do.

The bright green fire of her gaze slammed into him then, and he stumbled as the first two pots---the small dark one and the tall slender one---were immediately stoppered, their lids tight. He tore desperately at them, but they would not reopen. A detached part of his mind realised the storm had suddenly ceased, and all was quiet except the plaintive cries of hyenas broken around him---but the lids, they wouldn't budge.

\emph{They won't open!}

He slowly looked up at Old Eye, and she quailed at the absolute fury in his face.

\emph{The others will, though.}

He reached, and three other lids came away easily, one by one falling to the sand around him. Old Eye's emerald flame stretched towards him, seeking to silence the beauty of what he now held, and one by one, smothered by green radiance, the lids shut tight. Doors slammed closed in his mind, and he ached with the loss of the barely glimpsed wonders beyond. He cried out and in desperation sought out more---the shadowed pots, there in the far corner. They were barely visible in the dark alcoves of his cave, ancient and covered in dust.

A strange pot, weirdly shaped, greasy and mud-coloured---its lid dislodged, and the world tilted.

One of vivid blue, oddly sharp and sticky to his paws---the lid flew off, and new doors opened even as Old Eye barred others.

And a weatherbeaten wooden pot, simple and unassuming, knotted and burled. It yielded its contents with a satisfying click of its lid. When he saw what was within, he knew that she could not---\emph{must} not---know of it. Its brightness tore through him, twisting, warping, but it was too much, too fast.

Something broke in him then, a soundless snap in his mind.

In silence and utter fury he lashed out, and Old Eye's green fire was quenched, shattered into thousands of shards, its light snuffed. He strained at the many shuttered pots, but they refused him.

\emph{Why can't I open them? What did she do?}

Finally, he noticed the quiet, punctuated by occasional cries of anguish. Sreki opened his other eyes.

He stood alone, in the centre of the village. Blood drenched the earth at his paws, and unrecognisable lumps of what must once have been Old Eye were scattered far and wide. The village blurred before him, and his wounded tribemates looked upon him aghast, yelling things he didn't comprehend. He struggled to understand what he was seeing, his vision split between the cave---\emph{his} cave---and the world around him.

``Ruha?'' Sreki whimpered.

A flung spear grazed him, a hot line across his ribs, and awareness, realisation, and horror all jolted into focus.

Sreki slipped briefly on the crimson stains that were all that was left of Old Eye as he turned and bolted for the river. Those that were able charged after him; he could see each one with blinding detail, and he shut the new eyes in his mind so that he could focus on the river ahead.

He stopped then, at its banks. He reached inside himself and drew the path he desired, and wide Pindipindi let him cross. He paused and opened all his eyes. His tribemates clamoured on the far shore, screaming words that held no meaning. The agony was too much. He closed those eyes, turning away from the river, and the savanna stretched out to embrace him.

