The wind rustled through dry savannah grass under a hazy morning sun. Akachi's ears swiveled forward and stiffened with determination as he saw a lion in the distance. A younger lion---the painted wolf guessed---probably a hunter from the large bow she carried.

His paw tightened around his atlatl and he crouched low in the tall grass. Another hunter who had stepped too far. He turned and slowly made his way towards the shade of a broad acacia tree.

The Great War between their peoples was over, but his atlatl was carved out of a lion's thigh bone. He wasn't done fighting. The lion clans, safe behind the walls of their sprawling cities, were ever reaching out their claws to steal more territory. Everything they saw they claimed as theirs. No tribe, no people could stand alone against them, but he had to try. As long as he lived, there would be hope.

Akachi exhaled, reminding himself to focus. He keep his eyes on the lion while his ears turned to either side, listening to make sure she was alone. Then his foot slipped into a hole and he stumbled. The lion's ears twitched towards him and she pulled out an arrow from the quiver on her hip.

The painted wolf froze. He wasn't ready. Nocking one of his long darts to his atlatl would give away his position. He bit back a curse. She was sniffing. He was upwind, but the wind could change at any moment.

This was not something he could solve with skill, but he was reluctant to ask the spirits for their help. The pouch on his belt only held three lily petals. They were precious and he had no way to harvest more. For a moment, his heart despaired; they may be the last he'd ever have.

Even so, his life was worth more than any petal. He pulled one out and crushed it between his paw pads, whispering a gentle song as his offering.

For a moment, nothing happened. Then blue dragonfly-shaped lily spirits came to flutter around him, hiding him. Where his ears had been, there was nothing more than grass blowing in the wind. It wasn't much, but it was enough.

If he had been blessed, they would have done more. During the war, a single flower held in the paws by a priest of lilies would have summoned cold, malicious mists that rose from the earth as far as he could see. He had done it once, long ago, but those days had past and Monsoon was not so gifting to her priests.

He reached the tree and nocked a long dart---one of three his brother had prepared---to the spur of his atlatl. The flint head, two arm-lengths in front of him, was covered in a sticky black paste. The dart's white feather fletching rippled in the wind.

The painted wolf took a deep breath and placed his feet. The atlatl was almost cold in his paw as he held it up. A sudden gust swirled around him and a strand of wind brushed his ear, whispering---seventy-three paces.

Then the winds stopped, as if holding their breath.

Akachi felt pity. The lion stood there in front of him. She was not a warrior. She had never fought one of the Avoniya---nor a priest of Monsoon. The demons from the mists were nothing but stories to frighten children. If she heeded them, she would have dropped prone at the first sight of a black ear or the sudden stilling of the wind.

Now, she would know; then she would die.

Akachi stepped forward, turning his body and swinging his arm---driving the dart forward. Then he snapped his wrist to complete the throw.

The dart flew true and buried its flint head low and deep into her belly, just inside the joint of her hip.

She screamed and dropped to the ground.

The painted wolf knelt beside the tree, waiting. It didn't take long for the lion to stand up, highlighting her form against the clouds. He huffed out through his nose. Pity gave way to contempt. She was as foolish as she was young. Contempt turned to hate in his heart; not at her, but what she stood for---the ignorance and arrogance of her kind.

Then he felt shame.

He knew better. Nature was harsh and unforgiving, but not vengeful. All life was sacred and his duties as a priest came before those of a warrior. He closed his eyes and took a deep breath, then he pulled out his dagger.

Akachi stood up and left the shade of the tree. He waded through the grass, trusting the spirits to hide him. When she fell, he would be there.

The lion broke off the haft of the dart and staggered a cluster of trees. Akachi walked forward as her cries for help became weaker. Slowly, the poison seeped through her. Her left leg was the first limb to become rigid. She fell, but could no longer draw the breath to scream.

When he reached her, she was writhing on the ground, back arched as every muscle pulled tight---no longer able to fight. If he did nothing, the poison would take hours.

He knelt beside her and grasped her ear, turning her head so she could see his face. In her eyes, he could see the terror and the pain. He hope she could see there was no longer any malice in his.

Gently, in her own tongue, he whispered, ``may we find peace when we meet again.''

With a single cut, the lily spirits flew away, abhorring the taking of a life.

The painted wolf closed her empty eyes and said the prayers that would guide her soul to the world beyond the veil, but he could not bring himself to continue. He stayed beside her, repeating the prayers under his breath; her blood staining his fur and loincloth.

Eventually a vulture croaked overhead and he looked up. Three of the sacred birds waited---impatient. The painted wolf picked up his knife. He would fulfill his duties to Monsoon and then let her winged servants take care of the rest.

\secdiv

\noindent Hours later, with the sun high in the sky, Akachi returned to the valley with a pelt over his shoulder and his darts in a paw. Each step felt heavier than the last. He reached the stone path and walked past three jackals standing guard on the wall protecting the entrance to the valley. They looked up from whatever game they had been playing to thump their clenched fists against their chests in respect and he thumped his chest in return but didn't wag his tail like he usually did.

Where the well-trodden path came down beside the river, the welcoming scent of clean water and wildflowers surrounded him. Despite the heaviness of his heart, it sang when a lily spirit brushed against his muzzle. Even stained with death, lilies had welcomed him; he was home.

He dropped off the lion's pelt at the tanner's hut and continued down the road and trees gave way to past broad fields with round mud houses. A few jackals looked up from their work to thump their chests in respect as the guards had and he returned the gesture with his now free paw.

It was good to be back. Thousands of jackals lived in the valley and everywhere he looked, they prospered. Even the poorest family had a field they called their own.

On the far side of the valley, at the end of the stone road was a towering red mesa with a village carved into it, but it wasn't just a village and a home; it was a fortress. Each of the four tiers were carved deep into the rock, with only narrow steps connecting the increasingly higher and smaller levels. On the third tier, deep caves held enough grain for three years and sheltered a spring with cold, clear water. It would be an extravagance, if not for the grasping claws of the lion clans. These walls were all that stood against the further enslavement of their kind.

After he reached the first set of narrow steps, he was greeted with a course of yips from the six jackals standing behind a wooden palisade. When he got to the top, they set their large wicker shields and short spears aside and ran over, tails wagging.

The painted wolf knelt to avoid leaning over them and nuzzled their jaws in the traditional greeting of his own people. Jackals were less effusive towards their packmates than the Avoniya, but for him, they returned his affection with equal enthusiasm.

After exchanging licks and wags with everyone, he lingered over Okori. The jackal tilted his head so they could kiss muzzle to muzzle. Their tongues intertwined for one slow exhaled breath before they separated.

``See you tonight?'' Akachi asked.

``Ye---'' The jackal's tail froze before he could finish speaking, then he ran back to his post.

Akachi turned around to see an elderly jackal wearing a heavy necklace of clacking lapis stones striding angrily towards him. The guards had turned their attention back to the valley and kept their ears forward. The painted wolf stood up to his full height, towering above the jackal. Someone must have told Tahir about the pelt he dropped off. His hackles rose.

``What are you doing!'' Tahir whispered harshly. ``You'll bring the clans down on us. Is it not enough for you that we already deliver tribute, so they do not come into the mountains?''

``We've had this argument,'' Akachi growled---not caring who could hear him. ``You paid twice this year what you did last. How long until you can no longer pay? Besides, this one---'' he pointed towards the far end of the valley ``---was not three hours walk away.''

They stared at each other until the jackal snapped his jaw shut, huffed out his nose, and pointedly walked away towards the large house carved into the stone beneath the second level.

Beating the elder with his own gaudy necklace would be counter-productive, but that didn't stop the painted wolf from imagining it. The jackal's arrogant naivety was infuriating.

After Tahir was out of sight, Akachi turned towards the stairs to the second level.

\secdiv

\noindent As he slowly climbed and stepped around the smaller jackals, he reflected on the past. Tahir was one of the few elders left who had reservations about him, but it hadn't always been that way.

All of the elders had been hesitant to accept him and his brother at first. He couldn't blame them. The ways of the Avoniya where not theirs, but village had been desperate to find a shaman; they had no one who could train others in the way of the spirits. His brother---Chima---freely offered all he had despite his lame leg.

Over the years, suspicion lessened and friendship grew. Friendship had become family---even for Tahir, who would vehemently deny it. Akachi smiled in memory of the week before when the jackal had done just that.

\secdiv

\noindent On end of the fourth level, the furthest point from the stairs, the painted wolves had been given a generously proportion three-room dwelling carved into the mesa. It was a long, distant walk from where all of the elders lived on the first level. Akachi smiled as he heard the mournful drone of his brother's flute. The breeze and shade made the highest levels of the village almost comfortable in the afternoon heat of a late dry-season day.

Chima sat on a golden pelt over a pillow stuffed with straw. His left knee didn't bend completely, so his foot rested on a low wooden stool. He set his flute down as Akachi approached.

``The lilies don't like when you do that,'' Chima commented, wiping his paws on his loincloth.

``I know,'' Akachi said quietly. ``I'm a priest of Monsoon. They understand.''

``Understanding or not---'' His brother looked down and folded his ears back. ``That's a lot of blood.''

``Yes it is,'' Akachi said tiredly and walked into their house.

The painted wolf leaned his darts up against the corner of the wall and set his belt and loincloth next to them before stepping into Chima's workroom to wash. The other painted wolf limped in behind him and leaned against the whitewashed stone.

``You didn't bathe before coming back?''

Akachi didn't reply as he dipped a cloth into a large bowl of water and started scrubbing his head with it. His ears hung off his head. Finally he spoke.``Why are you up here so early?''

``I never went down,'' his brother said evenly.

``Why? Is your leg bothering you?''

``No more than usual.'' Chima turned to look out past the balcony. The blue sky was nearly cloudless. ``Begu came up and we did some reading. He left a couple of scrolls if you want to practice.'' The painted wolf grinned and pointed at the shelf above the work table.

``I have too many things to do to spend my time learning to read and you're not going to get me anywhere near a stylus, unless you add some fletching to it.'' Akachi remarked, grasping for something to talk about---anything except the blood. ``Did you eat?''

``Naqua brought me some of the fruit bread she made yesterday.'' Chima folded his ears back. ``You ready to talk?''

Akachi's ears sagged and almost a minute passed in silence before he spoke. ``I'm losing it''

His brother's ears turned attentively forward.

``She was strong enough to use a hunter's bow but too young to pay attention. Caught a glimpse of me.'' Akachi inhaled deeply. ``And just stood there. Stood there like startled prey.''

``Well, that makes for an easy kill.'' Chima frowned.

``I hated her, Chima. ``Akachi choked on his words. ``Hated what she stood for. Wanted revenge for all the clans have done.''

Chima's eyes widened and his ears pinned back. ``Please tell me you didn't\ldots''

``I didn't. It was a long throw and I missed her heart. I only waited for the poison to work before giving her a quick death.'' Akachi picked up the cloth to start cleaning his legs. ``Looked her in the eye; said the prayers; took her pelt; all the things I'm supposed to do.'' He sniffed. ``I waited for Monsoon to claim her before offering the flesh and bone.''

``That\ldots{} was not wise,'' Chima said softly. Then he flicked his ears. ``Sorry. You know that.''

``It's just too much. So much death. I know I'm supposed to kill people, but the balance is slipping away from me.'' Akachi set the cloth aside. ``I need the lilies.''

Chima nodded and frowned. ``There isn't much I can do as a shaman, they need a priest.''

``I know,'' Akachi replied waving his paw towards the broad valley. ``But there is only us. There's no way to get anyone from Lavotabar to live here.'' He stepped out on to the balcony and stared out. ``They still blame us for the lions killing our family.''

His brother said nothing. There was nothing more to say.

The rains were coming. If all had gone well, they would flood the valley and the lilies they worked so hard to plant would bloom. For a time, the swollen river would have become a sea of blue flowers. With a faithful priest of lilies, no person with ill-intent could find the valley through the mists protecting it.

But now, the seeds would rot without a gentle priest of lilies to coax them to life. In a few years, the clans would stake their claim on the valley and any jackals who remained would become their slaves. What happened to him afterwards would be of no consequence.

``I don't have any lily petals left,'' Chima said. ``But I do have some lavender.''

``If that's all you have.'' Akachi sighed. ``At least the rest of the spirits haven't forsaken us.''

``Yet,'' The other painted wolf replied with a slight smile. ``We can call some spirits at twilight. Maybe a blessing will help.''

``I asked Okori to come tonight.''

``We can include him. Jackals and lavender have some understanding.'' Chima grinned. ``Less stuck up than lilies.''

\secdiv

\noindent The sun was low in the sky when Okori arrived with a clay pot. The young jackal's tail wagged as he walked in without announcing himself.

The painted wolves were still on the balcony but had moved to sitting tailor-fashion on a soft, yellow pelt, an empty pot of stew and a frame drum between them.

``Brought some embers like you asked,'' Okori said and sat across from them.

Akachi gave the jackal a tired smile and nuzzled him. ``Glad to have you here.''

Chima ruffled the fur on the jackal's head. ``Hope you don't mind having me around tonight.''

``Uh---sure. You haven't invited me up for a ritual before.'' The jackal's ears folded back. ``Is there going to be a lot of blood?''

``Not all Avoniya rituals involve blood,'' Chima said dryly.

Akachi coughed and looked away.

``Okay, most of \emph{mine} don't.'' Chima looked pointedly at his brother before turning back to Okori. ``Hand me the embers and we can get started.''

The painted wolf slid himself to the edge of the pelt and settled the pot in front of him. He removed the lid and stirred up the embers. Akachi stood up to retrieve a copper pot of water and a small bundle from the workshop.

Soon, the water was boiling, filling the air with the scent of lavender. Chima divided the tea between three small cups before picking up his drum.

``Mind if I sing?'' Akachi asked.

``That would be best,'' Chima said as he started a simple repeating beat. ``You're the one asking for guidance.''

``What do you want me to do?'' Okori asked.

``Watch and drink the tea,'' Akachi said quietly. ``If you can meditate, it would help.''

``I'll try.''

``Try closing your eyes and listening,'' Chima added.

Akachi cleared his throat and took a sip of tea. Then he started singing. His voice was an octave higher in his native tongue and the words of his childhood flowed smoothly from his muzzle; the Avoniya language lacked the harsher tones and stops of the jackal's language. Okori sat, mesmerized.

The sun slid below the mountains, leaving a cloudless purple sky. The brightest stars were becoming visible.

A single ghostly moth appeared. Chima stopped drumming to sip tea. Another moth appeared. Then a swirling cloud of them descended on the balcony.

Akachi let his song fade and started reciting an ancient poem. Translucent wings fluttered. Chima tapped the edge of his drum.

The moths vibrated and then vanished in a cloud of petals. Akachi whispered his thanks, with tears sliding down his muzzle.

Okori was the first one to break the somber exhale of the rite. ``That was amazing.''

``It was,'' Akachi agreed as he rubbed his eyes. His voice was stronger and steadier than it had been.

``How do you feel?'' Chima asked the jackal.

``Like I just woke up.''

``Then it worked.'' Chima smiled and drank the last of his tea. ``You two have fun; I'm going upstairs.''

Akachi nuzzled his brother before the other painted wolf got up. ``Thank you.''

``Any time.''

\secdiv

\noindent Late the next morning, Akachi sat on the stone edge of the balcony, watching the jackals tending the fields. On the first level, there were shouts and grunts as the town guard trained. The sounds were too distance for him to pick out Okra's voice among them.

The painted wolf looked over as his brother walked out to sit next to him.

``How do you feel?'' Chima asked.

``Amazing. We should have ask the lavender spirits a long time ago,'' Akachi said.

``That would have been a bad idea.''

Akachi folded his ears back. ``Why?''

``It would have pissed off the lilies.'' Chima tilted his head. ``How could you forget that?''

The painted wolf scratched behind an ear. ``The lily rituals seem like a lifetime ago.''

``Five rains---or was it six?''

``Weren't you just past your rite of passage?'' Akachi said.

``Yeah,'' Chima said, staring off into the distance. Then his ears flicked. ``Speaking of that, you're a priest of Monsoon.''

Akachi blinked and stared at his brother. ``How \emph{you} forget \emph{that}?''

The other painted wolf ignored the comment.

``When you became a priest of lilies, Weyrn took you as her consort.''

``Yes?'' Akachi replied hesitantly. ``That didn't exactly go well.''

``That happened later. Do you remember the coronation ritual? Enough to do it?''

Akachi tilted his head, remembering. When a priest of Monsoon took a consort, they usually would become the tribe's priest of lilies. Usually male and female respectively, though reversed or same gender pairings weren't unknown. The ritual of rebirth at the end of the rains had no requirement for the coupling to produce pups.

``Is there any reason you can't take a jackal as a consort?'' Chima asked, interrupting his brother's thoughts.

``And you're talking about \emph{me} pissing off the \emph{lilies}? The consequences of pissing off Monsoon\ldots'' Akachi pinned his ears back and smacked his tail against the stone. ``Well, that would solve most of our problems.''

Chima ignored the jab. ``Does the coronation ritual do anything transformative?''

Akachi's ears relaxed. ``It's a minor summoning that merges a lily spirit and part of the priest's soul into the consort. Why?''

``That probably counts.'' Chima tapped his flute against his muzzle and looked at his brother. ``Any reason we can't change a jackal into an Avoniya?''

Akachi felt the blood drain from his ears. He curled his tail around his waist. ``You want me to summon Monsoon herself, out of season?'' Akachi swallowed. ``Even if I had a coven to work with, and the appropriate sacrifices, we'd risk destroying the entire valley and the mountains around us! We have rituals for a reason. Monsoon is not forgiving.''

``So it's possible?'' Chima pressed.

``Did I mention destroying the entire valley in the process?''

``Would you rather the lion clans do that in a year or two?''

Akachi buried his head in his paws. ``No.''

``Just think about how much Tahir is going to be screaming.'' Chima grinned.

``This idea is insane and the rest of the elders are going to throw us out of the village.''

``Good.'' Chima brought the flute to his lips again. ``I'll start making paints. And you should practice your sophistry.''

``My what?''

\secdiv

\noindent ``Absolutely not!'' Tahir shouted. His lapis necklace rattled with his fury.

There was only the faint red light from the stones glowing in the brass bowl in the center of the circular room. Akachi's white markings stood out from his nearly invisible markings of orange and black. He hoped no one could see his ears pinned back.

``I would like to hear him speak,'' Awiti said calmly.

Awiti was one of the newest members of the council but, as a spearmaster, she had considerable influence among many of the younger jackals. In addition, she was also one of the few in the village who could commune with spirits as Chima did.

A general rumble of agreement rose from the other elders. No one else supported the eldest jackal's objection.

``Continue,'' Awiti prompted.

Akachi laid out his plan to find a suitable jackal in the tribe who was willing to take the risk. He downplayed the possible consequences of a failed summoning. The floods would prevent a second harvest this season. Everyone should be safe enough in their homes for the few hours he needed. The risk was manageable for the possible benefit of hiding the valley from would be invaders.

The arguments continued deep into the night. In the end, Tahir was outvoted by the other elders and Akachi breathed a sigh of relief. But when he left the council chamber, Awiti came out to stand beside him.

``Would you walk with me?'' She asked. ``I would like to see where the flooding will be worst.''

With the moonless, overcast sky, it was far too dark to see much in the valley. The painted wolf agreed and followed her down the steps and onto the stone-paved road. When no one else could overhear them, the jackal clasped her paws behind her back.

``You haven't been fully honest with us.''

Akachi didn't reply.

``And furthermore, not everyone will approve of you taking a man as a consort,'' Awiti said evenly.

``Oh?''

``Everyone knows of your dalliances with the younger men,'' Awiti snorted. ``It is inappropriate. Boys fucking boys is a thing puppies do when they are still exploring the world and themselves. Not a proper thing for a man to do when he grows up and knows who he is.''

``Then why hasn't anyone objected?'' Akachi asked.

``You're a warrior and a priest, which is rare in these lands,'' Awiti turned towards him. ``And I have seen the spirits that surround you. You wield great magics. For that alone, even Tahir is willing to forgive many of the flaws you might have.''

``I see.''

``I don't think you do,'' She said reasonably. ``People are swayed by power. Your power is such that people ignore that you murder lions and attract men to yourself. And tonight, you used your influence to ends that we don't fully understand, for promises we trust are not empty. I see this but I fear the others don't.''

Akachi rested a paw on the jackal's shoulder and looked into her eyes. His voice was barely above a whisper. ``If you don't approve of me, why did you back me in the council?''

``I trust you, and they trust me,'' Awiti replied, ``but I want honest answers before you do this thing.''

``What would you like to know?''

``I want to know which one of our men you are going to take. Then you're going to tell me the truth about this ritual.''

``Okori,'' Akachi said quietly. ``We are close and he is one of many warriors. The village can afford to lose him.''

The jackal crossed her arms. ``He is young and will do anything you ask, simply because you ask it of him.''

``I know,'' Akachi agreed, his ears pinned back. ``Chima and I will make sure he knows the risks. Say what you will about other people over-looking my flaws, I am not a monster who sacrifices his family for a spirit's blessing.''

``And what about the lion pelts you collect?'' The jackal's tone was sour.

``The Avoniya have always done so. We take those who stray into the mists and offer their bodies to Monsoon, she leaves us their pelts in return. Our shamans and priests have many uses for them.''

Awiti huffed out her nose and furrowed her brows. ``That's not much of an answer.''

``Did you want me to explain the rituals? They aren't secret.''

She frowned for a moment. ``I think I'm happier not knowing.''

Akachi shrugged.

Awiti turned to continue walking down the road. ``So tell me the true risks of this ritual.''

\secdiv

\noindent Again, Akachi followed the drone of his brother's flute across the village's highest level. His ears relaxed at the sight of a small flame flickering from the oil lamp in the workshop.

``How did it go?'' Chima asked.

``They agreed.''

``That easily?''

``Not quite.'' Akachi sat on the bench beside his brother. ``Awiti twisted Tahir's arm and no one else knows what to do about the lion clans.''

``Literally twisted his arm?''

``I wish,'' Akachi said with a shake of his head. ``After the meeting, she followed me out.'' He sighed. ``I told her how bad it could go.''

``And?''

``She trusts me.'' The painted wolf's tail flicked. ``And she's worried for Okori.''

``I figured you would choose him.''

``He wasn't my first choice.''

Chima looked down and folded his ears back. ``I know. He's young.'' Chima looked up. ``But so were you.''

``I was.'' Akachi scratched behind an ear. ``Any ideas how we're going to do this? I know too much and keep worrying I'll get it wrong.''

Chima leaded back against the wall. ``As a shaman, I know most of the stories. In some of them Monsoon is pleased by a warrior's audacity to stand against her.''

``There's a very thin and deadly line between audacity and disrespect.'' Akachi's ears folded back and he stared at his brother. ``Just how many of those stories don't end badly?''

``Two or three.'' Chima rubbed his chin. ``\,''No, it's definitely three.''

``Not exactly a promising solution.''

``More than you think. We are Avoniya---the 'People of the Lily'. Lilies don't grovel. Futhermore, if we want her greatest magics, we should demand it. Monsoon isn't going to respect to anyone who whines like a hungry pup.''

Akachi's tail flicked. ``You make it sound simple.''

``It is.'' Chima placed his fingers on his flute. ``Besides, I already made war paint and I'd hate for that to go to waste.''

\secdiv

\noindent Three days later, the sun rose and painted the sky a bright, ominous red. Even though the rains were months away, dark blue clouds grew to the south. Furious lightning strikes flashed a blinding white. Distant thunder rumbled and Akachi's tail flicked nervously back and forth as he watched from the balcony. The scent of rain was heavy in the air and the hot, wet wind washed over his unclothed body.

``Weather looks promising.'' Chima said, handing over a necklace of loin teeth.

The painted wolf took the necklace. There was not a spirit in sight and most of the jackals in the valley had taken shelter in their huts. Akachi inhaled, tasting the wind.

Okori came up to rest on the low stone wall of the balcony, equally undressed as the other two. ``How long do we need to wait?'' The jackal asked.

``Not long.'' Akachi replied and turned to face the open room behind him. A straw mat had been laid on the floor and covered with a white pelt edged with tassels of small bone beads. Chima had brushed it smooth and sprinkled lily water over it. The droplets seemed to glow against the white fur.

Akachi folded his ears down and covered his eyes as he felt his fur prickle. A resounding crack shattered the air as lightning struck the prayers Chima had painted in blood on the stone path. In its wake, the symbols below glowed blue and their light did not fade as more thunder rumbled in the distance.

``Spirits.'' Chima blinked and worked his jaw. ``That was close.''

Okori shook his head to clear the ringing from his ears.

``Monsoon,'' Akachi whispered and his tail stilled, its end puffy with his fear.

``Well, the path is still there.'' The jackal said nervously as he leaned over the stone wall, looking down. ``That's good, right?''

``It's not bad,'' Chima replied before turning to his brother. ``Anything else?''

The winds swirled and twisted before them and Akachi's ears perked, listening for whispers only he could hear. He inhaled sharply. ``She's here.''

His brother gulped. ``And?''

Akachi sniffed the wind and his breath caught in his throat. ``She will spare the village,'' the painted wolf croaked.

Okori's ears shot up. ``It's working?''

Akachi nodded.

``You ready for the paints?'' Chima asked.

Akachi took a deep breath and stepped towards the work room. ``Yes, paints.''

In the relative shelter of the work room, Chima and Okori stuck their fingers into a jar of turquoise paint. The painted wolf started drawing forked lines of lightning strikes and the jackal carefully brushed teardrops of rain on the black splatches of the other painted wolf's fur. It was not a pattern the either of the painted wolves had done before.

``I wish one of us was better at making up songs,'' Chima said. ``I could use one right now.''

``The whole point was to avoid tradition,'' Akachi said over his shoulder.

``I could sing something.'' The painted wolves looked at the jackal and Okori's ears folded back. ``Or I could just be quiet.''

Akachi nosed Okori's muzzle. ``You're doing fine. Just do everything as we planned.''

``Okay.''

A few minutes later Chima clapped his paws and handled Okori an oiled rag. The paint had dried into a sticky film that stubbornly clung to paw pads and fur.

``What kind of paint is this?'' The jackal asked, ears perked back up.

``Huki,'' the shaman said, heading back into the workshop. ``It's a plant resin mixed with crushed rock. It dries pretty fast once you take the lid off.''

``What is it used for?''

``We paint ourselves with it before going into battle.'' Akachi said.

``Wouldn't you use blood for that?'' The jackal asked.

``Well, like my brother said, not every ritual uses blood. We mostly use blood for rituals of offering. Huki is used for blessings.''

``Right.''

Chima returned with three small, stacked pots holding the rest of the paints---black, white, and orange. He handed the black to his brother. Then thunder echoed across the valley and the shaman's ears flattened.

``Let's make this quick.''

Akachi nodded and dipped three fingers into the white paint. They hurried to finish the jackal's new colors. In the distance rain began to fall, while the lightning cracked and thunder boomed a heartbeat apart.

``Done.'' Chima shouted. ``Don't keep Monsoon waiting!''

Akachi took a quick breath and stepped out onto the slick, wet stone of the balcony. The painted wolf forced himself to keep his ears forward and tail still.

Standing in the rain made him feel small, but he imagined himself as a lily in a storm---petals fluttering, but not breaking. He looked up into the torrent, refusing to blink against the crashing drops stinging his eyes.

``\emph{Monsoon!}'' He yelled with all his might. Lightning flashed, making his fur prickle.

``I have hunted my enemies in your name.''The wind whipped around him but he stood his ground. ``I have given your servants their share while I have taken my due. There is not one kill I haven't given you respect.''

Was he glowing?

``Every rain, my knees quaked in awe of your power. Every rain, I've done my part in remaking your world. You have tested my spirit and found it worthy!''

Lightning cracked, striking the mesa above him.

``And now I come to you, claiming \emph{my} due.'' He pounded his chest and pointed behind him without turning away. All his seared eyes could see was afterimages. The was no turning back. He would live or he would die.

``As you remade this world, I demand you remake this jackal. He will be my consort as I am yours. If you still find me worthy, I deserve no less!''

The world shattered with a crack and then the thunder died away to become distant rumbles. Akachi gasped as his sight returned and his paws burned with blinding light. He looked down to see his fur crackling with static. The house was still standing, its stone unmarked. ``I'm worthy,'' he whispered. ``I'm worthy.''

``Spirits,'' Chima breathed. ``We're still alive.''

Okori shook his head, trying to clear the ringing in his ears.

Akachi grabbed the jackal by the shoulders and shouted. ``Will you be the Lily's priest?''

``Yes!'' Okori yelled

The painted wolf pulled the jackal close. He grabbed the jackal's head and turned it to fiercely kiss him muzzle to muzzle.

Lightning cracked and they stumbled onto the soaked pelt on the floor. Okori was still a jackal, but the white and orange paint on his fur glowed.

Akachi rolled Okori face down on the pelt and whispered in the jackal's ear. ``And you will be my consort.''

Thunder roared.

\secdiv

\noindent Akachi woke to the soft patter of gentle rain. Soft, wet leaves brushed his muzzle and he inhaled the sweet, sacred scent of blue lilies. Everything felt young and vital as if the world was new, unspoiled by other's paws. The world as it was meant to be.

A lily spirit gently fluttered past his ears and Akachi opened his eyes to see a ghostly blue dragonfly. The spirit dipped its head in respect before it flew on.

The painted wolf smiled and stared up at the overcast sky, only blinking when raindrops fell into his eyes.

Eventually, his restless heart forced him to sit up and look around. He was in a field planted high on the valley's southern wall. The red mesa stood tall and proud to his right. Smoke rose from cooking fires. Joy blossomed in his heart as he saw the village intact and knew Monsoon kept her promise. Tears blurred his vision.

Only then did he notice the rest of the valley. The lowest fields had completely flooded up to the carved stone banks that protected the road. Everywhere the river had touched, lilies bloomed; the entire valley was covered with their sacred blue.

Then his ears flicked as he heard the rustle of someone approaching in the grass. He turned to look and saw Chima, and another painted wolf.

``Okori?'' He asked tentatively despite recognizing the former jackal's colors.

``Yes!'' The painted wolf ran to embrace Akachi.

They held each other closely and Akachi wept and wagged his tail. ``You're more beautiful than I ever could have imagined.''

Chima limped over and wrapped his arms around the other two and nuzzled them. ``We did it. The lilies agreed to raise the mists around the valley.''

``Already?'' Akachi asked.

Okori smiled. ``Chima helped me.''

Akachi looked at his brother. ``You two couldn't wait to do it properly?''

``Of course not.'' Chima wagged his tail. ``Our family is safe. Isn't that what's really important?''

Akachi looked around the valley and sniffed against sudden tears. ``Yes. Yes it is.''

