\input{content/titles/requiem}

``Come in.''

Bodarn, a badger amidst his 24\textsuperscript{th} summer, stepped into the shrine.

In the centre sat Zohan, a fox clad in a loincloth and covered from eartip to toe in intricate bodypaint and tattoos. They were a Dreamweaver, a religious leader and spiritual interpreter for the community. Much of their role emphasised music and dancing and bright, colourful use of body decoration. They were devoted to the celebration of the Gods' will, and particularly to the most significant part in that will: Love.

On the walls behind them was a statue of a canine, bearing three eyes. These motifs were continued all around the room. In the artwork and the drawings, and in small statuettes placed about the abode.

The fox turned and smiled at the badger, but this smile faded as Bodarn's discomfort was apparent.

``I have questions,'' Bodarn began, his throat catching, then releasing. ``About the spirits of the dead.''

Zohan nodded and gestured the badger forward to sit. ``It's about your father, isn't it?'' they whispered. ``May you have reprieve from grieving.''

``It's not that simple,'' Bodarn said, sitting down on one of the benches, trying to keep his paws still and to his side, but failing.

``Nothing ever is,'' Zohan assured him. ``But your father loved you, and you loved him.''

Bodarn stared abruptly up into the fox's eyes. ``No. That's precisely the problem.''

-

The shrine was a sprawling pyramid, located in a jungle clearing. It was surrounded on all but one side with thick trees and dense bogs. The steps up the pyramid gave way to large, open floors, then sprouted more steps from the centre to climb higher, thus producing external walkways around the diameter of the structure.

For now it was bright and the sky was clear, thus Zohan invited Bodarn outside with him to make the most of it. Rainstorms were common and divine, but were ideal for singing, dancing, and celebrating, not the kind of guidance Bodarn needed.

``My father and I\ldots{} couldn't decide what I was to be,'' Bodarn explained. ``He wanted me to be close, to be protected from the wilds of the world. And I was perhaps less than keen to adhere. I wanted to be like the others, out in the jungles, learning, exploring, adventuring. In the garden of the Gods.'' He came to a stop at one of the sets of stairs, looking into the trees where a trap had been set. ``You remember when Father had the accident with the snare?''

``How could I forget,'' Zohan nodded. ``I performed the incantations while the botanists did what they could to heal. And heal well he did.'' The fox nodded. ``But you were there too. The son was beside the father in the time of need. As was he with you in yours. He gave you that jade necklace, do you remember?''

Bodarn nodded. ``The necklace, yes. He'd crafted it just prior to the accident. He was going to wear it on the hunt, but after the accident he gave it to me so I can remember him when I hunt in his stead.'' The badger took a long breath. ``The pain he was in after that. It drove him mad,'' he explained, continuing to walk, descending down the pyramid stairs to the next floor. ``Few people outside myself and my mother knew of how the pain was affecting him. Few saw him, and those that did only saw him when we had enough herbs to numb the demons.'' Bodarn stopped again, staring towards the village they called home. ``I just remember the pain,'' he muttered.

The pair embraced and Zohan held Bodarn's head to their chest. ``You did what you could.''

``No, I didn't,'' the badger replied.

-

``May you rest from grieving.''\\
``Thank you,'' Bodarn replied, looking at the jar that contained his father's remains, loaded with care upon a pallet such that it could be transported to the burial site.\\
``Do you know where they are to be buried?'' the morgue-keeper asked.\\
Bodarn nodded. ``In the grove by the brook. It's where we used to sit when I was young,'' the badger said. ``Back when we talked.''

The last comment puzzled the vulture, but the bird nodded and tilted her bill, and the badger bowed in return.

Bodarn led the vulture outside, helping to wheel the large ceramic jar out of the morgue. Outside, they met Zohan again, and the three made their way with the jar through the village, across the muddy holy bogs to the north and towards the burial site.

-

Within an hour, the jar had been moved to the grove. The badger thanked the vulture, who retired back to the town, leaving Zohan and Bodarn with the large burial jar.

In the silence, Zohan broached the question.

``Do you feel his death was your fault?''\\
``No, I\ldots'' the badger stammered. ``I don't pretend to understand life and death. I know only of myself and of how my father and I were. And I know when he died we were father and son in name alone.''

Bodarn stared off towards the river, holding himself firm and letting anger rise, bubble, then fall and decay. The whisper of the wind wafted through the evening air.

He could hear the voices ringing in it.\\
The shouting.\\
The fighting.\\
A memory cast into the sky.

``As the pain grew worse, so did my father's temper. He was never violent, not did he threaten it. But he had high expectations of me, and was very controlling. I couldn't always give him what he wanted and he would get mad and I would hide away,'' Bodarn explained.

He began to dig into the ground where he would lay the jar, with Zohan helping. The terrain here was soft soil. Wet from the rainfall, reasonably fertile, but too close to the river to be useful as farmland. It was easy for the badger's paws to scoop through it, but it remained fairly solid to be piled up, unlike the thick, comfortable mud of the bogs or the strong, hard ground onto which the town was built.

When Bodarn's arms tired, he sat back and spoke again.\\
``I didn't want to anger him, or to hurt him. I just\ldots{} couldn't give him what he wanted. And as he grew more angry and we fought, I grew to resent his control and his temper. I wasn't as helpful, as kind and considerate as perhaps I could have been. He'd do things that would hurt me, probably not on purpose but\ldots{} I could never tell him he'd hurt me and have him understand. When I went to see a healer, he demanded to know what was wrong. When I didn't want to tell him why, he grew so terribly cross. Eventually, he deceived me into telling him. I couldn't handle the shame.'' The badger grunted. ``I must believe that I had done things in kind, but by the time he passed, we were so incapable of talking, I don't think we'd ever be able to apologise for our transgressions.''

``These are the questions I have,'' Bodarn said at last, once the trench was dug. ``Will my father, in death, know what I feel inside? Will he see that I don't love him anymore? And if he knows\ldots{} can he hurt me?''

Zohan sat up and took a deep breath. ``Have you ever read closely the parable of Three-Eye?'' they asked. ``The wolf who was given the gift of a third eye by the Gods? Capable of seeing the past and the present in one perfect image?''

Bodarn shook his head. ``Not particularly closely. Only what you've said of them at ceremonies.''

The fox nodded. ``When Three-Eye saw the past, they could see their mistakes and their failures. But what is forgotten is that Three-Eye also saw their achievements and their sacrifices.'' Zohan reached into the river water, lifting it up in their cupped hands, then bringing it to the grave, pouring it slowly over the jar. ``Thus it is important to remember that sometimes, in family and in friends, we will have failed. But sometimes, we will have succeeded in great ways too.''

The pair moved to lift the jar, slowly easing it down into the dirt, manoeuvring it to lie flat, the stone only a foot or two under the top of the grass.

``We are not expected by the Gods to be perfect and this is true of both you and your father. Not even the Gods can achieve perfection, and they have powers beyond our wildest dreams.'' They took a deep sigh. ``But what you describe, transgressions which divide both you and your father to the point where your love is severed, that is not\ldots'' The fox paused and considered. ``That is not a sin. It is a disappointment, a pity, a shame. But not a sin.''

The fox stood back up again. With the jar lowered into the grave, the fox looked back up to Bodarn. ``To find but a lack of love in your heart in the face of such adversity is\ldots{} understandable. It is simply, as I'm sure you feel, a shame that it is this way.'' Zohan looked back towards the jar. ``The Gods give love, they can take it away, but they can also let it fade. Love is the most powerful force in the land, and if the Gods saw fit not to preserve it between you\ldots{} it is the Gods' will, not yours, nor mine, nor your father's.''

``But will he still be angry?'' the badger replied. ``Will he have hate for me for not being able to love him anymore?'' Bodarn deflated. ``He was affected so by the way I stopped saying that I loved him. When he feared it was true. Now he knows his fear is correct.''

Zohan and Bodarn sat in silence. They stared into the distance, the intangible far. Hoping that something from the Gods might hand them the words, the actions, the divine wisdom.

None was forthcoming.

``We should collect the adornments for the jar before the burial,'' Zohan said at last.

The badger nodded and got to his feet, the pair beginning to walk back towards the village.

``It is a great disappointment that it fell that way,'' the fox continued. ``Fault is wrong, fault is not the right word. It is a shame. A miserable shame,'' they muttered. ``The Gods may judge you for your failures, and for his, but they will judge you both for your sacrifices, your attempts, your will to try. They will not judge for the dimming of the love. It\ldots{} is beyond your control. If your father is angry and hateful for that failure, then the Gods will judge him too. Some situations are unfortunate, like his injury, and what befell of your kinship.'' Zohan paused abruptly at the temple of Three-Eye. ``But if what you say is true, then\ldots{} it is just that. A tragedy of mutual transgression and entropy.'' They put their paw on the badger's shoulder. ``I wish you peace from your sorrow.''

Bodarn nodded, looking quietly up at the fox, before pulling in tightly, pressing his head to the fox's shoulder and beginning to weep.

-

Inside the family home, now quiet but for himself, Bodarn reached into a small box and pulled out the jade necklace.

The stone was cold. Like his father.

He put the box back, but kept the necklace in his paw. He began the walk to the burial site, as other mourners slowly began to congregate.

It was a small crowd, maybe 20 folk. But each had a story to tell. One of their experiences with Bodarn and his father. How much they resembled each other. How much they remembered how well they got on in a public capacity. That special bond of father and son.

What once was.\\
What might have once become.

The throng of people parted such that Bodarn could walk to the grave.

The jar lay quietly, dirt ready to cover it, while Zohan stood beyond it. They had been freshly adorned with intricate body paint, giving the fox an ethereal look, breaking up their outline in a series of dazzling patterns.

People took their places.

For a moment, there was quiet.

Wind rushed out of the trees, across the congregation. The badger tried not to listen to its words. Not to imagine the voice.

A deep breath.

Bodarn held out the necklace, up to the sunlight.

The crowd stirred in understanding, and Zohan spoke an incantation to bless the piece. When the fox lowered their voice, Bodarn eased the necklace around the neck of the jar, then stood back up.

``Why did it have to end like this?'' the badger whispered. And it was for this, not for the loss, that the badger began to weep.

Those each side of him, an otter and wolf, took gentle hold of the badger in an effort to comfort him, as Zohan began the ceremony.

``Calhaan is in the arms of the Gods now,'' they began. ``When they saw Calhaan, they saw a man who wanted the best for his family and did what he could to see out that vision. When times became tough, he remained steadfast and strong as best he could. In the end, the Gods saw that making this sacrifice endure was unfair, and relieved Calhaan of his pain. We must imagine Calhaan happy, pain free at last. In a place of peace.''

The winds blew again, the fox pausing to let them flutter through.\\
Hedges bustled.\\
Trees rustled.\\
Bodarn screwed his eyes shut.\\
Tried to close his ears too.\\
He didn't want to hear, or to notice.\\
\emph{``Please, just make it stop.''} was his silent prayer.

When the wind was quiet, Zohan continued.

``Calhaan is survived by his son, Bodarn,'' the fox said, looking at the badger for a moment, then back to the sky. ``His son shares the sharp eye, the astute curiosity, and the cunning determination that is embodied in his father's spirit. His destiny will be unique, different to his father, but no less holy than that of Calhaan. Though the destiny of Bodarn, as decided by the Gods, will not match that which Calhaan had requested, we know that with hindsight and divine foresight, we shall see Calhaan proud of Bodarn for their accomplishments, both past and in future.''

With the speech concluded, the Dreamweaver stood back, and the crowd turned towards Bodarn, inviting him to speak.

It was tradition to speak. For someone from the family to make a departing speech at the funeral. Sometimes, the survivor is so over encumbered with feeling that this is, understandably, not possible.

Bodarn had no idea what to say.

It wasn't so much that he hadn't prepared.

More that nothing could prepare him.

On Calhaan, he had nothing to say.

On the resultant shards of broken feelings, he could speak for years.

As he stood, with those around awaiting him to speak, he spoke not a word.

The silence hung for a while. It was awkward. Uncomfortable.

At last, Bodarn sighed and uttered, ever so simply. ``I'm sorry.''

It was said without direction.

To the Gods.

To Zohan.

To the attending masses.

To Calhaan.

To all of them.

To none of them.

Bodarn stepped back into the throng of people, now confused and uneasy. As Zohan stepped back forward, they were the only person, other than the Gods, Bodarn, and Calhaan to properly understand what was going on. People seemed to understand that something wasn't right, but they were all far too polite to ask. Certainly not right now.

To conclude the proceedings, the Dreamweaver began to sing a slow, lumbering piece of throat music. People joined in once the piece reached more comfortable registers, but that too was awkward, abashed, and uneasy.

The badger joined in with the song, and, as Zohan stopped singing to let the crowd carry it onwards, stepped forth again to aid the fox in laying the dirt over the jar. The act of adding the dirt was done communally, led by the family, but all assembled would participate, for as a community they were burying one of their own too.

With all hands, paws, and wings on deck, as the sun set down to touch the horizon, the last handful of dirt was cast over the jar.

Calhaan was gone.

Bodarn knelt by the grave, breathless, while the rest of the congregation paid their respects in near silence and one by one, departed back for home.

Many would look upon Bodarn and seem keen, so, so keen to say something. To broach the enormous silence, but stopped themselves short.

When Bodarn and Zohan were alone, the badger spoke at last.

``It is done,'' he said.

``It is,'' Zohan replied.

The badger sighed and got to his feet. ``I think I'm going to have to answer a lot of questions in the coming months.''

``Tell them the truth, if you feel you want to,'' the fox replied, putting an arm over the badger's shoulder. ``The truth can only set people free.''

``People won't want to hear it, that's for sure.''

``Perhaps.'' Zohan nodded. ``But that's true of all great truths, isn't it?''
