``Hey, Amalu! Wait up!'' Naoum darted out from behind a retaining wall, huffing and puffing under the weight of the cloth sack slung over his shoulder. His tufted caracal ears swiveled left and right to check for eavesdroppers before he continued. ``Where are you going in such a rush? You're not hiding a girlfriend from me, are you?''

``Ha, I wish. I'm just trying to find a place to hide from my shame.'' The trim fennec fox braced his paws against a retaining wall and stretched until an air bubble popped beneath the bands of hard-earned muscle in his shoulders. ``Do you\ldots{} happen to know of any?''

``It's a happy coincidence you've found one.'' Naoum wiped his blood-stained paws off on his apron, making sure they were clean before giving the fennec a pat on the back. His fingers were sheathed in a healthy layer of fat from constantly snacking in the communal kitchen. ``This storeroom has been abandoned since the Two Banks raided our village.''

``Oh.'' Amalu's heart skipped a beat as he noticed signs of charring on the acacia wood door. He nervously fiddled with a band of silver set with a triangular piece of polished coral that adorned the middle finger of his right paw. ``That was many moons ago indeed.''

``It's where I escaped from my sisters growing up.'' Naoum shook his head and tapped a small doodle beneath a window of what looked like a steaming bowl of something tasty. ``Making pigments from animal fat and burnt charcoal was the hardest part. Leftover drippings in the summer heat are\ldots''

``So that's why you've never complained about supervising the nursery.'' Amalu slid down against the mud-brick structure and buried his muzzle in his paws. The full sleeves of his dark brown \emph{djellaba} robe slid across his wrists, giving him the appearance of a large bundle of un-milled grain. ``Since I know you're going to \mbox{ask---''}

``Did you uh---''

``Yeah, I failed to face the red deer again.'' Having uttered the dreaded words, Amalu lifted his head up as a gust of wind carried Naoum's scent to his muzzle. The caracal's musc---earthy and a little sweet---recalled the comforting odor of a household kitchen with warm bread baking in the oven. ``I was \emph{right} there, my spear was in the perfect position, and\ldots{} I\ldots{} I couldn't do it. My father had to salvage the hunt for me.''

``Maybe you're just not cut out to be a hunter.'' Naoum shrugged as he retrieved a small mortar and pestle from his rucksack and flopped down next to the fennec fox. Humming softly, he began grinding a few stalks of dried sweet marjoram. ``I like to have my meat pre-slaughtered. I can carve up a carcass no problem, it's the killing part that turns my stomach. It really spoils my appetite.''

``But everyone expects me to be brave. I'm the only son of the Imazighen.'' Amalu sighed, cuffing himself on the side of the muzzle in frustration. ``It's \emph{fucking} hard when everyone expects me to face danger without flinching and\ldots{} I just \emph{can't}. I freeze up like a dim-witted animal when fear strikes me.''

``Well, if you're dead set on filling your father's hunting boots\ldots{} I bet your courage will come to you when you most need it.'' While Naoum had not yet proven his manhood, the occasional dispensing of sage advice gave him the gravitas of an elder brother the fennec had never been blessed with. ``Trust in yourself\ldots{} and in the First Gods. Oh! Speaking of which---''

``Hrm?'' Amalu cocked an eyebrow as Naoum's face lit up.

``Haziz needs to see you. That's why I came looking for you in the first place.''

``Don't you have cooking to do?'' Amalu replied, playfully punching the caracal on the shoulder. ``I didn't take you for Haziz's errand boy.''

``My sisters want to prepare tonight's feast\ldots{} but I always have a spare moment to help the old man,'' he said with a smirk. Throwing his pack on the ground, he offered the fennec a clay pot decorated with crudely illustrated pictograms of what Amalu assumed were fruits. ``Hopefully they don't burn the meat too badly. Take this to Haziz for me---you know it's his favorite.''

Tugging the lid free, Amalu was delighted to see his favorite---preserved dates. Harvested a few weeks earlier, they'd been left to ferment in the village's preserving hut before being sprinkled with salt, blended with mint leaves, and garnished with a few delicate threads of wild saffron. ``And mine as well. Did you pack any---''

``Extra? Of course,'' Naoum said, dropping a small oilskin on top of the jar.

``Maahnoor is coming along well in her learning, isn't she? She should know how to prepare red deer by now.'' Amalu pursed his lips in thought. ``Let me guess\ldots{} Maahnoor preserved the lemons and Layla decorated the jar?''

``Layla is quite the artist\ldots{} for a toddler.'' With a grateful smile, Amalu plucked a quartered date from the bag and popped it into his muzzle. Sweet with a pleasantly salty aftertaste, the fennec held it in his muzzle for a good minute before finally allowing himself to swallow. ``Delicious, as always.''

``Don't eat the entire bag on your way. You'll ruin your appetite,'' the caracal admonished. After neatly packing his thoroughly crushed herbs away, Naoum waved as he set off toward the central kitchen of the village. It was readily marked by the pillar of dark woodsmoke its enormous oven produced. Amalu's stomach growled at the thought of dipping a hunk of \emph{khobz} into a rich bowl of cumin-seasoned red deer stew. ``And you better \emph{actually} get it to Haziz this time!''

``Have some faith in me!'' Rolling his eyes, Amalu made sure the jar's lid was tightly sealed by softening the beeswax lining around the rim with his paw pads. Plucking a few lingering thorns from his side---the unfortunate result of dodging into a spiny bush---the fennec stood up and stretched before setting off toward Haziz's dwelling at the outskirts of the village.

Known as Henchir-Aïn-Dourat, Amalu's village was half-encircled by the Mueti Alhayaa river flowing downward from the mountains. The snowmelt water was crisp, almost transparent, and refreshingly cool, a boon to the women doing the washing as the heat of the day faded. They kept their bodies comfortable with towels soaked in river water while draping colorful blankets and robes along drying lines formed from braided lengths of reed.

Haziz lived alone in a traditional tent, a short distance from the village and close to the foothills of the awe-inspiring mountains that had long guarded Henchir-Aïn-Dourat against invaders from the east. Their ink-black slopes were dusted with snow, which occasionally drifted down to the village during the height of the cool season. ``Magnificent,'' Amalu muttered, pausing to admire the work of the First Gods.

It was said that the peaks were formed from the scales of the great demon-snake, Thueban Shaytan, who had battled the First Gods to a standstill in his quest to consume all that ever was and would be. Unable to defeat him through strength alone, T-am-ădad, the hyena god, had offered him tea to spare just one village---Henchir-Aïn-Dourat. Thinking the hyena foolish, Thueban Shaytan consumed the poisonous oleander flowers hidden amongst the tea leaves and was thus felled by trickery. Ever since, his village had honored the hyena god as their patron.

Amalu turned his claws toward his heart in a gesture of reverence before crossing a wooden footbridge over the river. A few redbelly tilapia darted among the reeds, wriggling their streamlined bodies against the powerful current. The color of their undersides matched that of Haziz's humble dwelling, a triangular structure with a sharp and distinctive peak dyed brilliant vermillion.

``You asked for me, Haziz?'' Amalu brushed aside the flaps of the hartebeest-hide tent and stepped onto a lightweight \emph{kilim} rug. Though the Caspian culture had abandoned their nomadic lifestyle many years ago, some elders still had a longing for the old ways running in their blood. ``Naoum caught me just as I returned from the hunt.''

``Yes, yes, come in.'' A paw covered with close-cropped sandy fur waved him inside. Haziz was seated on an intricately woven \emph{kilim} dyed a yellowish shade of ochre. The remainder of his tent's floor was covered with rugs of varying quality---most given by the women of the village in exchange for his skills as a healer---which kept the dwelling pleasantly warm. ``Please, have some water; you must be thirsty. How was the hunt?''

``The red deer are moving higher into the mountains, where there is more water. Tanamart is bringing the meat back now.'' Amalu glanced at the silver hyena idol resting on a small sandstone platform behind Haziz's cot to avoid making eye contact with the shaman. ``Though it will be a long walk\ldots{} even longer than the last hunt.''

``And did you find your courage?'' Haziz stroked his chin as he seemed to magically draw Amalu's gaze. Not that there was much else to distract him; aside from rugs and pillows, Haziz's tent was sparsely decorated.

``No, I failed at my task.'' Amalu's shoulders slumped as he met the fennec's milky eyes. He was the oldest member of their village, considered ancient even when Amalu's grandfather was Imazighen, the leader of their tribe. ``The First Gods, they---''

``The First Gods provided for the village with a successful hunt. There is still something to celebrate, is there not?'' Gazing out at the distant sea, Haziz took a deep breath and curled his paws. ``I see great danger on the road you travel, young one.''

``What is the danger? My own cowardice?'' Amalu sighed as he rested against a semicircular pillow decorated with colorful seashells. ``I let everyone down. They were depending on me.''

``The danger comes from seeing your own struggles as unique. You forget that all members of Henchir-Aïn-Dourat are equal before the First Gods.'' Haziz sighed. ``Do you think that your father never lost his courage?''

``I\ldots'' Amalu awkwardly bit his tongue.

``Your father's first hunt was a disaster. When it came time for him to spear the red deer, he acted with too much vigor and hit another youth instead.'' Haziz's expression briefly softened. ``That young fennec was my grandson. After that, your father never wanted to hunt again.''

``What changed?'' Amalu leaned forward, heart pounding in his chest.

``I forgave him for the good of Henchir-Aïn-Dourat.'' Haziz reached out and grasped Amalu's paws in a trembling embrace. ``When he realized that even the accidental taking of a life would not be his end, your father found his courage. Courage is the willingness to pick up the pieces of yourself and carry on after even the worst failure. Now, let us speak no more of this.''

``Yes, Haziz.'' Amalu respectfully bowed. He then retrieved the jar of preserved figs from his knapsack and placed it in front of Haziz. The fennec fiddled with his ring as his stomach growled. Anticipating a productive hunt, he had only eaten only a pawful of pistachios that morning. ``Naoum sends his warmest greetings.''

``I know the Kitchen-Maester keeps too busy to deliver, so it is fortunate he has a reliable friend to arrange for such things. Now, let us discuss why I called for you\ldots{} and it wasn't simply to bring me a jar of preserved figs.'' Haziz set the jar aside as he stroked his tongue across his bottom lip. ``Though your small kindnesses are always appreciated.''

``I can tell by your tone that you haven't brought me here just to dispense some sage advice.'' Amalu sighed. ``Why am I really here, Haziz?''

``What I would give to sit you on my knee and allow a dollop of sage advice to be the end of this.'' Haziz stroked a paw through his ragged headfur and closed his eyes. ``There is a disturbance in the heavens. Surely you have seen the signs, yes?''

``The fishermen's catch is not what it once was\ldots{} I remember when the Mueti Alhayaa was so teeming with life a toddler could bring home a meal by tugging open their catch-cloth and letting the fish leap inside.'' Amalu reached for a hollowed-out ostrich egg perched upon a stand made from aromatic thuja wood. He jiggled the top free and poured himself a cupful of cool mineral water. ``Is that because the First Gods are displeased with us?''

``I don't fully understand what I've seen in my visions\ldots{} but I feel that something has happened to bring discord to our lands.'' Haziz's gaze remained fixed towards the distance, where an ominous cloud of sand had begun to gather near the Northern Sea. The thrashing sandstorms had increasingly blocked Henchir-Aïn-Dourat from the village’s traditional fishing grounds. ``The sands roll in a little further every day. Soon, they will be blanketing my tent in a layer thick as mountain snow.''

``Are you sure of that?'' Amalu gazed toward the shimmering water just before it vanished from his sight.

``Are preserved figs delicious?'' Haziz asked rhetorically as he popped the jar's seal. He set a whole fig on a carved olivewood bowl in front of the idol of T-am-ădad before pouring the remainder onto a mat equidistant between them. ``Please let Naoum know that I will make an offering for young Layla. I know she has been troubled by nosebleeds.''

Amalu waited for him to finish murmuring a prayer over the food before interjecting. ``My father says---''

``Your father is a wise Imazighen.'' Filling his own tin cup with a trembling paw, Haziz took only a small sip. He looked like a sunbird drinking from a bead of freshly gathered dew. ``But he has never been the most attuned to spiritual matters.''

``He certainly has never taken it upon himself to dust the household shrine. Is that why the First Gods are displeased with our people?'' Amalu's brow furrowed with concern as a list of potential sins raced through his mind like a scimitar oryx across the veldt. ``Is my cowardice---''

``No, this is not of your creation.'' Haziz looked like a gnarled desert tree as he used a flint to send a cascade of sparks into a small nest of tinder beneath a bronze teapot. ``But it falls to you to restore balance to our village\ldots{} much as I wish the burden would not be yours.''

``How can I help?'' Amalu took a preserved fig and added it to the bowl in front of the idol. ``I may not be courageous but\ldots''

``Don't sell yourself short. The First Gods have ordained this task for you.''

``What would you have me do?'' Amalu tilted his head as an ember began to glow in the depths of the densely packed straw. Like a tiny cherry, it took on a beautiful shade of red before finally transforming into a dancing pillar of flame that climbed until it licked the teapot's blackened bottom. ``This isn't the kind of task where you die, right?''

``I would hope not. I'd miss your red deer jerky.'' Haziz poured the remainder of the water into the teapot along with a smattering of brightly colored desert herbs. Leaning in to watch the petals swirl in the gentle heat currents of the water, Amalu caught an intense whiff of musk rising with the steam. ``You must go to Lalla Khedidja.''

``The Weeping Mountain?'' Amalu asked. ``But such journeys were forbidden after\ldots''

``Bachar's ill-timed disappearance was most unfortunate.'' Haziz shot him a soft frown of acknowledgement, showing off his missing inner incisors---the mark of manhood among the Caspian culture. ``But we must do as T-am-ădad wills. Now, drink the brew I've prepared. You will need to augment your strength\ldots{} it is a long night's walk.''

Haziz poured Amalu a full cup without spilling a drop. The younger fennec tried not to gag as he dumped the noxious concoction down his throat. It left a lingering tingle on his lips, core muscles almost immediately lighting up with a pleasant buzz of energy.

``What's in this drink, anyway?'' Amalu sighed and gratefully accepted a small clay bowl filled with dried green olives in date vinegar.

``A nut from a distant land. Very rare and hard to acquire\ldots{} especially since the traders haven't come in many moons. I was saving the last of it for an occasion of sufficient significance.'' Solemnizing the proceedings, Haziz presented him with a papyrus scroll upon which the elder fennec had scrawled a prayer in his inscrutable handwriting. ``Take it to the Weeping Mountain and lay it upon the Cracked Altar. This is your task.''

``But Haziz!'' Amalu started to object as the older fennec brusquely ushered him out of the tent. ``How will I know the way? That's further than I've ever gone on a hunt.''

``How should I know?'' The fennec shot him a sly smile as he gazed upward toward the last rays of the evening sun. Gently turning the scroll over in his paws, Amalu was surprised to find a crudely drawn map. ``I'm blind.''

\secdiv

\noindent Amalu drew his cloak up against his body as he followed one of the precarious hunting trails upward toward the Shrine of T-am-ădad. Taking a glance back at his house---a circular structure at the center of the village with the luxury of two mud-brick chimneys to fend off the chill of night---he sighed and finished the last of Haziz's invigorating tea.

``I can't believe I agreed to this,'' Naoum muttered, rock crunching beneath his rawhide sandals. Pudgy belly visible beneath his light yellow \emph{djellaba} robe, he kept his muzzle busy by chewing on a rod coated with crystallized sugar. ``Your red deer jerky is good\ldots{} but not worth dying for. We're probably going to end up just like Bachar. I still miss that old fennec.''

``Don't be so pessimistic.'' Amalu kept one paw resting on the hand-me-down sword belted next to his right hip, trying to avoid accidentally cutting his knee on the noticeable bend near the tip. ``Maybe Bachar opened a \emph{sahlab} stand just up the road and will give us a free sample.''

``At least we didn't miss the feast.'' Naoum changed the subject to something less morbid before pausing to nibble on a crusty bread roll. He fell a few steps behind the fennec while searching for a small pot in his rucksack. A few drops of fragrant sauce spilled onto the dirt as he thoroughly drizzled the leading edge of his \emph{khobz} with leftover mint sauce. ``Why the long face?''

``The mountains aren't what they used to be.'' Amalu saw better in moonlight than in the afternoon sun, easily dodging the ruts and gashes in the trail where a lack of maintenance had allowed significant erosion. He tried to ignore the sheer drop-off along the edge, no barrier separating him from the unforgiving rocks below. ``My father says they're infested with bandits now\ldots{} people displaced by the Sea-Raiders.''

``Maybe we can bribe them for safe passage?'' Rummaging around in the canvas bag strapped around his chest, Naoum's ears perked up as he tugged two jars of preserved figs free. ``I packed plenty of provisions.''

``First, I'm not much of a haggler,'' the fennec said with a soft sigh. ``Second, I'm not sure they're too interested in arranging a parley. Showing off any valuables might be treated as an open invitation for them to cut our throats.''

``Point taken.'' Paws trembling with nervous energy, Naoum traded the jars for a weathered dagger, handle wrapped in fraying rawhide. ``Do you think this is enough protection? I'm not much of a fighter.''

``Here\ldots{} you've taught me how to preserve my hunting spoils, and I think it's about time I return the favor.'' Amalu gestured for the caracal to pass the dagger. ``First, we need to make sure your weapon is in good repair. It'll be of no use if you can't cut through leather armor.''

``Right.'' Naoum's eyes lit up with interest as Amalu made a quick test cut against a flat stone plucked from along the trail's edge. ``So how do you sharpen one of these things?''

``You didn't bring a whetstone, did you?'' Amalu cocked an eyebrow as the dagger left a barely visible scratch on the argillite. He repeated the test on his forearm and found it barely penetrated the dense fur of his undercoat, let alone breaking skin.

``Would you be mad if I said that I don't even have one?'' Naoum apologetically rubbed the back of his head. ``I know I'm older and should be better prepared but---''

``Good thing I always have one handy. You'd be lucky to slay a carrot with this edge.'' The fennec frowned, holding the dagger's surface up so that it caught one of the twinkling moonbeams. Beneath the pitted surface, Amalu noted the metal was of surprisingly high quality. ``Did you never learn proper knife sharpening in the kitchens? I'd imagine a cook would take care of all his cutting tools.''

``My mother usually handles that. You know how she is,'' Naoum replied.

``Overprotective, I know.'' An oddity among the young males in the village, Naoum was more likely to be seen gathering desert herbs or overseeing the preserving hut than honing his fighting skills. Amalu chalked some of that up to his upbringing---Naoum's mother still breast-feeding him and changing his catch-cloths at the age where Amalu was beating other cubs in mock combat---a fact he had only learned recently. ``You will eventually need to stand up to her.''

``I'm not an adult yet. Maybe she'll finally take me seriously then.'' Naoum shrugged. ``At least then she might back off a little, you know?''

``Is that why you've always tried to act so mature around me?'' Pulling a compact whetstone about the size of his palm from a pocket on his scabbard, Amalu gave it a splash from his waterskin before putting it to use. Amalu meditatively dragged the dagger's edge across the quartz, ears swiveling back and forth at the sharp noise. He found the process soothing, intermittently pausing to check the sharpness against the softer test stone.

``That and taking care of my sisters.'' Naoum shrugged, picking his teeth with a small length of whittled antler. ``You're a natural fighter\ldots{} and I've been blessed by Em-ăsăww. One must accept such gifts as they come, even if we sometimes might wish things were different.''

``Would you ever trade places with me?'' Em-ăsăww was the lioness god, the protector of the hearth, and it was said that she bestowed the gift of fire upon his people in the form of a burning branch taken from the Ancestral Hunting Grounds. Though many men in the village derided her as weak, Haziz had once told him that she was the fiercest warrior among the First Gods.

``I don't know about that\ldots{} but I'll start keeping my dagger sharp.'' Leaving a deep scar in the rock, Amalu gave Naoum a satisfied nod before passing the weapon hilt-first. The caracal inspected it approvingly before tucking it into his rough canvas belt. ``For you, at least.''

``Hopefully you'll never have to use it for anything other than slicing through sinew.'' Amalu briefly tensed as Naoum hugged him from behind, the caracal resting the base of his chin on the close-cropped fur on his neck. ``H-hey---''

``Thank you.'' Naoum held him close for a moment before stepping back to pick up a discarded glass jar which might have once held a traveler's supply of honey. ``For an \emph{akhi alsaghir}, you have a lot to teach me. Speaking of which\ldots{} what exactly does Haziz think is causing this mess?''

``He claims it's something to do with the First Gods, but I'm not sure how much I believe that.'' Amalu sated his thirst with a long draw from his wineskin before continuing. ``My father believes the drought is worsening the storms\ldots{} all the vegetation that holds the sand back is drying up. At the fishing outpost it's all you can see. It's nothing but dead grass in every direction.''

``Perhaps the heavens are causing the drought,'' Naoum replied as Amalu held up a closed fist. In the distance, far beyond any of the village's outlying homesteads, the flicker of a campfire was visible against the pinkish rock. ``What do you think that is? Other travelers?''

``Whoever they are, I don't think they're friends to us. Keep your head low.'' Dropping down into a crouch, Amalu tried to minimize the crunching of stones beneath his foot paws as he cautiously advanced to a position behind a boulder shaped like a thumb. ``Oh, shit.''

A small camp had been set up next to the trail, beside an ancient fountain constructed over a natural spring to offer relief to thirsty pilgrims. Several bedraggled tents were circled round a dim campfire like a herd of gazelle facing down a leopard. Standing directly on the trail, a lone figure blocked their path as he kept watch. ``What do we do, Amalu?''

``They look like Two Banks,'' Amalu muttered, squinting to get a better view. The watchman turned, revealing himself to be a ram with a prominent \emph{ankh} in high relief on his bronze chest plate. ``This is not good. Should we turn back?''

``You got a task from Haziz, right?'' Naoum placed a reassuring paw on his shoulder. ``I think this is your chance to prove yourself. I won't stop you if you turn tail and run but\ldots{} I'm not going to abandon you while my dagger is still sharp.''

``You're a good \emph{akhi}.'' Amalu gingerly drew his sword and flicked his head toward the ram. Fear turned his blood to ice as he stared down the guard and imagined facing him. ``Do you think you can draw the watchman's attention without getting yourself killed?''

``I've gotten pretty good at drawing attention.'' Naoum smirked, pulling a small glass phial from his bag. ``But I assume your plan calls for something with a little more subtlety than a \emph{cla-chiss},'' he said with a wink.

``Yeah\ldots{} something that won't wake the rest of the camp. There's no way we can take all of them. Frankly, even facing one in a straight fight will brush up against the limit of my capabilities.'' Amalu nervously scraped his claws against the sand-smoothed trail stones.

``Give me your wineskin, if you would.'' As soon as Amalu handed it over, the caracal poured about half of its iridescent red contents into a marble pestle. After adding a small measure of the thickening agent in the phial, Naoum blended the contents into a fine slurry that---on first impression---replicated the hue of freshly-spilled blood. ``Convincing, isn't it?''

``Under the moonlight, I can barely tell\ldots{} other than the smell.'' Fire burned in his nostrils, the intoxicant swirling around deep in his skull. Naoum began staining his nut-brown fur while Amalu judiciously cut swatches from the caracal's coat, trying to make them appear as haphazard as possible. By the time they were done, it looked as though a bandit had done an extremely poor job of attempting to slash Naoum's throat. ``Okay. Do you think you can act the part? I just need you to buy me enough time to get him off-balance.''

``Pfft\ldots{} do you know how I get out of doing the difficult chores? Acting like I've caught a stomach bug does the trick every time.'' Sliding his fingers down across his muzzle, Naoum instantly transformed his countenance into an agonized snarl. ``Just don't let me down\ldots{} and don't die.''

``I've got you,'' Amalu said, gripping the caracal tight. ``We do this \emph{together}.''

``Then here we go. Spear the red deer this time\ldots{} for me, okay?'' Naoum cracked his shoulders before stepping out of cover and into moonlight that glittered like fish scales.

Steeling himself, Amalu gripped his sword tight as Naoum staggered forward, moaningly just loudly enough to catch the guard's attention. Paws trembling with fear, the guard held his sword out like a protective amulet as he moved forward and gradually out of earshot of the rest of the soldiers. ``W-who goes there! Name yourself, stranger!''

``I\ldots{} I-I've been stabbed!'' Tottering forward like a newborn calf, the caracal spurted the remainder of the viscous liquid down his robes for dramatic effect. Stretching a paw out, he groaned before collapsing with a soft \emph{crunch}. ``H-help me\ldots{} bandits!''

Raising his khopesh---a sickle-shaped sword that reminded Amalu of a skinny ax---the ram rushed over to the fallen caracal while sweeping his blade from side-to-side to fend off any threats that might strike from the darkness.

Heart pounding in his chest, Amalu's mind flashed back to the red deer charging at him, horns leveled at his throat. Claws digging into the fish skin leather that bound his blade's handle, he crept forward as the watchman hesitated, unsure of how to respond to the situation.

``Sometime this moon,'' Naoum mouthed, as the watchman seemed to make up his mind. Taking a few furtive steps toward where the caracal's collapsed body lay still, the ram twisted his \emph{khopesh} vertically as if preparing to plunge it through Naoum's chest.

It looked like their plan to catch the ram entirely off-guard had gone awry.

Amalu was a few seconds too slow to intercept the blade outside the zone of danger. Speeding downward, the pointed tip came within inches of touching Naoum's robe before Amalu's blade connected with a muted \emph{clang}. It threw the ram off-balance, and he stumbled a few feet off to the fennec's side. ``Sorry! I could have planned that better!''

``Well, don't stop now!'' Naoum unsheathed his dagger and wildly slashed at the ram, driving him back toward Amalu. ``I'm passing him to you!''

``I've got him!'' Spinning his \emph{khopesh} like a sharp-edged windmill, the ram kicked Naoum's leg out from under him before pivoting to go on the offensive. Grimacing, Amalu was pushed back nearly a foot as their blades met again. Spittle collected on the ram's lips, powerful shoulders supporting strikes that landed like blows from a blacksmith's hammer despite his weapon's dainty appearance.

``Is that the best you can do, whimpering cub?'' Snarling, the ram nearly battered the blade out of Amalu's paw with a vicious two-handed blow. ``After I'm done with you, I'm going to turn your plump little companion into cooking fat!''

``I won't let you hurt him!'' Amalu bared his fangs as he hacked and slashed at the ram, all-consuming rage compensating for poor technique. Fueled by tempestuous prayers to T-am-ădad, the fennec managed to push his opponent back with the might of the First Gods briefly on his side. ``Naoum and I will lay eyes upon the Cracked Altar\ldots{} together!''

``Ah, so it is your people who worship the false gods,'' the ram said, delivering a brutal kick to Amalu's knee that threw him off-kilter. ``Time to end your blasphemy.''

Employing relentless overhead strikes, the ram slowly battered the sword out of Amalu's paws, leaving the blade bent at a nearly thirty-degree angle by the time it finally slumped into the hard-packed dirt. Too weak to put up further resistance, Amalu shot the ram a defiant glare. By happy accident, the fight had taken them well beyond earshot of the camp, the lonely campfire still flicking in the distance. ``Are you going to strike me down?'' Amalu asked, panting and exhausted.

``Admit defeat and renounce your god and I will spare you\ldots{} though you will forfeit your right paw for attacking a servant of Aten.'' The ram sunk his \emph{khopesh} into the ground and fumbled about for the ram's horn slung over his shoulder.

``It is better to die whole in service of T-am-ădad than to die a scarred unbeliever.'' Drawing his tongue up against his teeth, Amalu hawked a glob of spit straight into the ram's eyes. ``May the hyenas feast on your heart.''

``Why you---'' Stumbling backwards, the ram's claws grasped around the horn just as Naoum's dagger plunged through his sternum. Gasping, the ram touched the razor-sharp tip before dropping to his knees. ``You're nothing but a cub\ldots{} you're---''

``We are the servants of T-am-ădad.'' Without hesitating, Amalu drove his sword through the watchman's chest exactly like he would a red deer. Eyes shooting open, the ram registered an expression of intense surprise before he expired. ``And we are your end.''

``Were you\ldots{} waiting for a moment to use that line?'' Naoum started to lose his balance as Amalu wrapped an arm beneath his shoulder. He gently lowered the caracal to the ground, bracing him against a rock before handing him a leather bag packed with healing supplies. ``Because you couldn't have just come up with that, right?''

``I mean\ldots{} I didn't think my first kill would be like this.'' Amalu dragged the ram's body out of sight as Naoum applied some medicinal herbs to his swollen ankle. ``I figured it would be more\ldots{} triumphant.''

``We're alive, aren't we?'' Climbing to his feet with a grunt of effort, Naoum took Amalu's paw with a weary grin. ``Come on. Let's get out of here before they wake up. Servants of T-am-ădad should not linger around unfriendly spirits\ldots''

\secdiv

\noindent ``You were brilliant back there, you know that?'' Amalu brushed his wrist through the sweat-drenched fur on his forehead as he excavated the last few shovelfuls of dirt from a hastily dug grave. With a thick layer of mountain frost still coating the ground, it was effortful work. ``Thank you for doing what I couldn't.''

``I just got a lucky shot. You were the one who really fought him.'' Dressed only in a loincloth, Naoum tipped the last of the wine into his muzzle. His robe had been donated as an improvised burial shroud for Bachar's body. They had found the wizened fennec at the base of the shrine, bow in paw, surrounded by three Two Banks warriors studded with arrows. ``Your father would be proud.''

``You really think so?'' Amalu rolled his eyes, turning away to hide the hotness beneath his cheeks. ``You don't have to flatter me.''

``I'm only speaking the truth.'' Naoum stretched his arms wide as clouds drifted low above the Shrine of T-am-ădad. A massive and ancient statue far beyond anything Amalu had seen in his village, it covered most of the western face of the Weeping Mountain. Water flowed downward from the hyena's eyes to his cupped paws, which then spilled into a midnight blue waterfall feeding the Reflecting Pool that stretched as far as the eye could see. ``You were the one who had to be brave.''

``More foolish than brave\ldots{} but I'll take the compliment.'' Amalu chuckled, refilling the empty wineskin with water from the sacred pool. Crisp and sweet, it tasted as though it were expertly blended with the finest honey. ``Have you sated your thirst?''

``Yes\ldots{} but let's make sure we drink again before we leave. It's a long walk back to the village.'' Amalu sighed, filling the wineskin to the brim before tucking it next to Bachar's shrouded form. Naoum had already used the last of their supplies to provision the grave with a jar of preserved figs, a clay amphora of olive oil, and a few strips of aurochs jerky. ``Is there anything I'm forgetting?''

``You've forgotten the prayer-dust.'' Naoum hummed as he dusted the shroud with a thick layer of ochre pigment. ``Let us bid our old friend a safe journey. Hopefully he will cook \emph{sahlab} for the First Gods in the afterlife.''

``T-am-ădad will show him to the Ancestral Hunting Grounds. I am sure of it.'' Amalu sighed as the first pearls of dawn peeked over the eastern horizon. Walking over to the Cracked Altar, the fennec tucked the prayer scroll in the largest fissure. Sighing as he held back tears, the fennec lit a small beeswax candle in the alcove above the altar, which contained a smaller figure of Em-ăsăww---placed by Naoum---beside the main carving of T-am-ădad. ``And Em-ăsăww will give him a bottomless canister of the Divine Spice for cooking.''

``Do you think we've proved our manhood?'' With their task complete, Amalu rejoined Naoum, the caracal staring into the mirror-like surface of the Reflecting Pool. Two hopeful reflections stared back at them from the depths, both missing their inner incisors. ``Facing another life-or-death challenge this year might be a bit too much for me.''

``I'd certainly hope so.'' Naoum's belly jiggled as he anointed Bachar's body with water from the sacred pool, allowing the dye to saturate the wizened fennec's light tan \emph{djellaba}. ``I think we both earned our manhood today\ldots{} in the eyes of the First Gods, if not the Elders.''

``I'll ask Haziz to put in a good word for us.'' Driving the shovel into the earth to serve as an ersatz headstone, Amalu padded over and helped the caracal cover the body with fresh sandy dirt. ``Now let us lay old Bachar to rest.''

Chanting in unison, the pair sang a wavering melody as they returned the shrouded figure to the earth, their voices echoing off the Weeping Mountain's contours until they replicated the agony of a thousand mourners. Though the meaning of the words had been lost to time, each syllable burned their throats with the melancholy of a soul leaving the mortal plane. They kept singing until their voices were hoarse and the grave's surface was smooth as the Reflecting Pool opposite it.

``And it's done.'' Flopping down against one of the Shrine's crackled marble pillars, Amalu sighed as he gazed back toward his village with heavy eyes. ``I just realized we haven't gotten a wink of sleep.''

``Rest then, little fennec. These should provide plenty of shade until at least midday,'' Naoum said, giving the pillar a gentle tap. Sitting down beside him, the caracal allowed Amalu to rest against his well-padded shoulder. Taking a deep whiff of his feline scent, Amalu sighed with contentment as he began to drift off to sleep. ``I'll keep watch, just in case the Two Banks camp sends a scout to investigate.''

``Thank you. Hopefully the First Gods hear Haziz's prayer\ldots{} and ours.'' Amalu yawned and snuggled up against the caracal with a contented sigh. Off in the distance, where the village sat at the edge of the horizon, silver-tinged rain clouds began to gather.

``Rest well, \emph{akhi alsaghir}.'' As Amalu drifted off to sleep, Naoum watched with hopeful eyes as, for the first time in many moons, rain began to fall on the dusty village of Henchir-Aïn-Dourat.
