The wanderer's torch cut a blazing red swath through the sea of stars as he trod the beaten path. Golden waves trickled and lapped over the coarse brown fur of his outstretched arm, and he raised his other paw, shielding his eyes from the glare, wondering what company an open flame might summon at this hour. Out there, somewhere, the crows who had haunted his steps since crossing into the foothills of Illyria still lingered beyond the sharp shadows, waiting. But he wasn't carrion yet.

A distant jackal-dog bayed its ghostly song to the slender moon, and even farther off, an invisible companion gave answer. Sikarios paused, careful to keep his tail from drooping to the muck of the road, and pulled his cloak tighter with his free hand. To the weary marten, the night's chill had teeth as sharp as any prowling beast. Months of winter rain had left mountain streams pregnant with bubbling snowmelt, and the feet of a thousand passersby had churned the once-sturdy highways to muck and mire, leaving his pads raw and aching. He had traded his finer clothes for thick traveling garb in a small village a few leagues outside of Aigos, now regretting that he had not bartered for a bristle-boar pelt or a hat of lynx fur.

Trudging on, the marten strained his ears for the telltale trickle of a brook, then hunted the free-flowing water down to slake his thirst and wash his muddied feet. Afterwards he let his canteen drink its fill. The moon was a bronzed sickle in the sky, like a shield battered and sundered. Sikarios settled down against a cold granite outcrop, studying it. In his heart, the marten knew he should press on, should claw as much distance as possible between himself and the battlefield that had rent his heart and damned his soul. But where was he to go that his sins would not follow him? Even if he were to slog his way up the coastline of the Adriatik, to seek employment in Istria or try for the wilderness beyond it, the shade of Alexios would still find him every time he lay down to sleep.

At the thought of his brother, Sikarios raised a trembling paw to the wound over his left eye, running his claws over the still-tender trio of gouges carved from his flesh. They were far from the only marks marring his body, but the rest had been cloaked by fur, a hidden map charting the course of these last four years. His mother had once compared the tinge of his pelt to cherry wood, but when he looked at it now he could not help but see dried blood. At least time had erased those wounds from the reach of wandering eyes.

The scars over his eye had never healed so; the fur there had grown back in a frail grey where it had done so at all, leaving him marked before gods and kounavi. As if he even deserved to be counted among his own people anymore. He could be named many things---Degenerate, Oathbreaker, Kinslayer---but not one of \emph{them}. His father had lost two sons that day.

A scattering of pebbles clattered over his resting form, and Sikarios stumbled to his feet. He didn't even recall drawing his kopis; the short, curved blade burned softly in the moonlight, eager for blood. As the marten scoured the darkness with his good eye, the prior four years washed over him in a tide of burning, vivid clarity: he heard the tread of a thousand boots over the charred and torn Morrean soil, and felt the blood of a dear friend quench the fire in his own heart as the nearby Aegean churned and spat in indifference. When the ash cleared to reveal a sprawling starscape, and the tortured face of his companion bled into the shadows of the torchlit crags before him, each breath was its own fresh battle. Sikarios staggered back, slipping to the grass, the blades still glistening with the leavings of the evening's rainstorm.

The rugged hill country lay silent around him. The gods, too, were silent, as they had always been. Sikarios drew breaths deep and steady as the ocean waves, like his mother had taught him a lifetime ago, and her words whispered through the years on the nightly breeze. \emph{You are stronger than you know}.

The trebled yap of a jackal-dog shook him back to the present. The creature was close, and their kind seldom traveled alone. The crafty mongrels who roamed the wilds of Epirus stood more than half the height of the average kounavi; even a marten would be hard-pressed to fight one off alone. Trusting that the burning light of his torch would prove more help than hindrance, he stumbled upright and wound his way among the rocks, seeking shelter. The cries continued to sound, and the thrill of being hunted washed the festering guilt from his mind like vinegar pressed to a fresh wound---a welcome sting, a reminder that he was still alive. He soon found a cave set into the side of a small hill, his fire throwing sharp shadows into the earthen recesses. Before he could investigate further, the marten's ears caught the telltale scuff of paws padding over dirt.

He whirled, thrusting the torch forward and drawing his kopis once more, this time with the practiced whisk of a warrior. Beyond the gaping mouth of the cave, a pair of golden eyes lurked within a shifting shadow. Savage teeth caught the firelight as the beast drew nearer, shedding the black of night for a patchwork of tawny fur with hints of russet and silver. A predatory spark gleamed in its eyes, that of one vagabond beast to another. Sikarios had seen jackal-dogs before, but never this close; from here the creature reminded him of the foxes his father's shepherds had fielded to guard their flocks, only twice as large and with a slender tail sharpened to a dagger's tip. He tried to picture his smaller kin standing before one of the canids: a mink or a weasel, perhaps a stoat from the northern forests or a polecat of the wandering clans. Herders were wise to fear them so, but the lone beast's efforts would be wasted here. With a final parting glance, and a strangely sly wrinkle of the face, the jackal-dog turned and slunk off into the night.

Sikarios watched for another few moments, just to be certain, before trudging deeper into the cave and laying down his traveling sack. He added his torch to a pile of dry wood, kindling a little flame in the earthen chamber and trying not to picture it as a tomb. As he huddled close to the low-burning tongues, doing his best to enjoy a meal of stale bread and an overripe apple he had salvaged from a flock of greedy magpies, his eyes returned to the far wall of the cave.

The shadows that had first drawn his attention were not shadows at all, but paintings: figures and beasts in black and carmine and ochre, a story stained into the very rock. Gritting through the final bite of bread, Sikarios forced his aching body upright and approached. The renderings were crude but easy to decipher; following the tale from left to right, he saw flames descend in strokes of white and orange, and from the ashes of the World Before, the familiar forms of his own people rising to inherit the earth. As he gazed at depictions of hunts and battles, seeing great beasts fall and heroes triumph, he wondered how long ago this must have been painted, if the marten or weasel who had dragged his claws over the rockface had seen the mighty cities of the Ancient Ones with his own eyes. And at the end of the tale, he found a hundred pawprints pressed into the stone, all a deep crimson, radiating outward from a central mark, like stars around the moon. He raised his own to the ghostly trace of his anonymous ancestor.

But when he pressed his pad to the mark, his paws were still slick with the blood of his brother, enough to paint every one of his sins upon the cold stone. The scars over his eye burned once more, and Sikarios turned from the mural, feeling suddenly unworthy to stand in its presence, to feel even a drop of kinship with this long-dead clan. He returned to the fire, and his worn cloth sack, rummaging through his few remaining possessions. Beneath a smaller pouch, heavy with three drachma and a pawful of obols, the marten found what he was looking for: a slender knife and a block of wood.

When he strained his eyes, Sikarios could see the lion lurking within the silver birch, waiting to be unleashed. Briefly he tried to recall the one Elias had carved, but seeking the memory was like probing an aching tooth with his tongue. Wincing, he set his mind to the present task, and began to steadily whittle away at the mane. He took little note of the fire's dwindling. By the time a majestic leonine face had emerged from the wood, drawn forth by fingers now trembling in the dark, the flames huddled close to the embers, like a mother eagle shielding her fledglings. Fearing what sleep would bring, and yet knowing that his body needed rest, Sikarios tenderly tucked the carving away before drawing his cloak tighter and laying his head upon the sack.

Sleep came quickly, and when it did, as always, he dreamt of his brothers: the one he had buried, and the one he knew was coming to bury him.

\secdiv

\noindent In his dreams he was young once more, loping through fields gilded with wild wheat as the first hints of autumn stirred on the breeze. His brothers were with him, and his family was still whole; Kyrios, the stalwart firstborn, led the way with a stick raised high, charging ranks of invisible foes as Sikarios and Alexios raced behind. The low walls of Nalanthis stood just beyond the tree line, calm and quiet in the shadow of the acropolis, from which their noble father ruled and their mother bore all the world's love in her breast. When their younger brother stumbled, Kyrios was there to help him up, and when Sikarios scraped his arm after falling from an oak, Kyrios found a patch of aloi to temper the wound's sting. He relived their expedition to the summit of Mount Nikthis: poor Alexi, legs still hobbled by youth, staggering the final league of the journey as their older brother sought out a cool-flowing mountain stream. Elias had come along that day, as he often did, and Sikarios and his friend had lingered near a ledge, choosing stones to hurl into a sky as vivid as the tourmaline necklace his mother was so fond of, listening and laughing as the rocks clattered their way down the slopes.

The memory of Elias' fur catching the evening light, the kine's amber coat bronzed with the lifeblood of summer, was like a knife through his heart. Slowly, the sorrow dredged Sikarios from the depths of the dream, and the marten awoke to find himself back in the cave. When he turned, a pair of vulpine eyes were peering into his own down a pointed snout.

Sikarios straightened, but at the first shift of his paw the fox snarled, then yapped sharply. The warning bark brought back a brief yet vivid memory of trespassing through a pasture with a pack of other young kines, the angry shouts of the shepherd following at their heels. It took the marten a moment to realize that he \emph{was} hearing voices---only those of kits, whispering from somewhere beyond the snarling fox. A kine and a doe, he was fairly certain. Straining his ears, Sikarios began to catch words from the murmuring.

``\ldots{} told you he wasn't dead.'' That was the doe.

``Maybe he's a dhampir,'' the kine shot back.

``Quiet! I think he's waking up.''

The fox sniffed tentatively, then scampered back to the mouth of the cave when the marten heaved himself upright. ``I'm not dead,'' he called to the silhouettes peering in from the wall of light. It had been several days since he had heard his own voice; the sound was harsher than he remembered, raspier. Sikarios shaded his eyes, then gathered his belongings and staggered forward. He heard the pair scurry out of his way.

The late-morning light, trapped and mirrored beneath a covering of thick, pale grey clouds, left him momentarily blinded. Rubbing his eyes, the marten took in the landscape, and found two young weasels standing a few paces away, watching him with bated breath and wary gazes. Each wore a loose-fitting cloth tunic, their feet clad in sandals. The kine, glaring from beneath a broad-brimmed hat, dangled a sling loosely from one paw, while the doe, standing a full head taller, had her claws wrapped tightly around a hooked staff. The vixen, nearly coming to the doe's waist, stood attentively between them, russet fur bristling, joined by a larger fox with a patchy black-and-white coat. Both bared their fangs in silence.

``Stay back!'' the kine shouted, sling hand twitching. The doe hunched slightly, as if she were ready to crack Sikarios over the head. The marten raised his hands slowly, fingers splayed, pads outward. At least they still spoke Elladian here.

``I mean no harm to either of you, or your flock. I was merely passing through, and sought shelter for the night. If I have trespassed upon your land, I---''

A bestial shriek cut his words short, and all three kounavi shifted their attention east, to the shade of the tree line. The larger fox took off at once, leaving the two weasels and the vixen to glance back to him before a second shrill cry drew them as well.

Burying his curiosity, Sikarios made for the road, only for a shout to stop him. Even from a distance, he recognized the fear in the kit's voice. He turned, letting his eyes follow the path the weasels had taken. \emph{Nothing to concern yourself over}, the marten told himself. After all the world had burdened him with, all it had taken from him, what could he possibly owe it? Nothing he did could ever change the past, and if the gods could not be bothered to set things right, why should he?

But when Sikarios turned back to the road, a sense of dereliction churned in his gut with every step. He halted again, let out a weary breath, and trotted after the kits. Following their tracks through a ridge thick with trees, the marten clawed his way out onto open range. A dozen sheep heavy and bloated with wool clustered nearby. He caught sight of the weasels at the far end of the pasture, and a moment later noticed the black shapes circling overhead like shades loosed from the underworld.

By the time he reached the kits, the kine had already launched several stones at the razor-hawks, while the doe stood swinging her crook, attempting to keep the flock from the wounded ewe. The foxes snarled and barked, snapping whenever one of the raptors drew too near, the scent of their fear sizzling on the air. Some of the birds had lighted on the nearby trees, while others continued to slice through the air, veering in only to sweep away.

Sikarios knew all too well what a pack of razor-hawks could do even to a grown kounavi. Racing to the stricken sheep, he drew his kopis and shouted. Dagger-sharp talons strangled branches in anticipation of the kill, and eyes rich with murderous desire shifted to focus on his ragged form. The scars over his eye burned with the memory of violence.

``Keep close to me!'' he shouted at the weasels. The pair shared a glance before hurrying to his side. Sikarios had hoped that the pack would flee, but the raptors were aflame with the blood they had already drawn. He lowered his voice. ``Good kits. Now, when they rush in, do not break---that's what they want. Stand your ground, and never falter.'' \emph{His brother's words}, a distant part of him remembered. From the corner of his eye, he saw the kine cock his head, eyes narrowing. The doe---his sister, Sikarios figured---nudged him roughly.

Two of the razor-hawks launched from their perches, catching the wind with feathers splayed. Sikarios steadied himself. But as they swept down, one of the birds tumbled from the sky, thudding to the earth with white plumage spouting from its breast. The other raptors veered sharply for the cover of the trees, and the trio turned to see a figure striding toward them across the meadow, a slender bow grasped firmly and another arrow already nocked. The marten finally let himself draw a normal breath, shuddering as he slunk to the welcoming coolness of the grass.

``Have you fought razor-hawks before?'' the doe asked, still clutching her crook so tightly it looked about to snap.

Sikarios drew several more breaths, then looked to her. ``I've seen my share of bloodshed.''

``Father!'' the kine cried, waving his paws wildly. The approaching figure quickened his pace, and Sikarios turned his attention to the prize that had drawn the ravening pack. The young ewe lay on her side, chest rising and falling with labored breaths, her white neck stained with carmine. Sikarios ran his fingers over her flesh, searching out the wound, feeling the beast shudder as his claws traced the gash. He looked up to find the doe staring at him.

``What's your name?'' he asked.

``\ldots{} Uh\ldots{} Aeda.'' Her voice was shaking almost as much as his own paws.

``And him?'' Sikarios inclined his head.

``That's Mylo, my---my brother.'' As she answered, their father arrived, and the marten rose to meet him. The new kine was a weasel like them, much older than Sikarios himself, sharing the golden-brown pelts of his offspring, only speckled with stony grey. The cream-colored fur of his chin and neck made the marten think of the one time he had seen snowfall. The grown weasel, slender in the manner of his kind, barely came up to Sikarios' neck, and he found himself suddenly conscious of how he must look to these poor shepherds, scarred and disheveled, with the wild eyes of a fugitive, armed with a blade likely worth more than their entire flock. The older weasel whistled sharply, and the two foxes bounded off toward the rest of the sheep. The marten whirled back to the wounded animal and stooped to his knees.

``We need yarrow,'' he said, trying his best to sound like his father, as if calm command were his birthright. He turned to the kits. ``You know what that is?'' The doe nodded, though her eyes were uncertain. ``You may know it as woundwort, or staunchweed,'' he explained, shifting his gaze back to the ewe. ``Green stem and serrated leaves, with clumps of small white-petaled flowers around golden seeds. Grows in high, dry places with ample sunlight.'' He retrieved his canteen, then tore a strip of cloth from the rags in his sack. When he looked back up, the kits were still staring at him. ``You should be able to find some nearby.''

The two scampered off, leaving their father to watch this strange marten tend to his livestock. Sikarios saw the kine's shadow fall across him, and scooted over for the smaller kounavi to join him.

``I am Tamyris,'' the stranger said. Sikarios merely nodded, and the weasel cleared his throat. ``Thank you for your aid. I have never known a razor-hawk pack to be so brazen, especially not this close to town.''

Sikarios nearly mentioned that the raptors who haunted battlefields often grew quite bold after gorging themselves on corpses. That there was a small gap between the dead and the dying, and only a slightly larger leap from that to preying on the able-bodied. Instead, he simply asked, ``And what town might that be?''

``Dalma,'' the kine said, pointing to the northwest. ``It lies about half a league that way.'' He spoke Elladian without flaw, though his rugged Illyrian accent churned his words like a plow turning rich soil. ``You\ldots{} have some knowledge of medicine, marten?'' Sikarios caught the slightest hesitation before the final word, a cautious probing.

``Enough to help here, at least.'' The patter of sandals echoed from the tree line, and a moment later Mylo and Aeda reappeared, each clutching a pawful of yarrow as if it were jewelry. ``This will be plenty,'' he said, spitting into his own paws before gently kneading the flowers into a pulpy paste. The ewe winced when he daubed it on her wound, but did not cry out. ``She should be fine,'' he said, running his claws delicately through her clumpy winter coat, ``so long as you continue to apply that daily, until the wound seals. Let's help her up.''

Together the four kounavi guided the ewe upright, grunting as her cloven hooves fought for footing. From there it was a short walk back to their cottage, where the foxes stood vigilant as the rest of the flock crowded into a cobblestone pen. The kits hurried forward to meet their faithful companions.

``Oh, \emph{Pyrra},'' Aeda crooned, kneeling to ruffle the fur of the russet vixen. ``And Kokkin, good Kokkin,'' she added, turning to pat the dog fox before he whirled to lick Mylo's muzzle. Sikarios could not help but smile at the sight. After the injured ewe had been reunited with her flock, and the gate securely set over the thatch-roofed pen, the four kounavi retired to the cottage for a lunch of dried fish, legumes, bread, and cheese. To the marten's surprise, the family washed their meal down with milk rather than water or wine, a barbarian custom he had heard rumors of from youth. Above the doorway hung a crude wooden rendition of a weasel with a bow, poised to strike down some unseen wild beast: Iluvex, goddess of the wilds, an import from Sikarios' homeland. Here, on the fringes of the Elladene, he suspected they would know her by another name.

The four ate in silence, and Sikarios felt his presence as a weight around their necks, growing heavier with each passing moment, with each question left unasked. The young kine, Mylo, was the first to speak.

``So\ldots{} where'd you get that scar?'' he asked, the innocence in his voice underscored by a touch of awe. The marten froze as if a knife had been pressed to his throat. He heard his brother's voice, \emph{I won't let you}, felt the dagger clatter from his blood-slicked paw. Saw the eyes he had known all his life staring back at him in shock and horror as the light trickled from them into the shadows of the tent. His nostrils filled with the scents of iron and fear and betrayal.

He jumped as a paw clutched at his tunic, finding himself back in the cottage, the doe watching him as if he were a wild jackal-dog. He swallowed, blinking rapidly, and cleared his throat.

``I\ldots'' Words trickled through his grasp like water. Tamyris cut in.

``There's no need to pry, son.'' He set a firm paw on the kine's shoulder, turning his gaze slowly to their guest. ``By the look of things, you've been on the road for quite some time, stranger.'' As before, he stressed the final word, curving it up slightly, almost making it a question.

``Meletos,'' the marten said, hoping to keep the quaver from his voice. ``And yes, I've---it's been quite some time. I\ldots{} I have a long journey ahead of me.''

The weasel met his gaze coolly from across the table, then drew in a deep breath and exhaled slowly, folding his hands over his stomach. ``Kits, could you check on the animals?'' He turned to his daughter. ``Just to make sure they're all settled in nicely.''

``But we just---'' Mylo's protest was cut short by his sister.

``Of course, father.'' She ushered her brother out the door, shooting a lingering glance at Sikarios before closing it firmly behind her.

Tamyris held his gaze, then straightened in his chair. ``We truly are indebted to you for your help today,'' he began, before storm clouds of worry drifted behind his eyes. ``But I know when a kine is running from something.'' Sikarios opened his mouth to speak, but the weasel forestalled him with the wave of a paw. ``Don't worry---I don't mean to ask any questions you aren't prepared to answer\ldots{}\emph{Meleos}, was it?''

The marten nodded absently. His host lifted a paw, running his claws through the cream-colored tufts beneath his jaw.

``Well, we are gods-fearing folk, and by rights we will offer you what hospitality we can reasonably spare. And I can tell you are no common brigand.'' He nodded to the sheath propped against the wall, beneath Sikarios' cloak. ``You could've already accosted us and been on your way, were you so inclined. What I mean to say is\ldots{} I just want your assurance that whatever trouble it is you're running from, you won't pass it on to anyone here. Not the townsfolk, not myself\ldots'' He trailed off briefly, and for a moment his eyes smoldered like the noonday sun. ``And most importantly, not my kits.''

Sikarios had stared death in the face, had looked into the eyes of a kine prepared to kill enough times to recognize that same readiness here. His mind wandered over questions he knew needed asking: \emph{How long could he afford to linger here? Was it truly wise to stay for even a single night?} \emph{Should he merely push on to Istria?} But he was tired, so tired. Brushing his doubts aside, the marten nodded again, more sharply. ``I was just hoping for a place to rest for a few days, that's all. Whatever needs doing, I can earn my keep, and then I'll be moving on.'' He raised his paws. ``Like I wasn't even here. You have my word.''

Tamyris' eyes slid down to the table. He was quiet a long time. ``I could pay, if you'd prefer,'' Sikarios added hesitantly, trusting the weasel's rugged rural pride to decline for him. ``I don't have much, but---''

``A bit of labor will suffice. Nothing too strenuous, I assure you.'' The older kine's gentle smile thrust him back to the days of his youth; it was strange how the slender weasel could in that moment look so much like the father he had once known.

``Thank you,'' the marten whispered, feeling a millstone lift from his chest. He offered a silent prayer of thanksgiving to Pallas Milosha, Lady of Wisdom, his former patron. It was the first in months, and despite the fear festering deep within his heart---that the gods had forsaken him, that the best he could hope for was to avoid their notice altogether---Sikarios could not deny he felt a flicker of solace.

\secdiv

\noindent The rest of the day passed quickly, a flurry of mundane tasks that drained the hours until dusk crept up from the eastern depths as an indigo haze. The razor-hawks did not dare show themselves again within range of Tamyris' deadly bow, and under the shepherds' watchful eyes the flock returned to the meadow to graze contentedly. When nightfall came and the sheep had been safely ushered back to their pen, the four retired to the cottage once more for supper.

After a meal of salted fish, grapes, and olives, Tamyris turned to his children. ``Meletos here will be staying with us for a few days.'' Mylo sat straighter at once, the kine's bright blues eyes tinged with reverent curiosity. Aeda simply said, ``Should I make room for him in here?'' She looked to the doorway, to the only other room in the cottage.

Sikarios cleared his throat. ``I can sleep in this room---I wouldn't want to impose any more than I already have.''

Tamyris nodded. ``If you have need of anything, do not hesitate to ask.''

Later, when the three weasels had retired to their sleeping quarters, Sikarios spread his cloak in the corner and stretched out, enjoying the simple luxury of secure walls and a sturdy roof. The gentle rhythmic breathing of the kits soon drifted to his ears from the other room, a comfort the marten had not realized he had so dearly missed. Somewhere beyond the mud-brick exterior of the cottage, the ghostly cry of an owl danced through the night. He let the strangely familiar environment draw him back, back to the days of his youth, when the world had made sense. And once more, he thought of Elias.

After years of youthful friendship, their shared fondness had given way to something more, something deeper. Sikarios had been frightened at first---they both had, fumbling for each other in the darkness as the autumn winds wound through the halls of his father's palace---but beneath the anxiety and peculiar, nameless shame he had found joy, and warmth beyond measure to brace himself against the cold of night. Familiarity soon smoothed the edges of their fear; the halcyon days had melted into one another, a time without true endings, where every parting was brief and every dusk promised a brighter dawn. Their bond had been like a secret fire, always in danger of being doused by an interloper or clumsy passerby, and yet all the more cherished for that vulnerability. But like all secrets, it could not hope to endure forever.

With a shudder, Sikarios recalled the night he had left the warmth of their bed to find his younger brother frozen in the hallway, eyes wide with shock and revulsion. Alexios had stared at his outstretched paw as if it were a burning brand.

``Alexi, please, wait.'' His desperate pleas washed over the young kine like sea spray against granite. ``Listen to me, \emph{please},'' he said, lowering his voice, crouching down, wishing that the darkness could swallow him. ``Please, don't tell anyone. Not father, not mother, not Kyrios or anyone. Can you promise me?'' he asked, holding out his own paw once more, palm up, like a supplicant begging his liege lord. Tenderly, he clasped his brother's paw, hating the way the kine winced. ``Promise me you won't tell anyone else?''

Alexi had closed his eyes slowly and nodded, his voice fragile as a shaft of moonlight. ``I promise.'' On the other side of the wall, Elias had shifted in his sleep, still blissfully oblivious. The thought had made his heart ache. It still did, all these years later.

At the time, Sikarios had believed their secret to be safe. He recognized the truth only with hindsight: that it was a splinter from an arrowhead lodged deep within the beating heart of his family, cloaked from the eye and yet slowly festering, year by year. If only he had known then what he did now, lying beneath a stranger's roof, having donned a stranger's name. If only.

Tamyris and his family slept soundly only paces away, and the marten found a part of himself wishing that the life of a prince could be traded for something as simple and honest as theirs. By reflex his paw sought another, and found only empty air.

\secdiv

\noindent Sikarios awoke well before daybreak, the memories that had shepherded him into sleep still swirling behind his eyes. The cottage lay in the peaceful almost-silence of pre-dawn darkness. As his body livened, preparing to face another day, the marten dug through his sack and once more retrieved the block of silver birch, a lion's face now showing clearly. With the aid of the knife, his fingers freed more of the beast, wood melting away to reveal the back and chest. The work was strangely calming; his mind emptied of everything else as shaving after shaving drifted into his lap. By the time his ears caught the first stirrings of his host family, he had begun to shape the lion's mighty legs.

Scooping the wood shavings into a paw, he stepped into the twilight and let them drift away on the chill breeze before returning to help with breakfast. The children prepared a meal of tagenites, a kind of pancake consisting of wheat flour, olive oil, and curdled milk, topped with goat's cheese and drizzled in honey. As they worked, Tamyris showed Sikarios to the nearest well, located on the borders of their farm and shared by their neighbors, a family of goatherds. The sheep pen lay quiet as they trotted past, the occasion muffled bleat echoing from beneath the thatch roof. Aside from that, the farm contained a small shed and a chicken coop surrounded by a low fence.

After drawing two buckets of water from the well, the pair returned to the cottage, where the scent of crackling pastries sizzled on the air, a smell of spring mornings and easy laughter. Watching the steady, measured bites of his hosts, Sikarios had to stay the temptation to devour his own meal like a starving jackal-dog. This time, however, they did not eat in silence; Tamyris, chewing around a mouthful of the cake, walked his guest through the routine he would be learning.

In addition to sixteen head of sheep, and two foxes to aid in watching over them, the family possessed a good two dozen chickens. Several of his ewes were pregnant, though none would give birth until later in the winter, leaving the family dependent on barter for milk, and on the eggs of his other livestock for the material with which to do so. ``We've considered acquiring a goat or two,'' he told Sikarios, ``but with only three of us to watch over everything, we've got our paws full as it is, eh?'' The marten chewed and nodded silently, watching the kits' faces for the telltale flashes of grief; every death leaves its mark in the world of the living, a gap in the light of the sun, a hole through the heart of a family, and that of a mother most of all. He knew that as well as anyone. But Mylo and Aeda simply carried on with their meal, as if their sorrow had long-since clotted and scabbed over, leaving a deadened callus to greet any mention of her absence.

The marten's eyes wandered to the shrine in the corner, a regular feature of any household---only upon this one, beside the icons of other gods and clusters of candles and prayer-beads, stood a little figurine of a raven, messenger of Mirod, the god of death. When his gaze focused on the little clay corvid, he noticed the flower resting in its shadow, a blue chrysanthemum, like a piece of the night sky carved out by the family's loss. \emph{I'm sorry to hear about her}, he wanted to say, \emph{I know what it's like}, and \emph{She knows how much you loved her} floating behind the words. But Tamyris had fallen quiet, a pensive expression on the weasel's face, and Sikarios could not bring himself to pry open old wounds, of another or himself. The meal concluded in silence.

From there it was on to the daily tasks of farm life: Mylo distributed chicken feed and collected eggs as the others, Sikarios included, led the sheep out to pasture, while Pyrra and Kokkin ran yapping and yikkering around their hooves. The hours passed languidly as the sheep milled about beneath a clear sky, rich with clouds as white and fluffed as their overgrown coats.

Aeda returned to the cottage to prepare lunch, and Sikarios helped her bring the food to the others. They ate atop a cloth spread over grass still speckled with dew. A yellowhammer swooped by like a flash of sunlight, vanishing into the trees; the bark of a distant fox roused the ears of Pyrra and Kokkin, then was quickly forgotten. The pair loped across the meadow, ushering two bolder rams back to the safety of the flock.

``Would you care to see our humble town?'' Tamyris asked, turning to his guest. He had donned a wide-brimmed straw hat much like the one his son wore, while Aeda had her own head wrapped in loose white cloth. ``Mylo is going to be heading into the market later.''

The marten found himself strangely curious. He nodded. ``I'd be happy to.'' Their meal concluded, he helped the young kine bring their wooden bowls and plates back to the cottage, where his kopis rested by the doorway beneath his cloak, secure in its sheath. Sikarios reached for the weapon, then hesitated, fearful of being caught unarmed, yet knowing it was bound to draw attention. His paw hovered before the hilt, then reached up to swipe the cloak off its hook, leaving the iron in the cool darkness of his host's home.

Dalma, as the marten discovered that afternoon, was a rather unremarkable settlement, barely more than a village clustered around a central square, in turn surrounded by farmsteads, all nestled within hill country well suited to raising sheep and goats. The sea lay slightly under a league from the town; on calm nights, a keen-eared kounavi could hear the heave of the Adriatik as it hurled wave after wave against the rocky shoreline. Rather than a river, the inhabitants of Dalma had access to a shallow brook that snaked its way down from the rugged eastern wilderness, bearing pure, life-giving water as it raced northwest in search of the sea. The town itself wasn't significant enough to warrant a proper lord, Mylo explained, but one wealthy farmer, a mink by the name of Berychis, loomed large in civic functions. It was one of his many daughters who had assumed the role of sofianthe, tending to the local shrine and overseeing public rituals on holidays.

``Her name's Mira,'' the young kine said, letting the syllables drip from his tongue like honey, ``and she's the most beautiful doe I ever seen.'' He swayed on his feet, staring up into the pale blue sky as the two trotted down the main road. ``\,`Course she can't marry, being a sofianthe and all,'' he added with a sigh, ``but still\ldots''

Sikarios smiled at the thought of young love, or what a young mind might think passed for it. The gods only knew how hard they could be to distinguish. He thought again of those long nights with Elias: their clumsy, fumbling forays into romance, after the initial hesitancy and uncertainty had been washed away in blessed reciprocation, but before his brother's discovery threatened to sever the ties that bound them.

``Come on,'' he said, nudging the young kine affably, ``there's got to be a doe you fancy around your age.''

Mylo shrugged, pausing to kick at a rock, scuffing his sandals in the dirt. ``Well, there's Lylla---she lives in the farm beyond our neighbors'.'' His shoulders sagged. ``But I heard from the other kines in town that Andris and Egnat have both been visiting her.''

``Is she fond of you, do you think?''

Mylo's face brightened, and he nodded eagerly, tail swinging through the dust his feet kicked up. ``Last time I saw her, she told me---'' An embarrassed grin crept over his face. ``Well, I think she likes me enough.''

The marten tried his best to echo his own mother's memory, the advice he recalled her giving his lovesick brother when Kyrios had been pining after the daughter of an officer. ``Then go and speak to her, and tell her how you feel. Let her know where your heart lies, without seeming overeager.''

Mylo's face grew thoughtful. It was advice he should have been able to hear from his own mother, Sikarios considered; the thought drew black clouds over his own heart, and yet an untroubled joy still sparkled in the little kine's gaze at every turn. The marten found himself torn between relief and envy.

After a moment, the young weasel looked up at him. ``You must know a lot about the world, mister, being so old and all.'' Sikarios furrowed his brow, but the kine's eyes were clear and innocent, and the sting of offense melted into amusement.

The marten forced himself to chuckle. ``How old do you think I am?''

``I dunno, maybe\ldots'' Mylo squinted, cocking his head. He turned to walk backwards, paws clasped behind him. ``Maybe 35?''

This brought genuine laughter. ``How old are you?''

``I'll be thirteen this spring.''

``Then I am not even twice your age.'' The kine gaped, and Sikarios nodded. ``I am just shy of twenty-three.'' \emph{Though the gods know I look older}, he thought, gently fingering the contours of his scars, feeling the weight of his past bearing down upon him.

Mylo seemed to sense his unease. ``Don't worry mister, Aeda says you're still handsome in a way, like the soldiers who come through last summer.'' He halted, grimacing. ``Please, don't tell her I told you.'' Sikarios chuckled softly. ``Besides, she's got eyes for Gallas, not that she'd admit it,'' the weasel added, sticking his tongue out. ``His father's a leatherworker in town. She's 14, so she'll be pairing off soon enough.''

By then the conversation had brought them into town, a collection of wooden-framed mud-brick houses, the fraying straw of their thatch rooves bristling like pelts in the sea breeze. As they neared the central square, heading for the market, he spotted a trio of polecats haggling with a local over some bauble; the strange kounavi, with their spiked, sable fur showing patches of sickly ochre, chittered amongst themselves in their alien tongue, distinctive crimson coifs clinging to their heads. The wary mink they bartered with waited in silence. Mylo stiffened as they passed the group, putting the marten between himself and the members of the wandering clans. Despite his own misgivings about polecats, bred from generations of mutual mistrust and hardened through his princely upbringing, Sikarios could not help but feel a stab of guilt at how the townsfolk shot them glances laden with disdain and suspicion while he could stroll freely, even marked as he was.

Farther in, where kounavi of all types bartered and haggled amidst the bustle of the market, his ears caught the familiar ring of a blacksmith's hammer. Trusting Mylo to seek out what was needed and find him later, Sikarios followed the sound. In the shade of a wooden overhang, surrounded by scraps of metal and half-assembled tools, stood a peculiar creature: short and grey-furred, with a vulpine face and a bushy tail ringed in black. \emph{A prokyon.}

Of all the kisenos, his people's term for members of the non-kouvani races, prokyons were the most common in Epirus---behind otters, of course. But where the latter were tall and sleek, traveling the continent's waterways and plying the currents of the Great Sea, and otherwise sticking to their own riverine fishing settlements, the former were stocky, ring-tailed forest-dwellers, known for their dexterous fingers. Among their people, it was customary for skilled families to seek employment in the cities of the Elladene, passing on the secrets of their trade from generation to generation. Sikarios' father had retained one in Nalanthis---Brennix, his name was, a taciturn creature, his thoughts always concealed behind those small, black, ever-watchful eyes. Growing up in Nalanthis, he had encountered far more than just kouvani: sandy-haired mankous from the jungles of Afrika, speckle-coated mardun of the northern taiga, even black-furred, thick-limbed viverrid traders from far east of the Indus. But while the sight of kisenos in larger towns and cities throughout the Elladene was common, to find one here was surprising.

The smith hammered delicately at something laid atop his forge, then wiped a dark paw across his ashen fur before glancing up and flashing a smile. Sikarios stepped nearer, watching as the prokyon set down the iron blade and fetched a bronze hilt. He held them up to his beady eyes, testing the fit before setting the blade aside.

``Do you require something?'' he asked, his Elladian gently flavored with the earthy tones of the northern forests.

``I just\ldots{} I am surprised to find one of your people here,'' Sikarios replied, ``in such a small town.'' The marten raised a paw. ``I do not mean to cause offense---''

The prokyon chuckled softly, retrieving a chisel-like tool and shaping the hilt. ``We can't all find employ in great cities, or the estates of mighty lords. And after all, even small towns need blacksmiths.'' He met the marten's gaze with a wink.

``Catharix,'' a voice called from across the street. Sikarios craned his neck to see a marten and two weasels approaching. The prokyon waved to them, brushing shavings from the bronze hilt.

``Still working on Berychis' sword?'' the other marten asked. His companions smirked, and Catharix nodded.

``He figures one of his sons may soon enlist.''

``The gods know the old bastard has enough to spare,'' one of the weasels snickered. His laughter spread through the crowd, and Sikarios felt a stranger among them. The other weasel's eyes flitted to him, his slender face hardening when they met the greyed fur and naked flesh of his scars.

Sikarios forced himself not to shy from the other's gaze. The weasel balked first, turning to Catharix. ``Did you hear ol' Thestor is looking to our own lands for recruits now, for the campaign in the Morrea? They're saying he'll try for Haikoth again this coming spring.''

Sikarios blanched at the familiar names: Thestor, King of Makketon, the mightiest kounavi in the Elladene, to whom his own father owed fealty. The Morrea, the land he had spent the last four years ravaging and bleeding over. Haikoth, the city that had broken him as it had broken so many armies against its walls. The city that had torn Elias from his breast. The city he had fled from, leaving the brother who had tried to stop him cold upon the blackened soil.

The others had continued without noticing, and he drifted back to the present to find them debating the foreign king's plans. Thestor's Makketonian League had warred with a coalition of rival cities for four long years, rending the Elladene and drenching its soil with the blood of countless fathers and sons, brothers and husbands. Tyrene, the coastal Anatolian republic, had led the resistance; with the fall of Haikoth they would stand nearly alone.

Of course, much of this was lost on a group of Illyrian farmers dwelling dozens of leagues from the nearest battlefield. Some of the rulers of the region's petty kingdoms might swear fealty to one side or another, but the war had, so far, left the hilly country untouched. As the three kounavi argued good-naturedly, and the prokyon's nimble fingers worked over the bronze hilt and a pair of gems meant for inlaying, Mylo skipped over to Sikarios' side.

``Hullo Gento,'' the young kine said cheerfully.

``Hullo Mylo,'' the other marten replied, then lowered his voice. ``So you're responsible for bringing this vagabond into town?'' He flashed a toothy smirk.

``This is Meletos, he's visiting with us. He saved an ewe from a pack of razor-hawks yesterday! And he has a sword!''

Four pairs of eyes centered on Sikarios, narrowing slightly.

``A sword, eh?'' One of the weasels said.

``I, um---I'm travelling\ldots'' the marten muttered, ``to see family in Istria. And with the war, the roads have been dangerous.'' As an uneasy silence settled over the crowd, Sikarios noticed the trio of polecats trotting past, and like foxes abandoning a scrap of bread for a slab of veal, the locals' shared suspicion leapt at the new target. Suddenly the marten was one of them.

One of the weasels spat and jutted his chin. ``Best you keep an eye on that lot.''

``There's too many strange folk passing through here of late,'' Gento said, as if he had forgotten Sikarios were standing right next to him. ``Remember those Saarenians, come through last week, or the week before? Heading for the Morrea, I figure, same as all the other vultures.'' Through all of the talk of outsiders, Catharix had kept silent. Sikarios could see the faintest flicker of fear in his small black eyes, knowing that the flame of mistrust could just as easily catch on him.

It was Mylo's innocence that broke the unease. ``Is there any news about the war?''

``Why,'' Gento asked back, ``thinking about joining up?'' He let out a deep, paternal laugh. ``I don't think they take `em so young, lad. Give it a few years, you'll get your chance at glory.''

Sikarios did not share their laughter. He knew that the army would take kines as young as Mylo as runners and aides; he also knew how easy it was for those very same kits to find themselves with a sling in hand, or pressed shoulder to shoulder in a phalanx when a desperate commander had need of all the bodies he could muster. The marten studied Mylo's face, watching as the young weasel followed news of the war with innocent eyes, dreaming of bloodless prestige. The thought of his body lying cold and broken in some far-off field made Sikarios want to dig his claws into his own flesh.

But they could not know who he was, who he \emph{truly} was. No one could. And so he held his tongue and bore his anguish in silence.

\secdiv

\noindent That evening, as the sheep grazed contentedly in the meadow under a sky stained with the fires of sunset, Sikarios once more returned to the carving. It was easy to lose himself in the pattern of the grain, the steady strokes of the knife keeping time with the beating of his heart. The lion had taken firm shape; all that remained was to free its legs from the remnants of the block the silver birch had once been. He drifted off, letting his fingers continue their work as his mind wandered back, to the summer of his sixteenth year. The storm clouds of war rumbling in every audience chamber, rumors abounding of the coming conflict. And he and Elias, both on the cusp of adulthood, eager to prove their worth, to win renown before gods and mortals, to carve for themselves a place in the storied halls of Elladian legend. Kyrios, the stalwart firstborn, had already been fitted for a suit of gleaming bronze armor, crested with a tuft of white bristle-boar hairs, and young Alexi, still wary around Sikarios, bounded through the halls of their home lancing invisible foes from atop an equally invisible mount.

They had lost their mother the year prior, and in his grief their father had taken closer counsel with King Thestor, whose firstborn had fallen to the Plague out of Parthus. Their plans of grand conquest had been birthed amidst tragedy; together they would make the world weep with them. As he sat on the hillside, his mind barely registering the grazing sheep, Sikarios remembered Elias racing across the field, eyes bright as the sun.

``You'll never believe it! I saw a \emph{lion}!'' The beasts were nigh-unheard of west of the Bospor, and yet the conviction in his friend's gaze was unshakeable. He had begun carving its likeness at once. ``For strength,'' he had said, clasping a paw in Sikarios'. ``If it does come to war. A charm to see us safely through.'' The marten's eyes watered at the memory.

``Meleos,'' a voice called, dragging him back to the sun-drenched knoll. Tamyris strode over, stabbing a crook into the soil. ``You are skilled with that,'' the weasel added when he did not answer, lifting a clawed finger at the carving knife.

``Thank you. I\ldots{} learned it from a close friend.'' Sikarios glanced up at the shepherd watching him with an arched brow.

``You know, it might be best to settle on one name.'' A smirk crept across the weasel's face. ``Meleos, Meletos---you've answered to both.'' He raised a paw. ``No, no, it's all right. Like I promised, I won't pry. There are plenty of reasons these days to guard something as precious as a name.'' He sat down, resting his back against the boulder. ``I'm just a shepherd, so I don't expect to have seen as much of the world as you, despite my age. But I am also a father,'' he said, laying a steady hand on the marten's shoulder, ``and my heart knows the sight of a young kine struggling.''

Sikarios couldn't bring himself to meet the weasel's eyes.

``The gods and fates weave tangled webs of our lives, but you don't have to face it alone. We have a sofianthe here, a rather beautiful mink, if the gods will pardon my saying it.'' He chuckled, but the laugh felt hollow, trickling away as he waited in vain for his companion to join in. ``Her name is Mira, and she lives in the hills to the northeast of town, in a little hovel by the shrine of Ilovek.'' His voice trembled, the faintest rumble of distant thunder. ``When we lost Bero to sickness, several years back, she helped me through my grief. She\ldots{} may be able to help you, too.''

Tamyris stood, groaning as his bony limbs stretched. He cleared his throat. ``It's almost time to bring the sheep in.'' The weasel started for the flock, but the marten's voice stopped him, turned him back.

``Sikarios.'' He let out a deep breath. ``My name is Sikarios.'' He tensed, waiting for the flash of recognition, the shock that would quickly sour into fear or revulsion. Instead, the weasel just smiled, mouthing the name silently with a nod.

\secdiv

\noindent A day passed, and then another, and Sikarios allowed himself to ease into the lull of the rugged hill country, so welcome after months of flight and years of blood and fire. Deep within his mind, a voice whispered warnings of his brother; he pictured Kyrios striding into town clad in bronze, burning like the sun. \emph{They would hate you if they knew}, the voice snarled. \emph{You do not deserve to share their peace. Leave, while you still can}.

And yet a part of him pined for the comfort of a home filled with laughter, wishing dearly that he could shed his past like an old skin, could bleed his lifeblood into the brook night by night until nothing remained of Sikarios the kinslayer, Sikarios the oathbreaker, until a new creature had taken his place: someone worthy of the shepherd family who had taken him in. There was an honor to this life, he reflected, equal to that of any warrior. His father would have laughed at the sight of him casting feed to chickens, or mending the gate to the flock's pen alongside Tamyris, but soldiers needed food and clothing as much as anyone else. And the paws of a farmer, of a shepherd or carpenter provided, where for years his own had done nothing but take. Perhaps a life of humble labor would be enough to earn forgiveness from the gods.

Perhaps a life like this would be worth fighting for. Worth dying for, even.

One crisp, clear morning, when the hearts of the townsfolk lightened with the first hints of spring, Sikarios joined the two young weasels on a venture into Dalma. The marten's kopis jostled against his leg from within its sheath; he had taken to wearing the blade on his forays into town, as if imitating the kine he was before might wash the guilt and dread of the prior months from his soul. A flock of starlings speckled the sky with their northward flight, and he glanced at the two kits trotting happily beside him: Aeda cradled a basket of eggs, while Mylo shaded his eyes and looked south.

``Kyto said he and his brother might join up, when the recruiters come.'' The kine's voice sizzled with excitement. ``A southerner passed through yesterday, said they were offering thirty drachma to anyone who fought, plus ten per month.'' Sikarios saw the weasel's eyes hungering at the thought of such a sum: a single drachma might feed a peasant for a week; a full thirty could purchase a plot of land and a few head of sheep or goats, perhaps even a pair of roe deer.

\emph{Your life is worth more than that}, the marten wanted to say. Instead, he asked, ``Do you know anyone who's fought before?''

Mylo nodded. ``Kyto's father fought before I was born, when the Kimmerians came down from the north. They say he slew five of them at the gates of Istria, before their chief turned tail.'' He lunged forward, thrusting an imaginary spear, growling and grunting. ``I'd love a chance to fight like him.''

``And I'd like to marry a soldier,'' Aeda said. ``That way I know he'd be brave and strong.''

``The only thing Gallas fights is deer hides,'' her brother said with a snicker. She swatted at him, then raised her muzzle.

``He may join up as well,'' she sniffed. ``The army has need of tanners, and he knows how to use a sling.''

``So do I,'' Mylo added with a huff. He plucked a rock from the road and launched it into the grass. Sikarios' heart sunk to hear them speaking like this, echoing the words he and his brothers had shared, happily dousing themselves in oil as the fires of war crept ever nearer. He had seen that same eager gleam in Elias' eyes, and had lived long enough to watch them darken.

``There's more to warfare than glory and victory,'' he said softly, trying not to growl the words. The weasels' eyes darted to his face; Mylo nearly tripped over his own feet. Sikarios' claws found their way to the marks scoring his face. He halted to let the two stare, their innocent eyes taking in the jagged ridge of bare skin and patchy, grey fur.

He let the silence stretch. ``Trust me, I saw much worse. I \emph{dealt} much worse.'' Stifling a shudder, he breathed out deeply. The day suddenly seemed much colder. ``When I was young, we spoke of war the same way you did, in my home. It was only later that I learned the truth.'' He set one paw on Mylo's shoulder, the other on Aeda's. ``I will not deny that fighting may be necessary at times, but it is not something to rush into eagerly.'' He longed to explain further, to stomp out whatever embers might be lingering within their hearts, but feared to reveal too much. ``I\ldots{} I wish someone had told me that, before I marched off to war.''

Without waiting for an answer, Sikarios started walking, hearing the slap of their sandals on the road a moment later. The trio remained silent the rest of the way into town. Dalma itself, however, bustled with activity. As soon as they neared the market, the marten noticed a number of strangers milling about, clad in tunics lined with dull bronze scales and draped in thick furs; smooth white or tawny coats showed beneath their armor, behind which dragged lithe, black-tipped tails. All were armed: some rested spears on their shoulders as they haggled with uneasy townsfolk, while others wore long knives or curved shortswords, or carried unstrung bows of yew that curled like the wicked horns of a steppe-beast. Sikarios found himself suddenly conscious of his own blade.

A local he didn't recognize waved the three over. ``Stoats,'' the weasel muttered, ``mercenaries from Kirkassios.'' Sikarios thought back to his father's maps: the Kirkassians were a long way from their rugged, mountainous homeland. But for the moment they seemed to be causing no trouble, and so the kits went about their business as he watched from a distance, the sight of so many warriors stirring up unwanted memories like silt in a shallow stream.

A raised voice drew his gaze to one of the townsfolk, standing in front of a stall, waving his hands at one of the stoats as another watched from nearby. Sikarios took a few steps closer. The mink held up three fingers, then pointed to the bowls of dried figs sitting on his stall. ``\emph{Three obols},'' he explained, dragging out each syllable, ``for \emph{one} cluster.'' Beside the fruits sat wedges of goat's cheese wrapped in arum leaves. The mink swept his arm. ``\emph{Two} for \emph{one} wedge.'' The stoat said something in his guttural, singsong tongue, then turned to confer with his comrade before handing the mink a pawful of coins. Without waiting, he snatched up two wedges of cheese and a few clusters of figs, and began stuffing them into a sack.

``No,'' the mink said, ``\emph{three} for \emph{each} of those!'' When the stoat ignored him, his voice sharpened to a snarl. ``Stop!'' His claws swiped for the sack. The mercenary caught his wrist and shoved him back against the wooden stall, and the cloth went with him, spilling figs and cheese to the dirt. As the mink scrabbled to collect his goods, a knife appeared in the stoat's paw.

Sikarios stepped in between the pair before he could think, his left paw finding the worn bronze hilt of his kopis. The mink looked up before scrambling back behind the stall with a whimper. The stoat glared, but as his attention fixed on Sikarios' face, as his gaze traced the grooves in his flesh, something between respect and challenge flickered behind his deep-brown eyes. He muttered something, waving his left paw languidly at the mink, his right still clutching the dagger. The bone hilt of the blade was white as its owner's fur. Behind him, his comrade stood straighter, resting his slender spear on an armored shoulder.

Sikarios cleared his throat. ``Give him what is owed.'' The stoat grinned, exposing a row of needle-like teeth. A pink tongue flicked over them. The mink cowered behind his stall, as if his fruits and cheese were battlements. Around them, the other locals had forgotten their mundane tasks.

Panic threatened to clot in Sikarios' throat like rancid blood. He seized the hilt in his right paw and bared a finger's length of the blade. His brother's words echoed in his mind: \emph{Stand your ground. Make them come to you. Make them pay for it.} The stoat tensed, head lowering, white fur bristling. The marten's heart pounded in his chest like a war drum.

Then a shout ripped their focus from each other, and Sikarios turned to see another Kirkassian stalking over, taller than either of the pair, a plume of crimson feathers fluttering from atop his helmet. He clouted his dagger-bearing subordinate over the head, barked something in his own tongue, and then turned to the mink, exchanging a few sentences in Elladian. The first stoat hefted over another pawful of obols.

As the captain of the mercenaries made to leave, his eyes settled on Sikarios, and he nodded sharply. ``Apologies. You will have no more trouble from us.'' His accent was crisp, words rustling like pines in a winter breeze. He strode away without waiting for a response, and just as soon, the marten felt claws clutching at his arm.

``Thank you,'' the mink started to say, but the rest of his words were lost in a rush of blood and fear as the world reeled. Sikarios staggered away from the market, away from the crowd of strangers to find himself plunging into the past, drowning in the wake of blood and fire that had eventually washed him onto these distant shores alone. He stumbled behind a mud-brick wall to cradle Elias' body, the lithe limbs that had once held him now broken and rent, the beautiful silken fur he had stroked in the moonlight now stained and clotted with crimson. He cringed as his brother's claws grappled for his own flesh, choking out a breath to find himself back in Dalma, huddled in the overlapping shadows of Aeda and Mylo.

Sikarios hated the way their eyes studied his wretched form, as if he were a crippled lamb, or a rabid jackal-dog. He gasped for air, wiping the tears from his bleary vision, wincing at the rapid stutter of his heart against his ribcage. The world slowly came back into focus, and the two kits gathered close once more, kneeling to help him stand.

``We saw what you did,'' Mylo said, the whisper laced with awe. ``You really are a soldier, then---not that I doubted you, of course, but---''

``I'm not.'' The marten waved a still-trembling paw. ``Not anymore.'' He sighed. ``I left that behind.''

``What happened?'' Aeda asked quietly, eyes softened with pity. Closing his own, Sikarios swallowed the knot of bitter longing welling up within his throat.

``I\ldots{} lost someone. And I hurt someone.'' He turned away, hating the way his voice broke, hating the ache in his chest, the flashes of terror and rage and bitter, biting pain. \emph{I won't let you}.

``Please,'' he muttered, ``don't make the same mistakes I did.'' His gaze flitted to the skies above, where the gods lurked, watching in silence. ``There is hardship enough in the world without rushing off to find it.'' Without waiting for an answer, Sikarios rose. The kits followed him back in silence.

\secdiv

\noindent By the time dusk had drained most of the sun's light, the marten's nerves had calmed enough to allow him to enjoy their supper, and the modest dessert of chestnuts served alongside a glass of watery wine. But a part of Sikarios still craved fresh air and solitude, and so he offered to clean the dishes and utensils, lugging the basket out to the nearby stream as the moon rippled over its trickling surface. The marten worked his claws slowly over the crude wooden cutlery and flatware, letting the cold, pure water rinse the day's tension from his mind, settling his own heartbeat into the tranquil rhythm of the quiet countryside. Once he had finished, he sat beneath the endless depths of the starscape, bathed in its pale fire.

Again, the thought of remaining here flitted into his mind; he let himself wander back through the years, to the day he and his brothers had made the decision to leave home. Kyrios, ever ready to honor their family name, was to be given his own command, while Alexi, barely thirteen, would serve as an officer's aide, away from the frontlines and yet still near enough to share in the glory of battle.

Sikarios himself had been hesitant. He remembered Alexi's pointed taunts as their family had taken dinner with King Thestor's envoys: ``Are you not strong enough, brother? Perhaps you would like to remain behind, weaving with the does?'' And when the others had laughed, their minds ringing with visions of the honor and renown they would doubtless win, Alexi had leaned in and whispered, ``Father will wonder, if you do not come. I am trying to \emph{help} you, Sikarios. Make you \emph{stronger}. For the honor of our family.''

In the end, Sikarios had knelt and pledged himself alongside his brothers. Elias, naturally, had been quick to follow.

He recalled the pride gleaming in his father's eyes, still tinged with sorrow even as they dreamt of greater conquest. And when he had confessed his fears to his older brother, Kyrios had devoted many of their dwindling hours to sparring with him, always besting the younger kine with a grace and dignity befitting a firstborn son. His words still rang clearly, even all these years later: ``Your problem, Sikarios, is that you hesitate at the crucial moment. Most individual fights last less than three heartbeats---in that time you will either have won, or be dead. But most people are not ready to face their death, and so by hesitating, or rushing in headlong, they meet it. You must stand your ground, and never falter.''

And to assuage the last vein of his fear, Elias had shown him the wooden lion, barely larger than his paw. ``For strength,'' he had said, lacing Sikarios' fingers through his own. They had each marked it with a drop of their own blood, drawn from the dagger his father had bestowed upon him.

An owl crooned into the night, dragging him back to the Illyrian hillside. The darkness quickly settled into silence. And in that silence, Sikarios remembered the shepherd's words: that there was someone here who could help him.

The following morning he rose well before the sun, leaving his kopis resting beside the door as a promise that he would return. All he knew of the town's sofianthe was that she dwelt in the hills, away from the coast, and so he trusted to the road and the first hints of daybreak smoldering in the east to guide him. One of the priestesses had served his father's court, though he could not remember her name; the short, ash-furred weasel had tended to a small shrine in the courtyard of the acropolis, but as a kine Sikarios had paid little mind to the workings of gods. It was not until the night of his enlistment that he had chosen Milosha as his patron, her warrior's wisdom a stark contrast to the passionate bloodshed of Voyokan, whom most of the other recruits had favored. And as far as the marten could tell, she had answered few of his prayers.

The path took Sikarios through brush greyed and withered by the wet chill of the Illyrian winter. About halfway up the hillside it passed a clearing containing a lump of stone, a small wooden structure nestled quietly in the shadows of the undergrowth nearby. As he drew closer, the marten recognized the worn, moss-covered figure of Iluvex adorning the shrine, various woodland creatures frozen midstride about her feet. The stone beneath her was charred and cracked.

``Hello?'' Sikarios called. ``I was hoping to speak with the sofianthe.'' At first the only answer was the high trill of a distant waxwing, but then a voice echoed from the hovel, smooth and gentle, younger than he had expected.

``Ah, you've come at last.'' A moment later a slender form strode out into the clearing, wrapped in a light grey cloak. She lowered her hood and bowed slightly before the shrine. ``I am Mira, and I have the pleasure to serve the gods and Dalma as sofianthe.''

The mink's eyes sparkled with calming warmth, and her coat of rich sable fur was dappled in glistening patches of bronze where shafts of sunlight pierced the canopy. Sikarios stared, and stared; it had been so long since he had known the warmth of another body against his own, and now before him stood one of the fairest does he had ever seen. A part of him knew how his longing smoldered in his eyes, fearing that the priestess would recoil at the sight, would see the beast lurking within his haggard face. \emph{Murderer. Oathbreaker. Kinslayer.} But she did not so much as flinch, meeting his gaze as if he were but an injured kit, and she was a mother who could mend any wound.

``You\ldots{} you've been expecting me?'' he finally stammered.

Her smile took on a hint of playful amusement. ``Well, word gets around, and I am not chained to this shrine. A scarred southern wanderer with a kopis at his side, here in humble Dalma?'' She led him to the altar, staring up at the goddess of the wilderness. ``And so, what is it that brings you here today?''

``I\ldots{} I was hoping for advice, after a fashion.'' He drew his paw back, curled it into a fist, fighting the urge to dredge every last detail of his past, knowing it would only make things worse. ``I\ldots{} am sorry,'' he sighed. ``It is difficult to speak about. But I feel as if the gods have forsaken me, and that every path forward has closed.''

A shadow passed over Mira's face. ``We are like children before the splendor of the divine, and discerning the proper path can often prove painful. I understand you are\ldots{} hesitant to speak freely, and I will not presume to know what a soldier such as yourself has endured---'' she paused as his mouth fell, giving him a look of somber understanding---``but we could try a divination.''

Sikarios grimaced, remembering the few he had been present for in his youth: a hare dragged screaming to the altar, or a crow bound and squawking, where a silver knife would reveal the secrets of the world in their steaming entrails, leaving a crimson stain upon the cold stone. But Mira simply kindled a tiny flame upon the altar before producing a clump of white flower petals from a pocket. She smiled, her eyes filled with sly understanding.

``None of that mess, I assure you. The gods eat well enough without me sending them a squealing rabbit. Now let us see what your own fate holds.'' She sprinkled the petals atop the altar, letting them dance down on the currents birthed by the fire, already dying. One landed directly upon the flames and sizzled, its edges glowing red, the white flesh curling into char. The marten thought that did not bode well, but the mink's face remained dispassionate.

Her voice, when it came, seemed to echo in the glade. ``I see a fire spreading northward, and withered trees embracing its flames. I see a kine bearing a torch in bleeding claws, coming to claim something that was stolen, and to take something more.'' The mink's paws hovered just above the scattered petals, as if afraid they might singe her rich brown fur. The last of the embers' light sizzled in the sheen of her coat. ``And\ldots{} I see a shadow racing ahead of the flames.''

Sikarios tried to swallow the unease that welled up within his throat. Mira clasped her paws and peered up at him, as if the answers might lay behind his own eyes.

``Thank you,'' Sikarios said, failing to keep the quaver from his voice. He dug out a pawful of obols from the pocket of his cloak and set them on the altar.

``Go with the peace of the gods,'' the mink replied. He nodded, and left without another word.

The forest lay silent around Sikarios as he followed the same narrow, muddy path back. \emph{A shadow, racing ahead of the flames.} A layer of thick, grey clouds settled in beyond the canopy, muffling the daylight and threatening rain. The pines rustled and creaked in the wintry breeze. For what must have been the thousandth time, the marten thought of home, only for the image of Dalma to seep into the memory.

When he neared the familiar cottage, Tamyris was waiting for him outside, with his crook gripped tightly and one of the foxes standing rigid in his shadow. Kokkin started towards Sikarios, but a hiss from his master stayed the fox. As the marten neared, fear bubbled up beneath his confusion.

``A messenger came through,'' the weasel said. ``King Thestor has dispatched emissaries to our lands in search of recruits for the spring campaign. One will be here tomorrow: Kyrios, Prince of Nalanthis.''

The mention of his brother's name tightened a claw around Sikarios' throat. The weasel went on, as if he were choosing every word with care. ``The kine said\ldots{} he said that this prince is seeking a deserter, an oathbreaker and kinslayer. His brother. A brown-furred marten, with a mark over his left eye.'' Tamyris' own eyes smoldered with betrayal, and the marten's words turned to ash on his tongue.

The shepherd lowered his voice. ``I know that I did not press you for the details of your past, Sikarios\ldots'' His claws tightened, scoring marks into the yew. ``But \emph{this?}'' He grimaced, shying from the marten's gaze, then waved a paw. ``May the gods themselves bear witness to the hospitality we provided a stranger. But there is no place for you here anymore.''

Sikarios let the silence stretch. ``I understand,'' he finally said, desperate to keep his voice from breaking. ``May I fetch my things?''

The shepherd nodded, stepping aside, giving him a wide berth. Kokkin shot a perplexed glance between the two. The marten retrieved his few belongings, buckling on his sheath before digging through his sack. Drawing out a drachma, he set it gently on the table.

``Thank you. You've shown me more kindness than I deserve.''

Tamyris simply stared from beyond the doorway. As Sikarios stepped out into the first gentle patter of rainfall, he turned one final time to his former host. ``Do the kits know?''

The shepherd's eyes softened ever so slightly. He looked away. ``Not yet.''

``Please, don't tell them.''

Tamyris' gaze rose to meet his. ``They're bound to hear it all sooner or later.''

\secdiv

\noindent Dusk found him huddled beneath a lip of rock in the hills north of Dalma, paws stretched to draw the warmth of a paltry fire struggling for life. Sikarios still dwelt on the stares of the townsfolk as he had passed through; eyes that had welcomed him in days prior, or passed him over with no more than a moment's consideration, now burned with contempt or widened in fear. Fishers and fruit-sellers who had greeted him eagerly now drew their wares back at his approach, muttering curses under their breaths. A part of him whispered that things were now as they always should have been.

Rain continued to thud down beyond the slim stone overhang. The fire hissed and sizzled like an angry serpent. With his tongue, Sikarios loosened bits of stale bread from his teeth, all that remained of his meager supper. Then, retrieving the carving, he began the final strokes that would leave the lion free of its wooden womb. His mind wandered back, back to the night before he and his brothers had departed. Kyrios, clad in armor that fit him so naturally he might as well have been born in it. Himself, anxious and yet eager to serve, to fulfill the oath he had sworn to their father. And Alexios, convinced he had salvaged his brother's honor, had saved him and their family from shame.

Kyrios had approached Sikarios that night with his own worries. ``Alexi will be away from the frontlines, but\ldots{} I still worry for him. He is young, and\ldots{}\emph{impulsive}.'' He still remembered how his brother had grinned. ``I have sworn to father that I will watch after you both, but my duties may lead me elsewhere. And if something should happen to me\ldots'' He had knelt, taking his brother's paw. ``Promise me that you will look after him as well.''

``I will,'' Sikarios had told him. ``I swear it.'' He had made a similar promise to Elias.

Gently, he blew the wood shavings from the lion, examining it in the flickering firelight. As far as he could remember, it was near enough a match for the one his friend had given him the evening before their final day together. After four years of fighting, Sikarios had told him how the clang of iron on an anvil, the flash of the butcher's blade, even a sudden shout might cast him back to the carnage of some nameless battlefield. How he wasn't sure how much more he could endure. Elias had clasped the lion in his paws, had held until Sikarios' breathing steadied. And even full of concern and pity and fear, his golden eyes had still held the fire of the sun.

``For strength,'' his friend had said. Gazing into the flames, Sikarios could still see him. He went to sleep with the whisper of broken promises echoing in his ears, and awoke well beyond daybreak to find that the rain had ceased.

As the clouds thinned into wisps and the sun baked the stones of the highland, the marten caught a pair of slender, ghostly pale trout in the stream. As he ate, his eyes were drawn to the distant spread of Dalma; he wondered if his brother had already arrived. If he was a fool to have lingered so late, or to have fled for so long. The lion in his cloak pocket dragged like a stone. He was so tired of running, always running---and what solace was there to be found in Istria, or the northern wilds beyond it, if he never tried to make things right?

Sikarios ran his claws over the ridges of his scar, then rose from the rock and glanced south. From here the settlement lay quiet, and his heart ached to know the tranquility was a lie. Staggering down to where the rugged trail met the road, the marten glanced right---to the north, where the well-worn pathway would carry him ever farther from his past, into the fog of anonymity and exile---and then left, to the lives he had come to know these last few weeks. To a town full of fresh kindling, eager to welcome the coming fire. His sigh carried all the weight of the prior four years. Turning left, he began his descent.

By the time he reached the edge of Dalma, Sikarios could see that most of the townsfolk had gathered in the market square, where a few mounted figures loomed above the crowd. A voice addressed them, rich and confident, strong as stone. A voice he knew, that had offered him counsel and reprimand and reassurance. A speech he had heard many times before, in one form or another; he let the words wash over him like mist. Some of the locals shot him casual glances that shifted quickly into lingering stares. Faces melted into scowls or twisted in fear; eyes full of reverence narrowed in contempt. He walked on, feeling for the lion in his cloak pocket. \emph{For strength}.

Sat atop roe deer, a few ministers in regal chitons turned to watch him, while their guards came more rigidly to attention. The crowd slowly parted, and the speaker's voice trailed off. And before him, across the dusty plaza, clad in a suit of gleaming bronze, stood his brother, Kyrios. Their eyes met for a moment, the warrior's mouth gaping, before Sikarios shied away. He turned to the townspeople.

``What you have here is more precious than you know. Do not be so eager to throw your lives away.''

Ever agile, Kyrios overcame his shock quickly. ``Death comes for all of us in time,'' he replied triumphantly, ``so why not meet it with bravery, why not live a life of adventure? Win honor and renown, and know that if you die, it is for a cause worthy of remembrance!''

``He speaks to you of a warrior's honor,'' Sikarios shouted, letting his eyes sweep the crowd, before settling them back on Kyrios. ``Well, brother, tell them of the honor to be found in an early grave, of the honor in a mother and father weeping over the memory of their son, buried in some far-off field. Tell them of the honor of striking down some other kine barely beyond adolescence, so that you might live in his place; of watching the earth drink the blood of your friends, one after another, while the kings who send you off to die grow richer and fatter. Tell them of the honor you will \emph{truly} give them.''

Kyrios strode forward, eyes blazing. ``\emph{Honor}? What do \emph{you} know of \emph{honor}?'' He thrust a clawed finger at Sikarios, voice crackling with rage. ``You, who broke your oath and deserted the service of the king you were sworn to serve. You, who slew your own brother when he tried to stop you.'' His roar trickled to a rumble. ``And now, you come slinking back. Have you finally grown tired of living in the hills like a polecat? Are you ready to return and face justice?''

Sikarios glared. ``I have not come to plead for mercy, Kyrios, from you or from Father.'' His kopis leapt from its sheath, the bronze cool against the pads of his trembling paws. He raised his free hand. ``With gods and kounavi as witness, I challenge you to single combat.''

His brother stepped nearer, until only a few paces remained to separate them, and lowered his voice. ``I accept, though I take no pleasure in this,'' Kyrios growled. ``But before I kill you, I want to know why. \emph{Why}, Sikarios?''

``I never meant to,'' Sikarios muttered, blinking away tears, his scars burning at their sting. ``But I\ldots{} I just couldn't bear it---battle after battle, week after week, seeing comrade after comrade fall. And then, Elias\ldots'' He choked down a sob, tightening his grip.

His brother's face was hard as granite. ``You think I haven't suffered these last four years? You think I haven't shed blood, haven't lost friends? But I let it strengthen me, shape me into something better!''

``Then I suppose you were forged from purer iron than I.''

Kyrios' face softened, tenderness creeping into his voice. ``Do you think I did not know what he meant to you?'' A glimmer of pity diluted the hatred in his eyes.

Sikarios winced. Tears matted the fur of his cheeks, and he wiped them away with his free paw. ``Alexi\ldots{} Alexi knew as well. He confronted me that night, as I was leaving our tent.'' \emph{I won't let you}. ``I tried to explain, to make him see, but he---he drew a knife. And when I tried to take it from him, we fell.'' His voice grew panicked. ``I don't even remember drawing my own knife\ldots''

``There is still time,'' Kyrios replied, sounding so much like their father had, before. ``Throw down your sword, come back with me willingly. Plead for mercy in Father's court. Even a dungeon, or a life of service in a temple would be better than this.''

``No\ldots'' Sikarios breathed out with a shudder. Fear coiled around his heart like a snake. His pulse thundered in his ears, blood burning in his veins. \emph{You are stronger than you know}. He took a deep breath, then another, forcing everything else from his mind. \emph{Stand your ground, and never falter}. ``No. I cannot go back. I \emph{will} not.''

His brother's eyes furrowed, fur bristling like a thousand dagger-points. ``So be it.'' Snarling, he ripped his blade from its sheath and launched forward. \emph{Three heartbeats}.

Sikarios brought his own kopis to bear, meeting his brother's slash. Iron screamed against iron. He buckled under the weight of the blow, and Kyrios swung again. Sikarios barely managed to meet it with a parry, then followed with a riposte that scored a crimson line across his brother's arm. As the older marten recoiled with a hiss, he brought his kopis down against the hilt of his foe's upraised sword, then gripped the flat of the other blade in his free paw and twisted. Kyrios stumbled back into a plume of dirt, his kopis sailing through the air to clatter to the ground with a clang.

Three heartbeats. When the dust settled, Sikarios' blade hovered only a hair's breadth from his brother's throat. Kyrios stared up at him with eyes that had faced death a thousand times. Neither dared to breathe: by the most sacred customs of their people, he held his brother's life in his paws. Slowly, Sikarios drew the blade back. ``I never meant to kill him, Kyrios. And I will not take our father's final son from him.''

He looked at his kopis. ``If I could trade my life for his, I would do so in a heartbeat. But it is done. He is gone, and I remain. Now, if you truly believe that killing me will make things right,'' Sikarios went on, thrusting his sword into the soft earth, ``this blade will work as well as any other.'' He unbuckled his scabbard and cast it to the dirt, waiting for the strike that would send him reeling into darkness.

But Kyrios merely stared. Finally, he bowed his head, eyes fixed on the kopis. ``I will return this to Father, and tell him the truth: that both of my brothers are lost.''

Sikarios turned away to find the people of Dalma watching in silence. When he advanced, they parted like water before him, muttering and whispering, clutching their kits close. But he paid them no mind until three familiar faces surfaced in the crowd. His throat tightened at seeing the shepherd's family watching him with the same revulsion shared by their neighbors. The marten stepped nearer, thankful at least that the trio did not flee from him.

While Tamyris glared and Aeda tensed with a shudder, Mylo simply stood there, gaze fixed on the dirt. Sikarios retrieved the carved lion from his pocket, and held it out. ``You will hear many things about honor, and duty, and strength,'' the marten said, fighting to keep his voice level. He let out a slow breath. ``But strength is not only measured by the force of a blade, or a spear thrust, or a slingstone. It is not only found in palaces or war camps, and it is not only proven on the battlefield.'' At that, the young weasel finally met his gaze. ``May you have the strength to know what is right, and to choose it, no matter what may follow. No matter what the world may say.'' As if handling a fledgling bird, Sikarios pushed the lion into the kine's paws. ``And may you not make the same mistakes I did.''

He rose without another word and started walking. Behind him, Kyrios' soldiers had helped their captain up, while the ministers who had accompanied them brandished tablets and bags of silver. Several of the locals had lined up, kines as young as Mylo among them. At the edge of town, Sikarios paused, and turned a final time to see Tamyris and his kits still standing off to the side. While his father and sister watched the proceedings, Mylo was running his claws delicately over the carving, tracing the wood's grain as if it held the answer to some powerful question.

Trusting that he had done all he could, and clinging to the hope that some worthwhile future waited for him beyond the horizon, Sikarios turned north and did not look back.
