\section*{---}

\hfill\textit{February, 2017}

\begin{verse}[1.01\textwidth]
  I see your past in cross-processed film,\\
  in blown-out colors and over-saturation.\\
  \vin You told me all about it, told me grand stories:\\
  \vin you were going to go back in time and save the world.\\
  I see your past in yellows and browns,\\
  in umber and sienna and amber, in a younger sun.\\
  \vin You sat and told me how --- and you were always sitting ---\\
  \vin you thought past-you dreamt of a future less complicated than today.\\
  I see your past through film-grain and vignette,\\
  with a thick white border, space on the bottom to write.\\
  \vin You told me how you learned so many imperfect things,\\
  \vin in so many less than ideal ways, always at inopportune times.\\
  I see your past in architectural drawings of unrealized buildings,\\
  in paperback covers reaching towards heaven, in trillions of words.\\
  \vin You figured past you dreamt of, not perfection,\\
  \vin but a world unconstrained by so many failures.\\
  I see your past with no me in it,\\
  and wonder if past-you dreamt of us.
\end{verse}
\newpage

\section*{---}

\hfill\textit{February, 2017}

\begin{verse}[1.01\textwidth]
  Resuscitating ancient coins in class, we learned,\\
  takes a toothbrush and olive oil.\\
  Slow, steady strokes across, around...\\
  soft bristles dislodging soil\\
  one speck at a time.\\
  But no one that day was nearly as blessed,\\
  seeing a coin shine through\\
  at the end, full relief brightly expressed,\\
  as I was to see you smile.
\end{verse}
\newpage

\section*{---}

\hfill\textit{February, 2017}

\begin{verse}[1.01\textwidth]
  When you arrive,\\
  the whole world gets slow.\\
  Sluggish, amber-colored air\\
  mellows lively conversations.\\
  Everyone stops, marvels,\\
  turns eagerly toward you;\\
  and there are no complaints\\
  about warming our faces in the sun.
\end{verse}
\newpage

\section*{---}

\hfill\textit{February, 2017}

\begin{verse}[1.01\textwidth]
  We fit together in the strangest ways\\
  and seem to seek new seams to savor.\\
  Such joins are hardly perfect,\\
  thread tugging fabric unevenly\\
  unless it's reinforced over and over again.\\
  We seem to seek new seams to savor,\\
  and, weak though they are,\\
  revel in the imperfect unevenness of joining.
\end{verse}
\newpage

\section*{---}

\hfill\textit{February, 2017}

\begin{verse}[1.01\textwidth]
  Complementary, clashing anxieties.\\
  Dull clamor of intersecting feelings.\\
  Need, desire, craving, jealousy.\\
  Worry, fear, care, prayerful fretting.\\
  Love, lust, friendship, a need to share.\\
  Emotions on emotions on emotions,\\
  and, often, comfortable silence.
\end{verse}
\newpage

\section*{---}

\vspace{-0.5cm}

\hfill\textit{May, 2017}

\begin{verse}[1.01\textwidth]
  Tightly wound springs\\
  Of very carefully\\
  Not touching.\\
  \vin Secret words\\
  \vin To be said\\
  \vin With confidence.\\
  Rules.\\
  Prohibitions.\\
  Limits.\\
  \vin Discussions planned,\\
  \vin Side-channels arranged,\\
  \vin Whiskey purchased.\\
  And now anxiety\\
  Over what it means\\
  And how to work it.\\
  \vin Is it worth it for\\
  \vin Long-standing questions\\
  \vin To be answered?\\
  To invite disaster\\
  For sake of knowledge\\
  And further dreams?\\
  \vin Maybe the answer\\
  \vin Is that tired refrain:\\
  \vin Perhaps, perhaps, perhaps.\\
  And now we're\\
  Awaiting weeks\\
  Of careful touches.
\end{verse}
\newpage

\section*{---}

\hfill\textit{August, 2017}

\begin{verse}[1.01\textwidth]
I could never tell you\\
that you feel too much.\\
That you feel too hard,\\
or that your feelings\\
overwhelm and overtake you.

I could never tell you\\
how beautiful that is.\\
That I wish I could feel those things,\\
that I wish I could feel that way.

All I can tell you\\
is how beautiful you are\\
when you feel love.
\end{verse}
\newpage

\section*{---}

\hfill\textit{August, 2017}

\begin{verse}[1.01\textwidth]
\textit{Yit'gadal v'yit'kadash sh'mei raba}\\
Would that I had the faith\\
To pray daily.\\
Eleven months to let you go,\\
And an amen to end the sorrow.
\end{verse}
\newpage

\section*{---}

\hfill\textit{June, 2018}

\begin{verse}[1.01\textwidth]
  Between our houses,\\
  there is a simple fence -\\
  not a chasm, not a wall.\\
  Chain-link, waist high,\\
  bedecked with sweet-pea\\
  and set about with violets.\\
  Something we can tend,\\
  something to feel good about,\\
  something between us\\
  other than nothing.
\end{verse}
\newpage

\section*{---}

\hfill\textit{May, 2019}

\begin{verse}[1.01\textwidth]
    I will swallow my love for you.\\
    I will swallow my love.\\
    I will swallow my love for you\\
    And relish the magnesium flare,\\
    Rejoice in immolation,\\
    Cherish the autolysis\\
    Of secret cells.\\
    I will swallow my love for you.\\
    I will swallow my love.
\end{verse}
\newpage
% Mi glutos mian amon por vi.
% Mi glutos mian amon.
% Mi glutos mian amon por vi
% Kaj frandos la ekflamadon de magnezio,
% Ĝuos la oferbuĉadon,
% Ĝojos la aŭtolizadon
% De sekretaj ĉeloj.
% Mi glutos mian amon por vi.
% Mi glutos mian amon.
