The pit revealed little.

There were twenty boxes set on a table in front of the snakehead. Twenty receivers for wireless mics. Twenty cables neatly velcroed together into a bundle, contracting from the boxes arcing catenary toward the dull grey plug-box. From there, the cables were reduced to a four-by-five grid. The cables arched up above the snakehead before plunging into it, XLR heads buried in XLR nests.

All of the boxes on the table were dull. Mute LEDs simple bumps on their surface. Dark. All but one, that was. The first one. The one with a piece of masking tape on its face scrawled with a `1'. That box had a single red light on the front, indicating that it was powered on, and a single green light, indicating that the corresponding mic was transmitting.

``Great,'' AwDae murmured. ``That leaves only half of the school to search.''

If it had been a wired mic, the search would have been over as soon as it started. The cable would've been plugged into the snakehead, and by following it until ey reached its end, there would be the mic.

And what?

There would be the mic, and ey would still be stuck in some parody of a nightmare. All dressed up for the high school performance and here, see? The auditorium is completely empty.

The fox barked a laugh at how many cliches littered the situation. Turning away from the receivers, ey rested eir weight against the edge of the table on which they were placed. Ey leaned a moment, then hiked eir backside up onto the familiar surface, relishing the squeak of stressed metal from eir sudden burden.

AwDae swung eir legs back and forth, hearing the table creak and groan in time with the slow movements. The sound was quiet, but in the dread silence of the auditorium, more than enough to fill the hall.

Ey stopped.

The hall was pleasantly wet: not damp or anything, but in terms of echo, it had just the right amount. Or, at least, as much as a high school auditorium was willing to muster. Had it been dry, the sound would've died away completely. The drier a room, the closer it got to approaching an anechoic chamber, a room lined with material such that it would reflect zero sound.

But neither did the sound bounce back endlessly like an echo chamber.

AwDae knew this hall, even years later, even in dreams. Ey knew the pockets of good sound and bad sound scattered throughout the seating. Ey knew the dead spots on stage where one's voice would fall flat if it weren't amplified. Ey knew how the stage was built rather like a horn, with the performers at the small end, so that their sounds were projected out toward the audience. Ey knew how the stage was built like a drum, the pit a chamber of its own.

And yet, there was that slight echo of the squeaking of the table.

An idea. A crazy one, sure, but by this point with despair nipping at eir heels, a crazy idea was better than none.

\emph{And}, a bitter portion of em reasoned, \emph{if getting lost is permanent like they say, I've got nothing to lose.}

Ey hopped back off the table and began to pace.

The squeal of feedback in an audio system is an emergent behavior, and even those who have not heard it before know immediately that something is wrong when it crops up. It begins a quiet hum in the background, builds exponentially.

It doesn't take long before it can be understood as something originating in the system, rather than coming from the speaker or performer. From there, it builds on itself, feeding back into itself, until it quickly overwhelms all sound coming into it. Rises, crescendos. Hearing and speaker damage equally likely if left unchecked.

Similar, in an upside-down sort of way, to the echo that AwDae had caused making the table squeak beneath eir weight. Sound was picked up by the microphone, transmitted through the sound board, then out into the room. Amplified, though, through the speakers.

If the microphone started to pick up sound from the speakers, though --- and sound was sound, the mic cared not where it came from --- that sound would loop through the board once more.

A feedback loop. It would continue to build through further and further iterations, until the auditorium was filled with a roar of the one pitch the microphone had first locked onto.

Dread and dire. Cursed. An eternal struggle.

Obviously, microphones were still in use. They hadn't been abandoned because of the loop, since there were plenty of ways around feedback.

One could angle speakers toward the audience, rather than the stage. Bodies were notoriously bad reflectors of sound. Part of what made the stage so acoustically dead, that. One could also turn down the monitor speakers facing the stage, but that was cruel to one's performers. One could turn down amplification, but that defeated the purpose.

The usual solution, then, was gain.

The simple adjustment was given a knob at the very top of the sound board governing the sensitivity of the mic. At the top, befitting its importance in the setup.

Turn the gain all the way down, and the mic was a dumb lump of metal and plastic. Turn it all the way up, and the mic picked up everything from the movement of the air to the slight hiss of the live sound system. Almost instant feedback.

AwDae turned up the gain almost to the point of feedback. If ey could make noise in various points throughout the auditorium, maybe it'd get picked up. The more feedback ey generated, the more sound the mic was picking up. The more sound it was picking up, the closer ey was to it.

Eir possible locations for the mic hadn't been reduced. It was still half the school, but eir chances would go up. If the mic was not in the auditorium, ey could turn the main system up and start venturing further afield. Leave a door open, let the mic hear. Let em hear the theater ring like a bell in turn.

Riddles. Triply weird.

AwDae felt stupid. Insulted. Trapped for life and still solving riddles. Hopelessness dimmed eir vision.

Ey shook eir head, ears laid flat. ``At least it's something.''
