AwDae slowly picked emself up off of the floor, staggering to eir feet.

Ey was standing, swaying, in the middle of a long row of lockers. And then ey was sitting again. Ey didn't feel weak, but the shock of being in the tech booth and theater sim, and then suddenly being back in high school was taking its toll on eir wits.

Ey swiped eir paw from left to right in front of emself to bring up the usual menu. Only, no menu came up. There was nothing in this sim, if sim it was. No global menu, no ACLs, no control.

Panic crested again.

AwDae felt behind emself, reaching for that sense of reality outside of the sim, that cool breeze of the tangible that should be at eir back. It \emph{was} there. Ey could feel it. A cool breath of air on the back of eir neck, but muffled. There was something keeping em from reaching for it, touching it. A thin barrier. A membrane. A sheet of keeping em trapped within the sim.

And then, with a jolt of pain driving like a spike down the back of eir neck and along eir spine, it was gone.

Throughout all of the practice runs, the endless training on the rig that had gone into eir education, that feeling had only come up a scant handful of times. It was the feeling of being forcibly disconnected from the rig through the manual expedient of removing the contacts from the cradles in which they rested. It was the shock of being brought to reality from out of a sim with no disconnection. It was the rush of eir exocortex dumping its core. It was panic made tangible, halfway between electricity and the feeling of missing one's step on the last stair.

With that, AwDae should've found emself back in the tech booth, trying to figure out what strange loop the theater had gotten itself into that would have frozen eir rig.

The lockers never wavered, though, and now ey found emself stuck in eir old high school school with no contact to the world outside of whatever this place was.

Ey screamed.

Ey didn't know how long ey screamed, how many times. Ey didn't know how long ey cried or beat eir fists against the lockers. Ey didn't know where ey was.

Lost.

Lost like so many others.

Lost like Cicero.

Or perhaps Aeneas, Odysseus.

Eventually, ey cried emself out. Eventually, eir tail went numb and eir feet fell asleep.

\emph{Nothing for it.} Ey wobbled to eir feet, kicked off ill-fitting shoes, and began to trudge.

Ey walked slowly down the halls, memories coming back in a wash. Realities blurred effortlessly. Realities of the embodied world. Realities of online life.

Nails on feetpaws clicking against the tile, following the math wing to the student center, a cavernous space that acted as a terminus for all of the different hallways, each hosting a different subject. They spread away from the cavernous room like limbs, a giant insect clutching at the earth.

Neither halls nor hub had ever seen a fox. They were supposed to be home to students. To students and teachers and staff. To humans. To anyone, not some lone half-beast.

Inside the student center, AwDae sat down and tried to reach towards reality once more. Ey sagged, rolling onto eir side in eir increasingly frustrated attempts to pull away from the contacts, though that shock of pain suggested those in reality had pulled em away.

Frustration, anger, fear. Hopelessness. Terror. All simmered within em, working up to a boil as ey tried increasingly harder.

Finally, ey gave up and, hastily brushing at the tears staining eir cheeks, slipped out of eir suit jacket as well. Why keep it?

Ey swished eir tail to the side, and lay flat on eir back on the cool terrazzo floor. Ey pulled eir suit jacket up over eir face and buried eir muzzle in the soft lining. With paws holding the cloth to eir face, ey deliberately let the tears come. Willed them too. Forced. Screamed and begged. Anything for release from the tension building up.

It was a few minutes before ey peeled the coat from eir face and stood back up once more. Exhausted, ey slipped eir arms back into the sleeves of the coat, letting it drape awkwardly from eir shoulders, unbuttoned, fill fitting around eir slim frame. Ey bent down to roll up the cuffs of eir slacks to keep them from bothering eir feet.

It was in the middle of the second cuff that ey realized the absurdity of the motion. In the theater sim, ey didn't have a body, and when ey `woke' in eir normal sim, ey was dressed only in the clothes ey had on when ey went to bed. Usually nothing. Ey disrobed before disconnecting more out of habit than anything.

Why was ey still in eir tux? Did ey even have a tux in eir wardrobe?

AwDae puzzled over this for a moment longer before completing the act. Something to look into later. For now, ey needed to find eir way out. Find eir way back out. Or, failing that, at least one thing ey could complete. One task to complete. Something to make em feel less powerless in the face of it all.

The sim was startlingly complete.

Perhaps. Ey had been in London a few years, and before that, on the coast at university. Was it complete? Was it accurate? Despair lay around the corner: the thought that the chances of em being able to compare the sim and reality vanishingly small.

In fact, the only thing that seemed to have changed was AwDae emself.

AwDae's curiousity won out. y had made eir way back to the school's auditorium. It was exactly as ey had left it all those years ago. Trudging up the few steps toward the entrance, ey feared that it would be locked. Missing. Somehow erased from existance, such that it had never been there in the first place.

But the door swung easily beneath eir paw and eir nails clicked against the lower portion of the sound guard in the doorway, leading em into a dimly lit auditorium.

The house lights were at quarter, the stage lit only by utility lights from the back. All the same, it was enough for em to find eir way to the small sound booth. A counter with a light --- off. A bank of sliders and knobs --- all zeroed out.

AwDae brushed eir fingerpads along the lower lip of the soundboard. The screws were exactly where ey remembered.

Swishing eir tail out of the way to, ey sat on the stool in front of it. Ey reached a paw up past the master sliders, just around to the back of the board, where ey found the power switch.

Click.

Nothing happened, so ey reached a little further back, finding the power strip for the booth itself, and toggled the switch on that. The board let out a satisfying pop of recognition as it came to life. The brief surge of power echoed throughout the room as speakers awoke. The theater uncoiled, purred to em, just as the one back in London had done\ldots{}what? Three hours back? Five?

Ey fumbled with the booth light, finding the ancient dial switch to wash the unlit portions of the booth in lazy red light. Light illuminated a thin layer of dust covering the board and booth in a matte coating, and countless motes already disturbed. The only breaks in the coating were where eir fingers had brushed the dust away, leaving black slicks.

So familiar. So many dreams. Dreams of flawless performances of breathtaking beauty. Nightmares of feedback and missing equipment.

Acting on a dream, ey slowly brought the master volume up to the spot ey still remembered from so long ago, turned the gain to mid on mic one, and brought the slider up slowly.

Blinked.

A soft hiss filled the hall. The channel was open.

\emph{That doesn't mean anything,} AwDae thought. \emph{Could be anything plugged into the snakehead in the pit. A line with a powered mic, a wireless receiver. Hell, a fault in the system.}

All the same, it was something. Something in this seemingly abandoned hulk of memory was turned on, something else besides emself was making noise.

Ey was about to head down to the pit to check on the snakehead, the terminus for all of the microphone cables or wireless receivers that stretched up to the board, when ey caught sight of a sheet of paper, folded in quarters, tucked between the side of the board and the wall of the booth.

AwDae plucked the paper free and unfolded it, then held it under the red light of the booth lamp to get a closer look at it.

There, in tiny print, was a good chunk of the content of the vcard ey had created earlier that morning to add to Sasha and Debarre's deck. Cicero's DDR ledger, containing transactions that comprised votes made, bounties collected, and comments posted.

A note, though. Doubly weird. The paper didn't act like a normal vcard. No menu, no ACLs ey could sense. And yet the closer ey looked at the paper, the more the data seemed to unfold, fractally nested and apparently infinitely deep.

Ey blinked, and the moment passed. The note once more contained only tabulated transactions.

Frowning, AwDae refolded the note and stuck it into eir trousers' pocket. A small scrap of the outside world stuck in this elaborate fantasy.
