\hypertarget{rj-brewster-2112}{%
\chapter*{RJ Brewster — 2112}\label{rj-brewster-2112}}

Sleep did not come easily.

As padded as the auditorium seats were, they were not made for laying down on. They folded down, and while there were no arms to get in the way of stretching out, the gaps between seats were painful. AwDae found that ey had to face toward the backs of the seats, lest eir tail would get crimped against them, leaving eir back exposed in a way that felt uncomfortable, no matter how empty the sim was.

At first, the faint dusty smell of the seat fabric inspired nostalgia, but it did not last. The memories were not comfortable, either.

Eventually, ey got up and began pacing blearily around the auditorium. There must be some way to get rest that did not involve folding seats.

Ey could pull down one of the curtains and make a nest out of it. But, as ey did not know how to do so without ripping the curtain, ey was loath to do so. They carried some of that same smell, the same memories. A last resort, then.

Exploring beyond the auditorium it was, then. The back door of the stage led to the hall containing music and drama classrooms. Ey started cataloging additional places where ey could get rest. The black fabric orchestra seats was a little promising, and they could be arranged however ey wanted, but ey hit pay dirt in the theater room.

The back of the room was sectioned off into a wardrobe area, housing costumes and rack upon rack of identical tuxes and dresses for the choir singers. Nestled back behind all of these rows of clothing was a sofa, old and sagging.

There was zero reason for the room to contain a sofa. As inexplicable as it was, AwDae wouldn't have been surprised if such a thing had existed in the school ey when had attended.

Thanking whoever had created this sim, ey flopped down onto it. Musty smell lingered, settled.

Ey was asleep within minutes.

Sleep, while restful, brought dreams of unnerving intensity. Dreams of twisting passages, of locker-lined corridors looping impossibly back on themselves, leading always into the same dim light of the student center. And in the middle, a menu, no different from what ey might get by swiping eir paw left to right in any sane and sensible sim.

Every time ey got close to try and read the menu, though, it would slide closed once more, leaving only its shadow behind, an unexpected rendering error.

AwDae jolted awake feeling as if ey had drastically overslept. Ey hadn't paid attention to when ey had gone to bed in the first place. One in the morning? Two? Rehearsal, and then hours of searching. All the same, ey felt late.

With the shock of the transition and the need to explore the auditorium and hunt school for the mic, ey never managed to make it outside of the school. Could ey even do so? Ey felt silly for not trying, now.

Wake up, then. Ey stretched and started to plan a way out of the school. If nothing else, they wanted to see how extensive the sim was.

It was customary to lock the doors that did not lead anywhere in a sim. Although the Crown Pub did have bathrooms and fire escapes, for instance — all things to make it authentic — the doors were locked tight. Beyond them would have been nothing at all. That was simply the extent of the sim. It was not inaccessible so much as nonexistent.

There were much larger sims than the school itself, much more intricate. AwDae couldn't be sure of the boundaries without exploring.

Ey wondered what must have happened to eir body back in reality, even as ey walked toward the front doors. Ey didn't feel hungry. Such things were translated in-sim — safety measures to keep addicts from starving themselves. After all, ey had still felt the need to sleep. Something had obviously been done with eir body.

That train of thought wound around the question of how exactly ey had gotten lost in a sim without being connected to it. Were other lost individuals in whatever sims they had been before, empty now of others?

Obviously, plenty of time had passed, and certainly the crew hadn't left em just sitting at eir rig after ey had finally lost touch. Even so, ey should've been pulled back to that reality when eir hands had been lifted from the cradles and head pulled away from the NFC headrest.

And yet here ey was.

Where was eir body, then? Some hospital somewhere? Insensate and tied to life support?

And if ey was in a hospital, where did this sim exist? A sim this size couldn't simply live in eir gear. Especially not with all of the mechanics ey had encountered so far. Fully functioning sound booth and mic. All of the papers in the office. The sleeves hanging from the racks ey had brushed eir hand across on the way to the couch.

No answers to be had. All ey could rely on was what was in front of em.

Ey stopped at the bank of front doors, staring at the panic bar. Would it be locked? Would it open a touch? Should ey slam eir weight against it, or test gingerly?

Resigning emself to whatever happened when ey pushed it, ey rested eir paws against the smooth metal, claws clicking against the door itself, and gave a firm shove.

The door swung open and ey laid eir ears back, squinting into the bright sunlight beyond. Holding the door open with one paw, the other shaded eir eyes.

Ey saw the cul-de-sac for dropping kids off. Ey saw the street beyond, the set of townhouses that lined the road opposite the school. Ey saw grey. Ey saw fog. Despite the very sunny day, shadows cast sharply against concrete, ey saw fog.

Fog of war? Render distance? That visual indicator representing the furthest that the system was willing to draw?

Old tech. Tech unneeded for perhaps a century. Was it a limit of eir exo? Some languishing remnant? It had occasionally been used as an invisible boundary, ey knew. That it was there in the first place, closing off the street in either direction about a hundred yards into the distance, confirmed that this was indeed a sim, not just some artifact of eir subconscious.

Did it, though? Did it confirm that? Did that truly follow?

Ey stepped out onto the sidewalk by the flagpole and stared. Shoulders sagged. Tail drooped. There were no answers. No answers.

Nothing for it but to keep looking.
