\hypertarget{rj-brewster-2112}{%
\chapter*{RJ Brewster — 2112}\label{rj-brewster-2112}}

No menu.

No menu and no HUD.

Without eir HUD, there was no way that AwDae would be able to teleport. Ey would need to swipe up a destination entry and tap or speak the command for sending emself off. Hell, even if ey \emph{were} able to get at the menu, ey wouldn't have the coordinates for any of the particular places ey had come up with to visit.

If they even had coordinates, that was. Of all eir explorations, ey had begun to doubt that this was a sim. No sim, no coordinates. No coordinates, no menu, no teleport.

Ey would have to walk.

Not that walking would be tiring. No calories burned when taking simulated steps in a simulated environment.

All the same, the prospect felt exhausting.

Eir first location on the list had been the university, that sprawling campus where ey had studied (and, later, pioneered) the integration tech ey used daily at work. Without teleport, however, that was out of the question. It was halfway across the continent.

``Something more manageable, then,'' ey grumbled.

The walk to the clinic where ey has had eir implants installed was halfway across town. It would take a few hours to traverse, ey supposed. A guess. Ey had never walked it before.

Ey had time, though. All the time in the world.

With little to do, ey slept early and woke early in turn. If it was to take a good chunk of the day, at least ey could do so while it was light out.

Shouldering the appropriated pack, ey set out from home as soon as it was bright enough to do so. A short walk down to the school, then further down the hill toward Broadway, which would get em most of the way there. After that, two blocks east, and ey would come across the squat, white building of the clinic.

From there, it would be easy. There had been about a dozen appointments in the building, so ey knew it well enough that it would likely be in reasonable shape. Hopefully the doors would be unlocked.

The first skip happened halfway down the hill from the school.

AwDae reached the corner of the fence surrounding the track and football practice field, remembered eir brief jogging phase, and how ey always turned north through the neighborhoods before reaching Broadway, which was always so noisy, and then ey was gliding down the street in a sitting position.

Ey yelped, startled, and flailed eir arms out for support, left elbow catching painfully on something solid a foot to the side of em.

The skip took perhaps a second all told. A second of blurred darkness, of shadow and motion. A second of panic and confusion before the rest of the car formed around em. Ey was sitting in the passenger seat of the family sedan, coasting down the road toward Broadway at what must have been the speed limit.

The car, like the books in eir room, took a while to swim into focus. Even then, parts of it shifted indecisively, unable to come to rest in some solid, known state. Ey had only tried to drive it once before giving up on the prospect, so the dashboard in front of the steering wheel was particularly vague. Hints of dials, with no needles on them. Smudges of marks on the levers on the steering column. The back of the car lurched in and out of focus sickeningly.

Ey realized ey was holding eir breath and let it out in a shaky whine.

The car continued down the street toward Broadway. Turned smoothly without stopping at the light. Accelerated seamlessly, without haste. The soft hum of the engine and the road noise beneath the wheels was as indistinct as all of the visuals. Indistinct and disconcerting.

After a few short blocks, AwDae had a hypothesis. Of course the sim — correction: eir memories — did not include walking along Broadway. Ey had never done it. Ey had only driven. Or been driven, as ey had never gotten a license emself. All eir memories could dredge up were those of the car, of moving smoothly along the road.

No teleportation, then. Just fast-travel.

Eir one experience with hallucinogens had prepared them for the blurring, smearing effect of the world around em. At least, somewhat. The fog did not diminish, but it played tricks with the buildings lining the road to either side. There was the house with the psychic's sign out front, relatively clear. But the rest of the buildings were shifting, unsettled. When focusing on them, AwDay saw them as flat facades. No depth. Textures on a low-poly wireframe. It was a nightmare of that hidden time of intrasaccadic perception, that moment of suppressed visual input when one shifts one's gaze. That moment laid bare, elongated.

Ey moaned and closed eir eyes. The sights were wrong. The sound was wrong. Even the feeling of acceleration and deceleration, the swing around turns, was off, as though the entire universe was poorly rendered. It \emph{was} poorly rendered. Eir stomach turned at the wrongness of it all.

The next skip hit as the memory of walking through the parking lot of the supermarket at Broadway and Timberline asserted dominance over the memory of driving along the thoroughfare. So suddenly was ey on eir feet and walking parallel to Broadway, so surprising the shift, that ey stumbled and fell to eir hands and knees.

AwDae retched. Nothing came up. Not even the sting of bile.

Ey lost track of time, sitting in the empty parking lot. Half an hour? An hour? Trying to master the urge to return home and disappear beneath the covers. Anything to avoid that horrible, half-remembered drive.

And yet, ey had to do \emph{something}. If there was even a chance of em being able to get out of this dream, this non-place, ey would have to keep moving. Keep moving and hunting and looking and thinking.

With a groan, ey stood and walked toward the road once more.

The skip came as expected, and ey gritted eir teeth as the world whirled past. Perhaps ey would be able to make it to the east coast, but if that meant eight hours of this — home to the airport, the plane, a different airport, transit to the dorms — well\ldots{}hopefully there was a work-around.

The rest of the journey to the clinic passed without further skipping. There were a few shaky moments passing through the pedestrian mall, where ey'd spent countless hours walking, but apparently ey had spent nearly as much time traveling along the road. Eir `car' continued down the empty street, blithely changing lanes to pass cars that weren't there, turn signal and steering wheel moving on their own.

And then parked.

The low-slung building of the clinic was just as AwDae remembered it.

The idiom got a laugh out of the fox. Perhaps that was literally true. It could be no other way than how ey remembered it. The building was as it must be.

Preempting another skip, ey scrambled to open the door of the car and hop out on eir own before it was done for em. With a satisfying thunk, the passenger door of the dusty blue sedan swung shut behind em.

\emph{Promising,} ey thought. \emph{Perhaps I just have to be more deliberate about it. I'll get in the car later, follow the drive back home, and maybe it'll park in the driveway as easy as that.}

Eir claws clacked against the pavement leading to the smoky glass doors. It wasn't overly warm out, but the cool air that breathed out of the clinic was refreshing nevertheless. Something static. Something still. Something known.
