\hypertarget{tycho-brahecastor-2346}{%
\chapter{Tycho Brahe\#Castor — 2346}\label{tycho-brahecastor-2346}}

After a certain point, when you get so far from the sun, the concepts of day and night stop meaning so much, and you rely instead on long habits borne out of a necessity to sleep, and to sleep generally on the same schedule as others. And if you must do that, you might as well follow the same schedule you've always kept, the same day-night cycle that even Earth understands. The same clock ticks across three different Systems.

And so it is that, in some wonderful serendipity, all three members of the Balan clade are asleep. Both Codrins have fallen asleep with Dear in their arms, as they so often do, while both versions of Dear's partner curl a few inches away, never having done well being touched while sleeping. The foxes fit so nicely against their fronts, their fur so soft.

Ioan sleeps, too, and in eir arms, May dreams. She is somewhere between waking and sleeping, and has been letting herself hover there for the last hour, while she does her best work, building hypnogogic myths out of dreams and reality both. Ioan sleeps with eir arms around her, snoring gently, while she stays curled against eir front, head tucked up under her partner's chin, tail draped loosely over eir hip. The skunk fits so nicely against eir front, her fur so soft.

Perhaps the other Odists sleep and dream and snore and curl, too. End Waking does, one supposes, having worn himself out with another day exploring that endless forest, another day climbing trees and clambering through ravines. Serene probably does, too, so that she can use those dreams to build new landscapes; mountains, perhaps, or maybe a swamp. Some instances of True Name must be sleeping, because we know that she must at some point, but others are likely out and about, walking sims, or perhaps planning with any number of different Jonases, scheming and conniving and workshopping and wargaming.

Douglas sleeps, out there on the dandelion-speckled meadow that he inherited from his long, long, long lost aunt, though he has since built himself a house.

Yared and Debarre and user11824 sleep.

Ezekiel no longer lives on either launch, is no longer a part of the universe, but one might guess that even prophets sleep.

One who is awake, however, is the astronomer who decided to call himself Tycho Brahe when asked for an interview and then simply decided to keep the name. He is not asleep, because he is too busy alternating between being scared shitless and too excited to breathe.
