\hypertarget{de—2325}{%
\chapter{de - 2325}\label{de—2325}}

de smiled sourly down into its champagne. The real stuff, too: the last supply ship had brought up a case of bottles, doubtless from the store of some wealthy oligarch with their finger in the pie that was the L5 station.

It could not taste the quality. It could taste nothing but ashes.

It slipped out of the celebrations early. Barely an hour had passed, and already the two LVs were something like five and a half million kilometers away. Green, heading out-system, was doubtless already deploying its solar sail — it knew that Blue would still have a while yet until its long arc took it past the sun.

No reason to stay and listen to the chatter or monitor the continuous text feeds from the LVs. The chatter would be the same inane bullshit the uploads always spouted. Clades! Sims! All the nonsense of life itself compounded and compounded again by their world of mirrors.

Better, instead, that it stew in the sour taste of its own failure.

The hab level was something of a relief after the command bulb, where the gravity had been harsher. Here, it could walk freely, feeling light, almost springy. It walked spinward, past the quarters and old hotel. It walked past the hydroponics labs. It walked past the long, thin strip of a park. It kept walking until it reached the manufacture sector, and then it turned to walk `north', perpendicular to the spin toward the sun.

The door to the factory slid open smoothly to a touch from its contacts, and de stepped into the crowded, red-lit space. It walked along paths of yellow-black tape, pausing to let the occasional autonomous worker bot pass, each of which beeped a cheery tune at it.

It gave them a variety of rude gestures each time.

When it reached the extrusion factory for Blue's launch strut, it climbed, a ladder up, in toward the system itself. It climbed slowly, feeling each rung beneath its feet, feeling the gravity lessen by the step.

Through an access hatch, a crawl around the cramped base of the extrusion machinery, and it reached the spot where it had placed the explosive. It was a thin putty around the base of a tube, looking precisely like the sealant they used to patch leaks across the station.

It scraped the putty away and pulled out the microfilaments, pocketing them separately.

And then back the way it had come.

From there, it leaded to the suit bay where it kept its personal EVA skinsuit — one which conveniently contained a fault in the audio recording system that it somehow kept forgetting to fix.

Once de had suited back up, it climbed up once more, waited for the airlock to cycle, then clipped onto the safety wires and walked (or bounced) carefully along the inside of the torus out to the south end of the torus. It stood there for a moment, looking out into the wheeling stars beyond. It stood for nearly an hour before it reached into the pouch at its hip, fished out the explosive and filaments, and dropped them over the edge, watching them fall away anti-spinward, quickly disappearing against the black of space.

Then it screamed. It screamed and shouted and cursed and cried, sending its suit-mask dehumidifiers into overdrive.

When its tantrum had finished and the urge to toss itself off the torus as well, it turned around, walked back to the airlock and re-entered the station. Doffed its suit. Trudged to its quarters. Fell into bed.

It was a failure. It had accomplished all the steps that it had wanted to, that its collective had wanted to, and then it had failed to complete the act. Now it was too late, and there was nothing to be done.

de lay, curled in bed, for who knows how long. It was sure that it slept somewhere in there, though it did not dream.

When it returned to its senses, it pulled out a pad and began composing the message home.

\begin{quote}
2325-01-21

d*,

I regret to inform the collective that the launch proceeded today without my actions complete. Both LVs are on their way undamaged, and the System continues as it always has.

The failure rests entirely on my shoulders and there is no excuse for my actions or lack thereof. I can't explain the reasons for them, not yet, but I will continue to meditate on my failure and report back as soon as I have reached an answer.

I await your response and my penance.

Yours, faithless,

de
\end{quote}

It did not hesitate to send the message. In all likeliness, the d* collective already knew that its mission had failed, as the news of a successful launch had certainly been received by the Earth elements of the Launch Consortium.

A response arrived less than a minute later.

\begin{quote}
2325-01-21

de,

Message acknowledged. Decisions in subsequent message.

Disappointed but not surprised,

db
\end{quote}

\emph{Disappointed but not surprised}. The words hung before de long after it tossed its pad onto its desk and rolled over to face the wall.

\url{It} would meditate. Or it would sleep. It no longer mattered which.
