\chapter{Aposematism}

``Alright, bid phase.''

Kira scowled down at their hand, their pile of tokens in ones and fives, and listened to the bids go around the table. Once more, when the bid reached them, they were out of their price range. They had the cash, but not if they still wanted to purchase the ornithopter card down the line.

``Pass,'' they grumbled.

The dog to their left picked up the lasgun, dopey grin plastered to his muzzle.

Kira sank deeper into their seat.

``Bidding phase ends,'' the \emph{de facto} leader of the game called, and then once more ran through an explanation of the movement phase of the game.

While this sort of territory control game was one of Kira's top choices, it also featured this bidding component, something which brought out a fiercely competitive streak in them. They didn't like who they were when they were bidding, when they were always thinking about how to build some ideal hand with which they'd deal a crushing blow.

It stole reason from them. It turned tactics on their heads and left them more frustrated than any game without might otherwise.

They should have just bowed out.

``Hey. You ready for movement?''

The skunk jolted upright in their seat and scrambled to get their cards in order, the dog to their left giving an apologetic sort of grin for having startled them out of their reverie.

``Yeah, sorry. Uh\ldots I'd like to beam two down to Bled and then move one space to the south.'' \emph{If I'd had the ornithopter, I could have moved three,} they continued silently.

``Alright that'll be six,'' Avery, head of the transit guild, murmured, the mountain lion's brow furrowed as he read through his notes. ``Though I'll let you do it for five if you turn east after that.''

Kira peered down at the board from above, taking stock of where all of the pieces were. A small concentration of their forces lay to the southwest, but so did a few of the transit guild's scattered forces.

``And I'll pay for half your transit costs if you don't turn east,'' the dog countered.

``And what, not attack you?''

That canine grin once more. ``Yep.''

Kira nodded thoughtfully, then reached over with a ring bedecked paw, the drape of their sleeve scattering neatly-stacked money chips, and offered to shake on it. ``Deal.''

The mountain lion scowled, but accepted three chips each from Kira and the dog --- some breed with long, golden-colored fur --- before placing the skunk's chips on the square marked \emph{The Bled} and scooting them one space to the south.

The game continued apace. With each turn Kira and the dog's alliance grew stronger and Avery's frustration more apparent. By the fifth round, when it was possible to form concrete allegiances in the game, it was only natural that Kira and Riley would form one.

They won handily. Kira even got their ornithopter.

The game was long enough, however, that by the time they had to start putting it away, the task of putting all those tiny money chips and figurines back into the slots of the box felt arduous and impossible. The cardboard felt simultaneously slippery and sticky between their fingers, and the refusal of inanimate objects to obey even the simplest of commands left them frustrated.

\emph{Tired,} Kira thought. \emph{Too tired to deal with this.}

``Kira? Hey. You okay?''

``Mm?''

Riley was smiling. Not a grin, the skunk noted, but a kinder, gentler expression. ``You doing alright? Looking kind of tired, there.''

``Yeah, pretty tired,'' they allowed. The lid of the box had finally been slid back into place, the flatulent noise of the box being shut setting their teeth on edge. ``These games always run so long.''

``Tell me about it,'' Avery said. ``Good one, though. You two kicked ass.''

``Mm,'' they allowed. ``Thanks for running tonight.''

The mountain lion grinned and nodded. ``Hate to game and run, but I got class in the morning, so I'll catch you all later. Same time next Wednesday?''

The group nodded. Avery waved, hiked their pack up, and ducked out into the night. The shop owner shooed the rest of them out after so that he could start cleaning up.

Kira thumbed at their phone, pulling up GetThere to hail a ride for the night. Nearest driver was a good ten minutes away, but at least it was a warm night. Besides, it'd give them a chance to smoke. They stepped away from the rest of the crew toward walkway that led to the plaza, lit their cigarette, and stared up at the washed out stars.

If tonight was a night for reveries, this would be a good spot for it. The chatter of voices, the taste of smoke hot on their tongue, and a ride on the way.

There was no pinning down their mood. They were pleased, they supposed, that they had won the game along with Riley. They were pleased that they got their ornithopter. They were pleased that they had even made it out tonight, had worked up the executive function required to get out of the house and head to the store for games.

And yet all those thoughts, all those things to be pleased about were like water. They kept bubbling out of reach. Any time they would try to hold onto one of them, it would trickle through their paws. It may leave them damp with a residue of positivity, but it would not stick, it would not stay.

``Going to make it home okay?''

Kira levered themself out of the reverie by force of will, stubbing out the sweet-spicy cigarette on the bottom of their shoe and tucking the butt into the empty pack they kept around for just such a purpose. Riley had walked away from the rest of the group --- now half the size it had been before --- and was standing beside them at what felt like a respectful distance.

The skunk wasn't sure why it was that they felt compelled to describe the distance as respectful. Riley was friendly enough. There was nothing about his attitude that suggested he was afraid of Kira. And yet here they were. Was it the smoke?

``Yeah, I should.'' They pulled out their phone to check on the ride. ``Five minutes away, looks like.''!\{Check tone against start of story\}

The dog nodded. ``Long drive?''

``Nah, not too long, but I'd prefer not to get beaned by a car on the way home.''

Riley laughed. ``I would hope so.''

Kira smiled faintly at him. It was a lame attempt at humor, but the laugh seemed earnest.

``Look, uh.'' He scuffed a shoe at the pavement. ``I don't know if it's too late to cancel the ride or anything, but if you'd like, I could get you home?''

The skunk tilted their head, the weight of piercings dragging ears down. ``Yeah? Let me check. You're not going to abduct me or anything?''

Another laugh. The dog laughed so easily. ``No, promise I won't abduct you or anything. Just figured a friendly face doing the driving might be more fun.''

Apparently, so long as the driver was more than a minute away, it was free to cancel the ride. Kira let their thumb hover over the button, frowned, shrugged, and tapped. The app confirmed the cancellation, and they pocketed the phone before holding out their fist, pinky extended. ``Alright. Pinky swear.''

Riley looked taken aback, then grinned and looped his pinky around Kira's just past the rings. Squeezed. ``Pinky swear. C'mon, let's say goodbye. I'm only a block away.''

Goodbyes were short and jovial, if tired. Kira and Riley got a few more handshakes and 'good game's. And then they were off, the dog walking quietly in tattered sneakers and Riley clomping along in boots beside him.

The two walked in silence. It was easy. Surprisingly so, Kira thought. Something about Riley had them thinking the dog would be more of a chatterbox than he was, but they simply walked in comfortable silence, each enjoying the last of the night in their own way, if what Kira was experiencing could be said to be enjoyment.

``Alright, here we go.''

They split around either side of the beater sedan that was Riley's, and after a strained-sounding click from the automatic locks, Kira climbed into the passenger seat. It was startlingly clean within, despite the battered exterior.

``Hey, nice. Thanks again for the ride.''

That got a wag out of the dog as he was sliding into the seat beside them. ``Yeah, no worries. Was a good night, figured a bit more wouldn't hurt. Where are we headed?''

Kira gave their address and some abbreviated directions, though Riley seemed to know where he was going on first mention.

The car started up with a surprisingly muted purr, the dash lighting up with subtle purples and oranges.

``Jesus, I wasn't expecting this from your car.''

Riley grinned. He looked pleased with this. ``I'm a fan of sleepers. Not going to open it up much tonight, but, uh\ldots it's fast.''

``Never pictured you for a car type.'' Kira buckled themself in. ``I guess I never really equate nerd with nice car.''

``Oh, trust me, car nerds are definitely a big thing.''

``Yeah?''

``I mean, if nerds are the types of people to care about something in fractal detail, then yeah. You can always do more, always research more, always find new folks to geek out with over cars. It's big.''

Riley pulled out of the parking space smoothly as he spoke. The car was extremely quiet, and yet somehow threatening for that. It felt crouched. Spring loaded.

``So, what's a `sleeper', then?''

The dog got the car in gear and lounged back in his seat, one paw on shifter, one paw on steering wheel. ``A car that looks like junk but is actually really nice.''

``I would've thought that car nerds were all into making their cars look as cool as possible.''

``Oh, that's definitely a big part of it for most people.'' They slid out onto the street smoothly. Kira knew little about cars, but the smoothness with which Riley was shifting was almost disconcerting. ``Me, though, I like things that are kind of a surprise. Y'know, really nice despite expectations.''

Kira nodded. ``I can see the appeal, yeah.''

There was a moment of silence before Riley continued. ``Kind of like you. I mean the really nice bit, not the looking like junk on the outside bit. I like the way you look.''

The skunk stiffened in their seat and frowned over at Riley.

``Uh\ldots sorry.''

``No, it's okay.'' They spoke cautiously, forced themself to relax. ``I just wasn't expecting flirting.''

``Yeah, sorry about that.'' Riley was clutching at the steering wheel perhaps a little too tight. ``Guess I'm still a nerd, right? No good at social cues.''

Kira laughed. The apology, the tenseness, the nervousness, they were all disarming and endearing. ``No, really, it's okay, Riley. I just wasn't expecting it, is all. My mind's been all over this evening.''

He relaxed at the reassurances. At least a little bit. ``Alright, yeah. I get that.''

Another small silence. Riley kept his eyes on the road, Kira kept theirs out the passenger window.

And then, ``But hey, thank you. That was sweet.''

That \emph{definitely} got a wag. ``Yeah. I dunno, you're just nice.''

Kira laughed. ``I don't know about that.''

``Nah.'' Riley shook their head. ``You are.''

They felt heat rise to their ears.

``But hey, I pinky swore I wouldn't abduct you, and we're just about here, so\ldots{}'' He trailed off, nerves perhaps getting the better of him, then the rest of the sentence came out in a rush. ``What do you say to dinner sometime soon?''

``You mean a date?''

``I guess, yeah.''

Kira tapped at each of their rings in turn with dull thumbclaws, bit at the inside of their cheek, averted gaze. Nervous habits ticked off one by one. ``Fuck it. Why not.''

Shoulders sagging, Riley let out a puff of pent-up breath. ``You sure? Don't want to force you into anything.''

``I'm sure.'' Kira laughed. It sounded strained to them, but Riley perked their ears all the same. ``Just never been on one before. Nervous.''

The car slid to a stop near the curb in front of their apartment building. Riley shifted into park and looked sidelong over at the skunk. ``Well, so long as you're sure. And no obligation, of course. Pinky swear.''

Kira blinked at the offered pinky, then grinned and looped their own around it. ``Nerd. Yeah, I'm sure.''

That wag was back, the dog's tail thumping against the paneling of the car. ``Good.''

They traded PostFast contacts, made their goodbyes, and Kira was out in the night once more, watching that beater pull smoothly away from the curb, engine sounding twice as menacing from the outside.

Kira watched until the car turned turned back out onto Seventeenth, turned, and walked inside. They still couldn't put their finger on their mood, but if nothing else, it felt more positive than before.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

``So, I've never done this before.'' Riley laughed. ``But I hope this isn't too out their or weird or anything.''

Kira clomped alongside the dog, surveying the storefronts and restaurants along the plaza. They frowned and shrugged. ``Well, neither have I, but hey, it's alright.''

"
