\chapter{Foxes and Milkshakes}

Two foxes walked into a bar.

Well, okay, a diner. But most of those middle-American diners are outfitted with a bar type area, complete with red-and-chrome stools --- you know the sort --- which is close enough, capitalizing on that thirty-year nostalgia cycle in the way it hearkens back to the 50s or 60s. Both were full of giggles, outfitted with grins and their most casual of ``nice'' clothes. Somehow managing to look similar without being related, the two got along as though they were brothers. One was taller than the other, and though both were thin, he came off as lanky, whereas the shorter fox seemed more waifish --- more of a track runner than his friend, the basketball player.

Although the restaurant was nearly empty --- its only other customer being one of those old hound dogs who sits at the bar, perpetually nursing his second cup of coffee while staring at the gold flakes on the formica counter as if they might somehow swirl into formation to reveal the deepest secrets of the universe or maybe just the solutions to all his problems --- the two convivial foxes made their way to the corner booth and plopped down across from each other.

Their animated discussion, more gossip than anything, was interrupted by a cat on roller skates popping her gum loudly by the table.

The foxes grinned up to the waitress, who, picking up on the jovial mood, beamed down at them. ``What'll it be, you two?''

Straightening up, the larger of the foxes proclaimed, well rehearsed, ``A vanilla shake, please, and a couple of spoons.''

The waitress' eyes flicked between the two, but she said nothing, simply taking down the order before rather pointedly asking the other fox what he'd like. The smaller of the two stammered for a second, caught off guard, ``Uh\ldots c-coffee, please.''

The rollercat nodded and skated on off, leaving the two foxes to glance at each other, nervous, unsure as to whether they'd committed some sort of faux pas. Each shrugged at each other at the same time and both giggled, slipping back into their animated chatter. The hum of a shake blender promised sweetness.

The feline rolled smoothly up to the table again, this time with a tray holding a shake, two mugs, and a carafe of coffee. Setting the shake pointedly before the larger fox and the two mugs in front of each of them, she poured them both a cup of coffee before zooming back to the kitchen with the kick of a skate.

The coffee sat ignored by both foxes as each grabbed a spoon from the shake, pulling it out to get that first bite: that one where the spoon's already covered with a liberal coating of shake, whipped cream, and chocolate sauce, somehow better, more complete, than the spoonfuls to follow. Coated spoons made their way into waiting muzzles and that sweetness spread like silver smiles.

With much laughter, the conversation continued, drifting from teachers, perhaps, to movies, parents, probably, to homework. Slowly, carefully, the shake was diminished, each taking care to leave the maraschino cherry standing in the middle of the glass atop a pillar of sagging whipped cream.

The talking wound down until the two were eating in silence, the taller of the foxes apparently lost in thought as he stared out the window, while the smaller watched his friend with tilted head.

``What?'' asked the larger vulpine when he caught the other's gaze, muzzle painted with a lopsided grin.

Laughing, the fox shrugged and dipped his spoon in the slowly melting desert, holding it out to the taller fox. Giggling at the patently tacky yet oh-so-sweet gesture, he leaned forward to take the proffered bite. Resting his chin on his the backs of his hands, he smiled happily as he let himself be fed another few bites of the treat.

Grin softening to smile, the shorter of the two fished around in the bottom of the glass with his spoon to get at the cherry, bright red, so bright it almost glowed beneath that coating of whipped and iced cream. Picking it up delicately by the stem, he offered that as the next bite, movements slow and deliberate. The larger fox leaned forward, delicately picked the almost-too-sweet fruit from the stem, and savored. If pink had a flavor, it had to be this.

With his co-conspirator in shake-enjoyment still leaning forward, it took little enough for the smaller fox, movements deliberate --- if shy --- to press toward him across the table. It was fairly clear what he intended to happen next, snouts aimed at snouts, young love pinkening the insides of ears.

Clear even to the waitress, who had rolled up at this inopportune moment to refill untouched coffees. With a snap of her gum and a look hovering between disgusted and weary, she jotted something on the order pad, slapped the sheet down on the table. She grumbled, ``Should'a known,'' and pushed off towards the kitchen.

Two foxes sat in stunned silence for several seconds as the matching blush shifted from one of embarrassment, nigh on humiliation. Shaky paws snatched at the check, the larger of the two's eyes going wide, while the smaller's welled up with tears, anti-sweet and hastily brushed away.

``Get a room queers'' was written under items ordered on the check, ``get out stay out'' scribbled hastily at the bottom. Taking that as their cue to take their leave, the pair made a clumsy escape from the diner, followed out the door by the disdainful gaze of the rollercat.

Once they had made it out onto the curb, warm evening air wrestling with the spreading coldness of milkshake and humiliation, the two foxes hazarded cautious glances back through the glass into the diner. The waitress watched still from behind the counter.

They decided on home instead.

They walked slowly down the street toward the larger fox's house, the closer of the two homes, in silence, very carefully not touching. The taller of the foxes kicked at the sidewalk, more trudging than walking, and the smaller fox peeked over with apologies in his eyes.

``I didn't think\ldots{} I mean, I guess I shouldn't have done that\ldots{}''

Nothing.

``I'm sorry, I guess I though it'd be\ldots{}'' he trailed off once more.

Still nothing. The larger fox was looking down at his shoes as they scuffed along the concrete, paws stuffed deep within his pockets.

``I think we should call off the rest of the night.'' He walked in silence for a few more steps, brow furrowed, before repeating, ``We should call off the rest of the night. See you tomorrow?''

The shorter fox stood still for a stunned moment before hurrying to catch up with the taller of the two, grabbing at his elbow. ``No, wait.''

The taller fox stopped, but would not or could not meet his friend's gaze.

``I'm sorry,'' continued the smaller fox. ``Please don't go.''

The tall fox turned slowly and unhooked the paw from his elbow, taking it instead in his own, slipping his other free of his pocket to hold both of his friend's in his own. ``I just feel weird about things, you know? If we were up in Boise, maybe, but what the heck does Sawtooth need with us?''

``Well, shucks, I do too, but\ldots{}'' A pause, then a defeated shrug. ``It was still a nice night, wasn't it?''

A smile tickled at the corner of the taller fox's mouth and the tenseness in his posture softened. ``Yeah,'' he said at last, nodding. ``Yeah, it was still a nice night.''

Shy smiles were shared, sweetness ticking back up a notch or two, then both looked down the street to where the larger fox's home lay, to the soft glow of the porch light.

The taller fox turned to look back the shorter, grunting in surprise when his muzzle clonked against another. One which had been aiming to give him a kiss on the cheek. Both blushing foxes mumbled apologies at the same time, giggled, and pressed into an awkward kiss. Noses all mushed together, lips not quite hitting their mark, and all the sweeter for it.

Two foxes stood on the sidewalk, half in light and half in darkness, working out the logistics of their first, vanilla-flavored kiss: all the little things that make fox-kissing nice, like tilting muzzles just slightly so that the nose is out of the way and standing on tiptoes, exploring new intimacies. Ears laid back and tails all aswish, still holding hands, the couple relaxed back from the kiss, bashful and giddy

Still blushing, still grinning, still paw in paw, they continued on their way to the taller fox's house.

``Times are changing,'' the smaller vulpine observed as they neared the low-slung suburban home. ``I think for the better better.''

The other fox was slow to smile, but it was an earnest one. ``Yeah,'' he murmured, nodding slowly, as though his mind was still churning away. Sweetness still hung about them, vanilla still lingered on lips, tongues. ``Y'know what? I take back what I said earlier. You want to come in for a while?''
