\chapter{Gigs}

\emph{Well, shit.}

Winter trudged heavily through the piles of dead leaves lining the gutter, the lynx's broad paws crunching through them. There was a sidewalk, but this wasn't a mood for sidewalks. This wasn't a mood for keeping clean, staying out of the way. This was a proper sulk.

She pulled her phone out for the umpteenth time and thumbed at the screen, tapping out yet another message to Katrin that she wouldn't send. Deleted message. Put phone away.

A low growl started in her chest, rose, crescendoed, and she let out a brief yell. No words, just a vent of frustration. Birds startled from the tree beside her.

It didn't help.

``Making a damn fool of yourself,'' she grumbled. ``Twice over.''

She hesitated on the corner of Linden and 18th, stopping mid-stride and staring down the street. She should turn. She should turn left and walk the next two blocks. She should head up the stairs. She should open the door, set her phone down, change out of her clothes --- clothes she'd now have to return to the market --- clean up, start cooking.

She should tell Katrin what happened. She should look for a new job.

``Shit,'' she repeated, this time aloud, and kept walking straight. Five blocks to the plaza. She'd grab a coffee, sit on one of the benches. Watch the early afternoon crowds putter along the mall.

Or maybe she shouldn't grab a coffee she could no longer afford. Maybe she should be saving her money.

She kept walking.

She got her coffee.

She sat, and she watched.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Katrin and Winter stood still, heads bowed, both searching through their thoughts.

Winter couldn't guess at her wife's thoughts. The fox was always so inscrutable. Winter would sometimes watch her face while the vixen worked, the blank mask of pure white, punctuated with only the pitch-black nose, those darkest-brown eyes, and try to decide if the inscrutable part was the all-white fur or some sort of Scandinavian magic.

Today, she couldn't tell. Katrin's matte-white fur reflected light so well that there were no shadows left to reflect her emotions. And yet, there was still something foreign to those features. The almond-shaped eyes, the blunt muzzle, the ears almost hidden in thick fur.

Perhaps another Swede would be able to read that face, to say what Katrin was feeling, but not Winter. Not right now.

``And they didn't give any recourse?'' The fox looked up to Winter. ``Just \emph{come pick up your last paycheck and drop off your shirts}?''

The lynx nodded. ``Just that. Mr.~Stevenson just said he couldn't keep both managers on board, and, well, Kayla's his daughter.''

Katrin nodded and slid her paw across the counter top to twine her fingers with the lynx's. ``I understand. I'm sorry, love.''

``It's okay.'' Winter sighed and gave those fingers a squeeze in her own. Even with the flour still clinging clinging to her wife's fur, even with the coarseness of her pads, worn from so much kneading of dough, they seemed so delicate in her thick-furred mitts. ``I'll start looking tomorrow.''

``Okay. Let me know if you need any help, I'll do what I can.''

The lynx nodded.

``It'll be okay, love. I promise.'' Her smile was tired.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Gone were the days of sitting up at the kitchen table, circling help-wanted ads in the newspaper. Hell, gone were the days of the newspaper.

Instead, Winter grew addicted to job posting boards, both local to her town and some that ran on a wider scale. Once she got her résumé all fixed up, she began flooding local stores with it, starting with all of the local grocers --- as Stevenson's had been --- and then broadening her search to related retail outlets.

And then unrelated.

Then non-retail positions.

She would work in shifts, spending an hour prowling through postings, then spending five minutes making sure her files were in order, then another two hours applying. The act of uploading a résumé to a site that promised to read all it could from it, then required her to fill in all that information again in form fields became rote, numbing.

There were a few calls back, but more often than not, silence. It was starting to feel futile. It was starting to feel like hollering into the void. She would click submit on yet another application, and it would just\ldots go away. It would go nowhere.

Even an outright rejection would feel better.

She had set herself a week to exhaust all of the usual application channels. On the third or fourth day, she started driving around to stores and dropping off paper copies of her applications as well.

It was on one of those outings towards the end of her time-boxed week that she first noticed the ride share sticker in someone's window.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

``Winter? For Malina?''

``Yep, that's me,'' the lynx replied cheerfully.

``Great!'' The badger hauled a few sacks of groceries into the back seat and slid in after them. ``Thanks so much for the ride. Car's in the shop and all.''

``Oh, no worries.'' Winter waited for Malina to get herself buckled in before tapping at the GetThere app on her phone to set the satnav to direct her to the badger's destination. ``Hopefully nothing expensive?''

Malina laughed. ``Shouldn't be. One of those warranty things. A part recall or something. I'm out a car for a day or two, but at least I don't have to pay for it.''

``No loaner, then? Do they even still do that?''

``I'm not sure, honestly. They might. But either way, I'm within walking distance from work, so I figured it wouldn't be that big of a deal.'' With a wry smile, she added, ``I just wasn't counting on having to do a grocery run for work. Starts getting cold out, and we start mowing through milk.''

Winter slid the car back into traffic --- mercifully light today --- and started down the road back toward 13th. ``Fair enough. Where do you work, that you go through milk so fast?''

``A coffee shop. The Book and the Bean, on the plaza. There's a few shops within walking distance that sell dairy, but none of them sell the more exotic milks, so I have to head further out. Easy enough to walk there, but I'm not hauling all of this back.''

``Oh, yeah! I know the one. My wife's restaurant, Middagsbord, is just down the block.'' She grinned. ``I doubt those bags are light, though, yeah.''

Malina laughed and shook her head. ``Not at all.''

There were a few moments of silence as Winter negotiated a left turn and the badger in the back seat thumbed through her phone.

``How about you?'' came a distracted voice from the back. ``Is this your full-time thing? Driving?''

Winter shook her head. ``Not exactly. I just started this not too long ago. This and random gigs on Simpletask.''

``What's that?''

``Just random things people want done but don't want to do themselves. I've done filing, transcription, cataloging\ldots boring stuff, really.''

Malina nodded. ``Sounds like driving's the more interesting of the two.''

``Wasn't really my first choice, but it's turning out to be way more fun than I thought it would be.''

``Oh yeah? What about it do you like? Setting your own hours?''

``I try to work pretty standard hours, though for me that means working morning rush hour driving, doing some tasks, driving during lunch, more tasks, and then evening rush hour.'' Winter thought for a moment, then continued, ``No, I think the thing I like about it is that it gets me a lot of the best things I liked about retail without the standing all day or dragging boxes around.''

In the rear-view mirror, Malina grinned. ``Yeah, that makes sense. Just the meeting people sort of thing?''

``Mmhm. Meeting people, being helpful. People are generally kinder here than they are in stores, too. Most folks are grateful for the rides, and those that aren't having a good day are usually pretty quiet. I don't get many people hollering at me.''

Malina laughed. ``Oh, I know that one. I used to work in finance, but got sick of it. I figured moving to where I saw people instead of numbers would be easier on the soul. I was mostly right.''

``Mostly?''

``Yeah. A lot of people are grateful for coffee, but like you said, those who aren't tend to holler.''

It was Winter's turn to laugh. ``Yep, that's the type. I guess that's what I mean, though. I got good at the sort of happy retail mask that one puts on around them, but I haven't needed it here. Not as much, at least.''

As expected, the drive was a short one. Once they made it to the loading zone at the end of the 13th Street Plaza, Winter helped Malina unload the bags of milk and other sundries from the back of her car.

``Thanks again, Winter,'' the badger said, loading herself up once again. ``Stop in any time.''

The lynx nodded and waved before hopping back in her car and turning off the hazard lights.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

While the biggest benefit to this new form of employment was the free-form nature of it, that very benefit worked against it. It was up to Winter to schedule her day around the best times for driving, and the best times for working on projects on Simpletask.

However, when Sawtoothians needed rides was unsteady. Sure, there were times when rides were more likely: rush hour, some time over lunch, Thursday, Friday, and Saturday nights. She started keeping track of sporting events, concerts, and conferences.

Some days, Winter would be flooded with rides, and the lynx would dart all over town, picking up passengers of all stripes and driving them to some concert venue or the UI-Sawtooth campus stadium.

And some days, she would be stuck on her laptop at The Book and the Bean --- Malina having convinced her to become a regular --- waiting for either a ride to crop up or a task she was qualified for. Warm days were usually slow, as folks would be more willing to walk or bike. Some days, she'd make seventy percent of the income for the week, and some days, she wouldn't make a thing.

And then there were the customers.

Her experience of folks being grateful for rides held true, as did her experience of folks having a bad day generally simply being quiet. Those types were both easy enough to deal with, if not outright enjoyable. Over time, though, she began to see a wider variety.

Around Thanksgiving, she started making trips too and from the airport and bus station, and families getting off longer trips were rarely happy. She got snapped at more than once by upset fathers trying to wrangle children or mothers coping with family through stony silence. On one occasion, played therapist along with a coyote to a frightened weasel having a panic attack, in town to visit her family and have some complicated-sounding interaction with her ex-husband.

The worst of all were the drunk folks. When she first started driving folks home from bars, it felt good. She was doing a sort of service by keeping tipsy bar-hoppers or plastered sports fans off the road. The first time someone vomited in the back seat, however, her opinion of the task began to sour. It may be nice to keep drunks from driving, but cleaning vomit out of the foot-wells --- thankfully, the dog had managed to miss the seat --- was hardly a pleasant task.

Football games became a source of dread. She wasn't even safe before they began, as she'd haul thoroughly pregamed fans from parties to stadium, groups of students hollering painfully loud, nigh unintelligible, whether from drink or simple in-jokey camaraderie.

The tasks from Simpletask, while a break from the enforced social interaction that was an integral part of driving, were riddled with their own problems. People generally expected that someone driving for GetThere knew what they were doing enough to leave them alone.

Not so with someone performing data entry from scanned documents or making brochures for events. She discovered a particular brand of cruelty that seemed unique to the role of small business owners, which they held in reserve for menial labor.

The lynx lost track of how many times she was called an idiot. She lost track of the number of times she was lured in by a sizeable tip, only to have it withdrawn after she had completed the project during the three-day grace period. She lost track of how often she was brought on to be the small one, to make someone feel bigger.

Still, she had to pay the bills, didn't she?

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Winter don't know how long she sat in the car, forehead resting against the steering wheel, before there was a soft knock at the driver's side window.

``Love?'' Katrin's voice was muffled through the glass.

Winter looked dully out the window at the vixen, unseeing. Some part of her knew that she should get out of the car and head inside, should at the very least lift her head from the steering wheel, and yet she lacked the executive function required to even do that.

``Winter, can you come inside?''

The lynx took a deep breath. Perhaps it was the lack of something that was keeping her trapped here rather than some unwanted presence. The lack of oxygen. The lack of air. The lack of motivation.

When the breath did not bring any further energy, she let it out in a rush and, through force of will, sat up straighter and unlocked the door. She might have sat there longer, but Katrin didn't give her the chance; the door she was leaning against angled smoothly away from her.

No helping it now.

Winter unbuckled her seatbelt and accepted her wife's paw to help lever herself out of the driver's seat. Together, they shut and locked the car and made their way inside.

Only once she was settled at the kitchen table with a small plate of dill-heavy dumplings --- some new recipe Katrin was testing out --- was she able to loosen up.

``I'm sorry, Katrin. I just\ldots long day.''

The fox nodded, frowning. Never able to completely cease working, she seemed to be dissecting one of the dumplings she had made and was poking at the insides of it with the tip of a knife. ``You've been having rather a lot of those lately, sötnos.''

Winter frowned. ``I suppose. I know it's not exactly ideal.''

``It's okay, don't get me wrong, I'm glad to see that you're out and about doing work. I just worry.''

``Yeah\ldots{}''

Katrin, apparently satisfied with the internal texture of the dumpling, popped half of it in her mouth and chewed thoughtfully. When she had finished enough to do so, she continued. ``Tell me about your long day, love. I want to hear, because it sounds like it was more than simply the length.''

``I suppose.'' Winter stalled for time by eating a few of the dumplings. They were quite good, though perhaps saltier than she would have liked. ``Just had a really gross ride partway through and never quite recovered.''

``\,`Gross' how?''

``He was just really adamant about sitting up in the front seat with me.''

Some inner part of her smiled, despite the competing emotions. She knew she had Katrin's full attention when the fox finally put down her silverware. ``I\ldots see. Are you okay?'' she asked.

Winter nodded. ``He didn't do anything super gross physically, but it was just everything else he did.''

Katrin blinked slowly, ears tilted back. Winter was never quite sure what emotion went along with such an expression, but this time, she was certain it was one of concern or worry. Perhaps anger.

``I'm alright, though, I promise. He just got really pushy about sitting up front and kept saying all these vaguely\ldots uh, sexy things, I guess, and kept staring at me.''

``Did you report him?''

``Yeah, I mentioned it on his review.''

The vixen nodded.

``It just made the rest of my shift feel extra long, is all. Every time I'd go to accept a ride, I'd get nervous. I drove to the other side of town just to be sure he wouldn't request another from me.''

``And did he rate you well?''

Winter winced. ``No.~He complained that I was unfriendly, and I got a note from the system about unacceptable behavior, like it was somehow my fault.''

Katrin reached out a hand to tug one of Winter's over for a squeeze. ``I'm sorry, love.''

Winter returned that squeeze of the fingers distractedly. She couldn't drop the topic, though. Not now. Not after the dam had burst. ``It's just so humiliating. I can't keep myself safe or I risk their ire. I can't look for jobs that pay well because I know they'll just recall the tip after and I'll be out a bunch of cash.''

``It's been a month,'' Katrin said once the flare of anger died out. ``Do you think you might look for something more traditional job again?''

``If anyone's even fucking hiring,'' the lynx growled.

``It's still worth looking, perhaps.''

Winter bit her tongue to stay silent. It must have been evident to the fox, whose frown deepened.

``Winter, you know that I love you and won't push too hard, but this is not healthy. You have been having `long day' after `long day' for the last few weeks. I'm glad you can get paid for stuff like this, but I don't know if it's worth it long term, at this rate.''

``You're right,'' she said after a long, deliberate pause. ``No, you're right. I'll finish these and then start searching again.''

As expected, reference to the food immediately drew the fox's attention away from the problem at hand. ``Do you like them?''

``A bit salty. Maybe more lemon?''

Katrin smiled ruefully. ``The salt is high, yes. I think you're just a sourpuss, though.''

Winter swatted at her wife and laughed. It had been a calculated gesture, getting her to talk food, but one that she knew would distract them both. "Not as salty as you, though.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

``Surprised to see you in today, Winter, and for so long.''

The lynx looked up from her laptop, gratefully accepting hot chocolate number three from Malina. ``I suppose I've been here for a while, yeah.''

``About two hours.'' The badger hastened to add, ``No complaints. The busier we look, the busier we get!''

The hot chocolate was good. Malina seemed to have picked up on Winter's penchant for whipped cream and piled this mug high. Something about the way the cocoa would break through the whipped cream was\ldots not exactly soothing, and yet nonetheless she felt more at peace after.

``As long as I'm not a problem,'' she said.

``Not at all. Just surprised you're not driving today. Figured it'd be lunch hour rush.''

Winter shrugged. ``Not really feeling it lately. Had a string of creeps, so I'm mostly doing Simpletasks and looking for something more stable.''

Frowning, Malina looked around The Book and The Bean and, seeing no one in need of drinks, pulled out the other chair at the lynx's table to sit. ``Hopefully nothing too dramatic happened.''

``No, thank goodness. Just a string of bad luck with lewd assholes.'' She typed at her laptop briefly, pulled up a site, and turned it toward the badger. ``Apparently there's a site for reviewing drivers on a sort of hot-or-not basis, and I guess I made the list.''

Malina's frown deepened. ``I'd say congratulations if that weren't completely disgusting.''

Winter laughed and shook her head. ``Yeah, no congrats needed.''

``There anything that GetThere can do about it?''

``I don't think so. They don't seem to care about the drivers all that much, truth be told. Not like I'm the first to bring it up or anything.'' Winter gave her hot chocolate a slow swirl, watching the skin that was starting to form on the surface ripple. ``They just sent me a canned response of, like, how to stay safe as a driver.''

Malina crossed her arms and leaned back in her seat. ``That's frustrating. Is Simpletask treating you any better, at least?''

Something about the lynx's expression caused her to look away. They sat in silence.

``Either way.'' Winter tried to keep the dejection out of her voice, tried to sound positive. Tried to smile. ``If you have any tips on job openings, I'm all ears.''

``Well, do you know anything about coffee?''

``I\ldots well, no. Are you hiring?''

``We've got some shifts that could use some coverage.'' The badger smiled, shrugged. ``It's a coffee shop job. Doesn't pay much and I don't have a full-time work week's worth of shifts open, but if you're willing to learn--''

``Of course!'' Winter caught herself short and laughed. ``Sorry. Yeah, I'd be up to learn.''

Malina's smile widened. ``Great. Follow me.''

Wrong-footed, the lynx tilted her head. ``What, now?''

``Sure. It's fairly slow. I can at least show you around behind the bar.''

She looked between the badger and her laptop, then shrugged and closed the lid, slipping it back into her bag. ``Well, fuck it. Why not?''

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

The Book and The Bean was not enough to carry Winter, but it was enough to allow her to be more selective in her jobs. She still drove occasionally when not at the coffee shop, but the added income let her focus more on Simpletask.

What it offered beyond that was something less tangible. It leant a sense of stability that the gigs could not. She could always rely on at least a little bit of money to help supplement Katrin's income from Middagsbord. She could trust that a few shifts would help cover her share of rent, and that anything else would be covered by one-off tasks.

More than that, it eased tensions between her and Katrin.

She hadn't realized how frustrated the lack of security made her wife until she had regained it. The vixen once again became easy to talk to. She laughed more readily. She gushed about new recipes and bitched about customers. All those little things that are part of daily interactions that had been tamped down in the face of trying to make ends meet were suddenly back and in full force. That Winter was now working in food service as well certainly helped her case. They could commiserate in ways that neither had expected.

And they were happy, in their own way. A new kind of happy. A different kind. And really, what more could they ask for?
