\chapter{Morning Of}

Something about the phrase 'ambulatory surgery' left the scent of opposites hanging thick in Alex's nose. It certainly wasn't actually an oxymoron, and yet here he was, sitting in the lobby, trying to pick apart why the sign felt wrong to him.

He had spent the last two days running back and forth between the couch or bed and the bathroom as the surgery prep emptied him all out. He had thought, at first, that he would be incredibly hungry on this strict fluids only diet --- and then nothing but a sip of water with his meds this morning --- but some combination of the laxatives and nerves made the thought of food abhorrent, and he had to force himself to stay hydrated as the magnesium citrate worked its wonders on him.

Add in the six hour drive to Portland and the complete inability to sleep during the night before, and it was no surprise that words and meaning were crowding uncomfortably inside his head.

"Alex? You ready?"

He shook himself out of his reverie. Liv was standing there, radiant as always, with an efficient-looking nurse. "Yeah."

They led him back to the pre-op room, where the young wolf stripped out of his clothes and into a hospital gown.

They shaved the back of his hand and got the IV line in place.

They gave him a pill to take 'for his nerves'.

They introduced him to the anaesthesiologist, an intense and hulking bear.

They let him shake hands with the surgeon.

And then they left him alone with Liv.

"You okay, Alex?"

He nodded, sitting on the edge of the bed. Was he? Was he anything? He didn't feel okay, but he didn't feel not-okay. "It feels what you say about flying. How you get past security, and then everything is suddenly someone else's responsibility, and all you have to do is let go and go along with what they say?"

Liv nodded.

"It's like that."

"They told me to tell you you have until they come back for you to change your mind." The older wolf's grin was sly. "I told them if you didn't keep going, I'd kick your ass."

Alex laughed. "Why's that?"

"You've been talking about this surgery non-stop for almost a year. If I had to listen to you talk about it anymore, I think I'd go nuts."

"Right." He cupped spindly hands over his breasts beneath the gown. The garment made him feel tiny, young. "I'd probably go nuts, too. It'll be so nice to be rid of 'em."

Liv's grin softened. "I know."

And then they came to take him away.

They came to whisk him down an anonymous hallway.

They came to wheel him into the OR, a room nothing like what he was expecting.

They came to ask him what music he liked.

They came to give him an oxygen mask to hold over his face.

And then he was truly in their hands.
