\documentclass[10pt]{memoir}

%%% Resets
% memoir defines footruleskip, we want fancyhdr's
\let\footruleskip\undefined
\DisemulatePackage{setspace}

%%% Packages
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{parcolumns}
\usepackage{setspace}
\usepackage{verse}

%%% Font
\usepackage{fontspec}
\setmainfont{Gentium Book Basic}
\newfontfamily\pfdfamily{Playfair Display}
\newfontface\pfdfont{Playfair Display}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\usepackage[none]{hyphenat}
\renewcommand{\chapterheadstart}{}
\renewcommand{\printchaptername}{}
\renewcommand{\chapternamenum}{\pfdfamily\Huge{\itshape\thechapter}}
\renewcommand{\printchapternum}{}
\renewcommand{\printchaptertitle}[1]{\pfdfamily\huge\itshape #1}
\setlength{\leftmargini}{0em}
\setlength{\vleftmargin}{0em}

%%% Headers/Footers
\pagestyle{fancyplain}{
  \fancyhf{}
  \fancyheadoffset[r]{.01in}
  \fancyhf[FRO,FLE]{\thepage}
  \fancyhf[HLE]{\pfdfamily{\itshape\thetitle}}
  \fancyhf[HRO]{\pfdfamily{\theauthor}}
}

%%% Spacing
\usepackage[
  % letterpaper,
  paperwidth=5.5in,
  paperheight=8.5in,
  % layoutvoffset=1.25in,
  % layouthoffset=1.5in,
  layoutwidth=5.5in,
  layoutheight=8.5in,
  vmargin=0.5in,
  outer=0.5in,
  inner=0.75in,
  includeheadfoot,
  showcrop,
  twoside
]{geometry}

\sloppy

%%% Commands
\newcommand\secdiv{
  \begin{center}
    \S
  \end{center}
}

%%% Title
\title{Collected verse}
\author{Madison Scott-Clary}
\date{}

\begin{document}
  \frontmatter
  \pagestyle{empty}
  \null
  \vfill

  \hfill\textit{Collected Verse}

  \vfill
  \cleardoublepage
  \null
  \vfill
  \begin{raggedleft}
    {\Huge Collected Verse}

    \vspace{0.4in}

    {\Large Madison Scott-Clary}

    \vfill

    {\pfdfamily\itshape
    Arctic fox's den\\
    adorned with flowers and snow\\
    garden in winter}

  \end{raggedleft}
  \newpage
  \null
  \vfill

  {\small
  \noindent All poems \copyright\ Madison Scott-Clary the year of their publications. Licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.

  \vspace{0.25in}

  \noindent Current publication \today.
  }

  \vfill
  \newpage
  \tableofcontents*
  \thispagestyle{empty}

  \mainmatter

  \onehalfspacing

  \pagestyle{fancyplain}

  \chapter{Poems from \textit{Missives}}

  I wrote a silly short story a while back. It was meant to be a joke; a pseudo-victorian epistolary romance. It didn't really go anywhere, even though I submitted it to at least one publication. That's fine, though. I got a kick out of it, and the person who inspired it did too.

  The end result was silly, but did include some poetry snippets. I didn't really think anything of them for a while, but one of them, the last here, kept coming back to me. on a whim, I completed all of the snippets into poems in their own right. They're presented in the order in which they appeared in \textit{Missives} itself.
  \thispagestyle{empty}
  \newpage

  %%%

  \section{Though the flow'r may bloom ere long}

  \hfill\textit{February, 2017}

  \input{content/though-the-flowr-may-bloom-ere-long.tex}
  \newpage

  %%%%%

  \section{Delay, then, the morn}

  \hfill\textit{February, 2017}

  \input{content/delay-then-the-morn.tex}
  \newpage

  %%%%%

  \section{Thy gift}

  \hfill\textit{February, 2017}

  \input{content/thy-gift.tex}
  \newpage

  %%%%%

  \section{You find me at a disadvantage}

  \hfill\textit{February, 2017}

  \input{content/you-find-me-at-a-disadvantage.tex}
  \newpage

  %%%%%

  \section{A rose, single, now blooming}

  \hfill\textit{February, 2017}
  \null
  \input{content/a-rose-single-now-blooming.tex}

  %%%%%%%%%%

  \chapter{Unimportant verse about important people}

  Love poems, of a sort.

  \vfill

  \hfill Ones I never sent.
  \thispagestyle{empty}
  \newpage

  %%%

  \input{content/important-people.tex}

  %%%%%%%%%%

  \chapter{Collected haiku}
  \thispagestyle{empty}
  \newpage

  %%%

  \input{content/haiku.tex}

  %%%%%%%%%%

  \chapter{Mental Health}

  Poems on mental health.

  \vfill

  \noindent Maybe I'll write a better intro at some point when I'm feeling better.

  \vfill

  \hfill I dunno.
  \thispagestyle{empty}
  \newpage

  %%%

  \section{There is too much fire in me}

  \hfill\textit{June, 2016}

  \input{content/there-is-too-much-fire-in-me.tex}
  \newpage

  %%%%%

  \section{Cycle}

  \hfill\textit{February, 2017}

  \input{content/cycle.tex}
  \newpage

  %%%%%

  \section{Heligoland}

  \hfill\textit{February, 2017}

  \input{content/heligoland.tex}

  \textit{Thanks to P.R.}
  \newpage

  %%%%%

  \section{Bruise Vision}

  \hfill\textit{June, 2017}

  \input{content/bruise-vision.tex}
  \newpage

  %%%%%

  \section{Beneath her coat was a whole identity}

  \hfill\textit{January, 2018}

  \input{content/beneath-her-coat-was-a-whole-identity.tex}

  \textit{First-place winner of the Typewriter Emergencies Poetry contest.}
  \newpage

  %%%%%

  \section{Asertu}

  \hfill\textit{October, 2018}

  \input{content/asertu.tex}
  \newpage

  %%%%%

  \section{Rush}

  \hfill\textit{June, 2019}

  \input{content/rush}
  \newpage

  %%%%%%%%%%

  \chapter{Gender}

  If you ever see me not take a chance to write about gender, call a doctor.

  \newpage

  \section{Being transgender}

  \hfill\textit{October, 2015}

  \input{content/being-transgender.tex}
  \newpage

  %%%%%

  \section{Somehow, she's me}

  \hfill\textit{April, 2018}

  \input{content/somehow-shes-me.tex}
  \newpage

  %%%%%

  \section{Fair and square}

  \hfill\textit{July, 2018}

  \input{content/fair-and-square.tex}
  \newpage

  %%%%%

  \section{Post-op images}

  \hfill\textit{May, 2018}
  \newpage

  \input{content/post-op-images.tex}
  \newpage

  %%%%%%%%%%

  \chapter{Miscellany}

  Poems without a category.
  \thispagestyle{empty}
  \newpage

  %%%

  \section{The dogs assure me}

  \hfill\textit{March, 2015}

  \input{content/the-dogs-assure-me.tex}

  \textit{Published in \underline{Civilized Beasts, 2016 Edition}.}
  \cleartoverso

  %%%%%

  \section{Growth}

  \hfill\textit{July, 2018}

  \input{content/growth.tex}
  \newpage

  %%%%%

  \section{When I fall, I will remain whole}

  \hfill\textit{November, 2016}

  \input{content/when-i-fall-i-will-remain-whole.tex}
  \cleartoverso

  %%%%%

  \section{Meaning \& Self}

  \hfill\textit{February, 2017}

  \input{content/meaning-and-self.tex}
  \newpage

  \section{Every time I fall}

  \hfill\textit{August, 2017}

  \input{content/every-time-i-fall.tex}
  \newpage

  %%%%%

  \section{Prima materia}

  \hfill\textit{April, 2018}

  \input{content/prima-materia.tex}
  \newpage

  %%%%%

  \section{Numeno}

  \hfill\textit{September, 2018}

  \input{content/numeno.tex}
  \newpage

  %%%%%

  \section{Kiun ŝi povus ŝati?}

  \hfill\textit{March, 2019}

  \input{content/kiun-sxi-povus-sxati.tex}
  \newpage
\end{document}
