\chapter{Gallery Exhibition}
\markboth{Gallery Exhibition}{}

A night on the town. A bar for an aperitif. A light dinner at a modern restaurant, one of those places with default sensoria settings that turn up the taste inputs and turn down the visual inputs, so that you eat intensely delicious food amidst a thick, purple fog. Another bar, livelier and less painfully modern, for a digestif.

Crowds. Crowds upon crowds. Your own crowd a cell within a supercrowd. Instances drifting, or perhaps forced by momentum --- theirs or others' --- along the thoroughfares of a nexus.

\vfill

\begin{center}
  And\ldots{}
\end{center}

\vfill

\newpage

\null
\vfill

A low slung building, a crowded foyer, fumbling for tickets.

\vfill

\begin{center}
  And\ldots{}
\end{center}

\vfill

\newpage

\null
\vfill

Waiting.

\vfill

\begin{center}
  And\ldots{}
\end{center}

\vfill

\newpage

\null
\vfill

Programs.

\vfill

\begin{center}
  And\ldots{}
\end{center}

\vfill

\newpage

\null
\vfill

Explanations. Elucidations. Errata.

\vfill

\begin{center}
  And\ldots{}
\end{center}

\vfill

\newpage

Words to chuckle over with your group of friends.

\begin{quotation}
Dear, Also, The Tree That Was Felled, of the Ode Clade is pleased to welcome you to its gallery opening. Tonight, it has prepared for you a modest exhibition of its works within the realm of instance artistry. This is presented at the culmination of its tenure as Fellow, though the name rankles, of Instance Art in the Simien Fang School of Art and Design.
\end{quotation}

\vfill

And the sound of a door opening.

\vfill

\newpage

\null
\vfill

\begin{flushright}
  Anyway.
\end{flushright}

\vfill

\newpage

A short, slight...thing, steps from the next room through one of the two doors on the far wall and calls for attention. To call it a person seems almost misleading. It's a dog. A well-dressed dog? A glance further on in the program offers a glib explanation:

\begin{quotation}
\textbf{The Artist}

This gallery exhibition serves as the capstone for Dear, Also, The Tree That Was Felled, of the Ode Clade in its role as fellow. The fellowship in instance art was created specifically for Dear in recognition of the excellence it brings to the field.

Dear's instance is modeled after that of a now-extinct animal known as a fennec fox, a member of the vulpine family adapted to desert living. Dear has modified the original form to be more akin to that of humans. The iridescent white fur appears to have been a happy mistake.
\end{quotation}

\vfill

Well.

\vfill

\newpage

\null
\vfill

That's a thing.

\vfill

\newpage

\null
\vfill

\begin{flushright}
  Anyway.
\end{flushright}

\vfill

\newpage

\emph{"If I may have your attention, folks. My signifier, or...ah, name is Dear, Also, The Tree That Was Felled, or just Dear. I come from the Ode Clade of Dispersionistas, and am a Fellow of Instance Art at the Simien Fang School of Art and Design.}

\emph{"An artist is, one might say, one who works with structured experience. A play is art, as is music, as both are means of structuring experience in a certain way.}

\emph{"So, also, is instance art. It is a way of using dissolution and merging in such a fashion that the experience of forking --- or of witnessing forking,"} it gives a polite nod to the room. \emph{"Becomes structured, becomes art."}

\emph{"Before we begin, I would like to take a small census of those present. This is for your own sakes as well as for that of the artworks, such as they are. We'll let them know. Could you please raise your hand if you consider yourself a Tasker?"}

A scant few hands go up in the air, all huddled in one corner of the room. Perhaps a group? A group of their own?

Uncomfortable titters waft through the...the audience? The ticket holders, at least. Talking about dispersion strategies is not something one usually does.

Dear holds its face composed in a calm, polite expression.

\emph{"Trackers? Raise your hands, please."}

Of those who remained minus the Taskers, perhaps a third raise their hands. Several individuals, a few distinct groups including your own. That leaves well more than half belonging to ---

\emph{"And Dispersionistas?"}

Sure enough, large numbers of hands lift into the air. The Dispersionistas are a vast majority, and surround most everyone else in the room, minus the Taskers, who remain off to their own side. The audience seems to be mostly fans of the work.

Dear gives a brief blink, likely saving a tally of represented dissolution strategies to some exocortex for other instances to access. It smiles kindly at the audience, \emph{"Thank you. Now, if you would be so kind as to follow me, I will be happy to walk through the gallery with you."}

Dear turns adroitly on its heel and without a moment's hesitation, forks. A second, identical instance appears to its left and finishes that turn in perfect synchrony.

\newpage

\null
\vfill

A small wave of applause begins. To fork so casually and continue to move in lockstep bespeaks no small amount of practice with the procedure.

\vfill

It doesn't last.

\vfill

\newpage

\null
\vfill

One instance of Dear (the original? maybe?) heads through the left-hand door and the other (the fork? it's so hard to keep track with all these people) steps through the right door.

\vfill

You fork and, with that copy, follow Dear both left\textsuperscript{\pageref{left-door}} and right\textsuperscript{\pageref{right-door}}.

\vfill

\newpage

\label{left-door}

The room you wind up in is smaller even than the foyer, and the ticket-holders have to press even closer together. The audience that winds up here is the least diverse, containing none of the Taskers and very few of the Trackers who wound up at this (apparently primarily Dispersionista) event. As such, the press is met with uncomfortable silence: one doesn't normally talk about dissolution strategies with strangers, but Dear has deftly forced it to be an issue.

There's no sign on the fox's face that it knows what it has done. Just that calm, polite smile. Curious. How can one know that a fox is smiling rather than snarling or something, much less that the smile is polite. Perhaps styled after those old cartoons of anthropomorphic animals, or simply just an impression.

\emph{"Thank you. Much cozier in here."}

Many of the proclaimed Dispersionistas are grinning at the trick, and even several of the Trackers are smiling.

\emph{"My only request is to not fork during the duration of the exhibition,"} Dear continues, giving a knowing glance to some of the Dispersionistas. \emph{``Exigencies aside, of course.''}

A thought crosses your mind. Perhaps it's the drinks, those hip and strong aperitifs and too-sweet digestifs.

\newpage

\null
\vfill

Well, hell. It's hard to take a fox standing on two legs seriously when it gives you instructions.

\vfill

\newpage

\null
\vfill

This all seems rather ridiculous, when you take a look at it. Instances as art?

\vfill

\newpage

\null
\vfill

You're not as smooth as Dear, but you manage to step a little further away from one of your friends, leaving enough room for you to bring into existence your own second instance.

\vfill

\newpage

For a moment, you aren't sure quite what happens. After a second, things start to click into place, though.

A mere fraction of a second after you forked, Dear also forked, instructing its instance to come into existence in a space overlapping the space that your instance already occupied. This sort of thing is very much frowned upon and, in most public areas, impossible to even pull off.

As it is, collision detection algorithms whine in protest and force the two instances apart with some force, causing a cascading ripple of collisions, spreading complaints of personal space. The room has safe settings, at least, and the collision detection algos register a bump at least a centimeter before one body touches another.

The Dear at the front of the room is smiling beatifically, but the one confronting your instance has undergone strange transformations. Its eyes are bloodshot, almost to the point of glowing red. It's mouth is gaping, lips pulled back in a snarl, muzzle flecked with froth. \emph{Rabid}, you think. It has lost most of its humanity, though it remains on two legs.

You let out a shout, but it's drowned amid a chorus of other yells and screams.

Post-humanity, confronted with humanity regressed feels a special kind of fear, and as the feral Dear herds your instance toward the back of the room, back toward the foyer, the other ticket-holders (though perhaps `audience members' is the correct term, now, you think, as you struggle to send a SIGTERM to your instance amid the distraction) surge forward toward the original instance of Dear.

It's still smiling.

It opens the next door.

\newpage



\newpage

\label{right-door}

The room you wind up in is smaller even than the foyer, and the ticket-holders have to press even closer together. The audience that winds up here is the most diverse, containing the entire group of Taskers who wound up at this (apparently primarily Dispersionista) event. As such, the press is met with uncomfortable silence: one doesn't normally talk about dissolution strategies with strangers, but Dear has deftly forced it to be an issue.

There's no sign on the fox's face that it knows what it has done. Just that calm, polite smile. Curious. How can one know that a fox is smiling rather than snarling or something, much less that the smile is polite. Perhaps styled after those old cartoons of anthropomorphic animals, or simply just an impression.

\emph{"Thank you. Much cozier in here."}

Right. The Taskers do not look cozy

You suppose it makes sense. There are bits of this that appeal to all: forking for a specific purpose, instances accomplishing goals. This was flagrant abuse of that in their eyes, however, given that these instances will likely move on and live their own lives. Independent, individual instances.

\emph{"I would like to elaborate on my previous point,"} Dear says. \emph{"This opening is about the idea of instance creation as art, and in that sense, it's the easiest job I've ever had. Instance creation is art."}

It holds up one paw as though to forestall further conversation. \emph{"All instance creation. This show is about utilizing that consciously, but all instance creation is art. It is structured experience. The Taskers, and I believe you're all here?"} Dear smiles kindly. \emph{"The Taskers are the tightest adherents to structure. The most baroque."}

Still holding its paw up, Dear, Also, The Tree That Was Felled forks once more, an identical copy of itself appearing standing just next to the original. The instance quickly quits and dissipates. An example, perhaps.

\emph{"The goal of this exhibition isn't to just talk about that, though, it's to explore the creative limits of forking as art."}

Dear forks once more, but this time into two additional instances. One short, lithe human, holding up its hand just as the original instance still holds up its paw. And on the other side of Dear, a small animal --- smaller than you expected, the size of a small cat --- that you suppose is the fennec mentioned in the program, colored in creamy tan fur. It becomes clear that the primary Dear is a synthesis between the two.

The human Dear reaches out to shake one of the audience members hands while the fox dashes toward the crowd, weaving its way between legs in a good simulacrum of an animal attempting to escape.

\newpage

\null
\vfill

Something about the fennec catches your eye as it dashes quickly through the crowd. It doesn't seem to be following any pattern, but its motions remain purposeful. It seems to be...perhaps, making eye contact with each person in the room?

\vfill

\newpage

\null
\vfill

And then it comes to you.

\vfill

\newpage

\null
\vfill

And it looks up to you.

\vfill

\newpage

And winks.

Can fennecs do that?

The strange critter holds your gaze for longer than some wild animal should, or so it feels, but the moment is broken by the soft sound of Dear clearing its throat at the front of the room.

\emph{"The next room is just through here. If you'll follow me\textsuperscript{\pageref{follow-dear}}, please."}

It's difficult to deny the tiny critter before you, to tear your eyes away from it. Easy enough to forget that its an instance of Dear as it leads the tour onwards. Perhaps if you could just dally a little and get a closer look\textsuperscript{\pageref{follow-fennec}} before moving on.

And then the explosion happens.

\newpage

\label{follow-dear}

\newpage

\label{follow-fennec}

A shuddering bang and sudden flood of smoke behind and to your right makes up your mind for you.

Turning, you find that the fennec has skittered away to the left. As the shouts of those nearest the banging noise and cloud of smoke rise up, you find yourself doing the same, following out of a sense of instinct rather than anything resembling logic.

Cliché as it is, the lights go out. Perfect.

\newpage

You keep heading left, where the fennec was going, pushing past scrambling attendees to get to the wall. The left wall, you reason, is a shared wall with the other room, the one which the other Dear had led the other half of the group through. There's probably a door between the two, though you hadn't had the chance to get a look, or perhaps you could break through.

The smoke thickens. It has a lemony, sulfurous smell that, although it's never something you've smelled before, makes you think of bullets, grenades, gunpowder.

In the dim light and confusion, you find the wall by abruptly slamming into it. Indeed, there's a door a few hand-spans away, and a tiny critter with big ears scratching frantically at it.

You shuffle quickly over to the door, barely able to see for the smoke and dimness, and grab at the handle, praying that it's unlocked.

\newpage

\null
\vfill

The handle turns.

\vfill

\newpage

\null
\vfill

You fall through.

\vfill

\newpage

It's a strange sensation to step from a cramped, crowded, loud, dark, and smoky room into such a space as this.

The fall you took couldn't have been more than a few feet, but even now, your senses still feel knocked slightly out of place. To have a space like this, one that's bigger on the inside than on the outside, or outside when it should be indoors, underground, is certainly possible. It's easy. It's just also considered incredibly rude. In most sims, it's even illegal. In this one, you vaguely remember hearing that it requires a permit.

But here you are.

\phantom{But here you are. }You and a tiny fennec.

\phantom{But here you are. }You and a lapis sky.

\phantom{But here you are. }You and endless green fields.

\phantom{But here you are. }You and a sunny day.

Outside \emph{and} a sunny day.

The fennec, which had been grooming itself after the flight from the explosion, gives you what can only be a smirk and another wink, and (link-reveal:"starts heading off away from where the door ought to have been but is no longer.

Nothing for it.

\newpage

You follow along after the tan beast, the fox looking minuscule amid the endless grass, nothing but its ears sticking up above the stalks. It looks out of place amid the green of the grass.

The ground had looked flat at first, but that seems to have just been the grass all growing to about the same height. Beneath the grass, you keep rolling your ankle over tussocks and failures in the earth, stumbling over the fact that the grownd the grass is growing on is annoyingly uneven.

The fennec winds its way amid these tufts, having an easier time of things with dainty paws.

Your mind fills with stories, of magical animals, of sleeping for years and waking up to see the world vastly change. You start to think of the fennec as its own entity, something completely separate from Dear, from the exhibition you just left.

\emph{"You're one tenacious fuck, you know that?"}

You look around, some part of you unwilling to believe that the voice came from the fennec.You had forgotten, lost in your fantasies, that the fennec was still Dear.

\emph{"Yeah, me."} The fennec continued its dainty walk. \emph{"I say 'tenacious fuck' lovingly, of course. I like you. You've got pluck. Gumption. Another you forked in another place, another time. We fought. We kind of fell for each other. It was fun."}

"Another...?"

\emph{"Not much in the way of brains, though."}

You roll your eyes. The fennec grins.

\emph{"You know you were told to send an instance to the exhibition, right?"} the fennec asks, casually.

"Yeah," you respond, wary of traps.

\emph{"So why not quit?"}

"Hmm?"

\emph{"Why not quit? Why not merge back with your\ldots{}"} The fennec pauses and gives you and appraising glance, \emph{"With your \#tracker?"}

You shrug helplessly, realizing the two of you have come to a halt at the base of a hillock, a rough cave dug into its side. The fennec sits primly. "This is\ldots{}this is an exhibition about instances as art, isn't it?"

The fennec gives a short bark of laughter, looking perhaps most feral at that moment. \emph{"It is, isn't it? Just thought you'd see it through, hmm? This exhibit?"}

You nod. You feel ill-prepared for this.

\emph{"I won't lie to you, then. This exhibit,"} and the fennec nods toward the horizon, toward the cave, toward you. \emph{"This exhibit is just a frame. It's just a canvas. You're the exhibit. You're the art."}

You catch yourself nodding once again and attempt a more graceful response. "There's a lot of shows where the audience becomes the cast."

\emph{"I suppose."} The fennec settles down onto its belly, stretching out. \emph{``That's one way to think of it, yes. I'm not fond of the play metaphor. Exhibit works better for me and the way I think, since I know who's watching.''}

Just as you begin to respond, the fennec quits. This sim, as a whole, provides a courtesy feature of a faint outline existing and then fading after a quit, crash, or failure. That just means you get to fume in the direction of a slowly fading outline of a fennec, standing at the mouth of the cave.

The fennec's right, though, you could just quit.

But \emph{you're} right, too, you think. You want to see how instances become art.

"Cave it is, then," you say, as though this is some sort of choose-your-own-adventure book or roleplaying game and you have to follow the available exits.

Ah well.

\newpage

As far as caves go, this one is rather unremarkable.

You laugh at yourself for having such a thought. The life you've chosen for yourself does not include many caves.

You drop to your knees, brushing a hand through the last vestiges of the faint outline of that shitty fox, and crawl past the entrance of the cave.

It is unremarkable in that it is almost cartoonish in construction. A low hillock with a rough hole bored in the side, rocks protruding here and there, worms and roots dangling from the ceiling. Always large enough to crawl through on all fours, but never enough to stand up in.

\emph{The construction is actually quite well thought out,} you muse. \emph{At least, as far as cramped spaces go.}

As soon as the cave turns a corner and the light of day behind you is lost to view, it all seems rather less inviting than it did before. The air was still before, but now it's stale; cool and moist has become humid and sticky.

It's difficult to say whether the walls are closing in or whether that's just claustrophobia setting an assertive hand on your shoulder.

You crawl on.

The ground starts to rise, and at last you think you may be nearing the other side of the hillock. Perhaps, given the non-Euclidean layout of the exhibit, an entry back in, or at least back out.

\newpage

\null
\vfill

The tunnel keeps rising.

\newpage

\null
\vfill

The tunnel keeps going.

\vfill

\newpage

\null
\vspace{2in}

Rocks dig into knees and palms

\newpage

\null
\vspace{1in}

And you keep climbing.

\newpage

Up and through.

\newpage

You climb.

\vfill

Nearly vertical.

\vfill

And, to your relief, it grows lighter.

\vfill

You hasten.

\vfill

Up and out.
