\hypertarget{tycho-braheemissary-2346}{%
\chapter{Tycho Brahe\#Emissary — 2346}\label{tycho-braheemissary-2346}}

``\emph{Nahi,} scientist Tycho Brahe.''

He sat up straighter and grinned, waving to the thirdracer. ``Uh, \emph{nahi}. Just Tycho is fine.''

Stolon tilted their head to the side, the frill of elongated scales stretching from the back of their neck spreading wider. He'd decided that this was an expression of happiness.

``\emph{Ka, ka,} can call Stolon also. I am, \emph{lu}\ldots sorry that your friend exits. I do not know how, Iska looks into this.''

He shifted to the side, making enough room on the low sill of the window that looked out over the curated garden beyond. Both times he'd managed to snag time with Stolon before, they'd met here, an incongruous alcove down the hallway from their rest area. He knew that he was technically supposed to be in the courtyard with Codrin and Sarah to wait for whatever it was that was supposed to happen next, but everything had just been so overwhelming\ldots{}

Stolon perched on the edge of the windowsill, tilting their head toward the bright sunlight that seemed to be perpetually streaming through to bask. The North American in him had taken to thinking of the spot as having southern exposure.

They sat in silence for a while, each enjoying the sun in their own way.

``Sci--\emph{lu,} Tycho, are talks going well for you?''

He picked at a corner of the stone sill, shrugging. ``I suppose so. I'm feeling really in over my head.''

``In over\ldots?''

``\emph{Nu\ldots nukupot\ldots kopotla\ldots{}}'' he stammered, hunting through the language he'd been trying to mainline over the last three days.

``\emph{Iha! Ka, ka, nukupotla,} not-knowing?''

``Something like that. I don't know what's going on, and don't have much to contribute. Not much knowledge to give, I mean, when we're talking about social stuff.''

``Rrr, \emph{ka,} I also.''

The thirdracer made what looked to be a frustrated gesture with one of their hands and then shifted to drape languidly over the edge of the windowsill, hands hanging nearly down to the ground and feet kicking lazily behind them in the alcove. It was a nearly childlike move that he found incredibly endearing. Something more\ldots well, not human, but perhaps personable in this otherwise impersonal conference.

``I went into academia because-- sorry, into studying as one of the only things I do in my life because that seemed to be the only way I could just do what it was that I wanted,'' he mused. ``No commitments, no distractions. Just the stars and math.''

Stolon stretched out long enough to grab a curly-edged leaf from one of the short bushes, picking at it between dull claws. ``I also, \emph{ka.} I am not\ldots combination? Child? I am from before embedding. Before before, I also study. I study stars and inside planets. I also in over my head. I am knowing how convergence works, so I am here, but still I dream of stars.''

``Is the convergence something you had to study for?''

``\emph{Ka.} I learn your language, not so well, maybe.'' They chattered their teeth in something like amusement. ``Also I learn path of convergence. Items on checklist, leader Turun Ka says. We have list of steps for convergence, and each of us\ldots{}\emph{jaruvi}\ldots see? Notice\ldots each of us notice what you say and what you do, and we complete checklist. I study this before.''

Tycho frowned. ``Checklist? Like there are things that need to be completed? Is there a goal?''

``\emph{Nu,} no goal, just to be happy and safe. No completed, just notice these things, and decide what to do next.''

``Oh, so more looking for patterns.''

``\emph{Anem.} We find patterns and say `yes yes' or `no no' and do next thing. You hear,''this is not time to have that conversation.'' We say because we use checklist.''

``Sounds like politics.''

``Rrr, politics, \emph{anem.} Want stars. Want to share knowledge. Want to make knowing full. Politics is not this.''

``Right, yeah. That's more True Name's field. I don't understand it at all.'' He shrugged. ``But who knows what will come next.''

``Turun Ka knows maybe. I think is okay, though. We think you are smart. We like you. We and you both want happy and safe. I am sorry about representative\ldots rrr\ldots{}''

``Answers Will Not Help.''

``\emph{Ka.} I am sorry. I am not worrying, though.'' They poked a torn bit of the leaf into their mouth and chewed thoughtfully before spitting it out with a choking sound. ``\emph{Natarla\ldots{}}''

Laughing, Tycho said, ``Not so tasty?''

``\emph{Nu, nu,}'' Stolon said, chattering their teeth again.

``Why aren't you worried?''

The thirdracer shrugged, tail flipping about in a wide arc as they rolled over onto their back, flexible enough to drape over the windowsill and sun their belly that way. ``Convergence is convergence. Is to be happy and safe, \emph{ka?} Is for leaders and representatives. Scientist, am not worrying. Stars are not lying. Artemis is not lying. Physics is not lying. If you do not join Artemis, will, \emph{lu}\ldots think about? Will think about you, but good to be happy and safe, and science is not lying.''

Throughout Stolon's short speech, Tycho sat up straighter, his grin growing wider. ``Yeah, I like that. Science is not lying. It can't, really, can it? Politics can lie, and maybe that's why I hate it so much.''

``\emph{Ka, ka.}''

``And I'd think about you too, if things go that direction. I honestly didn't really think about that being on the table until after the conference started and we began actually interacting with each other, and now I have to admit that I'm really hoping it \emph{does} work out. I like it here.''

``Is home, \emph{anem.} I am liking it, but I am also only living here.''

Tycho nodded, ``I'm only on Castor and Pollux, yeah.''

``Is Pollux same?''

``Yeah, they started out identical, but they've diverged over time.'' He frowned, shrugged. ``I bet Tycho\#Pollux is feeling awful now, missing all of this.''

``No Tycho on Legrange construct?''

``Nope, I invested fully. Did you leave an instance of yourself back on your original system?''

``\emph{Lu}\ldots yes, but they exited after convergence and distance grew. Friends say that Stolon got sad, spent all of time thinking about Artemis.'' They lifted their snout to peer up at him. ``Tycho will join if possible, \emph{anem?}''

He laughed. ``\emph{Anem!} Of course I will.''
