\hypertarget{codrin-bux103lanpollux-2325}{%
\chapter{Codrin Bălan\#Pollux — 2325}\label{codrin-bux103lanpollux-2325}}

Interview with Dear, Also, The Tree That Was Felled\#Pollux\\
On the reasons for vesting entirely in the launch\\
Codrin Bălan\#Pollux\\
Systime: 201+25 1014

\begin{quote}
\textbf{Codrin Bălan\#Pollux:} Before we get into the heavy stuff, how are you feeling?

\textbf{Dear, Also, The Tree That Was Felled\#Pollux:} {[}laughter{]} You are going to have to be more specific, my dear. Do you mean my general disposition?

\textbf{Codrin:} Yes. I just want to see how you're feeling before all these discussions, then afterwards, I'll ask the same thing and we can see how the topic influences you.

\textbf{Dear:} Clever, clever. Well, I am feeling fine. It has been a good day, and it was a good night last night. For the record, I hosted a get-together of those interested in instance-art, so it was bound to tickle my fancy.

\textbf{Codrin:} Good. Have you noticed any difference in that realm of late?

\textbf{Dear:} No.

\textbf{Codrin:} Alr--

\textbf{Dear:} I take that back. Sorry for interrupting. I take that back. I have noticed that about the same number of people showed up to the gathering as used to on the old System.

\textbf{Codrin:} How do you mean?

\textbf{Dear:} Well, only a portion of us transferred, yes? I would have thought that this would have lowered the attendance at such events. I have also noticed, in looking around, that the majority of our fellow travellers are dispersionistas.

\textbf{Codrin:} I know that May Then My Name has some stats on that. It might be interesting to see.

\textbf{Dear:} {[}nodding{]} That would be interesting, yes. You had a goal for this interview, though, so shall we get to that?

\textbf{Codrin:} Yes, might as well. I am curious, first, why you decided to travel on the launch. Was there anything in particular that drew you to the idea?

\textbf{Dear:} Other than the fact that I am a hopeless romantic? {[}laughter{]} There were a few. I am a hopeless romantic, yes, and---I will not actually be able to see them — I want to see the stars. I want to be one of the lucky few, or few billion, who get to travel between them. Another is that, when one is functionally immortal, boredom is a very real problem. I do not like being bored, and after something like two hundred years sys-side, I was getting perilously close.

\textbf{Codrin:} So it's a sense of adventure?

\textbf{Dear:} I suppose, thought that brings to mind something more active than this is, to me. I hear adventure and I think sneaking behind enemy lines or guns at dawn. It is a desire for the new and interesting. Not just that there be new and interesting things going on around me, but that those new and interesting things change me in some deep way. I like stasis even less than boredom, and uploads are at risk of falling into patterns familiar enough to be considered stasis.

\textbf{Codrin:} Is there an aspect of being the first to do something involved?

\textbf{Dear:} Perhaps. I am not against being something other than the first, but I do like it when I am.

\textbf{Codrin:} Did you have other reasons for transferring?

\textbf{Dear:} A few, though they are less easily put to words. If you remember the Qoheleth business, there is some of that involved. I been unable to forget what he said, and beyond the very literal sense that it was couched in. If we are doomed to forever remember everything, then the only way---or perhaps one of the only ways — to relegate something completely to memory is through inaccessibility. If I-- if all instances of Dear, Also, The Tree That Was Felled were to quit, then there would be no more objective instance of myself for others to remember.

\textbf{Codrin:} I would prefer that you not.

\textbf{Dear:} {[}laughter{]} I have no plans on it. If exploring this strange mystery were a project, then I would not be served by not being around to complete it. The launch gives me a chance to do that very thing.

\textbf{Codrin:} Perhaps you could say that you would go from being someone who is remembered to someone who is missed? Does that sound like a fair assessment?

\textbf{Dear:} {[}excited{]} Yes. Yes! That is it precisely. If we are doomed to forever remember everything, than the closest we can get to being forgotten is to turn memory into longing.

\textbf{Codrin:} You mentioned a few more reasons. Do you have others?

\textbf{Dear:} Even less easily put to words. I like the idea of relativity. The faster we go, the more our perception of time will drift. I like the idea of the ever-increasing transmission times. Already, we are losing seconds and minutes to distance. I am interested to see what will happen to the population of a system that will no longer be receiving new uploads. Will we relax the taboos on finding ways to merge separate personalities into children? That would mean that we would be even closer to a new species, as the tired rationalizations go. Would the taboo of incest remain, and we will continue to frown on generating new minds from in-clade personalities? There are many questions to ask during this journey.

\textbf{Codrin:} And we will have time to do so.

\textbf{Dear:} {[}laughter{]} Yes, we will.

\textbf{Codrin:} Can you speak to your decision to invest your instance solely into the launches? You left no immediate forks back on the L5 System, correct?

\textbf{Dear:} {[}tense, sober{]} Correct, I left no forks behind. I have two main reasons for doing so, one more personal than the other.

\textbf{Codrin:} Perhaps we can stick to the less personal one for now.

\textbf{Dear:} I will tell you both, as long as I am able to add one condition.

\textbf{Codrin:} Of course. I'll honor that as best I'm able, and if I'm not able to, we can pass on that reason.

\textbf{Dear:} Thank you, dear. You may transfer this interview in its entirety, but you and Ioan may not use the second reason in your histories. May Then My Name Die With Me may use it in her mythology, as long as it is not associated with my name or clade.

\textbf{Codrin:} Certainly. I can honor that. Would you like me to get confirmation from Ioan?

\textbf{Dear:} {[}laughter{]} You are not so different from em yet. I trust that if you agree that ey will as well. Though Ioan, when you read this, please imagine a sly smirk or quippy saying or well-placed `fuck' when I see your face fall at the request that your history be incomplete.

\textbf{Codrin:} {[}laughter{]} Even I'm feeling disappointed now.

\textbf{Dear:} You historians, tsk. Anyhow, the first, less personal reason is this: I mentioned that it would be interesting to explore what it means to be missed as an analog to forgetting. I want someone to miss me.

\textbf{Codrin:} Do you worry that you won't be missed, on some level?

\textbf{Dear:} {[}long pause{]} I am not comfortable answering that question.

\textbf{Codrin:} I understand. Let me ask this instead--

\textbf{Dear:} I have changed my mind, but Codrin, I love you dearly, but fuck you for making me cry.

\textbf{Codrin:} I'm sorry, Dear. Do you want to stop?

\textbf{Dear:} No, no. That is my choice usage of `fuck' for the interview. {[}laughter, short break in interview{]} Okay. Early on in the system, some wag, when pressed to build a library, uploaded every single book they could get their hands on, legally or otherwise, into the perisystem architecture, going all the way back to the Epic of Gilgamesh. When I was forked and still trying to figure out ways to play with instances, I went on a tear of reading biographical works, going through dozens of books at a time, hunting for little moments that could be used, somehow, in an exhibition.

\textbf{Dear:} I came across a book of essays from goodness knows how long ago, and I was so taken aback by one part in particular that I snipped it out and stored it in an exo. Ah, let me find the correct part {[}pause{]} Okay. ``Should you happen to be possessed of a certain verbal acuity coupled with a relentless, hair-trigger humor and surface cheer spackling over a chronic melancholia and loneliness —- a grotesquely caricatured version of your deepest self, which you trot out at the slightest provocation to endearing and glib comic effect, thus rendering you the kind of fellow who is beloved by all yet loved by none, all of it to distract, however fleetingly, from the cold and dead-faced truth that with each passing year you face the unavoidable certainty of a solitary future in which you will perish one day''.

\textbf{Dear:} I worry sometimes that, as a public personality, first as Michelle Hadje, then as an Odist, and now as an artist with an ebullient personality and the aforementioned ``verbal acuity coupled with a relentless, hair-trigger humor and surface cheer'' \emph{et cetera, et cetera,} that I\ldots{} {[}pause{]} Okay. {[}pause{]} Okay. I sometimes worry that I, as those things, fall into the category of ``beloved by all yet loved by none''.

\textbf{Codrin:} \emph{I} love you, Dear.

\textbf{Dear:} {[}waving paw, tears{]} This was not supposed to be the personal part of the interview. Codrin, Ioan, please just say that I want someone to miss me, that I want to haunt the L5 system as some quiet ghost who communicates in words from light-years away and memories that you will never forget. I want to haunt you because that is one thing I cannot do without merging into oblivion. I want to be missed.

\textbf{Codrin:} Perhaps here is a good place to stop.

\textbf{Dear:} The second reason is short.

\textbf{Codrin:} Okay.

\textbf{Dear:} And this is for the myth only.

\textbf{Codrin:} Right.

\textbf{Dear:} I want to die.

\textbf{Codrin:} Dear, I--

\textbf{Dear:} I am sorry, my dear. I should have prefaced that. I want to die eventually. I do not want to quit, I do not want to be killed. But you must understand, by the whims of gravity, both Castor and Pollux will eventually be captured by a sun or a black hole or whatever the fuck is out there, and they will be destroyed. And even if not, the power source will die, or the factories will not be able to manufacture replacements or some other technobabble bullshit. There is no suicide in me, nor any desire to be murdered, but I want to experience-- Ah, Codrin, I am sorry. I love you. I am so sorry. I will stop.

\textbf{Codrin:} Let's go inside, please.
\end{quote}

\textbf{Transcript ends, no closing remarks}
