The first message was not long in coming, arriving about an hour after Ioan\#c1494bf arrived home. At least it wasn't high priority; ey had the choice to accept then or experience later. Half duplex, though. Would be an actual conversation.

Ey sighed, closed eir eyes, accepted. The things ey did for work.

\emph{``Hi Ioan,''} came Dear's voice. It was still seated on the couch. \emph{``Long time no see, hmm?''}

Ioan nodded, subvocalized, ``Yeah, took you ages. Have something for me?''

\emph{``Maybe. We've got a file from someone down-tree. Or, well, hmm.''} It appeared to think for a moment before continuing, \emph{``Someone down-tree from me found a file, and she thinks it might be a file from the clade, maybe one of the original ten.''}

Ioan waited until the fox was done before responding, ``Alright, send it over.''

The file arrived promptly. Eir shoulders sagged. It began with \texttt{-\/-\/-\/-\/-BEGIN\ AES\ BLOCK-\/-\/-\/-\/-} followed by thousands of apparently random letters, numbers, and punctuation.

``What's an AES block?''

\emph{``An old encryption algorithm. And I mean \textbf{old}.''} Dear looked a little embarrassed. \emph{``We like old things. That's why we figure it's probably from one of us.''}

Ioan thought for a moment before responding, ``So do you want me--''

\emph{``You do not need to worry about the file itself. That is why I did not just forward it to you automatically.''} Dear paused, then added, \emph{``Though I probably should have. Amanuenses form an} Umwelt, \emph{so this is part of yours, now. We will talk about it at the end. Something to keep in mind, I guess. When we find the key, we will let you know and send over the contents.''}

``Good. I gave AES a check, and you're right, that's ridiculously old. Can't you just crack it?''

\emph{``We could. Some of us probably already have. I want the key, though. It's probably a word or something, and may prove interesting in its own right.''}

``Interesting?'' Ioan asked.

\emph{``Interesting in that the act of finding the key may turn up further clues.''}

``Ah. Good point. I'll do some digging on old cryptography, too, and see what all's out there. Keep in touch, yeah?''

\emph{``Good fucking luck. Cryptonerds were --- are --- very wordy. There's going to be a boatload to sort through.''}

Ey grinned, ``I'll fork and research, then.''

\emph{``Good plan. Gonna get back to the hunt, and hey, Ioan?''} The fox gave an earnest smile. \emph{``Thanks. Even if I'm just running ideas past you, it's good to put in words.''}

``Of course, Dear.'' Ioan waved. Ey always felt silly interacting with sensorium messages. Would \#tracker think em crazy? ``Thanks for the project.''

Dear bowed, signed off.

\#tracker was, indeed, giving \#c1494bf a bemused grin.
