%%%%%
\chapter{Again}

Michael woke blearily to the sounds of muffled giggling, rubbing the sleep from his eyes and lifting his head off the pillow.  He couldn't quite make out what was going on in the bed next to his own, but it appeared to be quite fun, or at least funny.

Rooming with his friends came with its benefits, but also its drawbacks. No one had been particularly shy about the fact that part of the reason they had come to the convention in the first place was to play around and get laid, and that was just sort of part of the bargain when it came to rooming with others.  He smiled slightly that it was those two who had started messing around before he and his own bed-mate had; he knew Bomber had quite the crush on him.

On that note, he rolled over in bed, putting the giggling behind him, and slipped his arm around the still sleeping Bomber.  He fit snuggly behind the slightly smaller form, doing his best not to rouse his friend, content for the moment just to enjoy the shared warmth of laying close to someone.  Bomber, for his part, simply mumbled something incomprehensible and appeared to go right back to sleep, comfortable against Michael's front.

He apparently dozed off, because the next time he woke up, the giggles had been replaced with muffled panting and the quiet, rhythmic rustle of\ldots{}it couldn't be much more than a blow job, given that only the blankets seemed to be rustling, rather than the entire bed.

``Morn','' mumbled Bomber.

``Shh, quiet,'' Michael whispered, confirming his hunch with a look over his shoulder.  ``Very important things happening over there.''

There came a laugh from the other bed, along with a muffled giggle. ``Very important, verrrry warm,'' Alexis replied, voice slurring with the effort of enunciation while receiving oral sex.

Michael rolled slowly onto his back and canted his head to watch the goings on, while Bomber sleepily rolled over next to him and rested his head on Mike's shoulder.

They couldn't see Corrin, and with as skillful as he seemed to be, could barely hear the fox moving rhythmically beneath the covers, except for the rustle of blankets on hair.

Skillful indeed.  Before too much longer had passed, Alexis' eyes shot open and his jaw dropped, breath catching in his throat only to be let out in a hasty, ``Oh fuck.''  Alexis shuddered, Corrin drastically slowed his movements, and Michael and Bomber looked on in appreciation.

``Mmm, well done, you two,'' Michael offered, getting a breathy giggle from Alexis and a grin from Bomber, whose own hand was inching its way down over his front, seemingly casually but obviously aiming for the crotch.

Both Michael and Bomber had slept only in their underwear, and watching the little show did have Michael somewhat worked up, so he tolerated the touches -- tentative at first, then a little more exploratory over the tented boxer-briefs that he wore -- though it felt a little awkward with Bomber.  He knew how much he meant to his friend, but considering him only a friend, felt he had little he could offer that would satisfy him. He tended towards women, usually, but wasn't above the friendly touch.

Corrin slunk from under the covers with a sheepish grin on his face, muttering, ``Hi, guys.''  He kissed Alexis on the cheek, took the other's hand in his own, and guided him out of bed.  ``C'mon, let's grab the shower first.''

Alexis nodded and managed to slip out of bed behind his friend, tugging his discarded boxers along after him and using them to cover his crotch, walking quickly behind Corrin, who was doing his best to hide his own erection.

``Have fun,'' Bomber offered.

``Yeah, and save some hot water for the rest of us.''

Michael and Bomber settled comfortably back into bed, Bomber nestled in against Mike's side as he continued to pet gently along his friend's flagging arousal, his own pressed firmly to Michael's hip.  After a silence, he asked, ``This okay, Roo?''

Michael nodded, eyes closed.

Another long silence, then, ``Can\ldots{}can I do any more?''

Michael hesitated a bit.  There was no denying that the touches felt good, but that lingering sense of awkwardness remained.  ``Um\ldots{}no.  Not this time, maybe soon?'' he offered.

Bomber nodded, abashed, and settled himself back against Michael's side.  The touches slowed, but continued, more carefully than before, lest they cross a boundary.  Eventually, they settled to a stop, and Bomber simply slipped his arm around Michael to hug himself closer, murmuring, ``This is good, too.''

Michael nodded in agreement to that, brushing his hand up along Bomber's back to hug around his shoulders, helping to keep his friend warm against him while they waited on their own turns at the shower.  It would be a bit, yet.

\secdiv

Saturday morning -- nearing afternoon by the time Michael, Bomber, Alexis, and Corrin drew the curtains and made it out of the room -- was a pleasant affair.  The four made their way to a nearby coffee shop, managing to pick up two more along the way: a lion and his intensely shy friend who looked to be some sort of blue fox or wolf, if the tail was anything to go by.

They shared coffee and gossip, laughter at the expense of Alexis and Corrin, and the Shy Blue Fox produced a clipboard with paper from his messenger bag and polled everyone for their species and began sketching.

Michael, from his position next to the Shy Blue Fox, watched the sketch take shape.  He wasn't much of an artist, himself, but always found it fascinating to watch artists work, turning what looked like the simplest of shapes into something that carried meaning.

``Is that you, Roo?'' he heard a husky voice from behind him, feeling crossed arms settle onto the back of his chair.

Michael turned quickly.  Something about the voice tickled his memory in strange, not altogether unpleasant ways.  A short man with a well-kept goatee stood back upright behind his chair, crossing his arms over his chest and smiling down to Michael.

``So it is.''

``Do I know\ldots{}'' Michael began, half rising out of his chair.

It was the height that tipped him off, more than anything.  The skin was rougher, the hair cut from waist-length to a sort of unisex pixie cut, the facial hair, the masculine, well-built chest.  There was something about how this person was exactly the same height as\ldots{}

``Glade!  Holy shit, is that you, Glade?''

The other man nodded, then bust into a wide grin, uncrossing his arms and holding them open in an invitation to a hug.  Michael stood fully from his chair and moved cautiously into to the hug, wrapping his arms firmly around Glade for a good long moment before stepping back once again to look over him.  The hug felt familiar, and yet incredibly different at the same time.

``You look\ldots{}ah\ldots{}very different,'' was all he could manage.

Glade laughed easily, tossing his head to clear the hair from in front of his eyes.  ``That's an understatement.  What do you think?'' he asked, standing a little taller.

Michael couldn't quite keep his mouth from hanging open, much less form any words.  ``I\ldots{}you\ldots{}well you look good!  You'd always talked about\ldots{}but I didn't think\ldots{}''

Glade kept grinning, reaching forward to pat Michael gently on the cheek, ``Don't worry, don't need to think too hard.  I'm doing things that make me happy.  I won't pester you too much, I just wanted to say hi.  It's been, what, five years?''

Michael struggled to define what he was feeling, the violent mix of old emotions combined with the surprise of seeing Glade after so long.  All he could do is nod.

The two stood in silence for a moment longer before Glade reached to give Michael's bicep a squeeze, ``Well, it's good seeing you.  I'll let you get back to it, maybe see you around?''

Michael nodded and croaked, ``See\ldots{}see you.''

When Glade sauntered off and he turned back to the table, he found everyone staring up at him silently. Alexis was the only one who had known Michael long enough to know of the stormy end to his relationship with Glade.  It had been kept behind closed doors for the most part, except for one notable exception, to which Alexis had been witness and help Michael clean up the blood from his broken nose.

``Sorry,'' he mumbled awkwardly.  ``Old friend.  Ex.''

The corners of Alexis' mouth twitched up slightly into a smile.

Bomber, sitting on the other side of Michael from the Shy Blue Fox, rested a hand on his knee and gave it a gentle squeeze beneath the table.  ``You okay?  Look kinda shocked.''

Michael nodded and scooted the last few bites of his breakfast burrito around on his plate before giving up and wrapping his hands around his coffee cup and leaning back in his chair.

``Yeah, it's just a bit of a shock.  We were only together for a year and a half or so, but she\ldots{}uh, he now, I suppose, cut contact after a bit of a messy breakup. It's just a surprise.''

``Been a long time then?''

Michael nodded once more, ``Yeah, about five years or so, I think.  Sh- he, I mean, had always talked about gender and stuff, didn't really think they'd\ldots{}change.''

Rubbing his hand on Michael's thigh comfortingly, Bomber nodded.  ``That'd be a big shock, I guess.''

Michael relinquished his coffee mug to rub his hands over his face before patting at Bomber's own on his leg.  ``Jesus.  Yeah.  It's\ldots{}not bad, of course, I'm happy for\ldots{}him, but I think I just need to think about it for a bit.''

Michael kept quiet through the rest of the brunch with his friends.  Bomber lost interest before long and went back to talking with Corrin and Alexis.  The lion had been edging closer to the Shy Blue Fox, and eventually seemed to cave and just rest his head down on the other's shoulder. watching the lazy sketch session.  The Shy Blue Fox hadn't said more than a handful of words through the whole morning, but the lion didn't seem to mind.  Con love, Michael thought.

It took them longer than Michael would've liked to make it out of the coffee shop.  He hadn't successfully worked through the mess of thoughts and emotions surrounding seeing Glade, and so different now, at least not enough to make it back into the conversation.  However, the hard wood of the seat hadn't let him relax at all, and so he'd been antsy as he alternated between wandering through old memories of his mistress (master?) and watching the Shy Blue Fox finish up his sketch with firmer strokes of his mechanical pencil.  It was a little cartoonish for Michael's taste, but he'd muttered his appreciation and thanks as the Shy Blue Fox tugged the sheet of paper from the clipboard and skimmed it to the middle of the table.

Eventually, a critical moment seemed to be reached when enough people decided that they were done and started clearing up paper cups and clinking plates to bring to the trash and dish drop.  Michael looked cautiously around himself before breathing a sigh of relief when Glade was no where to be found.  He scraped the uneaten bites of his burrito into the garbage and set his place along the growing stack above the trashcan before following his friends out into the sun and warmth.

They trundled back to the convention hotel before all seeming to split and go their separate ways. Alexis made his way to the art show to bid on a piece he'd heard would be in it.  Corrin followed for a few yards before getting intercepted by a friend of his and dragged into a growing conversation circle.  Bomber gave Michael a questioning look before heading off to the Dealer's Den to see if, luck of all luck, they had a mouse tail for him.  The lion and the Shy Blue Fox drifted down the hallway, away from the hubbub of the central lobby to, presumably, make out some more.

Michael stood for a few moments, finally free of the burden of conversation so that he could think about what had just happened.  Glade had always been\ldots{}

He shook his head to pull himself out of his reverie.  He was staring into space like some lunatic.  He forced his feet to move, carrying him toward the bank of elevators that would take him back to his room.  He did need to think, but he certainly didn't need to do so in the lobby.

He wound up sharing the ride up with a gryphon in suit (which took up most of the back of the elevator, and a skittish, stocky fellow who pressed the button for two, then spent the entire short ride with his palms pressed firmly over his eyes.  When the door opened and he didn't move, Michael gently guided him out of the elevator and received a mumbled, ``thanks.''

Michael shrugged to the gryphon and hit the door closed button.  The gryphon shrugged back, exaggerated in suit.

Three floors up, Michael made his way out of the elevator, giving the silent fursuiter a wave before trodding off to his room.

Housekeeping had obviously been through the place, replacing glasses, cleaning the bathroom.  He poured himself a rum and coke on a whim -- it was a con, after all -- then flopped down onto one of the freshly made beds and clasped his hands over his front, staring up the ceiling.

There hadn't been a huge, prolonged break-up; just a rough month of small spats and then the crushing argument wherein they had realized that they knew each other less well than they had originally thought.  That was when Glade had spilled her -- no, his -- heart out about the ways in which gender intersected with his life, their relationship, and his sexuality.  Michael had been dismissive, and it hadn't gone over well.

``You get only what you deserve, roo,'' Glade had growled, punched him in the face, and, minus a few curt emails, that had been the last either had seen of each other.

\secdiv

Michael felt the warmth of the rum-and-cokes he'd had up in the room starting to fill him by the time afternoon slid into evening and he made his way down to the bar. There was something cathartic, in a way, drinking to old memories.  It didn't necessarily resolve anything, but the alcohol could let you pretend that it had.  At least now he felt more able to take in the fact that he would be, in a way, sharing this convention with Glade.  After all, not all of the memories were unpleasant.

The elevators ejected him into a lobby more packed with people than it had been before, filled with hundreds of missed connections.  He made his way languidly through the crowd, scanning faces, scanning badges, handing out smiles.  It felt good.

``Oh hey, it's you guys!''

The lion and the Shy Blue Fox looked up from where they were trying to share a seat in one of the lobby's chairs, one earbud in each of their ears leading to a phone held by the Shy Blue Fox.  They looked up to him slowly, smiled with recognition and reached hands out to grab him in for an awkward hug.  Not sober, but maybe not necessarily drunk, the two seemed more alive and active than they had earlier in the day.

The three of them decided on the hotel restaurant as a good source of dinner.  Expensive, but fitting for three innebriated furries to chill and at least get food in the system before the evening's dances began.  They settled into a booth and ordered a round of drinks, beers and a gin and tonic.

``So,'' Michael began, putting what he had hoped was a conspiratorial tone in his voice.  ``Good day for you two?''

The Shy Blue Fox buried his face in his hands and giggled, while the lion looked serene.  ``Mmm, yeah, very good.  Bit of molly, lots and lots and lots of hugs.''

Michael laughed out loud.  Colorado wasn't exactly the heart of Ecstacy, but it showed up every now and then.  More common now was marijuana -- legalization had played a roll in a good number of the attendees showing up here, he was sure.

``Good, glad you guys are having a good time.''

The lion looked almost beatific as the Shy Blue Fox rubbed himself almost sinuously up against him, reveling in the touch.

``How about you, man?'' the lion asked.  ``Been a good con so far?''

Michael nodded distractedly and sipped at his water, ``Good enough, yeah.''

``Saw your\ldots{}your ex?  Saw your ex showed up, earlier.''

``Yeah, I was surprised to see\ldots{}them here.  I wasn't expecting that.''

The lion cocked his head, ``Been a long time?''

``Yeah, definitely.  Five years or so.''

``Not a pleasant break up?''

``Yeah she\ldots{}she at the time, broke my nose and we vowed to never see one another again.''

``But you hugged-'' the Shy Blue Fox began.

Michael brushed it off with a wave of his hand.  ``Yeah.  There's a lot there,'' he stammered, searching for the words.  ``Plenty of good memories, along with the bad.  It's good to see her.  Him.  It's good to see him.''

Ecstasy, in his own experience, added quite a bit to the level of empathy one normally had, and often led to picking up on cues that were embedded in day to day speech, bits of meaning that exposed more despite all attempts to hide.  It was no different with these two.

``He's not what you were expecting.  Quite the change, huh?''

Michael felt his face flush, and looked down toward the table, nodding.

There was a silence that stretched until their drinks arrived, thankfully not too long.

Finally, the Shy Blue Fox asked, ``Do you think you'll see him again, during the con?  Like\ldots{}actively?''

Michael hid his face in his beer, sipping slowly to buy himself time.  ``Maybe.''  He set his beer down and twisted the glass between his fingers.  ``Maybe.''

\secdiv

By the time Michael made it to the dance, he was decidedly buzzy, full of rum and coke, beer, and mediocre pizza from the hotel kitchens.  It was fuel enough for fucking around in the dance, he figured.  Not like anyone was likely to notice his un-fursuited form stomping away on the ballroom floor to deep house or yacht punk or whatever the hell kids were spinning these days.

The dance was a just good way to let loose.  For him and so many others.

He prowled down the long hallway from the hotel restaurant to the ballroom, weaving skillfully between clumsy fursuiters and those moving much slower than he.

He felt good.  Real good.  This had been a good day overall, from watching his friends have their fun in the morning, all the way down to dinner.  Even, he admitted to himself, seeing Glade again, in all his newfound confidence.

The dance was packed, even for as early as it was.  Saturday was one of the two big nights, with a line-up of two-hour DJ sets that lasted nearly until dawn, and programming had stopped hours ago.  So it was to be expected that there would be a ton of people there, Michael thought, showing his badge to the guard at the door and bouncing in time with the thumping music even as he made his way into the ballroom, quickly picking up the time as he moved.

The music washed over him, thick as honey, as he moved out onto the floor.  It pushed at him, tugged at him, guided his movements between the furries out on the floor, both in and out of suit.  He knew he wasn't a graceful dancer, or even a good one, but he couldn't deny how good it felt to move along with the beat.

It was some uncounted number of songs later before he noticed the form moving closer to him, hips swaying in the rhythm of the music through the crowd.  He was sweating, and he could feel dinner's two drinks coursing through his veins, that was about the only indicator he had that it was later on in the evening.

Glade.

He slowed his movements, settled down into a relatively quiet sway where he stood on the dance floor, watching as Glade moved up to him through the crowds.  The presumed hormone therapy had changed the shape of his previous mistress, shifting the bulk of his weight up toward his middle and away from his hips, and what had been a generous bosom had been drastically reduced -- how, he couldn't say.  The walk had changed too, though not in any way he could pinpoint.  More movement to the shoulders, perhaps.

What he saw, stalking toward him rhythmically through the crowd of dancing furries, was a well-built, clean young man, dressed in jeans, a skin-tight shirt, and a leather jacket, who somehow still retained so many recognizable features of his old partner.

Glade reached out and took his hand, drawing him dancingly from the floor and away from the speakers to the back of the room.  Michael followed helplessly, half in awe and half in shock at his former mistress' directness.

They both moved subconsciously to the beat, shifting their hips and their weight in time with the music, then nearly pausing as the beat built up to the drop.

Glade brought him to an unoccupied section of the wall at the back of the ballroom and turned him firmly so that his back was to the wall, then pressed him up to it.  He seemed deliberate in his actions, making sure that Michael's back was flat against the wall before planting his hands surely beneath each of his arms, leaning in close to him.  He had to stretch up a little in order to make himself heard as he spoke quietly.

``Lets have some closure here, roo.''

Michael swallowed roughly at the sure signs of dominance that remained in his ex's actions.  ``What,'' he began, and swallowed once more.  ``What sort of closure do you want?''

``One more night,'' Glade murmured.  ``Tonight, you're mine, we take what we had at the best of times, and have that be the end, and we go back to being comfortable friends, rather than what we had before.''

``But you're-''

``I'm me, and all you need to be is my little pet roo, just once more.''

Michael swallowed hard once more, keeping his hands flat against the fabric of the dividing wall behind him.  The alcohol, the dominance, the familiarity all worked in Glade's favor, and he couldn't do much to surpress the excitement that had lingered since that violent outburst that had ended their relationship in the first place.

All he had to do was reconcile that it was really over, and on agreeable terms.

He felt dizzy, looked up to find no relief in the swirling lasers and lights that projected from the stage, a glowing arachnid of greens, blues, and purples.

``T-tonight,'' he stammered, ``I'll be your little pet roo.''

The grin that creased Glade's face was knowing, pleased, with maybe a touch of evil.  The music began to rise once more in a crescendo.

``You're already a little buzzed, I can smell the beer.''  Glade held up a slender tube which tapered to a small mouthpiece and glowed with a blue LED, ``Will you still be my good little pet if I get you a little more buzzed?''

It took Michael a moment to understand what was being offered.  Once he figured out the vape pen, he nodded shakily.  Glade knew him through and through, knew how much he liked placing himself into someone else's hands.  Glade took the nod as assent and tilted the mouthpiece of the vape to his lips, not yet pressing the button that activated the heating coil.

``You'll be my pet?''

Michael nodded.

``You'll please your dom?''

Michael took in the new term, nodded.

``I've got my crop.''

Michael flushed in the dark, nodded.

``Do you have your paws with you?''

Another nod.

``Same safeword.  `Rouge'?''

Michael squirmed between Glade and the wall, nodded once more.

Glade pressed down on the stud that activated the vape and pressed the tip of it between Michael's lips, quietly instructing, ``Breathe in.  Slow.''

Michael knew the theory behind the devices, and so he breathed in slowly and carefully, tasting the not-quite-smoke flavor of pot on his tongue and down his throat, flowing liquidly within him and filling him with both a sense of fullness-of-being and hunger that he couldn't quite put his finger on.

The devices were frowned upon by the hotel, no matter what they contained, so Glade kept the LEDs covered by his finger and palm, letting Michael have a good long inhale before swiftly pocketing the vape once more.

Michael held the warm vapor for a few seconds, then let it out with a few gentle coughs, muffling the sound as best he could.

``Come on,'' Glade said, with a sudden, earnest smile.  ``Let's finish this set, at least.''

The two moved back out onto the dance floor.

Michael felt the pot take him over in a matter of minutes, rolling in from his extremities until he felt as though he was dissipating into a cloud.  The music moved through him with such ease, and he felt like some luminous being, moving against and with the other luminous being of Glade, enjoying both the space and tension between themselves, as well as the friction of cloth on cloth or leather as they brushed up against one another.

Some unknown amount of time later, the set drew to a close amid the cheers of their fellow dancers, and Michael and Glade drifted from the dance floor, hand in hand, out past the guard and into the hallway.

Michael found it difficult to stop dancing, swaying gently from side to side and rocking his weight back and forth even as they made their way over to the bank of elevators.  Glade laughing at him was all he needed in terms of encouragement.  He got the impression that Glade himself wasn't entirely sober, and he felt in good company -- comfortable, like how he used to feel when they smoked together.

They made their way to the elevators and stood with a tired looking canine suiter and a few other up-late furries, waiting.

Glade leaned in against his arm and tugged him down a little closer, murmuring, ``Your room okay?''

Michael nodded.  The whole room had agreed to let private liaisons be allowed, and so anyone who was there and not already in the middle of something should agree to clear out if Michael needed.

The ride up was uneventful, and likewise opening the door into an empty room.  Alexis was probably still dancing with Corrin, and Bomber was probably hovering around the edges of the dance, unsure of where he belonged.

Michael slipped into the room with Glade, then bent down to offer a kiss, falling back into old habits with the drink and pot filling him with warmth.  Glade leaned up to meet the kiss, but quickly took Michael's lower lip between his own and bit down on it.  He tugged carefully downward until Michael's face was level with his own before letting up on the bite.  ``You going to be a good pet tonight?''

Michael sucked his lower lip into his mouth and searched briefly for the taste of blood before nodding bashfully, ``I'm going to be a good pet.''

``Strip, then,'' Glade ordered imperiously.  ``And get your paws on.''

Michael hesitated, swaying a little on his feet.  Glade reached behind his back and extracted a small riding crop from his back pocket, simply holding it at his side.

Michael got the hint, and slipped over to where his bag lay next to the bed, fishing out his paws: gloves of dark brown faux fur.  He moved back to where Glade stood and carefully slipped out of his shirt and tugged his jeans and underwear off, standing exposed and erect in front of Glade. He shivered slightly in the air-conditioned room, though at least half of that was due to his excitement.

``Now me,'' Glade ordered quietly, holding his arms out.

``Yes mistr-'' Michael began, before realizing his mistake.  He winced as Glade raised the crop, then braced himself and held still.  There was a quick crack and an almost satisfying sting against the left cheek of his buttocks.

``You will call me Dom Glade, little pet,'' he purred.  ``No more slip-ups.''

``Yes\ldots{}Dom Glade,'' Michael whispered.  The strike had hurt initially, but with his body buzzing in its high, the sting was quickly turning into the familiar pleasant sensation they had experimented with so long ago.

Glade held his arms out and let the naked Michael slip the leather jacket off, then lifted his arms for Michael to lift his shirt.  There was something intimate about undressing his former partner, even having been ordered to do so, and he took his time, being mindful of the crop.

Beneath his shirt, Glade was bare, no binder or anything.  There were just two well-healed scars, each curving gently beneath his nipples, where the mastectomy had taken place.  Michael brushed his hands, fuzzy in their paws, softly down over his ex's chest, wonderingly.  There was so much more body hair than he had remembered, more than some of his roommates here at the con, come to think of it.

``There you go, little roo,'' Glade murmured, sounding pleased.  ``You're halfway there.  Kneel to do the rest.''

Michael nodded and obediently lowered himself to his knees, reaching up with his paws to work on unfastening the button of Glade's jeans, fumbling partly because of the fake fur and partly out of nerves and excitement.  Glade wore boxers -- though he always had -- which slipped part way off his hips as his jeans were carefully tugged lower.

Michael reached his fur covered hands up to rest just above the wasteband of Glade's pants and underwear, uncertainty growing within him.  He finally smoothly slid his hands down, taking the garments along with them to free his ex from his pants.  He hadn't been sure what to expect, seeing that Glade had opted for top surgery, but found himself confronted with the neatly trimmed crotch that still felt familiar to after all these years.

Glade chuckled quietly above him, drawing the tongue of his crop up along Michael's back to tease gently across his shoulders.  ``Expecting something different, little pet?''

Michael flushed and drew his hands lightly up over Glade's legs once more, the fur of the gloves brushing through the hair of his ex's body.  ``I\ldots{}don't know what I was expecting.''

Glade tapped the leather tongue of the crop gently against the back of Michael's head, ``I'm comfortable how I am.  I can present how I like, and little pets can still worship me.''

His cheeks still red, Michael nodded and swallowed, carefully rehearsing in his arousal- and drug-addled mind what he was going to say next.  ``May I worship you, Dom Glade?''

Glade walked slowly around Michael as he sat, kneeling and aroused on the floor.  He seemed intent on drawing the moment out and letting Michael stew.  The tongue of the crop kept tapping and prodding, as though it were inspecting all the ways in which his body had changed over the years.  The process of waiting had that flavor of delightful agony that Michael knew Glade was keen on.

Finally, Glade relented and sat back on the edge of the bed behind Michael, tapping him gently on the shoulder with the crop before leaning back onto one of his hands.  ``There's a dam in one of the pockets of my coat.  Get that, and you may worship me.''

Michael tried not to appear too eager as he crawled over to the crumpled jacket and tugged out the plastic-wrapped dental dam.  Aside from a few instances of almost fooling around, like that morning, he had been mostly abstinent throughout the last five years, and he lept at the chance to service his old owner as he used to (with that bit of latex in between, this time -- they weren't fluid-bonded anymore).  It might be the alcohol and pot buzzing through him, but he felt right, in his place.

Glade kept his noises primarily to purrs and growls, huskier than Michael remembered.  Even so, the act maintained its familiarity to him: the long teasing licks, the shorter feathery ones, lazily spelling his name out in cursive against the latex of the dam before delving a little more adventurously between the labia of his former -- and once more -- lover.  His hands, still stuffed in their paws, alternated between gentle brushings and firmer pets along Glade's legs, showing his adoration as he worshipped the best way he knew how.

He read his partner's body as best he could, finding all the spots that led to the reactions he craved.  He would focus there, then drift his attention elsewhere, not letting any one spot get played out.  Despite the years intervening, he still felt as though he knew Glade's body thoroughly.

``H-huff,'' Glade breathed with a stiff shudder.  ``Mmn, such a good little pet.''

Michael relaxed back onto his heels, peering up along Glade's more masculine body, eager to receive the praise.

``You did well, roo,'' Glade growled, hefting himself up further onto the bed.  ``Come up here by me, there's one more thing I want you to do, and I know you deserve it.''

Michael nodded shyly and stood to his feet, feeling the blood flow freely through his cramped legs.  He moved around to the side of the bed before climbing in, stretching out alongside his ex.

Glade leaned in closer and bit gently at the lobe of his ear, whispering quietly while he was there, ``I want you to paw, just one more time for me. I want to see you get off.''

Michael blushed and nodded, still shivering at the bite to his ear.  ``Yes\ldots{}yes, Dom Glade.''

He moved to slip one of his hands out of the paw mitts, only to feel the sharp crack of the crop against his thigh.

``But leave those on.''

Michael swallowed.  He knew he'd make a mess of the paws, that was inevitable.  He also knew how to clean them, though, and so after a moment, he nodded and rolled onto his back.

His erection hadn't let up since Glade had first gotten his attention with the questions on the dance floor, and by now, he felt an aching need for release.  The fur of the paws was dry and coarse against his stiff shaft, and though he usually required lube for masturbation, it seemed to feel just right to curl the clumsy fingers loosely around his cock and stroke along it gently.

It didn't take much, really.  The tickling of the fur and the occasional squeeze around the base of his cock as he stroked was enough to get him closer and closer to his orgasm.  What finally did it, though, was that last bit of mental stimulation when Glade leaned in close against him and nuzzled up to his ear, murmuring, ``You are just such. A good. Boy.''

His heavy breaths were cut short with a quiet whimper and he gripped tightly around the base of his shaft with his fur-covered hand and felt the rush of pleasure wash over him, felt the first few spurts of seed land on his front, and the rest dribble down over the brown fur of his paw.

``God, I missed that,'' Glade cooed as Michael settled back down onto the bed.

``Nnnf.''

Glade grinned and gave a gentle kiss to Michael's cheek before levering himself up out of bed.  ``Thank you, little pet.  Now, if you'll excuse me, I've got some other parties to go to.''

``Huh?  But\ldots{}'' Michael began.

``Hush, you did good.''

Michael leaned up onto one elbow, watching Glade tug his boxers and pants back on, then hunt for his shirt.  ``What\ldots{}what was that?  For us, I mean.''

Glade tugged his t-shirt back over his head and stood, regarding Michael for a moment.  ``Closure,'' he said simply.

``And where do we go from here?''

``I don't know, roo, I really don't.  I just feel like we're in a better place from where we left off before.''

Michael nodded.

His head still spun.

\secdiv

There was an electric-mechanical click as the lock on the door activated, and Michael jolted upright in bed, rushing to cover himself with his hands as he sat up.  He must've drifted off once Glade had slipped out of the room to head to his party.  He was still wearing the paws, even.

Bomber slipped quietly into the room, saw Michael in his messy and furry state, and smiled bashfully, turning away to face the wall.  ``Need a moment?''

Michael shook the paws off of his hands quickly and ducked over the edge of the bed to snag his underwear, slipping them on quickly, ``Just\ldots{}ah, just woke up.  You're fine.''

Bomber laughed and slid further into the room, slipping out of his canvas jacket and sitting down on the bed.  ``Hope I didnt interrupt, thought you were just sleeping.''

``I probably was, at that,'' Michael mumbled, rubbing his hands over his face, before reaching for his shirt to wipe up his spilled cum.

The two sat in awkward silence for a minute or so before Bomber asked, ``Good evening, then?''

Michael let out a breath, more forcefully than he had intended.  ``Yeah.  Glade came over.  Bit of\ldots{}bit of the old days, I guess.''

Bomber nodded and fiddled with one of his fingernails.

``Sorry,'' Michael offered.  ``Maybe a bit much information.''

``It's okay,'' Bomber responded.  ``Just wondering what he means to you.''

Sensing the undercurrent of meaning, Michael reached a hand over to rest on Bomber's knee.  ``We broke up, a long time ago. I don't think that's going to change.''  He took a deep breath before continuing, ``I know you like me, Bomber, and I know I've been distant, but I just don't really know where my head is anymore.  Glade meant enough to me that I don't know what to do after that ended.''

``I can't really say I know how you feel,'' the mouse replied hesitantly.  ``I've never been in a situation like that.  I don't want to push you or anything, I just like you, I guess.''

Michael nodded, silent.

The two sat for a while longer, touching and keeping contact.

Finally, Bomber asked, ``Think you guys will hook up again?''

Michael thought for a moment, then shrugged, ``Probably not.  Not in the same way we did before, certainly, but it's good to have contact open again.''

Bomber looked down and nodded.

Michael laughed and leaned over to hug both arms around his friend, ``Hey, don't worry, whatever happens happens, not leaving my friends behind at all.''
