%%%%%
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

I spend a lot of my time thinking and writing about the furry fandom.  It's something that's near and dear to me, and I would have been a much different person in life without it, and I don't think that would've been for the better, either.  It's made me who I am in a way that I really like, that I really cherish.

I love furry media, but I think that my strengths in writing lie more in the meta-furry side of things.  That's not to say that I don't enjoy fiction, by any stretch, nor that I won't try my paw at writing more traditional furry prose, because I do have my share of ideas.  Simply, that I think my first real forays into furry fiction ought to be on familiar ground for me.

Queer media also has a spot in my heart.  Coming to terms with myself as a gay man growing up in an upper-middle class mid-western town affected me greatly. And to say that coming out as a transgender person identifying as genderqueer later on in life affected me greatly would be a huge understatement.

Thorughout all of this, having representation of people like me -- gay folks, trans folks, even furries -- has meant a lot to me.  Seeing people that I can identify with going through all of the little dramas and small adventures, and yes, even sex, in daily life has made me feel less alone, more real, more complete.

So here I am, writing three short pieces of erotica featuring all sorts of queer furries, and you know, I feel alright about it.

-- Makyo\\September, 2015

\newpage
\textit{Since this isn't a bunch of animal people\ldots{}well, I mean it is\ldots{}you know what I mean.  Since this surrounds human furries, I should note this is a work of fiction. All events and characters appearing in this work are fictitious. Any resemblance to real persons, living or dead, is purely coincidental.}

\textit{This work of fiction is erotic in nature and contains graphic descriptions of sex.  It is not intended for minors.  Additionally, the first piece touches on the topic of non-consensual sex -- remember to always, always get consent from your partner or partners!}
