\hypertarget{ioan-bux103lan-2346}{%
\chapter{Ioan Bălan — 2346}\label{ioan-bux103lan-2346}}

Ioan knew well enough what was coming, so ey was able to brace emself well enough when May came barrelling out of the default entry point on the dandelion-ridden field that ey was not totally bowled over, managing at least a graceful descent to the ground. The skunk had already looped her arms around eir middle and tucked her head up under his chin before ey was even able to sit up straight enough to get eir arms around her.

``You nut.'' Ey laughed, reaching up to tug at one of her ears affectionately. ``Good to see you too.''

``Ioan, I am in no way sorry for knocking you over,'' she mumbled, her grip around eir middle tightening. ``Though I am dreadfully sorry that this happened again. I missed you.''

Giving up on the prospect of sitting up straight so that ey could keep both arms around her, ey leaned back onto one hand, propping emself up. ``No need to apologize, May. I'm just happy to see you again.''

The skunk leaned away from em enough to dot her nose against eirs. Her eyes were quite red and ey could see tear-tracks in the fur of her cheeks. She looked a mess. ``Do not take my apology away from me. I have been saving that one up.''

``Alright, alright,'' ey said, pressing eir nose a little more firmly to hers for a moment before leaning back again. ``Apology accepted. Are you feeling better?''

She sat upright rather than leaning against eir front and nodded. ``Yes. I was able to get a lot out that I think has been pent up for a while. Thank you for giving me the space. I promise I did not fuck with your pen collection.''

``Good. I had it all perfectly organized.'' Ey plucked a dandelion from the field and tucked it behind her ear. ``Now, do you want to talk about it? Or should we do that later? That was longer than the last few times.''

``Later, please. I want to say hi to Douglas and wash my face and just be normal for a bit.''

Douglas Hadje met them on the stoop of his house and, as had become their ritual over the years, hugged the skunk, lifted, and twirled her around, her bushy tail streaming along behind her.

``Hey May,'' he said, setting her back down again. ``Glad you made it through.''

``Of course I made it through. You still have at least seventy nine years of me haunting you before I can do something else.'' She grinned. ``And even then, the contract is renewable.''

``Ornery as ever. Well, want to come in?''

``For a bit, and then I want to come back out here and lay in the grass and bake in the sun.''

After May had cleaned up and Ioan had helped Douglas prepare coffee and some sandwiches, they sat around the table to catch up.

``So, what news of the aliens?'' Douglas asked.

The skunk squinted at him. ``Has Ioan not been keeping you up?''

``A little. Ey said ey wanted to wait until you got here, though.''

She rolled her eyes. ``Well, out with it, then.''

``I've gotten several messages from Codrin over the last few days, but nothing as of this morning, when ey said they were heading out to start the talks.''

``So they are already a week into them.'' She looked thoughtfully up to the ceiling. ``Perhaps well into them by now.''

``Or maybe they're already over,'' Douglas said.

``A gloomy thought. I would like to hope that they are going quite well. Codrin is there being a Bălan, Tycho is there being a nerd, this Sarah Genet is there being a whatever a Genet is like, Why Ask Questions is there being a shithead.'' She wrinkled her nose. ``And True Name is doing her best control the whole thing.''

Ioan was pleased to see the mildness of the skunk's expression. It really did seem like much of those overwhelming emotions had burned themselves out over the last few days.

``It's weird,'' Douglas said. ``Every now and then, I'll hear about something from one of the LVs that's anchored to a certain time and I'll remember,''Oh shit, yeah, they're billions of kilometers away by now``, and then I have to spend some time trying to conceptualize that distance.''

Ioan nodded. ``The transmission delay throws a wrench in things, doesn't it? I was just thinking about that on Secession day. We were celebrating and it sounds like they were, too, but we didn't learn about their party until a week later.''

``The thing that always catches me off guard is that our days do not seem to line up any longer,'' May said around a bite of sandwich. ``I mean, they do, but when the delay is off by half a day, we start getting messages at shit o'clock in the morning. It is a strange feeling.''

``Exactly.''

``I hope they're still in the talks, too. Codrin sounded hopeful, at least. The messages that they'd been getting from the Artemisians were interesting. I'm guessing the powers that be made em promise not to send the full message text yet, but what they have learned is fascinating. Four races on one ship must be a hell of an experience. The DMZ sim sounds pleasant, though, and all of the work they've done to prepare is really kind of impressive.'' Ey sipped at eir coffee to buy a moment's time to think before saying, ``There was a bunch of stuff in there for you, too, May. We can go over that later, though.''

The skunk frowned, finished the last of her sandwich, and then settled back in the chair with her coffee. ``You cannot leave me hanging, my dear. May I at least have a preview?''

``Well, Codrin's worried about you, as is Dear.''

``The memory thing?'' Douglas asked.

Ey nodded.

May sipped at her coffee, looking out the window to the rolling field beyond. ``I am worried, too. You know that.''

``I know. Reading between the lines, though, I think ey's worried about the whole clade. Ey's worried about you and Dear, and ey's worried about how True Name and Why Ask Questions are going to act through this. Dear reacted poorly to the whole time-modification thing.''

She nodded and sat in silence for a minute before setting her cup down. ``We are not doing as well as many of us would like, no. I have news as well, but I would like to share it outside where I can sit in the sun and feel the grass. Is that okay?''

Ioan and Douglas collected plates and coffee cups, then the three of them trooped out into the field while May spoke.

``We have lost May One Day Death Itself Not Die and I Do Not Know. Death Itself stopped talking, and then she stopped moving. In Dreams visited for a while there, and a few days ago asked me to come visit as well. That is why this spell seemed to last longer than usual. Evening hit, she smiled at us, shrugged, and then quit.''

May's voice was thick as she continued. ``They all lived in the same house, did you know that? All ten of that stanza. Many of them did not even talk with each other, and none of them ever forked. They were always quite unstable. The next morning, I Do Not Know was gone, and Names Of The Dead said that she had quit shortly before sunrise.''

Ioan and Douglas remained quiet as they walked. The skunk didn't seem to be quite done saying the things that she needed to.

She continued after a few minutes of mastering emotions, voice clear once more. ``In Dreams and I talked quite a bit. She said that there have been fewer instances of instability in older clades than expected, given \emph{On the Perils of Memory}. Fewer uploads are susceptible to the long-term effects of unceasing memory than expected, I guess. I was pleased to see that Debarre seems to be doing well.''

``That's heartening,'' Douglas said. ``At least in a way.''

The skunk nodded. ``I am happy that the System is more stable than feared, but I am unhappy that we seem so strongly affected. In Dreams said that she is going to do some research and see if there are ways that we can at least improve on the way we deal with the effects. I do not know that there is a way to get rid of them entirely, at least not without further individuation, but the least we can do is help keep ourselves sane for longer.''

Ioan took her paw in eir hand and lifted it to kiss the back. ``Please, yeah. If you go bonkers, I'll be furious.''

She laughed and gave em a pitying look. ``Mx. Ioan Bălan, you are pretty good at acting furious on stage, but I do not believe for a second that you could actually feel that way. Even Codrin was able to have a normal meeting with True Name after she did as she does with em.''

Ey did not laugh. Neither, ey noted, did Douglas.

``I am sorry,'' she murmured, ears laid flat.

``\,`Furious' is the wrong word, May. I'd lose my damn mind.'' Ey took a shaky breath and rubbed at eir face. ``I can't tell you you're not allowed to or anything, since I know it's not really up to you, but please at least try to stick around.''

``I'm not going to pile on or anything,'' Douglas said. ``But I will say I'd be pretty upset, too, so if there's anything I can do to help, I will.''

May dragged them both to a stop in the field. Her expression started out angry, then screwed up into sadness, and finally settled on tired. ``I love you both, each in your own way, and I promise I will do what I can to stay here, stay grounded. I cannot speak for the rest of the clade, and certainly not for Dear, but I will do what I can.''

It was not uncommon for these reunions to be tearful, Ioan knew, but it was a different sort of pang that settled in eir chest with the news, and it was a few minutes before ey was able to speak again. ``Sorry, you two.''

The skunk stuck her tongue out at em. ``I will allow you this one apology, but do not make a habit of it. You are allowed to cry at sad shit.''

Ey rolled eir eyes and shoved at her.

``Well, I was promised laying in the grass and baking in the sun,'' Douglas said. ``So come on, we can at least enjoy the rest of the afternoon.''

May made it through dinner — Ioan was heartened to see that she'd actually eaten all of the chicken soup ey'd made — before padding off to a beanbag to curl up. She kept up a sleepy conversation for a few minutes while Ioan cleaned, but even that tapered off to silence. When next ey looked back, the skunk was asleep.

Every time ey'd left her to sleep out on the beanbag in the past, though, she'd spent the next day disoriented and moody (ey suspected this is what she'd meant when she said she slept better next to someone all those years ago), so, once ey finished cleaning, ey knelt beside the beanbag, wormed eir arms beneath her, and scooped her up.

May made a sort of drowsy chirping noise as ey lifted her, hugging her arms around eir shoulders for the short journey to the bedroom. Long as her tail was, ey still had to be careful not to step on any of her fur with it hanging limply, almost to the ground.

Once there, ey helped her out of her clothes, unsteady as she seemed, and then tucked her in, leaning down to put a kiss on her cheek.

``Ioan?''

``Yes?''

``Can you stay?''

Ey hesitated then nodded, forking off a copy to finish cleaning up and taking notes. After a few minutes of eir own bedtime routine, ey slipped into bed with her. Ey was certainly tired enough, ey realized.

And so now, back at home, back in their own bed, alone together, May and Ioan had the conversation ey felt they truly needed. They talked quietly, almost \emph{sotto voce}, now that they were alone, now that it was dark and comfortable and they were no longer surrounded by the loud, raucous colors of Douglas's field. They shared their kisses, their small touches, they reaffirmed, in so many small, unspoken ways, their love for each other, and they talked.

``What do you think they are learning?'' May murmured, nose-tip poking up against Ioan's chin.

Ey had to speak carefully to respond, lest ey bump her snout. ``Who can say? Perhaps they are learning, perhaps they are teaching.''

``Poetic.''

``There are Odists involved, it's going to be poetic through and through.''

She laughed and poked em in the belly with a claw. ``Jerk.''

``That's me, yes,'' ey said, grinning and nudging her muzzle about with eir chin. ``The Odists are learning how to manipulate new species. Tycho's learning about the stars. I can't speak to Sarah, but Codrin is along for the ride.''

``Did ey have much more to say about eir doubts?''

``A little. Ey's still feeling more caught up in the events than an actual participant, but I think ey's also starting to look for ways out of the cycle. I don't know if ey's picked up any specific ideas on how to take charge, but that ey's decided that that's something ey'd like to do is change enough.''

The skunk nodded. ``You are a careful lot, but it is nice to see when you do become more assertive.''

``We lack your flair,'' ey said, ruffling up some of her fur.

``I also enjoy that, do not get me wrong. Not everything needs flair.'' She perked up, dotted her nose against eir chin, and asked, ``You said something about time modification earlier, but I was shattered and did not think to ask about it. What does that mean?''

``Oh, right. It sounds like the Artemisians don't fork, and instead rely on the ability to change how fast they experience time. Individuals or groups can speed up their perception so that the world around them seems to slow down, that sort of thing.''

There was a long moment's silence, and were it not for the shallowness of her breathing, ey might have thought May had fallen asleep. Eventually, she whispered, ``I do not like that.''

Ioan dipped eir chin enough to bump eir nose against hers. ``Codrin said Dear got quite upset about it, yeah. It warned em that there would be two Odists among the emissaries and that ey should watch out.''

She remained still, no reciprocating press of nose to nose. She continued in her whisper. ``Once, when I was in school, I performed in a play that used the works of Emily Dickinson throughout. I still remember it. \emph{Time feels so vast that were if not For an Eternity— I fear me this Circumference Engross my Finity—}''

Ey remained quiet as ey mulled over the words. The archaic language felt opaque to em, but, as ey prowled through synonyms, ey began to piece together meaning. ``You've mentioned eternity before in the context of getting lost. This sounds almost relieved, though, that eternity exists, lest everything get too overwhelming.''

``There was no eternity in there, Ioan. Time was beyond vast. I \emph{was} engrossed. There was no me left. When we were pulled out, we were finally confronted with eternity again.''

``\,`We'?''

May took a while to respond. ``Michelle and the author of the Ode.''

Ey nodded, letting the comment about the Name slip by, asking instead, ``And being stuck in a place with malleable time would bring back a lot of that?''

``Yes. Codrin is right to be careful. The clade struggles enough with stability as it is.'' She broke the tension of the moment by licking his chin. ``On a happier note, In Dreams mentioned a hypothesis about the struggles we've had with memory.''

``Oh?''

``Well, happier for the System, if not for us. I guess she has hunted down some other clades that have been having problems. She says there are uniting factors, such as a weaker boundary between subconscious and conscious, a greater sense of the numinous, and so on. I am too sleepy to remember the details, but she is looking into it.'' The skunk giggled. ``She says we should get therapy.''

``Oh, you definitely should,'' ey teased. ``Maybe this Sarah Genet is still on the System. That's what she does.''

``Therapy?''

Ey nodded.

A moment's hesitation, and then May nodded. ``I let In Dreams know.''

``Good. The more minds working on this, the better.''

``Are you really that worried, my dear?''

Ey frowned, shrugged. ``That's part of it. More, I just feel helpless. I'm not worried about you going sideways any time soon, really, and certainly hope you don't at all, but should that happen, watching helplessly would be\ldots well, it's a big fear of mine.''

May hugged herself closer to em, snout once again ducking beneath eir chin. ``I understand. I am stuck with the related fear of losing control. I do not like the feeling of not being in control of my emotions, even for these brief periods, but if that were to just become my life\ldots{}''

After she trailed off, ey tightened eir arms around her, brushing fingertips through fur.

They lay like that in the quiet and the dark. Eir fork apparently finished up with eir notes and quit, but given the topics of conversation, ey declined to accept the merge. Ey did not want to be distracted from the simple task of petting May, of enjoying the feeling of having her back.

``May?''

The skunk poked her nose against eir collarbone. ``Mm?'' She sounded half asleep.

``I really can't lose you. You know that right?'' Ey felt her stiffen in eir arms, continued, ``I said ages ago that I'm not built for a life with death in it. That's why I'm here. That's why I uploaded in the first place, to get away from that.''

``Ioan,'' she said, voice hoarse. ``I already-''

``I know, you already promised. I believe you. I'm not trying to berate you, I'm trying to say I love you.''

``Ioan Bălan, if you make me cry again, I will smother you in your sleep.''

Ey laughed. ``It sounds like it's already too late.''

``Thin fucking ice, buddy.'' May sniffled and squirmed around until she could tuck back against eir front. ``I love you too, my dear, top to bottom and front to back.''

As ey settled in for sleep, kissing the backs of the skunk's ears, ey marveled that ey could only remember the Ioan who never thought to form attachments, who could never remember to ask May if they were in a relationship, who continually wondered how she wound up in eir life as some other person. That Ioan was gone. Ey had slipped out while the Ioan ey was now wasn't looking, and had never come back. Ey wished em luck, this younger version of emself. Ey wished em happiness and fulfillment. And, should that Ioan ever find emself struck by the wonder of love, ey wished em courage in the face of it.

This Ioan, the one ey was now, understood the value in attachments, and yet ey could still marvel, twenty years on, at just how much more complete ey was with May in eir life, and for that, ey'd be forever thankful.
