\hypertarget{ioan-bux103lan-2346}{%
\chapter{Ioan Bălan — 2346}\label{ioan-bux103lan-2346}}

Ioan and May both awoke to messages. May, however, was the first to read hers, having gotten up before her partner, so when Ioan stumbled out of bed toward coffee, the skunk was already sitting at the table, her note before her and eirs still in its clade-eyes-only envelope, waiting for em.

``As soon as you are a real person, my dear, I need you to read this and tell me what is happening.''

Ey frowned, nodded, and diverted from the coffee pot to splash water on eir face to help em wake up further. Something about the skunk's attitude suggested something stressful was afoot. Stressful or exciting. Ey couldn't tell which.

Once ey sat down with eir coffee, ey opened eir letter and began to read.

May giggled. ``What the fuck does that expression mean?''

Realizing that ey was frowning, squinting and chewing on eir cheek all at the same time, ey forced emself to relax. ``Uh\ldots this is weird. Does yours have something to do with it?''

``Yes. It is from Dear, who says that Codrin sent you a letter containing a game.''

``A game?'' Ey frowned, started at the top of eir letter and read straight through to the bottom. ``How is this a game? Codrin says\ldots but, well. What does Dear say, exactly?''

``My dear May Then My Name,'' she read aloud. ``Ioan will be receiving a letter concurrent with this one that will bear both the end of an era and the beginning of a game between our two clades. The rules are as follows. First: remember that you love em, that ey loves you. Second: remember who you were, who you are, and imagine what you can become. Third: let go. Fourth: have fun. Fifth: pass this on to Dear\#Pollux concurrently with Ioan passing on Codrin's letter.''

Eir frown deepened.

``Fucking foxes, I swear to God,'' May said, laughing. ``Now, I am assuming that those rules apply to you, too. Remember that I love you and that you love me. Remember who you were, who you are, and imagine what you can be. Let go, have fun, and tell me what the fuck your letter says already.''

Ey did eir best to square Dear's `game' with the text of the letter ey'd received. There were so many ways this could go sideways. \emph{Let go, hmm?} ey thought. \emph{I guess there's nothing for it. Let go and have fun is about all that one can do in this situation.}

``Alright,'' ey said, holding up the letter to read from it. ``Ioan, I hope you are well. We have finished our talks with the Artemisians in grand fashion. They have invited us to become their `fifthrace', meaning that as many of us as would like are able to join them on Artemis, and the DMZ will be expanded to allow a portion of them to join us. There is so much more that I can say here, and will say in future letters, but this one comes with a specific purpose.''

``God, even when you talk to each other, you are nerds.''

Ey forced a laugh, shaking eir head. ``May Then My Name will be receiving a note from Dear about a game. I'm not entirely sure I understand it, but it promises me it's an Odist thing. When I think too hard about it, I get anxious all over again, but Dear keeps telling me to `let go and have fun', so I suppose all I can say to you is the same.''

``Uh, May,'' ey said after a moment's pause. ``This is making me really anxious, too. I promise I'm trying to follow Dear's rules and Codrin's suggestion.''

The skunk's smile fell. ``Well, please get it over with, then, and we can judge Dear on what it considers a game soon.''

``Alright,'' ey said. ``During the talks on Artemis, the time skew—what I'd previously called manipulation—got to be too much for who we thought was Why Ask Questions and she lost it. It turns out that, through some design of True Name's, they swapped in Why Ask Questions When The Answers Will Not Help for the emissaries to Artemis rather than sending Why Ask Questions.

``Anyway, she snapped. She quoted several lines of the Ode as well as several lines of Emily Dickinson, and then she said the Name. True Name got--''

``\emph{What?!}'' May pushed her way up out of her seat and began pacing. ``She did what?''

Ioan realized eir hands were shaking too much to continue reading the paper like that, so ey set it down on the table. ``Ey goes on to describe what happened, but does not include the Name itself. Ey continues: While I now know it, I'm following Dear's suggestion to keep it to myself lest I piss off a bunch of other Odists. It described it as\ldots well, ey continues, but you look like you're going to explode. Do you want me to stop?''

May's pacing had picked up in intensity and she had started compulsively brushing her paws over her whiskers and up over her ears. Ey couldn't read her expression.

``Ioan, listen,'' she said. ``Wait, no. Remember where you first took me for a hike? Bring me there again. Quick.''

Ey frowned, stood, snatched up the letter, and took her paw gently in eir hand before stepping out to the wooded lake ey had taken her several times over the years.

``You don't think someone's watching us, do you?'' ey said, looking around at the placid water, the deer trail, the forest.

``No, not at home, but\ldots well, better safe, yes?''

Ey shrugged.

``Okay.'' She looked to be forcing herself to stand still, now, and her grip on eir hand only tightened. ``I see what Dear is trying to do, and it is really, really smart. Please do not be anxious. At least, not of me, that is.''

Ey looked down at the letter ey still held in eir hand. ``Well--''

``No, disregard the letter, Ioan.'' She laughed and added, ``Or at least disregard it for now. There is info in there, I am sure, but the message is in the dynamic. Dear is an asshole, but a clever one. It has ensured that it doesn't re-learn the Name and that you never learn it for yourself, all while ensuring that it becomes an in-joke between our two clades. It has removed culpability from the Bălan clade and given both itself and me an out, should someone like True Name come asking. She can come hounding you for information like she did after that first letter and all she would find is a clever little way for lovers to poke fun at each other. Let me guess, Codrin said something about how it feels like this is something a Bălan could hold over an Odist.''

Ey blinked, lifted the letter, and read aloud, ``I do worry that this is the type of thing a Bălan could hold over the head of an Odist, but--''

The skunk laughed, lifted eir hand, and licked at the back of it affectionately. ``You two are so predictable. But yes. I do not think we need to worry about that. You did not learn the name, and Codrin\#Pollux will not learn it. It is a delightful strategy. Dear has suggested a move that will preempt most every compunction the conservatives might have. It even used your concerns over power dynamics as part of it. I bet it told Codrin to leave that bit in. It always was good at chess.''

``But ey still knows--''

``Who the fuck cares about the Name?'' she said, laughing. ``It is a stupid hook. It is a way to make us seem more mysterious than we really are. What began as a way of protecting our friend's identity during a shaky political period turned into a way to control how we were perceived. It is our own personal MacGuffin.''

``Wait, really?''

``Yes, really. Obviously, I do not want to share it. Dear does not want to share it. We are still serious about not wanting to share it. Serious enough for one of the conservatives to assassinate one of our own, even. This is a dynamic that has arisen over time, though. The Name itself does not matter anymore. The bearer of it has been lost to time, and any reason to keep it confidential is lost along with them, but it became a hook, and then it became an identity.''

Ey shook eir head numbly. ``You're all completely nuts.''

``Yes, well, tough shit. We have rules to follow, remember? I love you dearly, and I know you love me. I remember who I was. That is no longer who I am. I can imagine who I will be. I can let go of this anxiety around names enough to understand what Dear is doing. And hell it really is fun. You are stuck with me, Ioan Bălan.''

Ey lifted eir arm up, nudging May to twirl, balletic, beneath it. ``Yes, yes. Stuck with the world's most annoying skunk. I don't totally understand, but I trust you on this. You can play your game all you want, but can we head back now? I left my coffee on the table and you have therapy in a little bit.''

(Ioan and May discuss ramifications on history/mythos, and how none of the Bălans want to write it; Codrin learned the Name; news from Castor is shown to be shaped well by TN/Jonas, data dump from Artemis arriving only after local TN/Jonas have shaped expectations, etc, Odists do a therapy)
