\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  I see your past in cross-processed film,\\
  in blown-out colors and over-saturation.\\
  \vin You told me all about it, told me grand stories:\\
  \vin you were going to go back in time and save the world.\\
  I see your past in yellows and browns,\\
  in umber and sienna and amber, in a younger sun.\\
  \vin You sat and told me how --- and you were always sitting ---\\
  \vin you thought past-you dreamt of a future less complicated than today.\\
  I see your past through film-grain and vignette,\\
  with a thick white border, space on the bottom to write.\\
  \vin You told me how you learned so many imperfect things,\\
  \vin in so many less than ideal ways, always at inopportune times.\\
  I see your past in architectural drawings of unrealized buildings,\\
  in paperback covers reaching towards heaven, in trillions of words.\\
  \vin You figured past you dreamt of, not perfection,\\
  \vin but a world unconstrained by so many failures.\\
  I see your past with no me in it,\\
  and wonder if past-you dreamt of us.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  Resuscitating ancient coins in class, we learned,\\
  takes a toothbrush and olive oil.\\
  Slow, steady strokes across, around...\\
  soft bristles dislodging soil\\
  one speck at a time.\\
  But no one that day was nearly as blessed,\\
  seeing a coin shine through\\
  at the end, full relief brightly expressed,\\
  as I was to see you smile.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  When you arrive,\\
  the whole world gets slow.\\
  Sluggish, amber-colored air\\
  mellows lively conversations.\\
  Everyone stops, marvels,\\
  turns eagerly toward you;\\
  and there are no complaints\\
  about warming our faces in the sun.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  We fit together in the strangest ways\\
  and seem to seek new seams to savor.\\
  Such joins are hardly perfect,\\
  thread tugging fabric unevenly\\
  unless it's reinforced over and over again.\\
  We seem to seek new seams to savor,\\
  and, weak though they are,\\
  revel in the imperfect unevenness of joining.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  ``Comrade'' would I call you,\\
  and ``brave,'' and ``fierce'' and ``true''.\\
  ``Lovely'' have I called you,\\
  and hope but to live up to\\
  the example which you set for me.

  So, comrade, onward, ever onward.\\
  I know I cannot hope to offer\\
  much but word on cloying word,\\
  dull rhymes I strain to proffer:\\
  small flowers, small gifts, camaraderie.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  Complementary, clashing anxieties.\\
  Dull clamor of intersecting feelings.\\
  Need, desire, craving, jealousy.\\
  Worry, fear, care, prayerful fretting.\\
  Love, lust, friendship, a need to share.\\
  Emotions on emotions on emotions,\\
  and, often, comfortable silence.
\end{verse}
\newpage

\section{---}

\hfill\textit{February, 2017}

\begin{verse}[\textwidth]
  I chose your name.\\
  To defend, it means. To help.\\
  I admit, having chosen it,\\
  that I chose it to defend you.\\
  When I picked you up by the scruff,\\
  Dragged you off to that place\\
  I hoped we could call ours,\\
  I expected that we'd\\
  simply find a way to survive.\\
  I never expected love,\\
  and rejoice every day in that surprise.

  I chose to collar you.\\
  I admit it was an experiment,\\
  I submit to most, but not my partners;\\
  until then I'd never owned, claimed.\\
  It felt vulgar, at first,\\
  greedy, jealous, possessive.\\
  Through you I learned the joy of possession,\\
  the love and trust and exactness of terms.\\
  Owner, partner, love,\\
  and pup, partner, love.\\
  My beautiful, my own.
  \newpage
  I'll hand you off some day.\\
  I'm a less than ideal owner\\
  in so many terrible ways:\\
  I owe you more than you owe me.\\
  I'll gather your leash up,\\
  I'll let you keep your tag,\\
  I'll bow, I'll kiss you one last time,\\
  and I'll bless you and your new keeper.\\
  And I'll never stop loving you.\\
  And I'll never stop loving you.\\
  And I'll never stop loving you.
\end{verse}
\newpage

\section{---}

\hfill\textit{March, 2017}

\begin{verse}[\textwidth]
  You, for whom a heart means all feeling ---\\
  You, for whom yeah is an expletive ---\\
  You, for whom even computers sing ---\\
  You, for whom every tangle invites disentangling ---\\
  You, for whom even \textbf{I} will rub feet ---\\
  You, for whom shop always follows flop ---\\
  You, for whom words form a squall-line ---\\
  You, for whom I guess I ---\\
  You, for whom ---\\
  You, for whom even ---\\
  You, for whom I reach ---\\
  You, for whom my shit day leads straight to lets talk ---\\
  You, for whom I curate my week's feelings ---\\
  You, for whom I wait by the month ---\\
  You, for whom I structure my year ---\\
  You, for whom understanding of me seems always in grasp ---\\
  You, for whom my struggles provide no obstacle ---\\
  You and I, from whom us.
\end{verse}
\newpage

\section{---}

\hfill\textit{May, 2017}

\begin{verse}[\textwidth]
  Tightly wound springs\\
  Of very carefully\\
  Not touching.\\
  \vin Secret words\\
  \vin To be said\\
  \vin With confidence.\\
  Rules.\\
  Prohibitions.\\
  Limits.\\
  \vin Discussions planned,\\
  \vin Side-channels arranged,\\
  \vin Whiskey purchased.\\
  And now anxiety\\
  Over what it means\\
  And how to work it.\\
  \vin Is it worth it for\\
  \vin Long-standing questions\\
  \vin To be answered?\\
  To invite disaster\\
  For sake of knowledge\\
  And further dreams?\\
  \vin Maybe the answer\\
  \vin Is that tired refrain:\\
  \vin Perhaps, perhaps, perhaps.\\
  And now we're\\
  Awaiting weeks\\
  Of careful touches.
\end{verse}
\newpage

\section{---}

\hfill\textit{August, 2017}

\begin{verse}[\textwidth]
I could never tell you\\
that you feel too much.\\
That you feel too hard,\\
or that your feelings\\
overwhelm and overtake you.

I could never tell you\\
how beautiful that is.\\
That I wish I could feel those things,\\
that I wish I could feel that way.

All I can tell you\\
is how beautiful you are\\
when you feel love.
\end{verse}
\newpage

\section{---}

\hfill\textit{August, 2017}

\begin{verse}[\textwidth]
\textit{Yit'gadal v'yit'kadash sh'mei raba}\\
Would that I had the faith\\
To pray daily.\\
Eleven months to let you go,\\
And an amen to end the sorrow.
\end{verse}
\newpage

\section{---}

\hfill\textit{June, 2018}

\begin{verse}[\textwidth]
When a light so far above me shines down,\\
I lose my footing, stop, look around,\\
and for once, see my way lit before me.

Through you,\\
\vin I learn how I move.\\
Through you,\\
\vin I see how I act.\\
Through you,\\
\vin I judge myself.

When a light so far above me shines down,\\
I turn my face to the warmth and bask,\\
drawing strength, assured in my steps.

Through you,\\
\vin I recognize my failings.\\
Through you,\\
\vin I understand my strengths.\\
Through you,\\
\vin I gain perspective.

When a light so far above me shines down,\\
I reach toward it and grasp at what I can,\\
hoping I might somehow gain my own luster.
\newpage

Through you,\\
\vin I find my place.\\
Through you,\\
\vin I gain surety.\\
Through you,\\
\vin I learn who I am.

When a light so far above me shines down,\\
and I fail to shine myself,\\
I hope only to reflect what I can.
\end{verse}
\newpage

\section{---}

\hfill\textit{June, 2018}

\begin{verse}[\textwidth]
  Every time I seek to change\\
  my life, myself, my love, my name,\\
  every time I try and broaden my range\\
  in this shitty, all-encompassing game,\\
  I hesitate.

  With every change in my life\\
  comes the terror of maybe losing you\\
  of maybe being caught in strife\\
  over such insecurities as few\\
  have escaped unscathed.

  That you love me still\\
  reaffirms so many of my choices,\\
  and I set about with a will,\\
  ignoring querulous voices\\
  in favor of your calm laugh.
\end{verse}
\newpage

\section{---}

\hfill\textit{June, 2018}

\begin{verse}[\textwidth]
  Between our houses,
  there is a simple fence -
  not a chasm, not a wall.
  Chain-link, waist high,
  bedecked with sweet-pea
  and set about with violets.
  Something we can tend,
  something to feel good about,
  something between us
  other than nothing.
\end{verse}
