\hypertarget{tycho-brahe-2346}{%
\chapter{Tycho Brahe — 2346}\label{tycho-brahe-2346}}

The process of leaving the talks was one of emotion bound up in the stress of merging. As unpracticed as he was at forking, the process of quitting and reconciling memories was just as foreign to Tycho, so it would have taken an hour for Tycho\#Artemis to sort through the memories from Tycho\#Emissary and then another two for Tycho\#Tasker to sort through the memories from \#Artemis, even in ordinary times.

These were not normal times.

The better part of eight hours later, though, he was back in his field, back atop his hill, and finally able to sit and think and dream without having the pressing weight of memories holding him in place. He could lay on his back and look up at the sky — no longer just his sky — and think about all that had transpired and all that was yet to come.

At least for a little while.

He didn't know why the arrival ping did not wake him from his daydreaming, but the gunshot sound of a champagne cork popping was more than enough to get him to jolt upright.

``Sorry, Tycho,'' True Name said, laughing. ``That was far louder than intended. I did not mean to startle you.''

He frowned, shook his head. ``It's okay. I wasn't expecting you, though,'' he said, holding out one of the red-filtered flashlights that seemed permanently lodged in his pockets.

The skunk accepted the light and kneeled on the grass beside him, holding it between sharp-looking teeth as she poured two glasses of champagne.

Well, `glasses'; they were shaped more like wide-brimmed, stemmed bowls than anything, somewhat awkward to hold, but then he remembered similar from the dinner party three weeks ago — so many years ago, it felt like — when the skunk and her cocladist, Dear, had lapped at their wine.

He shared a secret smile with himself as he accepted his glass of champagne.

She removed the light from between her teeth and clicked it off again, touching the rim of her glass to Tycho's before taking a lapping sip. ``To the end of that fucking mess.''

He laughed as much as he felt was required to be polite and then took his own sip. \emph{Why is she here?} he thought, racing through a list of the day's actions, hunting for anything that might lead to a visit. He was, he realized, still terrified of her, despite the memories of her struggling, of her confusion, her tears.

The silence drew out. He looked up at the stars and thought about just how much bigger the universe felt now. \emph{I feel every minute of that eternity,} Dear had said back at that same dinner. \emph{I feel every molecule of that universe.}

And he did, now. He felt it all as something more real than it had ever felt before. The math now stood side by side with awe in a way that it had only ever eclipsed before.

``Do you know how old I am, Tycho Brahe?'' True Name said at last. ``I am two hundred twenty-two years old, a fork of an individual who is\ldots who would be two hundred fifty-nine years old.''

He waited in silence. There seemed to be more to come, so he enjoyed his champagne meanwhile. It was quite good.

``I have learned many habits, and I have forgotten countless others. Perhaps that growth is our protection from unceasing memory. We may retain our memories of concrete events, of who we must have been, but I am no longer the True Name of 2124. Even remembering her feels like remembering an old friend. I remember her perfectly, and yet I do not remember how to be earnest. I do not remember how to simply celebrate. I do not know how to simply be.''

Silence fell again while they both looked up to the sky. Nothing needed to be said right away, he figured. Something Codrin had said, though he didn't remember when: \emph{silences come with their own rhythms and will break when it's time.}

Once he heard the clink of champagne bottle against glass again, True Name pouring herself some more, he said, keeping his voice as kind as he could, ``Why are you telling me this? Why are you here?''

She laughed, set the bottle aside and shifted from her kneeling position to more of a lounge, canted to the side with her tail draped down the gentle slope of the hill. ``I do not know, Tycho. I do not remember how to celebrate, but I still want to try, I guess. Sarah has gone to Dear's, and I am not welcome there. Answers Will Not Help and Why Ask Questions are in conversation with another me. Jonas is\ldots Jonas.''

``So you came to me, of all people.''

He was startled away from looking at the sky by the sound of a sniffle from the skunk.

``I'm sorry, True Name. That was--''

``No, you are right, Tycho. I know who I am and how I became that,'' she said, voice thick. ``But I am feeling every one of my two hundred fifty-nine years tonight. I just wanted to be with someone. Just\ldots be, you know? Exist with someone without having some sort of agenda other than to celebrate something big.''

``But you don't know how?''

``I don't know how, yes.''

After a moment, he raised his glass, and the stars glinting off the rim clued the skunk in enough to once again clink hers with it. ``Champagne under the stars is a good start, I guess.''

She laughed.

``I can't speak to your thoughts on not knowing how to be. I don't think I'm any better at it, honestly. Sarah would probably be your best bet.''

``I will be meeting with her soon, yes. We have much to talk about.''

``About the convergence?''

She shrugged, a subtle shifting of shadow. ``That too, yes, but also, news from L5 has been distressing. Much of the clade will be seeking\ldots well, therapy.''

He frowned up to the sky, unable to think of anything to say to that that would not be rude or patronizing.

``Our cracks are showing,'' the skunk continued in a far away voice. ``Growth is colliding with eternal memory, and the cracks are showing.''

He nodded, unsure of whether or not she could even see the gesture.

``Turns out getting invited on a thousand year voyage with a bunch of aliens induces a whole lot of growth \emph{really fast,}'' she said, voice brightening. ``So I will be dealing with that. But come, if I share any more of my weaknesses, I will lose all of my hard-won respect. How do you feel about how things went?''

With that bit of humor, the walls were back up, he realized. The perfect self-deprecating comment brought back that tightly controlled voice, and he felt a sudden sense of\ldots honor, perhaps? He felt lucky that he'd been able to see that side of her, and he quelled the voice within him shouting that that was all a stage play for his benefit as well.

(how they both feel, She's kind of sad, but guess it went okay, he is on the cusp of something big even if he doesn't know why yet, finally feeling eager rather than just anxious)
