\chapter*{Ioan Balan\#c1494bf — 2305}

Mustering the Odists took surprising effort.

Qoheleth had said that he would welcome them at any time, and Ioan had thought that this would be easy.

It was not.

Some did not want to go, even with a forked instance. These took much persuasion. One did want to go but refused to fork to do so, or to fork at all --- this, above all else, set Dear off: the fox did not take confusion of this sort well --- and so the clade had to work with the one member's schedule. Some wanted to bring others (such as Dear bringing Ioan), and this set off another round of debate, delaying them further. They decided that they would only bring willing participants who had played a role in the project.

With little to do, Ioan read and waited. Ey read up on the history of the Ode clade. Ey read up on this form of public key encryption. Ey read Ecclesiastes and all ey could about it. Ey read about various mental vagaries and attempted to map them to Qoheleth, Dear, and various members of the Clade which Dear talked about.

This last was mostly for fun, but ey was also beginning to strategize eir report. Ey wanted to write something very full-fledged, an essay for Dear, and a slightly modified and anonymous version for publication, if the clade would let em. Ey wanted the result to be readable, rather than simply an account of events. Something that would help explain the whys and hows of an older clade in turmoil. A historical document.

And finally, the day had come, nearly two weeks after deciphering Qoheleth's last message. There had been no further communications from the wayward Odist. He seemed patient enough to wait.

\secdiv{}

\noindent Hebel Qoheleth is a patient man. I have time. Enough time, at least. I know I'm gone, I'm a lost cause, but much of the clade still has their faculties about them. Most of them, at least. So long as they act within the decade, I'll be here. Any longer, and we'll risk further degradation.

It's been two weeks since I pinged Dear --- lovely Dear --- and although it had tried to contact me several times, and pinged countless more, I never responded. I did my part. I called them, got them fighting, got them interested, and I think I got them invested.

Now, hopefully they will come.

\secdiv{}

\noindent The designated meeting point was the prairie in front of Dear's house. Ioan was confused as to why they didn't just meet in Qoheleth's sim, until ey realized that many members of the clade had not met in years or decades, or, in the case of up-tree instances, ever.

For a family reunion, it was quite stiff and formal, tense. \emph{Probably not the best of circumstances to regather the clade,} Ioan thought.

Ey focused on eir job as amanuensis.

Ey was surprised at the variety of the cladists. It made sense, of course, for a Dispersionista clade, but it was the direction in which the differences headed which intrigued em. The most notable difference was the gender presentation ratio. It was heavily skewed feminine. Michel Hadje had been born male, ey remembered, but had never transitioned, yet here was a crowd of primarily women, all similar enough to appear related, but different in their own ways. Kemmer indeed.

Ioan supposed it was due to the individual preferences that each long-lived fork had gained in its time away from the root of the clade. The remaining Odists who had not changed, or who had changed very little where the ones who Ioan suspected were the less liberal bunch Dear had mentioned. They all looked fairly similar.

Ioan couldn't help but think that they represented a lot of the various shames and repressions that Michel had held, that everyone held. It was an interesting dissolution strategy.

There was one other fox, as well. A female fox, similar in many ways to Dear, though with natural coloration rather than the iridescent white fur that Dear maintained. Dear gave her a tight hug and introduced her to Ioan as Serene, the one who had designed the landscape of its property. Ioan liked her at once.

Michel himself was notably absent, though Dear assured the historian that he was still very much alive. \emph{``He said that, if anyone should remain behind, it was him, as he had started this whole damn thing.''}

Ioan shrugged and nodded. Dear gave a small smile and shrugged as well.

There were a few tag-alongs, folks immediately identified as out-clade. A few friends, and a few partners, singular and plural. Some who Ioan suspected were like eirself, historians and helpers brought along to witness and record. One of the conservatives (at Ioan's guess, at least) had even brought a reputation analyst along with him, a slight Asian gentleman who introduced himself as Qián Chunyu.

Dear announced that the party would be leaving in five minutes.

\secdiv{}

\noindent Aha! Dear sent a sensorium message. Just a view of a crowd and it announcing that they would be leaving in five minutes.

I ran a quick count of the crowd I could see within the fox's few and it looks like I'll be expecting the entire clade plus a few here and there --- I can see Ioan next to Dear, there --- in just a few minutes.

I'm going to shut down all the exits from this room so that there will be less incentive to wander away. I'll make the extents a little bigger, too, in order to fit everyone comfortably.

This is going to be fun.

\secdiv{}

\noindent The room was a utilitarian grey, closer to black than to white, and the illumination was a central light source somewhere above the exact center of the room, looking slightly misted. It was enough to give definition to the room's corners and boundaries, those walls of matte grey, but not a whole lot else. A small pedestal was set a few meters from one of the walls, only a half a meter high.

A platform? A dias?

Except for that change, it was the default room created before one added modifications.

The Odists arrived in clumps of ten or twenty at a time, taking about thirty seconds to arrive in total. A low murmur started up almost immediately. If this meeting had to be called, then perhaps every detail was of the highest importance.

A man appeared on the platform.

Qoheleth.

Ioan wasn't sure how ey knew, just that it was Qoheleth. He was about Dear's height, but a touch heavier, and had affected a greying beard and receding hairline. His clothes were a simple cream tunic and trousers of\ldots{}was that leather? Atop this, a reddish-brown robe.

He certainly seemed to have adopted the part of a biblical notable. The murmuring doubled, trebled, and then subsided.

Qoheleth smiled, and then called out to the group, ``Welcome, folks. Good to see, er, most of you again, and I'm sure it'll be pleasant to meet the rest of you later.''

Silence. Part confused, part curious, part angry.

``I'm Hebel Qoheleth, though some of you remember me as Life Breeds Life, But Death Must Now Be Chosen, of the Ode Clade. For my own reasons, I've chosen to rescind my membership within the Ode clade-'' He held up his hands to quell the protests from within the crowd. ``I've chosen to rescind my membership within the clade because something is starting to go wrong.''

Iaon looked to Dear. The fox's brow was furrowed and intent. Ey looked from it to the rest of the crowd, studying the expressions. Many of the other outclade individuals were doing the same, confirming Ioan's hunch that they were other amanuenses. The reputation analyst, Chunyu, had positioned himself up near the platform itself and was scribbling notes.

The conservatives looked stoic.

Qoheleth continued, ``Something is going wrong in many of the old clades, with many of the old uploads. They should probably all hear this, but, even though I'm not a part of you anymore, I still feel the responsibility to tell you all.''

``Why the puzzles?'' a voice shouted.

The older ex-Odist grinned, looking proud. ``I had to get you interested and involved to get all of you here. I had to make you all think that there was more going on than just an old man convening a meeting.''

Grumbles greeted this.

``It worked, didn't it?'' Qoheleth smirked, then went on. "So, on to why I called you all here, hmm? Lets get to the good stuff. Or the bad stuff, really.

"There's a bit of a problem going on with the older uploads and their clades. It's a small one now, but I think it'll just get worse and worse over time.

``Actually, it may not be a problem with the uploads at all, but a problem with the system. I'll cut right to it: the problem is forgetting and aging. We can't forget. We never age. We're stuck. We never grow.''

Dear was nodding.

``Maybe some of you feel the wrongness in this, but I'm worried that it's too few of you. I called you here to teach you why this is a problem.'' Qoheleth ignored the indignant sounds from the audience and kept going, seemingly in a rhythm. "It feels good to be forever young, to be forever ourselves. But even if the physical and biological origins of aging have been obviated by the system, by being digital, the need to age and change is still there. It's a need backed by sanity and diversity rather and biology.

``Sanity drives the need because we can't forget. Maybe some of you have figured out ways to intentionally forget, but forgetting needs to be an organic process. It needs to be something that happens to us, not just something that we choose to do. All we can do is ignore, now, but even so, that just drives us further from sanity, over time. It's a limitation of the system applied to our sensoria, our minds.''

Qoheleth seemed to be gaining confidence, talking louder and more fluently as he went. ``Diversity, because we need to change more than just our shapes and our memories. All of us here, all of the Ode clade gathered today, are still essentially Michel Hadje. I don't see him here, and that's fine. His choice. But we're all still him. All hundred of us, all of our short-lived instances, all of our secret long-lived instances we didn't name after the Ode.''

Dear briefly splayed its ears, managed its embarrassed reaction, and then straightened up again. Ioan saw several others do the same, all of the more liberal bent. Ey smiled.

``It's not enough that we make nations out of individuals, we need to change beyond our root ancestors, if we're to survive. We need to breed, to produce more individuals. We can't keep relying on those who can afford to upload from offline for change. We need to forget at the very least,'' He pounded his fist against his palm with these last syllables. ``Or perhaps we need to learn how to die again.''

The silence was intent. Ioan made a note to eirself, \emph{Impressive. He has them hooked. All the way. Almost all of them except the conservatives.}

``That's why I posted The Name. That's why I gathered you here today. I'm telling you, we need to fix this, and I have some ideas as to how-''

Ioan missed the cue, if there was one, but with eir eyes locked on the stage, ey didn't miss the action.

At the mention of the name (and perhaps that was the only cue that was needed), Chunyu hoisted himself up on the stage, withdrew a syringe from his pocket, and slammed it into Qoheleth's back.

Then he quit.

Qoheleth had time to let out a soft ``hah,'' sounding bemused, and then began to artifact and jitter on the stage. The death lasted perhaps five seconds, as the old man's internals struggled against the intrusion of the virus, before he crashed, disappearing from sight much as the assassin had.

By the time Ioan looked around the room, the conservatives had left or quit.

Ruckus and uproar were too strong of words for what happened with the remaining audience. There were a few scattered shouts, mostly of surprise, but primarily just concerned murmurings. For its part, Dear stamped a foot and began to pace in the small space it had, tail lashing behind it.

``What just happened?'' Ioan whispered to the fox when it came close.

\emph{``One of the conservatives took a bet.''}

Ioan didn't press further.

\secdiv{}

\noindent I have them! I really, finally, truly have them all here!

I don't know that I have them all hooked, but I did it. I set my mind in motion by will alone. I count those who weren't hooked. Mostly first and second stanzas, mostly like me. How did they go so wrong, though? I'm a first-stanza instance. First stanza, second line, even, and I didn't turn out so bad.

Well, okay, I turned out kinda messed up, but only because I suffered the same fate that they all would, perhaps were already, only I suffered it a little bit earlier. I started going bonkers from the sheer amount of stuff in my head. I started living too long, living my Methuselah life while still having a mind like a steel trap. Nothing was getting out of my head. Nothing \emph{could} get out of my head. It just wasn't possible in the current system.

I have grand plans. Grand plans of organizing a petition among all the old clades, with the Ode clade leading and me leading them in turn. A petition to the system engineers to hire some damn developers again and stop treating this like abandonware that still runs. Get some devs in there and add the ability forget and the ability to die. Hell, maybe even the ability to breed. The word's even in my name, my old name, for chrissakes.

As I continue through my spiel, I can tell I'm hooking the liberals, the later stanzas, most of all. Dear's sold completely, I can see it on its face, fox or no. Can see it on Dear's other fox sib. Dear's whole stanza.

The conservatives are harder to read. The whole lot look blank and stoic. They just stand there, with their historians and their analyst --- the flash of his stylus as he scribbles notes in shorthand keeps distracting me. I power through, though, because it was working.

It's working, because I am Qoheleth. I am the teacher, I am leading the assemblage. I am instructing them in the dangers they face, telling them what's going on in forceful, no-nonsense terms.

And then I fuck up. I knew it as soon as I did it, too. I said something about The Name. I got too proud and started going into my whys. I shouldn't have done that at all. It'd lose me the conservatives. They, more than others, guarded that dumb name more jealously than all the rest.

I try to keep going to cover up my mistake, but there's that damn analyst, pulling himself up onto my stage. \emph{My} stage. It takes only a moment before I figure out what is going to happen, but by then it's too late.

The damn analyst's hand slaps into my back, and there's a sudden, searing pain. The only noise I can manage is a sort of strangled laugh at my own foolishness. My insides start to crumble.

Maybe I was Hebel after all. Vain, futile. Mere breath.

Havel havalim 'amar qoheleth, havel havalim, hakol havel.

Fuck. I was so close.

I'm glitching. Can see bits of myself spreading out.

So close.

Tunnel vision, blackness.

So close.

\secdiv{}

\noindent After the assassination, with no one to lead them and no reason to be there, the rest of the Odists and their friends left. Dear's pacing wound down, and it eventually stopped, shoulders sagging.

It paused, and then turned to Ioan, \emph{``Come on, let's go back.''} Then it turned and addressed some others near by, primarily from the same stanza, by the historian's guess. \emph{``Any of you are welcome, too.''}

It was Ioan, Dear, Serene, and Praiseworthy --- the first line of the stanza and down-tree instance from Dear --- who wound up back at the house. They entered the sim about twenty meters from the house, where Ioan had originally arrived, and trudged slowly up to the house.

Dear's partner greeted them at the door, silent. Perhaps Dear had sent ahead a message, for the individual mostly stayed out of the way of the four. They disappeared and returned shortly with mugs of coffee.

The four witnesses slumped into the couch, Dear and Serene leaning against each other, and Dear's partner settled on a stolen dining-room chair before them all.

``So,'' they said, finally. ``What happened?''

\emph{``One of the conservatives played their hand. He brought along an assassin, and as soon as Qoheleth revealed his reasoning for revealing The Name, the assassin acted and then quit. My guess is that Qoheleth hadn't forked and won't be heard from again, and that Chunyu, the assassin, was a fork who will `mysteriously' experience some problems merging back. No culpability for its \#tasker or \#tracker instance.''}

``Ah\ldots{}''

Silence fell on the group again.

Ioan waited for one of those ebbs in the rhythm of the silence before clearing eir throat. ``Perhaps it's too soon, but may I ask after everyone's well being? Their thoughts on the matter?''

Serene shook her head. Praiseworthy offered, ``I'm not surprised, really. Not happy, but not surprised.''

Ioan turned to Dear. ``You alright?''

It was a moment in responding, before it nodded. \emph{``I'm with Praiseworthy. I'm not surprised, but not happy. Kinda pissed, actually,''} it said, smiling sardonically. \emph{``That was short-sighted of them, though, because I have a hunch that Qoheleth was right.''}

``Right?''

\emph{``About the need to age, to die. About forgetting.''}

``Does this have anything to do with you trying to forget The Name?''

Dear shot a grin at its partner, \emph{``You two get along, I see. Yeah, it does. I think I did it, too, unless there's some association I missed. Can't remember it for the life of me.''}

``You'll have to tell me how you did that, sib,'' Serene laughed.

\emph{``Later, yeah. I think Qoheleth was right, though. We need forgetting. We need breeding and change and death.''}

``So how do you feel about the assassination?'' Ioan asked.

\emph{``I'd prefer that not be the only means of death, of course. Perhaps the primary way should be through\ldots{}ah, suicide is not the best word, but it's what I mean. Through choice, just like Qoheleth's old name.''}

Life breeds life, but death must now be chosen.

Ioan nodded.

\emph{``It's like I said. Batty. They're all batty.''} It stared at its paws, one of them brushing through its sib's forearm fur. \emph{``It's like some sort of Methuselah syndrome, or reverse Alzheimer's. Instead of being doomed for forget, we're doomed to remember. Doomed to remember everything. We can't forget, and it all gets to be too much for one mind.''}

``What about exos?''

\emph{``Exocortices are a fix, but an iffy one. You're still stuck with the knowledge that they exist, and their inventory. That's why I can't forget \textbf{that} The Name exists, or that there's an exo containing it which I can't access. Not unless I go through the whole shitty process again --- sorry, Serene, it wasn't pleasant --- with that bit of knowledge, and then what? I'll have the knowledge that I have an exo that I can't access pointing to something of dire importance.''}

Ioan shifted, leaning forward to rest eir elbows on eir knees, eir chin in eir hand. Ey sipped eir coffee as ey thought.

Serene piped up next, ``I get what you're saying, Dear, but I don't want to die. I don't want you to die, either.''

Dear's partner, frowned. ``Neither do I, fox.''

The fennec laughed and shook its head, ears flopping about. \emph{``Trust me, I don't either. I don't think many people do. I just think we need death, or something like it, as part of the system.''}

``Something like it?'' asked Praiseworthy.

\emph{``We need a way for an individual to end. We also need a way to create new individuals. Qoheleth called it breeding, but it could just as easily be a way of ending one individual and having them live on as another.''}

The others nodded. Silence once more.

Finally, Dear gave a lopsided smile, \emph{``Perhaps that's my next project.''}

\secdiv{}

\noindent Ioan Balan\#tracker chose a blithe-theirs merge strategy in this particular instance, when Ioan\#c1494bf finished the project and quit. They chose together, actually. \#c1494bf requested it, and \#tracker agreed.

There was one more sensorium chat after that, between Ioan\#tracker and Dear, Also, The Tree That Was Felled. Ioan thanked Dear profusely for the opportunity and experience. Dear cried and made Ioan promise to come back --- \emph{``your wall will miss you''} --- to which Ioan readily agreed.

Ey would, ey was sure, but for now, ey needed a bit of distance to sit and think and remember and write. Maybe not remember --- ey couldn't forget. To mix the thoughts around. To understand.

Ey moved out to eir favorite Adirondack chair on the deck with pen and paper. Ey spent a moment thinking back on Dear and Qoheleth, another moment savoring the heft of the pen and the texture of the paper, and then began to write.
