\chapter*{RJ — 2112}

The theater purred. It hummed to itself. It stretched and reclined. It relaxed, unwound.

RJ and the room let out a soft, long-held breath together, feeling muscles and wires relax, nerves and current disentangle themselves, slowly, slowly.

``Alright, everyone. It's midnight, time to start packing up,'' Johansson was saying from down in the front row. ``Ross, we're short one. Can you start pulling together all of the mics? RJ will help you get them sorted.''

``Mm,'' RJ offered through the sound system. Ey was busy putting the theater to bed, and couldn't spare more than a meager few syllables to the rest of the cast and crew. ``Get a headset, Ross, so I don't have to talk through the speakers.''

Those speakers were signing off, going to bed one by one through RJ's gentle attentions. The virtual board set about the task of returning to neutral, all of the gain knobs orienting themselves, then all of the monitor knobs, the sliders, the whole system ticking as it cooled down, minus the channel ey'd need to keep open to Ross.

``Hey boss, got a headset. Where do you want me to start?''

``Grab the lead, first,'' RJ murmured. ``Then Sarah and Catherine, they've got the nice mics. They should have a tiny number painted on the costume side that matches up with their box. All of the boxes are stacked in the pit, by the front wall, you should be able to get them out in one load, though be careful taking them back.''

``Got it, heading down to the pit now.''

RJ left the channel open just in case, though the soft sounds of breathing and the occasional curse as Ross bumped his head on the pit cover were distracting, while ey set about going through eir notes with the dozy theater. The next night's rehearsal was the last one before they went live.

Ey knew the show better than most of the cast, em and the theater. The two had to learn everyone's lines, plus a few cues when ey'd have to take care not to pick up any of the sound effects. Gun-shots. Chairs scraping. A scuffle. The clap of heels on the matte black of the stage itself.

The theater's job was to simply work with RJ and the lighting crew, responding to their knowledge of what was going on in the play, while RJ and Caitlin's job, as sound and lights, was to respond to the stage manager's near encyclopedic knowledge of the play, her view of the house.

All sound was under RJ's jurisdiction. Cast and crew both: ey spent as much time managing communication between the hands, the manager, and emself and Caitlin as ey did maintaining the sound from the performers.

They were all as ghosts in this. Even the theater. Their job was one that should be totally invisible to the audience, because it would only become visible if they fucked up. No one wanted to fuck up. Even the theater seemed to feel a sense of pride in doing its job and doing it well.

RJ soothed the room with a gentle cooing and reluctantly started the process of pulling back. Ey closed the channel with Ross and put all of the headsets to bed last of all, before ey slipped back from the interface, blinking as ey adjusted to seeing the cavernous hall with eir own eyes as eir fingers slipped from the contact points and ey leaned back from the headrest.

Ey shook eir head to clear it and stood up, stretching, before ambling from the tech booth down the stairs towards the stage. Letting gravity carry eir lanky form down two steps at a time, feeling air against eir face, smelling the treble note of dust and conditioned air all added to the newborn feeling of pulling back.

Ross was down there standing still and staring at the floor, muttering agitated questions into the headset.

``Hey bud, I'm here. The house is sleeping now.''

Ross jumped, then looked embarrassed as he tugged the headset off his head. ``Sorry, was wondering where you'd gone. I just heard a beep.''

``Yep, signing off from above. Did you get all the mics gathered up?''

``Oh! Yeah, that's what I was trying to tell you. I wasn't sure what to do next.''

It only took a few minutes for RJ and Ross to get the last of the sound gear settled, gathering the headsets from all of the hands and socketing them into numbered chargers against the wall. Everything would sleep tight until the next night on sound's end.

Caitlin and Sarai, the stage manager, joined them and the rest of the hands. They sat on the edge of the pit cover, unwinding from the tenseness of rehearsal. The actors slowly got out of their dress to clump together on the stage, unwilling to leave their beloved platform just yet.

``Gather 'round, children'', a voice boomed from out in the darkened audience.

``Yes, Mister Johansson'', one of the actors recited back. Tired laughter.

``Good job, I think we're nearly there. Still, we need a bit more polish. No flubbed lines, and mostly relaxed, but Sarah, you gotta loosen up. It's not Shakespeare, you can chill out. Crew, you guys got a little sluggish toward the end. I know it's late, but so are our shows. Don't work yourselves too hard, but keep on top of things, okay?''

RJ, Sarai, and Caitlin murmured their assent.

``Tomorow night, back here at five.''

``Early,'' RJ murmured. ``How come?''

Johansson grinned wryly. ``There's a school production that winds up around then and I want you all back here to make sure we still have a theater.''

There was a bit more grumbling, but RJ knew they'd be there on time --- it wasn't too much of a stretch.

``Back to base, then. Get some rest tonight, and I'll catch you all tomorrow. Remember, you can drink tonight, but tomorrow night, \emph{Das is streng verboten}.''

The company laughed and started to disperse, the tech leads lingering on the pit cover for a little while longer as they worked on reorienting themselves to the real world. A world limited by two eyes, two ears, two hands.

Eventually, RJ made eir way out onto the chill of the street, pulling eir thin waterproof gloves on to keep the contacts on the middle joints of eir fingers clean and dry.

At midnight on a weekday, there wasn't too much going on. Folks visiting the pubs to catch up with their friends after work. Black cabs, night busses. By the time that midnight rolled around, those who were left were the harder drinkers.

The idea of a warm pub and one quick pint before heading home tugged at em, but the pull of home was much stronger than that of beer.

Ey trudged instead up to the northwest corner of Soho to Oxford Circus. Central line up to Benthal Green, walk the few blocks from there to eir flat. Stopped to pick up a take-away carton of curry and rice from one of the more trustworthy shops along the way.

Once home, ey slipped out of eir jacket and welcomed the warmth of eir little flat after the damp chill of London outside. Eir cat trotted up to em, twining around eir ankles. A little ginger thing of a few years that ey had rescued from a friend who was moving deeper into the city, she was the only one to share eir space with em after eir last flatmate had left for somewhere cheaper.

``Hey Prisca, let me put my shit down before I get you food.''

A meow followed em to the kitchen, where ey set eir take-away on the counter and scooped a cup of dry food into a fresh dish, setting it on the tile for the delicate cat.

Ey thumbed eir phone with the contacts on the thumb-pads of eir glove to start music playing. Some of the stuff that reminded em of eir dad to go along with the curry that reminded em of eir mom. Quiet, but present.

Dinner was no more or less exciting than usual. RJ ate alone at the kitchen table with the carton spread out before em, baring orange curry and the soggy samosa that had come with it. Ey left eir gloves on just to be sure --- no sense in having to clean eir contacts more than ey'd already need to after a long rehearsal.

Ey scooped the last of the curry into a little plastic container for the next day's lunch, promising emself that ey'd cook an additional pot of rice before heading out in the afternoon so ey'd have more calories to keep emself running. Clean up as easy as tossing the container into the compost bin along with all of the others. Cooking much more than rice was for times other than crunch.

The rig in the corner of eir bedroom was exerting subtle gravities on RJ. As ey ran through the motions of the post-recital evening --- eating, cleaning, storing leftovers, using the toilet --- eir orbits grew smaller and smaller. Eir gloves were itching. Ey could feel phantom breezes brushing past phantom fur. Phantom fur. Phantom ears. Phantom tail. Phantom realities teased around the edges of eir perception.

Ey finally allowed emelf to sit down at eir rig, relaxing into the familiar curves of the chair. Even with the draw so close to em, ey took eir time. Ey picked up Priscilla and stroked her smoothly from ears to tail a few times until she started purring up a storm, informing her that, in fact, she was the prettiest kitty.

\emph{Peel your gloves off one finger at a time,} ey thought. \emph{Relish the anticipation. Get caught up in it. Hell, let it linger.}

Cat settled into eir lap and curled into a small crescent, ey set about cleaning the contacts on eir hands with lint-free paper and rubbing alcohol. Those done, ey wiped down the headset, removing the negligible residue of sweat and skin oils that had collected there. Clean enough as is. Ey had recently replaced the soft, padded headrest where eir forehead would lay, held inches from the minuscule cameras that tracked eir face.

Eir gear was more elaborate than the stuff in the tech booth at work ey shared with Sarai and Caitlin, and ey had drained eir savings to acquire it. The rig, as well as the contacts on eir fingers, the nanoscale interferites --- the ones that took over eir optic and auditory nerves, and the electroparalytics to keep em from acting out in reality what took place online --- the NFC connections implanted just under eir hairline and their ramifying tendrils, all of that painful work down eir spine that helped em more fully experience the connection.

Connections and gear cleaned, RJ finally felt at ease enough to pop open the lid on eir rig. The screen, all but vestigial when ey was inside, still served its role during boot and login.

Ey quickly keyed in eir passphrase and then rested eir right hand on the curved pad, eir fingers finding familiar grooves that held eir hand in place. The connection from eir contacts the other half of eir two factors of authentication.

``Gonna head in, Prisca,'' ey murmured to eir cat, stroking the fingers of eir left hand over her ears, fingering the soft, velveteen folds until the cat shook her head away. Purrs nonetheless ratcheted up a notch. ``I'll be back in a bit.''

Ey set eir left hand into its cradle. Tilting eir head against the headrest, feeling the comforting touch of cool microfiber and the little twinge of recognition from the NFC controllers, ey nudged the button beneath eir thumb.

The rig went immersive. As RJ delved in, the soft hum of a cooling fan picked up to handle the waste heat of countless computations.

Ey could no longer hear it.

%%%%%
\chapter*{AwDae — 2112}

AwDae sat up in bed and slid to the edge of the mattress. Ey stretched languidly and let eir fur bristle from tip to tail, the latter bottle-brushing out. Ey shook emself to settle eir fur back down and yawned widely, slender pink tongue curling just shy of sharp incisors. A formality, to be sure, or perhaps a wordless mnemonic to finish the context-shift. The final step in a ritual.

Brushing eir fur down, ey stood and padded to the dresser in the corner of the room, pulling out a thin white cotton shirt with laces up the front and a simple navy sarong, which ey tied around eir waist. Countless hours examining some of the highest fashions out there on the 'net, and ey'd come to the conclusion that, in these times of excess, the understated said the most. It also interfered with the fur least, worked well with a tail --- a simple slit cut down the length of the sarong let that slip free --- and it was cheap. There was no shortage of ways to spend money, and AwDae had better things to buy with what was left after London rent.

Ey swiped eir paw from left to right atop the dresser, revealing a dimly glowing arsenal of personal belongings. It'd be a simple night out, so ey tucked a few vcards and a limited credit chip into a shoulder bag and hauled the strap over eir head, ears laying flat and out of the way.

From there, eir claws clacked against the glossy surface of the tport pad. Gauche as it was to appear and disappear where folks could see, ey kept eirs in a corner of the studio apartment rather than an alcove. The feeling of exposure and the jarring change of scenery was titillating, racy.

Ey stood straight on the pad and brushed eir paw from left to right, bringing up a list of recently used commands. Had ey left fingerprints online, there'd be a clear smudge over the entry: ey rarely did anything else on work nights.

\texttt{tport:\ The\ Crown\ Pub}

Tapped, and the obligatory click that went along with the change of scenery brought em to an alcove paneled in oak, lit by green-shaded lights hanging pendulously from a cord directly above em.

Ey blinked to adjust to the comparatively dim light. The pub, which largely followed the circadian rhythm of the British isles, was just as dark as it was for RJ, back in London-as-it-was, but eir perosnal sim lived in a perpetual eleven AM springtime.

Ey turned and stepped away from the pad, narrowly avoiding a slender weasel stumbling towards the alcove.

``See ya, Debarre,'' AwDae said, though it came out more like `Shee-a, Debaw' coming from the fox's narrow muzzle. Ey got a curt wave from the weasel done up all in black.

The fox shrugged and headed into the pub proper, eir nose twitching. The scents of the room which told em more of those present than simply scanning the crowd. One or two gawking entities with no scent property set --- tourists --- and the usual crowd of aromas. Friends, mostly. Acquaintances all, minus those tourists.

Ears perked at the distinct whiff of dandelions, something leftover from eir youth, and ey made a beeline towards one of the window tables, where the scent seemed to originate, skirting around bodies of diverse shape.

``Shacha.''

``Come on, fox, loosen your filters, won't you?'' Sasha laughed, scooting her chair back to stand up and lean in for a quick hug. AwDae slipped eir arms around the skunk's waist in turn and gave a squeeze, tail aswish.

``Lame,'' ey drawled, but dialed back the output filters on eir speech, letting something more closely resembling English pass. ``How you been, skunk?''

``Oh, you know, same old, same old.'' Sasha settled back into her chair and fiddled with a stack of vcards on the table, giving an outsized shrug. ``Been kind of boring in here over the last few days, so it's good to see you.''

The fox nodded, tugging eir shirt straight and moving over to the chair opposite the skunk, sliding into it easily and resting against the back.

``It's late there, isn't it?''

``Not too late. One something. Made good time home at least. Rehearsal ran late.''

Sasha laughed, ``You know, every time you talk about rehearsal and such, I think back to school. You hunched over the sound booth, you know? It's hard for me to picture you as having grown up and taken that up as a job.''

AwDae adopted a look of mock-despair. ``Is it? I went to uni just for it and everything. But hey, London ain't bad, I can't complain any.''

The skunk rolled her eyes and leaned forward onto her elbows, muzzle resting on obsidian paws. ``Tell me about it. You're missing out big time here in the 'burbs, dear. You could be teaching high school theater in any town along the central corridor, doing the same plays once every five years so no students repeat them. Truly a life of glamour.'' Sasha laughed as AwDae buried eir face in eir own paws with a groan. She continued, ``Seriously though, you just remind me a lot of school. Maybe it's 'cause of all of the ways you haven't grown up.''

``Please, Sasha.'' AwDae poked eir tongue out. ``If you bring up dating\ldots{}''

``Hey, sorry, just looking out for you, fox.''

``I'm plenty happy on my own, I can promise you that,'' ey countered.

``No, I get that,'' Sasha admitted, lowering her gaze. ``Not all it's turned out to be. Just got me thinking, is all.''

``Oh no, struck out again?''

Sasha shrugged, nodded, shrugged once more, fiddled with a vcard. Still no eye contact.

AwDae reached eir paws out to take one of her own, black fur on black fur nonetheless mismatched. Both had opted for mostly hand-like paws, but differences were evident on contact. Where Sasha's fur was an even, silky black marked by white stripes that were a little too sharp, a little too exact, AwDae had labored to construct a version of emself as a cross fox to exacting detail, down to the point where eir muzzle couldn't even form the two letters that made up eir name offline.

It brought to mind thoughts of honing versus forging. AwDae had honed emself to a finer and finder point while everyone else forged ahead. Always a way to be a better tech. Always a chance to become more vulpine online. Always a way to become better at what one already was.

Ey shook eir head to dislodge the rumination.

``I'm sorry, Sasha\ldots{}''

Sasha shrugged again, as though she might be able to drop the very idea of bad break-ups like an overloaded backpack. She gave the fox's paws a squeeze in her own. ``Men are dicks. I'd take a fox like you over any dickhead guy any day.''

AwDae smiled faintly, returned the squeeze. ``Sasha, you know it wouldn't--''

``No, I know. I just wish there were more guys out there like you.'' When AwDae stiffened in eir seat and looked away towards the window, Sasha splayed her ears and added quickly, ``Sorry fox. I keep putting my foot in it, don't I?''

``Sorry, no, you're fine.'' AwDae grinned apologetically. ``I should get a thicker skin, maybe. Stand up for myself. I spend night after night hiding in here, and even then, can't really assert myself any. I appreciate you trying, though.''

Sasha smiled cautiously and nodded. ``You came out like ten years ago, dear. I should still be doing better.''

AwDae's turn to shrug. ``It's hard to ask for that is all. Always has been.''

``I think that's what I meant earlier, that you haven't changed, despite all the ways you have. You haven't done like all the rest of us and grown up, gotten married, all that crap. You're still doing what you loved to do in school. You seem kind of frozen, kind of stuck --- in a few ways, even, though you're succeeding in others.''

AwDae nodded, rumination hanging in a cloud around em. So many ways the world had moved on without em\ldots{} After a moment, though, ey sat up straighter. ``Oh, speaking of frozen.''

``Debarre?''

The fox nodded.

``No news, yet. He's been trying to get in touch with the center that's taking care of Cicero, but the family's been getting in the way. They're fielding everything. They always sort of supported the relationship on the surface, you know, but never actually approved of it. Of them being together, I mean.''

``What? Really?'' The fox shook eir head, poking a claw at the table, before rubbing the spot with a paw pad. The sim was hardly immersive enough to waste cycles on letting claw dent tabletop. ``That's unfortunate. Not all that surprising, I guess, given what Cice said about his family. They at least confirmed that's what happened, though?''

``That's what these are,'' Sasha said, slipping the stack of vcards over to em. ``There's contact info for the family, and a few centers around there that work on implants, some hospitals. We're thinking that those might be the types of places where he wound up. There's also a card detailing his \texttt{laston} information.''

AwDae twisted the stack of cards around in front of em, leafing through slowly and taking in a few of the details that slid across eir fingertips. ``Mind if I make a copy?''

``Go ahead. It's a deck Debarre and I have been working on. Not complete, but I'll give you ACLs.''

``Mm. Debarre looked crushed. Is he doing alright?''

Sasha hesitated for a moment, caught in the middle of a gesture to grant copy rights on the cards. She shook her head, to which AwDae could only frown. She finished the gesture, and another set of vcards shuffled itself out from the original stack. Crisp black embossed on the creamy cotton-paper that AwDae preferred.

``I'll take a look, too. I can't do too much right now, I've got a--''

``I know, you've got a show coming up,'' Sasha laughed. ``Don't worry about it, dear. Debarre's working on it, I'm taking a look when I can, and I'm sure the weasel's got others helping him out besides us. No reason not to, either. We all liked Cicero.''

The two sat in silence. AwDae slid Sasha's cards back and fanned eirs in front of emself before shuffling them back into a stack and swiping above them, instructing eir rig to make a copy of the deck.

Ey lifted eir gaze away from the silence to scan the scents in the room once more. Now that it was starting to get on in the evening even in the Americas, the scentscape was changing. Some familiar scents, some unfamiliar, but most of them at least detailed, which told AwDae that the owners had put some thought into them. None, however, really jumped out at em.

More rumination. Rumination edging into drowsiness.

``Hey, Sasha, I gotta get going. I know I just got here, but I'm starting to crash hard.''

The skunk nodded and gave a little flick of her tail. ``No, it's alright. It's late there, and I know you've been in rehearsals for a while. Go get some sleep.''

Both stood up and exchanged another hug, AwDae breathing in that dandelion scent of eir friend. Memories of school, drowsy, dreamlike. Dandelions in the lawn. An impromptu picnic. Rubbing one of the flowers on the back of eir hand, leaving a yellow stain. Sasha explaining that the smell always reminded her of muffins.

``I'll see you later, skunk, yeah?''

``Take care of yourself, okay? No working too hard, slaving over a hot rig\ldots{}''

AwDae laughed and shook eir head. Ey gave the skunk one last squeeze before making eir way back through the crowd toward the alcove, already swiping eir command palette into view to head home.

%%%%%
\chapter*{Ioan — 2305}

Ioan Balan awoke to an urgent message.

Ey didn't really like these, the sensorium messages. Ey liked paper messages. Ey mostly just liked paper. Ey was always accruing more. Paper and pens. Eir friends thought it creepy. Paper messages, or those rich messages that came attached to paper, played on its surface, or even messed with eir sensorium. To have one that just barged in on eir vision and endocrine system like this made em quite anxious. This one included a tiny jolt of adrenaline as an alert. Waking up with that jolt to have a partial sensory takeover just felt rude.

The benefit was that ey didn't have to get out of bed to deal with it.

The opacity on the message was turned up quite high, so that even in eir dark room, with eir eyes closed (and heart still pounding), ey could see the fox. A bipedal fox dressed quite sharply. It was sitting on a fairly plain wooden chair, situated in an empty room. The room had wood floors the same color as the chair, some very light wood, like hickory or pine. The walls were concrete where they weren't glass. Outside the glass was a sere shortgrass prairie, a cloudy day.

The combination of the fox's white fur, glistening and iridescent, combined with the room and landscape was all painfully pomo. Ey didn't consider eirself much of a pomophobe, but this was\ldots{}intense.

\emph{``Hi Mx Balan,''} the fox was saying. \emph{``I have a proposition for you.''}

Ioan grunted. The message was recorded, thank goodness. No interaction

\emph{``My name is Dear, Also, The Tree Was Felled, or just Dear, and I'm a member of the Ode clade. I'm an artist-''} Ioan rolled eir eyes. Ey could tell it didn't like the word. \emph{``-and performer. I'm not just telling you this to, ah, toot my own horn, I believe the phrase is, but just to underline the fact that I'm woefully unprepared for the situation at hand.''}

The fox smiled, looking tired. \emph{``I need some help finding someone,''} it continued. \emph{``Someone that doesn't want to be found. It's personally important, but also potentially damaging to the image of our entire clade.''}

Ioan furrowed eir brow.

\emph{``The person has information, a name, that ey have supposedly shared. We --- the other members of my clade and I --- don't precisely know if they actually did, unfortunately, we just have word from others close to the clade that someone knew and said The Name.''}

The fox shook it's head, ears flopping from side to side. \emph{``I'm sorry, I'm getting sidetracked by details. I try to be prepared for conversations and messages like this, but I'm a little worked up, excited, I guess. Can we meet?''} It listed some coordinates. \emph{``Even if only to talk. Even if you're not interested, I'd still like to meet you. You seem neat.''}

The message ended.

Ioan lay in bed, thinking. It was still about an hour before ey had to get up, and ey was loath to start the day before ey had to. Ey tried eir best to sleep for another ten minutes, at least, but eir mind kept slipping back to Dear's request.

\emph{Why me?} ey asked the backs of eir closed eyelids. \emph{Why hire a writer who fancied eirself a historian as a PI?}

With still a half hour to go before ey had to be up, Ioan slipped out of bed, stood, and stretched. The least ey could do was get a shower and some coffee. If there were any reason that the founders of the system had included sensoria in the works it must have been for those.

Those done and clothes donned --- ey knew ey could never out-natty the fox, so the usual faux-academia garb it was --- ey penned Dear a short note with a time. If it was day in that sim, or even late afternoon, it should get the note before dinner or bed.

\emph{Besides,} ey thought. \emph{Maybe it will get the fox to start sending notes this way in the future.}

No luck. Less than thirty seconds later, Ioan received a sensorium ping of acknowledgement, and a shiver up eir spine to go along with it.

Ey forked and sent \#c1494bf out to the meeting. Meanwhile, ey'd get some food.

%%%%%
\chapter*{RJ — 2112}

RJ slid eir hands from the pads and leaned back from the headrest, letting out a full-fledged yawn. The sound and motion startled Priscilla across the room. Ey levered emself up out of eir seat and trudged over toward the still-purring cat, stroking over her ears when she bunted her head up against eir hand

Eir mind foundered in a slurry of work, of Cicero's disappearance, of school with Sasha, of honing versus forging.

``I'm wiped, Prisca,'' ey informed the cat.

Priscilla purred louder.

Smiling, ey peeled eir shirt off over eir head and slipped out of eir jeans. Tomorrow's rehearsal would mean full dress for everyone and makeup for the actors. Ey'd have to make sure eir suit was clean. Should ey iron it? Maybe ey should iron it. Later. For now, as it neared two, ey focused on making sure the door was locked and the lights were out before stumbling over to bed.

Ey flipped the screen down on eir rig to signal for it to go to sleep and wandered over to eir bed. There seemed to be no shaking Sasha and all of her talk of high school, gone these last eight years now, out of eir head. Even as ey climbed into eir narrow bed and burrowed beneath the covers against the chill of the night, ey was replaying memories from school. Scenes from the US. A worn out film, dim and scattershot.

Honing and forging, honing and forging.

Ey and Sasha had tried dating early on. After a few weeks of it not going anywhere, they had both admitted that they had felt pressured into having a relationship, rather than actually wanting one. Good boys and girls fell in love with other good boys and girls, right? Pretended they didn't have sex. Went out to the movies.

The relationship petered out, rather than ending in some climactic fashion. They had continued the trend of going to movies, and later to live performances. They had never lost touch, at least.

Sasha had gone on to have a string of other relationships, some earnest and some not, some more intense than others --- a string that remained unbroken, if tonight's conversation was any clue --- but RJ had stopped there.

The intensity social pressure to date throughout high school was equaled only by RJ's total apathy toward the whole scene. Apathy or, often, antipathy. Ey'd felt the occasional twinge of romantic attraction, perhaps, but the expectation of sex that went along with the process so put em off that ey had instead buried emself in work.

Ey did well in some courses and not in others, but in the subjects that ey enjoyed, ey dumped all of eir effort. Huge gusts of energy that drove em forward.

Ey had started early on in working the school's older sound board in the theater Ey ran plays. Ey ran concerts. Ey ran assemblies and lectures and conferences, quickly earning the trust of the other tech crew and the staff and faculty. And then ey gained leadership. Prestige.

The various computer classes had captivated em as well, and for eir sixteenth birthday, eir parents had surprised em with the implants needed for full interfacing with a rig. Or, well, ``surprised'': eir father was an engineer and eir mother a fairly forward-thinking person, and they had promised em the procedure before university.

Honing and forging, honing and forging.

It was a straightforward procedure in an outpatient office, self-guided implants largely installing themselves. The worst had been the itching. It was bearable on eir hands and along eir spine, where the implants and exocortex breached the surface of eir skin, because at least ey could scratch, though ey had been cautioned not to. The NFC pads in eir forehead and the interferites embedded deeper --- far, far deeper --- led to an itch that no scratching would ever reach.

From there, sound and the interface had taken up all of eir energy, leaving little time to worry about any social stigma that went along with an aversion to romance. Ey was simply the nerdy sound kid who knew more about computers than the teachers.

It hadn't always been fun, of course, but by the ey quickly learned that the more ey put into the task, the more ey got out of it.

That ey had found furry in high school seemed almost a natural progression. Working and improving at the art of interfacing in a way that felt natural to em came just as natural to others on the 'net. Ey moved effortlessly through the Crown Pub and a few other choice spaces, slowly crafting the primary persona that ey used when interacting with others, the cross fox known as AwDae.

It was then that ey and Sasha had really started connecting, for it was her that introduced em to the community. They started hanging out more, talking more, building a network of friends together. Where dating hadn't worked out for them, friendship grew in depth and breadth.

Honing and forging, honing and forging.

The forging of the virtual theater environment had culminated in a scholarship at a big name university out on the east coast. Immersive interactive theater technology. Forging into honing.

It meant leaving Sasha and a few other close friends behind along with eir family, but it also meant that ey would be at the forefront of a new tech. Something used in production. Films and live work, too.

The field had been so new that eir own studies at the university helped fuel the change in theater tech work. Eir dissertation, what was meant to be eir capstone project, was published and spread. Theaters around the world were using immersive tech.

Ey had continued to work at the university for a while. It was one of the few places around with both a theater and the hardware to back it up. Ey had considered continuing eir studies, but the draw of the theater was too heady, too alluring. Academia spelled a life of forging, work one of honing. Why deny one's base nature?

Honing and forging, honing and forging.

The call from London came less than a year after ey graduated. Would ey like to help start a tech-savvy theater group in town? The pay would be slow to start, but the troupe had a loose collection of apartments on the East End. Ey would have full run of the sound department. When could ey start?

Eir parents had needed convincing. They were pleased, to be sure, but they London, so far away! Still in the western bloc, but so far.

Ey made eir promises that ey'd come and visit every year, and packed eir bags.

Burying emself deeper into the covers and the mattress, leaving enough room for Priscilla to join em later, RJ's thoughts alighted on Cicero, on the lost.

Losing Cicero had been a shock. A disappearance, at first, and then it went on. Debarre hollering one night after getting in touch with Cice's family. Lost, lost, he was lost.

Getting lost was rare. Vanishingly so, even, with perhaps two dozen cases. Still, among those who were counted among the lost, all were heavy interfacers. It was a risk, everyone had assumed, just as was travel. Call it occupational hazard. Something could always happen. Something could always go wrong.

To lose someone so close, though, hit hard.

It was a reminder of just how much ey relied on the integration tech, not only for work, but for a large part of eir social life. Ey enjoyed the company of the troupe just fine. Troupe pub trips were a weekly affair, but eir heart lay among eir friends on the 'net. Eir friends being on the 'net meant more interfacing, and more interfacing meant more risk.

Eir tech was truly immersive, after all. It was a dissolution of the body. Disembodied in the truest sense.

It was becoming the room. It was a new sensory experience. No limbs, no torso, no face or eyes or ears. Or maybe all ears: ey became the room, feeling the way sound echoed or didn't, knowing the limits of the speakers in a deeply physical way. Mics peppering the walls a new sensory input. The wires nerves. The speakers muscles to flex. Instincts, reactions, and actions responding to whole systems of stimuli.

Perhaps that was why ey felt so at risk. They all were, of course, but to dissolve one's concept of a body at work, and then come home to warp the very same concept into that of a fox --- no, a finely wrought amalgam of fox and self --- felt perilously close to being lost, sometimes.

Honing and forging, honing and forging. Risk and reward.

Ey slept.

%%%%%
\chapter*{Carter — 2112}

Carter rubbed her face into her hands, ground her palms against her eyes until she saw stars, slicked her hair back in a vain attempt to wrangle fly-away hair. It had been in a neat bun this morning.

She wasn't the last one left in the lab, but it had reached that point of the night where collaboration had stopped and everyone was butting their head against their own individual problems, toiling in silence. She folded her rig's screen down, sending it to sleep, socketing her tablet in next to it to charge.

It had also clearly reached the point of the night where she wouldn't be getting anything else done.

She felt out of her league. Everyone did, here on her team, but that didn't stop the fact from wearing on her. It's not that there wasn't any support from on high. There was. It's not that there wasn't anyone else trying. There definitely was.

It's that no one seemed to take it all that seriously. It was like addiction, or plane crashes, or suicide. Something to look at, to study long enough to say ``Ah, \emph{this} is happening now,'' and then set aside. Conversation-piece science.

People admitted that the phenomenon was there, but only in as much as it didn't affect that many people. A simple number to point to. See how small?

It was as though the brains of the Lost were just\ldots{}elsewhere. Just dreaming on some level. There was no sense to it, though. No rhyme or reason to why such a thing would happen to the patient. Some of her team were pulling together all of the facts about the population that they could, from demographics to physical stature, searching for clues in the rig and the 'net itself. The neuroscientists were digging into what was going on within the brain, and what few scans they had from before someone had gotten lost. Their two pet lawyers --- just law students on internship, both also versed in stats --- were digging into the legal status of the lost as well as writing queries to procure patient medical histories.

And Carter was supposed to tie it together.

Or, that was her stated goal. The university medical center had only grudgingly provided space and funding for the project. An attempt to win some much-needed kudos, she suspected. Still, she was beginning to doubt just how much the UMC wanted her to succeed.

There had been an initial dataset dumped on her team, and a slow trickle as new cases came in, but it all felt so carefully curated. As manager, she had been met with hurdle after hurdle as soon as she started to venture beyond that. Colleagues assured her that all projects worked this way, but it was as though the advisory board had given her all the data that it was willing to give, and any more might\ldots{}what? Put those kudos at risk?

Carter stood, stretched her back, winced. ``Sorry, Sanders. I'm shattered. Catch you in the morning?''

``Mm,'' he replied. The interruption seemed to him of his physicality. He rubbed at his eyes and stretched his arms out, alternating between clenching his long fingers into fists and flexing them out wide. ``Sounds good, Ramirez. Catch you then.''

Carter gathered up her coat and her messenger bag, taking one last look around the lab, counting heads to see who would be staying later than her. Not too many. Sanders, one or two of his neuroscientists.

She swiped her way out of the wing and signed out at the front desk before making her way out into the night, bundling up in her coat.

At home, she scavenged a few pieces of salami stacked onto a couple of crackers, enough to keep her empty stomach from complaining through the night, and crumpled onto the couch in the shared living room. She left the lights off so that she wouldn't bother her flatmates. Or so she told herself. In truth, the darkness felt good. She could keep her eyes open and not be greeted with a tablet, a screen, a sim.

She sat long after finishing her snack, listening to her flatmates sleep, the sounds of the road outside, her own breathing. Sat, thinking in the dark of all the administrivia on tomorrow's docket.

Eventually, finding herself at as much of a dead end as she had at work, Carter ambled off to her room, changed from her work clothes into a comfortable pair of lounge pants and a night shirt, and crawled into bed.

%%%%%
\chapter*{Ioan — 2305}

\noindent Ioan\#c1494bf found emself about twenty meters in front of the squat house. It was just as postmodern on the outside as it had appeared on the inside: a concrete block, a thick wrap-around patio covered by cantilevered eaves, floor to ceiling glass for walls. Ey wouldn't be surprised if the far side of the buiding --- ey couldn't see it very well, with the slope of the shortgrass-prairie it was on --- jutted out at some crazy angle.

Smiling ruefully, ey walked up toward the house.

A soft tone, a vibraphone struck with a soft mallet, sounded inside and outside of the house as soon as ey'd passed the barrier between grass and patio. Ey stood on the patio, waiting to be either admitted or greeted.

A shadow of a person, human, peeked out through the glass at em, gave a pleasant wave, and hollered through the glass, ``Ioan! Hi! I'll grab Dear.''

Before the person could do so, Dear came padding softly from around the side of the house, looking slightly more collected than it had during the message.

\emph{``Ioan,''} it said, smiling and offering a paw in greeting. Ioan wasn't sure how ey knew when a fox was smiling, but it was definitely a smile. \emph{``Thank you for coming on such short notice. Sorry for the urgent message, I just need to find someone to help out rather soon.''}

Ioan\#c1494bf took the offered paw and bowed. ``Of course, Dear.'' Ey realized how strange it was to call someone a term of endearment as a name. ``May we have a seat? I've just woken up and am still figuring out how to stand.''

Dear grinned and nodded, gesturing cordially with its paw around the side of the building from where it had come, leading the writer around and through a door in the glass.

The interior of the house was as ey had seen, though as they moved through the space where the message had been recorded (a gallery, Ioan noticed) and deeper into the house, things warmed up a little. The concrete walls were softened by hangings, and the furniture was unexpectedly plush, rather than of the firm-cushioned, straight-lined variety ey had expected. Fox and writer settled for an L-shaped couch, sitting facing each other across the bend.

After a moment's hesitation, Ioan began, ``I must apologize, Dear. I'm not sure that you have quite the right person. I'm not really a detective, wouldn't know the first way of finding the one you spoke of.''

Dear shook it's head, \emph{``I'm pretty sure you're the right person. I'm not really looking for a detective, per se. There's enough of those in the Ode clade. They'll suss out the whens and wheres.''}

``Then what-''

\emph{``There's a few kinds of people in the world, Ioan.''} The fox said, voice low and calm. \emph{"There's forgers and honers, of course. Forgers build a thing and plow ahead, and honers settle on a thing and perfect it. Artists generally fall into these classes: prolific and unfruitful artists, respectively.}

\emph{``But you're not an artist. You write, yes, but that's ancillary to what you do. A side effect. There are some other types of people out there, too: catalogers, feelers, experiencers.''} Dear shrugged, \emph{``For its own reasons, the clade needs someone to experience this. There's a lot of history in this, a lot that we've forgotten, a lot that we're trying to remember, maybe some that we're trying to forget. I want you to help figure out the history and story of this.''}

``An amanuensis,'' Ioan said.

Dear brightened, its ears perking. \emph{``Precisely. And what a delightful word, too.''}

Ioan grinned, ``That's good, then. This is very much more my arena. I'll keep this instance around and keep \#tracker up to date.''

The fox nodded and looked up, smiling as it's partner came in with three thick-walled, wide-brimmed mugs of coffee, setting two of them down on the corner of the table near Ioan and the fox. ``Heard you were tired,'' they said, walking off with their own mug.

Dear watched them go.

``Your partner?'' Ioan asked, feeling that a moment of chitchat was necessary. Ey grabbed eir mug eagerly. It smelled quite good.

The fox nodded, picked up it's mug as well and leaned back into the cushions of the couch, slouching. \emph{``Mmhm. Finally decided to explore relationships,''} it said. \emph{``They accuse me of treating it like an art project''}

Ioan grinned. ``Well, are you a forger or a honer of relationships?''

Dear rolled its eyes, said, \emph{``Touché. I'm trying to be a honer, with this one. For a long while, I forked to create lasting relationships. Gets lonely, though. It was like being turned down every time. At least from my --- this instance's --- point of view.''}

Ioan felt they were getting a little too deep for having just met, so ey steered the conversation in a tangential direction. ``You fork quite often, then?''

\emph{``Yeah, Dispersionista through and through. Or maybe profligate tracker, as sometimes I don't have the option to let instances linger.''} Something seemed to occur to it, and the fox sat up again. \emph{``Speaking of, do you know much about the Ode clade?''}

Ioan shook eir head, sipped eir coffee. It \emph{was} good.

\emph{``It's an old clade. One of the oldest on the system. Our founder, Michel Hadje, uploaded basically as soon as he could, and quickly became one of the, er, loudest voices on the system. He campaigned for sensoria to be included.''}

``I've heard of Michel!'' Ioan sat up straighter. ``Usually in the context of the founders.''

Dear nodded.

``So what is Ode, then? His old username?''

\emph{``No, a poem,''} Dear laughed.

``Oh! Oh, of course. So Michel wrote this poem\ldots{}''

\emph{``No, not actually. Michel had a friend, a good friend, who wrote the poem.''} Dear said, speaking more slowly now, sounding less rehearsed. \emph{``When the friend died, Michel memorized the poem. All us up-tree instances do our best to keep it memorized as well. Really memorized, too, in the forefront part of our head, up where we think about it, not stored in some exocortex.''}

``Is that where your names come from?''

\emph{``Mmhm. Each of us is named after a line in the poem. I'm Dear, Also, The Tree That Was Felled, and my first long-lived fork is Which Offered Heat And Warmth Through Fire. My immediate down-tree fork is Dear The Wheat And Rye Under The Stars.''}

Dear splayed its ears, grinning sheepishly, \emph{``It's not actually a very good poem, I must admit. Michel thought so from the beginning, too. His friend, though, when they died, when they killed themselves, it really tore him up. We all still think of them often.''}

Ioan nodded, ``It must be quite long, then.''

\emph{``It's only about a hundred lines, divided into ten stanzas. There are only ever ten branches as direct ancestors of Michel, and each branch only ever has ten long-lived up-tree instances. We may be Dispersionistas, but we're a small clade.''}

``And the poet? Who are they?''

Dear bristled, then mastered its instincts. \emph{``That's The Name that we don't share. The information that someone supposedly did share. Someone of the clade or close enough to it to know.''}

Ioan's mind swirled, confused at the fox's reaction, the concept of not sharing a name that was clearly important. ``I see,'' ey said into eir coffee, covering eir confusion. ``So you'd like me to help in finding this person and act as amanuensis along the way?''

Nodding, Dear held out its paw once more. \emph{``If you'd be willing, that is. We'd be glad to have you aboard.''}

Ey was already sold, Ioan knew, but all the same, ey took a moment longer to consider the ramifications of the job.

Ey shrugged, reached out and shook the fox's paw. Dear grinned, shook back.

\emph{``Excellent. I've shared just about all I have to share on the topic for now, though as we get updates, I'll pass them on to you.''} Dear leaned back into the couch once more, \emph{``For now, stay. Finish your coffee, at least, though feel free to putter around for a while. Or just stay here. We've got an apartment on the side of the house. I've already talked with-''} it said it's partner's name, Ioan didn't quite catch it \emph{``-about it.''}

Ioan nodded, ``Thank you. I think I'll head home in a bit and sync up with myself, and start the research plan. Do you have any suggested avenues I should start down?''

\emph{``Of course,''} Dear smiled. \emph{``As for research, dig a bit more into the Ode clade for now, probably. when I send you updates, maybe those will lead to different topics.''} The smile turned into a sly grin. \emph{``I know you're not a big fan of sensorium messages, but as that's how the clade communicates --- those of us who do, at least --- I regret to say that you'll be getting quite a bit more.''}

Ioan gave eir best polite smile.

%%%%%
\chapter*{RJ — 2112}

RJ allowed emself to sleep in until near eleven that morning. Last night of dress rehearsal, might as well be well-rested.

Many other members of the troupe held part time jobs during the day, and ey ran a small consulting business of eir own. The more industries that dove into immersive tech, the more eir expertise was worth. Even so, with all that ey did, ey made enough to not have to worry about holding down more than the one full-time gig.

As it was, on days when ey had nighttime rehearsals, ey felt no compunctions about sleeping in. Nothing to be up for, only the 'net to keep them occupied in the mornings, little enough need to get moving.

It was Priscilla who eventually succeeded in waking em, butting her head against eir cheek and purring obscenely. The more insistent the cat became, the less able ey was to ignore her intrusions on eir admittedly banal dreams.

Fine. Trudge out of bed. Refill cat's water and food. Give the requisite morning pets to keep her happy. Scoop the litter box. Make self a pot of tea. Tea to shake the grogginess.

Ey sat at the tiny kitchen table, sipping from eir oversized mug and watching the late morning traffic from their window. Mostly business traffic, with the occasional mother with child in tow. Black cabs. Scooters. Bikes.

By the time ey had finished eir first mug of tea, RJ had woken up enough to start on the prowl. As with the night before, ey made sure that everything was in order before touching eir rig. Ey'd taken care of the cat, but ey still needed to eat, emself. So, remembering eir promise, ey set about making a small pot of rice. Fifteen minutes to cook, plenty enough time to finish another mug of tea.

RJ left most of the rice cooling in the pot and took for emself a small bowl of rice and leftover curry. The process of swiping eir hand over the controls of the stove had reminded em of the deck that Sasha had shared last night. There was no reason to think that some random person in London would have much to offer in the case of another person ey had never met getting lost. No reason not to try, though. Maybe there was something, some small insight that ey had that, which, when pooled with those of others, which would help in some way.

So many maybes. So many mights and perhapses.

Empty bowl in sink. Third and final cup of tea in the thick-walled mug. Good enough. Ey allowed emself to settle before eir rig at last.

As before, ey keyed in the password and rested eir hand onto the cradle for the two-factor. However, instead of delving in as ey had last night, ey flipped up the monitor and pulled the keyboard closer, swinging the hand rests to the side and the headrest up and out of the way. No need to go immersive, with work like this. Ey could just as easily work as a fox, of course, but it was so easy to lose track of time in there, and the night's rehearsal mustn't be forgotten.

``Let's see,'' ey murmured, taking a sip of tea before setting the mug down

Ey called up Sasha's deck.

\begin{longtable}[]{@{}c@{}}
\toprule
\endhead
Cicero Lost Nov 2108\tabularnewline
Priv eyes only\tabularnewline
See Debarre for ACLs\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}c@{}}
\toprule
\endhead
Dr.~Carter Ramirez\tabularnewline
specialist in lost\tabularnewline
so. London\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}c@{}}
\toprule
\endhead
Mr/Mrs.~Jackson\tabularnewline
parents, can't get much more\tabularnewline
dad in govt, mother stays home\tabularnewline
\bottomrule
\end{longtable}

And on it went for nearly a dozen cards. Each had its own cover embossed with a few lines of type, and each contained upwards of a gig of information culled from various sources, doubtless of varied quality.

RJ flipped through each, gleaning what ey could from a quick scan, before collapsing the deck once more and sitting back to think. Nothing in there seemed new. Nothing out of place. Ey had only received the deck last night, and yet nothing felt like it had been revealed, uncovered.

Ey had heard of the lost before, and the name Ramirez was commonly tied with the hundred or so cases that had cropped up over the years. The family\ldots{}no, nothing to be gained there, at least not that had already been tried by Debarre. And again, there was the problem of being a random nobody in the UK: no one known, no one with power.

None of the rest of the cards carried any real significance to em.

If there was anything RJ was going to add to the conversation, it would be through eir connection to Cicero. Something ey knew, something the two had shared.

A small notification slid down from the top of eir monitor, covering the upper right corner of the screen.

\begin{quote}
\textbf{D --- D --- R}

Voting begins in \emph{5} minutes on \emph{referrendum 238ac9b8}:

Summary: \emph{Tariffs on importation of goods from the Russian Bloc\ldots{}}

Cost: 1,000

Bounty: 280,000
\end{quote}

RJ reached to swipe the notification away. Ey had very little stake in the uncomfortable alliance between Western Federation and Russian Bloc. Could care less, honestly, about taxes on things that ey'd never buy. Then something clicked within em, and ey halted eir motion.

\emph{Cicero.}

Ey hastily shuffled back through the \emph{Cicero Lost} deck until coming up with the `recent net activity' card and pulled up the contents. It took a few moments to remember how to sort tabular data --- database classes in high school, so long ago --- but eventually, ey got the table sorted around the activity type. Ey scrolled rapidly through the list until ey got to the list of Direct Democracy Representative entries.

There was the connection. The one thing that RJ and Cicero had was their arguments over politics. Not just politics, but the worthiness of the current political system in all of its facets. Arguments upon arguments upon arguments, cross fox and tabby cat with their ceaseless arguments in the Crown Pub.

RJ was firmly on the left, but ey felt the representative democracy combined with the DDR was a pretty good system. It was fine. It worked.

Cicero, however, seemed to waver between socialism and anarchy, depending on factors such as how much he had had to drink and how angry he was at the most recent vote.

\emph{I certainly can't see broad shifts going my way,} he had slurred on more than one occasion. \emph{Least I can vote. Vote on every damn thing that comes my way.}

Ey made sure syncing was turned on across all copies of the deck before snipping those rows out of the activity table into a card of their own:

\begin{longtable}[]{@{}c@{}}
\toprule
\endhead
DDR votes\tabularnewline
todo: process by record\tabularnewline
1 month, 835 votes (!)\tabularnewline
\bottomrule
\end{longtable}

The icon in the upper left of the screen showing the deck twirled gracefully to show the sync.

Cicero had voted precisely how he had talked. On the surface, he was no different than any other leftist socialist on the DDR.

Along with the ability to vote on issues directly came the ability to comment --- for a price. DDR votes didn't cost money, but they did cost credit. Up to 1,000 per. Credit gained by voting on cheaper issues, beginning with a few freebies in the tutorial.

What Cicero's records showed was that he was wealthy. Incredibly wealthy. RJ had a few million DDR credits banked away in case a high value issue that ey felt strongly about cropped so that ey could make a comment. Unlike voting, commenting could cost upwards of five million credits. And one could buy their way to influence by flooding issues with comments.

Cicero's wealth surpassed RJ's at least a hundred times over, if not more. For someone to be as active in commenting as ey knew the cat to be and still have that much in credits stored up showed a dedication to following politics that was just barely hinted at by those tispy rants. Cicero was well connected, well read, and, most importantly, a key political figure on the DDR comment sections to an extent that none of the Crown regulars had ever expected.

RJ sat back in silence for a few moments before muttering, ``Well, shit. Prisca, you don't suppose\ldots{}''

Rather than finishing the thought out loud, ey dashed off a summary in the notes attached to the card.

\begin{quote}
AwDae here. Looks like there's a lot going on in DDR activity (where'd you get this, Debarre?). Cicero was into a lot, and I'm not trying to go all conspiracy nut on you all, but do you think that maybe he got in too deep or something? Not saying someone tried to do it too him or anything, just that maybe the more one uses the net, the more likely it is to happen to them? I mean seriously, look at all of his votes, and his stash of credits! I'll keep poking at this after rehearsal.
\end{quote}

The tea had gone cold long ago, but ey downed it all the same. Ey'd spent longer than planned plowing through the data the hard way and ey was risking being late if ey didn't start hustling.

It was nearing dusk by the time ey left, the suit newly brushed and ironed, the gloves newly washed, the RJ newly shaven.

On the way back to the tube station, ey stopped by a Thai counter and picked up a take-away container of noodles for the night. Ey made it halfway through the container before the rancid belch of station wind suggested ey pack it away before heading down to the platform.

Throughout the ride from Benthal Green to Oxford Circus, RJ's mind continued prowling through the data in Sasha and Debarre's deck. Ey kept mulling over that surreal number of credits. Just how much social currency was bound up within the pseudo currency of the DDR credit system?

Cicero had built himself up into a proper political player.

%%%%%
\chapter*{Carter — 2112}

The morning's alarm startled her awake. Disorientation --- when had she fallen asleep? There seemed to be no line delineating squirming under the covers and the buzz of her phone.

And here she had thought that the end of grad school had meant the end of six-hour nights of sleep.

Blearily, she pawed at her phone to swipe the alarm off. It was tempting to go back to sleep --- \emph{after all,} she mused, \emph{the lost weren't going anywhere} --- but she managed to at least kick her feet out from under the covers and sit up. Frizzed hair hung down around her face, shielding her from the world for just a little bit longer.

It was her phone, as always, that brought her back to reality. It's mere presence, even silent, was enough to draw her forth.

\begin{quote}
Ramirez

Another, this time with scans from before the incident. Another furry, you don't think that's got to do with it, do you :p

S
\end{quote}

The brief, ungrammatical message from Sanders left her nonplussed until she'd put it together that he was talking about one of the other subjects' histories, something about him being part of some fandom. Sanders didn't honestly believe that people who pretended to be animals on the 'net were somehow more predisposed to get lost than everyone else. And, to be honest, neither did she.

All the same, the thought stuck with her through two cups of coffee that morning, the first in the kitchen and the second out of a travel mug on the tube as she headed out towards the UMC campus.

\emph{Another furry, you don't think that's got to do with it}.

She felt sluggish. Craved another cup of coffee even after she'd reached the bottom of the mug she had with her. The thought nagged at her, caught like some spinning shape against the threads of her thought in a way that the rattle and screech of the train couldn't displace. It tugged those threads free, stitch by stitch, until it reached\ldots{}what?

Until it reached the hem, and then the same thing over again.

``Holy\ldots{}holy shit. Holy shit.'' Carter said, startling the elderly lady next to her. She murmured an apology and fished her phone out, thumbing in a quick message to the team.

%%%%%
\chapter*{Ioan — 2305}

\noindent The first message was not long in coming, arriving about an hour after Ioan\#c1494bf arrived home. At least it wasn't high priority; ey had the choice to accept then. Half duplex, though. Would be an actual conversation.

Ey sighed and closed eir eyes. The things ey did for work.

Ey accepted the message

\emph{``Hi Ioan,''} came Dear's voice. It was still seated on the couch. \emph{``Long time no see, hmm?''}

Ioan nodded, subvocalized, ``Yeah, took you ages. Have something for me?''

\emph{``Maybe. We've got a file from someone down-tree. Or, well, hmm''} It appeared to think for a moment before continuing, \emph{``Someone down-tree from me found a file, and he thinks it might be a file from the clade, maybe one of the original ten.''}

Ioan waited until the fox was done before responding, ``Alright, send it over.''

The file arrived promptly. Eir shoulders sagged.

\begin{verbatim}
-----BEGIN AES BLOCK-----
QUVTAgAAGUNSRUFURUR...

-----END AES BLOCK-----
\end{verbatim}

``What's an AES block?''

\emph{``An old encryption algorithm. And I mean \textbf{old}.''} Dear looked a little embarrassed, \emph{``We like old things. That's why we figure it's probably from one of us.''}

Ioan thought for a moment before responding, ``So do you want me-''

\emph{``You don't need to worry about the file itself. That's why I didn't just forward it to you automatically,''} Dear paused, then added. \emph{"Though I probably should have. Amanuenses form an} Umwelt, \emph{so now this is part of yours, now. We'll talk about it at the end. Something to keep in mind, I guess. When we find the key, we'll let you know and send over the contents."}

``Good. I gave AES a check, and you're right, that's ridiculously old. Can't you just crack it?''

\emph{``We could. Some of us probably already have. I want the key, though. It's probably a word or something, and may prove interesting.''}

``Interesting?'' Ioan asked.

\emph{``Interesting in that the act of finding the key may turn up further clues.''}

``Ah, good point.'' Ioan pondered, then added, ``Keep in touch, yeah? I'll do some digging on old cryptography, too, and see what all's out there.''

\emph{``Good fucking luck. Cryptonerds were --- are --- very wordy. There's going to be a boatload to sort through.''}

Ey grinned, ``I'll fork and research, then.''

\emph{``Good plan. Gonna get back to the hunt, and hey, Ioan,''} the fox gave an earnest smile. \emph{``Thanks. Even if I'm just running ideas past you, it's good to put in words.''}

``Of course, Dear.'' Ioan waved. Ey always felt silly interacting with sensorium messages. Would \#tracker think em crazy? ``Thanks for the project.''

Dear bowed, signed off.

\#tracker was, indeed, giving \#c1494bf a bemused grin.

%%%%%
\chapter*{RJ/AwDae — 2112}

RJ arrived at the theater early, the last few meters of the walk having been spent hastily finishing the carton of Thai. Carton and chopsticks wound up in the trash as ey swiped eir way into the theater.

``Sorry, Johansson, I'm here.''

The hulking director laughed. ``You're here five minutes early, RJ. What on earth are you sorry about?''

``What? I- Oh.''

``Lot on your mind, kid?''

``Nah, I'm fine. I mean,'' RJ frowned, squinted. Anything to get emself in the work mindset. ``Yeah, sorry. Woke up early and spent a bunch of time researching. Guess my head's still elsewhere, boss.''

``Well, alright,'' Johansson rumbled. ``So long as you get your head around work. Hey. More crew.''

RJ bustled into the theater and made eir way down to the pit where the mics had been stored. Ey handed them out to the actors who would be wearing them, ticking off the cheat-sheet to align proper mic to correct actor.

Ey bounded back up the steps two at a time to the tech booth and set about waking the theater up. Caitlin was already delved in, so it would already be shaking its sleepy head. Ey just had to help it wake up the rest of the way.

RJ exchanged cheery greetings with the lights lead as ey shrugged out of eir jacket, draping it over the back of the chair. Ey slipped eir hands carefully out of eir gloves. Contacts gleamed from eir digits, freshly polished and clean.

RJ settled into eir chair and delved in to greet the theater. It purred in recognition, brushed up against em. It stretch stretched and unlimbered. Eir hands rested lightly on the contacts in the cradles, forehead against the headrest, thoughts of Cicero and Debarre, of Sasha and the lost left back with eir body.

The first half of rehearsal went by without much trouble. Johansson had apparently highlighted a few areas of concern, so they began with those. From there, the cast has followed his lead, adjusting as needed per their dear leader's suggestions. RJ and Caitlin kept a script running so that they could keep up with the director and Sarai, the stage manager.

When the clock hit eight thirty, Johansson called for a break and informed everyone that they would be running through top to bottom after. Last chance for a full run-through.

RJ gave the purring theater some reassuring warmth and backed out of the connection, reveling in the snap of eir fingers pulling away from that slight magnetic grasp of the cradles. Ey wiped eir hands dry and flexed fingers to keep limber.

Ey spent the break walking around the theater and stage in one big, looping arc, simply listening. Hearing from the theater's perspective so often, it was easy to get wrapped in the omniscience of it all. Good, too, to hear the way that the ambient sound moved through the room, reflected off of walls and ceiling, died among the baffles. It would all be different with people in the seats, to be sure, but the acoustics of the space were beautiful on their own.

Johansson whistled piercingly. Back to work, back to the stage. Back to the booth and back to the contented and satiny-soft embrace of the theater for RJ.

It was around the end of the first act that RJ started having problems.

When one was delved in, one could always focus hard enough to feel the way their head felt against the headrest, or sense the way that their hands rested within the cradles of the grips. Trickier, sure, when one was as immersive as tech required. Bodies weren't a thing in that liminal space. Ey was as much the room as the room was itself. No forehead, no hands. No headrest or grips

By the time ey had brought house sound down in time for the curtain, RJ could feel a numbness creeping. A stealing of sensation. A non-feeling flowing slowly over emself from the base of eir neck outwards, stretching out along eir scalp, down eir arms, not-tickling along eir ribs.

Ey had been willing, desperately, to chalk it up to nerves or exhaustion. It had been such a long week. Thoughts of Cicero, doubtless cradled in some hospital creche: strictly disallowed but nonetheless teasing around the edges of consciousness.

Tired, yes. Exhausted. Yawns.

By the time ey couldn't feel the plastic of the headrest or the cradles beneath eir hands, no matter the desperation, ey began to panic.

Panic, yes. Just anxiety. Performances.

All the same, it was final dress. Ey would be able to head home and catch up on sleep. Drink some tea. Hot chocolate. Pet the cat. Whatever ey needed.

Need, yes. Baser than want. Imperatives.

By the second curtain, something was desperately wrong.

Ey hadn't missed any cues yet, but ey couldn't seem to figure out how to work eir `voice'. That thing that wasn't talking. That subvocalization used to communicate with Caitlin Sarai Johansson anyone. The immersion-mouth to chat to talk to radio for help a non-entity non-thing non-here, gone, leaving em feeling exponentially more cut off from the rest of the theater as time went on.

Numb, yes. Yet strangely embodied. Strangely tangible. Strangely localized. Oh god oh god please help please help. The play. Ey had work. Ey had the theater. Ey had the room and the lines and time and space to manage. Ey had a home and a cat and Sasha and Debarre.

Had, yes.

It was the muzzle that was the kicker. The muzzle and the tail, which ey felt --- any feeling a beacon in the storm of numbness which had long since enveloped em entire --- with a piercing intensity. Felt, bordering on and then diving straight into pain.

\emph{Pull back,} ey begged. Every bit of training begged. Every nerve begged, screamed. \emph{A bug, a glitch, an error. Pull back oh god please pull back.}

Ey lifted eir hands --- paws? --- in a coarse, jerking motion which, along with the act of pulling eir head back from the contacts, led to em toppling over. There was no chair to catch em.

And that was when ey missed eir cue.

The curtain went down, the lights dimmed, and then, ringing clear, a thin giggle filled the auditorium. The lead laughing at a misstep. A quiet joke to share at the pub later. No harm. Sound was off, right? Curtains would eat the sound.

``RJ,'' Sarai whispered into the silence of the theater's sim. ``Stay on cue, bud.''

No answer, no apology, no acknowledgment that a note had been made. No signal.

``RJ?''

``What's going on up there?'' Johansson's subvocalization rumbled through the director's channel in the sim.

``Something's wrong, boss, lemme back out and check up on RJ.''

``Hold places,'' Johansson said aloud to the the theater. The open channels from the actors' mics carried a few quiet whispers in response. ``Hold on, quiet please.''

Moving with a quickness which belied his bulk, Johansson jogged up to the tech booth and slipped in as quickly as possible to keep sound from leaking out. Sarai was trying to rouse RJ.

Like the projector bulb's heat burning through celluloid film, the third curtain had signified a drastic change. Slow enough to be observed, faster than ey could hope to avoid. The few tenuous touches on reality that held RJ into eir seat in the tech booth scorched and peeled away, acrid smoke stinging eir eyes. And the pain spiked.

RJ lay on a tile floor. Dirty. Yellow. Brown specks, dark enough to be black.

The tiles were completely regular, one foot on a side, obviously made of some synthetic material. Harder than linoleum, softer than stone. They were glued to a concrete foundation. No wasting time with grout, each tile butted up against the others to form a grid of thin, black lines showing where the dirt of hundreds of feet had been ground into the remaining seams. Thousands. Millions.

Ey couldn't move yet, but ey could see that the world was bounded. There was a thin plastic strip of molding around the edge of a wall. Above that, regular rectangles of blue. A wall.

``Something's not right, boss. He's totally unresponsive on the line.''

``Pull him, pull him! Hit the panic!''

Caitlin, who had backed out moments before, and Sarai both leaped to RJ's sides and pulled eir hands up from the cradles, rocking em back from the headrest to lean against the back of the chair. All according to training.

Eir body flopped lifelessly against the cheap plastic mesh.

Caitlin slapped the small red button on the side of the rig, fingers coming away dusty. Below the desk, drives sparked to life and dumped the last thirty minutes of both sim and brain activity from the user.

``The hell?'' Johansson growled, reaching in a thick pair of fingers to press against the side of the sound lead's neck. ``He's got a pulse. Check his eyes, Sarai. Caitlin, call. Now.''

Shaking, Caitlin pulled her phone from her bag and struggled to unlock. She gave up, swiped to the emergency dialer, called out to emergency services.

``They're rolled back, boss. Bloodshot, too.'' Sarai tugged back the collar of RJ's shirt, exposing eir exocortex's simple color-coded readout, set at the base of eir neck. ``Blue. What the hell\ldots{}''

``Ey's not jacked in, though,'' Johansson said. A statement brooking no discussion. ``Can't be.''

``I think--'' Sarai trailed off hoarsely, cleared her throat, tried again. ``I mean, do you think ey's lost?''

``Caitlin, what's our status, girl?'' Johansson didn't wait for a response, throwing the door to the tech booth wide and shouting out toward the stage, ``Cut! Manually shut off your mics and take a seat where you are. Do not move. Emergency services will be here soon, and will record what they can.''

Lockers.

The blue rectangles were lockers. The first hint were the vent slots a few inches from the bottom of each narrow rectangle, but, as ey lifted eir muzzle from where it lay on the tile floor, ey could clearly see the locks halfway up each door.

Tall, narrow lockers. Blue. Yellow tile floors. Thin tile glued to cool concrete. The scent, the very feel of the place.

AwDae struggled against crashing waves of panic. Struggled to make all of this information fit in eir head. Struggled to make it all fit in with the fact that ey was currently halfway between human and fox. A cross fox dressed in a suit, laying on the floor of the central corridor of eir old high school.

``The hell?''
