\chapter*{Dr Carter Ramirez — 2112}

``Listen, Ramirez, I'm just not sure if you-''

``No.~Come on, Sanders, just hear me out.'' Carter sighed and settled her weight against the edge of her desk, taking a slow breath to buy herself some time and organize her thoughts. ``I'm just saying that we ought to look into social connections between the patients, too. That way, maybe we can see if there's some factor that's tying these occurrences together. With that under our belt, we may be able to formulate a better theory of what's going on here, even neurologically.''

Sanders hung his head, visibly counting to ten, and then shrugged, ``It's just that you're talking about a social vector here, Carter. Not only do we have very little data to go on, but there's no indication that this is something passed from one person to another. All of the data suggests random-''

``Sanders,'' Carter said, voice stern. ``I know how the project works. I know the data. There's a lot of questions still left in the air. I'm not suggesting that getting lost is contagious or anything. We dismissed the virus aspect ages ago. I'm merely suggesting that we might find shared factors within a social realm as well as the physiological.''

Carter stood her ground. No sense paling under his glare. She was lead of the research team, she could tell Sanders to do whatever she wanted him to. Or, well, strongly suggest. Hell, there was no reason for her not to. She was plugged into all of the teams that he was not privy to. He may have been lead of neurochem, but Carter was above basically everyone except the UMC itself, and whatever grantors were sponsoring the project.

Eventually, he caved, shrugged, turned his back on Carter. He nodded towards his own team.

``Look, Sanders,'' Carter said, following after. ``You're a fantastic doctor, and I really respect that, I really do. Not trying to impugn that or anything, and I'm not pulling labor away from the neurochem team. I'm merely suggesting that we add a sociological aspect to our attack here.''

He held up his hands in surrender, then headed for the coffee station.

Carter rolled her eyes and let him go. She turned back to the remaining team. ``We've got a hunch on the social front. Or, I do, but I think it's worth following. There's a couple patients who are involved in the a fandom and there's distinct ties between them. They're loose ties, sure, not everyone knows everyone else, but they \emph{are} there.''

They nodded. Some looked unconvinced, but none hostile.

``Let's time-box half a day to chase down these ties and see just where they lead. If they lead nowhere, fine. If we can find a way to tie them together, then we dig into all the ways that the web ramifies.'' She grinned in a way she hoped was disarming. ``Worst case, half a day is spent tracing along the 'net, but best case, we find a way to tie these cases together that lets us predict --- and then maybe interrupt --- future cases. Got it? Catch you at lunch.''

Carter sighed. Speeches. Hell of a start to the day. She collapsed into her desk chair, closing her eyes to collect her thoughts.

Rather than sequester herself in an office, she had taken a desk among the team. Four foot cube walls separating her from her neighbors. They were made of glass. Token walls rather than real ones. Not that there was much room for an office in the repurposed classroom. All the same, the deliberate attitude with which she had chosen to join everyone in equal conditions had endeared her to the more stubborn among the crew.

On the other hand, the lawyers-\emph{cum}-statisticians were badly out of their element. Thankfully they had their implants and were able to spend most of their time in the office sim.

All the same she wished for an office, if only for the door. A nice, thick, hardwood door. One with a solid core so that she could voice her ideas. Or scream.

Sometimes she just needed the ability to put things into words. No matter how often she tried to set things down in the notes on her phone, she always felt hampered by the relatively small screen and her clumsy thumbs. Neither had she gone full immersive-on-the-go yet. Something about that glassy-eyed stare, the silly headband, the controllers gripped like walking weights, packed full of electronics, set her teeth on edge.

At least she had a private corner in sim.

She delved in rather than work on a tablet or screen. \emph{One scream,} she promised herself. \emph{Then I'll organize shit.}

Once she left her office area, Carter's chosen workspace, her `desk', was totally black. Not the complete blackness of unseeing, but sort of vaguely luminescent darkness of \emph{Eigengrau}, as if wherever she looked, she saw the faint light of non-seeing. It was black enough to be easy on the eyes almost by definition. At least, such as they were in the sim. Black without being unnerving.

Scattered throughout the space were decks. Decks upon decks.

Each was a point of light. A white rectangle with just enough depth to give the impression of being several cards stacked on top of each other but no more. Each was surrounded by a dim halo that dispelled the darkness. If she were to engage with a deck, it would fill her vision almost to the periphery with that fine velum paper. Almost, but not quite: the non-black provided a border and seemed to shine, in its own non-light way, through the paper. From there, she would be able to explore and expand that portion of the project at will.

The decks themselves were organized into groups, surrounded by bright lines of white string --- literally string; Carter had chosen cotton string as her group delimiter. Decks within groups were linked by string, and many of these groups in turn were related to one another with more intangible threads.

She was as a ghost in this. A non-being. A being of nots. A gesture from her non-hand would show the whole setup from the top. The mind, ever attracted to a two dimensional representation, sometimes appreciated this aspect. The mind, ever attracted to the \emph{hereness} of space appreciated walking through the sim just as much.

Even with perspective in play, the scientists and lawyers working the project had tended to alternate between the aerial view and the interactive view, with the cards positioned at chest level throughout the sim.

Everyone's view of the sim was different, in its own way. Sanders, she knew, preferred an oak-paneled room with dark green carpet, a facsimile of luxury with each of the grouping lines drawn out in finest silver. Others preferred pencil sketches, harsh angles, subdued colors on a dim background, or even more abstract, textual interfaces. So long as the concepts of decks and spatiality were maintained, it was up to the individual.

Cards had their ACLs, too. Some were visible only to the individual. Some were visible to everyone, but only on the surface, with details invisible to others. The vast majority were visible to everyone, completely open.

Carter began creating a publicly visible grouping, knowing that others were delving into the sim along with her, visible as diffuse shapes in her dark space. She titled the group in her stolid, blocky font of choice. ``The Social Connection''.

From there, she began creating sub-groupings. For cases. For leads. On and on. For the ``cases'' group, she tapped a few of the case decks to make symbolic links, drawing lines of cotton twine which she dropped in.

Two were positioned at the top of the list:

\begin{longtable}[]{@{}r@{}}
\toprule
\endhead
Patient aca973d7\tabularnewline
M --- 2086-01-28\tabularnewline
Lost: 2108-11-08\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}r@{}}
\toprule
\endhead
Patient 0224ebe8\tabularnewline
X --- 2084-05-09\tabularnewline
Lost: 2108-12-04\tabularnewline
\bottomrule
\end{longtable}

Carter connected these two cards with fine thread. Hanging pendant from that, she created a metadata card, more tag than card:

\begin{longtable}[]{@{}l@{}}
\toprule
\endhead
Possible acquaintances\tabularnewline
\bottomrule
\end{longtable}

The others, those shadowy figures, caught on to what she was doing, and got down to work, dragging symlinks of decks and expanding this new group of social connections.

Carter pulled back out of the sim when her personal timer went off, fifteen minutes before the time-box was up.

She backed out and made her way from her workstation to the small counter at the front of the old classroom. She filled the electric kettle from the tap and set it on its base for tea, letting it heat up, then scooped a few heaping spoonfuls of coffee and chicory into the coffee maker. While she was in the sim, she had ensured that everyone else's rig would have an alarm for the time-box, and it was only fair that she make everyone a cup of coffee before they pulled back.

The coffee had finished brewing and the mugs were all set out in a row in front of the pot and kettle, each waiting with handles out toward the room for ready hands. Carter had poured herself some of the coffee, thick and bitter, and topped it off with a dash of sweetened creamer to dull the latter.

One by one, the ten techs pulled back from their workstations and ambled, glassy-eyed, to the counter where the coffee lay. Carter suppressed a smile: a horde of zombies in various states of disarray drawn to caffeine. It'd be nice, but over the months they had spent on the project, the team had settled into a comfortable ritual of meetings over coffee. The habit remained unbroken.

``So,'' she started, once everyone was gathered around and tead-and-coffeed.

Silence. Sanders wouldn't meet her gaze.

Finally, she caved and broke down her thoughts. ``Time-box is over. I think we got a bunch of good stuff done in a few hours. There's definitely connections there. We've got a good number of them among the cases we have at our hands, but there's precious little data on why those connections exist. We've got a few furries, a few 'net addicts --- well, more than a few --- and we've got a whole lot of DDR junkies. None of those point to anything that would lead people to getting lost.''

``Man, have you \emph{seen} DDR zombies, though?'' Everyone laughed.

Another voice piped up, ``And the correlation on the neurochem side is extremely low. Almost non-existent.''

Sanders smirked down to his coffee mug before hiding the expression with a sip.

``No, there's no doubt about that.'' Carter sighed, shrugged, ``So, again, time-box is over. What do you think? Is this line of thought worth pursuing? Plus-one, minus-one, zero. Sanders?''

``Minus-one.'' The response was immediate.

Carter slipped her phone from her pocket and started a tally on the vote app she used for that purpose. ``Alright,'' she continued. ``Jacob?''

``Zero.''

Tallying as she went, Carter went around the room, The running tally took a few dings (neither of the lawyers were for the idea, she noticed), but remained net positive until the end of the line.

``We're left at two, then.''

Sanders set his mug down with exaggerated care, but otherwise stayed silent.

``Hardly universal, so let's triage. Can I get one from neuro, one from stats and history, and would one of the law team be willing to devote an hour a day to helping us out? Just to run stuff by as we come up with leads.''

\emph{If you come up with leads,} was written on Sanders' face. She ignored it.

Prakash Das from the neurochem team raised his hand, and Avery from statistics and history volunteered. One of the lawyers, Sandra, gave a noncommittal shrug and promised some of her time, saying, ``We're on shaky legal ground, I think, but we can probably keep it in check.''

``Alright. Let's sync up, you three.'' Carter smiled toward the rest of the group, ``Not leaving you guys behind. One-on-ones and daily standups will continue at the usual times. We'll set another time-box of--'' She checked her phone. ``Three days, after which we'll reconvene and vote again.''

Sanders strolled back toward his workstation, Ramirez's eyes on his back.

%%%%%
\chapter*{Qoheleth — 2305}

Transcript of Node: \href{http://35.165.134.227/node/bea0cf302fcd00863f0c67a91b1a75c0e4ba4863}{{[}bea0cf302fcd00863f0c67a91b1a75c0e4ba4863{]}} with descriptive text by \#d5b14aa.

\secdiv{}

\noindent \emph{The footage shows two persons. One of them has to be Dear, Also, The Tree That Was Felled, who is an up-tree branch of the Ode clade, ninth stanza. No one else has ears that big, nobody else can somehow speak in italics. The other took some research, but I'm confident that ey are an instance of Ioan Balan, a historian and writer. Ey are a tracker, and eir habits tend toward few to no long-running instances. This instance is either \#tracker or one tasked to this project.}

\emph{The two persons are sitting outside of a cafe, from whom I obtained this footage. They are in conversation. Going to sit down and watch this.}

\begin{quote}
\textbf{Dear, Also, The Tree That Was Felled}: We - er, some other Odists, down-tree from me - have come up with some hints about the message.

\textbf{Ioan Balan}: Oh? Anything good?

\textbf{Dear}: I suppose it depends on your definition of good.

\textbf{Ioan}: Oh great. Excited already. Well, lay it on me.

\textbf{Dear}: So, one of us did a pretty exhaustive search of some records and found some old archive server running somewhere.
\end{quote}

\emph{Oh goodie. Better start gearing up.}

\begin{quote}
\textbf{Ioan}: Wait, start at the top. What were they searching?

\textbf{Dear}: They were searching for the block of encrypted text - not what was in it; they cracked that a long time ago, but I think this hunt is still valid and have some reputation to burn, so...anyway - they searched for the encrypted text itself, and they came across an archive server.

\textbf{Ioan}: Old node boxes? Man, even I feel crusty using one of those, and I'm a historian.

\textbf{Dear}: You're only a little crusty *laughter*. They found the archive server though, and there's a bunch of stuff on it. New, old, the whole thing. There's stuff from ages ago, and stuff from a few hours ago.

\textbf{Ioan}: You're kidding, right?

\textbf{Dear}: I know, it's ridiculous.
\end{quote}

\emph{The fox's ears flop when it gets excited and shakes its head, never noticed that. It's kind of cute.}

\begin{quote}
\textbf{Ioan}: Never met anyone who could actually get one working well enough to add new nodes. So the encrypted text was in a node on the server?

\textbf{Dear}: Yeah. It's still there. Just sent the URI.

\textbf{Ioan}: I...well, I'll have to take it at your word that it's the same as the one you found earlier, I'm not going character by character.
\end{quote}

\emph{Dear seems a little frustrated at this. About Ioan's slowness? I know I wouldn't compare the files. It sounds exasperated.}

\begin{quote}
\textbf{Dear}: Of course, Ioan. Promise it's the same. Needless to say, we found a crusty old server with the block on it, and there's other public nodes on there as well. I'm guessing a bunch of private ones, too.

\textbf{Ioan}: Anything good in those?

\textbf{Dear}: Nothing...penetrable. It's all fairly opaque. To me, at least.
\end{quote}

\emph{Ioan grins at this.}

\begin{quote}
\textbf{Ioan}: Thus us meeting here?
\end{quote}

\emph{Dear nods.}

\begin{quote}
\textbf{Ioan}: Want me to have a look, then? Tech stuff is going to go right over my head, you know that.

\textbf{Dear}: It's not all tech, promise. I just want you to give it a read and see what you pick up from it, you know? Put your amanuensis hat on and just spend some time experiencing.

\textbf{Ioan}: You think highly of me. No complaints, but why can't someone from your own clade fill this role?
\end{quote}

\emph{Dear's quiet. Struggling for words? Our Dear? This must have hit it hard.}

\begin{quote}
\textbf{Dear}: We...differ. The Odists, I mean. But we also want someone out-clade for this. I want someone out-clade for this.
\end{quote}

\emph{Ioan seems taken aback.}

\begin{quote}
\textbf{Ioan}: Do the others not like that I've been brought on?

\textbf{Dear}: Of the ones who know, most are fine with it.
\end{quote}

\emph{Now frustrated/confused.}

\begin{quote}
\textbf{Ioan}: The ones who know?

\textbf{Dear}: We're a little split on how to tackle this in the first place. Different camps, different strategies, infighting. Ioan, you have to understand that, when a clade gets old, it starts to get a little batty.
\end{quote}

\emph{Calm down fox, I'm working on it. Not so frantic.}

\begin{quote}
\textbf{Dear}: Some clades try to get around this by keeping a certain core group of instances - talking mostly Dispersionistas, mind - in a setting that keeps them as sane as possible, feels very 'normal'. Or maybe some are researching forking from earlier points, from down-tree, rather than from where they are now.
\end{quote}

\emph{It furrows its brow.}

\begin{quote}
\textbf{Dear}: We don't. First of all, we started way too early on for that to be a thing. We trusted that change would keep us sane, that as instances diverged, especially with mutation algos in place, they'd change enough to keep us from falling apart.

\textbf{Ioan}: And that didn't work?
\end{quote}

\emph{Long pause.}

\begin{quote}
\textbf{Dear}: It kind of worked. I'll put it that way. I feel pretty well rounded, and I'm sure those across the clade from me do too, but...it's complicated. It's like having a super close sib that was raised by a different family, in a different sim.

\textbf{Ioan}: More different than you'd expect, then?

\textbf{Dear}: 'Expect'...fits strangely for this. The problem is that they're still us, we're still them. Clades are like families in a lot of ways, but you have to realize that they're still one individual. We're more different than one individual should be. Does that make sense?
\end{quote}

\emph{It does, Dear. That's why I'm doing this.}

\begin{quote}
\textbf{Ioan}: I guess so. So some of your clade would prefer I not be a part of this?

\textbf{Dear}: They feel that investigating the matter of The Name being said is too close to investigating The Name itself.

\textbf{Ioan}: I don't know how I would respond to that.

\textbf{Dear}: That's my field. Don't worry about it.
\end{quote}

\emph{Ioan holds up eir hands, looks apologetic. The fox has lowered its ears.}

\begin{quote}
\textbf{Ioan}: Sorry, hope I'm not overstepping at all.

\textbf{Dear}: Don't worry about it. It's all good, I promise. It's just that we're really good at arguing, so I've been dealing with that a lot, the last few days. I'm a bit on edge. Let's get back to the archive server, yeah?

\textbf{Ioan}: Sure thing, Dear. Where did you say your cocladists had found it?

\textbf{Dear}: Just in a search. Don't know quite the details about how, assuming just a text search of perisystem stuff, I guess? Not too sure on the terminology, I bought into being an artist pretty hard.

\textbf{Ioan}: *laughter* No worries there, fox. I'm trying to keep up with you is all. I was just wondering if they found anything else.

\textbf{Dear}: You mean like other nodes on the server?

\textbf{Ioan}: I'll poke around at those, look for ties and such. I was more wondering if they'd found anything in their search that didn't meet the relevancy threshold for them. Stuff like things linking back to the server, or anyone talking about this *pause* Hebel Qoheleth.
\end{quote}

\emph{Silly name. Oh well. Dear looks taken aback.}

\begin{quote}
\textbf{Dear}: Hadn't really thought to ask. Don't suppose they did, though. Do you think it'd be worth having them search around more? Lowering the, uh, relevancy threshold? *laughter*

\textbf{Ioan}: Yeah, I think so. Though now that I've got it too, I can do some of my own digging. Kinda want to see who likes The Bible so much as to name themselves that.

\textbf{Dear}: The Bible?

\textbf{Ioan}: Yeah, Qoheleth is the...uh, the teacher, or gatherer, or a bit of both, really. That's what the book usually translated as Ecclesiastes is named after. Not sure about Hebel. What's kemmer, by the way? The passphrase?

\textbf{Dear}: How did you...nevermind. Kemmer is something from a book. One of our favorites. It's complicated and out of scope, but it relates to fluidity of gender. Very big, in our clade. I've opted out.

\textbf{Ioan}: So I noticed. It makes sense, though. I'll make a note to look it up.

\textbf{Dear}: Glad someone's thinking about this stuff. Sounding more like a-

\textbf{Ioan}: Private investigator?

\textbf{Dear}: *laughter* I was going to say historian, sounding more like a historian every time we talk. But you never know, maybe you'd make a good PI.
\end{quote}

\emph{That was fast! I may have less time than I had thought. Dear's lovely, and it's totally right: on the other side of the clade, there are some who'd not like this kind of digging. Too entrenched.}

\begin{quote}
\textbf{Ioan}: I can't tell whether or not I should be flattered.

\textbf{Dear}: It's a good thing. Just keep digging, and we will too. I'll be about, too. Got a few more things to wrap up to finish the current gallery business, but after that, I'm just going to work on this - with you if you don't mind - and try and figure out what's even happening in the clade. Keep in touch, yeah? Ping me whenever?

\textbf{Ioan}: Will do. *pause* Wait, you're an instance artist, right?

\textbf{Dear}: Yeah, why do you ask?

\textbf{Ioan}: Why don't you fork to work on both at the same time?
\end{quote}

\emph{Dear shrugs, grins, quits. Very lovely fox. Really quite lovely.}

\emph{No time to dawdle watching Ioan try and figure out up-tree instances, though. Must be getting ready. Quit this instance, flush the server of extraneous crap to guide a little more effectively - yeesh, how old is some of this stuff? Need to re-encrypt a bunch of it anyway - and get ready for some visitors.}

%%%%%
\chapter*{AwDae — 2112}

AwDae slowly picked emself up off of the floor, staggering to eir feet.

Ey was standing, swaying, in the middle of a long row of lockers. And then ey was sitting again. Ey didn't feel weak, but the shock of being in the tech booth and theater sim, and then suddenly being back in high school was taking its toll on eir wits.

Ey swiped eir paw from left to right in front of emself to bring up the usual menu. Only, no menu came up. There was nothing in this sim, if sim it was. No global menu, no ACLs, no control.

Panic crested again.

AwDae felt behind emself, reaching for that sense of reality outside of the sim, that cool breeze of the tangible that should be at eir back. It \emph{was} there. Ey could feel it. A cool breath of air on the back of eir neck, but muffled. There was something keeping em from reaching for it, touching it. A thin barrier. A membrane. A sheet of keeping em trapped within the sim.

And then, with a jolt of pain driving like a spike down the back of eir neck and along eir spine, it was gone.

Throughout all of the practice runs, the endless training on the rig that had gone into eir education, that feeling had only come up a scant handful of times. It was the feeling of being forcibly disconnected from the rig through the manual expedient of removing the contacts from the cradles in which they rested. It was the shock of being brought to reality from out of a sim with no disconnection. It was the rush of eir exocortex dumping its core. It was panic made tangible, halfway between electricity and the feeling of missing one's step on the last stair.

With that, AwDae should've found emself back in the tech booth, trying to figure out what strange loop the theater had gotten itself into that would have frozen eir rig.

The lockers never wavered, though, and now ey found emself stuck in eir old high school school with no contact to the world outside of whatever this place was.

Ey screamed.

Ey didn't know how long ey screamed, how many times. Ey didn't know how long ey cried or beat eir fists against the lockers. Ey didn't know where ey was.

Lost.

Lost like so many others.

Lost like Cicero.

Or perhaps Aeneas, Odysseus.

Eventually, ey cried emself out. Eventually, eir tail went numb and eir feet fell asleep.

\emph{Nothing for it.} Ey wobbled to eir feet, kicked off ill-fitting shoes, and began to trudge.

Ey walked slowly down the halls, memories coming back in a wash. Realities blurred effortlessly. Realities of the embodied world. Realities of online life.

Nails on feetpaws clicking against the tile, following the math wing to the student center, a cavernous space that acted as a terminus for all of the different hallways, each hosting a different subject. They spread away from the cavernous room like limbs, a giant insect clutching at the earth.

Neither halls nor hub had ever seen a fox. They were supposed to be home to students. To students and teachers and staff. To humans. To anyone, not some lone half-beast.

Inside the student center, AwDae sat down and tried to reach towards reality once more. Ey sagged, rolling onto eir side in eir increasingly frustrated attempts to pull away from the contacts, though that shock of pain suggested those in reality had pulled em away.

Frustration, anger, fear. Hopelessness. Terror. All simmered within em, working up to a boil as ey tried increasingly harder.

Finally, ey gave up and, hastily brushing at the tears staining eir cheeks, slipped out of eir suit jacket as well. Why keep it?

Ey swished eir tail to the side, and lay flat on eir back on the cool terrazzo floor. Ey pulled eir suit jacket up over eir face and buried eir muzzle in the soft lining. With paws holding the cloth to eir face, ey deliberately let the tears come. Willed them too. Forced. Screamed and begged. Anything for release from the tension building up.

It was a few minutes before ey peeled the coat from eir face and stood back up once more. Exhausted, ey slipped eir arms back into the sleeves of the coat, letting it drape awkwardly from eir shoulders, unbuttoned, fill fitting around eir slim frame. Ey bent down to roll up the cuffs of eir slacks to keep them from bothering eir feet.

It was in the middle of the second cuff that ey realized the absurdity of the motion. In the theater sim, ey didn't have a body, and when ey `woke' in eir normal sim, ey was dressed only in the clothes ey had on when ey went to bed. Usually nothing. Ey disrobed before disconnecting more out of habit than anything.

Why was ey still in eir tux? Did ey even have a tux in eir wardrobe?

AwDae puzzled over this for a moment longer before completing the act. Something to look into later. For now, ey needed to find eir way out. Find eir way back out. Or, failing that, at least one thing ey could complete. One task to complete. Something to make em feel less powerless in the face of it all.

%%%%% XXX do we really need a split here?
% \chapter*{AwDae — 2112}

The sim was startlingly complete.

Perhaps. Ey had been in London a few years, and before that, on the coast at university. Was it complete? Was it accurate? Despair lay around the corner: the thought that the chances of em being able to compare the sim and reality vanishingly small.

In fact, the only thing that seemed to have changed was AwDae emself.

AwDae's curiousity won out. y had made eir way back to the school's auditorium. It was exactly as ey had left it all those years ago. Trudging up the few steps toward the entrance, ey feared that it would be locked. Missing. Somehow erased from existance, such that it had never been there in the first place.

But the door swung easily beneath eir paw and eir nails clicked against the lower portion of the sound guard in the doorway, leading em into a dimly lit auditorium.

The house lights were at quarter, the stage lit only by utility lights from the back. All the same, it was enough for em to find eir way to the small sound booth. A counter with a light --- off. A bank of sliders and knobs --- all zeroed out.

AwDae brushed eir fingerpads along the lower lip of the soundboard. The screws were exactly where ey remembered.

Swishing eir tail out of the way to, ey sat on the stool in front of it. Ey reached a paw up past the master sliders, just around to the back of the board, where ey found the power switch.

Click.

Nothing happened, so ey reached a little further back, finding the power strip for the booth itself, and toggled the switch on that. The board let out a satisfying pop of recognition as it came to life. The brief surge of power echoed throughout the room as speakers awoke. The theater uncoiled, purred to em, just as the one back in London had done\ldots{}what? Three hours back? Five?

Ey fumbled with the booth light, finding the ancient dial switch to wash the unlit portions of the booth in lazy red light. Light illuminated a thin layer of dust covering the board and booth in a matte coating, and countless motes already disturbed. The only breaks in the coating were where eir fingers had brushed the dust away, leaving black slicks.

So familiar. So many dreams. Dreams of flawless performances of breathtaking beauty. Nightmares of feedback and missing equipment.

Acting on a dream, ey slowly brought the master volume up to the spot ey still remembered from so long ago, turned the gain to mid on mic one, and brought the slider up slowly.

Blinked.

A soft hiss filled the hall. The channel was open.

\emph{That doesn't mean anything,} AwDae thought. \emph{Could be anything plugged into the snakehead in the pit. A line with a powered mic, a wireless receiver. Hell, a fault in the system.}

All the same, it was something. Something in this seemingly abandoned hulk of memory was turned on, something else besides emself was making noise.

Ey was about to head down to the pit to check on the snakehead, the terminus for all of the microphone cables or wireless receivers that stretched up to the board, when ey caught sight of a sheet of paper, folded in quarters, tucked between the side of the board and the wall of the booth.

AwDae plucked the paper free and unfolded it, then held it under the red light of the booth lamp to get a closer look at it.

There, in tiny print, was a good chunk of the content of the vcard ey had created earlier that morning to add to Sasha and Debarre's deck. Cicero's DDR ledger, containing transactions that comprised votes made, bounties collected, and comments posted.

A note, though. Doubly weird. The paper didn't act like a normal vcard. No menu, no ACLs ey could sense. And yet the closer ey looked at the paper, the more the data seemed to unfold, fractally nested and apparently infinitely deep.

Ey blinked, and the moment passed. The note once more contained only tabulated transactions.

Frowning, AwDae refolded the note and stuck it into eir trousers' pocket. A small scrap of the outside world stuck in this elaborate fantasy.

%%%%%
\chapter*{Ioan Balan\#c1494bf — 2305}

Ioan sat back and rubbed at eir eyes. Time had gone all funny with all this research.

As with many of eir previous projects, ey tended to fall into a state of free-running sleep patterns and distractedness. Ey would work for a few hours and suddenly get quite tired, nap for what felt like fifteen minutes and wake up three hours later. Then ey'd work for twenty hours straight, neglecting to eat.

Ey had researched it and entertained the idea that it might be part of some larger sleep disorder, but had put it off as just one of eir (many) neuroses.

Less than healthy.

There were never any complaints about the quality or amount of work ey got done while free-running. Ey didn't slip up or stumble, and being methodical got one quite far as a historian and writer. Ey would write the same quality work at the beginning, middle, and end of eir waking periods.

What it did \emph{not} do, however, was endear oneself to one's housemates. Ioan\#tracker quickly grew frustrated, whether or not Ioan\#c1494bf used a cone of silence. Ey knew the feeling well. It was a common enough problem when multiple Balan instances stayed in the same house while on projects, and ey was nothing if not a Balan.

Ey considered digging a new spot for eirself to work, until ey had remembered Dear's invitation.

So thats how ey had found eirself rubbing eir eyes in front of a simple (if painfully modern) desk in a studio apartment attached to eir\ldots{}employer's? Friend? Eir friend's (equally modern) house.

The apartment really was a studio apartment, too: someone --- perhaps Dear --- had used it for painting, and rightfully so. The exterior wall was floor to ceiling glass looking out over that sere prairie. The landscape, Dear's partner had explained, was the work of Dear's sib, Serene; Sustained and Sustaining, `born' when their ancestor, Dear The Wheat And Rye Under The Stars had forked to explore its twinned interests of forming oneself and the of forming one's surroundings in greater detail.

Ioan's head spun whenever ey thought about the clade, but the longer ey spent around Dear, the more ey found eirself liking it. Ey was curious to get to meet another Odist.

If it weren't for the window, opaquable, the apartment would've felt totally like a cell. Simple cot, Desk, and kitchenette. The walls were whitewashed concrete, the floor that same pale hardwood, the fixtures all brushed steel. No doors to the rest of the house, nor even anywhere but outside, no restroom. One was expected to either turn off elimination or do so outside.

\emph{There's a cheap joke to be made there,} ey had thought, when first moving in. \emph{About Dear lifting its leg against some tree, but I doubt its body ever had that functionality enabled.}

Ioan shook eir head and rubbed at eir eyes more vigorously. Ey was daydreaming --- eveningdreaming, actually --- and that made em wonder how long ey had been awake.

``Probably some horrid number of hours,'' ey mumbled to the wall.

A sensorium ping, a gentle impinging of Dear upon eir senses, half-sensed words, \emph{``Does the wall reply back often?''}

Ioan spun around. Dear was standing, prim, dapper as always, at the door through the glass, paws clasped in front of it.

``Scared the hell out of me!'' Ioan blurted.

Dear's serene smile widened into a grin. \emph{``Sorry, Ioan. I'll wait until after the wall responds, next time.''}

``Jackass.''

\emph{``Foxass,''} Dear corrected, accenting that with an exaggerated swish. \emph{``Have some news. Care to walk with me?''}

Ioan nodded and stood, ``Glad to. Hitting a wall, here.''

The fennec adopted a look of concern, \emph{``Don't hit your friends, Ioan.''}

``Ha ha,'' Ioan rolled eir eyes. ``Something's got you in a state today. Tonight. Whatever.''

\emph{``Tonight.''} Dear's smile softened, \emph{``Come on, let's go walk. Storm scheduled in an hour, let's catch all of the nice smells.''}

%%%%%
\chapter*{AwDae — 2112}

The pit revealed little.

There were twenty boxes set on a table in front of the snakehead. Twenty receivers for wireless mics. Twenty cables neatly velcroed together into a bundle, contracting from the boxes arcing catenary toward the dull grey plug-box. From there, the cables were reduced to a four-by-five grid. The cables arched up above the snakehead before plunging into it, XLR heads buried in XLR nests.

All of the boxes on the table were dull. Mute LEDs simple bumps on their surface. Dark. All but one, that was. The first one. The one with a piece of masking tape on its face scrawled with a `1'. That box had a single red light on the front, indicating that it was powered on, and a single green light, indicating that the corresponding mic was transmitting.

``Great,'' AwDae murmured. ``That leaves only half of the school to search.''

If it had been a wired mic, the search would have been over as soon as it started. The cable would've been plugged into the snakehead, and by following it until ey reached its end, there would be the mic.

And what?

There would be the mic, and ey would still be stuck in some parody of a nightmare. All dressed up for the high school performance and here, see? The auditorium is completely empty.

The fox barked a laugh at how many cliches littered the situation. Turning away from the receivers, ey rested eir weight against the edge of the table on which they were placed. Ey leaned a moment, then hiked eir backside up onto the familiar surface, relishing the squeak of stressed metal from eir sudden burden.

AwDae swung eir legs back and forth, hearing the table creak and groan in time with the slow movements. The sound was quiet, but in the dread silence of the auditorium, more than enough to fill the hall.

Ey stopped.

The hall was pleasantly wet: not damp or anything, but in terms of echo, it had just the right amount. Or, at least, as much as a high school auditorium was willing to muster. Had it been dry, the sound would've died away completely. The drier a room, the closer it got to approaching an anechoic chamber, a room lined with material such that it would reflect zero sound.

But neither did the sound bounce back endlessly like an echo chamber.

AwDae knew this hall, even years later, even in dreams. Ey knew the pockets of good sound and bad sound scattered throughout the seating. Ey knew the dead spots on stage where one's voice would fall flat if it weren't amplified. Ey knew how the stage was built rather like a horn, with the performers at the small end, so that their sounds were projected out toward the audience. Ey knew how the stage was built like a drum, the pit a chamber of its own.

And yet, there was that slight echo of the squeaking of the table.

An idea. A crazy one, sure, but by this point with despair nipping at eir heels, a crazy idea was better than none.

\emph{And}, a bitter portion of em reasoned, \emph{if getting lost is permanent like they say, I've got nothing to lose.}

Ey hopped back off the table and began to pace.

The squeal of feedback in an audio system is an emergent behavior, and even those who have not heard it before know immediately that something is wrong when it crops up. It begins a quiet hum in the background, builds exponentially.

It doesn't take long before it can be understood as something originating in the system, rather than coming from the speaker or performer. From there, it builds on itself, feeding back into itself, until it quickly overwhelms all sound coming into it. Rises, crescendos. Hearing and speaker damage equally likely if left unchecked.

Similar, in an upside-down sort of way, to the echo that AwDae had caused making the table squeak beneath eir weight. Sound was picked up by the microphone, transmitted through the sound board, then out into the room. Amplified, though, through the speakers.

If the microphone started to pick up sound from the speakers, though --- and sound was sound, the mic cared not where it came from --- that sound would loop through the board once more.

A feedback loop. It would continue to build through further and further iterations, until the auditorium was filled with a roar of the one pitch the microphone had first locked onto.

Dread and dire. Cursed. An eternal struggle.

Obviously, microphones were still in use. They hadn't been abandoned because of the loop, since there were plenty of ways around feedback.

One could angle speakers toward the audience, rather than the stage. Bodies were notoriously bad reflectors of sound. Part of what made the stage so acoustically dead, that. One could also turn down the monitor speakers facing the stage, but that was cruel to one's performers. One could turn down amplification, but that defeated the purpose.

The usual solution, then, was gain.

The simple adjustment was given a knob at the very top of the sound board governing the sensitivity of the mic. At the top, befitting its importance in the setup.

Turn the gain all the way down, and the mic was a dumb lump of metal and plastic. Turn it all the way up, and the mic picked up everything from the movement of the air to the slight hiss of the live sound system. Almost instant feedback.

AwDae turned up the gain almost to the point of feedback. If ey could make noise in various points throughout the auditorium, maybe it'd get picked up. The more feedback ey generated, the more sound the mic was picking up. The more sound it was picking up, the closer ey was to it.

Eir possible locations for the mic hadn't been reduced. It was still half the school, but eir chances would go up. If the mic was not in the auditorium, ey could turn the main system up and start venturing further afield. Leave a door open, let the mic hear. Let em hear the theater ring like a bell in turn.

Riddles. Triply weird.

AwDae felt stupid. Insulted. Trapped for life and still solving riddles. Hopelessness dimmed eir vision.

Ey shook eir head, ears laid flat. ``At least it's something.''

%%%%%
\chapter*{Dr Carter Ramirez — 2112}

``Avery. What's up?''

The ping had sounded in Carter's ears like a soft bell, and the faint outline of a door had appeared at the periphery of her vision. Someone had requested a meeting. After a moment of dictating a note to herself for when she got back, she made her way through the door. One of the stats-and-history folks stood, waiting with arms crossed, in the private space.

``Running up against a bit of a snag, Dr.~Ramirez,'' they said. ``This new patient, uh\ldots{}0224ebe8?''

``What about them?''

``Well, I'm getting some doubled records. Weird things are duplicated.''

``Wait, duplicated?''

``Yeah. We've got some records with a different gender marker on them and no pronouns.'' They looked thoughtful. ``I ran into a bit of that when I changed everything over, myself, but the process changed across all of my past records, too.''

Carter frowned. ``So e8 changed their marker and pronouns officially, but you're seeing duplicate records under a different one?''

``Mmhm. I was wondering, do we have any location data on them?''

``Not really, no. You've got all the same data I do. Most have been redacted.''

``I figured, yeah, but wanted to ask. I just know some friends back in America ran into similar, too. Some ancient conglomerate or something holding onto old records or not updating their systems or whatever, so I was wondering if e8 was over there.''

Carter shrugged. ``I don't really know. That sort of thing is scrubbed before we get the cases. I'm actually surprised the files weren't normalized before we got them.''

Avery laughed. ``We're one of the big three, so of course it's all extra difficult.'' Carter must have looked nonplussed, as Avery continued, ``Banking, government, and healthcare. Ask any one of the big three to adopt to social change, and you'll get eighteen different reasons why it's impossible to update their systems.''

``Fair enough. So they have two markers and no pronouns.''

``Well, ey has two markers, X and M, but only the one set of pronouns. None listed on the records with the M marker.''

``Is this going to be much of a problem?''

``Don't think so,'' Avery said thoughtfully. ``The records are complete so long as we take both sets into account. You might want to run it by Sandra, though, is the thing. I don't know if us knowing that this change occurred is too much information for us to have. Legally, I mean.''

Carter knit her brow. ``And there's the snag.''

Avery nodded.

``Well, hopefully not.'' Carter leaned against the wall and thouht for a moment, then asked, ``What can we do with this information, anyway? We've seen a pretty good spread across gender markers with our set of cases, do you think this'll change anything?''

``I don't know. The friends back in America who ran into this were all ones that made the change later in life. The younger you are when you change markers and such, the easier it is because the less of a record you have to change. It's kind of like you're burdened with a marker from birth, and the longer you go before changing it, the heavier the burden gets.''

``And they had a big one?''

``Not so big, all told, but it's enough that all of eir records from when ey got eir implants are under a different marker.''

Carter nodded.

``From a history standpoint, that also means that eir marketing footprint takes something of a hard left at one point.''

``When th--'' Carter backtracked. ``When ey changed eir marker?''

It was Avery's turn to nod.

``So we've got someone who's advertised to with a masculine marker, then with a neutral marker--''

``And ey seemed to have given the whole romance thing a miss, too. Eir marketing footprint is mostly just rig gear and furry stuff. It's like they slipped through filters unnoticed.''

``Well, if you can't sell em sex, what's left to sell?'' Carter laughed.

``Oh, plenty, I assure you. Just that, pushing nine billion, advertisers mostly rely on larger demographics. GQ folks and asexuals aren't broad enough segments to bother wasting ads on. Granted this is only going by the transparency reports. There's all sorts of weird guerrilla marketing going on these days.''

``Yeah, fair enough. Any similarities with our other furry?''

Avery shook their head. They swiped their hand to the side to bring up a snippet of desktop, dug through a few decks of vcards. ``Being a furry seems to be the big thing they have in common. e8 is X, d7 is M. e8 is single and not looking, d7 is in a long distance relationship. d7 is almost a parody of a DDR junkie, e8 has almost no\ldots{}well, hold on.''

Carter waited.

``Looks like ey were prodding around the DDR spaces a few hours before the event.'' Avery had that far-away look to their eyes that one got while digging through data on cards. They shook their head to clear their vision, smiled to Carter. ``Sorry, looks like I've got a bit of work ahead of me on that end. Any thoughts on the snag?''

``No, carry on as you were, I think. Sandra will keep an eye on it and let us know if we're at risk of overstepping our bounds.''

Avery nodded and stepped back out of the meeting cubicle.

Back in the sim proper, Carter watched as the cards surrounding 0224ebe8 began to sift into two piles as the shadowy form that must be Avery worked. White cotton thread began to string itself into two groups, followed by the tags `0224ebe8 (M)' in one and `0224ebe8 (X)' in the other.

After a few minutes, she paced back to her constellation of decks. On a hunch, she created a small grouping in her area and labeled it ``DDR Activity Pre-Event''. She began looping in relevant cards from both 0224ebe8 and aca973d7.

There was a soft \emph{ding} within the sim, and a wave of shadowy heads looked up, Carter's included.

Directly above them in the middle of the `ceiling' was the current time in faintly luminescent letters. As always, they would look different for each member; for Carter, traced out in fine cotton string was the `12:00' that indicated lunch.

Carter's vision began to dim. She backed out before the ominously cheery message instructing her to stretch her legs urged her to do so. University policy stated employees should work in a sim no longer than five hours in a row without fully backing out, so when she pulled back from her rig, she saw everyone else doing the same.

Most of the team gathered around the fridge and microwave by the coffee station to collect their lunches. She hadn't had the time or energy this morning. Lunch out it was.

At least she wouldn't be alone. There a few folks who made their way across the street from the campus building to the shops, hunting falafel or curry. She put on her best chummy face and tagged along with. The group chatted, inevitably but amiably, about work, comparing notes on the cases they were focusing on.

The group --- three of them, with Carter --- decided on a small Vietnamese place nearby. It would be a long lunch, with the wait and all, but she was promised that the food was amazing. Besides: Friday. Even the boss can enjoy a lunch every now and then.

Standing outside as they waited on a table, they made an obvious target for the tabloid sellers. They were wandering a little further than usual from the tube station entrance today, and the restaurant hadn't noticed them yet to shoo them off.

Carter rolled her eyes when Prakash bought a copy.

``Hey, don't look at me like that. I promise I read it for the laughs,'' he said.

Carter shrugged, ``It's less about why you reading it, and more who you're giving money\ldots{}''

Prakash and Aiden stood in silence, eyes on Carter. They exchanged glances before Prakash broke in, ``Hey boss, you doing okay?''

``Can I see that?'' She didn't wait for an answer before she snatched the flimsy paper from his hands.

\begin{quote}
\textbf{Soho Theatre Mourns Lost Tech}

RJ Brewster was the pride of the Soho Theatre Troupe's tech department.

The brainy American who blessed them with boosted bass was admitted to the University College Hospital after apparently getting lost during a rehearsal on Thursday. Ey was discovered during an intermission completely unresponsive. Medical crews declared em lost on the scene after analysing eir implants.

The genderqueer young man was described as ``bright, but obsessed.'' Ey was a member of the furry cult and spent most of eir time on the 'net, which friends blame for em getting lost.

The STT promises that productions will go on as planned, with back-up techs running the sound system.

Brewster represents the 135th case of the lost marked in the world. Ey will be cared for by doctors at the UCH. Members of the University College London studying the lost were unavailable for comment.
\end{quote}

Carter let the paper droop. Aiden retrieved it before it was closed completely, opening to the page where she had been reading.

``Oh, hey! Stuff about a lost person!'' He read down further, then looked up at Carter. ``Did you get an interview request from them?''

She shook her head. ``Not a word. Not to me, at least. Maybe PR turned the interview down.''

Prakash read over Aiden's shoulder. ``Do you think we could go see em? We're with UCL. Maybe we could--''

He fell silent at a look from Carter. She spoke carefully, voice carrying the weight of a prepared statement. ``Ey's in good hands. Trust the doctors on this. We'll receive all relevant info from them. Any contact with a patient may introduce bias in the study.''

Aiden frowned. ``We shouldn't have this.''

``No, we shouldn't.''

He quickly balled up the tabloid and, finding no rubbish bins nearby, set it on the restaurant's outside windowsill. Researchers were as jealous of their data as the lawyers were of patient privacy. Keeping the tabloid would only be a risk.

``But what about the theater troupe?'' Prakash asked.

Carter caught herself in the act of shaking her head, turned instead toward the restaurant. She tilted her head back and let her eyes trace the sharp contrast between the gutters of the building and the steel-gray sky, seeing neither.

``We can't,'' she finally murmured. ``Same risk of bias.''

A safe answer. A rote one. A required one. The legal aspect was plain, the ethics clear. If she wanted to learn anything from the doctors treating this RJ or the Troupe, she'd have to file a request, wait for the ethics board, wait again for the lawyers, and even then, even if she succeeded, she would only be able to write a questionnaire for them to fill out.

And yet here, a half hour tube ride away, was a social connection. The very thing she wanted most to understand.

She was distracted, thankfully, by the host inviting them in to eat.

%%%%%
\chapter*{Qoheleth — 2305}

\noindent It had been long enough that I was thinking of myself as Qoheleth now. I had even begun introducing myself as Qoheleth, whenever I went out, just to try it on for size.

That I had never gone out was of little concern.

I liked the sound of it, though. I liked the connotations of `teacher' and `gatherer' and `director of the assembled'. I wanted to feel the way that it felt to be someone different, and I'd found at least a part of that in this name, the name that \emph{I} had chosen for \emph{myself}. I'd not yet taught or gathered, but I was working constantly to attain that.

And `Hebel'. Hebel was another name I had picked up. Vain, futile, mere breath.

Qoheleth's words, in the book they had written so very, very long ago were all about hebel --- or hevel, could never tell which. ``This, too, is meaningless,'' the author had written, after taking a walk down a path in life and exploring.

That's not how I envisioned the name, though.

I thought of the two names as signifiers. Thought of the two \emph{sources} of names.

Qoheleth. That was the name I had given myself out of hope. It was a name of goals and aspirations. It embodied the things that I wanted to do. It took all of my plans and me, as the maker of the plans, and bound them up neatly into a word. A name. A rejection of The Name.

Hebel was the name I had given myself out of despair. It was a name of self degradation and a way of reminding myself that, lofty as all my goals may be, they were all vanity. Mere breath.

Together, the names reminded me that I was doing this for a reason. All of these resources, mostly found objects and hand-me-downs accrued over the years (if you never leave your private sim and never publish outside of it, you get surprisingly little), were being built up and strung together into a cohesive goal. A net.

They, the resources, were all nothing. The reasons were all nothing.

The whole plan was nothing, except for the truth underlying it. Not to fear God, but to\ldots{}to something. To get the whole clade to see. My clade.

My \emph{old} clade.

I was now Hebel Qoheleth.

Hebel Qoheleth.

The old name was dead. I was Hebel Qoheleth.

% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %

%%%%%
\chapter*{Ioan Balan\#c1494bf — 2305}

Dear wasn't kidding about the smells. Ioan turned eir sensorium way up in intensity. Ey wondered if Dear's vulpine nose could smell things eirs could not.

Serene had worked wonders here. The smells, the textures, the raw beauty of the place. It was a fine line that they had walked, too. Any further in one direction and the landscape would have become nearly desolate, more forbidding than natural. Any further in the other direction, though, and it would've been softened too much, would've become too well-tended, or even cartoonish.

As the two crunched their way through the short, stiff stalks of grass, winding their way around the larger tussocks, Ioan realized that ey was quite taken with the place.

A ridiculous house in the middle of nowhere, a glittering white fox and its partner, the prairie fading off into downs on one side and stretching out to infinity on the other\ldots{}It had all seemed so contrived when ey had first visited. Too simple, too one dimensional. Kind of cheap.

But it was all so well done. So incredibly, skillfully executed. The artistry was in the details.

Ioan liked it here.

Ey realized ey had been dawdling, past the comfortable stage of just enjoying the petrichor being washed in before the storm.

``Sorry, lost in thought.''

\emph{``It's okay,''} Dear said. \emph{``You looked like you needed it.''}

``Hmm? Getting lost in thought? Or getting out of the apartment?''

Dear shrugged, smiled.

``Sorry, anyhow. I'm here now, will try not to do that again.'' Ioan grinned sheepishly. ``What did you find out? You seemed almost punchy.''

\emph{``I was, definitely. Still am.''} The fox grinned and shrugged again. \emph{``We seem to have found out who our\ldots{}ah, who our target is.''}

Ioan mulled over the word `target', searching for a better one. Ey couldn't think of anything better, so ey nodded. ``What do we know?''

\emph{``We know a name, and from there we can find a bit of history, which you may be able to help in filling in.''}

``Names are good! Something other than Qoheleth?''

\emph{``Other than that, yes, but almost certainly connected, probably the same. Not much more than the name, though. No location, no sightings in ages. Some aging --- or aged --- resources, a name, and some history.''}

Ioan gave an impatient gesture with eir hand. ``Well, what's the hold-up?''

Dear grinned broadly, \emph{``The hold-up is that I want you to feel some of the excitement that I felt on hearing this from down-tree. I want you excited and invested.''}

``I've been working twenty hour days on this, I'm pretty fucking invested.''

The grin turned into a laugh. \emph{``I know you have. My partner's worried about you.''}

Ioan felt eir cheeks flush, ``Sorry, I didn't mean to be a bother being up so much.''

\emph{``No, no, we can't hear you or anything. They're just worried because we \textbf{don't} hear you, or hear from you. We both like you.''}

The historian nodded, chastened.

\emph{``Don't worry about it, Ioan. It's all good.''} Dear patted eir shoulder. \emph{``The name, though, the name is the important thing right now.''}

``And the name is?'' Ioan's mind raced. Could Dear say the name? Was it the poet, some how miraculously talking through the system? That would be exciting, wouldn't it?

\emph{``Life Breeds Life, But Death Must Now Be Chosen, of the Ode clade.''}

Ioan froze.

Dear stopped a few paces in front of em and turned, grinning intently at em while its tail lashed excitedly behind it.

``They\ldots{}what?''

\emph{``Good,''} Dear's grin widened. \emph{``I'm glad I'm not the only one who had to pick their jaw up off the ground.''}

Ioan stuffed eir hands in eir pockets. Brought them back out to press against eir forehead. Crossed eir arms. Returned eir hands to eir pockets. Suddenly anxious. ``It's a real the-call's-coming-from-inside-the-house moment.''

Dear tilted its head, ears perked.

``Never mind. Old trivia.'' Ioan shook eir head and rocked back on eir heels. ``How, though? How'd you get the name?''

\emph{``A hunch I had, actually, though someone else dug it up.''}

``What was the hunch?''

\emph{``Signifier.''}

Ioan rifled through eir mental notes on the project. ``Signifier\ldots{}from the first encrypted note? Signifier is the password something something?''

Dear nodded, \emph{``Hardly anyone uses it anymore, but signifier used to be what we called the names of long-lived branches. It's still used here and there among older clades. I use it now and then, when I can get away with it.''}

``Makes sense, yeah. So they're\ldots{}''

\emph{``They're an Odist, yeah. Way, way down-tree. One of the first instances.''} Dear's smile faltered, \emph{``We weren't very good at record keeping back then. We aren't really now, to be honest, but the system's better. We\ldots{}we didn't know that he was still alive.''}

``Didn't know? I thought you all talked to each other. You must, in order to keep the names straight.''

\emph{``Remember, all of our names are chosen from our stanza. I talk with the other nine within my stanza fairly frequently, and we may fill out the stanza before too long.''} The fox's expression grew glassy, \emph{``Life Breeds Life\ldots{}that's the first stanza. They're a conservative bunch. Only know one or two, but I assume that others are out there.''}

Ioan nodded, ``So the first stanza were the first forked?''

\emph{``The first line from each stanza were the first forked, back when it cost to fork. Like, cost real money. Anyway, the first fork of the first stanza must've just been a little more conservative than the rest of us.''}

``I\ldots{}hmm. May I ask something potentially personal?''

Dear nodded.

``The Odists that don't want me digging into this too much, the ones you didn't really tell, are they from that side of the clade?''

The fox's ears perked, \emph{``To the last, yes. Why?''}

``How will, er\ldots{}''

\emph{``Life Breeds Life, But Death Must Now Be Chosen. Just Life is fine, too.''}

``How will Life react to the search? To me?''

Dear shrugged and turned its back on Ioan.

The historian stood where ey was and watched as the fox took a few steps further out into the prairie, crossed its arms and stood, staring up into the bruised-looking sky. \emph{``To the second bit, I don't know that it matters. They --- Life, or Qoheleth, or whatever --- are one of us. And even those of us who didn't want any outsiders brought on board are only frowning, looking down their at the thought, not gathering up arms.''}

``And to the first bit?'' Ioan pressed. ``What do you think they will think of the search?''

\emph{``What do I think? Or what do I feel?''}

Ioan scuffed eir foot against the grass. The temperature was dropping out on the prairie. It'd be an inconvenience to have to slosh back to the house if it rained.

``Both.''

\emph{``I think that they'd probably get a kick out of it. I am, several of the others are, and the ones who aren't just don't care that much or are too angry.''} Dear turned back around. Its arms were held tight against it's front though whether from cold or emotion, Ioan couldn't tell. \emph{``As for what I feel, I feel that it's their game. They're the ones running it. But even if it's a game, it's not play. There's no real fun in it, just snarkiness. It's a game they've worked at perfecting.''}

Ioan marveled at the change in Dear, though with these deeper thoughts, ey felt some of the same.

The fox's smile was weak as it added, \emph{``They have designs. Designs and reasons.''}

Ioan and Dear trudged back to the low block of concrete, a bunker against the storm, as a chill wind swept away the petrichor and brought with it the rain itself.

%%%%%
\chapter*{Qoheleth — 2305}

I loved this feeling. I loved the feeling of a project getting past the architecture state to that point where you could just start to use it. You'd been writing all of the interfaces and abstract classes and such for weeks and months (or decades, in my case). Then you'd started to fill in all of the inner workings, blocks of code filling out empty pairs of braces.

And then, one day, you had enough that you could type in a command and see if it actually compiled, ran.

And then you'd probably buckle down and start writing tests, start pulling together tasks and issues and such. No such luck for me. Old Qoheleth --- I still get a grin every time I say that --- gets to just keep writing until it's time to hit the big green button. There's no testing, there's no explaining if things go wrong. Just go.

I was actually pretty excited about it.

You get old, you know? And you can't die in this place. You can suicide, maybe, crash yourself and try to corrupt the merge, and I guess if I were to quit, there'd still be someone to merge with, but they'd be dealing with the same problems.

No one ever really dies in the system. They just stop.

And I'm sure one of those will happen to me at some point, and probably sooner rather than later, but until then, I'll just keep going more and more nuts. We all will. All of us old'uns, and then before long all the young'uns too. We gotta see. They all gotta see, but we gotta see, because we're the ones in a position to do something about it.

I keep using `we', too, damnit. I'm not part of their damn clade anymore. I don't know which of them are or aren't, either, and I don't think they realize that yet.

I just need to keep working on what I can. I kicked Node: {[}67e97446cdbe3a4a3cfd5ebd75b1260{]} out into the wild, so they'll probably get there before long. After that, we finish our little game and I get my moment as Qoheleth. I get to be the one to call the assembly together, the one to teach.

And, since I know they'll get into these nodes, too, I have to add that, no, I don't bear a grudge. There's no ill will. This isn't a ``now I'll show them'' moment.

I just need them \emph{invested}. I need them fighting, which is easy, and I need them interested, which is hard. I need them invested in the problem before I stand up and clear my throat, and then I might have the authority, in their eyes, to speak, to teach.

I got them fighting by saying That Name, and I've got Dear interested. Lovely Dear.

I just need them all invested.

%%%%%
\chapter*{Ioan Balan\#c1494bf — 2305}

Dear's partner had cooked that evening. They were good at it, so Ioan sat with them around the table and tried not to feel like a third wheel. Eating was not a necessity in the system, of course, not by any stretch, and while it was easy to go for months or years without eating, it was something that remained a habit for many of those who chose to upload. Ioan suspected that there was no small amount of hedonism involved in killing one's body to upload to a world beyond scarcity.

All the same, it was a muted affair.

Dear and Ioan had made it back to the house just as the first cold sprinkles had started to fall from the sky. Once they'd reached the patio, they took the chance to stand and watch, just out of reach of water, as the weather went from cloudy, through sprinkles and drizzles, to stormy. Ioan focused primarily on the sound, the way ey was able to pick out the individual sounds of droplets striking dry grass during the sprinkles, to the static of the drizzles, to the rush, roar, and whoosh of the storm itself.

Ey had no idea what Dear was thinking. It stood, watching the rain and shivering. It looked more contemplative, but was somewhere less than sad. Ioan spent a moment sifting for the word, before giving up and guiding the fox back into its house.

Ioan felt some energy return with the mix of curry and masala and rice. Calories would've been an empty term here, but that's what it had felt like: like eating a hearty meal and regaining strength. Likely, it was just the simple act of going back to where ey had been in the prairie when first heading out there. Engaging with one's sensorium. Maybe that's why the idea of food had been included in the system, after all.

Dear picked up a little with the food, but not as much Ioan had, nor, perhaps, as much as its partner had hoped, judging by their own apparent anxiety. Dinner was good, but plagued with silences. Even after, as the three sat talking, their conversation was full of nothings.

It wasn't until they poured some drinks and moved to the couch that Dear began to open up.

\emph{``I script a lot of my conversations,''} it said, staring into it's `glass'. All of the glassware in the house was wide-rimmed to make way for a fox muzzle to lap, having little in the way of lips. Ioan felt strange drinking wine from something more akin to a bowl

Ioan looked up. ``Mmm?''

\emph{``I was just thinking.''} It shrugged, giving it's wine a squirl and then a few laps. \emph{``Earlier, when I was sharing that bit about the name with you, I had that all scripted. It was all pulled together in my head. The whole thing. I'd make a few jokes, lead you on, tell you the name, and then we'd bask in the wonder of the truth of it.''}

Ioan nodded, silent.

\emph{``Just like I spent dinner scripting this conversation.''} Dear's partner gave its shin a playful kick. The fox grinned.

\emph{``It's thoroughly ingrained. I'm pretty sure most people do it, of course. It's just,''} it sighed. \emph{``I had the whole thing scripted and planned, and then you asked questions --- as you are meant to, of course --- and my script collapsed.''}

``I `went off script', you mean?''

\emph{``Mmhm.''}

``Sorry about that, I-''

\emph{``Oh goodness, no!''} Dear laughed, shaking its head, \emph{``I'm trying to apologize here, don't steal my thunder. I just meant to say that you asked good questions and got me thinking, and I wasn't expecting that.''}

``It likes to proclaim,'' teased Dear's partner.

\emph{``It's not \textbf{not} true,''} Dear grinned back. \emph{``But anyway, I'm sorry I got all quiet, I didn't mean to put a damper on things.''}

``You didn't, I-''

\emph{``I did, though. Dinner was like some depressing silent movie.''}

``Don't sulk, fox,'' its partner said. ``Dinner was fine. And let poor Ioan finish.''

Ioan grinned, letting the banter play out before continuing, ``All I meant to say was that I worried that I'd offended with one of my questions.''

\emph{``Not at all. I mean, not really.''} The fennec furrowed its brow. \emph{``I felt offended, is what I mean to say, when you asked how Life would react to you being a part of this investigation. An unfair reaction, though. Just one from the gut. I was offended because I realized that I'd invited you along on this as some sort of tool. Something I could wave about and say,''See, look what I have!" A tool or a trophy."}

Ioan looked down into eir wine, taken aback.

\emph{``Doubly unfair of me, and for that I apologize.''} Dear raised its glass. \emph{"So you asked a really good question, actually, because it made me question my own role in this hunt. It made me think of what others would think, me bringing along an amanuensis and historian, which made me think of why I'm doing so.}

\emph{``And I think the reason for me doing so goes further than even I had planned. I think I have you along as a means of keeping me grounded, of keeping the clade from just doing what the clade has always done yet again, of-''}

The fox stopped talking suddenly and set its glass down on the table. Its ears were standing erect and its fur bristled down along the back of its neck, hackles raised.

It looked frantic.

Ioan looked to Dear's partner, who sent a very faint sensorium ping in response.

Sensorium message. That was it.

The message lasted less than a minute before the fox leapt off the couch and dashed off to another room, forking almost as an afterthought along the way.

The fork turned quickly and paced back to the couch, looking anxious. It didn't seem to be able to sit, and instead kept up that pacing in front of the couch, before its partner and Ioan.

After a few tense laps, it said, \emph{``Qoheleth just sent me a message.''}

``What?'' Ioan rushed to place its glass on the table with Dear's. ``You mean Life?''

\emph{``He asked me to call him Qoheleth, but yes. He sent me a message. Can I pass it on?''}

Dear didn't wait. The message came in with a flash.

Highest priority, it came with a rush of adrenaline and a sensation of falling, sudden and intense fear replaced with an incongruously jovial voice. An old voice, almost Santa Claus-y. The contrast made Ioan's bones ache.

"Hi Dear, this is Qoheleth. Not Life Breeds Life, But Death Must Now Be Chosen, but Qoheleth. I'm glad to see that you've kept this up and gotten this close. Not sending this to deter you, but to cheer you on. I'm going to send you a bit more information --- just you, mind! --- and I want you to get the rest of the clade in on this, see if you can get them working with the same delightful fervor you and Ioan have.

"So anyway, here's the bone I'm gonna toss. You should be looking at Node: {[}32c5a64b66d0338be4373d796cf1eae5343f1077{]}. That'll get you right to my door. May need Gist Node: {[}0fedcbbb5e9839936ce799ece39fcd49{]} to help, too, though you already have the key, I think. I expect most, if not all of you, though, you understand? You're lovely, Dear, and I can't wait to see you and your friend, but I'd like to host as much of the clade as I can.

``I'm really excited for this, and I'm totally looking forward to see you all, yeah?''

There was a moment's silence, a sense of lingering, and then, "Oh, and thank you, Dear. You've made this a treat. You're the closest one to the thing I'm after, and I'm glad this tickled you as much as it did me. I think you and I both know why, too.

``Anyway, see you soon, fox. Cheers.''

The relative calm that fell over Ioan signified that the message had ended, and ey slouched back into the couch, eyes wide.

``Holy shit.''

\emph{``Right? Hold on, don't go anywhere. Going to reduce conflicts while I make the calls,''} the fork of Dear said rapidly, and quit.

Ioan shook eir head and said again, quieter, ``Holy shit.'' Ey reached for eir glass of wine once more.

``Bone I'm going to toss, hmm?'' mused Dear's partner. ``He makes it sound like a game.''

Ioan nodded and watched the fox's partner spin their wine glass by the stem between their two palms, watched the wine creep up the sides from centripetal force. ``It showed you, too, then?'' ey asked.

The figure laughed, ``Of course. I know I've not been hitting the books or the streets like you two, but I'm still in this. I was the one who pointed it to you.''

Ey nodded, feeling eir cheeks flush, ``Of course, sorry. Do you know what he meant by''closest one to the thing I'm after``?''

``Maybe. I only really have an inkling, though, and I'd rather let Dear explain.''

Ioan nodded again, ``That's fair.''

There was an uneasy silence for a few minutes. The two sat on the couch, sipping their wine and mulling over the message. For eir part, Ioan was considering the strange dichotomy of the familiarity with which Qoheleth had addressed Dear --- ``see you soon, fox'' --- as well as \emph{why} the fact that this seemed incongruous to em. It was difficult to think of Qoheleth as a member of the same clade as Dear, someone with whom Dear shared a root identity, after so long of thinking of this person as someone entirely different.

Silences have their own rhythms, Ioan knew, so it waited until there came a point where ey could ask, ``About all this, do you know much more about the whole name business?''

Dear's partner looked up, ``Who, Qoheleth's?''

``No, I mean the whole name of the poet.''

``Ah.'' They shrugged, ``Not particularly. I just know it's something the clade has an almost religious fixation on. Most of them, at least.''

``Do you know it?''

They laughed. ``Oh, gosh no. I mean\ldots{}well, do you know why Dear's a fox?''

``Why's that?''

``Because it likes foxes.''

Ioan felt as if ey'd stumbled. Dear's partner laughed.

``Seriously, that's true. But also, it was an experiment. I don't know The Name because I'm not allowed to know The Name, that much is obvious from the clade's reaction to this whole thing. But I also don't know The Name because I'm pretty sure Dear doesn't even know it. Not anymore.''

``How do you mean? I thought all of the Ode clade knew The Name, kept it secret and close to their hearts or something.''

``Many do, I've been told. And I think that Dear does this too, in its own way. That way means doing its best to forget it and to move on.''

Ioan nodded slowly, ``To get to the acceptance stage of grief?''

Dear's partner nodded. ``So it did its best to forget.''

``Is that something that one needs to work on, then?''

``Have you forgotten anything, recently?''

``I, well\ldots{}'' Ioan stopped and thought for a moment. It was a difficult question to comprehend, and more difficult to answer. How could ey know whether or not ey had forgotten something by going back through eir thoughts.

All the same, ey prowled through eir memories. Even just those from the time ey had been spending with Dear. They were jumbled, sure, and lots of impressions, but nothing was forgotten that ey could think of.

``I'll spare you by passing on some thoughts from Dear,'' said the fox's mate. ``We aren't gifted with eidetic memories when we upload, not by a long shot, but neither can we truly seem to forget anything we do remember, anymore. It's as thought each memory is labeled with a priority level from zero to ten, and when it hits zero, it's forgotten, except the actual scale only goes down to point oh oh oh oh one or something. We can kick it way to to the back of our minds, down the priority list, but we can't forget it. The system won't let us.''

Ioan nodded, realization dawning on em. ``So Dear tried to forget, tried to kick that memory all the way to the back of its mind. What does that have to do with being a fox, though?''

``Know much about exocortices?''

``Sure, I've got a few up and running for storing long term stuff. Hell, I've got one for this project. Isn't that kind of like forgetting?''

``Almost, but you can never forget that they exist, can never forget the passphrase, right?''

Ioan frowned, directing it to eir wine rather than Dear's partner.

``But exos also need part of your sensorium to match, right? That way you can't just tell someone your passphrase and let them in.''

Ioan nodded. Ey had a hunch of where this was headed.

``So Dear put The Name into an exocortex, all by itself, and then tried to change its sensorium enough that it couldn't get back in.''

``I see,'' said Ioan, sipping at eir wine again. It left em parched. ``It's a fox because it likes foxes, but that wasn't the goal. The goal was to no longer quite be the same Dear that put The Name into the exo.''

Dear's partner nodded.

``How did it do that? By forking?''

Another nod. ``Forking and mutating, forking and mutating. You can change your form easily enough, but it's much harder to change your sensorium. I don't even know how many times or tweaks it took. That's how it got into instance artistry, though.''

Ioan nodded, ``Damn. That's intense.''

``Dear's an intense fox.'' Its partner grinned.

``True enough.''

``It'll be back soon enough. Let me throw a question back at you, in the meantime. What are your thoughts on the last thing Qoheleth said?''I think you and I both know why``?''

Ioan settled back into the couch with eir wine and thought for a minute or two. ``I'm wondering if he was talking about what Dear did to forget the name. On one hand, it sounds like a sort of congratulations. Like,''I'm glad you're able to move on," but after all that talk of all the clade and all of what Dear said earlier, I'm not sure if that's the whole story."

``How do you mean?''

``Well, has Dear mentioned to you the more conservative side of the Ode clade?''

Its partner winced and nodded, ``Plenty.''

``It said that Qoheleth is from that conservative side. I wonder if that's not working out well for them.''

``Conservatism?''

``Yeah. Retaining all of those things from the original Michel Hadje, following a sort of Dispersionista path, but more in letter than in spirit. Dear called them batty.''

``It's called them that to me, too.''

``I'm just wondering if it's right,'' Ioan said, finishing eir wine. ``Maybe they are batty. And getting worse.''

% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %
% % % % % % % % % %

%%%%%
\chapter*{RJ 006}

It took AwDae just under two hours to find the microphone.

The first hour was spent searching the auditorium thoroughly. Ey searched by walking around clapping and humming, then singing songs half-remembered from productions ey had helped with in the past. Ey would've whistled if it wasn't for the structure of a canid muzzle. There was no way eir lips would manage to pull that off.

Silence.

After an hour, venturing even into the overhead areas where sound wouldn't reach, ey gave up and took a break.

Taking the slip of paper with Cicero's transactions from eir pocket once more, ey scanned over the titles of the initiatives voted on. There was very little there to latch onto. Or, rather, there was way too much. AwDae couldn't manage to even boil down the table into any single sentence, much less something useful. The cat had apparently voted on just about everything, without taking any breaks.

Eventually, when the rows started to blur into one another, ey levered emself up from the auditorium seat ey had chosen. Ey refolded the paper and slipped it back into the pocket before checking on the board once more. Everything remained set as it was before the break.

Venturing outside the auditorium, AwDae had imagined ey would work in concentric circle away from the auditorium. This turned out not to be the best idea. The theater was nestled between two arms of the school which did not meet. That made their routine fairly arduous. Ey'd walk down one hallway, poke into classrooms, and make noise before moving on. When ey reached the end of eir circle, ey had to jog around the auditorium through the student center to go down the other hallway and do the same

Eventually ey gave up on the concentric circle plan and started working from north to south. Ey worked through the entirety of one hallway, clapping and hollering, without hearing anything, before moving on to the area of the student center near the auditorium.

It was there that ey heard the first, faint hum.

At first, it had skimmed beneath eir attention, sounding rather like an echo from eir own voice in the cavernous space of the student center. When the open doors to the aduditorium caught eir eyes, ey tried once more, getting another faint hum that slowly died out as the space and air dissipated the tone.

It took another few minutes to find the microphone itself: a small bit of hardware resting delicately atop the door handle leading into the principal's office just to the northeast of the auditorium doors. It was surprising, in a way, that ey hadn't managed to trigger any feedback earlier, until ey realized eir mistake: ey would have to shout loud enough to be heard in the auditorium; without the speakers producing noise loud enough to make it back through the walls and reach the mic, there would be no feedback.

The door was labeled `Admin.', which was ominous. Although there was a head office at the front of the school, administration was where the principal and vice principals' offices were. It was one of those places that lingered in the mind of every student who had passed through the doors of the school. Getting called to the front office was usually bad enough --- a call from a parent!? --- but getting called to the admin office was worse still.

AwDae delicately picked up the microphone through mounting feedback before shutting it off, eir ears laid flat in an attempt to shut off the growing hum from the auditorium. The sound stopped a scant few moments after the mic was shut off, bouncing around the auditorium and the student center.

Ey pocketed the mic in eir trouser pockets and straightened back up, cautiously lifting eir ears once more. The school was once again silent. There was no hearing the hiss from out here in the student center. Remembering the position of the mic, AwDae wandered back over to the auditorium, turning the gain back down on the board and lowering the house volume. Ey even turned the mic back on and gave it a quick ``one-two'' to ensure that none of the speakers had been damaged.

\emph{This is a sim, and not even mine,} ey thought, ears tinted pink with a blush. \emph{What does it matter if a speaker blew?}

Ey shrugged it off after a moment. Habits were habits and there was no reason to break them now.

Wandering back to the admin office, tail swishing behind em, AwDae couldn't help but feel as though ey was trapped within a game, one of those first-person puzzle solvers that seemed to be forever popular. The fact that ey seemed to be receiving what amounted to clues while in an complex abandoned building only added to that.

Shaking eir head, ey turned the knob on the admin office and peeked carefully inside.

There were no traps, no jump-scares, just the six-sided room with its three doors on the opposite walls. One for the principal, and two for the vice principals. Taking the game metaphor to heart, ey started poking around the office where ey could, flipping through a datebook on the secretary's desk (empty) and rummaging through the drawers (office supplies). The waste baskets were empty.

Steeling emself for something shocking, with the game mentality still holding onto eir mind, ey tried each of the doors in turn.

It surprised AwDae that it wasn't the principal's office that opened, but one of the vice principals, though the name escaped em. The office was dark, but the lights responded to a touch on the pad, which ey sent to a comfortable level without being intimidating. Ey remembered being hauled into the room, all those years ago, with the lights all the way up, a gesture of power.

Rummaging through the desk revealed little of note. Rather than a planner on the desk, however, was a workstation; simple and, to eir eyes, ancient. It didn't respond to any of AwDae's interactions, though. Although how it would work, ey didn't know, ey had hoped that a connection like that might lead to a way back out of this mess.

The only other item on the desk was a scratch pad, and a pencil. They never seemed to go out of style. The pad contained a simple breakdown of costs, divided into departments, for the coming year. A simple three-column setup tallying subject, expense, and deductions from some number at the top which must be the classroom budgets. At the bottom of the page, was a final number, circled. Apparently, the administrator hadn't quite liked the result, for it was circled in dark, angry strokes.

AwDae flumped down in the chair at a bit of an angle, letting eir tail flop down between the arm rest and the chair's back so as to keep from crimping up uncomfortably. Tired, so very tired.

Ey rubbed eir eyes wearily, brushing away the sandy grit of tears already shed. Ey was moving in this search with determination, occupying eir mind, specifically so that ey wouldn't collapse into a depression borne of hopelessness and despair. It occurred to em that getting Lost was the perfect prison: complete freedom, or nearly so (ey had already fantasized about jimmying open the other doors), with nothing to do. Nothing to dream, nowhere to go, nothing to know.

Ey would go mad without a task. Ey could create, but why create in these empty halls? What would ey even begin to create that would matter the worth of a damn? Ey would never be able to share it. Ey would only be able to spiral inwards. Endlessly.

All AwDae wanted to do was curl up in the chair. It was comfortable enough, ey could probably manage to get some sleep in.

Instead, ey rubbed eir eyes once more and leaned forward toward the desk, letting eir eyes focus on the columns of scratched digits and marks on the sheet of scrap before em. Mindlessly working through the sums in eir head simply for lack of anything else to do.

``Hmm, that's weird,'' ey murmured sleepily out of the corner of eir muzzle.

The numbers didn't add up. In fact, everything added up within its own row, it was simply as though a row were missing.

Ey yawned and stretched before holding the sheet of scrap up to the light. There were no erasures, whiteouts, or anything like that. There was just simply not enough information.

Finally, the fact that ey was holding onto a ledger, such as it was, dawned on AwDae. If ey was meant to be looking for clues, then\ldots{}

Ey hastily fished the previous clue out of eir pocket. The ledger of Cicero's DDR interactions.

It wasn't nearly so simple as the scratch paper. For instance, each referendum had three different types of interaction: a cost, a bounty (if that referendum was referred back to the house), and any number of comments made on the issue, and they were often out of order on the sheet, given Cicero's habit of voting on everything.

Ey wished for eir workstation more than anything, as this would make the task almost trivial. Having to do without, ey snagged the half-used pencil and the rest of the scrap and worked it out. Each cost and comment would be a debit, and each bounty would be a credit. One could also buy DDR credits through a mechanism that basically acted as an additional withholding on one's taxes, and there were two of those in there, ensuring that Cicero would have enough DDR credit to make what AwDae assumed was some scathing political rant on an upcoming high-stakes referendum.

Even so, with all that work, it was clear that even the section of numbers on the paper didn't add up. Once more, there was a missing interaction. Three missing interactions, rather: one vote's cost, one vote's comment, and one vote's bounty, at AwDae's best guess.

The problem was that one's DDR records were public --- they had to be, for the system to work --- and, unless it had been tampered with (something AwDae had to take into account), eir was a combination of 1,252,000 credits unaccounted for in terms of transactions. One million debit to the comment, a quarter of a million credit for bounty, and two thousand to the vote cost.

AwDae tore off the top sheet of scrap and, working faster this time, ran the numbers once more, only to receive the same result.

``Well, huh.'' Ey sat, stunned, for a little while longer before gathering eir notes and folding them together with the original clue and stuffing them into eir pocket. Ey couldn't create a deck here, but ey could sure take items with emself.

If this all had something to do with what was going on outside, where ey was counted among the Lost, that was all well and good. But, how would ey get that information back out.

It was probably too early to be thinking of such things. Ey wasn't going anywhere for the time being. Sleep was taking too strong a hold on em. Ey gave token consideration to where ey would be able to sleep before deciding on the auditorium. The fold-down seats were cushioned, but not very well. All the same, the place had a sense of home about it. Perhaps the day to come would help em learn more.

%%%%%
\chapter*{Dr Carter Ramirez 004}

Carter hadn't meant to dodge her subordinate's question. They truly did need to go in to eat.

The food was, as promised, delightful, and Carter made a mental note to come here more often for more good Vietnamese food. That note, however, was filed by her mind and set aside so that she could work through the implications of what had been spilled to her by the tabloid.

She couldn't visit this RJ any more than she could fly out of the second story window here and back to her lab. There were several factors keeping her from doing so.

First, and foremost, it was useless. Her team didn't \emph{need} access to the Lost to do all of their work, because much of their vitals was provided as a real-time stream of data into the work group. Besides, it had been proven that physical contact registered little, if at all, to the Lost.

Secondly, there would be people between her and RJ. Not just doctors and nurses, but her own administration. She would have to go through any number of people just to get access to some variables that likely wouldn't help her investigation at all, such as eye color or hair color.

Finally, there was the law. Carter understood the purpose of WFPHIPA: the Western Federation Personal Health Information Protection Act. Hell, she had voted on it, herself. It was something she felt strongly about. The tabloid had technically breached that (though there was no culpability) by informing her that there was a good chance that one of the group they were studying was this RJ.

There was, however, nothing to stop her from going to a show in the next day or two.

Feeling very much the sleuth, she stuffed a small egg roll into her mouth with delight, savoring the taste of it.

Yes, she'd go to a show up in Soho.

With her resolution planted firmly within her, she found it much harder to make it through the rest of the day. Rather than wrangle the two competing strands of the work group into some cohesive goal, she spent much of her time distracted. She was thinking about all of the ways in which she could possibly approach the cast or crew. Would she be able to even get in contact with any of them? Supposing she would, what would she even say? ``Tell me about your sound tech''?

Eventually, though, the rush had worn off. Toward the end of lunch, she had purchased tickets (at no small cost) and been hyped up about visiting the theater. When the afternoon started to wear on, she found herself once more tied up in work.

Avery and Prakash had both settled into the routine of investigating what had gone on before the incidences of the Lost. Avery was collating what data they had from each case on the social front before the subject had gotten lost and searching for social connections between each of the cases. Prakash, meanwhile, was digging through biochemical data that had been collected from each of the patients and searching for similarities for them, based specifically on the time before they had gotten lost, rather than during or after.

Carter had supposed that this would be innocuous enough, but it seemed that Sanders had taken the opportunity of the boss dining out for lunch to chat with a few of the other members of the workgroup. Not once, but twice while she was working, she had fielded private messages from some of her teammates. Both had concerns around the direction of the project, and questions about the wisdom of separating the work group into smaller groups.

In both cases, she reiterated that this would be another temporary investigation. If it turned up any useful information, then they would have that conversation again in the near future. If it didn't, then everyone would cohere once again afterwards. There was comfort in the words, but all the same, Carter wasn't sure how much effect they were having.

She had an idea, one she thought worth investigating. Sanders, however, had an ideal.

Or so Carter was assuming. When assessing the team's standing on the issue, she had used a simple three point scale: for, neutral, or against. What she hadn't asked was, in the common usage, how many fucks each of them gave. There were, after all, two parts to making a decision. Which way you'd vote, and how much you cared about that.

Carter could easily estimate Sanders giving ten out of ten fucks against this current plan of dividing the team for exploratory purposes. In fact, until this afternoon, she would only likely have given seven or eight fucks.

That question hadn't been asked, though.

This afternoon, it was the combination of determination to see if she could learn more for the project and the sense that she was on the right path that had bumped her up on the number of fucks she gave. And, if she was honest to herself, the hope of proving Sanders wrong. There was no small amount of competition within academia, after all.

The play was a contemporary piece called The Short Trip. According to the season, it chronicled an indecisive youth taking a small trip away from his family on false pretenses to visit a bunch of friends for three days. The goal of the trip was to visit his long-distance partner, but in the setting of a party, with guests, both known and unknown, weaving their way through the scene over the three heady days.

This much she had learned as she made her way southwest. Carter had needed to duck out of work earlier than usual to make it over to the theater on time. She had actually to travel past RJ in the UCH, riding along the yowling Victoria line, to get to Soho where the theater was. Traffic at that time was was notorious for keeping the Tube cluttered and, at times, inaccessible. She had needed to wait for three trains to pass before she found one with room.

The train vomited her out into Oxford Circus and left her spinning, looking for the right exit to the tube station, each helpfully lit up with a thin, translucent display that overlaid the older signage in painted tile. Both bore the unerring curves of Helvetica, perpetual winner of the font wars.

It was easy enough to find the theater by following the crowds, and her identity --- and thus her ticket --- was proved by a taking her glove off and giving touch from her contacts, a grip around a simple bar in front of the theater. Once she had done so, the bar flipped around to provide its other end to the next customer, the end she had touched getting a quick sanitization so that everyone touched a sanitary surface. It was all rather like getting on the Tube, only much slower.

Carter was surprised by just how much she enjoyed the play. She had decided not to approach cast or crew beforehand. This had initially worried her, as she suspected she would spend the entirety of the play thinking about what to say. She wound up getting engrossed in the play, watching as the lead made his way through the party and met up with his partner.

The cast did a magnificent job of portraying the awkwardness of meeting up for the first time. She had had her own long-distance fling while an undergrad, and she knew that feeling well. Her mother had even cautioned her to meet up at a public space where you know people, like a party, just in case.

It was well into the third act of three that she realized she hadn't given attention to the sound of the play. A passing thought informed her that this was probably a good thing, that this was the sign of a job well done.

She applauded as heartily as the rest of her fellow audience members, clapping in that way that prevented any knocking of her contacts against each other. All the same, her mission, such as it was, was not lost on her. She was perhaps a little rude in her haste in making her way out into the lobby of the theater where some of the cast and the director were greeting the audience. It was opening night, after all.

``Mr.~Johansson. Mr.~Johansson!''

The bulky man turned toward her with a pleasant look despite the obvious worry lining his face. ``Ma'am. I trust you enjoyed the show?''

``I did. Not bad at all! I did want to ask you something, though, if I might.''

``Mm.'' The sound was assent, but with the rest of the audience starting to stream out of the theater, she could tell his mind was elsewhere.

``I was\ldots{}It's just, about RJ-''

That focused Johansson's attention in a way that startled Carter out of speech.

``I-I mean, if it's not too forward to ask,'' she trailed off, leaving a hint of a question.

``It is forward,'' he confirmed, eyes boring into her. ``But I'd like to know how you know of em?''

``I'm a researcher at UCL, working on the Lost.''

Johansson took her elbow gently in his grip and led her off to the side, out of hearing of the rest of the audience, as well as the other curious cast.

``That doesn't tell me how you know of em. Aren't you\ldots{}isn't that privileged information?''

``The tabloids had a--''

He growled and grit his teeth, ``They told me I couldn't contact anyone but doctors, but said you guys had declined contact. I saw that.''

Carter straightened and shook her head, ``We did not, nor would we have. Although, I must admit, the interview process would be far more formal with this. I only put the pieces together based on location and pronouns.''

``So what do you want from us?'' Johansson's shoulders sagged, ``We miss RJ. It's been a real mess without em. Please, Doctor-''

``Ramirez. Dr.~Carter Ramirez.'' She hesitated for a moment before continuing. ``We're looking for\ldots{}well, a few of us are looking for social connections between the Lost, rather than just simple personality correlations. What can you tell us about RJ in that sense?''

Johansson looked up toward his cast, then leaned a little closer to murmur, ``O'Niell's, once we're done, then we can talk. I have more to do here, so it may be a while. Please wait up, though.''

%%%%%
\chapter*{RJ 007}

Sleep did not come easily.

Auditorium seats, although padded, were not made for laying down on, and AwDae found that ey had to face toward the backs of the seats, or else eir tail would get crimped against them. At first, the faint dusty smell of the seat fabric had inspired nostalgia, but it didn't last long. Eventually, ey got up blearily and began pacing around the auditorium, looking for some way to get some rest that did not involve the seats.

Ey pondered pulling down one of the curtains and making a bed out of that, but, as ey did not know how to do so without ripping the curtain, ey was loath to do so. They carried some of that same smell, as well. Ey figured they would make a good last resort, if nothing else, and started exploring beyond the stage and auditorium.

The back door of the stage led out into the hall where all of the music classrooms were, and ey started cataloging additional places where ey could get rest. The black fabric orchestra seats were a little promising, but ey hit paydirt in the theater classroom.

In the back of the room was the wardrobe area, which also housed rack upon rack of tuxes and identical dresses for the choir singers. Nestled back behind all of these rows of clothing was an old sagging sofa. There was zero reason for the room to contain a sofa, but as inexplicable as it was, AwDae wouldn't have been surprised if such a thing had existed in the school ey had attended.

Thanking the gods, or at least whoever had created this sim, ey flopped down onto the sofa. Slightly musty smell aside, ey was asleep within minutes.

Sleep, while restful, brought intense dreams. Dreams of twisting passages, corridors lined with lockers that looped back around on themselves, leading always into the same dim light of the student center. And in the middle sat a menu, like the kind ey could get by swiping eir paw from left to right in any sane and sensible sim. Every time ey got close to try and read the menu, though, it would slide closed once more, leaving only its shadow behind, an unexpected rendering mistake.

AwDae awoke feeling as though ey had drastically overslept. Ey hadn't paid attention to when ey had gone to bed in the first place, but all the same, ey felt late.

The day before, with the shock of the transition and the need to explore the auditorium and school for the microphone, ey had never managed to make it outside of the school. Ey felt silly for that now, and so after ey woke, ey started to plan a way out of the school to see how extensive the sim was.

It was customary to lock the doors of a building that did not lead anywhere in a sim. For instance, although the Crown Pub did have bathrooms and fire escapes, all things to make it look authentic, the doors were simply locked. Beyond them would have been nothing at all. That was simply the extent of the sim. There were much larger sims than the school itself, and much more intricate, as well. AwDae couldn't be sure of the boundaries of the sim without exploring.

As ey walked toward the front doors of the school, figuring that those would be the most likely to lead anywhere, ey wondered about what was happening to emself back in reality. Ey didn't feel hungry, and such things were usually translated in-sim --- after all, ey had still felt the need to sleep --- so something had obviously been done with eir body.

That train of thought led to the question of just how exactly ey had gotten Lost in a sim without being connected. Obviously, plenty of time had passed, and certainly the crew hadn't left em just sitting on eir workstation after ey had finally lost touch. Even so, ey should've been pulled back when eir hands had been lifted from the cradles and eir head pulled away from the NFC headrest. And yet here ey was. Where was eir body, then? Some hospital somewhere, insensate and tied to life support?

And if ey was in a hospital, where did this sim live? A sim this size couldn't simply live in eir gear, with all of the mechanics ey had encountered so far: the fully functioning sound booth and mic, all of the papers in the office, the clothing ey had brushed eir hand across on the way to the couch.

No answers were forthcoming. All ey had to go on was what was in front of em.

Ey stopped at the front door, staring at the panic bar. Resigning emself to whatever happened when ey pushed it, ey leaned forward and rested eir paws against the smooth metal, claws clicking against the door itself, and gave a firm shove.

The door swung open and ey laid eir ears back and squinted into the bright sunlight beyond, holding the door open with one paw while the other shaded eir eyes.

Ey saw the cul-de-sac used by parents to drop their children off. Ey saw the street beyond, and the set of townhouses that lined the street opposite the school. Ey saw\ldots{}grey. Ey saw fog. Despite the very sunny day (ey had indeed slept in almost until noon), ey saw fog.

Fog, usually referred to fog of war or render distance, represented the furthest that the system was willing to render the sim away from the character. It was occasionally also used as an invisible boundary, so AwDae could not be sure which it was. That it was there in the first place, closing off the street in either direction about a hundred yards into the distance, though, confirmed that this was indeed a sim, and not just some artifact of eir subconscious.

Ey stepped out onto the sidewalk by the flagpole and stared, shoulders sagging and tail drooping. There were no answers. There was nothing for it but to keep looking.

%%%%%
\chapter*{Dr Carter Ramirez 005}

Johansson's hands dwarfed the pint of ale. Once they had managed to find each other in the post-theater rush of the pub, they'd managed to stake out a small two-top table, crammed against one end of the bar itself, leading the larger man to lean slightly to the side away from the noise coming from above it.

He'd hardly touched the beer, but it seemed to take on an almost talismanic significance to him. Carter drank her own cider slowly, careful not to press her luck too hard. Johansson seemed slow to open up.

``Alright, so, RJ.'' It seemed to take no time at all for his impressive vocal cords to unlimber and release what sounded like a well-rehearsed baritone.

``Ey was your sound guy?'' Carter winced at her slip-up, then added, ``Sound tech?''

There was a small smile tickling at the corner of Johansson's mouth, but he nodded and took a large swallow of the thin ale. ``Yep, lead sound tech. Best I've ever worked with, by a long shot. And don't worry, we still fuck up eir pronouns every now and then. I know we did on the night ey\ldots{}the night ey\ldots{}well, early last night.''

Carter nodded, ``And then you tried to pull em back out?''

He nodded and gave a small shrug. ``Nothing. It's like ey was still delved in even after eir contacts had been displaced. We hit the panic button and called the docs. Some ambulance-chaser seems to have caught up with them, which I guess is how you found out about us.''

``Yeah. I'm not really in the habit of checking the tabloids myself, but I'd gone out for lunch with a few coworkers and we got one pushed on us. The bit about you not being able to contact us got my attention, so I figured I'd make for the show tonight.''

``How'd you even manage that, on opening night, anyway?''

Carter laughed and sipped her cider before replying, ``Oh, don't worry, it cost me plenty. Christ, this is so far out of the realm of what I'd do, too. Truth is, I just feel like we're at an impasse.''

``An impasse?'' Johansson asked quietly.

``Yeah. We weren't getting anywhere.'' Carter leaned back in her chair to gather her thoughts once more before leaning over the table again. "I've only ever been on a few projects, I'll be honest, but all the same, this feels like a weird amount of interference. It feels like we're being made to trudge through mud. They won't give us access to the patients? Fine. WFPHIPA is what it is. We just need the data that they collect from them. This has never been a problem on any other project I've worked on.

``All the same, we're stuck with just little tidbits. We'll get a few hours of monitor scans, or a few bits of logs from before the event --- er, that's what we call it, at least --- and that's it. I don't mean to creep on you or anything, but with RJ, we've come across something we hadn't had before. We found out ey was\ldots{}well, you know\ldots{}''

Johansson canted his head to the side, ``Ey was genderqueer? Asexual? A furry?''

Carter laughed. ``A furry, though those other two are certainly interesting data points to keep in mind. We weren't totally sure ey was asexual.''

Johansson laughed in turn and took another swallow of his beer. ``Oh? How did em being a furry help you out at all?''

``Ey's the second furry we've had come across our desks.'' Carter averted her gaze toward her cider, then about the room, ``In fact, it's caused a bit of a schism. Some of us are looking into possible transmission vectors, while others are focused on the cases individually. How could something like getting Lost be transmitted from one person to another? It sounds like something out of an old anime.''

``I assume you're among those who doubt the transmission story?''

``Oh, no, I'm the head of it.'' She grinned wryly, shrugging again, ``But there are still convincing arguments against it. The leader of the opposition, such as it is, Sanders is his name, is dead-set against it. He thinks that we're wasting resources chasing up this transmission tree. We've got an agreement, though.''

``What's that?''

``Well, we'll keep poking at this lead and if it dries up, we'll agree to drop it.''

Johansson harrumphed and nodded, hunching his shoulders. ``Not much of a lead, I'll grant you that, but all the same, anything to try and get RJ back. Ey was more than just a tech, we all liked em. The tech crew, especially. We went through our share of fuck-ups tonight just getting by without em.''

``Oh? I didn't notice any.''

``You weren't on the headset, Carter. We had lights and sound arguing cues while stage desperately tried to keep them on track. It's a total mess.''

``All the same,'' Carter countered. ``I thought it was delightful.''

``Mmm.''

They both stared off into the pub. The room had that distinctly British dichotomy of being crowded and convivial, while also intensely conscious of personal space. The latter suffered as the night went on.

``Tell you what, though,'' Johansson mumbled, the rich baritone bringing Carter's attention back to the conversation.

``Oh?''

``RJ wasn't one for relationships, doubt ey would be, asexual and all, but of all the people ey was close to, it was definitely those furries ey was always hanging around. Come to think of it, I do remember em bringing up the Lost with regards to them.''

``Oh? Huh. It seemed like the to cases we have are certainly socially connected.''

``Yeah.'' Johansson shrugged, ``Not much for relationships romantically, but certainly no shortage of relationships on the friendship level. There was this one girl, Sasha, who ey was close to.''

Carter thumbed her phone on and swiped to a blank notes page.

``She was eir childhood sweetheart,'' Johansson laughed. ``As much of a sweetheart as ey would confess, at least. She knew 'em both. RJ and eir friend who got Lost.''

Carter nodded, jotting down quick notes in shorthand. ``She's still out there, then? Not Lost?''

``I assume so, I guess. You'd know better than I.''

She shook her head, looking down at her phone as she completed the note taking. ``Mmm, no, no female furries. A lot of 'net addicts, and I suppose there's no small crossover, but we're talking way deep. DDR junkies and layabouts.''

Johansson bristled, ``RJ was no layabout.''

She held up her hands and shook her head, ``Mostly, is what I'm saying. They don't have ties, or if they do, they don't hold them. Recently, though, in the case of these last few folks --- the furries --- they have lots of contacts. That's where our two groups disagree most. I think that we're seeing something novel. `I' being the leader of the group that thinks there's a transmission vector.''

``And the others?''

``They see it as chance, as too small an `n' --- too few cases --- to say one way or another. They say that there was bound to be both connected and unconnected folks among the lost. They'd say that it's a matter of chance, that those who use the 'net more would be more likely to wind up Lost, regardless of their social or economic situation.''

``Both make sense, I guess,'' Johansson offered. ``All the same, you know I've got a vested interest in RJ; I'm going to wind up seeing it from your point of view, since you're working with em. Never mind that you invited me out here. What do you need from me?''

Carter thought for a bit, ``I guess I need to know more about em. I have all of eir stats, the dump from eir workstation and the time leading up to it. I'm assuming we're getting all of it, but perhaps that's generous of me. What I need to know is what's slipping through the cracks. I need to know about who RJ was. How ey interacted with the theater, and anything you can tell me about eir friends.''

``Should you\ldots{}?''

``Should I have all of that information? I don't know. Is it against the law for you to tell me? No.~Is it unethical to further my own agenda with this project by consulting you? I don't know; maybe. If I were on a bigger, more mature project, we'd probably be interviewing you anyway. Is it because I think that the more we know, the more likely we are to get RJ and the others back?'' Carter furrowed her brow. ``I'd say yes.''

Johansson looked down into his beer, then, with a decisive motion, drank most of the rest of it in a few smooth gulps, holding up the glass with the last inch or so of amber liquid in it, an obvious toast. ``To RJ, then.''

Carter felt a little silly toasting to someone she'd never met, with a man she'd only just met, with a full glass of cider to his mostly empty ale. All the same, she raised her glass and clinked its rim to Johansson's.

``To RJ.''

%%%%%
\chapter*{RJ 008}

AwDae stood in the sunlight for a moment, blinking.

Ey felt weak. Not from hunger, nor lack of sleep. Just worn out, exhausted. This was starting to feel like grinding: that drudge that you went through when playing some role-playing game in order to level up. It was always cast in a negative light, but then, you could quit a game. Here ey was, finding clues and all the nonsense that went along with gaming, and for what?

There was even a fog of war.

``So much bullshit,'' ey laughed bitterly. No sense in keeping quiet about it.

Ey stripped down to eir underwear and shook eir fur out. There wasn't much in the sense of comfort in a sim, so much as sensory inputs that the computer decided to send your way. The musty smell of the auditorium seats had been one thing, but ey was starting to feel that, given the way this sim was constructed, there would be rather more than less sensory input. Eir tux was not made for fox-people, and eir fur was decidedly matted.

There was nothing to feel all that self-conscious about --- ey was a genderless furry in the middle of an abandoned sim, after all --- but ey folded eir clothes up all the same and set them on the sidewalk in front of the school before heading to the grass, the cool blades of the plants a welcome change from the indoor-outdoor carpet or tile of eir old high school and the roughness of the concrete. Still clothed only in eir underwear, a simple garment made more to keep other sim participants at ease should ey disrobe, ey sat roughly down on the patch of grass, tail flicking about behind em.

``Alright. So.'' Ey plucked viciously at a few close-mown blades of grass and held them pinched between eir pawpads. ``Cicero is Lost. He was voting on a bunch of stuff as usual, leading the comment boards. He voted on something, and it had passed, but that doesn't show in the records. That's three things gone.'' Ey plucked blades of grass with eir free paw, enumerating the facts. ``The vote cost, the bounty, and the comment he made.''

Ey swished eir tail around to the side and hiked eir backside up enough to slip it beneath em, rolling onto eir back to stare upwards. It was too bright, so ey draped eir arm, fingers still clutching at grass, over eir eyes. ``And now I'm Lost. I was working, and then I was here. Before working, I was digging into Cicero\ldots{}''

Ey trailed off and spent a few moments thinking, then a few more just feeling the earth beneath eir fur, the way the grass seemed to find a way through to tickle at em more directly.

``So had Sasha, though. She was the one who got me the deck in the first place.'' Ey ran through the acts ey had taken on the deck ey had been given. Eir first write to the deck had been on the note about the voting records. Prior to that, if such things were tracked, there was only the sorting and sharing of records.

Ey lifted eir paw once more and stared at the remaining torn blades of grass before tossing them aside. ``Ah, hell. I'm talking to myself. If I'm going to go all cast-away, I might as well pick myself up a real companion, rather than just some blades of grass.''

Laughing, AwDae stood up once more and gathered up eir tux, heading back to the room with the couch and all of the costumes. Ey hoped ey could find something that would fit eir form, taking into account that ey was a fox, now, instead of a human.

AwDae wound up in a simple, pleated skirt and a rather plain shirt.

The skirt fit well with a tail, certainly far better than having eir trousers sag beneath the base of the tail awkwardly. It was a nice robin's egg blue, but otherwise undecorated. After all, most decorations would get lost in the distance between the stage and all but the closest audience members.

The shirt was made for someone with broader shoulders. RJ might have filled it out, but on the fox's slim form, it was rather baggy, which ey could hardly complain about. Again, it was a plain white, but it didn't compress eir fur down too much, like the tux shirt with its fake pleats along the front had.

Ey spent a few minutes considering what to do with the tux. On the one paw, it was just an artifact. In theory, everything out here was just bits, even eir own body. By choosing clothes that were `more comfortable', AwDae was simply instructing the sim how best to treat eir body. Clothes that were more comfortable were no different from clothes that weren't, it was just how the numbers added up.

On the other, though, the tux was the only thing ey had brought with from reality, if such a thing could be said. It might just be a set of bits and bytes, but it was eir set of bits and bytes. Something to tie em back to the world outside this sim.

Ey finally came up with a solution and found a pack that had obviously gone along with some war-themed production. Drab and dusty, made of thick canvas, it would do well to carry along anything that would help, including eir notes ey had made. Ey laid eir tux out on the ratty sofa and rolled it into a tight cylinder; an empty sim would care little if eir tux got wrinkled. Ey stuffed the tux down at the base of the back and folded the notes into a small pocket on the side.

Finally, thus equipped, ey headed back to the auditorium on a whim. Once there, ey made sure that the room was put to sleep, and, without even thinking of it, snagged the one live microphone ey'd found earlier. Ensuring that it was off to conserve batteries, ey added it to the notes: a small token of where ey'd come from.

``Not going to do much without the receiver, much less a sound board to plug into,'' Ey murmured, then shrugged and buttoned down the flap above the pocket.

Ey briefly considered food or rations before dismissing that as an even sillier idea. Ey didn't feel hungry or thirsty, even after so long in the school, so obviously, eir body had been taken care of. There was nothing ey could do about it from within the sim. All that food and water would do would make the sim tell eir body that the pack was heavier.

From there, ey made eir way back toward the front doors of the school, pushing them open against the pressure differential, the breeze outside ruffling eir fur and skirt as ey stepped out into the sun once more.

The grey mist turned out to be a render distance.

Render distances were used to reduce the amount of work the computer had to do to render a scene in a sim. If one was in the school, that was pretty simple. Buildings were fairly easy, made up mostly of polygons with textures attached. Of course, if you got close enough, those textures would be mapped to an artificial surface to give them more depth, causing the system to work harder, but that was rarely an issue.

Outside, though, that was difficult. There were trees, curves in the ground, more complex shapes. If, as AwDae suspected, all of this was happening within eir own gear, a render distance made sense. It was as though visibility had been reduced to a hundred or so meters, but in a way that didn't dampen the sunlight at all.

Had it been a barrier, AwDae could have walked up to the fog, but no further. As it was, though, ey was able to follow the street ey would've taken to the home ey grew up in, way back in America, and the fog simply receded before em. Ey could never truly approach it, it was just a small bubble into which ey had been placed: a bubble that moved along with em.

The act of walking away from the school, wearing a backpack and heading towards home, did a lot to dredge up memories of their time in an American highschool in the '90s. Though ey was a fox now, not a whole lot had changed. Ey had carried eir tablet and few books too and from school in a pack not much different than the one ey had been wearing. That was about the time ey had started to get more inventive with dress, and ey had worn several bits of clothing ey had picked up from thrift shops, finding a few different antique fashions to throw together into something ey could call eir own.

Ey prowled through memories of Sasha --- of dating, and then of becoming better friends after anything more than that hadn't worked out. Ey thought back to her coming over to stay the night, eir mom checking in on them at one in the morning just to make sure everything was okay (and, bless her heart, to make sure they weren't having sex).

Ey missed Sasha's company, most of all. Together, the two of them would've been able to keep each others' spirits up. Sasha would've been able to figure out the problem with Cicero's voting record much faster then ey had, and ey would've been less alone, would've felt less hopeless.

Ey trudged on toward home, reaching a paw up to snag a handful of leaves from one of the trees as ey passed, feeling the reluctant snap as they pulled loose from the branches. For all the sim's complexity, school in the spring was pretty far remote from London in the winter.

``School, hmm,'' AwDae mused aloud fanning the leaves out in eir paws. ``Why school, anyway?''

%%%%%
\chapter*{RJ 009}

Home was unlocked.

AwDae wasn't terribly startled by this fact. Although the front door had always been locked when ey had been growing up there, the fact that this whole sim seemed oriented around clues led em to believe that ey'd be able to gain entry to eir old townhome. On a whim, ey checked the other doors in the complex, and they were all locked, as expected.

Although ey had braced emself for it, there was still a surge of emotion and memory as AwDae stepped through the door and into the entryway of eir old home. Ey could feel immediately that it was deserted, but all the same, ey felt as though eir mom could be just around the corner in the kitchen, prowling through the fridge, or eir mom's boyfriend laid out flat on the couch, snoozing in front of the TV running old science fiction shows.

It was silent, though, as silent as school had been.

AwDae shrugged out of eir backpack and set it down in the entryway, as ey had done countless times growing up, and paced into the common area, toenails clicking against the hardwood floor. Ey kept eir eyes peeled for any sign of a clue like ey had been pointed toward back at the school.

The sensation quickly grew to be too much, and the fox sat down on the rug in front of the coffee table, where ey had sat to eat dinner countless times, watching whatever was on the TV. It was one thing for the house to be so empty, and another thing entirely to be here as eir fox-self, but the two combined were quite overwhelming. Ey felt eir breath coming in short and shallow, and eir sense of vision being slowly reduced to only what was in front of them. Eir pulse felt elevated, no matter how still ey sat, and ey found it hard to concentrate on what ey was even supposed to be doing here.

The only thought that they could manage to pull up was, \emph{Is my pulse elevated offline, wherever that is?}

Ey let out a strangled sort of laugh, trying to picture some doctor's befuddled stare at the sudden signs of anxiety showing in their patient.

The laugh stopped quickly.

AwDae leaned forward onto eir forepaws, stretching eir legs out behind em to lay flat on eir belly on the oh-so-familiar rug, before rolling over onto eir side. Eir tail lay limp against the short pile of the rug behind em.

\emph{How had this happened?} ey thought to eirself. \emph{How did I wind up here? Why here? What did I do?}

Eir mind was awhirl with questions, and ey found that the questions were the only things there. Ey didn't have answers, ey didn't have the brainpower required to do anything other than watch those questions swirl yan-tan-tethera through eir mind. Ey was an observer, nothing more than a set of eyes with no will to drive them as ey watched all of the emotion that had been held at bay with the sense of doing something over the last day and change.

Ey found, in retrospect, that eir actions had been all wrong. Ey had accepted getting Lost with resignation. Ey had leaped at the chance to solve the `puzzle' of the microphone with something akin to joy. All this when ey should have been experiencing something more like terror, breaking down into sobs at the fact that ey had been struck with some sort of incurable\ldots{}disease. Ey was Lost.

AwDae was sobbing now, ey found. Eir perspective, that core of emself that spent its time reviewing life around em, watched with no strong emotions as eir body shook with gasps and tears streaked down over eir cheeks and muzzle, leaving tracks in the short fur. It was as though whatever part emself was in charge of releasing pent up emotions had been divorced from the part of emself that actually felt those emotions.

\emph{It was the emptiness of the place that had done it,} ey thought. \emph{This place was home, and the knowledge of being permanently removed from such a thing had led to this. There was no one here, and no one at school, and as much as I longed for the time and space to do my own thing, I never imagined like this. Not like this.}

``Not like this,'' ey repeated between heaving gasps for air, wiping eir tears away in a smooth, slicking motion that flattened eir ears against eir head. ``No, not like this.''

Struggling to bring those two parts of emself into alignment once more, ey levered emself up heavily, leaning on eir one paw while the other straightened the fur of eir face, brushing the last aftershocks of sadness away in a careful and calculated gesture. If it was not to be like this, then ey would have to carry on. Eir initial reaction has been wrong on the emotional side, but right on the intellectual. Ey would have to at least figure out why.

It was the only thing left here in this null space that had any meaning.

%%%%%
\chapter*{Dr Carter Ramirez 006}

That night, Carter dreamed of shadows.

And through it all, there was the river. The muddy and sometimes stinking river. The Thames which only seemed to generate affection that one might call `grudging' when she thought of it. When she had first moved to London, it had been one of her best guides --- the Thames was always vaguely downhill.

She strode aimlessly along the south bank of the Thames. The constant renovation of the area had led to not just a single revival, but countless smaller revivals, as buildings were torn down and raised back up, plots of land chopped into smaller portions, buildings growing higher, never quite managing to match. She passed towers, squat pubs, architecture new and old, but mostly new. She passed people and crowds, buskers and food carts. She walked beneath bridges, along railings, past tour boats gliding silently along the surface of the water.

And she passed shadows.

The shadows were like the people of the crowds, a little taller perhaps, but still like the people. It was as though someone had cut a person-shaped hole out of space and blurred the edges so as to make it indistinct.

It wasn't particularly through prolonged observation, she just suddenly seemed to be aware of the fact that the shadows were all behaving in the same way. They were always following one of the people walking along the bank of the Thames with her. Always just one person, never changing, never looking around at anyone else. No one else seemed to see or notice these shadows except her.

She started tailing one of the shadowy figures, as unobtrusively as possible. It was following a young black woman pushing a stroller, another young child walking at her side, with his hand curled loosely in the fabric of her pants, keeping her constantly in touch.

Carter felt as though she was struggling to keep up --- the harder she tried to keep up with the young mother, the slower she seemed to go. She tried to call out, but her voice came out only as a whisper. The shadow reached out it's hand. The shadow's fingers slid through the woman's hair reaching for the base of her scalp.

Carter screamed, inaudible.

The memory of the dream dogged Carter throughout her morning routine and into her commute. She kept thinking, if she'd just been able to keep quiet, maybe it would've been worthwhile to wait and see what would've happened when that young black woman was touched by the shadow. Was that some sort of metaphor for getting lost? Or was her sleeping mind just carrying too much work-burden along with it into the night?

She was only able to dispel the lingering sense of too much meaning, heady and intoxicating, when she got into work and check her email for news. There had been no additional cases added to the research load. The dream had only just been that.

After checking her mail on the screen, not bothering to dive in for something so simple, Carter stood and stretched, making her way blearily to the coffee machine in the corner of the room. She was one of the first to show up that morning, other than Avery and a few other early risers. Thankfully, Avery was the type to leave the coffee pot full rather than empty.

She doctored her coffee to her usual specifications and ambled back to her desk, setting the mug down on the smooth surface and scrolling aimlessly through her mail list. She didn't dive in just yet, despite the workload that she knew waited for her. The fog of the dream had been burned away, but there were still too many thoughts in her head that needed organizing to go through the process of setting up her workspace and ordering stacks of cards.

No, she corrected herself. She was \emph{wary} of diving in.

She had things she needed to do in the sim. She had things that the sim would help her do quickly, whether she wanted to or not. She wanted to start a stack for this Sasha that Johansson had brought up, to find a way to start making and notating all of those connections.

Working in sim was part of her job, and she had gone into this research project knowing that it was only in sims that people got Lost. It had never bothered her before. And yet here she was, waffling about whether or not she felt safe going in to do her work.

With an annoyed sigh, she shook her head and set her hands in the cradles and rested her head down against he head rest. Nothing for it.

Once she was within her sparse, black space again, Carter prowled through the stacks she had started with regards to this little side project. She saw that someone had already created a card in the stack for patient 0224ebe8 --- whom she now knew to be RJ --- with some details from the tabloid article they had found about em, such as eir affiliation with the Theatre.

Invisible to others, she created a private stack within the delineated area, next to the pendant ``Possible acquaintances'' card, These private cards showed up with a subtle blue tinge to her, and would only fully appear on her view of the workspace. On the first cards in the stack, she transferred over some of the notes she had taken with Johansson during their brief meeting in the pub. That done, she started another card simply labeled ``Sasha?'' and added it to the stack.

The whole private stack was looped up to RJ's card with a piece of cotton string. Others would be able to see that she had created the stack by virtue of how the sim was set up: they would see the string trailing off to a faint outline of a stack, or a grayed out pack of cards, or however their view of the sim chose to represent the data.

Strictly speaking, this wasn't the use for such things. They were intended to be for short notes to oneself about what one was working on, not for actual investigative work. This was something new.

As Carter stepped back to look at the whole cordoned off section of data, she frowned. Was she even supposed to be doing investigative work? She was supposed to be utilizing the data that the hospitals and the university provided her with, not running out into the field and talking with acquaintances of the Lost over pints after a show. She was sure Sanders would have a fit if he knew what she was up to.

Even with that in mind, she wasn't quite sure what it was that drove her to make the stack private. Some hunch. Some shadow lurking behind her. She needed to be more subtle about this than she had been.

%%%%%
\chapter*{Sasha 001}

Sasha clutched at the arms of her chair, white knuckled, before standing up.

That her relationship with RJ was so casual was working against her. She knew ey was in the UK, and that they worked at a theater, but for the most part, ey talked about other things. Ey talked about Cicero and Debarre. Ey talked about The Crown Pub. Ey talked about eir past and eir shared world, eir syncosm. Ey rarely got into the present and the embodied world, eir exocosm.

So she had been at something of an impasse, then, with no way to figure out just what had happened to lead to eir disappearance. There were rumors abound in the Crown Pub that ey was Lost, just like Cicero. She would have to admit that she had been the source of more than a few of them, given her guess that perhaps their combined work on figuring out what had happened when discussing Cicero might have been the inciting incident, somehow, to lead to this.

The thing that plagued her with doubts, however, was the sheer improbability of such a thing. How was it that thinking about, talking about, and working with data related to the Lost would lead to one getting Lost themselves? As far as she had read, there was absolutely no such correlation.

Perhaps it was that one who thought a lot about the Lost was more prone to getting lost? But no, that didn't make sense. Obviously there were the doctors, probably entire teams of people studying the cases, and as far as she could find, none of them had gotten Lost, themselves.

Perhaps it was something about the data? Still a dead end, she thought, as she had exactly the same data that RJ had had, as did a few other folks with whom she had shared the deck.

And perhaps ey wasn't Lost at all. There had been the show, of course. And while RJ had never disappeared during performances before, ey had certainly been quieter during her timezone.

No one else had seen em, though, which is what had raised alarms.

After the fact, she was embarrassed at how long it had taken her to think about simply searching eir name. After all, she was relatively privileged in that she had known em in school, and actually remembered eir legal name.

So it was that Sasha wound up reading the same article that Carter had found a few days earlier, confirming all her worst suspicions. She emailed Debarre the link first, the subject line simply the emoticon :/ --- distressed as she was, she deleted the auto-corrected emoji and replaced it with the emoticon, feeling, somehow, that that better represented her despair. She considered passing the article around further, but thought better of it. It pulled too hard at her heart, and had left her sobbing when she first found it. Their relationship, brief as it was, had been one of the happiest of the lot she had been through. There was no ire in the way they had drifted from `item' back to simply friends.

The one upshot to finding the article had been the name of the group that RJ worked for.

Thus Sasha, pacing back and forth in front of her workstation, trying to work up the courage to hit send on the email she had drafted.

She had considered sending an email to the leader of the troupe, one Bernhard Johansson, but had decided against it, figuring that the man had far more on his plate running a play than anything, too much to bother responding to a request such as hers. Ditto Sarai Coen, who was listed as stage manager. If the play was still running, she figured both would be swamped.

She had settled instead on a Caitlin Fowler, who was listed as working the lights for the stage. Given all that RJ had told her about working in a theater, she would likely be both the closest to em and one of the least busy, if there were such a thing.

Sasha was just thankful that email addresses had been listed for the cast members. Not the crew, but given the pattern of first-name-dot-last-name-at-sttroupe-dot-co-dot-gb, she was hoping Caitlin's would follow suit.

\begin{quote}
Caitlin Fowler,
\end{quote}

the email still up on her screen read.

\begin{quote}
I apologize for writing to you somewhat out of the blue, but I am a friend of RJ Brewster who I believe works with the Soho Theatre Troupe, and I was wondering if you would be able to provide me with a bit more information about em. I am a friend from high school and remember em working with theater there, and talked with em daily on a sim online.

I know this is a long shot, and I hope this reaches you, and I hope that you are well, all things considered. If you get a chance to send me a note, I would greatly appreciate it. Both email and meeting in a sim would be fine.

Yours.

Sasha
\end{quote}

Sasha had deliberated over this short, two-paragraph email for an hour and a half, deleting and correcting --- how much should she ask for? --- should she reveal where they interacted? --- how should she start the letter, and how should she finish it? Hell, how should she address herself? Her real name wasn't Sasha, though she often thought of herself that way, but she figured that, should they actually meet up in a sim somewhere, that would be the name that this Caitlin would see.

She ran quickly to her terminal and hit `send' before she second-guessed herself any further, and then\ldots{}

Oh, shit.

Now she realized her mistake, realizing that, if they \emph{did} meet up in a sim, Caitlin would be meeting up with an anthropomorphic skunk. Perhaps she had a human av stashed away somewhere, or she could buy one off the shelf real quick. It was seven thirty in the British Isles, she might have time before Caitlin woke up.

No luck. A scant two minutes had passed with Sasha fretting at her keyboard considering possibilities, before a ping alerted her to a new message.

\begin{quote}
OMG OMG we were hoping one of RJ's friends would contact us. We only know so much. Your sim or mine? Meet you in five. C.
\end{quote}

Sasha groaned. Far too little time to switch out an av for something a bit more\ldots{}presentable? A bit more human?

She was still grumbling as she delved in, setting her hands on the cradles and leaning into the headband of her workstation. Once in, she pulled up her in-sim email client and spoke quickly.

\begin{quote}
Caitlin,

Either is fine. Should warn you that I know RJ through furry, and may look weird. My address is 129.82.29.22 in case you want to meet here, or we can meet publicly.

Sasha
\end{quote}

The reply came in a matter of seconds, half a minute tops.

\begin{quote}
Sasha. Crown Pub? In case you want to tell others. That's what RJ always talked to me. We know about furry. C.
\end{quote}

Her relief was palpable, if incomplete. It would certainly be weird to actually interact with one of the tourists that drifted through that sim. She tapped one of the pre-written replies --- ``Sure, see you there!'' --- on her client, hoping that that would fit the appropriate levels of urgency that Caitlin seemed intent on, and then dashed over to her tport pad and swiped left, quickly selecting the top, most-visited option.

Caitlin was already there, and Sasha wasn't sure whether to be surprised or not that the woman had a custom avatar. She clearly was a fan of the past, with hair swept neatly to the side to reveal an undercut, a long, tank-top style tunic emblazoned with the word `heh.' running to mid thigh covering only leggings. Something from earlier in the century.

Sasha felt plain in her simple skunk av with baggy shirt and fisherman's pants, fashionable enough by today's standards.

``Caitlin?'' she said, voice raised.

The human waved frantically and ran over to her. ``Sasha, right? There a place we can talk? Anyone else you want to bring along?''

Sasha did a quick scan of the room, picking out Debarre sulking at the end of the bar. She ran over and tapped him on the shoulder. ``Someone who knows RJ is here, want to join?''

The weasel perked up at that, frowned, and nodded. ``Uh, sure. Do they know about Cice?''

``I don't know, but they might. They only said they know about RJ, and that the talked to em about this place.''

Debarre shrugged, then nodded again and slipped out of his stool, pacing after Sasha and nodding to Caitlin on his way to one of the empty booths.

The three settled onto the cushy seats, and there was a moment of silence before all three started talking at once, followed by another silence and some nervous laughter. Sasha gestured to Caitlin.

``RJ's Lost. It happened during a rehearsal.'' She frowned, a finger tapping at the scarred table between them. ``Should back up, though. How much do you know?''

``We read an article about em. Something from a tabloid. It just mentioned the Troupe, which is how I found you.''

Caitlin nodded, hesitated, then offered her hand to Debarre, who shook it cautiously. ``Sorry, I should introduce myself. I'm Caitlin, the lights tech for STT. I was there when\ldots{}when it happened.''

``Debarre,'' Debarre said, sounding gruff. ``Boyfriend's Lost, too. RJ, Sasha, and I were trying to figure out what happened.''

Sasha, fumbling some cards out of her pocket and duplicating them, added, ``We were exchanging a deck on Cicero, Debarre's partner. You don't have to do anything with them, but you might as well have a copy, too. And, hold on.'' The skunk swiped, tapped through menus, and created a new card titled `RJ Lost', and duplicated it twice, handing one each to Debarre and Caitlin. ``One for RJ as well.''

Caitlin swiped up the card and nodded, saying, ``Alright, so here's what I know.'' She tapped the card to add another to the deck and hit record. "RJ was working sound that night, last night of rehearsals, and started having trouble about halfway through. Ey went quiet on the mic, and then missed a cue or two before we noticed what was going on. We called a halt to the rehearsal and found em unresponsive at eir workstation. We pulled em back and hit the panic button and\ldots{}and nothing. Ey was gone and, even out of the station, eir implants indicated that ey was still inside.

``The cops and paramedics seemed to have a protocol for the whole thing, and ey was taken off to the hospital. It all happened so fast. Johansson --- that's the director --- met up with a woman from the university who said she was studying the Lost and had a talk with her. She said she had gotten information on em, but wanted more, so they talked for a bit. Her name was--'' Caitlin frowned and thought for a moment, then tapped the growing deck to add another card. ``Carter Ramirez. Remembered it was Spanish or something. Johansson mentioned your name, which is why I was so eager to meet up.''

``My name?'' Sasha said, incredulous.

``Yeah. Ey mentioned you. Hell, ey mentioned Cicero.''

At this, Debarre perked up, looking intently at Caitlin, who quailed under his gaze.

``Just that he was lost, I'm sorry. I don't know much beyond that.''

The weasel's shoulders slumped, and he nodded. ``Fair.''

``There's a lot of downtime, working tech. We all chat and\ldots{}hey, why did you contact me, anyway?''

``I figured you'd be the least busy. Plus, RJ said lights techs were always cool.''

Caitlin laughed, brushing her hair back. The motion seemed automatic, as her hair had hardly budged. ``It's true. Anyway, we talked. I don't actually know what more to tell you beyond that. The rest of our relationship was work. RJ was super focused on that, and didn't really chill with the rest of us when ey wasn't working. Ey had a cat, I know that.''

``Priscilla, yeah.''

Caitlin shrugged. ``Sure, I guess. I was hoping you could tell me more, actually.''

Sasha frowned and, on a whim, recounted much of her and RJ's history, all the way back to their relationship in high school. By the end, she was crying freely.

``I didn't know, I'm sorry. RJ never talked about relationships.''

``I think I was eir only one,'' Sasha sniffled. ``There weren't any others that I knew about, at least. Ey was kinda, uh\ldots{}aromantic, I guess.''

Caitlin nodded. ``That tallies, I guess. Listen, I gotta get going, though. I ran at this without really thinking, and your email ping woke me up. I don't know if I can, but I should try sleeping more before the show tonight.''

``No problem,'' Sasha and Debarre said in unison, then laughed together.

``No problem,'' Sasha repeated. ``Thank you so much for meeting up with us. And thank you for the name. I'll see if I can find this Dr.~Ramirez. Keep in touch, alright? And add to the deck if you find anything.''

Caitlin nodded. ``Will do. See you later.''

And with that, the woman signed off. It was generally considered rude to sign off in the middle of a public sim like this, but everyone was a bit jumpy, so the skunk and the weasel shrugged it off.

``Guess now we have another lead,'' Debarre said.

``Yeah. And if she's a big name researcher, I bet she knows about Cicero, too.''

At that, Debarre brightened, and the two spent the rest of the night talking.

%%%%%
\chapter*{RJ 010}

\emph{``You seem kind of frozen, kind of stuck, in a few ways.''}

Sasha's words, that night in The Crown Pub, pressed in against AwDae, pushing thoughts out of the way and blanketed eir mind.

Ey had lingered around the house for a few hours, simply laying on the floor and poking around in various rooms, all as empty and static as the school had been. Eventually, ey paced back outside and across the road, to the countless acres of state-managed open space that abutted the foothills. Walking slowly, ey paced along a few of the trails and deer tracks, mind spinning helplessly over eir hopeless situation.

There was no birdsong, and while ey occasionally heard the buzz and chirp of insects, ey never saw one throughout the long, aimless walk.

Ey gave up and returned home. Ey wasn't tired by the time the sun went down, but for lack of volition, ey bundled up in what had been eir old bed and slept.

Having gone to bed so early, of course, AwDae woke up before sunrise the next day. Eir alarm clock, still familiar after nearly a decade, told them it was just past four in the morning. \emph{At least I made it past the witching hour,} ey thought, barking out a laugh. Something about the idea of time in such a timeless space tickled em and made em sad all at once.

As it was still dark, ey decided to take advantage of it for another attempt at exploration. Fog be damned, ey slipped out of the house and started pacing around the neighborhood, even making it down to the school on the hill, searching for any lights that might be on in the middle of night that weren't otherwise expected.

The results were largely negative. While all the houses and the school's windows were dark, all the streetlights lining the road were still on in the pre-dawn darkness.

Ey trudged back up the hill toward home and slipped back inside in the dark. Turning on the kitchen light brought little warmth, so ey turned it back off again and waited for the sun to rise once more.

With the fog limiting render distance, sunrise took the form of a slow brightening, almost imperceptible at first, as the world around home lifted through grayscale into brilliant colors.

During high school, ey had often messed up eir sleep schedule enough to see the sun rise. Some days, ey would go down to the school for a run around the track before pacing eir way back up to the house again, sweating and invigorated. This whole sim seemed designed to, as Sasha had put it, keep em frozen in the past. The act of watching the world brighten and\ldots{}well, not come to life, but at least gain color tugged at memories of countless days, waiting for eir mom to wake and make coffee.

Coffee.

AwDae paced back to the kitchen, claws clicking on the hardwood beneath eir feet. Prowling through the cabinets revealed nothing. The fridge was bare, as well. There weren't even dishes to be used, and on testing, the faucet didn't produce any water.

``What in the hell\ldots{}''

It didn't make any sense. The whole world was rendered in such loving detail. Why not include things that others would expect to be in a house? Of courses, perhaps it was due to the limitations of the sim being run from eir implants, though ey still doubted that the implants would be able to run such a thing in the first place. Scent, taste, and texture were all available to the simulated experience, but were notoriously expensive to implement. Even if the cabinets had contained coffee, even if ey had been able to boil water, the chance that ey would be able to get the full experience was doubtful. Ey had smelled the seats in the auditorium, ey remembered, but the full experience might not be possible.

``All I want is something real,'' AwDae whined, fists parked firmly on the counter in front of the sink. Tears stung at eir eyes and ey slowly sunk down to the floor of the kitchen once again. ``That's all I want.''

The sulk lasted a good half an hour, with the fox crying off and on, and by the time ey levered emself back up onto eir feet, eir backside was numb.

Tail hanging limp beneath the skirt, ey trudged back upstairs to eir old room and slipped back onto the bed, simply laying down on eir front, muzzle facing away from the windows and in toward the closet. Ey ticked off the list of people in eir life who might be thinking of em.

Johansson was probably stressing out, and stressing out the rest of the Troupe in turn. His response to unknown situations was to try and make them into known situations, putting all his nervous energy to work getting things into a state where he could understand them again. Even with another tech handling sound, even if that had gone well, the boss would doubtless be jumpy and on edge.

Caitlin and Sarai would probably be missing em on a more personal level than Johansson. AwDae was certainly friendly with the entire company, but ey had gotten closest to those two, sharing conversation that went beyond the Troupe, beyond theater. If anyone was able to reach out to eir friends outside of STT, it was them.

And of eir friends, Sasha was the one that kept coming to the fox's mind. The skunk was the one person, aside from eir parents, who had been in eir life the longest, and probably the one who understood em best, even including eir parents. Sasha had to be worried, even with em having been gone for so short a time. She had to be looking for em. Or perhaps, ey thought wryly, ey simply wanted that to be the case.

Eir parents, always loving but always distant, would doubtless be concerned, but ey know their tendency to freeze up when confronted with something like this. Mom was the type who might sit by eir hospital bed and hold eir hand, but not necessarily the type of person to do any digging into what had happened or why. Dad would simply be frozen, unable to deal with any emotions surrounding the event.

Ey turned eir face to rub it against the pillow, leaving the pillowcase damp from tears, then grumbled and sat up once again, eyes wandering around eir old room.

On a whim, AwDae got up and padded to eir bookshelf and pulled down the most weathered book ey could find, a bit of sci-fi ey had read countless times, starting in high school.

The fox flopped back onto the bed once again and flipped open to a random page, then frowned. Ey blinked several times to try and focus, but the words seemed to swim across the page. Instead, ey flipped to the first page in the book, and the swimming effect seemed to slow and coalesce into words once more.

The effect was strange. As ey read, the words would slow slip into order --- though the world around em remained static and unchanging --- and each time ey flipped a page, it would take a moment before ey could move on.

Eir frown deepened. This wasn't the book ey remembered. The story was there, familiar as always, but the text read like a retelling of it. An admittedly quite detailed one, but a retelling all the same. It used words AwDae would've used, rather than those the author might've chosen.

Setting that book aside, ey levered emself up to go pull another book down and give that a go. The effect repeated itself, but ey had a hard time getting the words to settle down on the pages, even starting from the beginning. Brow creased with a frown, ey tried with a few more books. One ey hadn't read yet --- one of those impulse purchases that one always means to read but never gets around to --- was simply an unintelligible jumble of letters.

``Well\ldots{}huh.''

Still frowning, the fox sat on the edge of eir bed and picked up the original book, thumbing through the pages and watching the effect distractedly. Words jumped out, and occasionally a phrase would form, but nothing exact. It was as though the book was deciding what to become from moment to moment, based on where ey inserted their claw when flipping through the pages.

On a whim, ey skittered quickly back down the stairs to the pack ey had brought from the school and fished out the scraps of notes ey had there, including the piece of paper with Cicero's DDR votes on it. No swirling, disjointed effect happened with this text.

It took a good hour of exploration and thinking to puzzle out what might be going on.

Of course AwDae's implants wouldn't have the complete text of the dozens of books on eir shelf. How could it? Ey had only ever read them as hard copies, never through the software mediated by eir implants. Hell, never on a screen of any kind. So of course, ey wouldn't be able to read the books here in the sim, if the sim was confined to eir implants.

And ey was increasingly starting to doubt that the sim \emph{was} in eir implants.

A midday walk through the open space again netted them a hypothesis. A shaky one, perhaps, but something more plausible than what information they had been working with.

There likely was some information stored in eir implants. Some hundreds of gigabytes, a terabyte maybe, enough to store a good chunk of data, but not necessarily an entire sim. Certainly not one this big.

However, maybe it was that the implants themselves didn't store the sim, but simply acted as a framework? Maybe AwDae's brain provided all of the information needed to show em a sim, and all the implants did was turn it into an experience. Maybe the implants were the mirror to eir mind's eye.

That would be why the text of the books was jumbled, and when it wasn't jumbled, it was wrong. It was just eir recollection of the book being mirrored back at em in a way that was tangible, as much as anything was in sim.

That would explain why ey had been able to smell the seats of the auditorium, too. It was a scent that must've been permanently ingrained in eir memories.

And yet, this was an imperfect sim, based as it was on memories. The school with its countless hours of memory invested in it, doubtless had plenty of detail. As did eir home. And yet AwDae was willing to bet that, were they to go into another house on the block, ey wouldn't find anything. Or perhaps ey wouldn't be allowed in at all: after all, ey would have no memory of the inside, so why would the minimal system of implants-mirroring-memories be willing to show em anything.

Of course, this had some strange ramifications. This meant that eir implants were still acting as implants, but instead of taking signals from eir computer and eir mind, they were only taking in information from eir mind. That meant that everything was still up and running as though ey were delved into the 'net.

Which was absurd, of course. There was no way for the interferites to run without power and data coming from the NFC pads on eir forehead or the contacts on eir fingers.

Was there?

Perhaps getting lost was as simple as several redundant fail-safes failing in turn, implants remaining on even after contact was lost with a workstation.

As AwDae sat on the fence bordering the open space park watching the color of the light duck down through golden and into salmon, ey realized ey would need to be more deliberate about eir search. If ey was limited to places ey had memories of, ey would have to remember just which places those were.

%%%%%
\chapter*{Dr Carter Ramirez 007}

\begin{quote}
Dr Carter Ramirez

We'd like to thank you, first of all, for all of your efforts in working on these cases of the Lost. Your services are invaluable and are providing the families and friends of the Lost with hope, not to mention the world at large. We have come to rely on this technology in our daily lives in almost all spheres of work and pleasure.

As you know, research here at UCL is funded through a series of organizations and foundations working together. These relationships are both an expression of trust and a political statement, and both of those expressions work in both directions. As such, we welcome conversations, questions, and comments about research from the sponsors.

A recent suggestion regarding your project was that more effort be placed on researching the neurological aspects of these cases, focusing primarily on the treatment and prevention of such cases in the future.

As such, we're requesting that you add one more neuroscientist intern to the team. Unfortunately, due to budgetary constraints, your team must remain the same size as it is currently. Could you please respond with the name of a member of your group not on the neuroscience side who will, if possible, be offered a transfer to another project? Admin will take care of the rest.

Please continue the excellent work. If you have any additional questions, please don't hesitate to send a note.

Ari Liebler Research Coordinator
\end{quote}

Carter slid her chair slowly back from her workstation and paced over to the coffee station. She wasn't tired --- she wasn't tired; she was a bit too awake, if anything --- but she needed something to do while mulling over the email from admin.

Pouring herself a half cup of chicory coffee, she looked out over the room, at the heads bowed over tablets or nestled into the headrests of workstations. How could she possibly be expected to choose who would get the ax?

There was another thing bothering her, however, and the more she turned the thought over in her mind, the weightier it grew.

The shared workspace wasn't private to the team, of course. Their research was overseen by Ari as well as a few others, and there were likely reports that had been passed back to the backers of the project. Obviously there had been, now that she thought of it. How else would they know that effort was being spread out among a variety of different approaches the problem?

But why this sudden interest? Or, looking at it another, less favorable way, interference? The idea didn't sit will with Carter, especially so soon after starting to explore this new social avenue. That would probably take the hit the hardest: there were few other areas that could afford to lose a researcher.

The thought soured further as she remembered Sanders' resistance to the line of research from the start.

On a whim, having not even sipped her coffee yet, Carter slipped back to her workstation and delved in, stepping out of the workspace and into the anteroom, a small area off to the side of the main space where virtual meetings could be held, where others' avs would show up, rather than just the shadowy shapes.

``Anteroom, when you get a chance,'' she murmured into a message pane, then sent it off to Sanders.

She received a ping of acknowledgement and settled back to wait.

It was only a few minutes --- hardly enough time for her to organize her thoughts --- before the head of neurochem stepped into the anteroom and lounged in the chair across from her. ``What's up, boss?''

``Here,'' Carter said, swiping up a terminal to forward the email she had received over to Sanders. ``Give that a read.''

She watched as his eyes scanned over something she couldn't see. In public spaces, it was usually kind to pull up a tablet so others had a visual indication that one was occupied, but Sanders had never been one for formalities. Sims were only ever a tool for him, nothing more.

``Rough stuff,'' he said, nodding. ``Who do you think will be the unlucky one?''

Carter sighed. ``I'm not sure. I can't think of anyone I would want to lose. Anyone we could afford to lose, even.''

Sanders nodded.

``Look,'' Carter continued after an awkward pause. ``I know you weren't a fan of the social link I mentioned before. Did you\ldots{}?''

``Did I tip off the board?'' Sanders laughed, holding up his hands. ``No, of course not. I'd not presume to go behind your back like that. You knew my reservations, but I'd rather talk about it with you and the team than pull something like that.''

Carter nodded. The sincerity was evident in his voice, she felt, so she relaxed back against the seat. ``I got it, yeah. I'm sorry. It just came so suddenly and seemed connected, is all. Maybe I'm getting too good at seeing connections that aren't there.''

Sanders politely said nothing, looking down at his hands.

``Well, hey. Thanks for that. It's really reassuring. I'll let you get back to your stuff. Will call the team in for a huddle about this after lunch.''

``Sounds good,'' Sanders said, pushing himself up out of his seat and wandering back into the main room.

Carter watched the man's back as he turned from a solid avatar back into a shadow, thinking. If she was going to pursue this line any further, she'd likely have to do much of the work herself. Something, she realized, she was already prepared to do.

The team was none too happy to learn of the news. They had been working together over the months that they had on the project, and felt themselves a well-oiled machine.

``This is going to throw a huge fucking wrench into things,'' Avery grumbled. ``We'll lose one of our own, then have to get someone new up to speed. It's going to take ages.''

``I know,'' Carter sighed. ``I'd push back if I thought they'd let me, but they say it's a matter of those who sign the checks, so I think I'm S-O-L on that front.''

An unhappy silence greeted her. No one was looking at each other, all just staring at shoes, ceiling, or walls.

``Listen, I think we have some time. Absolutely no pressure, but if anyone wants to volunteer, cool. Otherwise, I'll put some thought into this and have to make a decision. Either way, I'll go to bat for you in trying to get a transfer rather than just the sack.''

Another sullen silence. Carter shrugged helplessly, and with an apologetic look, walked back to her workstation. She had little more consolation that she could offer them.

Once she delved in, Carter let out a low groan. A small, pulsing envelope icon in her peripheral vision let her know she had another email. \emph{If it's more bad news, I'm going to lose it.}

It certainly didn't look like bad news, though Carter remained wary. The address wasn't from someone at UCL, or the UMC, for that matter. It was a free address, something personal rather than professional. It had made it past the filters, though, so perhaps it was legit, despite its shady provenance.

\begin{quote}
Dr.~Ramirez,

I'm writing to ask for your help in the search for two of my friends who are lost.

I know there's probably little you can do to help, and you might not even be able to talk to me, but my friends and I are scared, and want to know what's going on. And if we can help, we'll do all we can.

Their names are RJ Brewster and Collin Jackson.

If you can, email me back. I understand if you can't.

Sasha.
\end{quote}

Carter frowned. Well, at least it wasn't bad news.

This Sasha was right, though, she technically wasn't supposed to respond, at least not with anything more than a form letter stating such.

In the midst of pulling up the file with the form letter, a thought struck Carter. She would have to do most of the work on this herself, true, but perhaps she could do a little bit more outside research, as she had done with Johansson. She wouldn't be able to rely on it, nor even publish it, but there was no harm in more information, if she had to strike out on her own.

Before she lost her resolve, she filled out the form letter and scheduled it to reply at five, near the end of her day. Then she paced around the workspace, organizing and cleaning decks as she sorted through her plan in her mind.

She left that evening at five after five, far earlier than she usually did. She had been prepared to beg off with feeling ill, but found she didn't need to: most of the team was also packing up and leaving. No one looked happy, with one of their jobs' on the line. Everyone avoided eye contact on the way out.

Determined now, Carter left quickly and, while standing in the station for her train, fumbled out her phone and started typing away on it.

\begin{quote}
Sasha,

I know you likely just got a reply from my work address, but I'm replying here as well. While UCL and the team I work with aren't able to provide any assistance or information with regards to the cases, I might be able to help a little on my own, and I'm sure you'll be able to help me. We don't have much information on RJ or Collin, and I'm desperate for more.

We can figure out a way for that information to get to the team later, but for now, we can talk here.

\textasciitilde{}Carter
\end{quote}

Thumb hovering over the `send' button, Carter hesitated. She was being reckless, she knew, but the more she thought about the interactions of the Lost, the more she was convinced that there was something to the connection, at least in this case. And the more sure she was, the worse the letter from admin stung.

She gritted her teeth and hit `send'.

%%%%%
\chapter*{Sasha 002}

Sasha wanted to be pleased with the rapidity with which everything was taking place. It hadn't even been a week, and here was one of the lead researchers of the Lost getting in touch with her.

And yet, she wasn't. It was all wrong. Everything about all of this was wrong. There was no way that she would be able to forget that, despite feeling like things were actually getting done, she was still doing all of this for what was widely acknowledged to be a lost cause.


%%%%%
\chapter*{RJ 011}

Without eir HUD, there was no way that AwDae would be able to teleport. Ey would need to swipe up a destination entry and tap or speak the command for sending emself off to the desired location. Hell, even if ey were able to get at the menu, ey wouldn't have the coordinates for any of the particular places ey had come up with to visit. If they even had coordinates, that was. This was no regular sim.

Ey would have to walk.

Walking in sim wasn't tiring, of course. There were no calories burned when taking simulated steps in a simulated environment.

All the same, the prospect seemed exhausting.

Eir first location on the list had been university, where ey had studied (and, later, pioneered) the abstract integration techniques ey used daily at work. Without being able to teleport, however, that seemed out of the question. It was halfway across the country.

``Something more managable, then,'' ey grumbled.

The walk to the clinic where ey has had eir implants installed was halfway across town, so it would take a few hours to walk that distance, ey supposed, though ey had never walked it before.

Ey had time, though. All the time in the world.

With little to do, ey had slept early and woken early in turn. If it was going to take a good chunk of the day, at least ey would be able to do it while it was light out.

Shouldering the appropriated pack, ey set out from home. It would be a short walk down to the school, then further down the hill toward Broadway, which would get em most of the way there. After that, two blocks east, ey would come across the squat, white building that housed the clinic. After that, it would be easy. There had been about a dozen appointments in the building, so ey knew it well enough that it would likely be in reasonable shape. Hopefully the doors would be unlocked.

The first skip happened about halfway down the hill from the school toward Broadway. AwDae noticed reaching the corner of the fence surrounding the track and football practice field, remembered eir brief interest in jogging and how ey always turned north there before reaching Broadway, which was always so noisy, and then ey was gliding down the street in a sitting position.

Ey let out a startled yelp and flailed eir arms out for support, eir left elbow catching painfully on something solid a foot to the side of em.

It took perhaps a second all told --- a second of blurred darkness, of shadow and motion --- before the rest of the car formed around em. Ey was sitting in the passenger seat of the family sedan, coasting down the road toward Broadway at what must have been the speed limit, though ey could hardly guess.

The car, like the books in eir room, took a while to swim into focus, and even then, some parts of it shifted indecisively, unable to come to rest in some solid, known state. Ey had only tried to drive it once before giving up on the prospect, so the dashboard in front of the steering wheel was particularly vague. Hints of dials, with no needles on them. Smudges of marks on the windshield wiper and turn signal levers. The back of the car lurched in and out of focus sickeningly.

Ey realized ey was holding eir breath and let it out in a shaky whine.

The car continued down the street toward Broadway and turned smoothly without stopping at the light, accelerating seamlessly. The soft hum of the engine and the road noise beneath the wheels was as indistinct as all of the visuals. Disconcerting, to say the least.

After a minute or so, AwDae had a hypothesis at hand. Of course the sim --- correction, eir memories --- did not include walking along Broadway. Ey had never done it. Ey had only driven. Or been driven, as ey had never gotten a license emself. All eir memories could dredge up were those of the car, of moving smoothly along the road.

No teleportation, then; just fast-travel.

Eir one experience with hallucinogens had prepared them at least a little for the blurring, smearing effect of the world around em. The fog did not diminish, but it played tricks with the buildings lining the road to either side. There was the house with the psychic's sign out front, to be sure, and it was relatively clear, but the rest of the buildings were shifting, indistinct. When focusing on them, AwDay saw them as flat facades, no depth. Textures on a low-poly wireframe. It was a nightmare of that hidden time of intrasaccadic perception, that moment of suppressed visual input when one shifts one's gaze, laid bare and elongated.

Ey moaned and closed eir eyes. The sights were wrong. The sound was wrong. Even the feeling of acceleration and deceleration, the swing around turns, was off, as though the entire universe was poorly rendered. Eir stomach turned at the combination of sensations.

The next skip came only a minute or two later, as the memory of walking through the parking lot of the supermarket at Broadway and Timberline asserted dominance over the memory of driving along the thoroughfare. So suddenly was ey on eir feet and walking parallel to Broadway, so surprising was the shift, that ey stumbled and fell to eir hands and knees.

AwDae retched, though nothing came up. Not even the sting of bile.

Ey sat in the empty parking lot for what must have been half an hour, trying to master the urge to return home and disappear beneath the covers. Ey wanted to avoid that horrible, half-remembered drive at all costs.

And yet, ey had to do \emph{something}. If there was even a chance of em being able to get out of this non-place, ey would have to keep moving, keep hunting and looking and thinking.

With a groan, ey stood again and walked toward the road once more.

The skip came as expected, and ey gritted eir teeth as the world whirled past. Perhaps ey would be able to make it to the east coast, but if that meant eight hours of this --- home to the airport, then the plane, then a different airport, then transit to the dorms --- well\ldots{}hopefully ey could find a work-around.

The rest of the journey to the clinic thankfully passed without another skip. Ey had been worried about passing through the pedestrian mall, which ey'd spent countless hours walking up and down, but thankfully ey had spent nearly as much time traveling along Broadway. Eir `car' continued down the empty street, blithely changing lanes to pass cars that weren't there, turn signal and steering wheel moving on their own.

The low-slung building of the clinic was just as AwDae remembered it.

The turn of phrase got a laugh out of the fox. In this sim, perhaps that was literally true. It could be no other way.

Preempting another skip, ey scrambled to open the door of the car and hop out on eir own before it was done for em. With a satisfying thunk, the passenger door of the dusty blue sedan swung shut behind em. \emph{Promising,} ey thought. \emph{Perhaps I can just be more deliberate about it. I'll get in the car this afternoon, follow the drive back home, and maybe it'll park in the driveway as easy as that.}

Eir claws clacked against the pavement leading to the smoky glass doors. Although it wasn't overly warm out, not with the fog-of-war fogging everything up, the cool air that breathed out of the clinic was nonetheless refreshing after the stomach-churning journey across town.
