\chapter{Sascha}

Painting their nails had always calmed Sascha down. The simple act of dragging a brush slowly and carefully, following along the contours of the curved nails in smooth strokes, moving deliberately so as not to bump those nails already painted. The whole act seemed to be almost a meditation, calming to the core.

At least, usually it did. It was difficult to contain the nervousness and excitement that filled them, and they found themself anxiously cycling over the list of things that needed doing before they headed out. Clothes: packed. Cat: fed. Tail and paws: in the bag. Phone charger\ldots{}

Phone charger!

Cursing quietly under their breath, Sascha quickly finished up the last two nails on their right hand -- always the hardest -- and ran down the hall to snag the charger from the plug by the bed, being mindful of their still-wet nails. No sense in having to clean polish off the wall.

No such luck with the charger, unfortunately, which received a dash of glossy paint.

``And of course. Piece of shit.''

Moving slower now, Sascha made their way back to the kitchen table and settled into their chair. They took a few deep breaths to calm themself before delicately twisting the cap off the polish again, straightening up, and working on adding an additional coat to cover up the ding in the polish they'd received from the charger.

``Getting all gussied up for the con?'' their housemate asked sleepily, drifting through the kitchen toward the coffee pot. Mike had a way of moving that looked almost effortless, a testament to his laid back life as professional dreamer. Sascha had always admired him for that, along with so many other things.

``Yeah, I figure if there's any one place where I can be assured to not be the weirdest one around, a furry con is probably it.''

``Oh, come on,'' Mike said, rolling his eyes and polishing off the coffee pot to fill his mug. ``You're hardly weird around here. College towns are full of people weirder than you, no need to drag yourself through the mud.''

Sascha sighed. It was a conversation the two had had enough times before that they didn't feel the need to list out all the counter-arguments they kept in stock. No amount of discussion could seem to dispel the deeper insecurities involved, anyway, much as Mike might try.

So the two shared an easy silence -- or perhaps it was easy on Mike's end; Sascha simply held still, fingers splayed, and watched the floor as they waited for the polish to dry. Their mind rolled through waves of anxiety and forced relaxation, focusing on holding still and not simply jittering right out of their chair.

``So,'' Mike finally said, voice softer than before. ``What's got you so nervous? Meeting up with whats-his-face?''

Sascha slumped, ``That obvious, huh?'' They bought themself a moment to think by blowing across the nails of one hand, then the other.

``Yeah, meeting Shadow,'' they continued. ``I'm not\ldots{}really sure what to do. I mean, I really like him, and I guess a con's a safe enough place to meet up with someone, since if it doesn't work out, it's not like you're trapped alone with them with nothing to do but feel awkward. And at least with this one, I can drive home if I absolutely need to.''

Mike eased into the chair across from Sascha and nodded, clearing a space for his coffee. ``Do you think you'll hit it off, though?''

``Maybe? I mean, we certainly get along well enough online, but you never really know in person until you meet. We talked through that, too, about how maybe things won't line up that well, and how this is just sort of an experiment.''

Sascha found it hard to meet Mike's sleepy gaze. They had tried dating each other once, earlier in college before they'd moved in together, and it only took a month or two before the realized how much better friends they made than a couple. They clicked well, just not on a relationship level. Ever since, though, Sascha had a hard time discussing relationship things with Mike. The fact that they now shared an apartment had instilled in them a hesitancy around relationships that had kept them out of anything more serious than a crush or fooling around online. This was the closest Sascha had gotten to another relationship since Mike, and it felt a little exciting, as well as more than a little scary.

``You'll do fine, kiddo,'' Mike laughed, sipping at his coffee.

The pet name got a smile out of Sascha -- the height difference between them and Mike when they were dating had led to them being confused as parent and teenaged child more than once. ``I know, I know. Thanks. And thanks again for watching the cat so I can go be a ridiculous furry.''

``Oh, that shithead and I will get along fine. We'll totally ignore each other except around dinner time.''

``Sounds about right, yeah.''

Mike finished his coffee and stood again, wafting easily toward the hall and giving Sascha's shoulder a squeeze on the way out. ``Good luck, kiddo, for real. Call me if you need.''

\secdiv

Sascha managed to make it through the rest of the morning without dinging any more nails, a real accomplishment. They had already packed up clothes and furry gear, and got the over-stuffed backpack into the back of their shitty Civic. They even managed to only turn around and retrieve a forgotten item once (the phone charger, natch), and that before they hit the highway. The trip was off to a good start, all told.

The drive itself was uneventful, a mere two hours from home down to the hotel hosting the convention. They were pretty confident that some of their friends would already be there, and thus would provide some distraction from the way their stomach seemed to be doing its level best to pirouette inside their abdomen.

Sascha had moved comfortably through the furry fandom for more than a decade now, having found it sometime in high-school, sticking with it through college, and into post-college life. More so than any other community, furry had helped them through some of the toughest parts of their life, from the divorce of their parents, to coming out -- first as gay, then genderqueer -- to moving away from home life. They'd tried to fit themself into countless other structures: gender and sexuality support groups, writing groups in college, all with more or less the same result: fading interest, spotty attendance, and eventually moving on.

The most comfortable thing about the fandom was that it provided a place for them to be themself. At times, pretending to be an animal person on the internet was almost ancillary to the sense of community, of just being able to feel comfortable with friends, something they'd never experienced in more structured environments such as all those carefully curated groups and meetups.

And furry is where they had met Shadow.

Shadow was, as his name suggested, a black wolf. Wolves were one of the more common species out there in the furry community, and Sascha had even known a different wolf named Shadow years back. Despite the rather plain name and everyday species, Sascha had found him to be a sweet, mature person who had seemed genuinely interested in them.

They had made an unusual, even rather awkward couple, Shadow the wolf and Sascha -- or Skylark, online -- the mink. Sascha had initially resisted getting much closer than friendship with Shadow, but he had eventually won them over. They had spent countless hours talking, role-playing everything from going for walks together to sexual encounters, and otherwise getting to know each other over the last four or five months. They'd even had a few short, tense phone calls, something Sascha avoided at all costs, getting to know each others' voices.

Shadow had seemed open to Sascha's gender identity and expression, saying that while he generally considered himself more straight than anything, he was willing to explore outside his normal comfort zone. They had both agreed that sex may not even be a thing for them, as it tended to make Sascha uncomfortable and Shadow had said he wasn't exactly sure what all he would enjoy with someone of indeterminate gender who nonetheless lacked a vagina. It was that open-mindedness that had convinced Sascha that meeting up, even if it wound up only being casual, would be okay.

Now, making their way down the highway and trying to drown out the rattling dash with music, Sascha felt less sure than ever that this was a good idea. Mike and their other friends had been pushing for them to find more of a relationship for years now. They knew their friends were right, too, given how much they talked about companionship and how much that meant to them. Still, though, this just felt like all the scenarios their parents had warned them about, and here they were deliberately going into it.

They shook their head and settled back into the seat. They were committed to going. They'd been telling themself that for weeks, now, and now that they were more than halfway to the hotel, where they'd already reserved a room.  There was definitely no turning back.
