\chapter{Ian}

Ian edged his way as quietly as he could into his room, finding it totally dark.

``Mmm, good evening, hon?'' he heard from the blackness, letting the door shut quietly behind him.

Ian nodded before realizing that Andrew wouldn't be able to see him, even if he had his eyes open. ``Mmhm, just some cuddling, was nice,'' he murmured, kicking his shoes off and tugging his shirt up over his head.

``Yeah, you weren't gone all that long.''

He blushed at the implication. Had he been gone longer\ldots{}but no, that was anxiety talking. Anxiety that was growing sharper edged as time went by -- the medication was starting to wear thin.

``C'mere, hon,'' Andrew murmured from the bed. ``I'm up now.''

Ian slipped out of his pants and down to his briefs, sitting for a moment on the edge of the bed. He could still feel Rei's warmth in his arms by its absence, still catch the faint scent of him in his hair. And yet, here was his boyfriend of the last six years.

Shaking his head to clear the confused tangle of thoughts, he tugged the covers up and slid beneath them alongside Andrew. He leaned in to kiss his partner three times, softly on the lips, before turning his back to him and nestling snug against his front. This is where he belonged. There was belonging with Rei, too, but this is where he was meant to be.

Andrew's arms slipped comfortably around his chest in the dark, pulling Ian warmly against his front, the soft breaths against the back of his neck raising small bumps from there all the way down his arms. ``Shh, just relax,'' came the whispered words against his neck.

Ian did his best to follow his boyfriend's suggestion, settling and relaxing within his grip by conscious effort. Andrew was warm behind him, belly pressed to the small of his back and hips pressed to his backside. He'd apparently been woken during quite the dream as the firm ridge within his boxer-briefs nudging along Ian's rear attested.

He stayed quiet, stayed still, stayed relaxed. This is where he belonged. His own erection strained at the front of his underwear, pent up after an evening of closeness with his other partner and still no release.

One of Andrew's hands wandered sleepily down over his front, brushing over freshly-shaved skin to trace a delicate fingertip along that tented fabric, ``Mmm, definitely didn't get up to much, did you, fox?''

Ian melted into his boyfriend's arms and let out a quiet moan. For all his anxiety and all the obsession over being in control, letting Andrew control things completely during sex was one of the only times he could truly let go.

With a deft hand, Andrew hooked both his underwear and Ian's down past their hips in one smooth motion, exposing his own arousal to slip stiffly along his partner's backside. ``Wolf wants inside his fox,'' he growled quietly. ``And fox needs his wolf.''

The sex was not gentle, though it was quiet, both of them aware of being in a strange room, in a strange bed, and not wanting to make too much noise. After a minute or two of firm grinding, underwear found its way to the floor and the lube had been snagged from the nightstand, and Ian felt himself spread wide by his partner.

The two moved in time, working from a few cautious initial thrusts to a steady rhythm with Andrew holding Ian to his front with one arm while the other hand clutched at his hip, tugging him back to meet his eager thrusts. The feeling was both familiar and titillating. Ian quelled a pang of regret as he felt himself leave streaks of slick precum along the underside of the sheets, the feeling of his erection being dragged across them almost enough to get him off as it was.

Finally, he felt those familiar fingers curl around his shaft and squeeze, stroking shakily as the thrusts became more urgent, less rhythmic. Ian began counting his breaths as they started to catch in his throat. He only made it to twenty-seven before he felt Andrew grind firmly against him from behind and let out a gasp, and only to thirty-three before he felt his own cock pulsing in his boyfriend's hand, waves of pleasure pushing through him and washing any thoughts of numbers out of his mind.

Once his climax had petered down to a dribble within Andrew's hand, Ian let out a long moan and relaxed back against his lover. Andrew had cupped his hand in front of Ian's shaft to catch most of the mess that he'd made, and before Ian could object, he wiped the slick mess up along Ian's clean-shaven front, leaving a smear of seed in a vertical swatch up to his neck. Hands clutched him close, and Andrew growled in his ear, ``Marked my fox. You smell of sex, and wolf''

Ian let out a sound, almost a whimper and tensed rigidly against Andrew's front, hands balling up into fists at the combination of erotic teasing and the feeling of being dirty.

``Mine now,'' Andrew murmured, then leaned in to kiss three times at the back of Ian's neck. ``Go, shower. I know you need to, love.''

The rush of relief at being given explicit permission to clean came through as a shudder when Ian relaxed against Andrew's front, pausing for a moment before carefully slipping free of the embrace and turning to kiss him firmly. ``Love you,'' he sighed, very nearly a moan, and slipped out of bed to go clean up.
