\chapter{Sascha}

Later that morning, once Volare and Vish had woken up and learned what Sascha would tell them of the night before, they made plans to get them back to their room. The two flanked them as they made their way up the flight of stairs and preceded them into the room in case Peter was still in there and upset.

Instead, they found the room to be empty, and Sascha followed after to find the room neatly kept -- the bed made hastily and Peter's clothes stacked neatly atop his bag. The bathroom was humid, a shower taken there not long before.

``At same coffee shop, meet me there?'' read a small note on the desk.

``That's good,'' remarked Volare. ``A question you don't have to answer. And he wants to meet in a public place. Shitty what he did and all, but I'll give him credit for trying to do the right thing today.''

Sascha was inclined to agree, but asked Volare and Vish to follow them to the coffee shop all the same. ``The sooner we can get this sorted, the better, I think. Otherwise I'll just fuck things up all the more.''

Vish pulled the door shut behind them as they left the room, and thumped Sascha on the shoulder lightly with a fist. ``Don't go blaming yourself, mink. There was booze, things went sideways.  It's not your fault.''

Sascha stuffed their hands stubbornly into their pockets and hung their head, then nodded as they made their way to the elevators. ``You're right, I'm sorry. I guess I was just worried that I'd chicken out on seeing him again.''

Vish grinned, ``Wouldn't blame you, but no, this is something that needs talking through before too much time passes, or it'll turn into something ugly.''

\secdiv

Peter met them at the fence of the coffee shop's patio, correctly foreseeing that Sascha would have a hard time making it through the doors if they knew that he was waiting inside.

He didn't hug them, he certainly didn't act out, he didn't do anything but stand with his hands in his pockets and quietly say, ``Hi.''

``Hi,'' Sascha offered, at a loss for anything else to say.

``Look, about last night\ldots{}'' He stared at his shoes for a moment before continuing, ``I'm sorry. I had too much to drink, and I know that doesn't excuse what I said, just\ldots{}I'm sorry.''

Sascha looked around to find that their friends had backed off and were standing by the entrance. Still within sight, but giving the two privacy.

``It's okay, but maybe we should talk about it,'' they offered cautiously.

Once inside and at their own table, each with a coffee, both Sascha and Peter seemed to relax. There was the requisite fiddling with condiments, lids, and hot drink sleeves to occupy them and get them used to each other's company in the wake of the previous night, but once seated, there was nothing left to do but talk.

``I'm really sorry,'' Peter began. He paused for a moment as if to collect his thoughts, then continued. ``I can't say I didn't mean to make it about gender, last night. I know we agreed that this would be an experiment, and I can't say yet whether it's passed or failed. I've never been with a guy-'' he held up his hand to forestall a response, ``I've never been with a guy, not to mention someone like yourself. I think you're wonderful, I really do, but I don't know how to make it work in my head.''

They sat in silence, Peter staring down at his coffee lid and Sascha down at their hands. Finally, they dredged up enough words to come up with a reply. ``I\ldots{}don't feel good about last night, but I don't feel bad about this, I guess. I mean, I kind of want to yell at you about that, but I also get what you're saying. I definitely accept your apology, but I need to think a little more about what you said.''

Peter nodded and sipped at his coffee, while Sascha's thoughts whirled wildly around their head. They wanted desperately for this thing that they'd been working on for months to work out, but they also wanted to feel safe, not to mention welcome to be who they were. Neither of those things seemed to fit in their mind with what had happened last night.

Finally, speaking slowly, they said, ``I know a con breakup isn't what either of us really wanted, but I don't know that this is going to work.''

Peter let out a heavy sigh.

``I've got a lot I can say on that, but I don't want to seem like I'm beating around the bush or anything,'' Sascha continued.

``No, no, I agree,'' Peter said quietly, clutching at his coffee. ``I really want it to, but when I think about you, I think about\ldots{}I think about my little minky girl, and I just can't make that jive in my head\ldots{}I don't know what I'm saying.''

``Mm, I think I get it, though,'' Sascha said gently, wary of the bright look of tears in Peter's eyes. ``I spent years having it not jive -- `boy this' and `boy that' didn't work, but neither did anything girly -- so here's how I am now.''

They drifted back into quiet for a good long while afterward, each watching the room from a different angle as furries bought coffee and early-sermon churchgoers boggled at those in tails and rave gear. They both stayed quiet until each had finished their coffee.

``So,'' Peter began. ``We've got one more day and one more night.''

``And everything after.''

``And everything after,'' he agreed.
