  The reason that this association between Secession and Launch is important is multifaceted. Yes, there was a similarity between the acts---those of dividing, of leaving---much of the first part of this history will be spent dissecting those. Yes, there was political maneuvering both phys- and sys-side in order to accomplish them both; you will read about that. Yes, there was discussion about the wisdom of actions such as these; this you will read about as well.

  The facet upon which this first chapter focuses is, however, one of correspondences. Both involved separation of one group from another. Both involved the construction and modification of a political system — or perhaps non-system — in order to accommodate the goals involved.

  In our immortal lives, however, one cannot deny that both Secession and Launch shared the same engineers. The same names, the same clades, the same individuals worked to bring about Secession as they did Launch. Get used to the names of the Ode clade and the Jonas clade. You will see them a lot.

  \vspace{1em}

  From \emph{An Expanded History of Our World} by

  The Bălan clade
  
  \vfill

\input{content/launch/launch/Codrin-castor/001}
\input{content/secession/sys/Michelle/002}
\input{content/secession/phys/Yared/002}
\input{content/launch/phys/Douglas/003}
\input{content/launch/sys/Ioan/003}
\input{content/secession/phys/Yared/003}
\input{content/secession/sys/True-Name/001}
\input{content/launch/launch/Codrin-pollux/001}
\input{content/launch/launch/Codrin-castor/002}
\input{content/launch/phys/Douglas/004}
\input{content/launch/sys/Ioan/004}
\input{content/secession/phys/Yared/004}
\input{content/launch/launch/Codrin-pollux/002}
\input{content/secession/sys/True-Name/002}
\input{content/launch/phys/Douglas/005}
\input{content/launch/launch/Codrin-castor/003}
\input{content/secession/sys/Michelle/003}
\input{content/launch/sys/Ioan/005}
