  Let us first consider a few of the subtler correspondences between the Secession and the Launch:
  
  \begin{itemize}
  \item Both have ramifications that stretch backwards and forwards through time for decades surrounding them.
  \item Both were intended, beyond the surface and altruistic reasons, to ensure the continuity and stability of the System.
  \item Both involved political manipulation phys-side and sys-side.
  \item Both involved historical manipulation to ensure that accounts align.
  \end{itemize}
 
  And now we may consider the facts that fall out of the sum of the correspondences:
 
  \begin{itemize}
  \item The history of the System, stretching all the way back to before its foundation, is one of technology, yes, but beyond that, is one of politics.
  \item Despite the assumption that such is not possible in the System and the promises that such is not the case, there are governing factions that guide the progression of the System through time via its interactions with phys-side politics.
  \item Per that fact, those controlling factions sys-side controlled --- and continue to control --- politics phys-side to a degree heretofore unimaginable.
  \item The unknowable size of the System and the unimaginable population within in all its variety and beauty retain the human characteristics of emotion and intellect, and are thus subject to the very same propaganda that has steered societies and civilizations for thousands of years.
  \end{itemize}

  \vspace{1em}

  From \emph{An Expanded History of Our World} by

  The Bălan Clade

  \vfill

\input{content/launch/launch/Codrin-pollux/003}
\input{content/secession/phys/Yared/005}
\input{content/launch/launch/Codrin-castor/004}
\input{content/launch/phys/Douglas/006}
\input{content/secession/sys/True-Name/003}
\input{content/launch/launch/Codrin-pollux/004}
\input{content/launch/sys/Ioan/006}
\input{content/secession/phys/Yared/006}
\input{content/secession/sys/True-Name/004}
\input{content/launch/launch/Codrin-pollux/005}
\input{content/launch/sys/Ioan/007}
\input{content/secession/sys/True-Name/005}
\input{content/launch/sys/Ioan/008}
\input{content/launch/launch/Codrin-castor/005}
\input{content/launch/phys/Douglas/007}
\input{content/secession/phys/Yared/007}
\input{content/launch/sys/Ioan/009}
\input{content/launch/launch/Codrin-pollux/006}
\input{content/secession/sys/True-Name/006}
\input{content/launch/launch/Codrin-castor/006}
\input{content/secession/sys/True-Name/007}
\input{content/launch/phys/Douglas/008}
\input{content/secession/phys/Yared/008}
\input{content/launch/sys/Ioan/010}
\input{content/launch/launch/Codrin-pollux/007}
\input{content/launch/launch/Codrin-castor/007}
