Ioan\#c1494bf found emself twenty meters in front of a squat house.

It was as postmodern on the outside as it had appeared on the inside: a concrete block, a thick wrap-around patio covered by cantilevered eaves, floor to ceiling glass for walls. Ey wouldn't be surprised if the far side of the buiding --- ey couldn't see it very well, with the slope of the shortgrass-prairie it huddled on --- jutted out at some crazy angle.

Smiling ruefully, ey walked up toward the house. Ey had eir own aesthetic. Might as well own it.

A soft tone, a vibraphone struck with a soft mallet, sounded inside and outside of the house as soon as ey'd passed the barrier between grass and patio. Ey stood on the patio, waiting to be either admitted or greeted.

A shadow of a person, human, peeked out through the glass at em, gave a pleasant wave, and hollered through the glass, ``Ioan! Hi! I'll grab Dear.''

Before the person could do so, Dear came padding softly from around the side of the house, looking slightly more collected than it had during the message.

\emph{``Ioan,''} it said, smiling and offering a hand --- paw? --- in greeting. Ioan wasn't sure how ey knew when a fox was smiling, but it was definitely a smile. \emph{``Thank you for coming on such short notice. Sorry for the urgent message, I just need to find someone to help out rather soon.''}

Ioan\#c1494bf took the offered paw and bowed. ``Of course, Dear.'' How strange it was to call someone a term of endearment as a name. ``May we have a seat? I've just woken up and am still figuring out how to stand.''

Dear grinned and nodded, gesturing cordially with its paw around the side of the building from whence it had come, leading the writer around and through a door in the glass.

The interior of the house was much as ey had seen, though as they moved through the space where that first message had been recorded (a gallery, Ioan noticed) and deeper into the house, things warmed up a little. The concrete walls were softened by hangings and the furniture unexpectedly plush. None of the firm-cushioned, straight-lined variety ey had expected.

Fox and writer settled for an L-shaped couch, sitting facing each other across the bend.

After a moment's hesitation, Ioan began, ``I must apologize, Dear. I'm not sure that you have quite the right person. I'm not really a detective, wouldn't know the first way of finding the one you spoke of.''

Dear shook it's head, \emph{``I'm pretty sure you're the right person. I'm not really looking for a detective, per se. There's enough of those in the Ode clade. They'll suss out the whens and wheres.''}

``Then what--''

\emph{``There's a few kinds of people in the world, Ioan,''} the fox said, voice low and calm. \emph{"There's forgers and honers. Most are familiar with those. Forgers build a thing and plow ahead, and honers settle on a thing and perfect it. Artists generally fall into these classes: prolific and unfruitful artists, respectively.}

\emph{``But you're not an artist. You write, yes, but that's ancillary to what you do. A side effect. There are some other types of people out there, too. Catalogers, feelers, experiencers.''} Dear shrugged, \emph{``For its own reasons, the clade needs someone to experience this along with us. There's a lot of history in this, a lot that we've forgotten before uploading, a lot that we're trying to remember. Maybe some that we're trying to forget. I want you to help figure out the history of this, yes, but I also want you to experience it and tell a coherent story after.''}

``An amanuensis,'' Ioan said.

Dear brightened, its ears perking. \emph{``Precisely. And what a delightful word, too.''}

Ioan grinned, ``That's good, then. This is very much more my arena. I'll keep this instance around and keep \#tracker up to date.''

The fox nodded, then looked up, smiling as the person Ioan had first seen came in with three thick-walled, wide-brimmed mugs of coffee, setting two of them down on the corner of the table near Ioan and the fox. ``Ioan, nice to meet you. Heard you were tired,'' they said, walking off with their own mug.

Dear watched them go.

``Your partner?'' Ioan asked. A moment of chitchat felt necessary. Ey grabbed eir mug eagerly. It smelled quite good.

The fox nodded, picked up it's mug as well and leaned back into the cushions of the couch, slouching. \emph{``Mmhm. Finally decided to explore relationships,''} it said. \emph{``They accuse me of treating it like an art project''}

Ioan grinned. ``Well, are you a forger or a honer of relationships?''

Dear rolled its eyes, said, \emph{``Touché. I'm trying to be a honer, with this one. I gave relationships a miss after\ldots{}well, some stuff before uploading. For a long while, I forked to create lasting relationships rather than holding any myself. Gets lonely, though. It was like being turned down every time. At least from my --- this instance's --- point of view.''}

Ioan felt they were getting a little too deep for having just met, so ey steered the conversation in a tangential direction. ``You fork quite often, then?''

\emph{``Yeah, Dispersionista through and through. Or perhaps profligate tracker, as sometimes I don't have the option to let instances linger.''} Something seemed to occur to it, and the fox sat up again. \emph{``Speaking of, do you know much about the Ode clade?''}

Ioan shook eir head, sipped eir coffee. It \emph{was} good.

\emph{``It's an old clade. One of the oldest on the system. Our root instance, Michel Hadje, uploaded basically as soon as she could, and quickly became one of the loudest voices on the system. She campaigned for more advanced sensoria to be included.''}

``I've heard of Michel!'' Ioan sat up straighter. ``Usually in the context of the founders. You speak of her like she's someone else.''

Dear nodded. \emph{``Dispersionista habit. We're quite different from each other, by this point. If you get the chance to meet Michel --- and you may --- you will see the differences.''}

``So what is Ode, then? Her old username?''

\emph{``No, an ode is a poem,''} Dear laughed.

``Oh! Oh, of course. So Michel wrote this poem\ldots{}''

\emph{``No, not actually. Michel had a friend, a good friend, who wrote the poem.''} Dear was speaking more slowly now, sounding less rehearsed. \emph{``When the friend died, Michel memorized the poem. All of us up-tree instances do our best to keep it memorized as well. Really memorized, too, up in the forefront, up where we think about it, not stored in some exocortex.''}

``Is that where your names come from?''

\emph{``Mmhm. Each of us is named after a line in the poem. I'm Dear, Also, The Tree That Was Felled, and my first long-lived fork is Which Offered Heat And Warmth Through Fire. My immediate down-tree fork is Dear The Wheat And Rye Under The Stars.''}

Dear splayed its ears, grinning sheepishly, \emph{``It's not actually a very good poem, I must admit. Michel was largely baffled at it from the beginning. The sentiments are nice, but this friend was not a poet. When they died, when they killed themselves, it really tore her up. We all still think of them often.''}

Ioan nodded, once more steering the conversation away from more sensitive topics. ``It must be quite long, then.''

\emph{``It's only a hundred lines, divided into ten stanzas. There are only ever ten branches as direct ancestors of Michel, and each branch only ever has ten long-lived up-tree instances. We may be Dispersionistas, but we're a small clade.''}

``And the poet? Who are they?''

Dear bristled, then mastered some complex set of instincts Ioan didn't understand. \emph{``That's The Name that we don't share. The information that someone supposedly did share, I mean. Someone of the clade or close enough to it to know.''}

Ioan's brow furrowed, startled at the fox's reaction, not to mention the concept of not sharing a name that was clearly important. ``I see,'' ey said into eir coffee, covering eir confusion. ``So you'd like me to help in finding this person and act as amanuensis along the way?''

Nodding, Dear held out its paw once more. \emph{``If you'd be willing, that is. We'd be glad to have you aboard.''}

Ey was already sold, Ioan knew, but all the same, ey took a moment longer to consider the ramifications of the job.

Ey nodded, reached out and shook the fox's paw. Dear grinned, shook back.

\emph{``Excellent. I've shared just about all I have to share on the topic for now, though as we get updates, I'll pass them on to you.''} Dear leaned back into the couch once more, lapped at its coffee. \emph{``For now, stay. Finish your coffee, at least, though feel free to putter around for a while. Or just stay here. We've got an apartment on the side of the house. I've already talked with--''} It said it's partner's name, Ioan didn't quite catch it. \emph{``--about it.''}

Ioan nodded, ``Thank you. I think I'll head home in a bit and sync up with myself, and start the research plan. Do you have any suggested avenues I should start down?''

\emph{``Of course.''} Dear smiled. \emph{``As for research, dig a bit more into the Ode clade for now, probably. When I send you updates, maybe those will lead to different topics.''} The smile turned into a sly grin. \emph{``I know you're not a big fan of sensorium messages, but as that's how the clade communicates --- those of us who do, at least --- I regret to say that you'll be getting quite a bit more.''}

Ioan gave eir best polite smile.
