Ioan sat back and rubbed at eir eyes. Time had gone all funny with all this research.

As with many of eir previous projects, ey tended to fall into a state of free-running sleep patterns and distractedness. Ey would work for a few hours and suddenly get quite tired, nap for what felt like fifteen minutes and wake up three hours later. Then ey'd work for twenty hours straight, neglecting to eat.

Ey had researched it and entertained the idea that it might be part of some larger sleep disorder, but had put it off as just one of eir (many) neuroses.

Less than healthy.

There were never any complaints about the quality or amount of work ey got done while free-running. Ey didn't slip up or stumble, and being methodical got one quite far as a historian and writer. Ey would write the same quality work at the beginning, middle, and end of eir waking periods.

What it did \emph{not} do, however, was endear oneself to one's housemates. Ioan\#tracker quickly grew frustrated, whether or not Ioan\#c1494bf used a cone of silence. Ey knew the feeling well. It was a common enough problem when multiple Balan instances stayed in the same house while on projects, and ey was nothing if not a Balan.

Ey considered digging a new spot for eirself to work, until ey had remembered Dear's invitation.

So thats how ey had found eirself rubbing eir eyes in front of a simple (if painfully modern) desk in a studio apartment attached to eir\ldots{}employer's? Friend? Eir friend's (equally modern) house.

The apartment really was a studio apartment, too: someone --- perhaps Dear --- had used it for painting, and rightfully so. The exterior wall was floor to ceiling glass looking out over that sere prairie. The landscape, Dear's partner had explained, was the work of Dear's sib, Serene; Sustained and Sustaining, `born' when their ancestor, Dear The Wheat And Rye Under The Stars had forked to explore its twinned interests of forming oneself and the of forming one's surroundings in greater detail.

Ioan's head spun whenever ey thought about the clade, but the longer ey spent around Dear, the more ey found eirself liking it. Ey was curious to get to meet another Odist.

If it weren't for the window, opaquable, the apartment would've felt totally like a cell. Simple cot, Desk, and kitchenette. The walls were whitewashed concrete, the floor that same pale hardwood, the fixtures all brushed steel. No doors to the rest of the house, nor even anywhere but outside, no restroom. One was expected to either turn off elimination or do so outside.

\emph{There's a cheap joke to be made there,} ey had thought, when first moving in. \emph{About Dear lifting its leg against some tree, but I doubt its body ever had that functionality enabled.}

Ioan shook eir head and rubbed at eir eyes more vigorously. Ey was daydreaming --- eveningdreaming, actually --- and that made em wonder how long ey had been awake.

``Probably some horrid number of hours,'' ey mumbled to the wall.

A sensorium ping, a gentle impinging of Dear upon eir senses, half-sensed words, \emph{``Does the wall reply back often?''}

Ioan spun around. Dear was standing, prim, dapper as always, at the door through the glass, paws clasped in front of it.

``Scared the hell out of me!'' Ioan blurted.

Dear's serene smile widened into a grin. \emph{``Sorry, Ioan. I'll wait until after the wall responds, next time.''}

``Jackass.''

\emph{``Foxass,''} Dear corrected, accenting that with an exaggerated swish. \emph{``Have some news. Care to walk with me?''}

Ioan nodded and stood, ``Glad to. Hitting a wall, here.''

The fennec adopted a look of concern, \emph{``Don't hit your friends, Ioan.''}

``Ha ha,'' Ioan rolled eir eyes. ``Something's got you in a state today. Tonight. Whatever.''

\emph{``Tonight.''} Dear's smile softened, \emph{``Come on, let's go walk. Storm scheduled in an hour, let's catch all of the nice smells.''}
