\hypertarget{ioan-balan-2305}{%
\chapter*{Ioan Balan — 2305}\label{ioan-balan-2305}}

Dear wasn't kidding about the smells. Ioan turned eir sensorium's sensitivity way up. Ey wondered if Dear's vulpine nose could smell things eirs could not.

Serene had worked wonders here. The smells, the textures, the raw beauty of the place. It was a fine line that she had walked, too. Any further in one direction and the landscape would have become nearly desolate, more foreboding than natural. Any further in the other direction, though, and it would've been softened too much, would've become too well-tended, cartoonish.

As the two crunched their way through the short, stiff stalks of grass, winding their way around the larger tussocks, Ioan realized that ey was quite taken with the place.

A ridiculous house in the middle of nowhere, a glittering white fox and its partner, the prairie fading off into downs on one side and stretching out to infinity on the other. It had all seemed so contrived when ey had first visited. Too simple. Too one dimensional. Kind of cheap.

But it was all so well done. So incredibly, skillfully executed. The artistry was in the details, and the details were fractal, continuing down through finer and finer layers.

Ioan liked it here.

Ey realized ey had been dawdling, past the comfortable stage of just enjoying the petrichor being washed in before the storm.

``Sorry, lost in thought.''

\emph{``It's okay,''} Dear said. \emph{``You looked like you needed it.''}

``Hmm? Getting lost in thought? Or getting out of the apartment?''

Dear shrugged, smiled.

``Sorry all the same. I'm here now. Will try not to do that again.'' Ioan grinned sheepishly. ``What did you find out? You seemed almost punchy.''

\emph{``I was, definitely. Still am.''} The fox grinned. \emph{``We seem to have found out who our\ldots{}ah, who our target is.''}

Ioan mulled over the word `target', searching for a better one. Ey couldn't think of any, so ey nodded. ``What do we know?''

\emph{``We know a name, and from there we can find a bit of history, which you may be able to help in filling in.''}

``Names are good. Something other than Qoheleth?''

\emph{``Other than that, yes, but almost certainly connected, probably the same. I think they're the same, at least. Not much more than the name, though. No location, no sightings in ages. Some aging — or aged — resources. A name and some history.''}

Ioan gave an impatient gesture with eir hand. ``Well, what's the hold-up?''

Dear's grin widened. \emph{``The hold-up is that I want you to feel some of the excitement that I felt on hearing this from down-tree. I want you excited and invested.''}

``I've been working twenty hour days on this, I'm pretty fucking invested.''

The grin turned into a laugh. \emph{``I know you have. My partner's worried about you.''}

Ioan felt eir cheeks flush. ``Sorry, I didn't mean to be a bother being up so much.''

\emph{``No, no. We can't hear you or anything. They're just worried because we \textbf{don't} hear you, or hear from you. We both like you.''}

The historian nodded, chastened.

\emph{``Don't worry about it, Ioan. It's fine.''} Dear patted eir shoulder. \emph{``The name, though. The name is the important thing right now.''}

``And the name is?'' Ioan's mind raced. Could Dear say the name? Was it the poet, miraculously talking through years to the system? That would be exciting.

\emph{``Life Breeds Life, But Death Must Now Be Chosen, of the Ode clade.''}

Ioan froze.

Dear stopped a few paces in front of em and turned, looking intently at em while its tail lashed excitedly behind it.

``They\ldots{}what?''

\emph{``Good.''} Dear laughed. \emph{``I'm glad I'm not the only one who had to pick their jaw up off the ground.''}

Ioan stuffed eir hands in eir pockets. Brought them back out to press against eir forehead. Crossed eir arms. Returned eir hands to eir pockets. Suddenly anxious. ``It's a real the-call's-coming-from-inside-the-house moment.''

Dear tilted its head, ears perked.

``Never mind. Old trivia.'' Ioan shook eir head and rocked back on eir heels. ``How, though? How'd you get the name?''

\emph{``A hunch I had, actually, though someone else dug it up.''}

``What was the hunch?''

\emph{``Signifier.''}

Ioan rifled through eir mental notes on the project. ``Signifier\ldots{}from the first encrypted note? Signifier is the password something something?''

Dear nodded. \emph{``Hardly anyone uses it anymore, but signifier used to be what we called the names of long-lived branches. It's still used here and there among older clades.''}

``Right, yeah. Ioan Balan is my name, Ioan\#c1494bf is my signifier.''

\emph{``Yes. It fell out of use quickly. Too clumsy a word. I use it now and then, when I can get away with it.''}

``Makes sense, yeah. So they're\ldots{}''

\emph{``They're an Odist, yes. Way, way down-tree. One of the first instances.''} Dear's smile faltered, \emph{``We weren't very good at record keeping back then. We aren't really now, to be honest, but the system's better. We\ldots{}we didn't know that he was still alive.''}

``Didn't know? I thought you all talked to each other. You must, in order to keep the names straight. Wait, `he'?''

\emph{``Remember, all of our names are chosen from our stanza. I talk with the other nine within my stanza fairly frequently, and we may fill out the stanza before too long.''} The fox's expression grew glassy, \emph{``Life Breeds Life\ldots{}that's the second stanza, first line. They're a conservative bunch. Only know one or two, but I assume that others are out there. And yes, `he'. Michel was a woman, but those early days were heady.''}

Ioan nodded, ``So the first stanza were the first forked, meaning he was the eleventh fork?''

\emph{``The first line from each stanza were the first forked, back when it cost to fork. Like, cost real reputation. Anyway, the first fork of the second stanza — second fork overall — must've just been a little more conservative than the rest of us.''}

``I\ldots{}hmm. May I ask something potentially personal?''

Dear nodded.

``The Odists that don't want me digging into this too much, the ones you didn't really talk to, are they from that side of the clade?''

The fox's ears perked, \emph{``To the last, yes. Why?''}

``How will, er\ldots{}''

\emph{``Life Breeds Life, But Death Must Now Be Chosen. Just Life is fine, too.''}

``How will Life react to the search? To me?''

Dear shrugged and turned its back on Ioan.

The historian stood rooted to the spot and watched as the fox took a few steps further out into the prairie, crossed its arms and stood straight, staring up into the bruised sky. \emph{``To the second bit, I don't know that it matters. They — Life, or Qoheleth, or whatever — are one of us. And even those of us who didn't want any outsiders brought on board are only frowning, looking down their noses at the thought, not gathering up arms.''}

``And to the first bit?'' Ioan pressed. ``What do you think they will think of the search?''

\emph{``What do I think? Or what do I feel?''}

Ioan scuffed eir foot against the grass. The temperature was dropping out on the prairie. It'd be an inconvenience to have to slosh back to the house if it rained.

``Both.''

\emph{``I think that they'd probably get a kick out of it. \textbf{I} am. Several of the others are, and the ones who aren't just don't care that much or are too angry.''} Dear turned back around. Its arms were held tight against it's front, though whether from cold or emotion, Ioan couldn't tell. \emph{``As for what I feel, I feel that it's their game. They're the ones running it. But even if it's a game, it's not play. There's no real fun in it, just\ldots{}snark. Anger. Pride, maybe. It's a game they've worked at perfecting.''}

Ioan marveled at the change in Dear, though with this raise in stakes, ey felt some of the same.

The fox's smile was weak as it added, \emph{``They have designs. Designs and reasons.''}

Ioan and Dear trudged back to the low block of concrete, a bunker against the storm, as a chill wind swept away the petrichor and brought with it the rain.
