\hypertarget{ioan-balan-2305}{%
\chapter*{Ioan Balan — 2305}\label{ioan-balan-2305}}

Interview with: Dear, Also, The Tree That Was Felled\\
On the formation of the Clade\\
Ioan Balan\\
Systime 181+338 1644

\textbf{Dear, Also, The Tree That Was Felled}: What, specifically, do you want to know about the clade?

\textbf{Ioan Balan}: Other than ``start at the beginning, and when you get to the end, stop?''

\textbf{Dear}: {[}laughter{]} Yes. I could do that, I suppose, but it wouldn't make for a very good story.

\textbf{Ioan}: Right. I suppose start at the beginning, specifically with your decision to upload.

\textbf{Dear}: You understand that there will be portions of that story that I cannot tell you, yes?

\textbf{Ioan}: Of course.

\textbf{Dear}: {[}thoughtful silence{]} Okay. Did you ever come across\ldots{}well, no. When did you upload?

\textbf{Ioan}: 2238. June or something.

\textbf{Dear}: {[}sighs{]} No.~Okay, well, in your research, did you ever come across mentions of ``the lost''?

\textbf{Ioan}: Yes. Lots of turmoil around then. Early 2100s, right?

\textbf{Dear}: {[}nods{]} Yes. Though it's strange. The turmoil at the time felt very small and personal. While there was all this grand scale stuff going on around us, we were dealing with friends and acquaintances disappearing. There were so few cases at first that it was just this thing the news would publish as a sort of curiosity. ``Look! Isn't this strange? The scientists are working so hard!'' {[}laughter{]} It wasn't until after that the turmoil you're talking about began.

\textbf{Ioan}: Okay. Did you upload during?

\textbf{Dear}: Oh goodness, no. Uploading had been something scientists and such had been poking at, but that no one had yet to accomplish. Or, well, perhaps someone had accomplished. Some had claimed to, at least. The consensus at the time is that, while it was likely possible, there would be little chance of having systems large enough to house more than two or three individuals. It was not a\ldots{}ah, not a linear increase in complexity, I think. Add another mind, and the complexity more than doubles. {[}pause{]} It was the lost who started it, in a way. The things we learned from them when they came back--

\textbf{Ioan}: How many-- sorry for the interruption. How many came back? Of those you knew?

\textbf{Dear}: Oh, all of them came back! Just that some of them didn't last long, after.

\textbf{Ioan}: Including the\ldots{}uh, the owner of the Name?

\textbf{Dear}: {[}pause, tense{]} Yes.

\textbf{Ioan}: Okay. Back to the uploading side, then. The lost taught you\ldots{}

\textbf{Dear}: {[}visibly relaxing{]} Right, yes. When they came back, many of them — many of us, for I was briefly among their number — talked about what we had learned while\ldots{}uh, in there. The things that we talked about and described are what sent the wonks down new avenues of research, and that eventually led to the first uploading tech. From there, there was the usual ``too expensive'' hand-wringing, but it all marches on, you know? {[}laughs{]} It got cheaper, the tech got better, the L5 station and ansible were set up. Population was getting out of hand again, and some wag decided to pitch uploading as a solution.

\textbf{Ioan}: I remember that, yeah. The posters were all over the place.

\textbf{Dear}: Yes. Notably, as the cost came down, it was pitched as something for the poorer classes to take advantage of.

\textbf{Ioan}: And were you\ldots{}I mean--

\textbf{Dear}: {[}laughs{]} Poor? Not particularly, actually. It appealed to me for\ldots{}different reasons. I'd prefer not to get into those at the moment.

\textbf{Ioan}: Alright.

\textbf{Dear}: Yes. Well. {[}pause{]} Okay, right, I uploaded in the 2130s, shortly after the L5 station was set up. It had become sufficiently cheap that It was something I could afford--

\textbf{Ioan}: Cheap? How much?

\textbf{Dear}: It was\ldots{}well, still a considerable portion of my savings.

\textbf{Ioan}: I see.

\textbf{Dear}: Why do you ask?

\textbf{Ioan}: We were — our families were, I mean — paid for us to upload.

\textbf{Dear}: Oh? Fancy that! {[}laughter{]} Anyway. It had become something that I could afford, and I leapt on the chance. It had been around long enough that it still felt relatively established, but was still a far cry from what it was now. This was probably early systime 10+, I mean. Folks knew what they were doing, but much of the society — what we think of society — here had not gelled into what it is today.

\textbf{Ioan}: You mention that it cost to fork, yes.

\textbf{Dear}: Yes. The reputation markets were already set up by then, but since this was before the system's proper expansion and some tech that came later — I couldn't begin to understand it — it was gently discouraged by the market.

\textbf{Ioan}: It hadn't reached this\ldots{}post-scarcity, you mean?

\textbf{Dear}: Right. There was still a scarcity of resources and we were still sufficiently\ldots{}uh, still sufficiently human, perhaps, socially human, that this was used as a lever, a measure of one's class.

\textbf{Ioan}: We still have the markets, though.

\textbf{Dear}: {[}laughter{]} Not like we did then.

\textbf{Ioan}: Alright. Don't suppose you would be able to do what you do today back then.

\textbf{Dear}: Not at all, no. It does still cost some minuscule fraction of credit for one to fork now, but I digress. We began as Michel and did the things that Michel did, forking infrequently. This was still a few years before the distinctions between strategies started up. Most everyone was a Tasker back then by virtue of the markets.

\textbf{Ioan}: It's hard to picture you as a Tasker.

\textbf{Dear}: {[}laughter{]} Right, yes. As everything started to get cheaper, though, those distinctions began to emerge. By then, Michel had a few long-lived instances, tagged as you are, Mx \#c1494bf.

\textbf{Ioan}: {[}laughter{]} Thank you. This was before the Ode?

\textbf{Dear}: The Ode itself existed. That came before we uploaded.

\textbf{Ioan}: Before the Ode clade, though?

\textbf{Dear}: Right, yes. Michel and her forks existed, but the very idea of clades was new at the time. At one point, though, she and a few other founders began to describe their trees as such. The larger trees grew — for those who maintained long-running forks, that is — the more unwieldy tags became, and folks decided on names. Some folks settled on simple standards. Another of the founders, the Jonas clade, for instance, uses syllabic prefixes. Ar Jonas, Ko Jonas, and so on. Leading vowels the first forks, then leading consonants, then the vowels following the consonants, \emph{et cetera ad infinitum}.

\textbf{Ioan}: And you chose the Ode.

\textbf{Dear}: Michel did, yes. She had picked up a contrarian streak during the whole lost saga.

\textbf{Ioan}: Did she play a large role in that?

\textbf{Dear}: {[}taken aback{]} Did her name not come up in your research?

\textbf{Ioan}: Not on the lost, no. Just on the founders.

\textbf{Dear}: {[}frowning{]} Well, alright. Yes, she played a role, but time softens rough edges, I suppose. Either way, she chose the Ode to name her instances while remaining Michel, herself. She started with the first lines of each stanza, then let them create and name their own forks from there.

\textbf{Ioan}: Thus the limited Dispersionista style.

\textbf{Dear}: {[}nodding{]} Right. Each stanza became a small family of Taskers, in a way. We, the Odists, create our own forks as needed, but don't let them live long. Or aren't supposed to, at least.

\textbf{Ioan}: ``Aren't supposed to''?

\textbf{Dear}: Oh, I'm sure a few of us have created long-running forks while everyone else has turned their head.

\textbf{Ioan}: Have you?

\textbf{Dear}: {[}smiling, shrugging, mu-gesture{]} By virtue of our set-up, though, such forks are not members of the clade. Those forks are not named as such, and likely not in communication with any other cocladists aside from their down-tree instance.

\textbf{Ioan}: Is the Ode available somewhere for me to read?

\textbf{Dear}: Of course. I'll give you a copy. That's hardly secret.

\textbf{Ioan}: And the clade, how long has it been since you have all been together.

\textbf{Dear}: This will be the first time there have been more than half of us together in one spot.

\textbf{Ioan}: Ever?

\textbf{Dear}: {[}nodding{]} Ever. Some Dispersionistas are families. I mentioned the Jonas clade before; Jonas Prime has set up regular intraclade communication. Some are just clades, defined by ancestry with no further connections.

\textbf{Ioan}: Are you in touch with any of your cocladists?

\textbf{Dear}: I'm assuming you mean ``in normal times''? Right. One or two. Serene and I get along quite well, and I talk with Praiseworthy — Those That Lived Are Forever Praiseworthy, the first line of my stanza — with some frequency. Michel and I have talked a few times. She comes to my exhibitions.

\textbf{Ioan}: Ever talked to, um\ldots{}

\textbf{Dear}: Qoheleth?

\textbf{Ioan}: Yes. I was going to say ``Life Breeds Life'' but forgot the line.

\textbf{Dear}: Names are important, Ioan. If he has decided on Qoheleth, then Qoheleth it is.

\textbf{Ioan}: Right, sorry. I was in the mindset of the lines. Have you talked with him?

\textbf{Dear}: Before this? No.~Not knowingly.

\textbf{Ioan}: And how do you feel about seeing the whole clade together?

\textbf{Dear}: I would be surprised if we manage to net all of them. {[}laughter{]} But I suppose I feel excited. Not necessarily because I have never met so many of them so much as because it feels like we as a clade have a goal in front of us. Seeing them is secondary to them — to us — actually doing something. Accomplishing something.

\textbf{Ioan}: And what do you hope to get out of it? This gathering?

\textbf{Dear}: {[}smiling{]} A story. Others want answers, and I suppose I do too, but I mostly want a story. I want \emph{the} story. I want to be the audience and a character. I want to dive into the story and bathe in it. I want a story.
