\hypertarget{ioan-bux103lan-2305}{%
\chapter*{Ioan Bălan — 2305}\label{ioan-bux103lan-2305}}

Dear's partner cooked that evening. Ioan sat with the two around the table and tried not to feel like a third wheel.

Eating was not a necessity in the system, of course. Not by any stretch. While it was easy to go for months or years without eating, it was something that remained a habit for many who chose to upload. Ioan suspected that there was no small amount of hedonism involved in killing one's body to decamp to a world beyond scarcity.

All the same, it was a muted affair.

Dear and Ioan made it back to the house just as the first cold sprinkles had started to fall. Once they'd reached the patio, they took a moment to stand and watch just out of reach of the rain. The weather went from cloudy, through sprinkles and drizzles, to stormy. Ioan focused primarily on the sound. The way ey was able to pick out the individual sounds of droplets striking dry grass during the sprinkles. The static of the drizzles. The rush and roar of the storm itself.

Ey could not guess what Dear was thinking. It stood, watching the rain and shivering. It looked contemplative, pensive. Somewhere north of sad, south of simply thoughtful. Ioan sifted for the word, gave up, and guided the fox back into its house.

Ioan felt some energy return with the mix of curry and lentils and rice. Calories an empty term, that is nonetheless what it felt like: like eating a hearty meal, regaining strength. Perhaps it was just the act of being. Of existing. Engaging with one's sensorium. Perhaps that was why the idea of food had been included in the system, after all.

Dear picked up somewhat with the food. Not as much Ioan had, nor, it seemed, as much as its partner had hoped, judging by their own apparent anxiety. Dinner was good, necessary, but plagued with silences. Even after, as the three sat talking, their conversation was full of nothings.

It wasn't until they poured wine and moved to the couch that Dear began to open up.

\emph{``I script a lot of my conversations. Perhaps most,''} it said, staring into it's `glass', wide-rimmed to make way for a fox muzzle to lap. It had little in the way of lips. Ioan felt strange drinking wine from something akin to a bowl

Ioan looked up. ``Mm?''

\emph{``I was just thinking.''} It shrugged, swirling its wine. It took a few laps. \emph{``Earlier, when I was sharing that bit about the Name with you, I had that all scripted. It was all pulled together in my head. The whole thing. I'd make a few jokes. Lead you on. Tell you the name, and then we'd bask in the wonder and truth of it.''}

Ioan nodded, silent.

\emph{``Just like I spent dinner scripting this conversation.''}

Dear's partner gave its shin a playful kick. The fox grinned.

\emph{``It's thoroughly ingrained. I'm pretty sure most people do it, of course. It's just,''} it frowned, sighed. \emph{``I had the whole thing scripted and planned, and then you asked questions — as you are meant to, of course — and my script collapsed.''}

``I''went off script``, you mean?''

\emph{``Mmhm.''}

``Sorry about that, I--''

\emph{``Oh goodness, no!''} Dear laughed, shaking its head, \emph{``I'm trying to apologize here. Don't steal my thunder. I just meant to say that you asked good questions and got me thinking, and I wasn't expecting that.''}

``It likes to proclaim,'' teased Dear's partner.

\emph{``It's not \textbf{not} true.''} Dear smirked. \emph{``But anyway, I'm sorry I got all quiet, I didn't mean to put a damper on things.''}

``You didn't, I--''

\emph{``I did, though. Dinner was like some depressing silent movie.''}

``Don't sulk, fox,'' its partner said. ``Dinner was fine. And let poor Ioan finish.''

Ioan grinned, letting the banter play out before continuing, ``All I meant to say was that I worried that I'd offended with my questions.''

\emph{``Not at all.''} The fennec furrowed its brow. \emph{``I mean, not really. I felt offended, is what I mean to say. When you asked how Life would react to you being a part of this investigation, it stung. An unfair reaction, though. Just one from the gut. I was offended because I realized that I'd invited you along on this as some sort of tool. Something I could wave about and say,''See, look what I have!" A tool or a trophy. Offense borne of shame."}

Ioan looked down into eir wine, taken aback.

\emph{``Doubly unfair of me, and for that I apologize.''} Dear raised its glass. \emph{"So you asked a really good question because it made me question my own role in this hunt. It made me think of what others would think. Me bringing along an amanuensis and historian. It made me think of why I'm doing so. Something I hadn't considered as well as I thought.}

\emph{``And I think the reason for me doing so goes further than even I had planned. I think I have you along as a means of keeping me grounded. A means of keeping the clade from just doing what the clade has always done yet again, of--''}

The fox abruptly stopped talking and its glass down on the table. Its ears were standing erect and its fur bristled down along the back of its neck. Hackles raised. It looked frantic.

Ioan looked to Dear's partner for explanation. They sent a very faint sensorium ping in response.

Sensorium message. That was it.

The message lasted less than a minute before the fox leapt off the couch and dashed off to another room, forking almost as an afterthought along the way.

The fork turned quickly and padded back to the couch. It didn't seem to be able to sit, and instead kept up pacing in front of the couch, before Ioan and its partner.

After a few tense laps of wine, it said, \emph{``Qoheleth just sent me a message.''}

``What?'' Ioan rushed to place eir glass on the table with Dear's. ``You mean Life?''

\emph{``He asked me to call him Qoheleth, but yes. He sent me a message. Can I pass it on?''}

Dear didn't wait.

The message began with a flash. Highest priority. It came with a rush of adrenaline and a sensation of falling. Sudden and intense fear replaced with an incongruously jovial voice. An old voice, almost Santa Claus-y. The contrast made Ioan's teeth ache.

"Hi Dear, this is Qoheleth. Not Life Breeds Life, But Death Must Now Be Chosen, but Qoheleth. I'm glad to see that you've kept at it and gotten so close. I'm not sending this to deter you, but to cheer you on. I'm going to send you a bit more information — just you, mind! — but I want you to get the rest of the clade in on this. I want to see if you can get them working with the same delightful fervor you and Ioan have.

"So anyway, here's the bone I'm gonna toss. You should be looking at Node: {[}32c5a64b66d0338be4373d796cf1eae5343f1077{]}. That'll get you right to my door. May need Gist Node: {[}0fedcbbb5e9839936ce799ece39fcd49{]} to help, too, though you already have the key, I think. I expect most, if not all of you, though, you understand? You're lovely, Dear, and I can't wait to see you and your friend, but I'd like to host as much of the clade as I can.

``I'm quite excited for this, and I'm totally looking forward to see you all, yeah?''

There was a moment's silence, a sense of lingering, and then, "Oh, and thank you, Dear. You've made this a treat. You're the closest one to the thing I'm after, and I'm glad this tickled you as much as has me. I think you and I both know why, too.

``Anyway, see you soon, fox. Cheers.''

The relative calm that fell over Ioan signified that the message had ended.

``Holy shit.'' Ey slouched back into the couch, eyes wide.

\emph{``Right? Hold on, don't go anywhere. Going to reduce conflicts while I make the calls.''} The fork of Dear quit without fanfare.

Ioan shook eir head and said again, quieter, ``Holy shit.'' Ey reached for eir glass of wine.

"``Bone I'm going to toss,'' hmm?" Dear's partner mused. ``He makes it sound like a game.''

Ioan nodded and watched them spin their wine glass between their palms by the stem, watched the wine creep up the sides from centripetal force.

``It showed you, too, then?'' ey asked.

They laughed, ``Of course. I know I've not been hitting the books or the streets like you two, but I'm still in this. I was the one who pointed it to you.''

Ey nodded, feeling eir cheeks flush. ``Of course, sorry. Do you know what he meant by''closest one to the thing I'm after``?''

``Maybe. I only really have an inkling, though, and I'd rather let Dear explain.''

Ioan nodded again, ``That's fair.''

There was an uneasy silence for a few minutes. The two sat on the couch, sipping their wine and mulling over the message.

For eir part, Ioan was considering the strange dichotomy of the familiarity with which Qoheleth had addressed Dear — ``see you soon, fox'' — as well as \emph{why} the fact that this seemed incongruous to em. It was difficult to think of Qoheleth as a member of the same clade as Dear, someone with whom Dear shared a root identity, after so long of thinking of this person as someone entirely different.

Silences have their own rhythms, Ioan knew, so ey waited until there came a point where ey could ask, ``About all this, do you know much more about the whole Name business?''

Dear's partner looked up. ``Who, Qoheleth's?''

``No, I mean the whole name of the poet.''

``Ah.'' They shrugged. ``Not particularly. I just know it's something the clade has an almost religious fixation on. Most of them, at least.''

``Do you know it?''

They laughed. ``Oh, gosh no. I mean\ldots{}well, do you know why Dear's a fox?''

``Why's that?''

``Because it likes foxes.''

Ioan felt as if ey'd stumbled. Dear's partner laughed.

``Seriously, that's true. But also, it was an experiment. I don't know the Name because I'm not allowed to know the Name, that much is obvious from the clade's reaction to this whole business. But I also don't know the Name because I'm pretty sure Dear doesn't even know it. Not anymore.''

``How do you mean? I thought all of the Ode clade knew the Name, kept it secret and close to their hearts or something.''

``Many do, I've been told. And I think that Dear does this too, in its own way. That way means doing its best to forget it and to move on.''

Ioan nodded slowly. ``To get to the acceptance stage of grief?''

Dear's partner nodded. ``So it did its best to forget.''

``Is that something that one needs to work on, then?''

``Have you forgotten anything recently?''

``I, well--'' Ioan stopped and thought for a moment. It was a difficult question to comprehend, much less answer. How could ey know whether or not ey had forgotten something by going back through eir thoughts?

All the same, ey prowled through eir memories. Even just those from the time ey had been spending with Dear. They were jumbled, sure, and lots of impressions, but nothing was forgotten that ey could think of. With focus, ey could recall the entire afternoon on the prairie with startling precision.

``I'll spare you by passing on some thoughts from Dear,'' they said. ``We aren't gifted with eidetic memories when we upload, but neither can we truly forget anything we experience after that point. It's as thought each memory is labeled with a priority level from zero to ten, and when it hits zero, it's forgotten. Except the actual scale only goes down to point-oh-oh-oh-oh-one or something. We can kick it way to to the back of our minds, down the priority list, but we can't forget it. The system won't let us.''

Ioan nodded. ``So Dear tried to forget, tried to kick that memory all the way to the back of its mind. What does that have to do with being a fox, though?''

``Know much about exocortices?''

``Sure, I've got a few up and running for storing long term stuff. Hell, I've got one for this project. Isn't that kind of like forgetting?''

``Almost, but you can never forget that they exist, can never forget the passphrase, right?''

Ioan frowned, directing it to eir wine rather than Dear's partner.

``But exos also need part of your sensorium to match, right? That way you can't just tell someone your passphrase and let them in.''

Ioan frowned. Ey had a hunch of where this was headed.

``So Dear put the Name into an exo all by itself, and then tried to change its sensorium enough that it couldn't get back in.''

``I see,'' Ioan said, sipping at eir wine again. Dry. It left em parched. ``It's a fox because it likes foxes, but that wasn't the goal. The goal was to no longer quite be the same Dear that put the Name into the exo.''

Dear's partner nodded.

``How did it do that? By forking?''

Another nod. ``Forking and mutating, forking and mutating. You can change your form easily enough, but it's much harder to change your sensorium. I don't even know how many times or tweaks it took. That's how it got into instance artistry.''

``Damn. That's intense.''

Dear's partner grinned. ``It's an intense fox.''

``True enough.''

``It'll be back soon enough. Let me throw a question back at you. What are your thoughts on the last thing Qoheleth said?''I think you and I both know why``?''

Ioan settled back into the couch with the remainder of eir wine and thought for a moment. ``I'm wondering if he was talking about what Dear did to forget the Name. On one hand, it sounds like a sort of congratulations. Like,''I'm glad you're able to move on," but after all that talk of the clade and all of what Dear said earlier, I'm not sure if that's the whole story."

``How do you mean?''

``Well, has Dear mentioned to you the more conservative side of the Ode clade?''

Its partner winced and nodded. ``Plenty.''

``It said that Qoheleth is from that conservative side. I wonder if that's not working out well for them.''

``Conservatism?''

``Yeah. Retaining all of those things from the original Michelle Hadje, yet following a dispersionista path more in letter than in spirit. Dear called them batty.''

``It's called them that to me, too.''

``I'm just wondering if it's right,'' Ioan said, finishing eir wine. ``Maybe they are batty. And getting worse.''
