The designated meeting point was the prairie in front of Dear's house. Ioan was confused as to why they didn't just meet in Qoheleth's sim, until ey realized that many members of the clade had not met in years or decades, or, in the case of up-tree instances, ever.

For a family reunion, it was quite stiff and formal, tense. \emph{Probably not the best of circumstances to regather the clade,} Ioan thought.

Ey focused on eir job as amanuensis.

Ey was surprised at the variety of the cladists. It made sense, of course, for a Dispersionista clade, but it was the direction in which the differences headed which intrigued em. The most notable difference was the gender presentation ratio. It was heavily skewed feminine. Michel Hadje had been born male, ey remembered, but had never transitioned, yet here was a crowd of primarily women, all similar enough to appear related, but different in their own ways. Kemmer indeed.

Ioan supposed it was due to the individual preferences that each long-lived fork had gained in its time away from the root of the clade. The remaining Odists who had not changed, or who had changed very little where the ones who Ioan suspected were the less liberal bunch Dear had mentioned. They all looked fairly similar.

Ioan couldn't help but think that they represented a lot of the various shames and repressions that Michel had held, that everyone held. It was an interesting dissolution strategy.

There was one other fox, as well. A female fox, similar in many ways to Dear, though with natural coloration rather than the iridescent white fur that Dear maintained. Dear gave her a tight hug and introduced her to Ioan as Serene, the one who had designed the landscape of its property. Ioan liked her at once.

Michel himself was notably absent, though Dear assured the historian that he was still very much alive. \emph{``He said that, if anyone should remain behind, it was him, as he had started this whole damn thing.''}

Ioan shrugged and nodded. Dear gave a small smile and shrugged as well.

There were a few tag-alongs, folks immediately identified as out-clade. A few friends, and a few partners, singular and plural. Some who Ioan suspected were like eirself, historians and helpers brought along to witness and record. One of the conservatives (at Ioan's guess, at least) had even brought a reputation analyst along with him, a slight Asian gentleman who introduced himself as Qián Chunyu.

Dear announced that the party would be leaving in five minutes.
