\hypertarget{ioan-balan-2305}{%
\chapter*{Ioan Balan — 2305}\label{ioan-balan-2305}}

After the assassination, with no one to lead them and no reason to be there, the rest of the Odists and their friends left. Dear's pacing wound down, and it eventually stopped, shoulders sagging.

It paused, and then turned to Ioan, \emph{``Come on, let's go back.''} Then it turned and addressed some others near by, primarily from the same stanza, by the historian's guess. \emph{``Any of you are welcome, too.''}

It was Ioan, Dear, Serene, and Praiseworthy — the first line of the stanza and down-tree instance from Dear — who wound up back at the house. They entered the sim about twenty meters from the house, where Ioan had originally arrived, and trudged slowly up to the house.

Dear's partner greeted them at the door, silent. Perhaps Dear had sent ahead a message, for the individual mostly stayed out of the way of the four. They disappeared and returned shortly with mugs of coffee.

The four witnesses slumped into the couch, Dear and Serene leaning against each other, and Dear's partner settled on a stolen dining-room chair before them all.

``So,'' they said, finally. ``What happened?''

\emph{``One of the conservatives played their hand. He brought along an assassin, and as soon as Qoheleth revealed his reasoning for revealing The Name, the assassin acted and then quit. My guess is that Qoheleth hadn't forked and won't be heard from again, and that Guōwēi, the assassin, was a fork who will `mysteriously' experience some problems merging back. No culpability for its \#tasker or \#tracker instance.''}

``Ah\ldots{}''

Silence fell on the group again.

Ioan waited for one of those ebbs in the rhythm of the silence before clearing eir throat. ``Perhaps it's too soon, but may I ask after everyone's well being? Their thoughts on the matter?''

Serene shook her head. Praiseworthy offered, ``I'm not surprised, really. Not happy, but not surprised.''

Ioan turned to Dear. ``You alright?''

It was a moment in responding, before it nodded. \emph{``I'm with Praiseworthy. I'm not surprised, but not happy. Kinda pissed, actually,''} it said, smiling sardonically. \emph{``That was short-sighted of them, though, because I have a hunch that Qoheleth was right.''}

``Right?''

\emph{``About the need to age, to die. About forgetting.''}

``Does this have anything to do with you trying to forget The Name?''

Dear shot a grin at its partner, \emph{``You two get along, I see. Yeah, it does. I think I did it, too, unless there's some association I missed. Can't remember it for the life of me.''}

``You'll have to tell me how you did that, sib,'' Serene laughed.

\emph{``Later, yeah. I think Qoheleth was right, though. We need forgetting. We need breeding and change and death.''}

``So how do you feel about the assassination?'' Ioan asked.

\emph{``I'd prefer that not be the only means of death, of course. Perhaps the primary way should be through\ldots{}ah, suicide is not the best word, but it's what I mean. Through choice, just like Qoheleth's old name.''}

Life breeds life, but death must now be chosen.

Ioan nodded.

\emph{``It's like I said. Batty. They're all batty.''} It stared at its paws, one of them brushing through its sib's forearm fur. \emph{``It's like some sort of Methuselah syndrome, or reverse Alzheimer's. Instead of being doomed for forget, we're doomed to remember. Doomed to remember everything. We can't forget, and it all gets to be too much for one mind.''}

``What about exos?''

\emph{``Exocortices are a fix, but an iffy one. You're still stuck with the knowledge that they exist, and their inventory. That's why I can't forget \textbf{that} The Name exists, or that there's an exo containing it which I can't access. Not unless I go through the whole shitty process again — sorry, Serene, it wasn't pleasant — with that bit of knowledge, and then what? I'll have the knowledge that I have an exo that I can't access pointing to something of dire importance.''}

Ioan shifted, leaning forward to rest eir elbows on eir knees, eir chin in eir hand. Ey sipped eir coffee as ey thought.

Serene piped up next, ``I get what you're saying, Dear, but I don't want to die. I don't want you to die, either.''

Dear's partner, frowned. ``Neither do I, fox.''

The fennec laughed and shook its head, ears flopping about. \emph{``Trust me, I don't either. I don't think many people do. I just think we need death, or something like it, as part of the system.''}

``Something like it?'' asked Praiseworthy.

\emph{``We need a way for an individual to end. We also need a way to create new individuals. Qoheleth called it breeding, but it could just as easily be a way of ending one individual and having them live on as another.''}

The others nodded. Silence once more.

Finally, Dear gave a lopsided smile, \emph{``Perhaps that's my next project.''}
