\chapter{Michael}

Michael woke blearily to the sounds of muffled giggling, rubbing the sleep from his eyes and lifting his head off the pillow.  He couldn't quite make out what was going on in the bed next to his own, but it appeared to be quite fun, or at least funny.

Rooming with his friends came with its benefits, but also its drawbacks. No one had been particularly shy about the fact that part of the reason they had come to the convention in the first place was to play around and get laid, and that was just sort of part of the bargain when it came to rooming with others.  He smiled slightly that it was those two who had started messing around before he and his own bed-mate had; he knew Bomber had quite the crush on him.

On that note, he rolled over in bed, putting the giggling behind him, and slipped his arm around the still sleeping Bomber.  He fit snuggly behind the slightly smaller form, doing his best not to rouse his friend, content for the moment just to enjoy the shared warmth of laying close to someone.  Bomber, for his part, simply mumbled something incomprehensible and appeared to go right back to sleep, comfortable against Michael's front.

He apparently dozed off, because the next time he woke up, the giggles had been replaced with muffled panting and the quiet, rhythmic rustle of\ldots{}it couldn't be much more than a blow job, given that only the blankets seemed to be rustling, rather than the entire bed.

``Morn','' mumbled Bomber.

``Shh, quiet,'' Michael whispered, confirming his hunch with a look over his shoulder.  ``Very important things happening over there.''

There came a laugh from the other bed, along with a muffled giggle. ``Very important, verrrry warm,'' Alexis replied, voice slurring with the effort of enunciation while receiving oral sex.

Michael rolled slowly onto his back and canted his head to watch the goings on, while Bomber sleepily rolled over next to him and rested his head on Mike's shoulder.

They couldn't see Corrin, and with as skillful as he seemed to be, could barely hear the fox moving rhythmically beneath the covers, except for the rustle of blankets on hair.

Skillful indeed.  Before too much longer had passed, Alexis' eyes shot open and his jaw dropped, breath catching in his throat only to be let out in a hasty, ``Oh fuck.''  Alexis shuddered, Corrin drastically slowed his movements, and Michael and Bomber looked on in appreciation.

``Mmm, well done, you two,'' Michael offered, getting a breathy giggle from Alexis and a grin from Bomber, whose own hand was inching its way down over his front, seemingly casually but obviously aiming for the crotch.

Both Michael and Bomber had slept only in their underwear, and watching the little show did have Michael somewhat worked up, so he tolerated the touches -- tentative at first, then a little more exploratory over the tented boxer-briefs that he wore -- though it felt a little awkward with Bomber.  He knew how much he meant to his friend, but considering him only a friend, felt he had little he could offer that would satisfy him. He tended towards women, usually, but wasn't above the friendly touch.

Corrin slunk from under the covers with a sheepish grin on his face, muttering, ``Hi, guys.''  He kissed Alexis on the cheek, took the other's hand in his own, and guided him out of bed.  ``C'mon, let's grab the shower first.''

Alexis nodded and managed to slip out of bed behind his friend, tugging his discarded boxers along after him and using them to cover his crotch, walking quickly behind Corrin, who was doing his best to hide his own erection.

``Have fun,'' Bomber offered.

``Yeah, and save some hot water for the rest of us.''

Michael and Bomber settled comfortably back into bed, Bomber nestled in against Mike's side as he continued to pet gently along his friend's flagging arousal, his own pressed firmly to Michael's hip.  After a silence, he asked, ``This okay, Roo?''

Michael nodded, eyes closed.

Another long silence, then, ``Can\ldots{}can I do any more?''

Michael hesitated a bit.  There was no denying that the touches felt good, but that lingering sense of awkwardness remained.  ``Um\ldots{}no.  Not this time, maybe soon?'' he offered.

Bomber nodded, abashed, and settled himself back against Michael's side.  The touches slowed, but continued, more carefully than before, lest they cross a boundary.  Eventually, they settled to a stop, and Bomber simply slipped his arm around Michael to hug himself closer, murmuring, ``This is good, too.''

Michael nodded in agreement to that, brushing his hand up along Bomber's back to hug around his shoulders, helping to keep his friend warm against him while they waited on their own turns at the shower.  It would be a bit, yet.
