\chapter{Sascha}

``Sky, I'm really sorry about earlier, I promise I'll do better about the pronouns thing.''

Sascha laughed and leaned themself in against Peter, slipping their hand into his and entwining their fingers. ``Oh, don't worry about that. I dumped my friends' drinks all over them and fucked up my finger in the process of trying to say hi to you, I'm pretty sure I'm the one that owes you the apology.''

Peter laughed as well, and the two of them settled in to the bed they would be sharing for the rest of the con. They had splurged for this trip since Sascha wouldn't be flying and Peter was paid fairly well. They'd gotten a room to themselves with a king bed, and had piled all the myriad pillows up against the headboard in order to create a sort of cozy nest for themselves. After an evening of drinking and watching Volare get drunker than everyone, they had felt the need for a space that was quiet and soft. It was here that Sascha felt most at ease, opening up around Peter, leaning closer and closer to him as they had talked, getting more and more affectionate.

``Sky, I promise, it's fine! I'm just, uh\ldots{}I'm just really happy to see you. Like, I don't think I've been this happy to meet someone for the first time in a long time.''

Sascha tucked themself comfortably against Peter and nodded bashfully, ``It's really good to get the chance to actually meet up in person, and I'm really glad-''

They were cut short as Peter fumblingly nudged their head toward his and pressed a shy kiss to their lips. The kiss lingered for a brief second or two before Peter settled back, averting his gaze and admitting shyly, ``I, ah\ldots{}I just wanted to\ldots{}have wanted to for a while.''

``It's okay,'' murmured Sascha, twisting a little to face Peter more directly and slipping their arms around him. ``I'm not complaining one bit.''

Peter smiled and helped to tug Sascha a little closer to him, saying, ``I've never really kissed\ldots{}I mean, I guess I should say I've only really kissed girls\ldots{}er\ldots{}women in my life. Oh\ldots{}that sounded bad\ldots{}''

Sascha laughed and leaned up to kiss Peter once more, shaking their head. ``It's fine, Shadow, really. Is it any different?''

``Ohh, I dunno,'' he said, trying to pull what was obviously his best attempt at a sly look. ``Might have to continue experimenting to find out.''

Peter, Sascha discovered, tasted slightly of beer, and slightly of the sea, in some inexplicable way. Mike had never been much for kissing, though it was something Sascha had always found to be enjoyably intimate, so they relished the opportunity. Peter was an active kisser, too, leading his partner through his actions, guiding them with his hands on their sides and back, first closer to his side, then, with a gentle tug, up into his lap, leading Sascha to straddle his thighs and lean against him as he leaned back on the headboard. The kisses grew in intensity, as did the tension in both of their bodies.

``Mmn, slow down, just a sec,'' Sascha whispered, pulling back.

``Everything alright, mink?'' Peter asked, looking concerned.

``Yeah just\ldots{}just need to slow down for a few, little bit of vertigo, feels a little sudden.''

``Okay, didn't mean to rush, that was just really nice.''

Sascha smiled and slipped their arms up around Peter's shoulders, ``It was nice. Very nice, trust me. Just needed a second.'' They relaxed against his front and calmed their breathing, ``Did you figure out if kissing me was different?''

Peter laughed at the question and nodded, ``It is, but damned if I know how. Maybe it's just that everyone kisses different, who knows.''

Sascha grinned and nodded, ``Thought so. Here, lets just get a little more comfy on the bed and we can go back to exploring.''

Through concerted effort, the two slid a little further down onto the bed so that Peter rested mostly on pillows instead of the headboard, and Sascha was able to rest their weight more evenly against his front, stretching almost luxuriously along him as they leaned up to meet him in another kiss, moving more slowly and deliberately this time. Tongues teased at each other and hands gripped at shoulders as the couple worked on gaining the comfort that had come so quickly online in a new context.

This time, as the kisses grew more intimate, Sascha quelled their anxiety and opened themself to Peter's obvious desire. They clutched themself closer to him with hands on his shoulders and pressed warmly to his front, feeling the way he moved slightly against them, feeling the slight bulge of his erection grow into a firm ridge against their thigh, feeling his hands move down to the small of their back and pull them to him as his hips nudged gently upwards.

``This okay?'' he breathed quietly. Sascha nodded in reply and pressed gently down to him in time with his own motions, slipping back into the comfort and intimacy of the kisses. Their mind was focused on that warmth, focused on making sure that Peter felt as good as they could make him in the moment. Their own arousal, much more constrained by panties and an undershaper, felt secondary to sharing the moment.

Over time, Peter's motions became more insistent and he rolled the two of them onto their sides, still clutching close as he ground his hips firmly to Sascha's. Kisses grew more passionate and hands rubbed along sides and back as the couple rocked together in the bed, both seeming content to be simply be that close, even fully clothed.

Sascha's nervousness began to pick up once more at the thought that Peter might want to go further than simple grinding and kissing in bed, unsure if they were ready to feel that exposed before someone they had just met in person for the first time earlier that evening. However, Peter broke the kiss first and gave a sudden buck of his hips, then shuddered in Sascha's arms, letting out a shaky moan that trailed off into something like a sigh.

Understanding dawned on Sascha and a feeling of intense emotional warmth overrode their anxiety. They simply clung tightly to their lover as he shook gently against them, reveling in the feeling of someone experiencing the rush of pleasure in climax so close to them, sharing in that through proximity as best as they could. There was too much fabric in the way to feel much more than a gentle pulsing of that firm ridge pressed to their thigh, but Sascha could tell that the orgasm was intense, if unexpected.

``S-sorry,'' moaned Peter, turning his head slightly toward the covers as if to hide his face. ``I think\ldots{}I think I was a little more pent up than I thought\ldots{}''

Sascha, practically purring in contentment, replied quietly, ``No, no, it's okay. That was actually really delightful. Are you okay?''

Peter worked to calm his breathing as he slowly settled down against Sascha, nodding. ``I'm fine\ldots{}I'm fine. Though I'll need to change pants before too long. Um\ldots{}thank you, Sky.''

Sascha laughed and pulled themself even closer to Peter, placing a delicate kiss at the corner of his mouth and marveling at how perfect it felt to be so close.
