\chapter{Michael}

Saturday morning -- nearing afternoon by the time Michael, Bomber, Alexis, and Corrin drew the curtains and made it out of the room -- was a pleasant affair.  The four made their way to a nearby coffee shop, managing to pick up two more along the way: a lion and his intensely shy friend who looked to be some sort of blue fox or wolf, if the tail was anything to go by.

They shared coffee and gossip, laughter at the expense of Alexis and Corrin, and the Shy Blue Fox produced a clipboard with paper from his messenger bag and polled everyone for their species and began sketching.

Michael, from his position next to the Shy Blue Fox, watched the sketch take shape.  He wasn't much of an artist, himself, but always found it fascinating to watch artists work, turning what looked like the simplest of shapes into something that carried meaning.

``Is that you, Roo?'' he heard a husky voice from behind him, feeling crossed arms settle onto the back of his chair.

Michael turned quickly.  Something about the voice tickled his memory in strange, not altogether unpleasant ways.  A short man with a well-kept goatee stood back upright behind his chair, crossing his arms over his chest and smiling down to Michael.

``So it is.''

``Do I know\ldots{}'' Michael began, half rising out of his chair.

It was the height that tipped him off, more than anything.  The skin was rougher, the hair cut from waist-length to a sort of unisex pixie cut, the facial hair, the masculine, well-built chest.  There was something about how this person was exactly the same height as\ldots{}

``Glade!  Holy shit, is that you, Glade?''

The other man nodded, then bust into a wide grin, uncrossing his arms and holding them open in an invitation to a hug.  Michael stood fully from his chair and moved cautiously into to the hug, wrapping his arms firmly around Glade for a good long moment before stepping back once again to look over him.  The hug felt familiar, and yet incredibly different at the same time.

``You look\ldots{}ah\ldots{}very different,'' was all he could manage.

Glade laughed easily, tossing his head to clear the hair from in front of his eyes.  ``That's an understatement.  What do you think?'' he asked, standing a little taller.

Michael couldn't quite keep his mouth from hanging open, much less form any words.  ``I\ldots{}you\ldots{}well you look good!  You'd always talked about\ldots{}but I didn't think\ldots{}''

Glade kept grinning, reaching forward to pat Michael gently on the cheek, ``Don't worry, don't need to think too hard.  I'm doing things that make me happy.  I won't pester you too much, I just wanted to say hi.  It's been, what, five years?''

Michael struggled to define what he was feeling, the violent mix of old emotions combined with the surprise of seeing Glade after so long.  All he could do is nod.

The two stood in silence for a moment longer before Glade reached to give Michael's bicep a squeeze, ``Well, it's good seeing you.  I'll let you get back to it, maybe see you around?''

Michael nodded and croaked, ``See\ldots{}see you.''

When Glade sauntered off and he turned back to the table, he found everyone staring up at him silently. Alexis was the only one who had known Michael long enough to know of the stormy end to his relationship with Glade.  It had been kept behind closed doors for the most part, except for one notable exception, to which Alexis had been witness and help Michael clean up the blood from his broken nose.

``Sorry,'' he mumbled awkwardly.  ``Old friend.  Ex.''

The corners of Alexis' mouth twitched up slightly into a smile.

Bomber, sitting on the other side of Michael from the Shy Blue Fox, rested a hand on his knee and gave it a gentle squeeze beneath the table.  ``You okay?  Look kinda shocked.''

Michael nodded and scooted the last few bites of his breakfast burrito around on his plate before giving up and wrapping his hands around his coffee cup and leaning back in his chair.

``Yeah, it's just a bit of a shock.  We were only together for a year and a half or so, but she\ldots{}uh, he now, I suppose, cut contact after a bit of a messy breakup. It's just a surprise.''

``Been a long time then?''

Michael nodded once more, ``Yeah, about five years or so, I think.  Sh- he, I mean, had always talked about gender and stuff, didn't really think they'd\ldots{}change.''

Rubbing his hand on Michael's thigh comfortingly, Bomber nodded.  ``That'd be a big shock, I guess.''

Michael relinquished his coffee mug to rub his hands over his face before patting at Bomber's own on his leg.  ``Jesus.  Yeah.  It's\ldots{}not bad, of course, I'm happy for\ldots{}him, but I think I just need to think about it for a bit.''

Michael kept quiet through the rest of the brunch with his friends.  Bomber lost interest before long and went back to talking with Corrin and Alexis.  The lion had been edging closer to the Shy Blue Fox, and eventually seemed to cave and just rest his head down on the other's shoulder. watching the lazy sketch session.  The Shy Blue Fox hadn't said more than a handful of words through the whole morning, but the lion didn't seem to mind.  Con love, Michael thought.

It took them longer than Michael would've liked to make it out of the coffee shop.  He hadn't successfully worked through the mess of thoughts and emotions surrounding seeing Glade, and so different now, at least not enough to make it back into the conversation.  However, the hard wood of the seat hadn't let him relax at all, and so he'd been antsy as he alternated between wandering through old memories of his mistress (master?) and watching the Shy Blue Fox finish up his sketch with firmer strokes of his mechanical pencil.  It was a little cartoonish for Michael's taste, but he'd muttered his appreciation and thanks as the Shy Blue Fox tugged the sheet of paper from the clipboard and skimmed it to the middle of the table.

Eventually, a critical moment seemed to be reached when enough people decided that they were done and started clearing up paper cups and clinking plates to bring to the trash and dish drop.  Michael looked cautiously around himself before breathing a sigh of relief when Glade was no where to be found.  He scraped the uneaten bites of his burrito into the garbage and set his place along the growing stack above the trashcan before following his friends out into the sun and warmth.

They trundled back to the convention hotel before all seeming to split and go their separate ways. Alexis made his way to the art show to bid on a piece he'd heard would be in it.  Corrin followed for a few yards before getting intercepted by a friend of his and dragged into a growing conversation circle.  Bomber gave Michael a questioning look before heading off to the Dealer's Den to see if, luck of all luck, they had a mouse tail for him.  The lion and the Shy Blue Fox drifted down the hallway, away from the hubbub of the central lobby to, presumably, make out some more.

Michael stood for a few moments, finally free of the burden of conversation so that he could think about what had just happened.  Glade had always been\ldots{}

He shook his head to pull himself out of his reverie.  He was staring into space like some lunatic.  He forced his feet to move, carrying him toward the bank of elevators that would take him back to his room.  He did need to think, but he certainly didn't need to do so in the lobby.

He wound up sharing the ride up with a gryphon in suit (which took up most of the back of the elevator, and a skittish, stocky fellow who pressed the button for two, then spent the entire short ride with his palms pressed firmly over his eyes.  When the door opened and he didn't move, Michael gently guided him out of the elevator and received a mumbled, ``thanks.''

Michael shrugged to the gryphon and hit the door closed button.  The gryphon shrugged back, exaggerated in suit.

Three floors up, Michael made his way out of the elevator, giving the silent fursuiter a wave before trodding off to his room.

Housekeeping had obviously been through the place, replacing glasses, cleaning the bathroom.  He poured himself a rum and coke on a whim -- it was a con, after all -- then flopped down onto one of the freshly made beds and clasped his hands over his front, staring up the ceiling.

There hadn't been a huge, prolonged break-up; just a rough month of small spats and then the crushing argument wherein they had realized that they knew each other less well than they had originally thought.  That was when Glade had spilled her -- no, his -- heart out about the ways in which gender intersected with his life, their relationship, and his sexuality.  Michael had been dismissive, and it hadn't gone over well.

``You get only what you deserve, roo,'' Glade had growled, punched him in the face, and, minus a few curt emails, that had been the last either had seen of each other.
