\chapter{Sascha}

The day wound down slowly, and since all had been out and about on their feet all day, none were all that keen on heading to the dance. Dinner had been a simple, if stressful affair at an overcrowded sandwich place.

Afterwards, everyone had decided to congregate in Maverick, Volare, and Vish's room. The fourth member, Anna, hadn't been able to make it to the con, and they hadn't been able to pick up anyone else by the time the con rolled around, so Maverick had a bed to himself while Volare and Vish alternated between cuddling and arguing in their own bed.

Volare had, of course, procured a fifth of rum and a two-liter bottle of coke, despite Vish's grumbling. Everyone sat down on the beds and the single office chair, passing around one of the two water glasses filled with rum and coke, while Vish claimed the second glass as his own without any rum. Eventually, Peter caved and ran up the one flight of stairs to his and Sascha's room to get a few more glasses.

``So how's it goin', Sky?'' Volare asked, his voice perfectly level, but the redness in his cheeks showing that he'd had two rum-and-cokes to everyone else's one. ``With Shadow, I mean. Seems like things are going well.''

Sascha blushed as Maverick immediately laughed. ``Ignore him. Things are going well. We had a good night, and today was good. It feels\ldots{}I don't know. It just feels good to be close to someone again. Some awkwardness, you know, with the gender thing. Nothing bad, just kinda finding ways to work it out, I guess.''

Volare nodded, hugging an arm around Vish next to him. ``You sure everything's okay, though? I hate to go all motherly-gay-dude over you, but I just want to make sure.''

Passing the last of the drink off to Maverick, Sascha nodded. ``I think so. I worry that I'm too outside of the realm of experience, for him, though it seems like he's trying, in his own way.''

Volare nodded again, and a silence fell over the room as Maverick set about mixing another drink, this one stronger than the last. He was larger than anyone in the room (though that was hardly a stretch, given how small Volare and Sascha were), and tended to make things to his own tastes and constitution.

There was a quick knock on the door, and Sascha jumped up to open it, letting Peter back in carrying two glasses and a small metal flask. ``I've got the glasses, and I've also got some crappy whiskey some rando in the hall filled my flask with. Evan Williams or something equally awful.''

``Mmm, shitty bourbon,'' drawled Volare.

The group laughed and welcomed him back into the circle, letting him take his spot by Sascha. He poured a finger or two of whiskey into one of the glasses and beckoned for the coke, passing the other glass to Maverick in exchange, then topped off his own glass with soda.

The pleasant banter continued around the room, minus the bits about Peter now that he was there. At some point someone put some music on through their cell phone, though later, Sascha was hard pressed to say who exactly had done so. Something chill, calm, something to fill the silences when conversation waned.

Sascha noted that, when he wasn't drinking from the communal rums-and-coke going around the circle, Peter was also sipping from the flask that he carried, and quite obviously getting drunker as the night went by. That was okay, though, they figured. They were drinking plenty, themself, and it was good to feel the warm buzz surrounding everyone as the night wore on. Even Vish seemed to be getting in the spirit, laughing along with jokes and getting closer and closer to Volare through the night.

``'m glad you all seem pretty cool with me tagging along like this. Know I'm new to the channel and all, but I'm glad Sky put in a good word for me,'' Peter said quietly during one of the little lulls in the talking.

Maverick, always a happy person and a happier drunk, laughed and leaned over to give Peter an awkward sort of sideways hug. ``Of course, man, you seem cool, and I know we trust Sky.''

Peter returned the half-hug and grinned to himself, looking sleepy. ``Yeah, he's a good mink,'' he said, sounding satisfied.

The silence lingered on for a few seconds before Sascha hunched their shoulders and quietly murmured, ```They're'.''

Peter laughed loudly and hugged his arm around Sascha's shoulders, pulling them firmly toward his side. Definitely drunk. ``He, they, whatever. You can be my good little minkyboy too, right?''

The silence continued to stretch out, glances were exchanged.  Eventually Sascha sat up a little straighter, trying to look as dignified as their drunk self could manage. ``I'm not feeling very boyish. I know I'm maybe not as much of a girl as you'd like, but I'm not a boy.''

There were a few nervous laughs around the group, but Peter furrowed his brow. ``I'm trying to compliment you, Sky. I think you make as good a boy as a\ldots{}as a\ldots{}as a whatever.''

Sascha watched Peter fall into a sulk and frowned. They didn't feel like there was much that they could do. The drunk reasoning with the drunk is a fancy way of talking in circles.

It was Vish, of all people, who saved them the trouble. ``Hey, it's getting late, and I want to crash. Sounds like folks have stuff to work out, too, so maybe we can catch up tomorrow?''

Maverick caught on and stood up right away, only wobbling a little bit. ``Hey, Shadow, was really good to get the chance to catch up. I'm out early in the morning, so\ldots{}'' he trailed off, offering Peter a hug, as was customary.

Peter struggled to his feet and leaned silently into Maverick's hug, then seemingly on impulse, hugged Vish and Volare as well. He straightened up deliberately and made his way back to Sascha, who had made it to their feet by then as well, and held their hand, firmly entwining fingers with fingers.

``Drive safe, Maverick. See you guys later,'' Sascha offered, trying to sound light-hearted
