\hypertarget{yared-zerezghi-2124}{%
\chapter{Yared Zerezghi — 2124}\label{yared-zerezghi-2124}}

Yared was not sure how he felt that the politicians — true politicians, at least — had been right. Demma had said, so, Jonas and True Name had said so, and yet something about the whole process felt slippery to him. It was a feeling beyond even that, for while that implied that it was simply politics as usual, this was something more visceral. It was slimy, like the algae that clung to his skin after he'd gone swimming in a small pond during a visit west: something that made him specifically feel disgusting.

Because they \emph{had} been right, hadn't they? They'd been right that there were strings to be pulled. They'd been right that politics was a game that was played by the bigger players, that the bigger players used the smaller ones as pawns, that the goal was some non-zero-sum game of pushing the populace around like a fungible good.

He had been the pawn, and his belief had been his utility. He was the knight moving three spaces up, one space over to outwit some other politician's bishop.

They'd been right, both Demma and the sys-side pair, because support for secession had swung his way with surprising rapidity, and there had suddenly been other strident voices that had once been on the other side of the equation agreeing with him, arguing along side him for the right of the System to become a political entity of its own.

There had been a logical procession to their thought process within their posts. It wasn't some sudden coin-flip, but over the course of the week, debates on the DDR-adjacent channels, where it didn't cost credits to post, suddenly swelled, and he'd seen the light dawning in their eyes, such as they were, as they realized that the System's political landscape fundamentally differed from that phys-side, that it couldn't but differ, given the root functionality of the populous, of the reality that sims were the only way to live. It was a true anarchy in that way. There was no ruling class because of what utility would there be for a ruling class when one could just split off and create one's own sim or set of sims, such that any attempt to rule from some central sim could simply be ignored as though it had never happened.

True Name and Jonas, now openly named, had been integral in helping convince him originally, and their words had played an enormous role through him to convince others. ``There are sims in which a strict monarchy rules,'' True Name had said. ``There are places governed by a theocracy. The Catholic church remains, albeit in reduced form without a bishopric, relying solely on adherents phys-side uploading all papal pronouncements, a near exact copy of the Vatican the phys-side popes and cardinals are represented by scrolling fields of text. Yet what influence could they hold on any other sim? What possible sway could they hold over anyone who didn't subscribe anyway?''

And so he dutifully passed these on under the tutelage of True Name and Demma, and they, too, influenced the voices on the DDR.

But for the voices to swing so quickly bespoke influence beyond just him. It showed that he was not the only pawn, that many of these other strident voices that quickly changed their voices were under the control of the big players phys-side, and perhaps sys-side as well; why wouldn't True Name and Jonas be talking to other DDR junkies like himself?

He was too afraid of them, now, to ask.

All he could do was sit by and watch, and pray that the secession amendment wasn't altered to include some equally slimy additions that would limit the total freedom granted by the secession.

Even there, he was lucky, so far. The clauses about declaring war had been strengthened, the clauses about asylum seekers hardened with wording surrounding the impossibility of extradition and the acknowledgement that any such seeker would no longer have a tangible physical affect phys-side. In fact, the only provision that had felt sour was one to cut off communication with the System from suspected terrorist cells, but it had done little to dampen the feeling of success from the overall amendment, the overall referendum.

The only issue, in fact, was a personal one. All of these changes of the amendment had been made under his name. Others had convinced him to add them. Even the sour change had been suggested and Demma had strongly suggested that it be included.

The end result was that his name was inextricably linked with the amendment, meaning that those who hated it — indeed, those who hated the entire referendum — began to hate him, too. They hated Yared Zerezghi specifically.

And boy did they hate with a passion.

His name had become a curse in their circles. He wasn't just the man who had introduced the amendment, he was the man who poisoned any hope of control over the System, that very System that they had declared a danger or a source of labor or a host to terrorism. He, Yared Zerezghi, was personally responsible for all that was wrong with the System.

When he mentioned how much he felt like a scapegoat to Demma and the pair sys-side, both had reassured him that that fervor would soon die down, and both had assured him that, as their names were also inextricably linked with the bill, they were feeling some of the same heat.

He wasn't sure that he believed them, though. Politics phys-side at the governmental level did not have the same level of personal hatred. At best, Councilor Demma might have some sort of parasocial relationship with his supporters and detractors, but at that point, he was still just a figurehead, an abstract concept of a person and that concept was a stand-in for a power so far beyond the quotidian masses that it hardly mattered. At best, True Name and Jonas were as intricately linked to the very same anarchy that ruled the rest of the System. Their role — indeed the role of the entire Council of Eight — was one of guiding the System in the form of its core functionality, interfacing with phys-side on behalf of those sys-side, rather than interfacing solely with those sys-side.

And so Yared kept taking his walks, kept eating spicy food and getting drunk on tej, to shed what he could of that slippery, slimy feeling that still clung to him whenever he thought too hard about his position in all of this.

He had become a hero and a villain for this, though, and there was no shaking that.

\textbf{The Only Time I Know My True Name Is When I Dream:} What can we do to soothe your worries, Yared, except tell you that your vision is becoming reality?

\textbf{Yared Zerezghi:} I don't know, really. Probably nothing. There's nothing really to be done when no one else will put their name on the amendment. I feel like it might be an intentional move by Demma and others to ensure that there is someone they can put the blame on who has an actual human face.

\textbf{Jonas:} That may well be true, actually. If I were still working phys-side and needed to influence a referendum from the DDR, I'd probably do the same.

\textbf{Yared:} Is there anything I can do about it?

\textbf{Jonas:} Nope! You're stuck with it, my friend, and for that I'm eternally sorry. The best you can hope is that everyone will forget about you, and the best you can do to ensure that is to become a loud voice on other issues, hopefully ones that a lot of people agree with, so that you simply become ``the loud voice'' instead of ``the secession guy''. This is turning into the biggest thing the DDR has voted on essentially ever, though, so it's going to take a lot of that hollering to drown your voice out.

\textbf{True Name:} And even then, because your name is on it, that is likely what you will go down in the history books for.

\textbf{Yared:} Uuugh. I've been thinking about that, too. It makes the concept of dying terrifying. As long as I'm alive, I at least have some hope of trying to become a less divisive figure.

\textbf{True Name:} You could upload. There is no death here, after all.

\textbf{Yared:} I'm seriously considering it, after this. At least that way, they'll know that I really meant what I said, and then I'll become someone they don't have to worry about.

\textbf{Jonas:} And you can help us keep fighting the good fight by whispering in everyone's ears.

\textbf{Yared:} That's \emph{precisely} why I want out, Jonas, and you know it. If feeling like some sneaky little political figure is what's making me feel bad, why on earth would I keep doing that?

\textbf{True Name:} Jonas is an asshole, do not listen to him.

\textbf{Jonas:} I am, yeah, and I'll have you know that True Name just punched me in the shoulder, if that's any consolation.

\textbf{Yared:} Do it again, and maybe I'll feel better.

\textbf{Jonas:} Confirmed, she did it again.

\textbf{Yared:} Ahhh, such relief!

\textbf{True Name:} In all reality, Yared, do think more about uploading. We would welcome you, here, and I am sure that, should anyone step down from the council (the Russians might when there is no need for their representation), you would be welcome to take their place. That would not be slimy politicking, just helping the System out.

\textbf{Yared:} You two are on the Council, how would that not mean slimy politicking?

\textbf{True Name:} I will let the insinuation that I am in any way a politician slide this time, but you are on thin fucking ice, buddy.

\textbf{Jonas:} True Name's an asshole, don't listen to her.

\textbf{Jonas:} Third punch to the shoulder confirmed.

\textbf{Jonas:} But really, no need to worry. This is 1000\% the slimiest politicking that the Council has ever done. Most of the rest has been, like\ldots{}``how do we keep forking from getting out of hand?'' or ``let's set systime to start when the reputation market begins'' or ``what if we could create telepathy''. It's bullshit.

\textbf{Jonas:} Fun bullshit, but it's bullshit. You'd like it.

\textbf{Yared:} I might, at that, yeah. I'll think about it.

\textbf{True Name:} Please do, we would welcome you.

\textbf{Jonas:} Lighter topic: what most excites you about the prospect of uploading? Beyond getting away from ignominy and beholding True Name's indescribably beautiful countenance, I mean."

\textbf{Yared:} Isn't she a skunk-person?

\textbf{True Name:} An indescribably beautiful skunk-person, thank you very much.

\textbf{Yared:} Uh, I don't know. Honestly probably meeting you two in person is the biggest draw. You seem really fun to be around.

\textbf{Yared:} Hopefully this isn't insensitive, but are you two a couple?

\textbf{True Name:} God no.

\textbf{True Name:} Jonas may be pretty, but he drives me up the wall. I would murder him in his sleep two nights in.

\textbf{Jonas:} If I didn't get to you, first. We're good friends, but not on that level.

\textbf{Yared:} Okay. Thanks for clearing that up. Was just wondering.

\textbf{Yared:} Wait, \emph{can} you murder other people?

\textbf{True Name:} Yes. Some enterprising individual found a way to disrupt the concept of self so quickly and so thoroughly that one basically disintegrates and, just like an avatar crash, all you are left with is a core dump, and no one has figured out how to deal with those in a place that is a consensual dream.

\textbf{Yared:} Seriously???

\textbf{Yared:} What the fuck.

\textbf{Yared:} How often does that happen?

\textbf{Yared:} Fucking terrifying.

\textbf{True Name:} Oh, not often at all! It is pretty hard to actually make the virus, as it does require some tailoring to the individual, though doubtless that same enterprising individual is working on a way to make it universal, if they have not already been murdered, themselves.

\textbf{Jonas:} And before you ask, no, there's no way to prosecute them, even if we found them. They could just fork and keep on living somewhere else, changing themselves to look like someone else.

\textbf{Yared:} Ugh.

\textbf{Yared:} I'll just have to trust you, I guess.

\textbf{True Name:} Do you not?

\textbf{Yared:} Slimy politician, remember?

\textbf{True Name:} There is a punch on the shoulder waiting for you as soon as you upload, my friend.

\textbf{Jonas:} Tiny little skunk fists. Don't worry, they don't hurt.

\textbf{Jonas:} OW

\textbf{Jonas:} Unless she punches you in the kidney.

\textbf{Yared:} Hahaha. I stand by my assessment that you two sound fun to hang out with.

\textbf{Yared:} You can change how you look that drastically up there?

\textbf{True Name:} In theory. I do not know of anyone who has actually managed to do so.

\textbf{True Name:} I am a special case due to some psychological/neurological damage from getting lost. Those up here who are furries are those who so strongly identified with their furry selves on the 'net that they began to think of their human selves as as the avatars and their furry selves as the real versions.

\textbf{True Name:} The reason I got around it is that Michelle's neurological issues meant that she oscillated between her human self and furry self, and I just happened to be forked during a wave of her furry self. That also meant that I (and each of her forks) lack the effects of that damage.

\textbf{True Name:} Or most of it, at least. You have mentioned the speech patterns before.

\textbf{Yared:} Yikes, that sounds kind of horrifying.

\textbf{True Name:} It was. I still remember it. I remember how often I felt terrible due to the constant oscillation that only settled down when I focused or utterly relaxed. Were I able to choose at will, I do not think that this would have been a problem, and you would likely have been talking to me as Michelle Hadje, not as True Name.

\textbf{Yared:} Well, I'm happy for you, even if that makes me sad for Michelle.

\textbf{True Name:} She is spending her retirement relaxing, so there is less of that for her.

\textbf{Jonas:} Is there anything else you're looking forward to, Yared?

\textbf{Yared:} I suppose just getting away from the DDR. I don't think I could manage to just drop it out here, as there's not really anything else I'm interested in enough to replace it.

\textbf{Yared:} Up there, though, I'd be forced to do something else, and that'd really keep me from getting so anxious about everything.

\textbf{Jonas:} Makes sense. What sorts of things do you think you'd go for?

\textbf{Yared:} I like food, I guess. I like walking. When I'm not really around here, I'm sleeping, eating, or walking. I've never had the chance to really go for a hike anywhere that isn't still in Ethiopia, but I imagine there's places like the Alps or Himalayas that are delightfully cool.

\textbf{True Name:} There are, yes. Plenty.

\textbf{Jonas:} A lot of the earliest sims were based around nature, actually. It's as if people wanted to reach for places that they loved phys-side.

\textbf{True Name:} Or to counteract the thought that they now live in a computer.

\textbf{Jonas:} True Name, naturally, takes the pessimistic approach.

\textbf{Yared:} To turn it around, what do you both like best up there?

\textbf{Jonas:} Oh shit. You can't do this to me. I'm not ready!

\textbf{True Name:} He loves that he can still be a slimy politician without any of the actual hard work.

\textbf{Jonas:} Ugh.

\textbf{Jonas:} The problem is, you're not wrong. I loved what I did phys-side, and I have to admit that I still love it here.

\textbf{Jonas:} I also really like coffee. Coffee and food. I get to have all of those that I want without worrying.

\textbf{Jonas:} Oh! And alcohol. No liver disease, and also you can choose when to sober up.

\textbf{Yared:} Oh damn, that's awesome. I like wine well enough, but being drunk is mostly escapism. If I could find that fun balance with friends, that'd be nice.

\textbf{Jonas:} You can't phys-side?

\textbf{Yared:} If I had any local friends, maybe!

\textbf{True Name:} Ouch. Well, you have friends up here, and we would gladly take you to bars good and bad.

\textbf{True Name:} As for me, I love all of the variety in sims and people. When I am not working or sleeping, I will walk the public sims, jumping from one to another when I have had my fill of them.

\textbf{Yared:} That sounds nice. I've only traveled a few times, and still within Ethiopia. There's different climates and such, but only so much.

\textbf{True Name:} I will take you walking with me, then.

\textbf{Jonas:} And I'll be a slimy politician with you!

\textbf{Yared:} Ugh, you're the worst.

\textbf{Yared:} Anyway, thanks for letting me vent and lifting my spirits.

\textbf{Yared:} I needed it.

\textbf{Jonas:} Of course, Yared.

\textbf{True Name:} And please remember, uploading is always an option, and we would welcome you with open arms. I know that you will come join us, sooner or later.
