\hypertarget{qoheleth-2305}{%
\chapter*{Qoheleth — 2305}\label{qoheleth-2305}}

Transcript of Node: \href{http://35.165.134.227/node/bea0cf302fcd00863f0c67a91b1a75c0e4ba4863}{{[}bea0cf302fcd00863f0c67a91b1a75c0e4ba4863{]}} with descriptive text by \#d5b14aa.

\emph{The footage shows two persons. One of them has to be Dear, Also, The Tree That Was Felled, who is an up-tree branch of the Ode clade, eighth stanza. No one else has ears that big, nobody else can somehow speak in italics. The other took some research, but I'm confident that ey are an instance of Ioan Bălan, a historian and writer. Ey are a tracker, but only just, as eir habits tend toward few to no long-running instances. This instance is either \#tracker or one tasked to this project.}

\emph{The two persons are sitting outside of a cafe, from whom I obtained this footage. They are in conversation. Going to sit down and watch this.}

\begin{quote}
\textbf{Dear, Also, The Tree That Was Felled}: Thanks for your letter, Ioan. Lots of really good stuff in there, most of which I'd missed simply out of nearsightedness.

\textbf{Ioan Bălan}: You've got me hooked on this project, have to say. It's fascinating stuff.
\end{quote}

\emph{Dear grins at this.}

\begin{quote}
\textbf{Dear} We - that is, some other Odists down-tree from me - have come up with some further hints about the message.

\textbf{Ioan}: Oh? Anything good?

\textbf{Dear}: I suppose it depends on your definition of good.

\textbf{Ioan}: *snark, good natured* Oh great. Excited already. *more earnest* The fascination continues. Well, let's have it.

\textbf{Dear}: So, one of us did an exhaustive search of some records and found an old archive server running somewhere.
\end{quote}

\emph{Oh goodie. Better start gearing up.}

\begin{quote}
\textbf{Ioan}: Wait, start at the top. What were they searching?

\textbf{Dear}: They were searching for the block of encrypted text — not what was in it; they cracked that long ago. They searched for the encrypted text itself, and they came across an archive server.

\textbf{Ioan}: Old node boxes? Wow, even I feel crusty using one of those, and I'm a historian.

\textbf{Dear}: You're only a little crusty *laughter*. They found the archive server though, and there's a bunch of intriguing stuff on it. New, old, the whole thing. There's stuff from ages ago, shortly after we got here, and stuff from a few hours ago.

\textbf{Ioan}: You're kidding. Newly created stuff?

\textbf{Dear}: I know, it's ridiculous.
\end{quote}

\emph{The fox's ears flop when it gets excited and shakes its head, never noticed that. It's kind of cute.}

\begin{quote}
\textbf{Ioan}: Never met anyone who could actually get one working well enough to add new nodes. So the encrypted text was in a node on the server?

\textbf{Dear}: Yeah. It's still there. *pause* Just sent the URI.

\textbf{Ioan}: I\ldots{}well, I'll have to take it at your word that it's the same as the one you found earlier, I'm not going character by character.
\end{quote}

\emph{Dear seems a little frustrated at this. About Ioan's slowness? I know I wouldn't compare the files. It sounds exasperated.}

\begin{quote}
\textbf{Dear}: Of course, Ioan. Promise it's the same, though. Needless to say, we found a crusty old archive with the block on it, and there's other public nodes on there as well. I'm guessing a bunch of private ones, too.

\textbf{Ioan}: Anything good in those?

\textbf{Dear}: Nothing\ldots{}penetrable. It's all fairly opaque. To me, at least.
\end{quote}

\emph{Ioan grins at this.}

\begin{quote}
\textbf{Ioan}: Thus us meeting?

\textbf{Dear}: \emph{nodding} Yes. The only bit that I have any insight into is the deck listing, which I think might be another bit of old encryption--
\end{quote}

\emph{Ioan groans aloud, at which Dear grins.}

\begin{quote}
\textbf{Dear}: My sentiments exactly. It is another encryption scheme which relies on a deck of cards for a stream of random numbers. I haven't dug into it in years because the decryption process is so slow, but there may be a node on that box containing the encrypted text.

\textbf{Ioan}: Want me to have a look, then? The techier stuff is going to go right over my head, you know that.

\textbf{Dear}: It's not all tech, promise. I just want you to give it a read and see what you pick up from it, you know? Put your amanuensis hat on and just spend some time experiencing.

\textbf{Ioan}: You think highly of me. No complaints, of course, but I feel I have to ask, why can't someone from your own clade fill this role?
\end{quote}

\emph{Dear's quiet. Struggling for words? Our Dear? This must have hit it hard.}

\begin{quote}
\textbf{Dear}: We\ldots{}differ. The Odists, I mean.

\textbf{Ioan}: ``Differ''? Within the clade?

\textbf{Dear}: Yes. A hallmark of Dispersionistas is that we treat each of our forks as fully-realized individuals. We may have a shared past, but from the point we fork, we grow ever further apart.

\textbf{Ioan}: I assume you mean more than just a matter of increasing conflicts.

\textbf{Dear}: Yes. Although we Odists limit our instances to the one hundred available names, we still consider ourselves Dispersionistas as we never merge back down-tree. But, that aside, we also want someone out-clade for this. \emph{I} want someone out-clade for this.
\end{quote}

\emph{Ioan seems taken aback.}

\begin{quote}
\textbf{Ioan}: Do the other Odists not like that I've been brought on?

\textbf{Dear}: Of the ones who know, most are fine with it.
\end{quote}

\emph{Now frustrated/confused.}

\begin{quote}
\textbf{Ioan}: ``The ones who know''?

\textbf{Dear}: You have, of course, noticed that you have not interacted with any of my cocladists. I have told some about hiring you, but not all.

\textbf{Ioan}: Alright, I suppose. If you're independent, then I guess it makes sense that I be your amanuensis rather than the clade's.

\textbf{Dear}: Yes. Perhaps more evidence that we're split on how to tackle this in the first place. Different camps, different strategies, infighting. Ioan, you have to understand that, when a clade gets old, it starts to get a little batty.
\end{quote}

\emph{Calm down fox, I'm working on it. Not so frantic.}

\begin{quote}
\textbf{Dear}: Some clades try to get around this by keeping a certain core group of instances — talking mostly Dispersionistas, mind — in a setting that keeps them as sane as possible. Something that feels very `normal'. Or maybe some are researching forking from earlier points, from down-tree, rather than from where they are now.
\end{quote}

\emph{It furrows its brow.}

\begin{quote}
\textbf{Dear}: We don't. First of all, we started way too early on for that to be a thing. We trusted that change itself would keep us sane, that as instances diverged, especially with mutation algos in place, they'd change enough to keep us from falling apart.

\textbf{Ioan}: And that didn't work?
\end{quote}

\emph{Long pause.}

\begin{quote}
\textbf{Dear}: It kind of worked, I'll put it that way. I feel pretty well rounded, as much as that means, and I'm sure those across the clade from me do too, but it's complicated. You would not recognize my cocladists as Odists without knowing beforehand. It's like having a very close sib that was raised by a different family in a different sim.

\textbf{Ioan}: More different than you'd expect, then?

\textbf{Dear}: `Expect'\ldots{}fits strangely for this. The problem is that they're still \emph{us}, and we're still them. Clades are families of separate individuals in a lot of ways, but you have to realize that, in the end, they're still one individual. We're more different than one individual should be. Does that make sense?
\end{quote}

\emph{It does, Dear. That's why I'm doing this.}

\begin{quote}
\textbf{Ioan}: I guess so. *pause* So some of your clade would prefer I not be a part of this?

\textbf{Dear}: More than that. They feel that investigating the matter of the Name being written is too risky, too close to investigating The Name itself.

\textbf{Ioan}: I don't know how I would respond to that.

\textbf{Dear}: That's my field, Ioan. Don't worry about it.
\end{quote}

\emph{Ioan holds up eir hands, looks apologetic. The fox has tilted its ears back.}

\begin{quote}
\textbf{Ioan}: Sorry, Dear. I hope I'm not overstepping at all.

\textbf{Dear}: *calmer* Don't worry about it. It's all good, I promise. It's just that we're really good at arguing, so I've been dealing with that a lot the last few days. That's why I hired you; I'm relegated to an administration role so I'm a bit on edge. Let's get back to the archive server, yeah?

\textbf{Ioan}: Sure thing. Where did you say your cocladists had found it?

\textbf{Dear}: Just in a search. Don't know quite the details about how, assuming just a text search of perisystem stuff, I guess? Not too sure on the terminology, I bought into being an artist pretty hard, all that knowledge is in exos.

\textbf{Ioan}: *laughter* No worries there, fox. I'm trying to keep up with you is all. I was just wondering if they found anything else.

\textbf{Dear}: You mean like the other nodes on the server?

\textbf{Ioan}: I'll poke around at those, look for ties and such. I was more wondering if they'd found anything in their search that didn't meet the relevancy threshold for them. Stuff like back-links to the server, or anyone talking about this Qoheleth. Hebel. Whichever.
\end{quote}

\emph{Silly name. Oh well. Dear looks taken aback.}

\begin{quote}
\textbf{Dear}: Hadn't really thought to ask. I don't suppose they did, though. Do you think it's worth having them search around more? Lowering the, uh, relevancy threshold? *laughter*

\textbf{Ioan}: Yeah, I think so. Though now that I've got it too, I can do some of that digging myself. I want to see who likes the Tanakh so much as to name themselves that. And why `kemmer'.

\textbf{Dear}: I\ldots{}well, it's complicated and out of scope, but it relating to fluidity of gender is relevant to the clade as a whole. Very big, for us. I've opted out.

\textbf{Ioan}: So I noticed. It makes sense, though.

\textbf{Dear}: Glad someone's thinking about this stuff. You're sounding more like a--

\textbf{Ioan}: Private investigator?

\textbf{Dear}: *laughter* I was going to say historian, sounding more like an historian every time we talk. But you never know, maybe you'd make a good PI.
\end{quote}

\emph{That was fast! I may have less time than I had thought. Dear's lovely, and it's totally right: on the other side of the clade, there are some who'd not like this kind of digging. Too entrenched. Too Conservative.}

\begin{quote}
\textbf{Ioan}: I can't tell whether or not I should be flattered.

\textbf{Dear}: It's a good thing. Just keep digging, and we will too. I'll be about. Got a few more things to wrap up to finish the current gallery exhibition, but after that, I'm just going to work on this — with you if you don't mind — and try and figure out what's even happening in the clade. Keep in touch, yeah? Ping me whenever?

\textbf{Ioan}: Will do. *pause* Wait, you're an instance artist, right?

\textbf{Dear}: Yes, why do you ask?

\textbf{Ioan}: Why don't you fork to work on both at the same time?
\end{quote}

\emph{Dear shrugs, grins, quits. Very lovely fox. Really quite lovely.}

\emph{No time to dawdle watching Ioan try and figure out up-tree instances, though. Must be getting ready. Quit this instance, flush the server of extraneous crap to guide Ioan a little more effectively — yeesh, how old is some of this stuff? Need to re-encrypt a bunch of it anyway — and maybe get ready for some visitors.}
