\hypertarget{qoheleth-2305}{%
\chapter*{Qoheleth — 2305}\label{qoheleth-2305}}

It had been long enough that I was thinking of myself as Qoheleth now. I had even begun introducing myself as Qoheleth, whenever I went out, just to try it on for size.

That I had never gone out was of little concern.

I liked the sound of it, though. I liked the connotations of `teacher' and `gatherer' and `director of the assembled'. I wanted to feel the way that it felt to be someone different, and I'd found at least a part of that in this name, the name that \emph{I} had chosen for \emph{myself}. I'd not yet taught or gathered, but I was working constantly to attain that.

And `Hebel'. Hebel was another name I had picked up. Vain, futile, mere breath.

Qoheleth's words, in the book they had written so very, very long ago were all about hebel — or hevel, could never tell which. ``This, too, is meaningless,'' the author had written, after taking a walk down a path in life and exploring.

That's not how I envisioned the name, though.

I thought of the two names as signifiers. Thought of the two \emph{sources} of names.

Qoheleth. That was the name I had given myself out of hope. It was a name of goals and aspirations. It embodied the things that I wanted to do. It took all of my plans and me, as the maker of the plans, and bound them up neatly into a word. A name. A rejection of The Name.

Hebel was the name I had given myself out of despair. It was a name of self degradation and a way of reminding myself that, lofty as all my goals may be, they were all vanity. Mere breath.

Together, the names reminded me that I was doing this for a reason. All of these resources, mostly found objects and hand-me-downs accrued over the years (if you never leave your private sim and never publish outside of it, you get surprisingly little), were being built up and strung together into a cohesive goal. A net.

They, the resources, were all nothing. The reasons were all nothing.

The whole plan was nothing, except for the truth underlying it. Not to fear God, but to\ldots{}to something. To get the whole clade to see. My clade.

My \emph{old} clade.

I was now Hebel Qoheleth.

Hebel Qoheleth.

The old name was dead. I was Hebel Qoheleth.
