I loved this feeling. I loved the feeling of a project getting past the architecture state to that point where you could just start to use it. You'd been writing all of the interfaces and abstract classes and such for weeks and months (or decades, in my case). Then you'd started to fill in all of the inner workings, blocks of code filling out empty pairs of braces.

And then, one day, you had enough that you could type in a command and see if it actually compiled, ran.

And then you'd probably buckle down and start writing tests, start pulling together tasks and issues and such. No such luck for me. Old Qoheleth --- I still get a grin every time I say that --- gets to just keep writing until it's time to hit the big green button. There's no testing, there's no explaining if things go wrong. Just go.

I was actually pretty excited about it.

You get old, you know? And you can't die in this place. You can suicide, maybe, crash yourself and try to corrupt the merge, and I guess if I were to quit, there'd still be someone to merge with, but they'd be dealing with the same problems.

No one ever really dies in the system. They just stop.

And I'm sure one of those will happen to me at some point, and probably sooner rather than later, but until then, I'll just keep going more and more nuts. We all will. All of us old'uns, and then before long all the young'uns too. We gotta see. They all gotta see, but we gotta see, because we're the ones in a position to do something about it.

I keep using `we', too, damnit. I'm not part of their damn clade anymore. I don't know which of them are or aren't, either, and I don't think they realize that yet.

I just need to keep working on what I can. I kicked Node: {[}67e97446cdbe3a4a3cfd5ebd75b1260{]} out into the wild, so they'll probably get there before long. After that, we finish our little game and I get my moment as Qoheleth. I get to be the one to call the assembly together, the one to teach.

And, since I know they'll get into these nodes, too, I have to add that, no, I don't bear a grudge. There's no ill will. This isn't a ``now I'll show them'' moment.

I just need them \emph{invested}. I need them fighting, which is easy, and I need them interested, which is hard. I need them invested in the problem before I stand up and clear my throat, and then I might have the authority, in their eyes, to speak, to teach.

I got them fighting by saying That Name, and I've got Dear interested. Lovely Dear.

I just need them all invested.
