\hypertarget{qoheleth-2305}{%
\chapter*{Qoheleth — 2305}\label{qoheleth-2305}}

I have them! I really, finally, truly have them!

I don't know that I have them all hooked, but I did it. I set my mind in motion by will alone. I count those who weren't hooked. Mostly first and second lines, mostly like me. How did they go so wrong, though? I'm a first-line instance. Michelle's second fork, even, and I didn't turn out so bad. Did I?

Well, okay, I turned out pretty messed up, but only because I suffered the same fate that they all will. Perhaps were already! Only I suffered it a little bit earlier. I started going bonkers from the sheer amount of stuff in my head. I started living too long, living my Methuselah life while still having my Michelle mind. Nothing was getting out of my head. Nothing \emph{could} get out of my head. An impossible poison.

I have such grand plans!

Grand plans of organizing a petition among all the founders and old clades, with the Ode clade leading and me leading them in turn. A petition to the system engineers to hire some damn developers again and stop treating this like abandonware. Abandonware that gives them, what, a dumping ground for the poor and a small brain trust? Get some devs in there and give us the ability forget and the ability to die. Hell, maybe even the ability to reproduce, to breed. The word's even in my name, my old name, for chrissake.

As I continue through my spiel, I can tell I'm hooking the liberals. The later stanzas, most of all. Dear's sold completely, I can see it on its face, fox or no. Can see it on Dear's other fox sib, on Praiseworthy. Dear's whole stanza.

The conservatives are harder to read. The whole lot look blank and stern. Stoic. They just stand there, with their historians and their analyst — the flash of his stylus as he scribbles notes in shorthand keeps distracting me. I power through, though, because it was working.

It's working because I am Qoheleth. I am the teacher. I am leading the assemblage. I am instructing them in the dangers they face, telling them what's going on in forceful, no-nonsense terms.

It's working because I am Qoheleth. I am the gatherer, the assembler. It's working because I'm the one who brought them together and gave them what they need to understand this. It's working because I'm the leader.

It's working.

And then I fuck up. I know it as soon as I do it, too. I say something about the Name. I get too proud and start going into my whys. I shouldn't have done that. It'd lose me the conservatives. They, more than others, guarded that dumb Name more jealously than all the rest.

I try to keep going to cover up my mistake, but there's that damn analyst, pulling himself up onto my stage. \emph{My} stage. It takes only a moment before I figure out what is going to happen. Takes less than a moment. I know immediately, but by then it's too late.

The damn analyst's hand slaps into my back, and there's a sudden, searing pain. A hot wire being drawn through my spine. The only noise I can manage is a sort of strangled laugh at my own foolishness.

My insides start to crumble.

Maybe I was Hebel after all. Vain, futile. Mere breath.

\emph{Havél havalím 'amár kohélet havél havalím hakól hável.}

Fuck. I was so close.

I'm glitching. Can see bits of myself spreading out.

So close.

Tunnel vision. Blackness.

So close.
