\hypertarget{codrin-balanpollux-2325}{%
\chapter{Codrin Balan\#Pollux — 2325}\label{codrin-balanpollux-2325}}

The first direction from the L5 System came in the form of a message from May Then My Name Die With Me. ``Find Ezekiel,'' it said. ``Talk with him. Be patient, be kind.''

When ey showed it to Dear, the fox's ears stood erect, and it had led Codrin out of the house to stand on the patio and watch the storm from the safety of the overhang.

\emph{``Please be careful, my dear.''}

``Do I have something to worry about? Should I be prepared for violence or something?''

It should its head. \emph{``I do not think so, no. Zeke — Ezekiel — was a member of the Council of Eight. One of the founders. He was close to much that happened in the early history of the System.''}

``What did he do?'' Codrin shook eir head. ``I mean, what is it that he's known for?''

\emph{``Forking.''}

Ey let out the air in their lungs in one, low \emph{huh}. It felt as though ey had been kicked in the stomach, and ey struggled to regain eir breath as stars swum before eir eyes. ``\emph{Forking?} You've got to be kidding me, Dear.''

The fox laughed. \emph{``I am not.''}

``I thought that that was a core aspect of the system from the beginning.''

\emph{``It was an accident at first. Someone split in two — not Michelle, before you ask — and the System automatically corrected and deleted both forks. The population was quite low at that point, and Zeke knew the victim. As part of his grief, he began to formulate the sys-side algorithms and drafted the petition to phys-side for allowing legitimate forking of personalities.''}

``And Michelle helped?''

\emph{``She coordinated between Zeke and another council-member on the logistics and how it was associated with the reputation markets, yes.''}

After a moment of staring out into the rain-clouded prairie, Codrin said, ``I'm constantly surprised at just how much of a frontier it was back then, and just how many pies your clade seems to have had its fingers in.''

Dear smiled tiredly.

``So, why did you bring me out here?''

\emph{``It is nice to talk about serious things with the sound of rain in the background.''}

``Really?''

\emph{``Of course not, my dear.''} It gestured back through the window, where its partner sat, reading. \emph{``They do not enjoy hearing me talk of that time in our lives.''}

Codrin frowned. ``I think I know the answer, but should I interview them?''

\emph{``Please do not, Codrin. I do not want to bring up painful conversations of the past, nor do I wish to you to learn all that they know from a single source.''}

``Ioan mentioned that May Then My Name has been cagey around her past as well-- No.'' Ey held up a hand to forestall a comment from Dear. ``You don't need to defend her, or yourself, for that matter. I won't push you for more history. I would, however, like to hear your reasoning for these decisions.''

\emph{``For withholding information?''}

``For withholding it, yourself. It seems as though you want us — you as in the Ode clade, us as in the Balan clade — to discover things on our own. Why?''

Dear stuck a paw out, palm up, beneath a downspout and the steady stream of water that flowed from it, letting the water soak into its fur. \emph{``There are parts of our past that I am ashamed of. May of my cocladists are, as well. You could interview any one of us about the entirety of our story, even me, and we would tell you, but we would also resent you for that.''}

Codrin waited Dear out.

\emph{``We would resent you, and the temptation to lie would be too great. It is better that you gather this information piecemeal to gain a more accurate picture of what it is that happened leading up to both Secession and Launch. May Then My Name is right. You should seek out the founders. You should seek out someone other than an Odist. You should seek out one who did not simply agree with us that far back.''}

``Alright, I can accept that.''

It leaned in to bump its nose against eir cheek. \emph{``Thank you, my dear. Be kind to Ezekiel, as May Then My Name suggests. Be patient with him. Be prepared for a difficult conversation.''}

``Difficult how?''

\emph{``He is not who he used to be. Time has not been kind to him, to his sanity. He is no longer the shrewd and funny politician he was back then. Since about the time of the launch proposal, he has returned to being called Ezekiel and donned the mantle of his namesake.''}

``What's that?''

\emph{``A prophet.''}

Codrin was not sure what a prophet looked like, but the conversation with Dear dogged em all the way until ey was finally able to find Ezekiel and get him to agree to an interview.

\ldots{}
