\noindent \emph{Here is the difference betwixt the poet and the mystic, that the last nails a symbol to one sense, which was a true sense for a moment, but soon becomes old and false. For all symbols are fluxional; all language is vehicular and transitive, and is good, as ferries and horses are, for conveyance, not as farms and houses are, for homestead. Mysticism consists in the mistake of an accidental and individual symbol for an universal one.}

\ally{Pretty.}

\noindent I didn't write it.

\ally{I know.}

\noindent I scramble through great heaps of words and sounds to try and at least pin some of them to fleeting symbols. Maybe then I'll be able to learn to see more of the accidental and individual symbols.

\ally{Too many words, too many sounds.}

\noindent Yes.

\ally{You wrote four pieces about the winds coming down over the foothills near Boulder (for, of all things, wind quartet), just to try and capture one ecstatic experience.}

\noindent I like those. I like the result.

\ally{You like the first two, most of all. They remind you of how hollow you felt, how you could feel the wind blow through you, vibrating your soul like the pipe of an organ, exciting you to ever higher harmonics.}

\noindent Yes.

\ally{But then you kept writing.}

\noindent Yeah. I make a terrible poet.

\ally{You make a terrible mystic. Your poetry's just okay.}
\newpage

\noindent How can I capture that essence of stillness? How can I become nothing?

\ally{Not reaching. Not trying.}

\noindent How can I read the ecstasy of signs? How can I feel those black birds bursting free of my hunched shoulders?

\ally{Step beside yourself. Take your own hand.}

\noindent How can I feel the cord that ties me to the center of the earth? How can I see where it leads? How can I walk the spiral?

\ally{Reach down, bury your fingers in rich earth, take root.}

\noindent The cant of ritual.

\ally{The scent of incense.}

\noindent The rhythm of chant.

\ally{The ripple of water.}

\noindent Call and response.

\ally{The flicker of a candle.}

\noindent Voices echoing voices echoing voices echoing...

\ally{Clay between fingertips.}

\noindent And then?
\newpage

\noindent March 10, 2004:

\begin{quotation}
\noindent We wandered around for a bit before ending up sprawled in a fire-escape at FHS with Shannon in my lap, me in Ash's lap, and Andrew in Kiran's lap. Andrew ditched to go shooting with Ash and Kiran, while I went to bomb a history test. That's when things started getting really weird. I had a percoset relapse (whether that's what it was or not, it felt oddly similar to the real thing: an incurable itch buried beneath my skin, to the point where I can't actually scratch it) near the end of the period, and then in choir I imploded from empathy - so many emotions from others that I had no room for my own. Then, horns grew from my chest and head, and wings from my back; a giant fox escaped, left, and exploded into a thousand birds over Viele. Mind you, none of this really happened, but I sure felt strange. During latin, I exploded from empathy in a patchwork swirl of colors while Starin et al. stared on as I banged my head against the desk. Ms. Gibert didn't notice. I yelled for help inaudibly and searched out white points of light in the black silhouette of Boulder. I yelled for Ash and searched for Moondog.

Afterwards, I figured out how to regain control (mostly) and just in time for the bell to ring. I got a small mocha at Cafe Sole, got eaten by small greenish crystals on a table while supposed psychics did fairy readings from a kids book, and here I am, about to take a shower and get ready for Great Works rehearsal, and then group, whereupon I shall request to Reiki Moondog (again) during the speakers board on gay marriage. Hopefully I don't ex-/im-plode again ^^
\end{quotation}
\newpage

\noindent April 12, 2004:

\begin{quotation}
\noindent You have come, finally, to a safe place. You have arrived at the point where it counts most, the point at which Life itself seems to fall away, leaving behind nothing of it's former shell: that blackened husk of body and mind that housed a bright bright star. Years and years, it took, places and places and each day offering good and bad, but you, lucky you, saw past that, saw beyond the grid of your perception to see inside others, touching and caressing the bright points of light that were essentially them, cherishing each for not only their good points, but for their faults as well. The energy flowed around and through you in the concentric spirals of the labyrinth and the Bat Qol kept you clean and pure with the voice of God and the Buddha in me to the Buddha in you weaved everything under the sun into Life itself. This is Rapture.
\end{quotation}
\newpage

\noindent June 7, 2004:

\begin{quotation}
\noindent I'd like to chant, perhaps Emmeleia.

\ally{Or.. you could come up with something on your own. You know, do something productive with Nanon.}

\noindent There's a thought. I still need to do those spells for Androo.

\ally{Exactly. Productive}

\noindent I've noticed that, while my emotional colors are fading, you're becoming more prominent.

Who are you?

\ally{I'm a meme; I'm the idea of Lady Sage and Master Yage,}
\ally{or maybe Eris and God. Are they the same?}
\ally{I'm me.}
\ally{I'm you. Are they the same?}
\ally{I'm the fifth line of five.}

\noindent You're an elusive bugger, that's what you are.

\ally{Damn straight.}

\noindent You're depressing, too.

\vspace{2\onelineskip}

\noindent\ldots{}hello?
\end{quotation}
\newpage

\noindent October 5, 2004:

\begin{quotation}
\noindent Eloi, Eloi, lama sabachthani.

Upon reading certain things, upon hearing certain songs, upon seeing certain people, upon smelling certain scents, upon tasting certain foods, upon feeling certain feelings and upon losing myself, it flows, the light, in through the head, out through the heart, washes over all, and, being lost in it, have found myself without.

\ally{How poetic.}

\noindent These are the white things. Cold, bright, burning, white.

Eloi, Eloi, lama sabachthani.

But the light isn't as it used to be. It was a thing to light up a day, a thing to light up me, filling completely. Now a simple thread flows from head to heart, and the light doesn't stray from the path of least resistance.

\ally{Love follows not the law of Ohm.}

\noindent Eloi, Eloi, lama sabachthani.

Light can be many things, but here, now, it means love - all four loves - and it's a strange feeling to have been so full of it for so long, then to suddenly be nearly without.

\ally{Full of what? Full of shit? How pathetic, how trite.}

\noindent Having deified love for several years, it's a shock to my faith to have it disappear, even if it only turns out to be temporary.

\ally{Faith? You're faithful? How have you EVER been faithful to love?}

\noindent Eloi, Eloi, lama sabachthani!
\end{quotation}
\newpage

\ally{What is your point?}

\noindent You know.

\ally{Yes, but it is important that you make it.}

\emph{It's the immediacy, the seamless immediacy\ldots{}}

\noindent It's about meaning and self. It's about defining where your boundaries are; your physical boundaries, your mental boundaries, your spiritual and emotional boundaries. It's about that ground-state training that you undergo so that you might step just a bit to the side. An inch. A mile. An age.

It's about breathing in for the count of four, holding for the count of two, breathing out for the count of four, holding for the count of two. It's about feeling where your feet touch the ground. It's about drawing a straight line from your center of gravity to the center of the world. It's about becoming totally present.

\ally{So that you can disappear entirely.}
\newpage

\ally{Why this? Why now?} % Why after your dad?

\noindent Why talk about ecstasy?

\ally{Yes.}

\noindent Dissociation.

\ally{Well, that was quick. I was expecting more roundabout. We would banter. You would get flustered. I would get smug.}

\noindent Derealization, depersonalization, dissociation. Pure and simple.

\ally{Well huh.}

\noindent Would I lie to you?

\ally{Oh, totally.}

\noindent Fair.
\newpage

\ally{You're not very focused.}

\noindent I know.

\vspace{2cm}

\noindent It's just

\vfill

\noindent that I'm
\newpage

%%%%%

\null
\vfill
\noindent overflowing
\vfill
\newpage

\null
\vfill
\begin{center}
    with
\end{center}
\vfill
\newpage

\null
\vfill
\begin{flushright}
    words
\end{flushright}
\vfill
\newpage

\null
\vfill
\begin{center}
\begin{Spacing}{0}
speak to me\\\vspace{-7pt}
speak to me\\\vspace{-7pt}
speak to me\\\vspace{-7pt}
speak to me\\\vspace{-7pt}
speak to me\\\vspace{-7pt}
speak to me\\\vspace{-7pt}
speak to me

that i may see\\\vspace{-7pt}
that i may see\\\vspace{-7pt}
that i may see\\\vspace{-7pt}
that i may see\\\vspace{-7pt}
that i may see

the face of god\\\vspace{-7pt}
the face of god\\\vspace{-7pt}
the face of god
\end{Spacing}
\end{center}
\vfill
\newpage

\begin{verse}[1.01\textwidth]
    I was born at the edge of the numinous.

    That is why I can tread along the border.\\
    That is why I'm able to whisper the name of God.\\
    That is why I'm allowed to know the number and how to factor it.\\
    That is why I have seven fingers spread wide and three curled toward my heart.\\
    That is why my limbs trace the curves and lines of power when I dance.\\
    That is why I sit with my back to the sun in summer.\\
    That is why my body is a canvas.

    You were born in sunlight.

    Speak secrets into my hair.\\
    Take my words from me.\\
    Spend the intercalary days telling me lies.\\
    Break my dystonia with a breath.\\
    Wash my face with salt water.\\
    Tell me the name you call yourself.\\
    Close my eyes.

    We will sleep in the shade.

    Let me bless you with smoke.\\
    Let me bathe your feet.\\
    Let me light the candles.\\
    Let me place a stone beneath my tongue.\\
    Let me taste copper.\\
    Let me draw in ash.\\
    Let me rise up until my head is in the branches and my hair becomes the leaves.
\end{verse}
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
    {\vgap1em
    At the beginning of time,\\
    \vin \vin when chaos birthed to order and disorder,\\
    we were blessed with two souls.

    One has seven eyes and can see all of the monsters in the dark,\\
    \vin \vin but is blinded by the sun.

    The other has no eyes,\\
    \vin \vin but can feel no pain.

    When order and disorder were close as children,\\
    \vin our souls experienced the world hand in hand,\\
    \vin \vin but as they drifted apart and began to fight,\\
    \vin \vin \vin some of us left one of our souls behind,\\
    \vin \vin \vin \vin and that is why we search.
    }
\end{verse}
\vfill
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
    {\vgap1em
    Babel was a collaborative effort.

    Once,\\
    we all spoke the same language,\\
    \vin but on seeing god grow increasingly anxious with the rate of our progress,\\
    \vin \vin we agreed to let our tongues be confused,\\
    \vin \vin \vin so that he could take things at a more comfortable pace,\\
    \vin \vin \vin \vin and we could be assured he would not understand us \mbox{unless} we prayed in silence,

    for only then do we speak the language of angels.}
\end{verse}
\vfill
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
    {\vgap1em
    When I speak, the words drip from my tongue as ink,\\
    and form writing on the ground,\\
    and I leave a trail behind me,\\
    and the ink stains your feet,\\
    and when you walk, words and phrases and sentences are pressed into the soil,\\
    and the ink breathes life into the plants,\\
    and even the grass will flower,\\
    and the bees will flourish,\\
    and they will both sting you and provide you with sweet honey.

    The ink stains my chin and my clothes.\\
    \vin Sometimes, I speak into my hands and stain my cheeks as well.\\
    \vin \vin I speak against my fingers and press them into my flesh until I am covered in rosettes.\\
    \vin \vin \vin I stretch my hands to the sky and marvel at how black they are.\\
    \vin \vin \vin \vin And as with the grass, where the ink stains, growth\\*
    \vin \vin \vin \vin quickens, and I am covered in soft fur.\\
    \vin \vin \vin \vin \vin I fall to all fours and hunt amid the rocks and the\\*
    \vin \vin \vin \vin \vin buildings, between cars and along trails.\\
    \vin \vin \vin \vin \vin \vin And when I am full, I curl up to sleep, and awake\\*
    \vin \vin \vin \vin \vin \vin human once again.\\
    \vin \vin \vin \vin \vin \vin \vin My skin is clean and my mind is clear,

    and I cannot speak.}
\end{verse}
\vfill
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
    The only time I know my true name is when I pray.\\
    The only time I pray is at the utmost need.\\
    To pray is to ask yourself what you dare not ask god.\\
    To answer your own question, you must step outside yourself.\\
    To step outside yourself, you must forget your true name.\\
    The only time I know my true name is when I pray.
\end{verse}
\vfill
\newpage

%%%%%

\null
\vfill
\ally{Ask.}
\vfill
\newpage

\noindent How does one approach what one can't describe?

\ally{Swing the flashlight rapidly across the room. Piece together what you can from the sweep of the beam across the walls, the furniture.}

\noindent How does one hunt down what leaves no tracks?

\ally{Unwind the maze by keeping your right hand on the wall. Pray that the walls do not move.}

\noindent How does one call down the gods to commune?

\ally{Speak thrice, and enter.}
\newpage

\null
\vspace{1cm}
\noindent There was a sort of succulent quality to the air, as though, were I to bite down on it, it would all come bursting forth at once. Dribble down my chin. Stain my shirt. It would be sweet, almost saccharine. It would beg for a pinch of salt to quell all that sweetness.

I didn't know whether or not I'd be able to stomach it, honestly. I was dizzy. I was apart from myself. Above, and beside. I was looking down at myself. Were I to do so, to bite into time itself, I would surely overflow.

\emph{Was} overflowing, I realized. Was bending forward at the waist where I was sitting. Those black choir chairs were comfortable, but made you sit up straight, so I couldn't slouch. I was bending forward, resting my elbows on my knees, and then bowing my head, bowing further.

I was overflowing, and there was nothing I could do to stop it. We weren't singing, the basses, we were watching the altos rehears a part, so it wasn't too far out of the ordinary for me to be hunched over, breathing shallow, watching myself from above.

I was overflowing, and there was nothing I could do to stop it. Hunched over, breathing shallow, and watching from a few feet up, a few feet to the right, so that I could see my shirt tear even as I felt it against my back. I was so thin, then. So thin.

I was overflowing, and there was nothing I could do to stop it. I watched my shirt tear, and my skin follow. I watched it split along my spine and peel back. It was bloodless, but not painless. The feeling of those wings, newborn and weak, slipping from the wound was raw.

I was overflowing, and there was nothing I could do to stop it. I watched the wings stretch and extend from the wound on my back. ``Aha,'' I thought. ``This is it. This is finally it. It's finally happening. I am becoming something greater, and here I am, so unprepared!''

I was overflowing, though, not transforming, and there was nothing I could do to stop it. The growth did not stop at wings. An eye. A beak. The graceful curve of a head. Plumage.

``No, this isn't it.'' I panicked, and could think of nothing else but to apologize. ``I'm sorry. I'm so sorry.''

The bird cocked its head as it climbed free of my back and perched on my shoulder. It cared not for apologies. Why would it?

Another pair of wings followed.

Another.

Another.

My hands were buried in my hair, I could see - barely - through the forest of pencil-thin legs crowding my shoulders, my neck, my head. Their weight had forced my shoulders down until my head was nearly between my knees.

We were singing now, and I was silent. How could I sing, when all I could do was beg silently for forgiveness? How could I sing with the weight of a dozen crows slowly crushing me into my seat? How could I sing when I was overflowing? There was nothing I could do to stop it

Chaos. The director stopped the choir, and as one, the flock lifted off. The weight was lifted off my back. The cacophony filled the air. I was borne up through the air by the birds. The birds were splitting, multiplying, avian mitosis. I was borne up, up. Up.

I was told afterward that my body stumbled, unthinking along the row and toward the double doors, that the director had sneered, "It sure would be nice if we had all our singers here today." I was told that folks defended me, saying I was sick, I was pale, I was feverish.

I don't know, I wasn't there. I was above the Flatirons. I was beyond terror. I was beyond joy. I was beyond sensation, beyond any emotion except for that bottomless, black guilt. Sticky. Tar-like. Bitter. The flock numbered in the thousands, and still we flew up.

The blue of the sky became white, blinded, became black, and I was sitting in the hallway. I was with my body again. I was sobbing. A teacher stared. Students gave me a wide berth.

I cleaned myself up. I went back to choir. What else could I do?

A bird had plucked something from me. Something precious. Something unknowable. Something important and integral. Something hard. Something emerald and glassy. Before the white of the sky overtook me, I saw it in its beak.

The caw it gave as my vision left me and my ears filled with static was\ldots{}triumphant? No, not quite. Triumph implies that the birds could do anything but succeed. In that sound was inevitability.

After school, - - - and I tramped through the `mini-forest' and, impelled by something of the avian within, I collected five sticks.

They had to be as straight as possible.
They had to be balanced as close to the middle as possible.
They had to be the same length without me breaking them.
They had to have been from different trees.
They had to have fallen more than a year prior.

When I got home, I lay them in a row, asked my questions, and, one by one, broke them in half.

\begin{quotation}
\emph{What had I lost?}

\emph{What had I gained?}

\emph{Where had I gone?}

\emph{Where did I come from?}

\emph{Why does memory stain me with that black, tarry guilt?}
\end{quotation}

I had forgotten about the birds until recently, but every time I feel that ecstasy --- that ekstasis --- I am pitch. I am tar. I am sticky with apology. I am the living embodiment of ``I'm sorry''.
\newpage

\noindent I'm tired. I'm so tired. I'm tired and I'm upset and I'm lost.

\ally{I know.}

\noindent I want to shout and to whisper. I want to talk about how the light flows in through the head and out through the heart. I want to put words to the feeling of falling to the ground and taking root.

I want to say how it feels when I step outside myself.

\ally{You tried.}

\noindent I guess that's all I can do.

\ally{It's not, but it's important that you have tried.}
