\hypertarget{ioan-bux103lan-2350}{%
\chapter{Ioan Bălan — 2350}\label{ioan-bux103lan-2350}}

Of all that had happened over the past several weeks, Ioan was surprised to find that it had taken until now for literally anything to feel like it had been planned. Clearly none of them had planned on Jonas coming after True Name, but all of the decisions that had been made after that had been made on the spot, snap decisions that had led to True Name moving into their house, to End Waking merging down, to the three of them all overflowing at once.

All of those had been made what felt like intolerable pressure, and it was only now that they had time enough to relax. There was an uneasy (and certainly temporary) stalemate between Jonas and True Name that gave them enough time to properly consider a decision instead of feeling compelled to make it right away.

Ey'd harbored a concern that May, one borne out of stress, might just merge down without talking further, but ey kept that to emself, doing eir level best to reason emself out of it. The last thing they needed at the moment was further doubt within their relationship.

And she certainly didn't. In fact, she drew the negotiations that followed that first discussion out by nearly a week, putting lie to that concern. Much of these discussions took place between the two skunks as they walked out on True Name's prairie.

At first, ey'd felt left out. After all, didn't ey also have boundaries to negotiate and concerns that needed addressing?

After bringing this up with May, however, she had laughed and poked em in the belly, explaining, ``I do not mean to leave you out of anything, my dear. We are discussing elements of the past that kept me from merging down, and elements of the future of the relationship between us. You are not missing anything so important, but if you would like, I am happy to keep you apprised of the general content.''

``Given how anxious I've been, I'd appreciate that,'' ey had said. ``But no need to share anything private.''

And so now ey got updates on the conversations with sensitive or personal information redacted.

They spent much of their time discussing various parts of May's life and how comfortable she'd feel sharing those through a merge, and if not, why not. They also talked with End Waking several times, the third skunk of the stanza coming out to visit her prairie so that they could discuss the ramifications of their merge and how to be more thoughtful with May's.

This wasn't to say that ey didn't have a chance to sit with them at times and discuss eir thoughts on the matter, of course.

``Feelings are complex, Ioan,'' True Name explained as they sat around a low fire before her tent. ``If they are created by memories, then there is little that I can do to completely control how I might feel about something beyond picking and choosing the memories carefully. However, one can never be sure what memories may lead to which feelings. If they come from something more intrinsic to one's personality and thought patterns, then it is even more difficult to attempt to control them.''

Ey nodded. ``That much I can certainly understand. I trust the idea that you'll be a synthesis of your various histories rather than simply May's feelings tacked onto you.''

``Yes. I cannot predict how I will feel about you after this. Your relationship and existing boundaries will take precedence over whatever happens, though. I will respect that.''

((Maybe a bit more))

Finally, though, a week to the day after the topic had first come up, Ioan awoke to find May and True Name already sitting at the table, speaking earnestly in a cone of silence. Once they noticed em, True Name waved it away and May grinned, saying, ``Sorry, my dear. We did not want to wake you.''

Ey poured emself a cup of coffee before joining them. ``Appreciate it. Hope I'm not interrupting.''

True Name shook her head. ``We are discussing our plan for the day.''

Ey knit eir brow, taking a sip of coffee. ``Is today the day, then?''

``May Then My Name think so, but we were also waiting for you to join us to make sure.''

``Well, if it were solely up to me, I'd just spin my wheels worrying about it until we ran out of time, so I suppose I'm alright with it. What all will go into it?''

``Well,'' True Name began, a fork appearing next to her. ``First I fork.''

The new instance of True Name bowed. ``And I will return to my tent in the interim,'' she said before waving goodbye and padding back out through her room.

``And then we will set up a space for me to rest in the meanwhile, and then I suppose that is all there is to it. May will fork and quit and I will process the merge.''

``And your fork is just there in case something goes wrong?''

``Or if the result is not acceptable.''

Ey frowned. ``\,`Not acceptable'?''

``If the merge does not go well or if I wind up being unable to work as I would like.''

``Or if all of my emotions get overwhelming,'' May added. ``Since I do rather have a surfeit.''

Ioan leaned over and ruffled a hand over the skunk's ears. ``Yeah, you definitely do.''

``Yes, yes, and you love me for it.'' She laughed and pushed eir hand away, straightening the mussed up fur. ``Breakfast first, though, and then we can work from there.''

After another Scandinavian-style breakfast, the three of them re-organized True Name's room. The bed was made larger and set in a corner instead of up against one wall, allowing a collection of pillows to be placed against the walls in case she wanted to lean against them or organize them into a nest.

``Are you sure you don't want to set up something out in the prairie?''

``I did consider it, but May Then My Name talked me out of it, stating that she would like to be at hand without having to spend all of her time out there, herself. Besides, if I learned one thing from End Waking merging down, it was that the less I have to think about my body, the easier it is. Comfort will only ever help.''

They also supplied her with ready water, coffee, and a few comforting snacks on one of the bedside tables so that she wouldn't have to get up just to go to the kitchen.

Another beanbag was added for May, in case True Name requested that she stay in there for any length of time, and a more comfortable bench-swing was added to the balcony in case she needed to go outside but wasn't feeling up to walking down to the prairie itself.

It felt like rather a lot of preparations to make just for a merge, but then May had last merged down eighty-three years before ey had even uploaded, nearly sixty-four before ey'd even been born, and after seeing how intense End Waking's merge had been, none of them felt up to cutting any corners and having to rush comfort after the fact.

Finally, though, there was nothing left to do, no further preparations to be made, so May took eir hand to hold em still so that ey'd quit pacing.

``I don't even know why I'm fretting so much, I'm not even the one merging.''

True Name grinned and shrugged. ``I am fretting too, my dear, do not worry.''

``It is a big event,'' May added. ``It will be an even bigger merge and, while it may be more comfortable than End Waking merging down as she has said, it will be no less complex.''

Ey sighed and nodded, squeezing her paw before tugging eir hand free. ``Right, right. I'll relax and leave you to the rest of it.''

``Please stay, Ioan,'' True Name said quietly.

``Stay?''

``Yes. Please stay. I do not think it will be dramatic, but, well\ldots{}'' She frowned as though hunting for words. ``You are a grounding person. Is that not what my counterpart on Castor said about Codrin? I do appreciate your presence.''

Ey considered any number of responses ey could give before just nodding. If nothing else, ey didn't want to hold either of the skunks up from what would most certainly affect both of them more than it would em.

May forked and the new instance climbed up onto the bed with True Name, the two skunks kneeling, facing each other, amid all the blankets and pillows.

Both Ioan and True Name watched as the down-tree instance of May scrubbed her paws over her face vigorously for a moment, gave a shaky wave, and then quit. True Name winced and screwed her eyes shut, and the May who had knelt with her on the bed reached out and took the skunk's paws in her own.

``Go ahead.''

It was still another ten seconds or so before True Name managed to relax enough to permit the merge to progress, and even then the only visual indication was a slow slump of her shoulders and a relaxing of the muscles of her face.

Ioan stuffed eir hands in eir pockets and did eir best to feel rooted to where ey stood, hoping against hope that ey could keep from pacing. Both em and May watched True Name carefully, though she seemed almost frozen, breathing shallowly despite the relaxed set of her features.

They stayed like that for nearly five minutes — two skunks kneeling on the bed while ey watched from beside it — before True Name moved again.

``Oh, May,'' she whispered, and started to sag over to one side.

The other skunk shushed her quietly and helped her to lay out on her side before settling down with her. They curled together, still facing each other, nearly snout to snout and still holding paws.

It was more than an hour later before May forked beside em, took eir hand, and led em from the room. Neither of the skunks on the bed had moved or made a sound other than May asking True Name if she was okay in a quiet murmur and the other skunk shaking her head.

Once the door was shut behind them, May let out a shaky sigh and padded over to the kitchen. ``That was very hard.''

``Why, do you think?'' ey asked.

The skunk took a moment to pour herself a glass of water before replying. ``I want to be here with you, and I also want to be in there with her, and I also want to go back in time and tell her I do not want to merge, and I also want to go back in time and merge instead of End Waking, and and and\ldots{}''

\ldots{}
