\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Debarre was still mostly full from dinner at home, but he had a few bites of fish forked from End Waking's plate. Tasty, but, as always, lacking in salt.

After they ate, End Waking tasked Debarre with washing off the plate while he tucked another small log into the stove and started the kettle for tea, which they shared while sitting on the step at the entrance to the tent, keeping the last of the spring chill away.

``So, my political junkie friends aside, do you have a better idea of what's going on with Jonas and company?''

End Waking shrugged. ``A little, perhaps. I think it is this upcoming A/V tech. I do not think he wanted--''

``Moment,'' Debarre said, holding up a paw while he sent a hasty message back home. ``Sorry. We'd been guessing at that, just sent a confirmation. Done now.''

``Please do not act on it yet, my dear.''

So serious was the skunk's tone that Debarre set down his mug of tea and turned to face him. ``I won't, but you gotta tell me why.''

``I am going to be at this meeting. I should probably not even know about their AEC, but I do because of True Name.''

``And given you and I, there's probably only one place I'd get it,'' he guessed and, when the skunk nodded, sent another message back home. ``You sure this place is secure, then? And you're sending a fork, right?''

``Yes and yes.''

``Good.''

End Waking smiled. ``I know that you do, but it is always pleasing to have confirmation that you think so much of me, Debarre.''

``Of course I do,'' he scoffed. ``But I interrupted, sorry. You were saying?''

``Right. With this AEC technology, I think that Jonas sees an opening to edge True Name out. I do not know why, but she mentioned something about a diversity of governance across Systems. I do not agree with him on this. I think he is playing a dangerous game by treating each of the Systems so different. Each System treating itself as a separate country is one thing, but potentially destabilizing them by giving each a different form of governance feels like him treating politics as his plaything. I do not like it.''

The longer End Waking spoke, the deeper Debarre's frown got. ``Yeah, ever since they set up that Guiding Council thing over on Pollux, we've been wondering about that. It sounds innocuous enough. Reasonably close to the Council of Ten over on Artemis, I guess, just folks you can go talk to about disagreements and mediation, at least on the surface. That part was inoffensive, but that they would even do such a thing in the face of the \emph{History} is just wild.''

End Waking shrugged. ``You know more than I on that end. I do not keep up with either LV beyond what you and Ioan care to pass on.''

((What EW hopes to learn from the visit with Jonas, EW is mostly just there to witness, or to be scared into silence, but Debarre worries that it's to scare \emph{him} into silence. Why is he even going? Because this feels like a step towards letting go and becoming independent))

((Debarre heads back home to afterdinner w/ a few people, talks in generalities, that something big is coming soon, that he'll keep them up to date, but that life will be getting both more and less simple in the next little bit))
