\hypertarget{ioan-bux103lan-2350}{%
\chapter{Ioan Bălan — 2350}\label{ioan-bux103lan-2350}}

Ioan quickly began to wish for boredom. They'd made it into April and so many things had happened. Assassination attempts, centuries of merging, overflowing\ldots{}

Ey just wanted to be bored.

At least they'd settled into a routine once more, and it was far more comfortable than either of the previous ones — when True Name had first moved in, and then after End Waking's merge — so ey couldn't complain too much.

True Name managed May's merge much more easily than she had End Waking's, and ey could see now the benefits of that week of negotiation beforehand. Nearly two months later, and she still occasionally mentioned a pressing memory or two from End Waking demanding attention.

It was just another part of the routine. A rocky routine, and an exciting one, but still a routine.

It wasn't all bad, of course. For every talk they had about meeting with Jonas or what Zacharias had become or some boundary one of them had crossed, there were still the pleasant meals, the shared quiet, and, ey had to admit, ey rather liked who True Name had become.

Ey had certainly liked who she was, of course. Three years of coffee dates stood as testament to that, but a large part of this, ey'd come to realize, came with just how much more settled in herself she was. Even that drive she cherished about herself had been tempered into something smoother, less laser-sharp. She was more well-rounded, more able to relax, more able to work without it occupying the whole of her.

The weirdest part, though, had to be sleep. They spent two nights staying with True Name while she processed first the memories and then the conflicts before trying to go back to sleeping separately.

She spent the next day distracted and out of sorts, first begging off breakfast to sit outside, then joining them in the common areas before getting anxious and slipping off to go lay down again. That night, she woke them a few hours after they'd gone to bed, tearfully asking to join them.

``This is so fucking stupid. I feel like a fucking kid,'' she'd said between sniffles. ``I am sorry.''

May had shushed her and held up the covers for her to climb in, letting her settle back into much the same position she had those first two nights.

It had certainly worked well enough, with Ioan rising at eir usual eight o'clock while the two skunks slept in for another two hours. Later that day, May had instructed her how to get at least some comfort out of sleeping curled up with a fork.

Still, once a week or so, they'd wake to her asking to join them, and eventually Ioan had given in and expanded the bed by a foot to at least make it roomier when she did join them. She'd at least been quite understanding when May had requested that it not be every night.

Ey was unsure of eir feelings on the matter. On the one hand, it was still intensely weird to see True Name, of all people, openly seeking affection and a shared bed, and stranger still to see just how much May's opinion of her had softened.

On the other, so had eirs. The nights when she joined them weren't unpleasant, even if it would be a while before ey was used to sharing a bed with anyone other than May. This was to say nothing about the shyness ey felt about eir body. The first few times she had joined them, ey had wrapped emself up in a sheet before leaving the bed to maintain some sense of modesty, though given that these nights had often included the skunks sleeping in, ey eventually gave on that.

And ey was genuinely pleased to see her happy, or at least on her way to happiness.
