\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

May's response to the discussion of encroached boundaries, later that night when they'd moved to the couch, knocked both Ioan and True Name off-kilter. She laughed and tousled eir hair and the fur atop True Name's head, saying, ``Well, took you long enough.''

``Wait, what?'' ey asked.

``I have been placing bets with myself on how long it would take until it came up. Whichever part of me guessed''the minute I leave you two alone together'' wins, I guess.''

True Name stared coolly at her. ``And here I was worried that you would blow up at me.''

``Of course not, my dear. If you are like me, then I, of all people, can guess the hows and whys. My position remains that, so long as everything was discussed in the open, veto-able, and come by earnestly, we will make it work.'' She smiled and leaned over to pat at the skunk's paw. ``Which is not to diminish \emph{your} feelings on the matter. How are you doing?''

``If I say `confused' one more time, I am going to lose my mind. I do not have a better word for it, though. I do not know how I feel about the touch itself. It was fine, I am sure, but I am starting to think that what is so jarring to me is that it was almost an automatic action.''

Ioan nodded. ``It felt a bit incongruous because it's a hundred percent something you'd do, May.''

``And perhaps that is why it feels fine to me: it is what I would do, I would expect nothing less from someone with so much of me as part of them now. I would like you both to feel comfortable, of course, but I am more\ldots well, `concerned' is not quite the right word, but concerned about the emotional side than you two just physically touching,'' May said, shrugging. ``Though I do appreciate you keeping me apprised. I trust you on that.''

``Well, thank you,'' True Name said, rubbing at her face, though whether out of exhaustion or to forestall tears, ey couldn't tell. ``The other thing we discussed, though, was setting a deadline of one month to get this shit with Jonas out of the way.''

May perked up. ``Are you feeling ready, then?''

She laughed, shaking her head. ``I do not think I ever will, but there is little that I can do to change that. I will change and he will do whatever the fuck he wants and I will do my best to wash my hands of it. Will you be ready?''

``Sure. I do not imagine my part in it will be big. Just be there to witness, perhaps lose an instance if he decides to go after us, too. Have you spoken with End Waking?''

``I sent him a simplex message,'' she said. ``I will ping again tomorrow if he has not replied.''

``If he has not had another tree fall on him,'' May grumbled. ``And you, Ioan?''

Ey shrugged. ``I've got my notes all in order. I don't want to do it at all, but I'm ready, I guess. Did you talk with Debarre about this?''

``No.~I\ldots well, he is not ready to engage, I think. I would like End Waking to bring it up with him, if possible. I have meddled a bit much of late.''

True Name smirked, leaned over and tugged at May's tail. ``You have, yes.''

May pulled her tail around to hug it protectively. ``Yes, yes. I know.''

The conversation trailed off from there, Ioan and May cozying up and chatting via sensorium messages once True Name had started to doze, using May's thigh as a pillow. She caught em up on gossip from Debarre — one of his boyfriends visited and was, apparently, quote the looker — and ey accused her of leaving em for the weasel, as ey always did when she visited him.

Eventually, even they fell to silence, and when May started to nod off as well, ey roused the two skunks. ``Come on, beds are comfier than couches.''

True Name nodded groggily and stood, swaying for a moment before gaining her balance once more. ``Thank you two for talking this evening.''

``Would you like to stay with us tonight?'' May asked. ``If you are this exhausted, I imagine you need it.''

She stood silent for a few moments, then nodded. ``If you are willing, yes. I am also happy to sleep out on the plain. Either would be good for me.''

May shrugged. ``That is why I asked, yes.''

When May looked to em, ey sighed. ``Perhaps tomorrow? Need a night to think on things.''

True Name's face fell, but she bowed. ``Of course, dear.''

Ey reached out and gave her paw a squeeze. ``Thanks, True Name. Tomorrow.''

She smiled gratefully and, after a hug from May, made her way to her room and out to her tent on the plain, visible as a bobbing lantern moving through the grass.

By the time ((they chat))
