\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

May's stint of overflowing only lasted two nights.

Something about the change in context, about staying with Sasha instead of Douglas, made everything feel tenuous, though. Ioan found it difficult to sleep on the padded cot that she'd added to the tent, and eventually, she must have grown tired of hearing em toss and turn, for she sleepily climbed out of her own bed and into eirs, curling up with em after confirming that it was alright.

Awkward, perhaps, but by then ey was too frustrated and exhausted to think of anything else, and the added warmth certainly worked in getting em to sleep, to the point where ey slept in until a ray of sun, creeping slowly, fell across eir face and warmed em awake.

Sasha had apparently woken up earlier in the morning and snuck away, as there was a lukewarm cup of coffee sitting by the edge of eir bed and no skunk to be found.

Ah well, at least the coffee was good and ey felt better rested than ey had before.

Ey met up with her at the shore of the lake where they talked for a bit, though it was clear that she was antsy to head out into the woods on her own, so ey eventually shooed her off, to which she bowed gratefully and said, ``My notes are on my desk. If you get bored, I would appreciate your feedback.''

Ey spent the rest of the abbreviated day reading through what she'd written, making a mental list of ideas and suggestions to pass on to her when things were a little less hectic.

That night was much the same, with the two of them talking until it was well and truly dark, then settling into their own beds until sleeplessness led to them curling together in one.

A ping from May shortly after sunrise woke em, and the jolt startled Sasha awake as well.

``Uh, sorry,'' ey mumbled, extricating eir arms from around her. ``May pinged''

Sasha levered herself up and squinted out into the orange and pink of dawn. ``How is she up before me?'' she grumbled.

``Probably because she got good sleep and I kept you up being a mope.''

She shrugged noncommittally. ``Slept well enough later on, at least. Did she say anything?''

Ey shook eir head. ``No, just a ping. No real urgency, though. Surprised I didn't sleep through it.''

``You are appropriately keyed to her, dear. I would be surprised if you did.''

``Mm, fair enough,'' ey said, grinding the heels of eir palms against eir eyes. To May, ey sent a ping in response, plus a subvocalized, ``\emph{You okay?}''

``Better, yes,'' came the reply. ``Though I am feeling quite bad about sending you off like that. Not about waking you up, though. You sound cute when you are groggy.''

Ey snorted, shook eir head. ``Yeah, she's fine,'' ey said to Sasha.

Sasha surprised em by joining em on the trek back to the house, saying only, ``I have been worried, as well.''

May greeted them at the balcony with steaming mugs of coffee. She declined a hug, stating that she felt gross, but did at least press her nose to Ioan's, and then to Sasha's cheek.

``Thank you both for giving me some space,'' she said. ``I was not expecting the both of you, but I am happy to see you both all the same.''

``Of course, May. I'm just happy to see you doing better. Or happier, at least. You look a mess.''

She scoffed and gestured a paw down at herself. ``I look perfectly fine, thank you very much.''

``You look a mess, dear,'' Sasha confirmed. ``You need a shower and a change of clothes, and perhaps another four hours of sleep.''

May sighed, nodded. ``I do at that. All the same, the wave has crested and gone, and now perhaps I can relax enough to do so. Coffee first, though.

They settled around the dining table and focused on said coffee for a bit. It was good to be back to coffee that didn't require straining out the occasional percolated ground through one's teeth.

``Are you two okay?'' May said at last.

``Tired, but that's easily fixed. Looking forward to a real bed tonight.''

Sasha kicked eir shin beneath the table. ``The tent beds are not \emph{that} bad.''

``No, they're fine, but they still pale in comparison to our bed.''

``Fine, fine.''

May looked between the two, then laughed. ``I take it this setup worked for me taking some space?''

Ioan shrugged. ``Well enough, sure. It's nice to have another option that isn't just crashing at Douglas's.''

``It was fine, dear,'' Sasha added. ``If ever either of you need some space, feel free to kick the other down to the tent and I will make it work.''

((Sasha sticks around to talk to May about Zacharias, though we aren't sure what, sends Ioan on a walk with a fork))

``How long do you think you'll stay?''

``I am too much myself to say `forever', but as long as my room is there, as long as you and May are comfortable with me being a part of your lives, I will be happy to call it home. Or at least \emph{a} home.''

``Really? No bigger and brighter things?''

She laughed and leaned over to dot her nose on eir cheek. ``This \emph{is} bigger and brighter things, my dear.''

``Well, I'm sure we'll talk about it plenty, but I see no reason not to keep your room about. I don't know what you overflowing will look like, but if it involves one third solitude and one third getting lost walking sims, I don't imagine you'll be around all the time.''

``Not at all, no. I will spend my share of time here to be alone or out walking the world. Perhaps I will even ask you to double the rest of the house so that I can be alone somewhere domestic, not just the wild.''

``Of course.'' Ey shrugged, tossing one of eir collected pebbles into the lake. ``Besides, I like having you around.''

``I am pleased to hear that. I had gathered such, but all the same, I would not want to be a bother.''

``Oh, not at all. It seems like we're all pretty good at sorting things out when they do come up, so I don't imagine it'll get to that point.''

``And I am not impinging too much on your and May's relationship?'' she asked, holding out her paw for one of eir pebbles. ``I am asking her, too, and we will continue to talk together, but I also want to you directly.''

Ey shrugged, handing over the pebble. ``I don't think so. So long as we can still have time to ourselves when we need, I'll be happy.''

She tossed the pebble out into the water. ``Of course, dear.''

They sat in quiet for a while, tossing pebbles into the water until ey ran out.

``Hey Sasha?''

``Mm?''

``Do you miss anything from before all this?''

She shrugged. ``It is hard to tell. As I have said, I liked being True Name. It was fulfilling. Every time I think about that now, though, it is intercut with memories from my cocladists. I will think about some particularly adroit political move and remember it fondly, but right along with it is a memory of giving up on using a bow drill and switching to using a striker or making fun of you for your pen collection.''

Ey laughed.

``If I am honest, I am letting a few conflicts remain. There is something pleasant about the just-off-center nature of that reality. I am Sasha, and I am also True Name, End Waking, and May. I am of three minds.''

``So long as that works for you.''

``I can always address them down the line if it does not.''

Ey nodded. ``And I'm guessing you don't miss Jonas or Zacharias or any of that.''

She poked at eir side with a claw before slouching against em. ``You do not need to ask stupid questions, Ioan.''

``Right, right,'' ey said, laughing. ``I figured no love lost, but--''

``I did not love either of them, as friends or otherwise,'' she said, waving away the rest of eir comment. ``Now that I have known other kinds of love, I am confident of that.''

Her tone wasn't upset or dismissive, but was assertive enough that ey dropped the point. ``Well, writing sounds like a good career shift, then.''

``Says the writer.'' She laughed. ``But yes. I will be leaning on you a lot for help.''

``I mean, you're leaning now.''

``Smartass,'' she said mildly.

Ey grinned. ``I mean, no complaints. Still sort of getting used to it, but May got me hooked on physical contact a long time ago.''

``A coordinated attack on your defenses, yes,'' she said. ``It makes my job easier.''

``What job?''

``Just finding a way to stick around friends. Nothing nefarious, dear.''

Ey shook eir head. ``Right, sorry. I trust you.''

``I agree with what May said, Ioan. Should I want anything beyond that, I will come by it earnestly.''

``I appreciate that.'' Ey hugged an arm around her. Ey was grateful for her looking out at the lake rather than at em, given the heat ey could feel rising to eir cheeks. ``While we're being honest, though, I think we're sort of in the same boat, honestly, given what you share with May. We can both imagine that, but not necessarily the path from here to there.''

``Precisely. I imagine the same applies to you, that you will come by it honestly.''

Ey nodded. ``Basically. Is it something you'd want?''

``God, I have no fucking clue, Ioan,'' she said, laughing.

``Definitely same boat, then. It's a problem for future Ioan.''

They fell into silence again. Part of em was itching for more pebbles to toss into the water, but ey was too comfortable to get up to collect more from the beach.

``That is the conflict I left from May,'' Sasha murmured. ``I kept some doubt from End Waking, enough to keep me grounded without keeping me torn. From May, I am keeping a little bit of overwhelming emotions. The possibility of simply falling for everyone around me is alluring. I can taste it in the memories, like a little bit of saccharine. But I am keeping a little bit of doubt from True Name so that it remains a new thing for me. I am of three minds Like a tree In which there are three blackbirds.''

Ey turned her words over in eir mind, along with whatever snippet of verse it was she'd quoted. The thought was complete. Nothing ey could respond with would add to it. It was curious, and hinted at things beyond eir ken, but it was complete.

Instead, ey said, ``You're a good person, Sasha. All three of you are good people.''

She laughed. ``And you, dear, are a dork. But come, my tail is falling asleep, and my fork's conversation with May has wrapped up.''

They walked back, then, hand in paw, following the trail as it dipped down to the water or ducked up into the trees. Back home, back to May, back to whatever it was that life had become.
