\section*{Timeline}
\addcontentsline{toc}{section}{Timeline}

The timeline of the Post-Self cycle spans just over two and a half centuries, encompasing both the creation of the upload system and the arrival of the Artemisians on the Castor launch vehicle and partial dissolution of the Ode clade.

\begin{description}
\tightlist
\item[\emph{2112 --- December 7}]
RJ Brewster gets lost, triggering a cascade of events leading to a deeper investigation into the lost.
\item[\emph{2115 --- February ??}]
The first partially successful upload, RJ Brewser, leads to a breakthrough and, shortly after, the foundation of the System.
\item[\emph{2117 --- ???}]
Michelle Hadje and Debarre pool their money to upload.
\item[\emph{2124 --- January 1}]
Systime set at year zero, day zero in order to help manage the reputation market.
\item[\emph{2125 --- January 21}]
The System secedes from the planetary governments on Earth thanks to the efforts of Yared Zerezghi, Counselor Yosef Demma, The Only Time I Know My True Name Is When I Dream of the Ode clade, and Jonas Prime of the Jonas clade.
\item[\emph{2170 --- Throughout the year}]
Most planetary governments begin compensating the families of those who choose to upload.
\item[\emph{2238 --- July 28}]
Ioan Bălan uploads to use the compensation to help eir brother, Rareș Bălan, out after eir parents' death.
\item[\emph{2305 --- November 8}]
Dear, Also, The Tree That Was Felled of the Ode clade contacts Ioan Bălan for assistance with a project that leads to the publication of \emph{On the Perils of Memory}.
\item[\emph{2325 --- January 21}]
The launch project concludes with the launch of the Castor and Pollux Launch vehicles.
\item[\emph{2326 --- October 30}]
The Bălan clade publishes \emph{An Expanded History of Our World} In conjunction with May Then My Name Die With Me of the Ode clade's \emph{An Expanded Mythology of Our World}, collected together as \emph{On the Origins of Our World}.
\item[\emph{2346 --- May 28}]
The Artemisians make contact with the Castor launch.
\item[\emph{2350 --- January 21}]
Assassination attempt on The Only Time I Know My True Name Is When I Dream on the Lagrange System, leading to her stepping away from the politics of the System and, through two long-diverged merges, becoming Sasha.
\item[\emph{2351 --- November 8}]
Ioan Bălan publishes \emph{Individuation and Reconciliation}, containing the story of the assassination attempt on True Name and her subsequent transformation into Sasha through the merger of two long, long diverged forks.
\item[\emph{2365 --- July 18}]
Sasha releases \emph{Ode}, a companion volume to \emph{On the Origins of Our World} describing the Ode clade's movement from before the founding of the System, finally publishing RJ Brewster's name when she describes the origin of the System itself.
\end{description}
