\chapter{Ian}

``Oh for pete's sake, quit fretting,'' Andrew chided, bumping his elbow against Ian's as they crowded into the too-narrow seats. Neither of them were all that skinny anymore, and Andrew was bordering on fat, to Ian's stocky.

Ian closed his eyes and gritted his teeth, focusing on wedging himself in between the window and his boyfriend, counting up slowly through the numbers as he absentmindedly slipped the buckle around his waist.

``Sorry, Ian. I know it's probably harder for you than for me. Like\ldots{}twice as hard, or was it three times\ldots{}'' Andrew continued, a slight smile twisting the corners of his mouth.

Ian had to smile as well, caving to his partner's wiles and leaning over to place a kiss on his cheek. ``I'm just happy you're coming with, really. I can't promise I won't be freaking the whole time, but at least there will be wolves to come back to in the evenings.''

Andrew grinned, ``Damn right there will! No gallivanting off with weasels for me. Just sitting in the room, twiddling my thumbs, waitin-''

Ian kicked Andrew's foot under the airline seats before settling down against the side of the wall of the plane. ``You get plenty of fox time, don't you worry. Rei's there with his whole group of friends. I'm not going to leave you hanging or anything.''

``I know, I know. You've told me a few times. I swear you have all your bases covered, just relax and promise me you'll have a good time.''

``I'll\ldots{}I'll try. I promise I'll try.''

Ian jumped as there came a steady, barking sound beneath their feet, clutching earnestly at the arm rests as though he might actually leap to his feet, though the plane was taxiing steadily to the runway.

``Hey, hush,'' Andrew soothed. ``Don't worry, it's a normal sound. Just\ldots{}just make sure you count, and you'll be fine, promise.''

Ian nodded. He edged his hands from where they were grabbing at the seat to mock stretch, feeling the sweat coating his palms. Dragging his palms along his jeans from knees to waist, he did his best to calm down and simply let his hands rest, adopting the attitude of someone who wasn't terrified of what was to come, as if that would keep him calm.

It didn't.

Once the engines started to spin up, Ian went rigid, his whole body tensing from head to foot. He deliberately edged his hands back to the armrests, only to find his right hand intercepted by Andrews. Holding gratefully onto both his boyfriend and the plane, he closed his eyes and began counting.

``One, two, three,'' he mouthed silently, tracing the outline of each number in his mind as he counted up. ``Four, five\ldots{}'' The plane began to shake, his eyes went from merely closed to clenched shut. ``Six, seven, eight, nine,'' he continued, feeling himself sink back into his seat with the acceleration, feeling Andrew's hand getting coated with the sweat from his own. ``Ten\ldots{}eleven\ldots{}''

``Keep counting,'' Andrew urged quietly, leaning his bulk toward Ian so that the other could feel the comforting touch all the way from fingertips up to shoulder.

Ian's lips stopped moving, but he kept up the ritual in his head, tracing the numbers, drawing them with a saturated brush on imaginary paper in his mind, from eleven on up. By the time he reached seventy, the plane had gone airborne and made its first little dip after takeoff. By the time he reached one hundred, they were climbing steadily out of Portland International, and he felt more settled than he had during take-off. Just to be sure, however, he began counting once again, starting over at one. It was one of the rules: never count above one hundred.

Andrew, well accustomed to the ritual, relaxed his grip on Ian's hand when he felt him settle down next to him. He knew how much internal strife the anxiety caused, and he knew that it had a half life, decaying exponentially into the ground state, something just slightly more anxious than what he supposed he would consider his own `normal'. Being a hand to grab as needed was one of the roles he played.

\secdiv

It took seventeen counts of one-hundred to make it through the flight. The nice part about flying, Ian knew, is that by the time one was at cruising altitude, the plane seemed to morph from a trap into simply a cramped, tube-shaped room. The view out the window turned from horrifying evidence of their speed to something like a tapestry being drawn slowly beneath him. At that point, height seemed to matter less because it was outside his brain's ability to grasp.

The counting came up primarily during take-off, landing, and any turbulence -- twice there -- as well as the stolid progress of the flight attendants down the aisle-way. They were seated just aft of the wings on this flight, which afforded Ian plenty of time to watch the cart of drinks make its way row by row down the aisle, and he found himself counting -- twice again -- out of habit as he fretted about what to order to drink, knowing that he'd fail to be understood when the time came.

``Rum-and-coke,'' he answered, well rehearsed, when the attendant finally made it to him. There was no fall, no muttering or mumbling, nothing exploded, just a quiet response.

The flight attendant accepted his card as he reached past Andrew, knowing that the alcohol would likely calm him in the short term at the expense of the long term.

Andrew knew this too, and murmured to him as his plastic tumbler of ice was prepped, ``You sure, hon? I suppose we land late enough we can take it easy\ldots{}''

``Or stop and get another drink before dinner,'' Ian joked, accepting the cup, can, and tiny bottle of rum.

Andrew thought for a minute, then shrugged, ``We probably could, at that. Vacation Rules.''

Vacation Rules meant different things to Andrew than it did to Ian. For Andrew, it meant a relaxation of the stringent ways in which he kept himself, letting the excess that had led to his belly creep into other areas of his life. For Ian, it was another ritual in and of itself, a way to follow up ever action one took with ``but we're on vacation'' as a means of alleviating the inner tension that went along with his anxiety.

This particular vacation had come with all sorts of extra rules for both of them. Andrew and Ian had made it to plenty of different conventions in the past, both together and separate, but this was the first time both would be going to the same convention with Rei also there. They'd talked through the procedures involved in visiting a shared third partner plenty of times in the past, but only in the last few months had it involved a third partner involved only with one of the two.

It's not that Rei and Andrew didn't get along. They got along fine. They just never seemed to connect on the same level that Rei and Ian had, and they both had seemed happy with that.

Even as Ian counted his way through the plane's choppy descent into Colorado, he felt giddy, as well as nervous. Going through the process of getting close with Andrew, going through the outings-with-friends that slowly turned into dates, had felt natural, but this was something wholly different.

He was going to a Convention! To go on a Date! With someone he \textit{Liked}!

It was all so explicit.

He had only made it up to about thirty-eight or so by the time the plane touched down once more, and was still gripping Andrew's hand in his own. He couldn't stop now, though, so even though Andrew turned to face him, he held up a hand to signal the wait as he made his way through the rest of the numbers before finally settling back into his seat, turning to smile sheepishly at his boyfriend.

``So, um\ldots{}about that second drink?''
