\chapter{Ian}

As the night wore on, through at least two more rounds, Ian settled into a very comfortable spot between Andrew and Rei. The medication he'd taken had filled his head with the softness of cotton and soothed the jagged edges of his anxiety, leaving him feeling almost languid in combination with the alcohol. He contented himself with touching each of his partners, sometimes evenly, sometimes not, enjoying the slight thrill of the lack of symmetry.

By the time he started to feel as though he was nodding, he had his hands entwined with Andrew's and Rei's both.

``Hey, I'm fading, guys,'' Andrew murmured. He'd always been something of a lightweight when it came to drinking. ``Mind if I call it? You two can totally keep up or do whatever.''

Rei nodded, ``Sure, I've had about my fill of these stools, anyway. Do you\ldots{}um, do you mind if I steal Ast for a little while?''

Ian felt the blush begin to return as his partners talked about him so plainly.

Andrew laughed, ``Sure, go ahead, as long as that's okay with you, hon. You guys should spend some time together.''

The blush deepened, but Ian nodded and said, ``Yeah, I'd like that. I'll be back tonight, okay?''

Nodding and leaning in to give him a light kiss, Andrew smiled, ``You, sir, need to have a good evening, don't fret any. You know where I'll be and how to get in touch. Have fun, you two.''

Andrew sauntered off and left Ian with Rei, the both of them sitting in silence for a moment longer.

Finally, Rei offered shyly, ``Would you like to head up to the room? Not, like, for anything, just some place quieter? Roommates should be out still.''

Ian squeezed Rei's hand in both of his own. ``Yeah, let's do that. I'm a little buzzy, and it's a little loud down here.''

Rei nodded and moved to settle the tab, covering all three's drinks over Ian's protests, before standing. The two smiled at each other and, before his sleep-, medication-, and alcohol-addled mind had the chance to talk him out of it, Ian stood quickly and leaned to give Rei a soft kiss, more of a smooch than anything.

Rei looked a little startled, but smiled all the wider, slipping his arm around Ian's back and gently guiding him out of the bar, the two talking softly about how good it was to finally have the chance to meet.

``So,'' Rei said as the door to the room shut behind them. ``How'd you and Andrew meet, anyway? I mean, I know how we met\ldots{}''

Ian laughed and settled onto the bed that Rei led him too, leaning back onto his hands. ``We actually met outside of furry, at school. Our campus had a GLBT Student Services office, and we both met there, though I think it only took us a couple of days to figure out that we were both into the furry thing. He's been in it a lot longer than I have.''

Rei slipped his messenger bag off of his shoulder and set it down atop a hard-shell suitcase as Ian talked, chatting about how he and Andrew had started dating by default, but found themselves more than compatible.

Rei slipped up onto the bed behind Ian, carefully settling himself on the bed with his legs to either side of his partner's waist. He leaned back onto one of his own hands before carefully drawing Ian toward his front, letting him rest half in his lap, half against his slender front.

Ian fretted for a moment about letting his weight rest against Rei before remembering Andrew's admonition. He had fallen silent when his partner had drawn him close like that, and eventually he managed to relax, murmuring affectionately, ``Weasels are slinky.''

Rei chuckled and placed a kiss atop Ian's head, replying, ``It's in the job description. We can't help it.''

Sighing quietly at the kiss, Ian settled both of his hands on Rei's arm around his front and made himself cozy. Everything felt warm, comfortable. There wasn't the same safe feeling he felt with Andrew, but he figured that would come in time.  For now, he was content to rest against his lover, asking quietly, ``How do you feel about tonight? I hope it wasn't too, you know\ldots{}awkward.''

Rei appeared to think for a moment, then shrugged. ``It was good. I mean, I've talked with Andrew some, too, it's not like we don't have anything to talk about or anything.''

``But it wasn't weird with me being affectionate with both of you?'' Ian fidgeted, ``Wasn't weird when I kissed him?''

Rei shook his head. ``No. I'm happy to have the time with you now, but I still really enjoyed the evening.'' He paused for a moment, then asked, ``Did the evening make you anxious?''

Ian shook his head drowsily, hiking himself up a little further onto the bed so that he could rest more comfortably against Rei, ``Not really, no, just wanted to make sure. I took meds before meeting you in the bar.''

Squeezing him a little tighter against his front, Rei nodded silently.

Ian lay for a little bit longer, but eventually sat up, turned to face his partner, and leaned in to kiss him once more, more thoroughly this time. Rei carefully brought both arms up around Ian's shoulders and guided him down to the bed as he lay flat on his back.

Ian shifted up along Rei's front, careful to match movements and stay close. He made sure to set his elbows down to either side of Rei, resting most of his weight on them. The kiss lingered a little longer before parting with the two looking quietly at each other.

``I'm not crushing you, am I?'' Ian asked quietly.

``Hush, fox,'' Rei laughed, taking a cue from Andrew. ``Don't fret.''
