\chapter{Sascha}

Sascha woke slowly, curled at the edge of the bed, to the gentle sound of Peter's snoring -- quiet enough to be more endearing than annoying. They had fallen asleep in a tangle of limbs, once they'd gotten cleaned up and into pajamas, but, as had always been the case in Sascha's experience, had separated during the night and slept in late on opposite sides of the bed.

The evening of drinking, talking, intimacy, climax, and more quiet talking drifted back into focus, and Sascha curled up a little tighter, smiling against their pillow at the memory. That things had wound up heading in the direction of sex wasn't all that surprising, given how the two generally acted online. Sex had loomed large in their relationship, and although the idea of getting too much further into it still made Sascha nervous, they found themself relaxing in a warm afterglow the next morning. The simple act of being so close to someone during such an intense moment filled them with happiness. Even if they themself hadn't reached climax, it still felt as though they had gotten a chance to share something special.

``Mmmf, morning.''

Sascha was startled out of their reverie by Peter's quiet mumbling, smiling, ``Hey, morning.''

Peter tugged the covers up under his chin seemingly still asleep, but after a minute or two of silence, he asked, ``Time is it?''

Sascha yawned and peeked back over their shoulder at the alarm clock, ``Nine-ish, bit after.''

Peter nodded and rolled onto his back, muttering, ``Sleep. Gooood.''

With a quiet laugh, Sascha shifted closer to him under the covers until they were nestled in against his side, head resting on his shoulder and arm slipped over his front, finding the most comfortable way to fit against him. Peter slipped his own arm around their shoulders and rumbled quietly in contentment, though he still hadn't managed to open his eyes.

The two stayed like that for half an hour more, Sascha nearly dozing off before Peter finally stretched out and yawned. He tilted his head down to kiss lightly at Sascha's forehead, leaving behind a gentle tingle from the soft, not unpleasant bristle of his stubble.

Sascha leaned up to return the kiss, but after a moment Peter turned his head to the side, then carefully slipped out from under their arm to stand up out of bed.

``Mm? Is everything alright?'' Sascha asked.

``Just wasn't expecting\ldots{}I mean, would it be okay if you shaved?''

Sascha brought their hand up to feel their own unshaven face -- barely a hint of coarseness, but enough to feel -- and felt their body tense. They nodded and sat up in bed, crossing their arms over their knees and settling their chin down behind them, doing their best to hide any shadow that might be showing, ``I'm sorry.''

``It's okay,'' Peter mumbled, slipping into a T-shirt. ``I just wasn't expecting it, I guess.''

Sascha nodded again and slid quietly out of bed, grabbing a change of clothes -- jeans today -- and their toiletries bag and headed for the shower, hoping they'd remembered their razor.

\secdiv

The embarrassment didn't last long. A good shower fixes a lot of things, and Sascha always felt better after shaving, often to the point of doing it twice a day to ensure they had as little shadow and stubble as possible. It was one of those things that wouldn't go away without an investment, and they'd had enough trouble scraping up for this splurge of attending the con.

Sascha thought back to the previous day's conversation with Maverick about not wanting to appear dishonest to Peter about gender. They winced, but got themself cleaned up well and even added a touch of makeup, just a bit of concealer and eyeshadow to feminize their features somewhat. Something conciliatory to make things go a little more smoothly. Soon, that warm afterglow they had felt before was back, along with a smile.

Getting dressed, they belted on their tail and opted for fuzzy paws instead of shoes. Now that the con would be in full swing, it wouldn't hurt to furry things up a little. After all, just paws and a tail would put them at the low end of the dress-up spectrum.

Sascha packed up their kit and slunk out of the bathroom to find Peter gathering his own things up for a quick shower. They leaned down and kissed him lightly on the cheek, ``This better, Shadow?''

He smiled up to them bashfully and nodded, ``Sorry about before. I know it wasn't very nice of me. I just was caught off guard.''

``No, it's alright. I don't like it either. Go ahead and get ready, and we can get some food. There's a coffee shop down the street that does good breakfast burritos.''

While Peter showered, Sascha caught up on how their friends' nights had been. Volare had gotten drunk, of course. Vish had gotten upset, of course. Maverick had apparently spent much of the evening trawling the lobby and Friday night dance in hopes of running into anyone else he knew with little luck. His job kept him busy enough that he wasn't totally in touch with the furry scene, so it wasn't a big surprise. A few more of Sascha's friends and acquaintances had shown up, and they made a note to say hi at some point during the day.

They spent a few minutes poking at Twitter, drafting message after message

\begin{quote}
  Fantastic night last night :)
\end{quote}

Delete delete.

\begin{quote}
  Really good evening, so good to meet up with @ShdwWolf.
\end{quote}

Delete delete delete.

\begin{quote}
  Good evening last night. Caught up with friends, had a fantastic time with @ShdwWolf. Glad I could make it.
\end{quote}

They pondered for a second before hitting send. It would be enough to state that the night had been positive without necessarily tipping their hand as to how positive it had been for them.

Peter eventually made his way out of the bathroom, clean-shaven and damp, and smiled to Sascha. They finished getting dressed -- standard furry wear of con shirts, jeans, paws, and tails -- and made their way to the elevators.

Sascha leaned against Peter's arm in the elevator, taking his hand in their own. He smiled down to them and gave a little wagging motion of his backside. It made Sascha laugh.

Once in the lobby, they ran into Maverick looking bored, and roped him into going to grab breakfast and coffee with them. The three chatted amiably as they made their way to the coffee shop and through the line to order, each getting a breakfast burrito or other treat and a coffee drink to finally wake up.

Peter excused himself to go wash his hands, and Maverick pounced. He took Sascha's hands in his own and grinned widely at his friend. ``So! A fantastic time, huh?''

Sascha did their best to not look embarrassed, ``Yeah, it was a good evening all around.''

``Come on, you're glowing!''

``What? Am not!''

``Trust me. Take it from the glowy cheetah.  You're glowing.''

Sascha couldn't do much other than bow their head to keep their blush from being seen.

``It's good, minky,'' Maverick continued, voice softening. ``I won't pry, I'm just happy for you.''

Sascha smiled shyly and drew one of their hands back, enough to take a sip of their coffee and hide their face for a moment. ``It was a good and comfortable night. We didn't\ldots{}you know, do much, but it was just good.''

``Well, hey, `good' is what cons are for. Oh, hey Shadow, promise I'm not mackin' on your mink.''

Peter pulled his chair up to the table and grinned, adopting an air of incredulity, ``Macking? Really?''

``Yeah, come on, Maverick. We left the nineties behind a while back,'' Sascha laughed.

Later that day, by the time they'd made it back to the hotel and met up with Volare, an icy Vish, and a few others from the IRC channel they all hung out on, the glow that had obviously suffused Sascha had calmed down to a sense of peace and happiness. They were pleased to tag along after Peter and the crew as they made their way slowly through the dealer's den, ogling books and art, carefully noting commission prices (and snagging one or two that were within their range), and just generally being a giggly group of friends.
