\chapter{Michael}

By the time Michael made it to the dance, he was decidedly buzzy, full of rum and coke, beer, and mediocre pizza from the hotel kitchens.  It was fuel enough for fucking around in the dance, he figured.  Not like anyone was likely to notice his un-fursuited form stomping away on the ballroom floor to deep house or yacht punk or whatever the hell kids were spinning these days.

The dance was a just good way to let loose.  For him and so many others.

He prowled down the long hallway from the hotel restaurant to the ballroom, weaving skillfully between clumsy fursuiters and those moving much slower than he.

He felt good.  Real good.  This had been a good day overall, from watching his friends have their fun in the morning, all the way down to dinner.  Even, he admitted to himself, seeing Glade again, in all his newfound confidence.

The dance was packed, even for as early as it was.  Saturday was one of the two big nights, with a line-up of two-hour DJ sets that lasted nearly until dawn, and programming had stopped hours ago.  So it was to be expected that there would be a ton of people there, Michael thought, showing his badge to the guard at the door and bouncing in time with the thumping music even as he made his way into the ballroom, quickly picking up the time as he moved.

The music washed over him, thick as honey, as he moved out onto the floor.  It pushed at him, tugged at him, guided his movements between the furries out on the floor, both in and out of suit.  He knew he wasn't a graceful dancer, or even a good one, but he couldn't deny how good it felt to move along with the beat.

It was some uncounted number of songs later before he noticed the form moving closer to him, hips swaying in the rhythm of the music through the crowd.  He was sweating, and he could feel dinner's two drinks coursing through his veins, that was about the only indicator he had that it was later on in the evening.

Glade.

He slowed his movements, settled down into a relatively quiet sway where he stood on the dance floor, watching as Glade moved up to him through the crowds.  The presumed hormone therapy had changed the shape of his previous mistress, shifting the bulk of his weight up toward his middle and away from his hips, and what had been a generous bosom had been drastically reduced -- how, he couldn't say.  The walk had changed too, though not in any way he could pinpoint.  More movement to the shoulders, perhaps.

What he saw, stalking toward him rhythmically through the crowd of dancing furries, was a well-built, clean young man, dressed in jeans, a skin-tight shirt, and a leather jacket, who somehow still retained so many recognizable features of his old partner.

Glade reached out and took his hand, drawing him dancingly from the floor and away from the speakers to the back of the room.  Michael followed helplessly, half in awe and half in shock at his former mistress' directness.

They both moved subconsciously to the beat, shifting their hips and their weight in time with the music, then nearly pausing as the beat built up to the drop.

Glade brought him to an unoccupied section of the wall at the back of the ballroom and turned him firmly so that his back was to the wall, then pressed him up to it.  He seemed deliberate in his actions, making sure that Michael's back was flat against the wall before planting his hands surely beneath each of his arms, leaning in close to him.  He had to stretch up a little in order to make himself heard as he spoke quietly.

``Lets have some closure here, roo.''
