\hypertarget{sorina-bux103lan-ioan-bux103lan}{%
\subsection{Sorina Bălan — Ioan Bălan}\label{sorina-bux103lan-ioan-bux103lan}}

Ioan,

While I'm sure that Codrin\#Castor's already told you plenty about me, I wanted to send you a letter directly.

Something about winding up here in a place so fundamentally different from where we've lived before has me in mind of the past. I wasn't quite sure why this was, at first. Obviously, I miss the prairie and life aboard Castor, and that's all in the past, but one would think that I'd be more worried about what's in front of me than what's behind me. The prospect of months or years aboard this new world — never mind the core facets of existing in this world — give me plenty of time to worry about the future, though.

I suppose leaving behind so much is reason enough to think about the past.

I could spend all of that time thinking about my partners (and I've certainly been thinking about them plenty), but you've been coming up in my thoughts more than I'd expected. Something about this extra layer of individuation has you feeling even less like a down-tree instance than you did before, and far more like a good friend — especially given how much I miss you.

I miss you! Isn't that weird to say? Perhaps. We've never met, have we? Ruminating on my roots has me thinking fondly on the past, though. We are stuck however many billions of kilometers apart, though, and that distance will only grow, the time between messages will only ever get longer. At least I think I better understand what Dear was talking about with regards to the difference between longing and being missed.

Ah well, perhaps I'm just lonely. Lonely and moody. It's so strange here, and it's been playing havoc with my emotions.

I miss you and May Then My Name, and I hope you're both doing well. Pass on my love.

Sorina Bălan\\
33 et-ularaeël, 4775 Artemis Reckoning
