\hypertarget{codrin-bux103lancastor-ioan-bux103lan-codrin-bux103lanpollux}{%
\subsection{Codrin Bălan\#Castor — Ioan Bălan, Codrin Bălan\#Pollux}\label{codrin-bux103lancastor-ioan-bux103lan-codrin-bux103lanpollux}}

Ioan, Codrin,

I'm glad that you enjoyed my description of Dear's recent performance, Ioan. Codrin, I hope your Dear manages to take some good stuff from that (I know mine sent over a whole sheaf of notes). Watching foxes of various sizes try to waltz with second- and thirdracers was funny enough, but the sole firstracer in attendance (Anin Li, who I've mentioned before as one of the two Artemisian psychologists, I've been working with) trying to figure out how to waltz even with a fox the same size as it was more amusing than it should have been.

I had to make sure that there was at least some pleasantness to this letter, because I'm afraid that the rest of it is going to be a bit dreary.

You'll notice that Sorina isn't in the recipients list. I've mentioned to you both previously that the process of seeing her off to Artemis was more painful than expected, that I've been struggling with the feelings that I have both about that act of individuation and the possibility of forgetting that Artemis grants its occupants. Now, though, you can add, ``radio silence from her'' to the list of things I'm having a hard time with.

It's not even that big of an issue. Her last letter to me was a short, polite request that she be given a little space while she works out her feelings on Dear and █████. I can very much respect that, of course, as well as the idea that
