\hypertarget{aurel-bux103lan-the-bux103lan-clade}{%
\subsection{Aurel Bălan — The Bălan clade}\label{aurel-bux103lan-the-bux103lan-clade}}

The Bălan clade,

For as often as we talk about being trackers, I sometimes wonder if we aren't maybe more aligned with the Odists than we give ourselves credit for. Not the structure, perhaps, but to hear May and Dear talk, this idea that each of the first lines would fork to explore an interest isn't that unfamiliar to us, is it? We fork to work on projects and usually merge back, and yet when we are taken up by fixation, individuation sets in and we are suddenly no longer who we were.

And yet that's not all the Odists do, and, apparently, it's not all we do, either. They have their secret, long-lived selves, those who drift away from who they used to be, and they fork often enough to work on a task. Their instances will linger to track a task from start to finish and then they'll merge back down, just as we did.

All this by way of greeting. Ioan and I have flipped a coin as to who would be the one to send this email, for even though ey's listed as the sole author, that I am borne from the work that went into \emph{Individuation and Reconciliation} — and indeed was em for much of its writing — gave me some claim over writing this.

Attached is the full transcript. This is one that I'd like to be very careful with given its contents. The ways in which it will affect the entirety of the Ode, Jonas, and Bălan clades are too complicated to wholly understand, so the more input we can have on it, the better.

Through a winding series of events following the ordeal between Sasha and Jonas, then between Sasha and the rest of the Ode clade, we've found use for yet another one of us. I chose the name `Aurel' mostly on a whim, as well as in response to some gentle ribbing about gender from a few people now. I guess dressing like a A name with diminutives that can head masculine with `Aurică' or feminine with `Aurica' seemed like a simple way to explore that a bit more. As I've stated in the past, I like being a Ioan and have never enjoyed `Ioana' (two many bad memories from school, perhaps?), but we're nothing if not deliberate, right?

I will likely only be around off and on, forked as needed to track an intermittent identity, so if at all possible, avoid individual eyes-only material for me. I don't know if quitting and merging back down, then forking again will let me access eyes-only stuff should it arrive after the fact. I'll be testing that over the next time I merge back down, and I'll let you know the results. There's some info on the perisystem feeds, but not as much as I would like, so, better safe than sorry.

Separate letters for each of you to follow.

\textbf{SORINA BĂLAN INDIVIDUAL-EYES-ONLY MATERIAL}

Sorina, you are welcome to offer what input you might have or completely disregard the manuscript. I know that your relationship with the Odists is complicated, and the last thing I want to do is make you feel bad without recourse. I've only been Aurel for a few weeks now, so I have memories of our all of our correspondences to date.

To that end, I've set a portion of this letter as eyes-only for Codrin largely due to the context of our relationships with the Odists — em with Dear, Ioan with May, and now me with Sasha. I don't want to come off as hiding anything from you, but I do want to ask before I send a bunch of stuff that might cause distress given all that's been going on of late.

On that note, how are you doing? We've been quite worried about you. I know that trying to balance the emotional pain of being so far away from your exes and Codrin doesn't play well with the ownership of your life that goes with individuation and being the only Bălan on Artemis.

Know that Ioan (and thus I as well) love you for all of your individuality and strength. Stay safe, stay in touch, okay?

\textbf{END}

\textbf{CODRIN BĂLAN INDIVIDUAL-EYES-ONLY MATERIAL}

I'm separating this content out for you two to keep from overwhelming Sorina with a bunch of information about Odists and relationships. Also, I gave her the option of disregarding the manuscript, lest that prove to be too much.

Things have been a bit shaky throughout the clade, haven't they? I'm unsure of how much you two speak with each other, so I won't go into specifics except to say that I'm worried about you both. You and those in your lives are still incredibly important to me, even after all these years apart. Please do all that you need to keep yourselves safe and healthy.

Please feel free to take your time with it, but we really would like to hear your thoughts on both the project and the events. Releasing something here is essentially equivalent to releasing it on all three Systems, so we can't simply release it here and see what happens before sending it over to the LVs. Do you have any expectations as to the reception given the general mood of the various societies? I will note that this has already been given to Jonas here, which means it has doubtless been sent out to Castor and Pollux for them to prepare for its arrival. The events were not quite what Jonas here on Lagrange was expecting, so I doubt that his expectations on the LVs were all that different.

I will note that this is in spite of the apparent differences between the societies themselves. I know I wasn't able to properly articulate it in my letters at the time, as writing letters and writing a book are quite different activities, but it'll soon become clear that the Jonas lives within these three different societies has diverged little, that all three of them share the same goals they began with perhaps even centuries back and the launches become yet one more tool.

And what of the Odists?

I know that we're fond of blaming them for how complicated things get sometimes. They seem to heap plenty of blame on themselves, for that matter. E.W. (\emph{né} End Waking) spoke to this several times, describing the Odists' clade identity as a sort of idolatry, and not in positive terms.

I'm starting to wonder just how universal that is, though. How much is their complication a factor in others' lives? I suspect for more people than not, they're simply weird. Dear's weird. May's weird. Were he to speak with anyone else with any regularity, I'm sure that many would find E.W. weird too.

But complicated? How much of that is just observation bias? Do they seem complicated because their relationships with us are complicated? Dear's relationship with you two is full of complications that we initially chalked up to the fact that Dear's weird. May's relationship with Ioan is full of complications that we initially chalked up to True Name making her what she is and shoving her Ioan's way.

And now here I am, having wound up in yet another relationship with yet another Odist. Or perhaps more than one. It is unclear to me (or any of us, really) just how to count Sasha in terms of quantities. She is that of True Name, that of E.W., and that of May, and yet there's this fourth part of four that is something new, something else.

\textbf{END}

May and Sasha send their love, as do Ioan and I. We miss you and yours, and hope that you're doing as well as can be.

Aurel Bălan
