\hypertarget{aurel-bux103lan-the-bux103lan-clade}{%
\subsection{Aurel Bălan — The Bălan clade}\label{aurel-bux103lan-the-bux103lan-clade}}

All,

You'll have to forgive a rather lengthy, rambling letter. Aurel was just forked\footnote{Five minutes ago. \emph{Just} forked.} the four of us are sitting out in Douglas's field along with him, E.W., Debarre, and a few other friends after a small potluck of sorts. There wasn't any real reason for the get-together other than it's snowy at our sim, the skunks were whining, and it's always nice here. What started as a plan for Ioan, May, Sasha, and Douglas having a picnic blossomed on a whim to something of a party.

(Some descriptions of the party; maybe SH telling two truths and a lie about others, Debarre promises fireworks, Vos and AFP set up a bar, Marsh sings a song)

When we all got to talking about memories, Ioan suggested that we start compiling them into a letter just to share them with you. It's a good day, and we should be able to share our everyday weal as well as our occasional woe.

(Clade is fading in preparation)

(Sasha back to striped skunk)

(Aurel in and out of existence)

(Sasha's work included)

(Rareș update)

With all the love in the world,

\begin{itemize}
\tightlist
\item
  Aurel Bălan
\item
  Ioan Bălan
\item
  May Then My Name
\item
  E.W.
\item
  Sasha
\item
  Douglas Hadje
\item
  Debarre
\item
  A Finger Pointing
\item
  Slow Hours
\item
  Yared Zerezghi
\item
  Vos Barzee
\item
  Marsh Hart
\end{itemize}
