\hypertarget{codrin-bux103lanemissary-2346}{%
\chapter{Codrin Bălan\#Emissary — 2346}}
\markboth{Codrin Bălan\#Emissary — 2346}{}

\noindent ``Given the differences between our systems, the focus on time skew versus forking, I'd like to see what some of the political and sociological differences there are that result from that,'' Codrin said, starting a new page of notes.

Both Iska and True Name sat up straighter.

``This is broad-large-all-encompassing topic, recorder Codrin Bălan.'' Turun Ko angled its head down and to the side, a move that appeared either confused or perhaps condescending. ``Please restrict-refine.''

``Well, okay.'' Ey tapped the end of eir pen against eir lower lip, considering. ``Perhaps we can begin with how common working with skew is among everyday individuals. We have our concept of dissolution strategies, based on how one approaches forking, after all.''

There was a blurred conference between the Artemisians, then Iska said, ``There is a spectrum of approaches to skew. Some rarely utilize it, some utilize only fast-time to complete tasks or slow-time to pass long stretches of time out of boredom or to wait for a specific event. Some, such as myself, utilize skew for fun.''

``These map loosely to your concept of taskers, trackers, and dispersionistas,'' Artante added. ``We noticed similar during the third convergence, though the concept remained only within fourthrace, and died out within a century of the convergence. I was reminded of the topic by one of your early letters.''

``I remember you a mention that fourthrace had forking,'' True Name said, voice tightly controlled. ``Was the transition from that to skew difficult for those members of fourthrace that joined?''

``For some, yes. There was one recorded instant of a member of fourthrace becoming so despondent about the lack of forking that they exited the system.''

True Name and Answers Will Not Help looked at each other, letting the silence that followed speak for itself.

Codrin let the moment pass before continuing. ``Thank you. For what occupations there are—I believe you also described them as `intensive leisure activities'—is there any particular expectation regarding one's approach to skew?''

``Expectation?'' Turun Ko asked.

``I suppose activities have their own requirements for how one utilizes skew. For instance, representative Iska doubtless relies on it quite heavily. Does knowing one's interest tell you about their skew habits? Is there pressure for one to not take up an activity due to the skew habits one has already formed?''

Iska was practically purring at this turn in the conversation. ``Had one of us asked that question, I would have said `no', but hearing it from you has made me think about it in a new way. I would have said that one simply would not think to take up that activity, but now that you say such, I think that this is the case. I am uncomfortable with not utilizing skew, yes, but for activities that are pinned to common time such as cooking and storytelling, there is an expectation that I would not be a good cook or storyteller, yes. Were I to pick up an interest in cooking, I would be looked on with a small amount of concern. One would say about me: `I hope that they do not burn the food by shifting to slow-time' or `I expect that their food will be very rushed'.''

Codrin grinned as ey took down notes of the answer. ``One of my romantic partners, as an instance artist, has stated that it can't understand what a life without profligate forking would look like, but has never said that it feels as though it is not able to take part in another profession. That said, there are several interests or professions that one would not expect taskers or even trackers to go into. Many would sneer at a tasker trying to go into instance artistry. Does the same apply here? Are there more interests or profession that are out of reach for those who do not use skew than for those who use skew often?''

Another, longer blurred conference followed this question, during which True Name gave em a tired smile. ``Excellent questions, Mx.~Bălan.''

``We have decided that there has not been much thought put into this topic, but that our instinct would be to say yes, the interests which belong to those heavy users of skew are more specific and thus more likely to carry some level of prestige that might be out of reach for those who remain in common time.''

Sarah sat forward, leaning on her elbows on the table. ``Can you expand on `prestige', here? Are there interests that are considered less prestigious? Do some interests reflect poorly on the individual?''

``Please confirm: do you mean social-stratification-caste?'' Turun Ko said, and both Codrin and True Name rushed to write a note.

``I'd also like to know about that, yeah, so let's come back to that later. In this instance, I was wondering there are interests that are seen as distasteful or silly.''

``We have decided that there are not any that are seen as distasteful,'' Turun Ka said after another conferral with its delegates. ``But there are many that are seen as frivolous. Some view contemplative or spiritual life as frivolous, particularly among secondrace, which is very old.''

Codrin frowned, making a note to ask about that later. They had the concept of spirituality, and even the concept of a life lived in in contemplation. It raised several other questions besides, such as why it was that the second oldest race bore the brunt of that assumption, and why it had been implied that firstrace was immune. Were religions shared between the races? Were religions time-bound? In eir hundred and twenty-eight years of life, the world had yet to end, despite countless predictions.

Ey shook the rumination from eir eyes in time to hear True Name asking, ``What is the view of the Council of Eight?''

Turun Ka rocked its head from side to side. Amusement, Codrin\#Artemis had written. ``We are seen as almost vestigial except during convergences. What guidance we provide we do so through through advisory not--''

It was interrupted by a bang as Answers Will Not Help, who had been nearly in a stupor up until this point, slammed her fists down on the table. ``I must keep no veil between me and my words. I must set no stones between me and my actions.''

There was a tense moment of silence.

``Apologies,'' she said, rubbing her hands over her face and then yelping as a wave of skunk washed beneath them. ``I cannot stop myself from speaking.''

Artante nodded slowly. ``Would you like to take a break, representative Why Ask Questions?''

``I\ldots yes.''

``We shall reconvene in five minutes common time,'' Turun Ka said. ``We wish you the best, representative Why Ask Questions.''

Sarah helped her to her feet and walked her down the hall to her room.

True Name slouched down in her seat with a wave of Michelle rolling across her form.

``Are you alright?'' ey asked, patting her hand.

She jolted to the side with a quiet grunt, pulling her hand back as though burned. She rolled her head to the side against the back of the chair looking steadily at em. ``I will be okay, Mx.~Bălan. Thank you for your concern. Please refrain from touching me when my form is shifting, though. It is quite uncomfortable.''

``Apologies.'' Ey bowed her head. Something about the skunk's voice brooked no further questioning.

``You asked some very good questions today. I am quite happy that you decided to come along.''

``It's an honor.''

She rolled her head back once more to stare up at the ceiling. ``Have you heard further from your counterpart back on the LV?''

``Ey mentioned that the common tongue is remarkably well-preserved for being on the system for four thousand years, and suggested that there might be political implications behind that.''

``Right, yes,'' True Name said, closing her eyes. ``Should Why Ask Questions start feeling better, perhaps we can have that discussion more in depth, but I will ask either way. Anything else?''

Codrin\#Artemis had clearly picked up on eir hint, and had hinted in return. There would be much to think about, and ey had a return letter planned, as well as a discussion with the other three delegates. It had been a good guess on \#Artemis's part that Tycho had been the one to spot the subterfuge.

``No,'' ey said. ``They wish us well.''
