\hypertarget{codrin-bux103lanemissary-2346}{%
\chapter{Codrin Bălan\#Emissary — 2346}\label{codrin-bux103lanemissary-2346}}

(AWNH breaks down (revealing she's AWNH, not WAQ), quits, break immediately called, TN is having a REALLY HARD TIME, Turun Ka shows up, TN comes clean, talks about getting lost, Turun Ka says Artante's race ran into similar, but stops her from talking about AWNH further for now)

``Prophets!''

Silence around the table. Answers Will Not Help pushed herself to her feet. Waves of skunk and human crashed violently across her form. She was laughing. She was crying. Her back arched taught and she laughed up toward the ceiling, a choked, gasping sound.

True Name, struggling to hold her own form together, reached out to tug at Answers Will Not Help's sleeve. ``Please, my dear,'' she murmured. ``Why Ask Questions, please sit down. I know it is--''

``I am not her! I am not her. I am Why Ask Questions When The Answers Will Not Help. Don't\ldots I\ldots{}''

True Name froze. Everyone froze.

``You told us you were--'' Sarah began, before Answers Will Not Help cut her off.

``Oh, where is Ezekiel when we need him? A meeting of prophets! Navi to nevi'im! The voice of God from the sky in a pillar of flame! Or Qoheleth, a prophet of our own blood, bearing warning of memory entrancing!'' Her words came out in an unceasing torrent. ``But instead we are Israel to nevi'im, a people to prophets, a people to prophets, and the only time I know my true name is when I dream, and to know one's true name is to know God. Time feels so vast that were it not for an Eternity— Fuck, I\ldots time makes prey of remembering, I\ldots I fear me this Circumference engross my Finity— Oh AwDae, oh AwDae. Could you ever have guessed at the depths of the death of memory?''

True Name stood quickly and, with a decisive wash of skunk down her form, growled, ``How fucking dare--''

``To his exclusion who prepare by process of Size\ldots of\ldots{}'' She was phasing in and out of local time now, her words jittering now fast, now slow. ``I miss em, I miss em. I miss\ldots was that eir prophecy? Was that why ey wrote me? Is this AwDae's words come true?''

``Stop!'' True Name shouted, tackling the blurring, crumbling form of Answers Will Not Help to the ground. ``Fucking stop! You cannot--''

After a moment's tussle, Answers Will Not Help collapsed to the ground, limp and laughing. ``For the Stupendous Vision of eir diameters—'' she said, and then quit, leaving True Name to fall to the ground, weeping.

There was a shocked silence around the table, and when no one moved, Codrin slid out of eir chair to kneel by True Name's side. Her form had begun to waver once more, and, remembering the aversion to touch that came with that, ey simply sat beside her, waiting until she calmed down.

It was Sarah who broke the silence. ``What just happened?''

``True Name and, uh\ldots Why Ask Questions — that is, Michelle Hadje — was one of the lost, and I guess time skew is similar enough to—''

``No,'' the Odist said between heaving breaths. ``She was right. That was Answers Will Not Help.''

Tycho frowned, nodded. ``We had guessed.''

``Leader True Name,'' Turun Ko said. ``Please explain `lost' in this context.''

She did not move from her spot on the floor. "
