\hypertarget{codrin-bux103lanemissary-2346}{%
\chapter{Codrin Bălan\#Emissary — 2346}\label{codrin-bux103lanemissary-2346}}

As suggested, Codrin and Sarah wound up in the courtyard.

There seemed to be no immediate recovery from the events of the past hour. There was no conversation to be had, no words that could be spoken to express so singular an event. There had been a\ldots was it a death? And then a cryptic pronouncement. And ey had watched True Name\ldots was it sharing in confidence, a request for companionship, or something else?

Ey felt dazed, unmoored from reality. Ey could feel more clearly the way that time clung to em in a way it couldn't back home, back on Castor. It was no stronger now than it had been at the beginning of the day, but, as might happen when one remembers that one is breathing, ey was suddenly and intensely aware of it.

``Codrin?''

Sarah's voice jolted em back to the present, and ey smiled sheepishly to her. ``Sorry. I was elsewhere. What's up?''

She laughed and waved her hand. ``It's alright. That was a whole lot all at once. I was asking how True Name was when you left her. Is she alright?''

``Yeah. She was sleeping. I don't know how much they-- well, how much she has been sleeping of late, but given that she seems constantly exhausted, I'm glad she's getting at least a little.''

``This does seem to be taking its toll on her. When this is all over, I'd like to sit down with you and her and learn a bit more about this.'' She hesitated, then added, ``Or at least with you, depending on how willing she is.''

Ey nodded. Ey could feel the knowledge of what ey'd learned clawing at eir insides. The Name, the pronouns, feeling the owner of the Name in the system. It wanted out, at least in some way, but there was no one other than True Name ey'd be able to share that with from now until eternity.

Swallowing down the feeling clutching at eir throat, ey said instead, ``You know, she said something to me when she was laying down to nap. She said something like,''I need someone to anchor me and you are very good at that``. Come to think of it, I got a note from Codrin\#Artemis that Tycho said similar earlier, that he said I'm `grounding'.''

Sarah nodded readily. ``You are, yeah. Why do you bring it up?''

``It's not something I'd really considered about myself, honestly.'' Ey spoke slowly, piecing together eir thoughts as ey went. ``I've been questioning my path in life so far. I've been very passive, very much like a recorder. I'm good at being a recorder, but I also feel like I get dragged into it more often than I choose to do so.''

``Does being a grounding person help with that?''

Ey shrugged. ``I suppose so. Empathy helps, because it lets me understand what's happening more readily. The way Tycho and True Name put it, though, sounds more active.''

She nodded again, waiting in silence until ey was done speaking.

``Ioan's moved on to theatre, Codrin\#Pollux is a librarian now, and I'm just doing the same thing I was doing almost a hundred years ago. This whole thing about being grounding combined with the need for something new just has me thinking about what to do with my life.''

``It's a complex question, Codrin. Hell, even when we were limited to ninety or a hundred years, folks would talk about having midlife crises, questioning what it was that they really wanted to do, and a lot of times it came down to feeling a lack of agency. Psychologists would\ldots{}'' She trailed off, looking over eir shoulder. ``Well, lets pick this up later. Artante and Turun Ko are on their way.''

Ey turned to look over eir shoulder, noticing the two Artemisians moving slower than expected. A moment's thought showed that ey was still running at a skew of one point two as the meeting had been, so ey dropped back down to common time.

Turun Ko dipped its head as Artante bowed, saying, ``Recorder Codrin Bălan, representative Sarah Genet. Do you know where the scientists are?''

``No,'' Codrin said, returning the bow. ``I suspect they snuck off together somewhere to talk astronomy.''

The fourthracer laughed. ``Yes, I suppose they must have.''

``We are pleased-excited to witness mutual enjoyment,'' Turun Ko said, voice bouncing between registers in amusement. There was a ping against eir sense of time, a sensation of insistent pressing. ``Please? We will speak at synchronized skew.''

Ey frowned, relaxing against the sensation and feeling eir control over time diminish. After a moment of looking uncomfortable, Sarah nodded as well.

There was a brief lurch as time skewed quickly up to two point five, moving far more quickly and with more surety than eir experiments up to that point.

``Thank you, recorder Codrin Bălan, representative Sarah Genet.'' The firstracer shifted back, settling onto its haunches and tail and clasping its hands together over its front, which appeared to be the default resting state for its race. ``We wish to speak-discuss with you the events-proceedings from earlier.''

``To begin with,'' Artante said, picking up the conversation. ``Do you have any questions that we can answer? This may inform the discussion.''

When Sarah did not speak, ey asked, ``I don't imagine there's much you'll be able to answer so soon in the talks, but leader Turun Ka mentioned that deception had been wargamed. Is this the type of thing that's expected at a convergence?''

``Yes, recorder Codrin Bălan. The possibility-probability that a new race-culture-species practices-engages-in deception is one item on a checklist of one beginning and two endings.''

``Beginning? Endings?'' Ey shook eir head. ``Well, stepping back, what do you mean by checklist?''

``Convergences are processes. Processes may be smooth-easy or rough-difficult. It is our goal-aim to ensure smoothness-ease, as I think-suspect must be that of leader True Name.''

This was the most that Turun Ko had said at once over the last three days and, despite its statuesque nature, ey was keen on drawing more out of one so aligned with eir own goals. ``So you have a list of items and possibilities that might happen during a convergence, then, and we're making our way down the list?''

``\emph{Anem.}''

``And the beginning was first contact?''

``\emph{Anem.}''

Ey frowned. Ey wanted nothing more than to write this down, to do as ey always had done and incorporate this into a story, but something about this meeting seemed to preclude that possibility. Something about it was meant only for this space.

``I see,'' ey said. ``And that you have two endings implies that there is a goal, \emph{anem?}''

``\emph{Anem.}'' Turun Ko lifted its snout. ``You will join-converge with us as fifthrace or you will not.''

There was silence within that bubble of fast-time, and ey imagined that it was em and Sarah struggling to process this information while the two Artemisians waited patiently for the next step in the conversation — or perhaps the next item on the checklist.

The pressure to ask the correct question weighing down eir shoulders, Codrin nonetheless stood up straighter. ``Is there a correct ending?''

A smile tugged at the corner of Artante's mouth, leading to a sense of relief within em. Ey suspected that em asking that very question might have been an item on their list.

``\emph{Unot.} The endings share equality-correctness.''

``Will the decision be mutual?'' Sarah asked.

``\emph{Ka,} representative Sarah Genet. The decision-ending must be mutual-shared before the Ansible-transmission-mechanisms will be unlocked-ungated-opened on both Castor and Artemis, \emph{Ka?}''

``I suppose so,'' Codrin said. ``If one side, as a whole, did not want to join, they wouldn't turn on their Ansible for general use.''

Artante nodded. ``And the other, seeing that, might feel enough unease that the decision would become mutual, even if it had not started that way.''

``Are we on the path towards becoming fifthrace, then?'' ey asked.

After a pause, Turun Ko said, ``The list does not work-function in this way, recorder Codrin Bălan. The decision-inflection-point is preceded by a cloud-tree-collection-net-pile-table-graph of interconnected actions-items-steps.''

It took em a few frowning seconds to plow through the litany of synonyms to reach the heart of the statement. ``To be clear, there are a bunch of steps leading up to this decision point?''

``\emph{Anem.}''

``Can you tell us what they are?''

``\emph{Nu.} We cannot.''

``There's some different shades of meaning to that word, recorder Turun Ko,'' Sarah said thoughtfully. ``\,`Cannot' can mean that you aren't able to, or that you are unwilling to. Can you expand on that? Are you able to, I mean?''

``We cannot,'' it repeated, and Codrin once more caught that ghost of a smile on Artante's face.

``Either could be true, but that's not the correct conversation to have right now,'' ey hazarded.

At this Artante laughed. ``You learn quickly, recorder Codrin Bălan.''

Ey smiled, shrugged. ``It's my job to pay attention, I guess. You can just call me Codrin, by the way.''

``And you can just call me Sarah.''

``\emph{Aet.} Thank you Codrin. We will continue to use full names during the talks, but you may call me Artante outside of them.''

``I will remain-always-be Turun Ko.''

There was another moment's silence as Codrin and Sarah processed and the Artemisians waited.

There was so much to take in here, but on further examination, it all made quite a bit of sense. The Artemisians had prepared for this event as thoroughly as had the Odists and Jonases. Of course there would be things that would happen — or at least could be reasonably expected to happen — throughout the convergence. The Artemisians had a head start in that they had history to lean on: they'd been through at least three convergences prior to this one.

``I don't imagine there was anything like what happened with Answers Will Not Help in your steps,'' ey said, finally.

``\emph{Nu.} There are analogous-similar topics. Psychosis and time-sickness have been seen-observed in the past. This is why quitting-exiting-death are prevented-illegal in the conference and rest areas. That representative Answers Will Not Help quit-exited-died is upsetting-distressing-concerning. Representative Iska has undertaken the task of exploring-examining the event.''

``Right. I'm sure True Name and Turun Ka are discussing this, too.''

Artante shook her head. ``They are having a different discussion. It is not the time for them to have the conversation of steps and checklists.''

Sarah frowned. ``Should we tell her about this discussion?''

After a hesitation, the fourtracer replied, ``There are steps on the checklist for if you do and if you do not.''

\emph{Sounds like a no, then,} Codrin thought, working to maintain a neutral expression. For all their talk about staying away from manipulation and subtlety, there sure seemed to be plenty going around among the Artemisians. It was as Tycho said: they seemed to be working on some higher level, less comprehensible to em as a mere mortal. Ey supposed five thousand years of flying around through space would change how one engages with the world no matter what.

``And how about you two?'' ey said.

Turun Ko tilted its head far to the side. ``\emph{Lubaenåtam?}''

``Do you two have steps of your own?''

``You ask an interesting question,'' Artante said, sounding thoughtful. ``I want what's best, and with each passing conversation between delegations, the meaning of `what's best' shifts. I'm sorry that I can't put it more clearly than that, though I can assure you that I consider us to be together in this; what's best for the Artemisians will also be what's best for you.''

``And you, Turun Ko?''

It straightened up, joints and synthetic flesh shifting smoothly in a well-articulated dance, as though it was running through some internal checklist to straighten and correct its posture. ``I want-desire stories. There is no combination of steps-items on our list that will not result-in-lead-to stories, so I will not be disappointed. I have received-learned many already, so I am content-happy-satisfied-fulfilled and will remain-continue-to-be so even if you become-turn-into the most exceptionally-stupendously boring-droll numbskulls-sad-sacks-dipshits in the visible-observable universe.''

Codrin and Sarah both stared at the firstracer before laughing, joined by Artante. Even the fourthracer seemed taken aback by the sudden injection of humor.

``I guess we have proven interesting, if nothing else,'' Sarah said.

``\emph{Anem,}'' Turun Ko confirmed, and the single word came out nearly a song.
