\chapter{Early August}

Sleeping in a new place was always disorienting to Jeff.  The fact that it was his same old bed, same old covers, didn't to anything to cover that up.  The smell of him lingered on the comforter, which he hadn't had time to wash beforehand, but the smells of the room itself were new.  All new.

It would take weeks or months of living there, maybe even longer, before the scents of him and his two children had permeated the place enough to call it their own.  Until then, it would be late nights surrounded by the tough odor of latex paint and spackle, of carpet cleaning and of not-his-own memories.  Until then it would be lying awake at night, learning the new smells, the new creaks and groans of the new house, finding all of the new patterns in the texture of the ceiling before he could actually manage to let sleep overcome him.

It was Kayla who had adapted fastest out of the three of them.  Not only had the seven year-old bustled into the house with more happiness than tiredness (for Jeff) or apathy (for Justin, his older son), but she had immediately found all of the interesting places to hide and sequestered herself in her room, laying on her undressed bed with her colored pencils and a sheet of paper.  Jeff had had an additional few days to scope the place out before moving there, but that had been a month and a half ago, and more than once, he found himself calling for his daughter, confounded by unexpected corners.

Justin had had the hardest time, and Jeff suspected that that was an issue of maturity.

As an adult, he'd been through his fair share of moves, and had the benefit of being the one who had gotten the new job out here on the east coast.  Justin had been pulled from his junior year of school, where he had established friendships and toiled through countless classes; as a kid (and, Jeff reminded himself, he \textit{was} still a kid), Justin had the benefit of none of this.  He may still be adaptive in time, as Kayla had been, but for now, he was stuck finishing out his tenure in high school in a strange and new place, surrounded by new people and with suddenly altered college prospects: what was in-state before was seemingly out of reach within the span of a few short months.

For now, though, Jeff vowed to help his eldest to adapt as best as he could, and maybe rope Kayla into that as well.  He would only have a portion of the time with his children that he used to, having gone from being an unemployed single father to the new and improved Dad-With-A-Job.

He had meant to take that time off, as he'd told himself and his kids countless times.  A few years of helping to get Kayla into preschool and then into grade school after that, months of helping Justin with his homework.  The pay-out from Karen's life insurance had more than covered the fifty grand they had still owed on the house, giving him the leeway to take the occasional consulting gig, but otherwise to spend the time with his kids.

The money hadn't run out, necessarily -- not yet, at least -- but his patience for being a stay-at-home father had.  He loved his kids, dearly so, but the long days alone with only the occasional bit of shopping or consulting to break up the time had been so counter to how he felt he operated best, that when the opportunity for permanent employment with a pretty decent firm had come up, he'd leapt at it.  The pay was good, but, he made sure to remind himself, it wasn't about that.  It was getting the kids a good chance at life, and getting himself up and moving again.

Being an adult, Jeff suspected, was all about setting up hoops that you would then have to jump through.  He envied Kayla, whose duties were simplified to finding the best hiding place in the house and drawing, always drawing.

Jeff wasn't sure when it was that he'd fallen asleep, other than the last time he'd managed to check the time, it was nearing three in the morning, and that the light under Justin's door still hadn't gone out.  He'd long since given up policing bed times for his eldest.  There were measures -- getting up on time, doing well in school -- that Justin always seemed to meet or exceed, anyway.

\secdiv

Jeff blearily slapped at the alarm that finally got him out of bed, having already silenced his phone and stuffed it under his pillows.

It was only Saturday, but given that he had cut it down to the wire with his new job starting on Monday, he wanted to get at least a few things unpacked before then.  He pried himself out of bed and nearly made his way down the hall to the kitchen so that he could make himself coffee, before remembering that he hadn't unpacked any of the kitchen gear yet.

\textit{That was dumb.}

He sat back down on the edge of is bed and stared at the low barrier of boxes that lined one of the room's otherwise unoccupied walls.  The month or two before the move, he and his kids had gone through a culling of the unnecessary, moving unwanted stuff to a mixture of Goodwill, ARC, the humane society (their dog Benji's passing had spurred Jeff on to eventually find and apply for jobs outside of the state), and even the food bank, seeing no reason to move their non-perishables with them on the road trip.

Some part of him had obviously thought ahead, as the box with his robe and pajamas had been on the top row.  He had already dug through to get out his PJs, and his robe was laying sprawled on the rest of the boxes.  He shrugged it on tiredly and, careful to be quiet, made his way down the hall to the kitchen.

Kayla had yet to reach that point in her life where she slept in much later than eight or nine in the morning, so she woke and surprised him as he was digging through boxes in the kitchen, searching for the coffee machine.  The noise of him putting away dishes and silverware as he rifled through the cardboard tower had obviously woken her.

``Morning, daddy,'' she said, looking bleary-eyed with mussed-up hair.

``Hey, little blossom,'' Jeff said, edging cheerfulness into his voice to cover up the lingering thought that he might've tossed the coffee beans with the move, leaving himself with nothing.  ``You sleep alright in your new room?''

Kayla started, then nodded sheepishly before returning to the apparently important task of looking around the kitchen.  ``It's pretty here,'' she offered, distracted.

``I know, Kay-bear.  It seemed like a good place for us.  All finished so we don't have to do any work.''  He shoved another stack of plastic cups up into one of the cupboards.  He knew he should be paying more attention to where things were winding up, since there wouldn't likely be any motivation to move them again, but he suspected that the next box contained the coffee machine, and hopefully a bit of coffee.  ``Good schools, too.  I think you're gonna like it here.''

``Mmm,'' Kayla rolled her eyes.  Must've learned that one from her brother.

``Finally!'' Jeff said, lifting the coffee pot out of the box.  It was wrapped around with plastic wrap, crumpled up newspaper stuffed into the gaps to keep the pot from moving around.  And, lo, a small tupperware container of pre-ground coffee settled in alongside it.  ``Past me, I love you.''

Kayla giggled and tilted her head, brushing hair out of her eyes, ``What?  You're weird, daddy.''

Jeff turned and grinned lopsidedly at his daughter.  ``Weird and tired.  I'm going to make some coffee real quick, Kay-bear.  Do you know if your brother is awake yet?''

Kayla shook her head.  ``I peeked last night, he was listening to music on headphones.  I don't think he'll be up for a long time.''
