\chapter{Late August}

``Did you practice?''

Justin stared down at his dinner, a one-pot chicken and noodle dish that Jeff had perfected in the years of raising his children, spooning up small bits of chicken and ignoring most everything else.  Not their favorite, but it at least passed muster after a day of work, for Jeff, and school shopping in the evening for the kids.

``Justin, I'm not upset,'' Jeff sighed, composing himself so as to reflect that.  ``I'm just curious why you didn't get into band.''

Justin shrugged in response, his shoulders sinking lower than they had already.

``I mean, come on, man.  You don't think it's a little weird that you spend all those years focusing on this thing, and then suddenly it's just gone?''

``I tried practicing,'' Justin mumbled.

``And?''

The boy languidly picked at his dinner, found another bite of chicken, and ate that, not responding.

Jeff sighed.  ``Hey, I'm sorry, Justin.  I know the move hasn't been great for you, but you just seemed to have so much fun with band.''  He poked around in his dish, chewed a mouthful of food thoughtfully, and tried a different tack.  ``You said you tried practicing.  Just not feeling it, bud?''

Justin shook his head, bangs shifting over his brow to hide his face.  Another wan bite of chicken and more silence.

The table sat in near silence for a bit, the only sound that of Kayla poking around her empty bowl with her fork, drawing something in the cream-of-mushroom-soup gravy that was left in the dish.  A flower.  Jeff took the opportunity to clear his own plate, keeping an eye on his son, who managed at least half of his food, Jeff's measure of `at least enough'.

When Jeff finished his last bite, Kayla leapt from her seat and picked up her bowl, fork clattering against the rim.  ``All done, all done!'' she cried, trooping off to the sink to deposit her bowl there.

Jeff settled onto his elbows, leaning over the table toward Justin and lowering his head so that he could see under the boy's bangs.  ``Everything alright, kiddo?''

Justin hesitated a moment before shaking his head, ``None of it really matters, in the end, dad.''  Slowly scooting his chair back and standing up, he shuffled over to the kitchen.  He scraped the last of his food back into the pot -- it would become leftovers for lunch the next day -- and set his bowl into Kayla's.  Making his way slowly out of the kitchen, he shuffled down the hall and closed his bedroom door quietly after himself.

All that was left was the soft noise of the radio playing in the living room, where Kayla was drawing.

Jeff sat back in his chair and frowned at the bowl ahead of him.  He'd call the school tomorrow, without letting his son know, and see what was up, if his new teachers had noticed anything about how he was feeling during the day.

\secdiv

Jeff never did manage to call the school, the next morning.  He'd hit snooze on his alarm and wound up cutting breakfast time a little short.  Hustling the kids and drinking some too-hot coffee a little too fast, he'd gotten the children to their schools and made it into the office by eight, but only just.

``Perez!  Sneaking in just under the line, huh?''

Jeff whirled in the lobby of the small architectural firm, the reason he'd moved across the country in the first place.

``Mr. Pike!''  Jeff tugged his jacket straight and corrected his posture, holding out his hand to the company's owner just coming through the front door.

Mr. Pike smiled and shook Jeff's hand, then clapped his left on Jeff's shoulder.  ``Chill, Jeff, you're fine.  No need to rush.  We've got half an hour before all-hands, and as long as you're not consistently late, no one really cares.''

There was the soft sound of the doors opening behind them, and two others -- higher up in seniority than Jeff, judging by their suits -- sauntered past them and offered a greeting, ``Mr. Pike, Jeff.''

``See?  Even the boss can afford to dally in the lobby.''

Jeff smiled faintly, but nodded.  The boss's reassurances aside, he still felt compelled to make a good impression early on, especially if he planned on making a name for himself in the business down the line.

He trooped into the office after his boss, slipping out of his jacket to let it dangle from his hand.

There was still time to grab some coffee before the meeting, so, after dropping his jacket off at his desk, he made his way to the kitchen.  Whoever had gotten there before him had finished off the pot of french press, so he set about making another.  There was something comforting about the rush of warm water over his hands as he cleaned out the pot and the filter, and the simple act of scooping beans into the grinder.

It was the noise of the grinder that started to wake him up a little more, along with the smell of freshly-ground coffee wafting up to him.  He knocked the grounds into the bottom of the press and filled it with nearly-boiling water from the kettle.

The five minutes it took to brew the coffee gave Jeff plenty of time to consider the conversation the previous night.  It was too late for him to call the school, but something was clearly up with Justin.  He had been so deeply involved with music back out west, for him to have dropped that interest completely in the short time since they'd moved east, something must've happened.

The move had been precipitated, oddly enough, by the death of their elderly dog, Benji.

An early windfall from a severance package, combined with the money that had come from his wife's death -- a settlement from the other driver and a life insurance policy -- had been enough for Jeff to take a bit of time off of work and pull his life together.  It had only been intended to be a year, when he had volunteered for the company's next layoff, but the money had been enough to cancel their mortgage and leave him owning the house free and clear.  The burden of raising two kids on his own was more than enough work for him, as it was.

By the time that Kayla had made it into school, he had grown used to the routine of fatherhood.

The dog had been an early gift to the family after Karen's death.  Something that they could all take part in, something to take care of after the family was abbreviated so suddenly, an adoption away from death that they could all take part in.  Benji was a terrier mutt that had never grown to be as large as his namesake.  All the same, both Kayla and Justin had grown to love the dog, and Jeff himself had spent many hours caring for the dog: walking and feeding him, brushing out the mats in his fur, and playing with him out back when he got tired of finding contract jobs to keep himself busy.

Benji's death had been anything but sudden, and in a way, Jeff realized, that had hurt Justin and Kayla more than their mother's passing.  They had gotten to watch Benji's body slowly deteriorate as the cancer ate at him.  They got to find new lumps and see his energy decline.  They had gotten to see him totter out of bed to say goodbye to them that last morning, knowing that he wouldn't be there that evening.

Jeff had called the vet and arranged a house call.  He had cried as he stroked the dog's head, the vet sitting silently beside them as Benji fell into sleep and then into something deeper than sleep.

The kids had been crushed.  Kayla, had cried throughout the night with little that Jeff could do to comfort her, though over the next few days, she had steadily improved.  Eventually she would only mention missing Benji once a week, then once a month.

Justin had taken it harder.  The death of his dog had come at that time in his life when mortality strikes one as real, and one understands that those who die are truly inaccessible.  He had started spending much more time in his room, and much less time practicing his clarinet.  He would often be nearly silent for evenings in a row, eating quietly and retreating to his room where he would write, draw, and do homework with his headphonse socketed into his ears.

That was what had made Jeff start looking for a permanent job, and looking for something away from their home state of New Mexico.

The search had been easy.  There were several phone and a few on-sight interviews that Jeff had flown out for, leaving Kayla in the care of her taciturn older brother, and then arranging the move-

Jeff's thoughts were interrupted by the timer going off, signifying that the coffee was ready.  He shook his head and fished a mug out of the cabinet above the office sink, and poured himself a cup of coffee.  He just had enough time to check email before the all-hands meeting started.
