\chapter{Halloween}

\begin{itshape}
  Just as before, they called him on his cell phone at work.  This was the county coroner's office, and could he please come down sometime today before 5:30 to help identify a body.  Yes, now would be fine.  The sooner the better.  Thanks.

  Just as before, his heart seemed to seize within his chest.  He had taken the time to only dash off a quick email to his boss.  There was an emergency.  Yes, he'd make up the time later.

  Just as before, he left his coat slung over the back of his chair and his computer logged in and unlocked.  He jogged to the elevator, punching in the address that he had been given on his phone, but by the time he had made his way from the sixth to the first floor, the anxiety had welled within him such that he sprinted from the building to his truck.

  Just as before, he was met with calm professionalism at the door and quietly, efficiently ushered from the entrance to the room where he would view the deceased.  No, they could not tell him more.  He would have to wait, then speak with the coroner directly.

  Just as before, Karen, unmistakable as ever, lay on a clinically cold table, eyes shut, though her nose and jaw were badly disfigured from the car accident, lacerations covering her torso down to her midriff, an ankle oddly angled.

  Just as before, he knew her immediately.

  Just as before, he ran to her, the shout of anguish already welling up within his chest.

  And then he hit a wall.  There was no rebound, no noise, nothing to see.  He was simply stopped five or so feet from his wife as she lay on the table.  He could not go closer, he strained ineffectually, his muscles seeming to go slack as they encountered the transparent barrier before him, not allowing him to go to his wife.

  And the coroner's assistant or whomever had guided him there kept asking, ``Sir?  Is this your wife?  Sir?  Sir?  I need to know if this is your wife.  Sir.  Are you alright?''
\end{itshape}

Jeff didn't awake with a gasp, though he did start enough that he felt disoriented as his eyes struggled to make out the darkness of the room surrounding him.  And yet, as the disorientation passed, he felt himself completely awake, as though he had simply never been asleep.

He rolled onto his other side and peered at the glow of the numbers on the clock, willing them to swim into focus.

\textit{Three AM.  Shit.}

It was that awkward period of the night where he knew that, unless he got to sleep immediately, there would be no making up for the lost rest and he would feel terrible all day.  And there was no way he could sleep soon.

The pain of losing Karen had slowly left him over the months and years that followed her death, and love for his children had taken over once the estate had been settled and life insurance worked out.  Even so, it was possible to bring back that ache with a simple memory, or a dream.
