\chapter{Early November}

``Oh!  Kayla!  Those are beautiful!''

Kayla looked up, dully at first, from the crocus she had been drawing, one among many, in a sea of graphite.  Recognizing the voice as Mrs. Willis, she had brightened and smiled, setting her pencil down and shuffling the papers nervously.

``You think so, Mrs. W?''

Mrs. Willis beamed down to Kayla.  ``They're beautiful, dear.  Where did you learn to draw like that?''

Kayla shrugged, her feet swinging, crossed at the ankles, beneath her chair.  ``I just draw a lot.  Daddy draws, and so I started drawing, and now it's just what I love to do.''

``They're beautiful,'' Mrs. Willis reaffirmed, then paused.  ``The class is scheduled to move to clay tomorrow.  Do you want to work with clay?  I can let you do clay flowers, if that's what you like, instead of the slab pottery.''

Kayla, thought about that.  The thoughts were crowded with flowers.  Perfect curves along petals, the gentle arc of a stem softened by trichomes.  Colors that seemed to blur within her head.

``I-'' she began, then stopped once more.

Perhaps sensing the remainder of the thought, Mrs. Willis took stock of the rest of the class, drawing inverted images as a study of negative space, though she hadn't introduced that term yet.  Other than a young boy and girl trying desparately not to look like they were talking across the room, everyone was behaving well.

``Come, Kayla.  Come with me.  I want to have a word with you in the hall,'' she murmured quietly.

Kayla flushed, gave one last look to her flowers, and nodded, carefully scooting her chair back from the edge of the desk.  She followed after her teacher, mindful lifting her feet too high.  It was best to move among flowers in a flowing fashion, with grace so as not to crush any.

Once outside, Mrs. Willis closed the door most of the way after one last look, then appraised her student.  ``Do you know what an `independent study' is, Ms. Perez-Gray?''

Kayla stared at her feet (surrounded by dandelions -- delicate flowers of all yellow on a sturdy stalk) until the words `independent study' caught her attention.  ``Mmn?  No.''

``It means that a student gets to direct their own study into a field that they love.''  Mrs. Willis peered down through her glasses at the young girl, ``You have an interest -- a thing that you love -- and you have the will to make something beautiful.  Would you like to do an independent study?''

Kayla poked her toe against the linoleum (against the green leaves at the base of a dandelion) and thought for a moment, ``What does that mean?''

Mrs. Willis face softened into kindness.  ``It means that I would give you resources to learn how to draw and paint flowers.  Some books, some examples.  Georgia O'Keefe\ldots{}no, not yet.  Anyway, dear, I'll give you some examples and books on drawing flowers, and you and I will come up with some goals for you to reach, and you can work towards that, rather than following the curriculum of the rest of the class.  Does that make sense to you, Ms. Perez-Gray?''

The flowers were so fragrant.  They smelled like muffins.  The color drained from them down into the linoleum, then flowed back into them from the ceiling.  Yellow and green -- gray -- yellow and green.

Kayla nodded.

``Good.''  Mrs. Willis smiled brightly.  ``I'll write your father a note during class today.  You can bring it to him and it will explain what we plan on doing.  I'll leave a spot for a signature at the bottom so that you can have him sign it.  Bring it back to me, okay Kayla?  So that I know he's alright with our little plan.''

Kayla felt neither relief nor upset, nor anything really.  She was overwhelmed by the heady scent of a field of dandelions, coarsely toothed leaves brushing against her ankles and reminding her that this was good, that this was right.

``I will, Mrs. W.''  She smiled at the tickling of the leaves against her, a brush of smoke, the sensation seeming to pass through her socks and sneakers.  ``I will.  Thank you, Mrs. W.  I want to draw more.''

\secdiv

Dinner that night was the most jovial affair that Jeff had witnessed at the house in days.

Kayla had come home and dropped her bag at the door, rather than the usual spot inside her room, and kicked her shoes off quickly.  She rummaged through her bag hastily and yanked out a sheet of paper that had once been folded in thirds but was now a good deal more crumpled.

``Daddy, daddy! I have a thing for you.''

Jeff, hanging his jacket up over the back of one of the dining room chairs, turned in surprise.  There had been no rumors of field trips leading up to today, and other than knowing that it was Art Day for Kayla, he could remember nothing that would've been so exciting for her.

``What'd you get, Kay-bear?''

``Mrs. W. gave me a thing and I need you to sign it.''

Jeff felt a thrill of fear rise within him like a wave of warmth.  Surely not in trouble, not this early.  The letter proved him wrong, though, as he read through Mrs. Willis' loopy scrawl, perfect cursive characters befitting an art teacher at an elementary school.

\begin{quotation}
  Mr. Jeff Perez,

  I am your daughter's art teacher, as doubtless she has told you by now.  I have been watching Kayla carefully over the past few months and have come to a few conclusions.

  First, although she does not always seem to endeavor to complete the assignment at hand, preferring drawing to any other medium, she does seem focused on improving the significant skill that she does have.  I have been consistently impressed with her work, the latest of which shows an innate talent that I have not seen in a girl of her age before.

  Secondly, as this is a magnet school for the arts, and as the school's art teacher, I do have some authority to encourage children to pursue areas of their talent, so long as they remain within the bounds of the class.  The class will be moving on to slab pottery and basic sculpture next week, but I have offered Kayla the chance to continue with her studies in the realm of drawing, specifically of drawing flowers.

  This is all with your permission, of course.  Please feel free to return this to me with your signature and I will provide Kayla with books that she can use to further her work.  If not, Ms. Perez-Grey will continue on with the rest of the class.  If you have any questions, please do not hesitate to call me.

  Sincerely,

  Janice Willis
\end{quotation}

``Kayla!  Kay-bear!'' Jeff exclaimed, scooping his daughter into a hug.  ``This is wonderful, Kayla.  I know your drawing has gotten more and more beautiful, and I'm glad to see your teachers appreciating it.''

Justin scuffed his feet on the stoop before prying his own shoes off.  ``What's up, dad?''

``Here!'' Jeff handed the paper over to his son and dashed off to the kitchen, hoping against hope that he had the ingredients for burritos, his daughter's favorite.

``Kay-beaaaarrrr!'' Justin roared from the other room, and Jeff smiled, pulling canned beans and a bag of rice he hoped had enough for a batch from the cupboard.  He could hear the sounds of scuffing and giggling, and could imagine his son picking up his little sister, twirling her around.

Dinner was simple, if non-traditional.  They had beans, and they had rice, but they didn't have any tortillas.  Jeff had looked into what it would take to make tortillas, but had decided against it, in the end.  Instead, he made beans and rice as usual, and served them alongside some grilled chicken breasts sprinkled with chili powder, with a dish of salsa and the container of store-bought guacamole that he had found in the back of the fridge, only a little brown with oxidation.

Contrary to the rule of nothing at the table but conversation, Jeff had invited Kayla to show some of her drawings that she felt were the best, father and son admiring the flowers, vines, and plants that she had set down on paper, talking about art long after the plates had been cleaned of food, even Justin's.

They were only interrupted by a loud \textit{*krak-thwop!*} from the living room.

``The hell-'' Jeff muttered.

\textit{*krak-thwop!*}  \textit{*thunk thunkthwop kra-krak!*}

Jeff jumped up from his chair, Kayla and Justin rising more apprehensively from theirs, just as a book came skidding across the floor in a loud rustle and crashed into the wall visible even from the dining room.

``Whoa, holy shit!'' Justin shouted.

``Justin!'' Jeff admonished, then gave a yell as two more books arced across the room to slam into the wall.

Jeff edged forward toward the entrance to the living room, gesturing to his two children to stay back, though Justin crept forward to follow his father after a moment's hesitation.

The noise grew rapidly from the scattered rustle and thunk to a small roar as book after book hurtled itself noisily to the floor, or across the room into the far wall.  By the time that Jeff and Justin had made it to the entryway, the torrent had nearly ceased, book after book fluttering down to the floor.  Justin's mysteries and science fiction, Jeff's old college textbooks, kids books that Kayla hadn't been able to part with.

The flow of books from shelves to floor petered out just as father and son worked up courage enough to peer around the corner.

The shelves were completely empty.

\secdiv

``This house scares me, daddy,'' Kayla admitted to her father as he tucked her in.  No bedtime story tonight, no books, just talking.  Neither of them had wanted a story.

``I know, Kay-bear, that was weird, wasn't it?''  Jeff was tired, but consoling his daughter was his first job

``We're not going to have to move, are we?''  Kayla turned to face her father under the covers, ``It's so pretty here.''

``I don't know,'' Jeff admitted stroking fingers through Kayla's bangs, brushing the blond hairs away from her face.  ``I don't know.  I'm going to call around, but I don't think so, Kayla.  Sometimes weird things happen.''
