\chapter{Wednesday, December 23 -- Midnight}

%%% cut to Kayla, worried for her father and brother, mind filled with flowers
Kayla's mind was blossoming.

She felt sick to her stomach, having mostly pushed her food around the plate, taking a few bites that she knew she needed.  Hunger would eventually win out and she would down a whole meal and then some in a day or two, but for now, the macaroni and cheese, when it wasn't obscured by lilies, looked like a mound of undifferentiated plastic, and the broccoli was too close to blossoming itself to seem appetizing to her.

She took up the time alternating between drawing and pacing back and forth in the living room.  She would spend enough time on a drawing to feel it either finished or abandoned, tendrils of morning glories creeping across a page, or slender, crowded stems of snapdragons.  When a page was set aside, she would walk from the kitchen to the living room, turn on the television, watch for a few minutes until the vines had thoroughly covered the screen, turn the TV off again, and walk back to the kitchen where she would draw again until the flowers had been beaten back through acknowledgement.

Kicking her feet at the table, head bowed over the was distracted by a light flickering to life at the periphery of her vision.  Kayla realized she had lost track of time -- it felt late, and she felt more than a little sleepy.  Looking up from her paper, he peered around the warm glow of the kitchen, eyes lingering tiredly on the digital clock above the stove.  Just a bit after midnight, she realized.

She tore her gaze away from the clock and continued to peer around her for the source of the flickering before her eyes landed on the large picture frame on the wall of the living room opposite the television.  The picture was obscured by the reflections in the glass that covered it.  Flickering orange, too much contrast.

And no flowers.

It was the last part that got her to lever herself out of her seat.  She slipped carefully from her chair and walked delicately through coarse rows of decorative flowers, until she had made her way back to the living room, looking up at the picture.  The orange glow was gone, and there were creepers exploring the edge of the picture frame.  Instead, the glass reflected her face, sad flowers of eyes, and a gentle, flickering orange glow lighting up her left cheek.

Turning to look out the picture windows across the street, her eyes going wide.  Fire!

Her father had been adamant about raising her to fear fire and he had done a good job of thoroughly instilling that fear.  She had had no desire to play with the few flames she had the chance to see throughout her life.

She ran to the window, heedless of the plants beneath her feet -- though, as usual, there was no sensation of walking through them -- to gape at the fire outside.

It was obvious that there wasn't a fire in the house across the street itself.  The flames flickered and rose in a smooth, unbroken ring around the property, crossing the driveway about two thirds of the way down.  And in front of it stood a man.

Her father.

She saw him take a step back, get a running start toward the fire, and then, as his courage failed him, skid to a stop inches shy of the flames and fall back onto his rear, hurriedly scuttling back from the fire.

``Daddy!''

She ran for the front door, stepping through rows of flowers, vines reaching in toward her and crowding out her vision.  The door was a solid mass of ivy.

Kayla scrabbled frantically at the door, struggling through the mass of green-turned-black in the darkness of the living room.  As always she felt only the faintest brush of leaves, but it still took her what felt like achingly long seconds to find the handle and deadbolt.  She hurriedly unlocked the door and yanked it open.

She gasped.  The whole street was lit by the yellow-orange glow of light. from the flames, and yet, for once, wherever that light shone, there were no flowers, no plants except the cold, greenish-brown of the grass in her yard and the stubbly scrub of the house across the street.

The change was drastic enough to stop her in her tracks.  The flowers had been with her for months, something that she had never talked about and had only just started getting used to, and now, for the first time, she could see the ground beneath her feet, could look at the houses on the street and finally understand that clinging vines were not a feature of every building around her, blurring corners.

The flicker of the flames once more caught her eye as her father gathered up his courage once more and this time leapt succesfully through the flames
