Mom and I piled into the car at about seven that morning, squeezing ourselves in amongst a laundry basket full of a bubble of my clothes, my computers, and bedding enough for one who lives in Colorado and knows what the winters can be like.  Check in wasn't until four that afternoon, but there was still quite the drive ahead of us in order to get there on time and to give us some time in town for lunch and walking.

``Exciting, isn't it?'' my mom said.

``Yeah, stoked,'' I replied with as much sarcasm as I could muster that early in the morning.  ``Why can't you empty-nest like all the other parents?''

She laughed.  ``Why would I?  I get the dogs all to myself now, I can go hiking whenever I want, and hey, I can make as much spinach as I want.  Maybe I'll even rent out your room''

``Hey, I like spinach too!  And you know I'm going to go crazy without my pups there to keep me company.''

She nodded and focused on getting us down the mountain of her driveway and onto asphalt.  Steamboat is tucked nicely in a valley, and the floor of that valley is decently flat, but unless you live in the middle of the town, you're in the hills.  Much as I loved the Rocky Mountains, I had no desire to go to college in my hometown, sacrificing proximity to home for a school that wasn't filled with slackers who picked the school based on its proximity to the very popular ski slope.  I really was excited to be going to college, where I could get an education that was pertinent to me.

The next hour or so was spent in silence rather than our usual banter due to the early hour.  I nursed my coffee for most of that time and watched as we pulled north from the town, slipping past habitation and into the densely packed wilderness, walls of building giving way to the walls of the pine forest.  We wound our way up and north - up into the passes and north of the town, driving for Wyoming.  Even though I was going to school almost directly east, it was faster for us to duck up to Wyoming for I-80 and head for I-25 to duck south back into Colorado to head for Fort Collins than to try driving east.

With the sun heading to the top of the sky, I drained my now chilly coffee in a few quick gulps and reached back  behind my seat to tuck the travel mug into my backpack.  The mug had been one of my parting gifts from my friends who still had a year left of high school, and my mom had supplemented that with a small coffee maker.  I had told her I didn't like drip coffee, but she assured me that I would most certainly get more use out of that coffee maker than any of my textbooks.  Hard to disagree there.

``I can't believe you picked somewhere so flat!'' she exclaimed, breaking the silence of our drive to that point.

``Me either.  I feel as though I'm twice as tall there and I might just tip over, like it's harder to balance or something.''

``At least there are plenty trees.''

``Yeah, to hide the lack of mountains.''

``And you can bike easier.''

``Mmhm.''  I could sense where this was headed.  My mom would always talk about the town before broaching the next subject.

``And why did you pick such a stuck up little cow-town?  I mean, it's not Greeley, but you could've gone to Boulder!  Fort Collins is so... so...''

``Conservative?  I know, but that's just the town.  I'll be living in the dorms.''

``Do you think they'll be that different?'' she asked, sounding genuinely worried by now.

``I hope so,'' I murmurred distractedly.  We'd had most of this conversation before.  ``You know what they say: if you're not a liberal in college, you have no heart.''

``Well, you know the rest of that saying says that if you're not a conservative by forty that you have no brain, and plenty of your classmates' parents will have chosen their school for them; indoctrinated them.''

``Like you did me?''  I grinned back to her sidelong glare.

``Be serious, you know what I mean...''

I nodded and sat for a bit before replying, ``At least I'm not going to Wyoming.''

``I don't think I'd let you.''  Her expression turned pained, ``Don't want you to be the next Matthew Shepherd.  Poor kid...''

``I know, mom.  You saw the office, though, they clearly have enough gay people there for them to have an office, and to have some influence ofver how things are run.''

She nodded and shrugged as best as one can while holding at ten and two, a cautious driver.  ``But that's a group thing.  You know, sociology and what not.  That's not going to stop some crazy individual who's convinced deep down that God hates fags and it's their sworn duty to usher them straight to hell.''

``Well, yeah.  I promise I'll be safe,'' I said dismissively.  This conversation was getting worn out from how often we had had it.  ``And hey, maybe I'll even meet someone local to date.''

Smirking, she replied, ``You can date whoever you want, Cory, I'm not going to stop you.  I am going to suggest that those internet relationships you've had aren't exactly healthy, is all.  Much as I liked Chris...''

Nice disclaimer, I thought.  And she really had liked Chris.  It was tough on both of us when that relationship had ended as poorly as it did.  ``I know, I know.  I'll go shopping and bring home a nice boy sometime, one of those funny ones.''

``Hey,'' she said mock defensively, laughing.  ``I'm not the one that needs a boyfriend, it's you.  Date who you want, seriously.  Jared and I will support you, whoever you wind up with.''

``Yeah,'' I said distractedly.  I got the feeling that Jared wasn't exactly a big fan of having a gay step son.  Mom had the final say, though, and promised me that even if that was the case, I came first for her, and didn't have anything to worry about on that end.

Another bit of silence greeted us as the trees around the road began to thin and the omnipresent greenery shifted from the greenish blue of the pine trees to the brownish green of scrub.  Wyoming was close.  I hoped that meant food was close, as well.  We had planned on stopping somewhere along I-80 in order to pick something up.


``Did you ever get in touch with your roommate?'' mom asked.

``Yeah, he emailed me back.  Sounds like kind of a jerk,'' I said, brow furrowing.  ``He's in some sort of fraternity, I think.  Hopefully that means I won't see him much.  Don't know how I feel about living with someone who spells `cool' with a `k'.''

``Great,'' she muttered in response.  ``Now I'm really worried.''

``Don't be, mom.  You know I can take care of myself.''

``So you always say, I just don't want you calling me to say you couldn't prove that.''

I blinked and frowned, mildly offended at that.  I stared out the window for a little bit before looking over at my mom who had the steering wheel in a while-knuckled grip.  She looked genuinely worried, ``I'll talk to the GLBT student services guys about it, just to make sure I've got someone on my side if something happens, promise.''

She nodded and relaxed her grip somewhat, ``Alright.  Didn't mean to sound rude, I just worry sometimes.''

I gave a little sigh of a laugh, ``Maybe you are empty nesting.''
