I climbed out of bed after an hour of trying to sleep and sat on the floor in front of my computer, watching the screen dully as it lit the room with streaming characters, the boot sequence scrolling by haltingly.  The grayish glow it cast around the room left only a rectangular shadow from my bed against the wall, my room almost completely empty other than that, a few boxes stacked in one of the corners contained most of the rest of my stuff.

The stream of characters blinked to nothing before being replaced by a gray screen, and then a blue one, prompting me to log in.  I typed in my username one-handed --- CoryroC --- and then the string of letters, numbers, and punctuation that served as my password, watching the system load the rest of the way.

I stared at the fractal pattern of my desktop for a few moments longer before finally moving, dragging the mouse cursor up to the top of the screen to select the wireless network to connect to, the one I had set up nearly two years ago for Jared.  I barely waited for the network manager to finish authenticating before opening up my browser and, on a whim, my IM client.  I told myself that I was hoping that a few friends from high school would be on, that I wasn't really hoping against all logic that Kris would be on at midnight.

Rather than watching the names pile up in the contacts window, I switched immediately to my browser to check email and forums, figuring that maybe if I didn't look at the buddy list, I wouldn't be disappointed.

My email had hardly loaded before the window was partially obscured by a message.\vspace{1em}

\textbf{\color{red}krisTALsaidso}: no sleep?

\vspace{1em}I tried to keep my heart from squeezing out from between my ribs as I typed back.\vspace{1em}

\textbf{\color{blue}CoryroC}: No.  You?

\textbf{\color{red}krisTALsaidso}: just got home from a movie with the folks

\textbf{\color{blue}CoryroC}: Cool, cool.  How are things going down in Boulder?

\textbf{\color{red}krisTALsaidso}: alright so far

\textbf{\color{red}krisTALsaidso}: how bout up in the mountains?

\textbf{\color{blue}CoryroC}: Cold and boring :P

\textbf{\color{red}krisTALsaidso}: aw poor boy. having fun with the family at least?

\textbf{\color{blue}CoryroC}: Nah, they're the boring part :P  I told my mom and step dad about us, though.

\textbf{\color{red}krisTALsaidso}: howd that go?

\textbf{\color{blue}CoryroC}: My mom was fine with it, though she said she was worried that I got into the relationship too fast, and that I was trying to make my life extra different by moving away and dating a girl.

\textbf{\color{red}krisTALsaidso}: weird.. do you think you rushed into this?

\textbf{\color{blue}CoryroC}: Yeah, but that's why it's so fun :)

\textbf{\color{red}krisTALsaidso}: god your such a dork.  what about your stepdad?

\textbf{\color{blue}CoryroC}: He was happy.

\textbf{\color{red}krisTALsaidso}: cool

\textbf{\color{blue}CoryroC}: I guess.  I feel a little offended because he was only happy that I wasn't going out with boys anymore.  He's kind of a dick like that.

\textbf{\color{red}krisTALsaidso}: that sucks

\textbf{\color{red}krisTALsaidso}: like he wasnt happy for you just happy at your expense

\textbf{\color{blue}CoryroC}: Yeah.  He told me he was glad that he could finally relate to me now, and asked all these questions about you.

\textbf{\color{red}krisTALsaidso}: ew like what kind?

\textbf{\color{blue}CoryroC}: Just like how you looked and why I liked you and if you were hot or not.

\textbf{\color{red}krisTALsaidso}: how did you answer?

\textbf{\color{red}krisTALsaidso}: answer carefully ;)

\textbf{\color{blue}CoryroC}: Hehe.  I said you were short and had short hair.

\textbf{\color{red}krisTALsaidso}: dick

\textbf{\color{blue}CoryroC}: Heh.  I said I liked you because you're funny and sweet and more honest than anyone.  And I said you were hot :)

\textbf{\color{red}krisTALsaidso}: good boy

\textbf{\color{blue}CoryroC}: Thanks :P  It's really weird having this random old man asking me about you, whether you're hot or not.

\textbf{\color{red}krisTALsaidso}: i know, gross

\textbf{\color{red}krisTALsaidso}: what are you doing for thanksgiving?

\textbf{\color{blue}CoryroC}: I'm supposed to drive to my dad's and have it down there with him and his girlfriend in the Springs.

\textbf{\color{red}krisTALsaidso}: aw ;( i was going to ask if you wanted to come to boulder

\textbf{\color{blue}CoryroC}: Aw :(  That would be nice.  Though I'm driving back up from the Springs straight to school, I could come see you then. :)

\textbf{\color{red}krisTALsaidso}: really?  could you give me a ride to school then?

\textbf{\color{blue}CoryroC}: Of course :)

\textbf{\color{red}krisTALsaidso}: yay ill let my parents know

\textbf{\color{blue}CoryroC}: Cool :)  Maybe you can show me some of Boulder when I pick you up

\textbf{\color{red}krisTALsaidso}: yepyep its a cool place

\textbf{\color{red}krisTALsaidso}: i need to go to bed cor :(

\textbf{\color{blue}CoryroC}: :(:(:(:(

\textbf{\color{red}krisTALsaidso}: im sooooorry.  i need to

\textbf{\color{blue}CoryroC}: I suppose I can let you go ;)  Sleep well.  I'll talk to you later.

\textbf{\color{red}krisTALsaidso}: thanks hun.  you sleep soon too.  **MWAH**

\textbf{\color{blue}CoryroC}: Hehe, mwah.

\textbf{\color{red}krisTALsaidso}: :)

\textbf{\color{red}krisTALsaidso}: bye :)

\vspace{1em}I read through the conversation again once the icon on the window turned from green to grey before closing the window, closing my email without reading any of it, and telling the computer to suspend.  I climbed back into bed once the screen went dark and stretched out on my back.  I'm sure I fell asleep still smiling.

The next morning, I felt just as good as last night had made me feel, and so the drive down south to visit my dad didn't seem to be that big of a deal as I packed up everything I needed for school once more in my car and said goodbye to my mom and Jared.  My mom kept telling me to have fun and be safe, and Jared just kept grinning at me in a way that made me want to slap him.

``How's it goin', jerk?'' I asked my car as I settled into the seat again for the first time in nearly six months.  I spent a minute or two making sure everything was adjusted to my preferences before starting the little sedan up and setting it into reverse, letting off the brake and just touching the gas to get the car smoothly up over the hill of our driveway and onto the street again, grateful that I could once again describe anything my car did with the word `smoothly'.

Once I wound through the southern edge of town and got back onto the highway headed up the pass, I settled back into the rhythm of driving once again, sipping at my coffee and lifting a CD out of the center console to slip into the player.  I let Bernstein lift me up over the pass, easing my way along with traffic carefully and relaxing at the sight of real snow piled all around me, not the thin, anemic stuff that Fort Collins called snow.

Once I was over the pass, the drive became easier and afforded me plenty of time to think, considering I still had a few hours to go until I reached my dad's.  I struggled to digest the recent abrupt change in my life and more easily put it into words.

Kris had walked into my life with an ease that belied how much she had come to mean to me.  My attraction to her, to her height, to the way she did her hair and the clothes she wore, her belly and her hips, and even her breasts; to her personality and her laugh and the way she always called me `boy' or `Cor', somehow morphing my name into `heart' in other languages.  It seemed obvious to me why I had fallen for her, until I took her gender into account, and I was confronted with the fact that, for all of my life as long as I could remember, I had never been attracted to girls at all.

Pacing myself with traffic and watching the road with half my attention, I set the other half to try to define what it was that I liked about guys that I didn't like about girls.  There were, of course, the obvious physical differences --- I could hardly deny the fact that most girls simply weren't attractive to me.  I chalked up stereotype after stereotype under the female column and countered each with a stereotype about guys before scrapping that project.

Maybe it was just Kris?  I tried to define what was different about her that didn't seem to fit in with my previous definition of Girl.  She certainly did seem more easy-going than most of the girls I had been friends with, and she did seem surprisingly unself-conscious, a trait I had found distinctly lacking in many of the girls at my school.  Thinking back on it, though, the same trait reared its ugly head in guys, and had been a large part of why I had focused less of my attention on the guys at school and more on those I met on the internet.

I did my best to skirt the possibility that my mom had mentioned, that I was just going out with Kris because I was trying so hard for something different than what I had in high school.  I felt that I couldn't be that shallow, and more than that, I wanted to give Kris the benefit of the doubt.  Clearly there was something about her that had caused me to let her into my life and to get as close with her as I did.

My thoughts were derailed as my mind wandered from trying to define Kris to trying to picture her, which led to the inevitable thoughts about the night before break.  I shifted slightly in my seat and winced, kneading the heel of my palm down against the crotch of my pants as if to stiffle the erection that had resulted from such thoughts.  I settled for rearranging the uncomfortable situation in order to continue thinking about it.

The sex had been perhaps the most surprising part of it all.  Where I normally was so nervous around guys that I could hardly perform, that night had gone startlingly smoothly in my opinion.  It took me a few minutes to remember the fact that both Kris and I had been a little drunk, which certainly must've helped with my nerves.  I struggled with the conflicting feelings of the experience going counter to everything that I had previously desired and all that I had enjoyed about that one night a few days ago.

Sex, it occurred to me, was just sex, no matter with whom.  I suppose I could've enjoyed sex with just about anyone, so long as the desire was there, so that wasn't part of the problem.  Of course, that just brought me back to pondering the source of my desire for Kris, which really boiled down to the question I'd been asking myself for nearly eight years now: why did I generally prefer guys in the first place?

I shrugged off this dead-end and slipped in a different CD once the Bernstein finished, going back to remembering about that night instead, and thinking of how good it would be to see my girlfriend --- girlfriend! --- again.
