Kris and I pooled our resources.  Kris had a joint and a half, I had half the bottle of Gin left, plus a beer.  Our combined monetary assets were a handful of bills totaling fifteen dollars and seventy eight cents (three pennies courtesy of the bottom of Kris' backpack --- I only ever kept quarters).  By our powers combined, we were going to make the most of our Wednesday night.  After all, I would drive Kris back down to her parents' the next day on my way to my Dad's.

``A walk is necessary,'' Kris anounced, grandiose.  ``A journey, if you will.''

``Would you perhaps be willing to call it a mighty journey?'' I hazarded.

Kris rewarded me with my jacket, which I slipped into.  The warmth of a shot of gin, `preloading' she had called it, made the coat seem almost superfluous, but there was a fresh four inches of snow on the ground.  ``Well,'' she looked thoughtful.  ``I suppose Old Town could be considered mighty.  Yes, then.  A mighty journey.''

I laughed and followed her out of the room.  ``What are we going to find in Old Town that we can get for fifteen and change?''

Kris slowed her strides somewhat to let me catch up as I worked on zipping up my jacket.  ``I dunno,'' she said cheerfully.  ``Something.  Just want to get a last look at the place so I can go home and feel superior about Pearl Street.''

``Aw, come on, Old Town's not that bad.  They practically have the same shops on them, the only difference is that there are cars on College.''

``Yeah, I guess.''

``Guess we all gotta have goals.''

Kris laughed and pinched me in the side, ``Hey, at least I can get from one side of the street to the other without fearing for my life or waiting for twenty minutes.''

``True, true.''

``Girl's gotta be proud of where she comes from.''

I shook my head, ``You can't talk like that.  You're a very, very white neohippie.''

Kris pinched me again, harder this time.  ``Pot.  Kettle.  Black.''

The banter continued as we made our way out of the dorm and up across campus.  It was hard not to feel light and goofy.  Gin not withstanding, the lack of finals hanging over our heads was making us giddy, and the air being cold enough to burn the back of our throats did little to dampen our spirits.  We just walked faster.

``Oh my God!''  Kris dragged me to a stop only half a block north of campus.  ``Calzones!''

There was no arguing with calzones, so we dined on folded-up pizza and drinks, which left us with only a couple of dollars left.  We huddled over our cardboard boxes of food, sitting around a polyurethane slab that appeared to have some wood in the middle, an adequate substitutde for a table.  We took turns kicking each other's shins beneath the table and giggling at each other over the lids of the boxes which sat propped up in front of us like Battleship sets.  Pepperoni had never tasted so good.

Emboldened by gin, full of cheese and starch, we made our way back out into the night and trudged back north, bumping into each other every now and then as our steps just happened to line up wrong (or right).  We passed restaurants cheap and expensive, all starting to fill up with equally excited students.  A block or two later and we started passing bars, already packed to the brim with the older students, just as excited and much drunker.  Kris mimicked the various types of drunkards for me, and I laughed as she procured looks of disdain or amusement from passers by.

When that entertainment wore thin, we walked silently holding hands and weaving around countless others on the sidewalks.

Our warmth started to leak away by the time we reached the northern end of the street mall, and my patience with the crowds was beginning to wane.  We turned west instead of directly south and walked a block in that direction before heading back to the campus.  Someone had wisely planned a major railroad line down the middle of this one way street, as well as through campus, a fact which made me late for class on more than one occasion as I waited for a train to pass.  Now, it just enforced a few minutes more of silence for Kris and I as a train blared, then rumbled past, a comet shaped noise trailing off as the train passed.

``So,'' Kris said when we could speak again.

I nodded sagely, ``So.''

Her grip on my hand tightened briefly before she tugged free and pocketted the hand.  ``What are we going to do with a month?''

``I'm not sure.  Gonna try to do odd computer jobs for cash in the Springs and Steamboat, hopefully find a way between the two that has Boulder as a midpoint.''

Kris nodded and tucked her chin down so that she could push the lower half of her face into her scarf.  ``Can get us a few days together that way, I bet.''

``Yeah.  Probably not as much as either of us were hoping for.''

She shook her head.

``You're welcome to come visit either place, too,'' I murmurred, mind already tripping over the logistics of that.  ``Though that may be kind of weird.''

``Parents?''

I nodded, ``Unfortunately.''

We walked quietly again, watching a horde of bicyclists swerve and waver down the street going the wrong way.

``What about a party?'' I quipped.

``Hmm?''

``Well, I mean, we've got mutual friends.  Eric and Erin.  Jamen, maybe Joseph.  Probably a couple of others.  We could all get together somewhere, try to convince parents that we're reasonable and logical enough to spend a weekend in a hotel at a ski resort or something.  Make it into a party or something.''

Kris brightened up, ``That could work, if we can somehow combine enough money for it.''

``Well,'' I shrugged.  ``I've got a credit card I've used twice or so, I guess we could put it on that, so long as everyone pays us back.  I think most people get money for Christmas, now that they're in college.  At least, that's all I ask for.''

Kris laughed and goose-stepped to try to show me her shoes, ``I need more of these, better for walking.  S'what I asked for.''

I laughed, ``Fair enough.  Think your parents would go for that sort of thing?''

She shrugged, ``My dad will be all gung-ho about it, and I think it'll be pretty easy to convince my mom.''

``Cool, cool.  My dad will be all for it, dunno about my mom.  I can beg and beg, I suppose.''

``You'd better!'' Kris laughed, elbowing me.  ``I want to see you in some context other than walking around Boulder.''

``Ah hell, even if it doesn't pan out, I promise that's not all we'll do.  We can go see movies and stuff.  So long as they're matinees.''

Kris rolled her eyes, ``So we can catch all the field trips and old people.''

``I know!  Won't it be romantic?''

She laughed and leaned against me as we walked, two blocks to go until we got onto campus again.  ``So where were you thinking we could have this party thing?''

``Oh, I dunno.  One of the less expensive ski areas, I guess, or close by.  I know a few places in Steamboat, but that might be too far of a drive.  I guess we could do it in other places, too, like Denver or wherever.  Just get a hotel room somewhere.''

``Yeah.  I mean, I didn't expect that we'd be going out to a ski area to ski, really.''  She shrugged, ``I've only ever gone once or twice before.  I sucked at it.''

I grinned, ``Aw, it'd be fun.  I can ski backwards.  Could give you lessons skiing in front of you like that.''

``That sounds disgustingly cute.  Not sure how I feel about it.''

``We all need somebody to lean on,'' I warbled.

She snickered and freed her hand to hug onto my arm, giving it a squeeze.  ``Shut up.  I hate that song.''

``Pff.  Alright.''

``Well, anyway.  I think the ski area would be better for partying if we decide to drink or anything, since Denver's likely to be much stricter about that.  Denver will be cheaper, though.''

``Yeah.  And closer for more people.''  I nodded, ``But you're right.  I don't think going to some hotel in Denver just to party would be that good of an idea, especially if we want to drink at all.  I don't think any of us would be over twenty-one.  Besides, from watching the crowds at Steamboat, it seems like just the Thing You Do when you go to college; partying in a ski slope hotel.''

``Yeah, I remember my dad talking about it from his college days.''

The rest of the walk to my dorm was spent hashing out possible plans and discussing various results of such a party.  We stomped the snow from our feet after crossing a field to more quickly get to the entrance to the building, finally shedding layers and relaxing once we got to the room.  Thomas was gone for the time being, but his screen saver was on, indicating a temporary leave.

Kris dug her backpack from under the bed and pulled out the oboe reed case containing her minimal stash extracting the half-smoked joint from the tube and setting it delicately on the corner of my desk before returning the tube back to her bag.  As if magically drawn by the scent of newly exposed pot, Thomas wafted back into the room with a beatific smile on his face and a campus paper tucked under his arm.

I burst out laughting, ``I've never seen someone look so relieved.''

``Hey man,'' he said dreamily. ``Never underestimate the power of a good shit.''

``You, my friend, are disgusting,'' Kris said, sticking her tongue out.  Her expression immediately brightened as she gestured toward the half-joint on my desk, ``Smoke?''

Thomas nodded sagely and set about fishing his towel out of the pile of clothes that served as his laundry basket.  While the other two made preparations for the pot, I cracked some ice into my travel mug and added about a double shot of gin to that, setting the rest of the bottle out for those who wanted.  Thusly situated, we settled in to party as quietly as possible.

``Fuckin' refrieds,'' Thomas sneered, but accepted Kris offer of letting him start the nub of a joint out, setting the sploof in his lap and the incense nearby as he drew the harsh smoke deep.  Passed the marijuana on to Kris and sat still for a moment, face screwed up as if he was concentrating.  His brows furrowed into a frown as he grabbed at the soda bottle he used as a sploof, coughing violently into it.

Kris raised her eyebrow and shrugged, taking her turn at the still smoldering pot, relighting it as she held it carefully, taking a large pull from it herself and passing it almost immediately on to me.  I watched bemusedly as the ritual repeated itself with my girlfriend --- the pained look and then the coughing into a bottle.  The whole concept seemed decidedly silly.

As both of the others relaxed, I pondered the quarter of a joint left in my hand.  Then, on a whim, snagged the lighter from the floor and joined in, figuring I'd give the stuff one more try.

My throat burned on contact with the harsh smoke, and I had to stiffle the urge to swallow convulsively.  My eyes watered and I swallowed a laugh as I passed the joint on to Thomas, who was chuckling at my expression.  Kris laughed as she handed the soda bottle to me, which I, desiring only to fit in, coughed into explosively, sending up a cloud of weirdly scented smoke from the hole on the end of the bottle.

``Figured you'd come along?'' Kris giggled.

``Why not?''  My voice was hoarse and choked, and my throat felt like I had swallowed a thistle blossom.  ``Worth a try.''

Thomas laughed and waved the smoking brand of his incense stick around the room briefly to douse us in the saccharine scent.  ``Thanks for smokin' me up with my own cheap-ass shit,'' he murmurred, licking his fingers and pinching the ember on the stick of Nag Champa.  ``Y'all gonna get crunk, too?  C'n I have some of that gin?''

I laughed at the wording and nodded, gesturing to the bottle with my head as I took a swallow of the liquor from my travel mug, the cold liquid soothing my scorched throat, only to introduce a different type of burn.  I passed the cup on to Kris and scooted over next to her where she sat on the bed, ``Thanks.''

``Mm,'' she said, taking a few sips of the drink.  ``You're my boyfriend, I think I'm, like, required to share with you.  Didn't know you'd be smoking up, though.''

I nodded and shrugged, already feeling the fog roll into my thoughts and blanket them in mist.  ``Figured why not,'' I mumbled, leaning to give her a kiss on the cheek.

``Cute,'' Thomas mumbled from across the room, spending the rest of his attention on trying to pour some of the gin into half a Mountain Dew he pulled from his backpack.

``Ain't it grand?'' Kris giggled.

Thomas snorted.

``How come we never see you with anyone, anyway?'' I managed to slur.

Thomas, drink held proudly in hand, recapped the gin and set it by the fridge, hidden in case someone opened the door.  ``Got a girl off campus.  Says she don't want to come over here.''

``Yeah?'

``Don't think she did so well in the dorms.  Does her best to stay out of them now.''  He shrugged and pushed himself back onto his bed, only spilling a little of his drink onto his front.  ``I stay with her for the weekends.  Gives you two room to, heh, do your thing, anyway.''

My thoughts meandered dully around, and it took a few seconds to parse what he had said.  I went to reply but found that I had been sitting with my mouth open, so I settled for just closing it and shrugging.  Kris stuck her tongue out at Thomas and flopped back onto the bed, throwing a corner of my comforter over her face.

``What?  S'not a problem,'' Thomas chortled.  ``You two are cute, in a kiddy sort of way.''

``Thanks a lot,'' I managed before a giggle took over.  Heh, `kiddy', went my brain.

He saluted and set his drink down on his desk, levering himself up to take another toke from the remainder of Kris' joint, leaving it as little more than a nub afterwards.  The coughing was repeated, abbreviated, and he set to puttering around the room.  He picked up a DVD and set it to play on his computer, keeping the volume turned way down, then put his headphones in anyway and turned up his music.  He told me that he was dead set on finding new soundtracks to movies, and this was how he went about it.

Feeling my eyes glazing and my eyelids drooping to half-mast, I finished the rest of my cup of gin.  I refilled the travel mug with another double shot of liquor before setting it on the desk next to the head of the bed.  Kris, meanwhile, cold as usual, pulled herself up into my bed and climbed in under the covers, hugging some of them to her front.  She chuckled as she watched me struggle to untie my shoes, then helped to pull me up onto the bed with her after I got them off.  I climbed up over her only to flop down behind her.  I rolled to face away from the wall, an effort on about the same scale as Boston's big dig, what with pot and alcohol both impairing, and tugged the covers over me so that I could nestle in behind Kris, head propped up so that I could watch Starship Troopers over her shoulder.

My thoughts were still meandering, but I was no longer in control of them.  It left me feeling mute and stupid, unable to express or even experience any of the numerous ideas and emotions that swirled together in a vague blur inside my head.  After a while, I gave up trying.  The one clear thought left was that I was getting to spend the last night for more than a month with Kris here away from home.  It was depressing at the same time as it was comforting, but that's about as far as I got in analysing it before giving up and hugging my arm around my girl.
