``Is this...?  Yeah, this has to be it.''  My mom muttered.

I jerked my head up from where I was half-dozing against the window at the words.  Blinking at the light, I looked around.  From the time I had spaced out an hour or so before, the landscape had changed from brownish scrublands of Wyoming to the tan plains east of the Rockies that I knew from the drives to band camp.  That had always been my dad's deal, and this was only my mom's second time driving to Fort Collins.

``Yeah, take this one,'' I yawned.  Rubbing at my face, I struggled towards wakefulness.  I fumbled around and found the second half of my coffee, long cold by now, and finished it with a grimmace.  ``Hopefully the places here have better coffee than this.''

``Can't have you without your coffee,'' my mom laughed.  ``Good dreams?''

``Nah, wasn't sleeping.''

``Mmhm.  Do you always drool when you're not sleeping?''

``Sure,'' I mumbled.  ``That's what spit valves are for.''

She laughed and steered her way towards campus.  I guided her through the move-in day traffic onto the campus and toward the dorms, letting her interrupt me as patiently as I could with her outbursts of drumming the steering wheel while sing-songing, ``This is exciiiiitiiiiing!''

Following the crowds, we made it to the south end of campus slowly and pulled up along the side of the street with the other cars disgorging students and stuff.

``Glad we made it here early,'' I mumbled.  There were already twenty or so other families unpacking along the stretch of road, and more were visible in the parking lots on either side of the building.  Looking over the bent `H' shaped dorm and trying to count rooms, I grimmaced at the thought of that many families trying to move their children in at once.  No, I corrected myself, that many times two, what with the whole roommate thing.

Before unpacking anything, my mom and I made our way around one wing of the building toward the lobby.  We stopped to pick up my key and get directions to the room itself.  Walking along the hallway to the wings, my mom was bouncing on the balls of her feet, poking fun at me for being more excited than I was.

``I'm excited, I promise.  Just dreading the common restrooms.''

``Aw,'' she jibed.  ``They're not that bad, I promise.  Just have to get used to it.  And schedule your showers for when the least amount of people are in there.  And wear sandals when you do.''

``Thanks mom, you fill me with confidence.''

``I aim to please,'' she shot back.

The doors to the southwest wing on the second floor were propped open and standing just inside was a man who looked to be in his late twenties who introduced himself as Mark, the RA for the hall.

``Small!'' my mom blurted as we were shown to my room.  Both Mark and I laughed as we followed her in, but I had to agree with her.  The far wall was taken up by a bank of picture windows, and opposite that was a bank of closets, split into two sets, one for each person, I supposed.  Other than that, the room was a bit drab and depressing.  The two empty walls were tan brick, though each one was partially obscured with a cork-board painted an institutional sort of off-white.  Along each of those walls was a long twin bed and a wooden desk that looked functional enough, though instead of drawers, the side of the desk held shelf space.  Addict that I was, I was already mentally fitting my printer onto one of those shelves and my computer down by my feet.  Tight fit.

It looked all the more shabby for how empty it was: my roommate had yet to show up.

I buried my sense of disappointment about the room under the activity of moving my stuff from the car to the room, one armload at a time, with my mom.  She had made me clean out my whole room at home and throw away, give away, or sell as much as I could stand to, promising that it would be better, and after lugging only my computer, a laundry basket of clothes and bedding, and a few loads of books into the room, I had to agree with her forecast.  In the process of cleaning out my rooms at my mom's and dad's, I was exposed to just how much junk one person could have.

When we finished getting everything stacked on my bed, we made our way back to the car to make way for another family while we went out to lunch.

``Well, your RA seems nice,'' mom quipped on the winding drive off campus.  ``Mine, when I lived in the dorms, was a big priss.  She was useless as an RA, so we just pretended we didn't actually have one.''

``Yeah, he was cool,'' I replied distractedly, pointing her towards a little mexican restaurant I had found in my last year of band camp.

After a pregnant pause, my mom asked, ``So, when are you going to come out to him?''

``I'll get around to it,'' I sighed.  ``It's not that big of a deal to me; I mean, it is normal for me.  I think if I act that way, others will see it as normal, too.''

Mom nodded hesitantly.

We made our way inside and ordered our food, taking our burritos and drinks to a booth out of the way near the back of the restaurant.

``I don't mean to be such a worrywort,'' my mom began, and I knew that was a disclaimer that more worrying was on the way.  ``But I just think that it's something you need to worry about a little yourself.  In high school, it doesn't mean as much because you're not living with those people, and the teachers are pretty much required by law to be okay with it.  They can't show it if they're not, I mean.''

``Well, sure, but I'd like to think that since I'm going to a school the size of the town I grew up in, that I'd get a little anonymity from that,'' I countered.  ``Sure I live with these people, but it's only for this year.  And besides, I can sort of... keep things down low, know what I mean?  I can wait to meet people and see how they are before I go about being openly gay.  Hell, I waited for fourteen years, trying to figure out how you guys would react before I mentioned it to my own parents.''

Mom laughed around her bite of food and nodded, pausing to swallow before continuing.  ``I know I should trust you more, but it's my job to worry.  Highschool went pretty smoothly for you, especially once you started doing so well in band, but that's not to say that the same thing will happen here.  Just saying.''

We finished in silence before making our way back out to the car, my mom tapping the ``Now Hiring'' sign taped up next to the door and raising her eyebrows at me.  ``You should think about this, Cory.  You know we kind of had to skimp on your meal plan a bit, so you should probably think about getting a job pretty soon to get some food for yourself.''

I nodded as I slid into the passenger seat again, ``Hopefully the market's a little better out here than it was in Steamboat.  I'd prefer to avoid working at Subway again.''

``Yeah, that wasn't exactly your dream job, was it?''

``I worry for those who dream of working at Subway.  Anyway, let's check out this Old Town thing before I have to get back for yet another campus tour.  Get to see the town before I'm buried under homework and classwork.''

As we drove up north to seek a parking spot near the long row of shops that was Old Town, I worked to reconcile my mom's worries with my lack of them.  I just hoped it would be as easy as it was in my imagination.
