It turned out that there were still quite a few people flumoxed by those newfangled computer things that people seemed to go on about.  Purchasing one had proved to be quite an adventure and, despite the promises made by salesmen at every location, they weren't quite as easy to set up as anticipated.

Another hundred dollars found its way into my pocket by means of five hour long lessons given across the town.  One person had already called the service branch of a well known store in order to have them come out to her house to fix her computer, but they had just messed it up further.  On the plus side, the machine was still under warranty and the visit didn't cost anything.  Unfortunately, that warranty carried little weight after that visit, and so I had been called.

Despite the money I had made, I was under no illusions of continuing to make it at the same pace.  Most all of that cash had come straight from people who needed help with their new Christmas presents, and I knew such things would taper off.  I was honestly surprised to make as much as I did.  Of course, tempting as the money was, I felt that I would likely hang myself before I went into tech support as a profession.

And I still had a week to go until the party.

I decided I'd rather spend my time relaxing for the rest of the break and drove around town tearing down all of the signs I had posted and finally stopping off at the bank to deposit the cash into my checking account.  Debit cards were much easier than a fist full of twenties, at least for myself.

Once home, of course, I was confronted with Jared.  He seemed to alternate between watching TV, ripping through the classifieds of various newspapers, and surfing the internet.  Sometimes, of course, I'd find him watching TV shows on the internet with a paper strewn over his keyboard and desk.  While I applauded him on his efficiency, he was decidedly uncomfortable to be around, so after feeding the dogs, I slipped back into my room and sprawled next to the computer on the floor, shaking the mouse and waiting for the aged CRT to click to life.

I took down my away status on both IRC and my instant messenger client, taking a few minutes to scroll through backlogged messages on the former and seeing who was online in the latter.  It was enough to make me doubt my choice of leaving the rest of my break open, and I cursed my relatively remote location in keeping me from possible meetups and all sorts of action.

Resigned to watching music videos on the internet and reading webpage after countless webpage, I pulled my pillow and blanket down from the bed to make something of a nest for myself there on the floor.

My third music video was interrupted by a an instant message popping up and covering a portion of the singer's face.  I reached for the mouse in my usual reaction to minimize the window to allow me to finish the video but hesitated when I skimmed over the message.

\vspace{1em}\textbf{\color{red}aramanth}: Hey, Cory.  Jamen.\vspace{1em}

I blinked away boredom and couldn't help but smile.  I let the video continue in the background, moving the conversation window over to the side so that I could keep an eye on both.\vspace{1em}

\textbf{\color{blue}CoryroC}: Oh, hey!  What's up?

\textbf{\color{red}aramanth}: Not a whole lot.  Just being lazy, I guess.  You?

\textbf{\color{blue}CoryroC}: About the same.

\textbf{\color{blue}CoryroC}: How'd you get my s/n?

\textbf{\color{red}aramanth}: It's on facebook, duh :oP

\textbf{\color{blue}CoryroC}: Crap.  Almost forgot I was on that.

\textbf{\color{red}aramanth}: *laughs*

\textbf{\color{red}aramanth}: Excited about the trip?

\textbf{\color{blue}CoryroC}: Thrilled.  Gonna be a boring wait until then, for sure.

\textbf{\color{red}aramanth}: I know what you mean.  Alamosa's not really a very thrilling town.

\textbf{\color{blue}CoryroC}: Yeah, neither is Steamboat, especially when it's so expensive to ski.

\textbf{\color{red}aramanth}: *laughs* Yeah.

\textbf{\color{red}aramanth}: So anyway, I figured I'd message you to ask a favor.

\textbf{\color{blue}CoryroC}: Sure, anything.

\textbf{\color{red}aramanth}: I don't know if I'll have enough to both drive diagonally across the state and pay for the room.  Think you could help out some.

\textbf{\color{blue}CoryroC}: Oh!  Of course.

\textbf{\color{blue}CoryroC}: What would work best?

\textbf{\color{red}aramanth}: Well, you live in the Springs, right?

\textbf{\color{blue}CoryroC}: Some of the time yeah.  In Steamboat now.

\textbf{\color{red}aramanth}: Oh.

\textbf{\color{blue}CoryroC}: Why, what were you thinking?

\textbf{\color{red}aramanth}: *shrugs*  Well, I was hoping I could just drive over to the Springs and catch a ride with you from there to Winter Park.

\textbf{\color{blue}CoryroC}: Oh, that should be fine.  I can head down to my dad's on Monday or something, and just spend some time there until you come over.

\textbf{\color{red}aramanth}: You sure that's alright?

\textbf{\color{blue}CoryroC}: Of course :)  I'm pretty eager to get out of this place, anyway.  Step-dad's driving me nuts.

\textbf{\color{red}aramanth}: You're telling me.  I need to get away from my family something awful.

\textbf{\color{blue}CoryroC}: Its enough to make one want to go back to school sooner.

\textbf{\color{red}aramanth}: No kidding.

\textbf{\color{blue}CoryroC}: So how've you been, anyway?

\textbf{\color{red}aramanth}: Well, aside from parents, alright.  Bored.  Couldn't get any seasonal job so I've just been sitting around on the internet mostly.  My parents think I'm researching a project for next semester.

\textbf{\color{blue}CoryroC}: I assume you're not? :P

\textbf{\color{red}aramanth}: Hell no.  Give myself more work?  That goes counter to the artist's creed!

\textbf{\color{blue}CoryroC}: Haha, of course.

\textbf{\color{red}aramanth}: Besides, it's better that they think that than find out I'm talking to others.

\textbf{\color{blue}CoryroC}: Not too keen on the internet, are they?

\textbf{\color{red}aramanth}: No, definitely not.

\textbf{\color{red}aramanth}: They're afraid I'll meet someone who will turn out to be a rapist or something.

\textbf{\color{blue}CoryroC}: Oh.  Yeah, had to break my parents of that assumption pretty early.

\textbf{\color{red}aramanth}: I wish I could, man.

\textbf{\color{blue}CoryroC}: Good thing I'm not a rapist, then.

\textbf{\color{red}aramanth}: *laughs* No, I didn't figure you to be one.

\textbf{\color{blue}CoryroC}: Good :P

\textbf{\color{red}aramanth}: You're gay, though, so it wouldn't make a difference to my parents.

\textbf{\color{blue}CoryroC}: Aw.  I guess I'm bi, but I guess that wouldn't matter, would it?

\textbf{\color{red}aramanth}: Oh yeah.  Still just as bad.  Worse, 'cause they think that means you're just a gay guy who rapes girls too.

\textbf{\color{blue}CoryroC}: Jesus..

\textbf{\color{red}aramanth}: Sorry :oP  Probably more than you really needed to know.

\textbf{\color{blue}CoryroC}: No, it's alright.  I just didn't know.

\textbf{\color{blue}CoryroC}: Don't know anything about your life at home, so it's kind of interesting to hear if nothing else.

\textbf{\color{red}aramanth}: *nods*

\textbf{\color{blue}CoryroC}: So your parents are really that homophobic?

\textbf{\color{red}aramanth}: Yeah.  Makes me wish I was back up at school.

\textbf{\color{blue}CoryroC}: So, uh.. no offense or anything, but are you gay?

\textbf{\color{red}aramanth}: *nods*

\textbf{\color{blue}CoryroC}: Oh, alright.

\textbf{\color{red}aramanth}: Sorry.  I kind of led the discussion there.

\textbf{\color{blue}CoryroC}: Hmm?

\textbf{\color{red}aramanth}: Well, it's easier to just answer truthfully when someone asks than to come out.

\textbf{\color{blue}CoryroC}: Oh.

\textbf{\color{blue}CoryroC}: Yeah, I know how it goes.

\textbf{\color{blue}CoryroC}: So do your parents know, then?

\textbf{\color{red}aramanth}: They did.

\textbf{\color{red}aramanth}: I told them it was just a phase.

\textbf{\color{blue}CoryroC}: Ah, alright.  So they think you're straight now, then?

\textbf{\color{red}aramanth}: *nods*  Better that than the alternative with some people.

\textbf{\color{blue}CoryroC}: I guess, yeah.

\textbf{\color{red}aramanth}: I envy you with having found Kris.

\textbf{\color{blue}CoryroC}: Well

\textbf{\color{blue}CoryroC}: I wasn't really planning on it.

\textbf{\color{blue}CoryroC}: Besides, my situation at home is quite a bit different from yours.

\textbf{\color{red}aramanth}: Yeah.  Parents a little more cool with it.

\textbf{\color{blue}CoryroC}: Mom and dad were, yeah.  Step-dad not so much.

\textbf{\color{red}aramanth}: Ah.

\textbf{\color{blue}CoryroC}: Yeah, he was pretty happy about Kris.

\textbf{\color{red}aramanth}: How did your parents deal, then?

\textbf{\color{blue}CoryroC}: Heh, strange.  It was almost like coming out all over again.

\textbf{\color{red}aramanth}: How so?

\textbf{\color{blue}CoryroC}: My mom worried that.. uh.. that it was just a phase from me moving to school.

\textbf{\color{red}aramanth}: Oh, heh.

\textbf{\color{red}aramanth}: And your dad?

\textbf{\color{blue}CoryroC}: It was almost the same as when I came out.

\textbf{\color{blue}CoryroC}: Though I think he was a little excited about possibly having grand children.

\textbf{\color{red}aramanth}: Yeah.

\textbf{\color{red}aramanth}: That was a big problem with my parents.  Any relationship that didn't lead to kids was just wrong.

\textbf{\color{blue}CoryroC}: I'm sorry, man :/

\textbf{\color{red}aramanth}: Nah, it's cool.  that's why I went to the other side of the state for school.

\textbf{\color{red}aramanth}: Anyway, I really am happy for you and Kris.

\textbf{\color{blue}CoryroC}: Thanks :)

\textbf{\color{red}aramanth}: It was kind of strange for me to hear that you could be going out with a girl.

\textbf{\color{blue}CoryroC}: How so?

\textbf{\color{blue}CoryroC}: Have anything to do with what we talked about earlier in the semester?

\textbf{\color{red}aramanth}: *nods*

\textbf{\color{red}aramanth}: Sorry again about that.

\textbf{\color{blue}CoryroC}: No problem.

\textbf{\color{red}aramanth}: So the whole story is that my parents found his phone number and looked it up, then called his parents to tell his.

\textbf{\color{blue}CoryroC}: Jesus..

\textbf{\color{red}aramanth}: Yeah..

\textbf{\color{red}aramanth}: Then he got stuck in aversion therapy.

\textbf{\color{red}aramanth}: My parents were going to do the same, but I told them it was only a phase and found a girl willing to be a cover-up girlfriend for me.

\textbf{\color{blue}CoryroC}: Ack, was wondering who you were talking about before.

\textbf{\color{blue}CoryroC}: That's pretty crazy :/  They left you alone after that?

\textbf{\color{red}aramanth}: For the most part, yeah.  They watched me pretty close until college.

\textbf{\color{blue}CoryroC}: They're not watching now, are they?

\textbf{\color{red}aramanth}: No, they suck at computers, and are out for the day anyway.

\textbf{\color{red}aramanth}: Besides, they're more worried about my sister now.  She's starting to go after boys now, and they're worried she'll have premarital sex or something.

\textbf{\color{blue}CoryroC}: So they're pretty christian?

\textbf{\color{red}aramanth}: Yeah.  I was for a while.  Kind of stopped believing when I was twelve or so.

\textbf{\color{red}aramanth}: Kept going to church because I had no choice with parents and such.  Didn't make me any more of a believer.

\textbf{\color{blue}CoryroC}: I suppose it wouldn't.

\textbf{\color{blue}CoryroC}: Both my parents are pretty liberal.  We went to church for easter twice before they decided it wasn't worth it for me.

\textbf{\color{blue}CoryroC}: Then they got devorced and gave up on the religion thing.

\textbf{\color{red}aramanth}: *nods*

\textbf{\color{red}aramanth}: It's always strange to hear about families different from my own.

\textbf{\color{blue}CoryroC}: Yeah, sounds like it was pretty rough for you.

\textbf{\color{red}aramanth}: I guess.

\textbf{\color{red}aramanth}: I love my parents, and they love me.  They just have different ideas for how I should live my life.

\textbf{\color{blue}CoryroC}: Well, I think you turned out pretty nice :)

\textbf{\color{red}aramanth}: *laughs* Thanks :o)

\textbf{\color{blue}CoryroC}: So how'd you convince them to let you go to the party?

\textbf{\color{red}aramanth}: Told them the truth.

\textbf{\color{red}aramanth}: Working with my partner on this art project.

\textbf{\color{red}aramanth}: :o)

\textbf{\color{blue}CoryroC}: Heheh, awesome :)

\textbf{\color{red}aramanth}: Anyway, they'll probably be back pretty soon, so I should get going.

\textbf{\color{blue}CoryroC}: Alright.  Hey, it was good to talk to you.

\textbf{\color{red}aramanth}: Definitely.  Don't think I could've said any of that to your face.

\textbf{\color{blue}CoryroC}: Well, I'm glad you did, even if online.

\textbf{\color{red}aramanth}: Me too :o)

\textbf{\color{red}aramanth}: See ya, man.

\textbf{\color{blue}CoryroC}: See ya.

\vspace{1em}The music video was long stopped so, as Jamen's icon flicked to grey as he logged off, I lingered long enough only to switch to the next video in line before rolling onto my back in my little next.  Nothing like having to reevaluate everything you knew about one of your friends, I thought.  Made me realize just how good I had it.
