Thanksgiving had come and gone without any flair.  Dad had spent his inventiveness with the holiday early on and, a few years ago, cooked turkey once a week for about a month and a half in order to find the best and simplest recipe, rather than every year trying something different.  I suppose it was his attempt at working toward tradition.  He had tried to make deep-frying the turkey the tradition, but on only the second year, he had splashed the oil on himself and burned his hand badly enough to put that project permanently on hold.

Now that Saturday had come around, though, I sat at the breakfast bar near the kitchen in his apartment, watching him putter around the kitchen, a series of disposable tupperware containers set out along the counter.  He carefully filled each with a serving of mashed potatoes and gravy, slices of turkey breast, and green beans.

``There,'' he announced, snapping the lid on the last of the containers.  ``Five of 'em should keep you going for... what, a day and a half, at the rate you eat?''

I laughed and nodded, slipping off the stool to grab the two dollar styrofoam cooler we had picked up at the grocery store the day before, setting it on the counter so that he could empty the five pound bag of ice we had also picked up into the bottom.  He stacked the rectangular meals above that.  He hesitated for a moment before unpacking the containers again and reaching into the fridge to grab four bottles of the inexpensive beer he drank and lay those on the ice before repacking the meals on top of them.

``You be way fucking careful bringing this into your room.''  He shot me a sly grin, ``Though from the sounds of it, your roommate is teaching you how to party already.''

I laughed and nodded, ``Thomas is a pro, that's for sure.  Thanks, dad.''

He nodded and rummaged around the junk drawer for a moment before procuring a roll of clear packing tape, taping the lid onto the styrofoam cooler.  ``This tape is not to come off until you get into your room and right next to the fridge.  If you get a ticket for drunk driving, I'm disowning you.''

I nodded, ``Of course.  Driving drunk scares me almost as much you.''

``Brat,'' he said, throwing the tape at me and grinning.

``Yeah, that's me, I guess.''  I got up to put the tape back in the drawer.

``Now two of those are Kris's, you hear?''  He whacked me between the shoulder blades, ``And some of that food, too.  Girlfriends are work, and they take bribing to keep them happy.  It's a big responsibility.''

``Damn straight!'' Jennifer, my dad's girlfriend, hollered from the living room.

Dad favored me with a commiserating look and I laughed.  ``Thanks again, dad.  Gotta get going here, though.  Picking Kris up on my way to school.''

``Alright, Cory.  You drive safe, yeah?  And call us once in a while.  We like hearing from you, despite what you may think.''

I leaned in and gave him hug with one arm while shaking his hand with the other, ``Will do.  Talk to you soon.''  Jenny had appeared at the doorway to the kitchen, so I gave her a quick hug as well, ``See you both around.''

They nodded and said their goodbyes as I grabbed the cooler, making my way out the door and down the flight of stairs to the parking lot.  The cooler made its way into the back seat in the footwell by my laundry basket.

Once I made my way back onto I-25, I headed north.

My dad's reaction had been the most surprising of all.  He somehow managed to find the perfect balance between the non-reaction that had bothered me about coming out and the concern that my mother had shown.  He told me that he loved me no matter what and, despite the cliche, it really did sound genuine.  He sat me down with a beer and sat across from me with his own as I talked.  It was awkward at first, but the fact that he seemed genuinely interested and actively listening soon got me to open up about my own concerns about the relationship.  He agreed with my mom's prognosis about getting into the relationship too quickly, but said that it wasn't a problem if we were both willing to work at it.

``I don't think you're trying to be too different too soon,'' he had said, shaking his head and leaning back in his chair, cradling his beer to his chest.  ``I just don't think that's like you.  Really.  To be honest, I was worried that you would drop into some of your old habits from early on in high school when you moved to college.  I was worried you'd focus just on your trumpet and not on your school or personal life.  It's good to hear that you're building a new life up there, and hey, it's good to hear that you're taking advantage of all new surroundings to even experiment a little.  This Kris sounds nice, and I want to meet her sometime, since it sounds like you two really do well together.''

I replayed more of the conversation in my head as I drove up towards Denver.

``What should I do if it doesn't work out, though?'' I had asked.  ``Girls seem so much more emotional that guys, so I don't want to start some big fight or make her freak out.''

He had laughed at me for that one, ``You seem to be ignoring the first Chris you went out with.  Christopher.  The angry phone calls?  Him threatening to kill himself?  You walking around always on the verge of crying?''

``Well, yeah,''I laughed too, then.  ``That's true.  That was a whole big mess.''

``I think you'll be fine, to answer your question.  You seem to have found a real gem.  One of those girls who doesn't seem burdened by her gender.  She's just a person, not a girl.  And I think she found a good boyfriend, too,'' he said, canting his beer towards me in a toast.  ``You're just a person, too, not a guy.  Just be careful this situation doesn't turn you into a guy.  You make a much better person.''

I had nodded along with him then, but now as I thought back, I think I was a lot closer to understanding how I had gotten myself into this wonderful mess.

I thought about it until I found myself on the outskirts of Boulder, setting the directions Kris had given me against the steering wheel and winding my way west, toward the base of the mountains.  The town was beautiful, and I had a hard time taking it in while driving and following directions at the same time.  It felt like a perfect mixture home and Fort Collins, with the mountains and the mild weather both, not to mention the beautiful planes of ruddy rock jutting up just west of the town, providing a comfortable backdrop for the city that promised to be amazing during sunrises.

I found myself in front of Kris' house sooner than I had expected and parked the car along the street in front of it, sitting for a second before digging in my pocket for my phone.  I was startled with my cell halfway out of my pocket by a knocking on my window, looking over to a positively beaming girl standing next to my car.

``Hey!  Get out here and meet the parents!'' she shouted, gesturing vaguely back to her house.

I laughed and unbuckled my seatbelt, slipping out of the car and trying to swallow the lump that had formed in my throat when she had mentioned parents.  I surrepititiously checked my hair and shave, straightening my shirt as I walked around the car and followed her up the lawn to the front door where her father was standing.  He was wearing a red hoodie and khakis, and I could tell that he was likely the source for that little bit of weight Kris had on her; he seemed almost larger than life.

``James Careen,'' he offered, sticking out a meaty hand for me to shake.  ``You must be Cory.''

Startled by his solemnity, I shook his hand as firmly as I could manage without shaking, nodding.

Kris reached around me to punch her father in the shoulder, ``Daddy!  Cut it out.''

James Careen bellowed his laughter and reached his free arm around to slap me on the shoulder, pulling me into a very manly sort of hug.  ``Relax, kid, you'll be fine.  Damn, Kris, you picked a nervy one!''

``Don't give that poor boy a heart attack, Jim,'' a bright voice sounded from behind Kris' father.  Opposites apparently do attract, I thought.  Hardly taller than Kris herself, her mother seemed frail enough to be snapped by a slight breeze.  She edged herself between her husband and me and leaned to give me a feather-light hug, smiling widely all the while.  ``I'm Kathy, dear.  Kristal has told us an awful lot about you!''

``Mom,'' Kris whined through clenched teeth, leaning in against me as her mother let me free of the hug, slipping her hand into mine.  ``Making me feel like I'm in high school again.''

``Oh, come on, girl,'' her father rumbled, grinning at the two of us.  ``Now that you've left us, for that flat, wicked place up north, we're allowed to dote at least a little bit.''

I was herded into the house by Kris and her parents and stood just inside the door.  Their house was painted a series of colors, each of which seemed to go with whichever room it belonged to: the dining room was painted a comfortably warm yellow to pick up the sunlight from the south-facing double french doors.  Hard wood flooring extended from the living room to the dining room and, I assumed, down the hallway as well.

``You have a beautiful house,'' I commented to no one in particular.

``Thank you, dear,'' Kris' mom quipped, smiling as Kris set a laundry basket in my hands.  Judging from its weight, it either contained several bowling balls, or else the clothes were packed to be just as dense.

``We gotta get going, I think,'' Kris said.  ``I want to take Cory to Pearl Street before it gets too dark, and we have to head up after that.''

``Sounds like a plan.''  Kris' dad was burdened with another laundry basket that seemed to be filled half with bedding and half with clothes, ``Shall we load up, then?''

Kris nodded and led the parade of her belongings out of the house, burdened only with her backpack.  The two laundry baskets wrangled for space in the trunk of my car, but eventually fit, leaving the passenger footwell for backpack storage.  With the car loaded, we gathered back on the foreshortened front lawn of the ranch house so that Kris could say goodbye to her parents.  Hugs were had and Kris' father clapped me on the back again, saying, ``Tell your boyfriend to relax.''

Kris rolled her eyes, ``I will, dad.''

And with that, we were in the car again, pulling back out into the street and heading toward the road that would take us further into town.

``Sorry about my parents,'' Kris sighed, slouching in the passenger seat. ``They're pretty weird.''

``They were nice, I thought.  Never met anyone's parents before.  When I was in a relationship with them, I mean.''

``Really?'' Kris laughed, pointing out the way towards downtown. ``Why not?  I'm not your first relationship, right?''

I grinned and shook my head, ``No, just that I was always the one with the liberal parents willing to meet a boy's boyfriend.  The two or three boyfriends I had all had parents that weren't too happy about the whole thing.''

Kris nodded a little and picked at her nails distractedly.  ``You'll have to tell me about them sometime.  I'm curious.''

``Uh... well, alright, so long as you tell me about your exes,'' I shot back.

``Ex.  Only one.  Fair enough, though.''  She stared out the window for a few seconds before seeming to perk up, ``It's good to see you again!  Sorry, I was all wrapped up in thinking about parents.''

I laughed and nodded, patting at her thigh with my free hand.

We pulled into a parking space in what seemed to be the middle of a neighborhood, which Kris assured me was close enough to our destination.  Sure enough, a block north of where we parked, we walked out onto a brick-paved lane.  Brownstone style storefronts lined the street as pedestrians, bundled against the chill of November, wandered between planters, each covered with a thin rime of snow.

``It's kind of like Old Town up by campus, except cleaner, and with no cars.''

I nodded and looked around before following Kris as she started to wander along with the pedestrian traffic, ``It's pretty awesome.  There's a place sort of like it up in Steamboat, too.''

Kris bumped against me as she slid her arm through mine, hand holding onto my elbow loosely.  ``Tell me about your break.  We didn't talk enough while you were gone.''

``It really was pretty boring,'' I shrugged, marvelling at the fact that I had never escorted anyone like this before.  ``My step-sister came home and spent most of the break whining.  It was good, though, because it kept my step-dad out of my hair for the most part.  Went on some walks with my mom and her dogs.  Spent a bit of time talking about, you know, us.''

She smiled and gave my arm a squeeze in her hand.  ``Yeah?  How'd everyone take it?  Other than your step-dad, I mean.''

``Well, I think I told you about my mom.  She's happy for us and all, but still thinks that me going for a girl right after moving out is just some sort of reaction thing.  I spent more time trying to convince her that I really do like you than i wanted to.''

Kris nodded and guided me as we walked along Pearl Street, walking us between planters, along storefronts, and around sculptures.  ``And your dad?'' she asked, pulling me toward a shop that seemed to specialize in Tibetan and Indian imports.  There was a dearth of those all over Colorado.

``He was way cool with it, actually.''  I blushed a little as I added, ``He made a bit of a scene about the fact that he might have grand children.  I guess I was going to be the last of the line if I didn't have kids.''

``Weird,'' Kris laughed, shaking her head and pulling me into the shop, making a bee-line for a shelf full of brass and what appeared to be glass bowls.  ``I hope you aren't planning on that yet, sir.  I'd like to go ahead and enjoy life for a few more years before I spoil it with children.''

I grinned and nodded, watching as she picked up a suede-covered mallet and a brass bowl.  She struck the side of the bowl with the suede end of the mallet and got a multi-tone ring out of it before flipping the mallet around and drawing it around the rim of the bowl, always keeping contact with the metal.  After a few turns around the bowl I began to notice that one of the tones produced from the strike wasn't fading like the rest.  Instead, it got louder and louder until a piercing tone was flowing steadily from the bowl.  The tone crescendoed until the bowl was vibrating so much that it caused the handle of the mallet to bounce against the bowl and bring out the other tones.

``Holy crap!'' I exclaimed.  ``That's awesome!  What is that?''

``Singing bowl,'' Kris said proudly, as if she had invented the concept.  She quickly set the bowl back down and moved to stand in front of one of the crystal or class bowls.  These were much larger, probably a foot and a half in diameter and about as tall.

``Whoa, are those singing bowls, too?''

To answer me, she grabbed the mallet with both hands and drew it around the rim of the bowl, using the felt-lined end of it this time.  It took a few seconds, but a low hum rose from the bowl.  The hum grew and grew in volume until I had to step back from the bowl it was so loud.  Kris grinned at me, then adopted a sheepish look, quickly setting the mallet back down on the shelf.  I turned around to find the whole store staring at us.

We left quickly, laughing amongst ourselves.  ``I used to do that every time I came down here, so I had to do it now while I was visiting.''

Slipping my arm around her shoulders, I smiled at the thought of a girl visiting once a month for years, older every time, just to play the little singing bowls.  ``Cute,'' was my verdict.

She elbowed me in the side and grinned up to me.

``Anyway,'' I said, picking at the thread of our previous conversation.  ``Did you tell your parents you're dating a gay guy?''

Walking with me toward the end of the street mall, she nodded.  ``Yeah, they were kind of interested in it.  My dad's a psychologist, and made me promise that I wasn't trying to convert you or anything.  He's not a big fan of the whole ex-gay movement.''

``Well, neither am I.''

``Me either,'' Kris laughed.  ``I told him it was more like you figuring out you were bi instead of just gay.''

``True enough, I suppose.  I mean, I don't really know what it is, why I got in a relationship with you, I just like you.''

``You're a dork,'' Kris explained, and I noticed that it wasn't likely just the cold that was making her ears so red.

``Can't help it, sorry,'' I grinned.  ``What about your mom?''

``She was cool with it, I suppose.  My first relationship didn't end very well, so she's all protective of me.  She was worried, sort of like your mom.  Almost about the same thing, even, that you were just experimenting and would wind up hurting me.''

``Well, that's not, like, my goal or anything.  I--''

``Shh,'' she interrupted, giggling.  ``I know you're not aiming to hurt me.  Mom just wants me to guard myself so I don't get hurt bad if things don't work out.  She also told me not to tell you that, by the way...''

``I understand, I guess.''  I shrugged, ``I don't want to hurt you, and I don't plan on it.  What do you think you'd do if things don't work out, though?''

``Probably feel hurt.  I'd kick you in the shins, too, so that you'd feel hurt, too.''

I laughed, ``Fair enough!  I just don't want it to, like, destroy your life if this relationship ends, though.''

She smirked and leaned in against me, ``That won't happen.  I'm not that fragile.  And even if I was, do you think I'd tell you.''

``Well, I'd hope so.''

She shook her head.  ``No, because then you'd try to stay with me even if you didn't want to, just so you wouldn't do that.  I think that would hurt the most.''

I shook my head and tugged her against me, ``Well, whatever.  Lets talk about something else.''

Kris laughed and stuck her tongue out at me.  ``Come on, lets check out the book store, then we can head back up to school.''
