My alarm startled me from one of those sleeps without dreams that comes with exhaustion and I nearly fell out of my bed.  The narrow twin-size mattress would take some getting used to, to be sure.  I sat up on the edge of my bed blearily and looked out the window across the open field separating the wings of the dorm to the northwest arm of the `H'.

I hadn't set up my coffee maker yet, and finding a place to do so proved to be a challenge.  Eventually, it wound up on the bottom shelf of my desk while my paper wound up under my printer and the binders stacked neatly under the head of my bed.  Liquids above electronics equipment had gotten me in trouble before, and I was nearly paranoid now.

Coffee got me awake enough to make it to the showers with my towel, where I rinsed off quickly, standing on the balls of my feet to avoid as much contact as possible with the distressingly textured floor.  At least they had water pressure to the point where I could barely stand the shower turned on to full blast.  Excellent.

There was a sign taped to the doorway to the stairwell that said we would be meeting at eleven.  ``Good, three hours,'' I mumbled.  Time to eat and maybe go buy books.

The eggs were unimpressive, but plentiful.  I sat with Mark, who was holding his head in both hands over a cup of coffee.

``Rough night?'' I asked, dousing the eggs in pepper.

``Not a morning person,'' he grumbled, sucking down half the cup of coffee at once.  ``And the coffee, it does nothing.''

``Well, yeah, if you can see the bottom of the mug through a full cup of coffee, you know it's going to be worthless.  Brought my own coffee maker.''

``Good man, good man.  Gotta say, if you want coffee, stay away from the dorms, go to one of the bajillion coffee houses out around campus.''

``Yeah?  Any good ones in particular?''

``Any of them are good after a month of drinking this stuff.  Don't get my first paycheck until Friday.'' 

I winced, ``Yeowch.  There much in the way of jobs here on campus, speaking of?''

``Sure,'' he nodded.  ``Check the campus site.  They have some student job listings there.''

Eggs were followed by a bowl of cereal.  So much cereal.  At least breakfasts were looking to be fairly enjoyable.

``Hey, uh, Mark,'' I mumbled, poking at my `Frosted Mini Spooners' with my spoon, the bran pillows only stubbornly soaking up the milk. ``My mom told me to say, er... well, she told me to, well, to come out to you,'' I continued hastily, sure that my face must be past red and well into purple.

Interrupted from his coffee gazing, Mark blinked up at me blearily.  ``Oh.  Okay, cool.''

Anti-climax is the warp and woof of the world, but reactions like this were always a bit of a let down.  The logical side of my brain argued with the illogical side, which was claiming loudly inside my head that this was a Big Deal, don't you know, and that Matthew Shepherd died in a hospital in this town, it's a Big Deal.  ``Think it's gonna be a problem on the hall?'' is what I said instead.

``Nah,''  he shrugged and downed the rest of his coffee.  ``If they do, we can talk.  Talk with the gay office, too, they can help if that happens.''  He heaved himself up from his chair and made his way to get coffee and cereal.  He was wearing rubber ducky print pajama bottoms.

Well, at least that's done, I thought, staring after my stumbling RA.

I finished up my breakfast and left my tray at the window to the dish room before making my way back to my own room to pick up my class schedule.  I wandered over to the student center and found the bookstore on the lower floor.

Music theory one.  New books only, sixty dollars.

Introduction to music history.  A used book, forty-eight dollars.

Analytic trigonometry.  One used book, twenty dollars.

No books for trumpet studio, marching band, or symphonic band.

I wandered to the other side of the shelves to look for the college composition books, gritting my teeth over the price I was paying for my few books.  There was a crowd around the shelf holding the books for CO150, and it took a bit of waiting before I got to the sheet taped over the shelf, listing which sections needed which books.  Great, two more books for that one class.

``This is absurd,'' the girl mumbled to herself, squatting down and peering at the stacks of books I was headed towards myself.

``Pardon,'' I said quietly, kneeling down and juggling the books I was already holding as I reached for one of the books.  She smiled and handed me the other, one of the two used copies left, taking the other for herself.

``Another thirty dollars, here you go,'' she said.

``Really?  Jeeze... this is, like, half of my savings!''

``I know, I should go into text book publishing.''  She smirked and hefted her own stack, looking appraisingly at mine, ``You got a pretty light load, though, looks like.''

Following her over to the zig-zagging line to check out, ``I suppose.  How many classes are you taking that you have eight... ten books?''

``Four,'' she said over her shoulder.  ``I'm an English major.  We're sort of required to read.''

I nodded, feeling my ears redden, ``Oh, yeah...''

When we reached the end of the line, she tilted her head and shifted her weight to one side so as to read the spines of my own books, ``Music major?''

``Yeah, music education.''

``Mm.  I guess they just lump everyone together in composition, I guess.  I thought the entry exam was BS, so I skimped on it.  A basic writing class sounds just as full of BS, though.  Guess I should've tried harder.''

I nodded with as much commiseration as I could muster.  I had done my best on that exam and placed solidly into that middle level class.  ``I'm Cory, by the way, since we're in the same section and all.''

``Kris,'' she replied.  ``I'd shake your hand, but I got an armload of books, so I guess this awkward run-on sentence will have to do for now.''

We chatted our way through the line.  She was the daughter of two engineers and lived in Boulder.  She certainly looked the part.  Two t-shirts --- one brown and one pink --- with band names on them; a tiered, crepe-fabric skirt the color of green tea; and her short, dishwater blonde hair done up in chaotic whorls above her head, doing little to hide the lopsided piercings in her ears: a silver hoop in each, two studs in her left ear and one in her right.  She was fairly attractive, I thought, as much as I could be the judge of that.  Rumpled without being dumpy, stocky, a bit of a tummy without being fat.  It suited her.

We each went our separate ways after paying for our books, waving our goodbyes as I headed back to my room, dwelling on how much money it had cost for my five books.  Hopefully the classes would be worth it.  I hadn't seen the bills my parents had gotten from the university, but from the way they talked, this was quite the undertaking in all aspects.  

Relevant education is expensive, I thought.
