Johansson's hands dwarfed the pint of ale. Once they had managed to find each other in the post-theater rush of the pub, they'd managed to stake out a small two-top table, crammed against one end of the bar itself, leading the larger man to lean slightly to the side away from the noise coming from above it.

He'd hardly touched the beer, but it seemed to take on an almost talismanic significance to him. Carter drank her own cider slowly, careful not to press her luck too hard. Johansson seemed slow to open up.

``Alright, so, RJ.'' It seemed to take no time at all for his impressive vocal cords to unlimber and release what sounded like a well-rehearsed baritone.

``Ey was your sound guy?'' Carter winced at her slip-up, then added, ``Sound tech?''

There was a small smile tickling at the corner of Johansson's mouth, but he nodded and took a large swallow of the thin ale. ``Yep, lead sound tech. Best I've ever worked with, by a long shot. And don't worry, we still fuck up eir pronouns every now and then. I know we did on the night ey\ldots{}the night ey\ldots{}well, early last night.''

Carter nodded, ``And then you tried to pull em back out?''

He nodded and gave a small shrug. ``Nothing. It's like ey was still delved in even after eir contacts had been displaced. We hit the panic button and called the docs. Some ambulance-chaser seems to have caught up with them, which I guess is how you found out about us.''

``Yeah. I'm not really in the habit of checking the tabloids myself, but I'd gone out for lunch with a few coworkers and we got one pushed on us. The bit about you not being able to contact us got my attention, so I figured I'd make for the show tonight.''

``How'd you even manage that, on opening night, anyway?''

Carter laughed and sipped her cider before replying, ``Oh, don't worry, it cost me plenty. Christ, this is so far out of the realm of what I'd do, too. Truth is, I just feel like we're at an impasse.''

``An impasse?'' Johansson asked quietly.

``Yeah. We weren't getting anywhere.'' Carter leaned back in her chair to gather her thoughts once more before leaning over the table again. "I've only ever been on a few projects, I'll be honest, but all the same, this feels like a weird amount of interference. It feels like we're being made to trudge through mud. They won't give us access to the patients? Fine. WFPHIPA is what it is. We just need the data that they collect from them. This has never been a problem on any other project I've worked on.

``All the same, we're stuck with just little tidbits. We'll get a few hours of monitor scans, or a few bits of logs from before the event --- er, that's what we call it, at least --- and that's it. I don't mean to creep on you or anything, but with RJ, we've come across something we hadn't had before. We found out ey was\ldots{}well, you know\ldots{}''

Johansson canted his head to the side, ``Ey was genderqueer? Asexual? A furry?''

Carter laughed. ``A furry, though those other two are certainly interesting data points to keep in mind. We weren't totally sure ey was asexual.''

Johansson laughed in turn and took another swallow of his beer. ``Oh? How did em being a furry help you out at all?''

``Ey's the second furry we've had come across our desks.'' Carter averted her gaze toward her cider, then about the room, ``In fact, it's caused a bit of a schism. Some of us are looking into possible transmission vectors, while others are focused on the cases individually. How could something like getting Lost be transmitted from one person to another? It sounds like something out of an old anime.''

``I assume you're among those who doubt the transmission story?''

``Oh, no, I'm the head of it.'' She grinned wryly, shrugging again, ``But there are still convincing arguments against it. The leader of the opposition, such as it is, Sanders is his name, is dead-set against it. He thinks that we're wasting resources chasing up this transmission tree. We've got an agreement, though.''

``What's that?''

``Well, we'll keep poking at this lead and if it dries up, we'll agree to drop it.''

Johansson harrumphed and nodded, hunching his shoulders. ``Not much of a lead, I'll grant you that, but all the same, anything to try and get RJ back. Ey was more than just a tech, we all liked em. The tech crew, especially. We went through our share of fuck-ups tonight just getting by without em.''

``Oh? I didn't notice any.''

``You weren't on the headset, Carter. We had lights and sound arguing cues while stage desperately tried to keep them on track. It's a total mess.''

``All the same,'' Carter countered. ``I thought it was delightful.''

``Mmm.''

They both stared off into the pub. The room had that distinctly British dichotomy of being crowded and convivial, while also intensely conscious of personal space. The latter suffered as the night went on.

``Tell you what, though,'' Johansson mumbled, the rich baritone bringing Carter's attention back to the conversation.

``Oh?''

``RJ wasn't one for relationships, doubt ey would be, asexual and all, but of all the people ey was close to, it was definitely those furries ey was always hanging around. Come to think of it, I do remember em bringing up the Lost with regards to them.''

``Oh? Huh. It seemed like the to cases we have are certainly socially connected.''

``Yeah.'' Johansson shrugged, ``Not much for relationships romantically, but certainly no shortage of relationships on the friendship level. There was this one girl, Sasha, who ey was close to.''

Carter thumbed her phone on and swiped to a blank notes page.

``She was eir childhood sweetheart,'' Johansson laughed. ``As much of a sweetheart as ey would confess, at least. She knew 'em both. RJ and eir friend who got Lost.''

Carter nodded, jotting down quick notes in shorthand. ``She's still out there, then? Not Lost?''

``I assume so, I guess. You'd know better than I.''

She shook her head, looking down at her phone as she completed the note taking. ``Mmm, no, no female furries. A lot of 'net addicts, and I suppose there's no small crossover, but we're talking way deep. DDR junkies and layabouts.''

Johansson bristled, ``RJ was no layabout.''

She held up her hands and shook her head, ``Mostly, is what I'm saying. They don't have ties, or if they do, they don't hold them. Recently, though, in the case of these last few folks --- the furries --- they have lots of contacts. That's where our two groups disagree most. I think that we're seeing something novel. `I' being the leader of the group that thinks there's a transmission vector.''

``And the others?''

``They see it as chance, as too small an `n' --- too few cases --- to say one way or another. They say that there was bound to be both connected and unconnected folks among the lost. They'd say that it's a matter of chance, that those who use the 'net more would be more likely to wind up Lost, regardless of their social or economic situation.''

``Both make sense, I guess,'' Johansson offered. ``All the same, you know I've got a vested interest in RJ; I'm going to wind up seeing it from your point of view, since you're working with em. Never mind that you invited me out here. What do you need from me?''

Carter thought for a bit, ``I guess I need to know more about em. I have all of eir stats, the dump from eir workstation and the time leading up to it. I'm assuming we're getting all of it, but perhaps that's generous of me. What I need to know is what's slipping through the cracks. I need to know about who RJ was. How ey interacted with the theater, and anything you can tell me about eir friends.''

``Should you\ldots{}?''

``Should I have all of that information? I don't know. Is it against the law for you to tell me? No.~Is it unethical to further my own agenda with this project by consulting you? I don't know; maybe. If I were on a bigger, more mature project, we'd probably be interviewing you anyway. Is it because I think that the more we know, the more likely we are to get RJ and the others back?'' Carter furrowed her brow. ``I'd say yes.''

Johansson looked down into his beer, then, with a decisive motion, drank most of the rest of it in a few smooth gulps, holding up the glass with the last inch or so of amber liquid in it, an obvious toast. ``To RJ, then.''

Carter felt a little silly toasting to someone she'd never met, with a man she'd only just met, with a full glass of cider to his mostly empty ale. All the same, she raised her glass and clinked its rim to Johansson's.

``To RJ.''
