\hypertarget{dr-carter-ramirez-2112}{%
\chapter*{Dr Carter Ramirez — 2112}\label{dr-carter-ramirez-2112}}

Carter could not have explained why she had created the throw-away account to talk with Sasha. Nor could she fully explain the panic that washed over her, strong enough for her to immediately log out and wipe both account and sim.

All she could explain was that Sasha's simple questioning had thrown her estimate of what might be going on within both the dynamic of the team as well as within the 'net as a whole into utter turmoil. The woman\ldots{}skunk\ldots{}skunk-woman had been correct. While there were occasional reports on their findings published to a few reviewers and advisors within the UCL itself, there had been none since RJ had gotten lost. No papers published in any journal, public or private. The phenomenon of the lost was new, and so was the study of them.

So how was it that the grantors were throwing their weight around in terms of the directions her team was taking? How would they know to do so? An informant? A mole?

After logging off, she picked up a sandwich at a nearby M\&S, but could not bring herself to eat more than a few bites of it. When she lay down, sleep would not come easily, and when it did, all it brooked her was the same, stressful dream of shadows.

How does one encompass all of this in one mind? How does one take in the knowledge of being spied upon, of having decisions made — decisions made by the unseen and unknowable — that impact one's life on such a base level and some how make that\ldots{}what? Work? Make it fit? How does one do these things, and still go back to a workaday life?

Work felt impossible. Everyone around her was a suspect. Everyone around her was suspicious in their own way. Everyone around her was someone who was communicating to others, and, without any knowledge of those communications, what guarantee did she have that she was safe?

And was she not communicating with others? She was the one who had contacted Sasha. She was the one who had contacted Johansson. Was she not worthy of suspicion?

The worst was the lack of answers. She could ask all the questions she wanted, and there were no answers to be had.

Finding it impossible to get down to the business of actually working, she paced between rig and coffee station. If, perhaps, there were some way that she could think harder, think better, then perhaps she might be able to fit all of this within her newly updated worldview.

All the coffee did was up her heart rate. It did not wake her any, did not make her more efficient. It simply kicked her anxiety up another activation level.

All her rig had to offer was the work at hand.

She delved in all the same. If nothing else, she could use the dark. She could use the cool \emph{Eigengrau} of her workspace, the order of information neatly delineated by thin cotton twine. Perhaps numbers would sooth her anxious mind.

A soft ping. A notification. A small bell still loud enough to jolt her out of her reverie, or non-reverie, or whatever this caffeine-tinted haze was. Avery would like a meeting.

Carter found it hard to sit still in the small room. It was all she could do to keep from pacing agitatedly, and she focused instead on keeping her steps more on the level of being slow and contemplative. \emph{Is this out of the ordinary? Is me walking back and forth out of the norm enough to report to some higher authority? Is Avery on my side?}

``Dr Ramirez, sorry for bothering you.''

``No problem, Avery. What's up?''

Her subordinate shrugged. ``That's just the thing, I'm not really sure. I started digging into what we were talking about, about how e8 was digging into DDR records before eir disappearance, and on a hunch, I decided to look at all of our other candidate cases. Turns out most of them, even the ones who weren't heavy politics junkies, had a massive uptick in the amount of engagement they showed prior to getting lost.''

Carter frowned. ``Wait, so not just e8? All of them?''

``Well, sort of. Of those who are just the junkies, it's hard to pull apart just how much of their interactions were actually off baseline for them, you know? A set that large, a slight increase might not be that out of the norm. Still, it's there.''

``Do you have a starting point for these increases?''

``Nothing in particular. In absolute terms, no.'' Avery's smile was wry. ``Perhaps obviously. Everyone got lost at different times. Relatively, though, maybe. It looks like everyone who had this uptick had it within seventy-two hours of getting lost.''

``How confident are you in that?''

``Are you asking how strong the correlation is?''

``Sure.'' She hesitated. ``Though I'm also curious about your confidence in this line of reasoning.''

They frowned. ``Well, in terms of the line of reasoning, I'd say that it's strong enough that it's got me actually interested in looking into it. Not that I wasn't interested in these cases before, but this is really intriguing. I like the sort of\ldots{}well, mystery aspect of it.''

Carter laughed. ``Yeah, it does have that going for it, doesn't it?''

Avery nodded. ``And it always did before, too, just that now, I feel like I was handed a big bone in terms of what could actually be going on. It's not an answer, but of all the correlations we've been looking until now, this is one of the bigger ones.''

``That strong of a correlation, then?''

``Well, look.'' They summoned a snatch of workspace, pulled a vcard from one of their decks, and tugged on the corners to expand it to presentation size. A table filled the page, but after a few commands from Avery, it shrunk, slid up to the corner, and in its place, a graph appeared, showing a series of correlation points and a trend line. ``It's fairly strong if we leave everyone in, but if we filter\ldots{}out\ldots{}there. If we filter out the junkies, you can see how high it spikes.''

Leaning in closer to the page, Carter scowled at the graph, then up at the minimized table, and back to the graph. ``That's higher than anything else we've gotten, right?''

Avery nodded, tapped in a few more commands, frowning at some mistakes they made along the way, and then the graph was overlaid against other correlations they had been investigating throughout. ``Just over one standard deviation, yes, though\ldots{}wait.''

Carter had started to nod along with Avery, then frowned at her subordinate's growing confusion. ``What?''

``Do you see that?''

She looked back to the graph. ``See wh--wait, what?!''

``Do you \emph{see} that?'' Avery said, louder. It was as though they themselves needed the convincing, that they needed to have this witnessed right along with them.

And it was worth witnessing. As both of them watched, wide-eyed, the graph shifted. The strength of the correlation started to dip. Not smoothly, but in fits and starts. Avery's hand darted up and, with a fingertip, they dragged the table out to fill more of the card's surface. There, along with the graph, the numbers of the correlation were beginning to change. Row by row, the `interactions DDR by hour 72 lim' column were dropping. They were still high, yes, but perhaps more reasonable. The correlation was still there, but weaker.

``What--''

``Do you have this data backed up anywhere?'' Carter was shouting. Didn't know how to keep from shouting.

``I-- maybe. Sec.'' A few hasty commands, and the data was dumped to another card, the column name changed. The numbers stopped dropping on that card, even as they continued on the first. They handed the card to Carter. ``But what--''

``Pull me back and hit my panic button. Quick!''

Avery stared, open-mouthed.

``\emph{Go!}''

There was the pleasant animation of someone logging out and Avery disappeared.

Carter braced herself, but even so, the jolt of pain running in a sparkling thread down along her spine was stronger than she remembered, and she came up gasping, hands shaking from where Avery held them just above her contacts. With their knee, they hit the panic button on the rig, and the flip-up screen began ticking off cores dumped and suggesting that an official report be filed.

Still shaking, she looked around the office. Everyone was delved in except her, Avery, and Prakash, standing startled by the mini-fridge.

``Everything alright?'' he asked, brow furrowed.

Carter waved her hand dismissively, trying to look calm. She doubted she did. ``Was in a meeting. Crashed or something.''

Avery, perhaps picking up on the anxiety of the last minute, perhaps experiencing their own terror, nodded. ``We were in a meeting, uh\ldots{}trying something. She started\ldots{}'' they trailed off and shrugged.

Prakash nodded. ``Need to file a report? Anything like that?''

Carter stood, wobbled, and regained her balance. ``I will after some water. Getting yanked hurts worse than I remember.''

``I haven't done it since training.''

Avery shrugged. ``I don't think many have. It's not all that common.''

Rinsing her mug free of coffee residue — additional caffeine at the moment being contraindicated — Carter attempted a laugh. ``Right, yeah. I've had sims crash before, but not myself.''

The laugh didn't seem to soothe either of her coworkers.

``Well, either way, I'm kinda shaken up. I think\ldots{}uh,'' she trailed off, looking at her phone. ``Maybe a walk. Yeah, I think maybe a walk.''
