\chapter{Sascha}

``Well if it isn't Skylark, pretty as always.''

The voice from behind the chair Sascha had managed to commandeer in the lobby made them jump, startled at first, then hit with recognition. ``Maverick! Holy hell, I didn't know you were planning on making it down this weekend!''

They jumped up out of the seat, tail smacking against the coffee table nearby.  They remembered to put their purse on the chair to claim it as best as possible, and dashed around to throw their arms around Maverick, who picked them up in a tight squeeze in turn.

``I managed to wrangle some time off. I'm only down here through Sunday at stupid-o'clock in the morning, but hey, at least I made it.''

Sascha settled down once Maverick let them go and straightened their skirt out, nodding. ``Well, still, glad you could. It's been forever since I've seen you. Haven't caught up with any of the rest of the crew, I figure I'm probably here a little earlier than most.''

``Oh, well, I'm here, and I know Volare's around somewhere, I ran into him at the bar, naturally.''

``Of course, I'd expect nothing less.''

Maverick laughed, straightening his badges and lifting Sascha's purse from the chair before plopping down into it, ``I'm sure the bar's gonna make plenty good money this weekend.''

Sascha snagged their bag from their friend. Online, Maverick was a rather glowy cheetah whom they'd known for years, and met several times in person at local meets. They settled for sitting down on the arm of the overstuffed chair, leaning against Maverick and draping their stuffed tail across his lap. The two caught up on recent happenings -- who was quitting furry forever, what art had caused a big stir among their group of friends, what they had been saving up to buy in the dealer's den this year.

It was Maverick who finally broached the subject of Shadow.

``So when does your\ldots{}uh\ldots{}guy friend get here? You've been looking left and right since I spotted you.''

``Not until later tonight,'' Sascha sighed. ``I'm just so nervous, I can't stop thinking maybe he'll somehow magically get here early.''

``Excited, huh?''

``I'm not even sure it's that, really. Just nervous.''

Maverick furrowed his brow. ``What, do you think it won't go well or something?''

Sascha buried their face in their hands and trailed their fingers up through their hair, freshly dyed a subdued red just for the occasion, mumbling behind their forearms, ``Yes. Well, no. I mean\ldots{}I guess I don't really know. I haven't been this close to someone since Mike, so it just feels so weird. I don't know what to do about it.''

Maverick nodded and brought a hand up to rub up over Sascha's back, tracing along their spine soothingly. ``You'll do fine, minkypie, and you know you've got a bunch of us here to take care of you if things don't go well. They will, though, trust me. Shadow's a little plain, given the rest of us, but he's good people.''

``Oh, come on, he's not that plain. You just say that because your spots glow blue and Volare's bright pink. By your standards, I'm plain.''

``That you are, girlie.''

Sascha groaned and draped herself dramatically across Maverick's lap, ``Girlie, huh? I haven't been called that since\ldots{}well, ever. Congrats on being the first.''

``Skylark the delicate minkygirl, plain as day, swooning wildly into the muscle-bound arms of her manly wolf lover.''

Sascha's groan turned into giggles, muffled by their hands as they hid their face. ``Seriously? I should hit you for that. And lay off the `girlie' and `her' nonsense.''

``Oh? Feeling more boyish of late?'' Maverick asked, still grinning.

Sascha sat back up on the arm of the chair, twisting around to settle more comfortably against their friend as they toyed with the fluff at the tip of their tail, ``A little, I guess. Maybe it's the possibility of meeting up with Shadow, though. I don't want to come across as\ldots{}as\ldots{}I don't know, disingenuous.''

``Hey now, I've heard you talk about gender enough to know that you're hardly disingenuous about it. You talk convincingly enough to get me doubting my own gender, for Christ's sake. Shadow really has you feeling more like a boy?''

``Um, there's just\ldots{}it's just\ldots{}there's more to it than that, I guess. I've been honest with him and all, but he's so much more, well, active than I am. I don't want to surprise him or anything.''

``Because you interact with him mostly as a girl online?''

``Yeah and\ldots{}'' Sascha stammered for a bit, hunting for the best way to convey the way they'd been feeling. ``And I just don't want him to think I'm dishonest or anything.''

``Hey mink,'' Maverick said soothingly, ``I don't think you're being dishonest, and I don't think Shadow will think you're being dishonest, either. If you've talked about gender already, then I don't think there's anything you need to worry about. Heck, you're wearing a skirt and have your hair done up all nicely, you're certainly not looking boyish.''

Sascha couldn't think of much to add, nodding and murmuring a quiet ``thanks'' in reply.

The two sat for a little longer, watching the congoers and confused non-attendees streaming past the lobby chairs in various amounts of costume.

It was Maverick's phone buzzing that brought their attention back to the moment.

``Oh, hey, Volare found Vish, and they're at the bar, want to go meet up with them?''

Sascha gave one last look around searching for the buzz-cut that they knew they would spot first, that first sign of Shadow, then finally nodded, ``Sure, I could use a drink, anyway.''

\secdiv

The initial meeting between Skylark and Shadow was widely panned by critics as a romance, though some praised its comedic aspects.

By nine that night, Sascha was still in the bar, nursing their second Manhattan and making sure that Volare stayed on his stool more often than not. Maverick had gone off to the restroom something like fifteen minutes ago, and Vish, a non-drinker, was looking more than a little hemmed in. Everything was that delightfully confused mix-up of a convention, and everyone was settling into it in their own way.

``Your hair is\ldots{}redder than I was expecting.''

Sascha whirled. The voice was undoubtedly Shadow's -- Peter's -- recognizable from the phone.  And sure enough, the buzz-cut towering nearly a foot over their own head had them immediately feeling dwarfed. The second thing to catch Sascha's attention was the crash and tinkle of not one, but two glasses as the back of their stool knocked into the bar table and tipped both Volare's and Vish's drinks.

Rather than rushing to hug their partner as they had immagined, Sascha was overcome by an intense feeling of self-consciousness and guilt at what they'd done. They quickly helped pick up pieces of glass and ice, mopping up spilled beer and soda while muttering hasty apologies to their friends. In the process, they managed to cut open a finger on a piece of glass, adding to the confusion.

``Whoa, whoa! Slow down. Skylark!''

By the time Peter had gained their attention, Sascha was fighting to hold back tears and refusing to meet anyone's gaze, never mind that of their boyfriend.

The waitress rushed over to the table with a rag and a bandage for Sascha, and was helping to clean up the sticky mess. She commented on how lucky everyone was to have been spared the deluge for the most part -- Volare and Vish both had only a few scattered droplets on their shirts, the rest of the beer-soda flood having made its way onto the floor.

Sascha managed to pry their eyes from the mess and look sheepishly up to Peter, who simply held his arms out. No leaping to the offer of a hug, nor collapsing, weeping, into his arms. Instead, they hesitated for a few seconds -- long enough for the entire table to go silent -- before slowly leaning into the offered embrace, covering their face with their hands and crying as quietly as possible as Peter held them.

``I'm sorry, that was\ldots{}that didn't go as planned,'' Sascha said, once they were sure their voice wouldn't crack.

``Hey, hey. It's okay. I'll just take it as you were really happy to see me. Everything's okay.''

``Sorry, I'm just a little anxious, awkward\ldots{}''

Peter leaned down and placed a tentative kiss to the top of Sascha's head, cooing gently, ``It's okay, I promise. Come on, let's sit back down, and we can grab a drink and relax and catch up. You look really good, by the way.''

Sascha felt a good portion of their tension melt away at the relaxing murmuring of their partner, enough that they could disentangle their own arms enough to slip around Peter's stocky middle and finally return the hug, taking comfort in the fact that he practically enveloped their smaller frame.

Eventually, Sascha let go and dried their eyes, tugging another stool over for Peter and introducing him to the crowd, most of whom he'd known online for the last few months of hanging out with his partner, and a few of whom he was just meeting for the first time. Peter made his dramatic arrival up to everyone by covering a replacement beer and soda for Volare and Vish, another Manhattan for Sascha, and a beer for himself.

``So,'' said Volare, sitting up as straight as he could, a sure sign of his drunkenness. ``You're the Shadow that we've been hearing so much about! You and Skylark make a really cute couple.''

While Sascha hid their face behind their drink, Peter grinned widely and nodded, ``It's been an interesting few months for me -- for both of us, I think. I don't think Sky was really looking for much in the way of a relationship, and I wasn't really looking for someone like him.'' Realizing his mistake quickly, he rushed to add, ``Er, them. I'm sorry, Sky\ldots{}''

Sascha hunched their shoulders in an attempt to get even smaller, feeling the attention shift from Peter to themself. ``It's\ldots{}it's okay. I appreciate the correction.''

Vish and Volare let their gaze linger on the couple, one smiling and the other looking nervous.

``Anyway,'' Peter continued, hoarsely. ``I think it's worked out well, there should be plenty to do this weekend, anyway.''

Feeling their courage return after having tripped over themself so much early on, Sascha nodded. ``That's why cons are so awesome. We can all hang out together, and we automatically have stuff to do.''

Maverick finally made his way back to the table, having been gone for nearly half-an-hour on some minor adventure. Introductions were made and the conversation began to wind comfortably around the group, settling into rhythms at once familiar from all the time they'd spent together online, and foreign in this strange and new setting. A hotel, Sascha decided, was not the most comfortable of places, but the convention was a sort of force working actively against that, bringing comfort to a comfortless place.
