\chapter{Ian}

The couple managed to make it all the way to the hotel without stopping, despite the rising panic on Ian's part, checking his pockets repeatedly to make sure that he hadn't misplaced his phone, wallet, or keys -- the all-important keys with their little vial of emergency pills. No matter how thoroughly he convinced himself that he had everything that he needed, the results would slowly fade into is-it-a-dream-land, and he'd begin questioning his judgement again.

He kept his mouth shut, though, and mostly just clutched at Andrew's hand, letting himself be led to the shuttle, to the hotel, to the front desk, to their room, before finally letting his guard down.

``Hey,'' Andrew said quietly, resting his hands on Ian's slumped shoulders and guiding him into a hug. ``We made it. We don't have to do anything else tonight, except maybe get that drink. That sound good?''

Ian leaned tiredly into the hug, slipping his arms around his boyfriend's waist and holding himself close for a moment, just nodding.

``Need a shower or anything?'' Ian asked after a moment.

Andrew shook his head.

Ian nodded and pulled out his phone, quelling the feeling of being sweaty, being caked with sweat, being coated with grime, dirt and grease, grease so thick it showed through his clothes, enveloped them, darkened and then made them translucent, coating him in-

``Ready hon?''

Ian nodded, relaxing his grip on his phone long enough to text Rei to tell him where they would be before stuffing the phone into his pocket. ``Yep, let's go,'' he chirped, striding to the door before another cycle had the chance to start up.

They made their way down the hallway to the stairs, thankful for the low floor as the elevators were already starting to back up with fur-clad congoers. Elevators were usually okay for Ian, except late at night, and except for glass elevators. Since there would doubtless be late nights at the con and since this hotel had glass-walled elevators overlooking an atrium, they'd specifically requested a lower floor when booking, and had been pleasantly surprised by a room on the second floor.

As they trooped tiredly down the stairs, Ian thought for a moment before pulling out his keys and unscrewing the vial containing his medications.

``Think you'll need that?'' Andrew asked.

``Think I already do.''

Andrew nodded a little and continued on to the landing before pausing to let Ian catch up.

He carefully split one of the small tablets in half and placed one of the halves beneath his tongue, the learned reaction to the taste bringing an almost immediate sense of calm, however superficial.

``Gonna be okay taking that with a drink?''

``I should be, yeah,'' Ian responded. ``If anything, it'll just make me sleepy, and sleepy is an okay way to be.''

Andrew brushed his hand down over Ian's back and nodded, ``Well, just keep an eye on yourself. Yap if you need anything.''

``Yap!'' Ian grinned.  ``Like that?''

He followed Andrew down the rest of the steps, yapping as he planted his foot on each one. The meds hadn't even started to kick in yet, but he knew they would, and knowing that was enough to lift his spirits to the point where he was actually looking forward to the bar, to seeing Rei.

Rei was shockingly easy to spot at the bar. He wasn't remarkable in his build, but having bleach-blond hair made him stick out in a sea of dark.

``There he is. There he is!'' Ian exclaimed and bounded ahead of Andrew. He took the steps up to the bar -- a group of two and a group of three separated by a small landing (five was a perfectly acceptable number) -- and called out, ``Rei!''

The man with the blond hair shot upright and pocketed his phone quickly. ``Ast! Is that you?'' he asked, meeting Ian -- or Ast, as he knew him -- in a quick, firm hug. ``Jeez, it's good to see you!''

The two regrouped into a more comfortable, less hasty hug, leaning in against each other and simply spending a moment holding tight. The sound of a shutter clicking brought Ian back to attention and he turned his head quickly to see Andrew grinning from behind his phone, holding it up to take another picture.

``H-hey!'' Ian stammered.

Rei laughed and grinned, ``You must be Andrew. Gonna have to send me those pictures.''

Ian felt himself flush, biting back a stinging retort and simply tucking his head back over Rei's shoulder, thankful that they were about the same height. He focused instead on counting. He didn't need a hundred, but he made sure to hold the hug until fifteen. Three and five were particularly auspicious.

Slipping away from Rei, Ian gestured to Andrew, ``Um, let me formally introduce you two. Andrew, Rei. Rei, this is Andrew.''

They shook hands, then seemed to think better of it and hugged before settling into stools around the bar table, Andrew picking up where Ian left off. ``Ast's told me a lot about you, too. Good to finally put a face behind the name.  And hey, I like your hair.''

``Hah, thanks. Yeah, it feels like I already kind of know you.'' Rei said, rubbing at the back of his neck.  ``I uh\ldots{}I hope it isn't too weird meeting up with your boyfriend's partner. I don't want to\ldots{}like, impose or anything.''

Andrew shook his head and put his hands up disarmingly. ``No, trust me, it's fine. We've had this talk so many times just between the two of us, it's good to put it into practice.''

The tinkling of glasses breaking behind the group drew their attention, and they turned to see a young woman in paws and a tail rush to clean up a small flood of drink from the table. Ian saw her cut herself on a piece of broken glass, feeling the glass slice into his own flesh within his mind, and winced, swiveling back to face his own table, clasping his hands together in front of himself to keep himself from forcing both Andrew and Rei to turn away, second-hand embarrassment running deep.

Ian had realized how close he was to panicking and had taken the brief, calm interaction between his two partners to clutch at the edge of the table for dear life and work on calming himself. Breathe, slow, calm, chill, breathe. Simple one-syllable words said in order to restore a sense of balance within himself. Finally, he stood, paced in a quick circle behind his chair and shook his hands to dry the sweat from his palms, before settling back onto the stool and grinning sheepishly at Andrew and Rei.

``Sorry,'' he said breathlessly. ``I'm really excited. Um\ldots{}hi!''

Rei looked a touch taken aback, but Andrew laughed. ``Long flight, we're both a little on edge. Seen the waitress around here? I think a drink might do all of us good.''

Rei smiled warily, but nodded to someone behind Andrew, catching the eye of the server.

``Help you gents?'' the man asked, whisking a cocktail napkin down in front of each of them with practiced ease.

``What beers do you have?'' Andrew asked.

The server rattled off a list. The only one that seemed to ring a bell outside of the standard macrobrews was some craft beer, so Andrew ordered that.

Ian tore his gaze off of the table and managed to order a rum and coke. He focused on not fiddling with his napkin too much as Rei ordered a mojito.

Once the server went back over to his station to put in the order, Ian rested a hand on both Andrew's and Rei's knees. Forcing himself into a calmer composure, he smiled between the two of them, ``Really glad we could make it, and really good to finally see you, Rei.''

Andrew simply smiled back, but Rei leaned in to kiss Ian on the cheek, ``You okay there, fox? You seem pretty on edge. Rough flight?''

Ian swallowed hard and quelled the sense of unbalance of only being kissed on one cheek. He focused on the swelling warmth inside his chest, the first sign that the anxiolytics were kicking in. ``Uh, well, yeah. I'm just really anxious. Like, most of the time. I'm sorry, it sometimes comes out in strange ways.''

Rei reached a hand over and brushed it down Ian's back before resting it on the chair behind him, ``No, it's okay! I just wasn't sure what was up, is all.''

``I type better than I talk,'' Ian admitted. ``And I talk better if I'm pacing.''

Andrew leaned over and knowingly placed a kiss on Ian's other cheek, helping to restore balance, ``Hey, don't worry about it, hon. We're all just animals here, no need to worry about how you talk.''

Ian was sure that he was blushing red. Bright red, cherry red, fire-engine red, beet red, turning purple, lips blueing, struggling for air, hypoxic. No, none of those. Just blushing, he smiled and gave the knee under each of his hands a gentle squeeze, murmuring, ``Just really glad.''

Once the drinks arrived, Ian felt that he could relax. The warmth within his chest swelled slowly and was augmented by the addition of the rum in his drink. Conversation eased for him, and he felt himself opening up both to Rei and Andrew. His two lovers shared an occupation as software developers and had plenty to talk about when Ian's stories of online goings-on flagged. He felt comfortable sitting between them, watching someone dressed as a cat flirt with someone who was dressed for something other than the convention, who may not actually have been a part of the convention, but was willing to humor the cat.

Balance became less of a pressing concern as the meds took firmer hold, but even so, as Andrew and Rei chatted about computers, Ian revelled in the feeling of love flowing out from himself and into himself evenly from both sides.
