\chapter{Michael}

Michael felt the warmth of the rum-and-cokes he'd had up in the room starting to fill him by the time afternoon slid into evening and he made his way down to the bar. There was something cathartic, in a way, drinking to old memories.  It didn't necessarily resolve anything, but the alcohol could let you pretend that it had.  At least now he felt more able to take in the fact that he would be, in a way, sharing this convention with Glade.  After all, not all of the memories were unpleasant.

The elevators ejected him into a lobby more packed with people than it had been before, filled with hundreds of missed connections.  He made his way languidly through the crowd, scanning faces, scanning badges, handing out smiles.  It felt good.

``Oh hey, it's you guys!''

The lion and the Shy Blue Fox looked up from where they were trying to share a seat in one of the lobby's chairs, one earbud in each of their ears leading to a phone held by the Shy Blue Fox.  They looked up to him slowly, smiled with recognition and reached hands out to grab him in for an awkward hug.  Not sober, but maybe not necessarily drunk, the two seemed more alive and active than they had earlier in the day.

The three of them decided on the hotel restaurant as a good source of dinner.  Expensive, but fitting for three innebriated furries to chill and at least get food in the system before the evening's dances began.  They settled into a booth and ordered a round of drinks, beers and a gin and tonic.

``So,'' Michael began, putting what he had hoped was a conspiratorial tone in his voice.  ``Good day for you two?''

The Shy Blue Fox buried his face in his hands and giggled, while the lion looked serene.  ``Mmm, yeah, very good.  Bit of molly, lots and lots and lots of hugs.''

Michael laughed out loud.  Colorado wasn't exactly the heart of Ecstacy, but it showed up every now and then.  More common now was marijuana -- legalization had played a roll in a good number of the attendees showing up here, he was sure.

``Good, glad you guys are having a good time.''

The lion looked almost beatific as the Shy Blue Fox rubbed himself almost sinuously up against him, reveling in the touch.

``How about you, man?'' the lion asked.  ``Been a good con so far?''

Michael nodded distractedly and sipped at his water, ``Good enough, yeah.''

``Saw your\ldots{}your ex?  Saw your ex showed up, earlier.''

``Yeah, I was surprised to see\ldots{}them here.  I wasn't expecting that.''

The lion cocked his head, ``Been a long time?''

``Yeah, definitely.  Five years or so.''

``Not a pleasant break up?''

``Yeah she\ldots{}she at the time, broke my nose and we vowed to never see one another again.''

``But you hugged-'' the Shy Blue Fox began.

Michael brushed it off with a wave of his hand.  ``Yeah.  There's a lot there,'' he stammered, searching for the words.  ``Plenty of good memories, along with the bad.  It's good to see her.  Him.  It's good to see him.''

Ecstasy, in his own experience, added quite a bit to the level of empathy one normally had, and often led to picking up on cues that were embedded in day to day speech, bits of meaning that exposed more despite all attempts to hide.  It was no different with these two.

``He's not what you were expecting.  Quite the change, huh?''

Michael felt his face flush, and looked down toward the table, nodding.

There was a silence that stretched until their drinks arrived, thankfully not too long.

Finally, the Shy Blue Fox asked, ``Do you think you'll see him again, during the con?  Like\ldots{}actively?''

Michael hid his face in his beer, sipping slowly to buy himself time.  ``Maybe.''  He set his beer down and twisted the glass between his fingers.  ``Maybe.''
