\chapter{Ian}

Saturday morning started out slowly. Andrew and Ian had spent the hour or so after Ian's shower talking about the night past and hadn't gotten to sleep until late. By the time they made it out of bed, Andrew needed a shower, and Ian felt as though he did too, so they wound up showering together. That ate another hour of time, though Ian felt it was time well spent.

They didn't even really make it out of their room until late in the morning, partly because Andrew kept teasing Ian about the night before, brushing fingertips down over his front right where he'd smeared that slick mess the night before and making Ian squirm at the touch.

This playful attitude kept up all the way down the stairs and out of the hotel before Ian remembered about Rei. There hadn't been any plans around breakfast, though, and he sheepishly left his phone in his pocket. They had all weekend to spend together, and doing something as simple as going and getting coffee with Andrew shouldn't be that big of a deal.

They strolled leisurely through the crowds of begoggled and betailed folks in the lobby, making their way out through the doors and down the street to the coffee shop, also visibly filled with the furry crowd. They could spy no less than three tails in the line of five waiting for drinks, and several others who might be congoers as well throughout the seating area.

The settled in a corner table next to a window, Ian keeping his back to the wall so that he could see both out the window and into the room.

``I know I got a little wound up last night, but how was your evening?'' Andrew asked, splitting his breakfast burrito in half to let it cool.

Ian blushed and polished his silverware on his napkin, ``Not much more than I said, really. Got all cuddly, kissed a little, talked about you and I. It was a good evening.''

Andrew laughed and forked bite of burrito into his mouth, nodding and chewing, huffing slightly to cool the bite. ``That's good, though. I'm really happy for you,'' he said, once he could speak again.

Focusing on cutting his burrito into sixteen bite-sized pieces (four was important, but square numbers more so), Ian nodded and took the time to formulate a response. ``Yeah. I mean, I feel good about the way things went\ldots{}er, are going well. I feel really safe with you, and I think I'm learning to feel that way with Rei as well.''

Ian tried not to notice as Andrew haphazardly cut off another bite of burrito, ``Can you unpack that a little?'' he asked. ``I mean, I'm glad you feel safe and all, but I\ldots{}well, I guess I want to make sure you keep feeling that way.''

Ian shrugged and nodded, taking the first bite of his burrito and chewing thoughtfully, counting as he went. ``I guess, like, it's a two way thing. I feel like I can be myself around you and you accept and work with that, and vice versa. We each have our idiosyncrasies and the other knows how to make\ldots{}that\ldots{}work. Sorry.''

``For what?''

``I ran out of words.'' Ian frowned, fumbling over his own thoughts for a moment. ``We work with each other, rather than against each other. We don't focus on the thing the other might like, we focus on just being happy, and it works out. I don't honestly know if Rei and I are there yet, but I want to see if we can be,''

Andrew nodded thoughtfully as he chewed on his burrito, washing it down with a coffee drink as he stared out the window. ``I think I get it, yeah. It's safe because it doesn't have much friction, and you're finding the way to um\ldots{}.interact with Rei, cold as it sounds, without that friction?''

Ian nodded and worked his way through the first half of his burrito before polishing off a quarter of his coffee. He thought for a moment before adding, ``I wish he were here. Rei, I mean. I wish we could all have this conversation together.''

``Why didn't you invite him?'' Andrew asked, concerned. ``He's more than welcome, you know that.''

Ian flushed, then rubbed his hands over his cheeks, then his eyes. ``I thought about it, I just didn't know if he was awake.'' The excuse sounded lame, even to his own ears.

``I think it's good stuff, though, have you talked about this with him?''

Ian shook his head and focused on finishing his own burrito in eight smooth motions.

\secdiv

\begin{quotation}
  Rei: Hey, what's up foxy?

  Ast: Hi weasel. Sorry I was out most of the morning. At the dealer's den, wanna join?

  Rei: In friend's panels. Join later? Dinner?

  Ast: Erf, forgot about panels, sorry. Dinner sounds good. Hotel or out?
\end{quotation}

The lack of reply vexed Ian as he made his way through the Dealer's Den, mentally noting the artists he liked and their positions within the ballroom, planning a future route. He did want to keep up with Rei, this was their time together, but he felt unable to assert himself even enough to ask which panels he was in. He could guess, maybe, by looking at the schedule, but the thought of showing up unannounced presented itself as a jagged corner of anxiety in an otherwise smooth mood.

These corners had been getting out of control, today. It was like some square -- or no, some pointed star rotating within him with the points of the corners catching on his soul as though at the hem of a fraying cloth, tugging and pulling at loose threads as he wound his way through the crowds. There wasn't any way for him to keep moving without invoking some ritual or another, whether it was counting to some unattainable number or holding still long enough for his subconscious to catch up.

Ian loathed the fact that there was some sort of medication he needed in order to function within the world around him, and he avoided it at all costs. Cons, or any open, public space, however, seemed to demand such things of him, and there was little he could do to escape it.

``I won't need it,'' he sub-vocalized. ``I can take it later when I can lay down. I won't need it. I can make it through this.''

The affirmations had little impact on the part of his brain that kept repeating, ``You're visible, you're known, they know you, they can see you, they know how guilty you are, they know what you've done to Rei, how you've betrayed Andrew, they've seen the filth, they know, you're visible\ldots{}''

He shook his head, trying to clear his mind.  It was just the inner critic, he thought, shouting down all the other parts of his personality.  He just needed to calm that part of himself, bring the meeting back to order.

Ian found himself standing outside the dealer's den, facing out the windows of the hallway with his hands over his ears.

``I gotta stop,'' he told the glass. ``It needs to stop. I need to stop it.''

How he found himself by the elevators, or why, he never knew. Ditto the trip up to the second floor: there was simply no memory of what had happened, beyond the feeling of hands on his shoulders, guiding him out of the tiny box into an empty hallway, limitless placards, hungry doorways.

His mind was filled with numbers.  One, two three, four, five six, six\ldots{}did he get three already?  One, two\ldots{}

``Two\ldots{}one eight,'' he repeated to himself. ``Two\ldots{}two nines\ldots{}two one eight.''

The simple math problem calmed him enough to allow him to recognize the placards next to each door before him, and he found himself counting up by twos until he reached the door that proclaimed itself. Two. One. Eight.

Retrieving his wallet was easy, but managing to get the key-card into the slot required to open the door less so. He found himself confronted with a monumental task, weighted down with years of emotion, the actions of his own history, and the incredible importance of what it would mean if he were to open the door.  Would they all come tumbling out?  It wouldn't mean anything to open the door.  It would mean everything if he opened the door.

``Open it,'' he mumbled, pressing his forehead to the door, eyes angled sharply down to the lock. ``Open it.''

He slipped the card in. The simple electronic shuffle of the lock cycling was almost a let down. Rei? No. Andrew?

Ian collapsed into the room, the door having provided less resistance than he was expecting. As the door clicked shut, he found himself on all fours, then knees and elbows in front of it. Two. Two nines. Two one eight. Two three four, one two, two times four. Two one eight.

Bed?

The thought was distant, but it seemed to resonate with his elbows and knees. Something something lay down something. The words didn't really line up in his head. Andrew. Rei. The things that made him feel safe. If he could only lay down with Andrew and Rei\ldots{}
