\chapter{Sascha}

``I feel like I've let you down,'' Sascha said quietly. ``I feel like I've lied to you.''

Peter stomped up the stairs, two steps ahead of them. ``Tell me about it.''

Sascha followed on in silence up the next flight and out the door by the ice machine, making their way after Peter down the hallway to their room. They unlocked the door and entered in silence, Sascha sitting carefully on the bed and Peter falling gracelessly into the desk chair. Silence, thick and tangible, hung between them.

``I feel like we had a really good night last night,'' Sascha offered, after a minute or two. ``I feel like we connected in a really important way-''

Peter cut them off, ``I feel like I was imagining you as my little girl, like you were the person I've been imagining the whole time these last six months.''

Sascha fell quiet again. They stood, paced to the end of the bed, paced back, sat again, and stood once more. Finally, they buried their face in their hands and mumbled, ``I'm sorry. I'm not trying to\ldots{}you know, be difficult. I want to be that person for you, I just\ldots{}there's just so only so much I can do.''

``You could've not been\ldots{}'' Peter started. ``You could've acted like what I should have expected from the start. You're not really what I expected at all.''

Sascha clenched their fists and stuffed them into the pockets of their hoodie, ``I want to be something good for you, that's all I've ever wanted to be. I don't know how to be anything else.''

Peter looked away in silence.

Sascha lowered their head, closed their eyes, and resumed their pacing circuit. They didn't look at Peter, they didn't look at the ground, they simply paced and did their best to cut out all input. Anxiety welled in their chest like some awful, noxious bubble aiming to burst in the form of some horrible meltdown. They focused on breathing. Count of four in, hold for a count of five, count of seven out. Anything to calm the situation, even if only internally.

``Here, I'll tell you what you can do, sweets,'' Peter slurred, sounding half angry, half something else.

Looking up, Sascha found that Peter had unzipped his fly and tugged his boxers down, and was aiming his erection in their direction. ``Even boyminks got warm muzzles, hmm?''

Sascha was shocked. Their head was spinning, and they couldn't tell if it was from the alcohol or the proposition.

``Well, c'mon, you were eager enough last night, though you must've had some rockin' panties on, didn't feel a thing,'' Peter sneered.

``You want me to give you a blow job,'' Sascha asked incredulously. ``But you just said I wasn't what you expected.''

``Come on. Bygones and all that crap. Take care of me and I'll forget about all this gender shit. I came here thinking we'd have a good time together, so let's have a good time.''

The combination of vague threats and an act that Sascha had rehearsed in their mind over these past few months countless times -- had acted out through role-play online with Peter more than once -- was too much for them to handle. Their mouth went dry, they couldn't swallow, the room seemed closer and closer.

``Fuck it,'' they whispered. ``Fuck you, if you think sex'll clear this mess up.''

And they stepped out the door.

\secdiv

Sascha made it to the stairwell before the tears hit, and when they did hit, they hit silently and with no force, simply spilling down over their cheeks and into the waiting sleeve at the crook of their elbow. Growing up a boy, taught to be a man, had left them much that needed to be unlearned, but the secret of crying quietly when one was supposed to be strong felt like an inheritance of sorts.

Their phone buzzed. Twitter.

\begin{quotation}
  fine

  Direct message from @ShdwWolf
\end{quotation}

The tears came harder.

\secdiv

\begin{quotation}
  SkylarkMink: you awake?

  Mavcheets: Just getting ready.  What's up.  You okay?

  SkylarkMink: no.

  SkylarkMink: can i come by

  Mavcheets: Sure, just be quiet. V and V are asleep, was packing
\end{quotation}

\secdiv

\begin{quotation}
  Sky I'm sorry, drank too much :(

  Direct message from @ShdwWolf
\end{quotation}

\secdiv

\begin{quotation}
  Sky, take your time, but please come back :(

  Direct message from @ShdwWolf
\end{quotation}

\secdiv

\begin{quotation}
  Mav sent me a dm, can we talk

  Direct message from @ShdwWolf
\end{quotation}

\secdiv

\begin{quotation}
  Mav says your okay and sleeping there, talk tomorrow pls? :(

  Direct message from @ShdwWolf
\end{quotation}
