\chapter{Sascha}

Sascha awoke neatly wrapped in Maverick's -- they still didn't know his real name -- arms when their friend's alarm went off. Maverick was well attuned to his alarm and reached across Sascha to turn it off with ease before returning to the hug that had apparently lasted all night, burying his face against the back of Sascha's neck.

They had fallen asleep with their clothes on, for lack of any pajamas. The night had drawn out for another hour or so of whispered conversation in bed, keeping quiet lest they way Volare and Vish. Sascha had fallen asleep dressed and crying, but safe against their friend, feeling his bulk behind them as something of comfort rather than as a source of anxiety.

Maverick had done admirably. He'd asked if everything was okay several times, and gotten the full story of what had happened after Sascha and Peter had left. He didn't pass any judgements on either of them, and had let Sascha talk until they had started to doze.

Even so, Sascha wasn't sure what to make of the remainder of the evening. Everything felt so safe with Maverick and so\ldots{}well, cold with Peter. They were hesitant as always to draw conclusions on that -- just because a friend was nice to them when something had gone wrong didn't mean that\ldots{}well, it meant that he was a good friend. To be honest, their first instinct had been to take Mike up on his offer to call whenever, but it had been so late, and only a little bit since they had left Maverick's room in the first place with alcohol buzzing through them. Nothing to feel sorry about.

Except Peter.

Maverick grunted and leaned up on an elbow in bed behind them, then leaned forward to give a friendly kiss to their cheek. ``Hey, morning. I gotta start getting ready, but you sleep in, okay? I'll send V and V a note explaining that you needed a place to stay for the night and took my bed.''

Sascha curled themself a little tighter in bed and nodded silently.

``You keep in touch, okay hon?'' he murmured, giving one last gentle squeeze. ``And be safe, minkypie. Things got rough, but you've got friends here.''

``Thank you,'' whispered Sascha, clutching briefly at Maverick's hand before letting him get up and get ready to drive.
