\chapter{Ian}

Ian woke later that evening to find himself laying down between two sets of hips, the thicker of the two he recognized almost immediately as Andrew's, and on further investigation, he realized Rei was on the other side of him. The TV was playing softly in the background.

``Hey, um,'' he mumbled, licking his lips to clear the dry mouth that seemed to occupy all of his attention. ``Hi.''

Both Rei and Andrew smiled down to Ian, and he basked briefly in the glow of their attention.

``Hey,'' Andrew said. ``We got pizza. Just pepperoni. Want some?''

Sitting up in bed made Ian feel the cottony softness that the medications brought to him still filling his mind. He nodded sleepily and accepted a paper plate with a slice of admittedly pretty good-looking pizza from Andrew. He leaned first to the right to kiss his boyfriend on the cheek, then to the left to kiss Rei in the same spot on the other cheek, ``Thanks. Um, sorry about all that.''

``It's fine!'' Andrew promised.

``And sorry I didn't get to see you much until tonight, Rei,'' Ian offered. ``I kinda panicked.''

Rei grinned and hugged his arm around Ian's shoulders, ``It's okay, really. We've got tonight and the rest of this weekend.''

Ian relaxed into his partner's side and focused on eating. Pizza was less than ideal, but it sated the hunger that had cropped up as he slept, though sleep wasn't quite the right word for the fugue of deep anxiety.  It was tasty, but simply difficult to decide how best to eat it. He could make it about halfway through with single, even bites, but then had to proceed boustrophedon along the thicker portion of the slice until he got to the crust, which he could break up into four pieces and eat one at a time.

Knowing that he wasn't up for leaving the room again that night, Ian settled into bed between his two partners. Watching TV at a convention wasn't really what anyone wanted, but being able to spend time with loved ones was certainly worth it. They managed to find some movie to leave on quietly in the background and settled in to talking, then into cuddling, with Ian feeling safe between Andrew and Rei.

As the night went on, the trio slipped further down into bed until they were lying flat, Rei spooning up behind Ian with his arms wrapped around him, Ian hugging those arms to his front as he nuzzled and kissed with Andrew.

As the cuddling grew in intensity and sensuality, Rei bit gently down on Ian's shoulder, right where it met with his neck, getting a quiet moan out of his partner.

``Uh-oh,'' Andrew grinned. ``You found one of his buttons. Keep it up, and make sure to get the other side, too.''

Rei held his grip a little longer before kissing at that spot, then along the back of Ian's neck, to bite gently on the other shoulder.

The fact that both of his partners were taking control of him in such a way had Ian blushing bright red, not least of which because he was also intensely aware of his arousal, as well as that of Rei pressed firmly to his backside. The gentle biting continued along his shoulders and neck as Rei pressed firmly to him with a gentle rocking motion.

Andrew shifted some in front of Ian, slipping one hand down to cup over his boyfriend's tented jeans as he reached back with the other to snag the plastic bag that held the condoms and bottle of lube they had brought along to the con. The biting on his neck stopped as Rei looked up, curious.

Ian's eyes widened, ``H-hey\ldots{}''

``Shh, it's okay, just relax, fox,'' Andrew murmured, passing the bag over Ian to Rei, who took it cautiously. ``You two should have some fun, it feels like you're already on your way.''

Ian chewed on the inside of his cheek for a moment, then nodded. ``Can you\ldots{}can you stay? Is it alright if he stays, Rei?''

Andrew thought for a moment, then nodded, ``I'll stay if you want, if it's okay with Rei.''

Rei had been quiet throughout the exchange, holding himself still against his partner and clutching the plastic bag in one hand. ``Um\ldots{}If you'd like, sure. I'll admit I've never done anything in front of someone else, much less my partner's partner.''

Ian felt flustered, but clutched one hand on either of his partners, unable to meet either of their gaze. His blush seemed to be consuming his face with its heat, but he could feel his shaft pulsing stiffly against Andrew's hand still lingering on his crotch.

After a few more moments of stillness and silence, Ian worked up the courage to stammer, ``T-take your fox?''

Rei let out something akin to a quiet growl and gave another firm grind of his hips to Ian's, biting down on his shoulder once more, more firmly this time, before rolling free to extract a condom and the lube from the bag. Andrew did his part in helping by unfastening the button to Ian's pants, slipping the zipper down and helping his boyfriend scoot both pants and briefs down to his knees, freeing his erection from the confines.

Leaving himself mostly clothed as well, Rei managed to unroll the condom down along his own shaft and coat it thoroughly with the slick lube. That accomplished, he rolled himself back to face Ian, leaning away from him enough to peer down his front as he worked the tip of his cock up against, then very carefully into his lover.

Ian, for his part, clutched tightly to Andrew, burying his face against his boyfriend's shoulder and letting out a soft moan as he felt Rei slide into him. Rei felt thinner inside of him than Andrew did, but longer as well, and the whole experience was almost jarring, in a pleasant sense. He felt connected, emotionally and physically, to both of the people he treasured most.

Edging himself forward until his hips were pressed firmly to Ian's bare backside, Rei let out a shaky breath. He slid his hands up under Ian's shirt and inched the fabric up until he could help his partner out of the garment, breaking his grip on Andrew only momentarily.

Thus exposed, he dragged his fingernails down over the skin of Ian's back, grinning as the back arched to the touch.

As they relaxed, the two settled into a slow and comfortable rhythm. Ian rocked gently with each of Rei's thrusts into him as he held his upper body close to Andrew. Rei, confident in the red scratch-marks along Ian's back, settled his hands on his partner's hips to hold them still as he moved within him. Andrew contented himself with kissing gently along Ian's forehead while his hands busied themselves with his boyfriend's own stiff arousal, caressing along it in time with the thrusts.

Ian focused on counting along with his breaths. He made it a point during sex to breathe steadily and evenly. Four counts in, hold for one count, four counts out, hold for one count. He knew that the definition of a `count' changed as he got more worked up, but it was important that he remain consistent.

They didn't speak much, and the TV was too low to make make out, and so the only sounds were the gentle sounds of sex: quiet affirmations, gentle rustling, and the occasional sound of Rei's hips meeting up with Ian's rear after a particularly hard thrust. Andrew coaxed Ian on with gentle cooing, while Rei murmured, ``My fox,'' under his breath.

The feeling of belonging, of being taken by both his partners in a way, touched Ian both emotionally and physically. Usually, it took him longer to get off than Andrew, but tonight, his body seemed to rush toward climax. He didn't even have a chance to count his breaths before he felt the familiar surge of pleasure, spurt after spurt of his cum coating Andrew's hand, wrist, and front.

``Mmm, goodness,'' Andrew murmured into his ear. ``There you go, good fox\ldots{}''

Ian whimpered and shivered through his orgasm, tilting his head up to kiss Andrew firmly on the lips, something he couldn't easily do during climax in their usual set of positions.

Rei, sensing his partner's climax, redoubled his efforts, picking up the pace of his thrusts and clutching all the more firmly at Ian's hips. It didn't take too much longer -- only twelve more shaky breaths by Ian's count -- before Rei pressed himself firmly forward one last time, leaning forward to bite down on Ian's shoulder as pleasure overtook him.

Spent, the partly clothed couple simply held themselves still and worked on catching their breath. Ian could feel Rei's chest heaving against his back beneath the soft fabric of his t-shirt, reveling in the comfort of being held twice over as he rested his head back down against Andrew's chest.

``Mmm, two good animals,'' Andrew hummed softly, holding himself still as his boyfriend relaxed into calmer breathing and relaxation.

Ian held himself still as long as he was able. The corners of his anxiety were starting to make themselves felt once more, spurred on primarily by the sensation of his semen starting to cool in the room's air, making him feel coated and dirty. Even so, it was nice to be held by both partners and share in the moment while he could.

Finally, the need to be clean overrode the coziness, and he murmured quietly, ``I need to go get cleaned up, can I get up real quick?''

Rei peeked questioningly over Ian's shoulder to Andrew who nodded his assent. Both of them disentangled from their lover and let him slip carefully out of bed and shuck his pants the rest of the way before making his way off to the bathroom.

``\ldots{}just needs to be clean, nothing wrong\ldots{}'' Ian overheard Andrew explain before he shut the door, keeping his embarrassment to himself as he started the water running for the shower.

A scant minute or so later, he heard the door to the bathroom open. Someone washed their hands thoroughly followed by a bulk settling onto the closed lid of the toilet. Peeking out from behind the shower curtain, he saw Andrew sitting there, rubbing his face in his hands.

``You okay, wolf?'' Ian asked quietly, soaping his hands up for another round of trying to clean himself of the slick lube.

``Yeah. I'm okay. I don't know if that was really what I needed, but I'm happy for you.''

Ian stood in silence for a moment until he was done soaping and rinsing. Finally, he replied, ``I'm sorry, I just\ldots{}I just wanted you both there, I guess. It was very nice to feel.''

``Yeah, no, I get that.'' Andrew sighed, ``You're just my fox, you know? I could accept you and Rei as an intellectual thing before now, but that just kind of made me internalize it\ldots{}a little more forcefully than I was expecting.''

Ian nodded and ran his hands down over his body, checking for any hint of slickness from lingering spots of lube before realizing that Andrew couldn't actually see him. Rather than replying right away, he shut the water off and grabbed a towel, drying himself in the tub. Once he was mostly dry, he folded the towel neatly in quarters and slid the shower curtain back, laying the folded towel on the floor in front of the toilet before daintily stepping out.

``I'm your fox, wolf, and nothing's ever going to change that,'' he murmured, settling himself down onto his knees and resting his hands on his partner's knees. ``You and Rei play different roles in my life, and nothing is supplanting anything that was there before.''

Andrew nodded and took one of Ian's damp hands in his own and smiled tiredly. ``Promise?''

``Promise,'' Ian murmred, leaning up to kiss his partner on one cheek, then the other. He stood to dry the rest of the way with a smaller towel.

``Hey Ian?''

``Yes, wolf?''

Andrew paused for a moment. ``How many? How many roles do you think you need filled?''

Ian draped the smaller towel around his shoulders and thought for a second. ``I don't have an answer for that, hon. I just know you're the first, and will always be.''

Andrew stood again, level with Ian so that he could kiss him gently on the lips. ``And you'll always be my fox?''

Ian nodded, smiled.

``Come on, then,'' Andrew rumbled. ``I left Rei out there to clean up. Thanks for yapping, though.''

``Yap!''

Andrew smiled, more earnestly this time.

Ian let Andrew precede him out of the bathroom. He thought for a moment, smiled, and hung up his towel. Anxiety quelled, he headed back out into the room, to both his partners.
