\chapter{Michael}

Michael swallowed roughly at the sure signs of dominance that remained in his ex's actions.  ``What,'' he began, and swallowed once more.  ``What sort of closure do you want?''

``One more night,'' Glade murmured.  ``Tonight, you're mine, we take what we had at the best of times, and have that be the end, and we go back to being comfortable friends, rather than what we had before.''

``But you're-''

``I'm me, and all you need to be is my little pet roo, just once more.''

Michael swallowed hard once more, keeping his hands flat against the fabric of the dividing wall behind him.  The alcohol, the dominance, the familiarity all worked in Glade's favor, and he couldn't do much to suppress the excitement that had lingered since that violent outburst that had ended their relationship in the first place.

All he had to do was reconcile that it was really over, and on agreeable terms.

He felt dizzy, looked up to find no relief in the swirling lasers and lights that projected from the stage, a glowing arachnid of greens, blues, and purples.

``T-tonight,'' he stammered, ``I'll be your little pet roo.''

The grin that creased Glade's face was knowing, pleased, with maybe a touch of evil.  The music began to rise once more in a crescendo.

``You're already a little buzzed, I can smell the beer.''  Glade held up a slender tube which tapered to a small mouthpiece and glowed with a blue LED, ``Will you still be my good little pet if I get you a little more buzzed?''

It took Michael a moment to understand what was being offered.  Once he figured out the vape pen, he nodded shakily.  Glade knew him through and through, knew how much he liked placing himself into someone else's hands.  Glade took the nod as assent and tilted the mouthpiece of the vape to his lips, not yet pressing the button that activated the heating coil.

``You'll be my pet?''

Michael nodded.

``You'll please your dom?''

Michael took in the new term, nodded.

``I've got my crop.''

Michael flushed in the dark, nodded.

``Do you have your paws with you?''

Another nod.

``Same safeword.  `Rouge'?''

Michael squirmed between Glade and the wall, nodded once more.

Glade pressed down on the stud that activated the vape and pressed the tip of it between Michael's lips, quietly instructing, ``Breathe in.  Slow.''

Michael knew the theory behind the devices, and so he breathed in slowly and carefully, tasting the not-quite-smoke flavor of pot on his tongue and down his throat, flowing liquidly within him and filling him with both a sense of fullness-of-being and hunger that he couldn't quite put his finger on.

The devices were frowned upon by the hotel, no matter what they contained, so Glade kept the LEDs covered by his finger and palm, letting Michael have a good long inhale before swiftly pocketing the vape once more.

Michael held the warm vapor for a few seconds, then let it out with a few gentle coughs, muffling the sound as best he could.

``Come on,'' Glade said, with a sudden, earnest smile.  ``Let's finish this set, at least.''

The two moved back out onto the dance floor.

Michael felt the pot take him over in a matter of minutes, rolling in from his extremities until he felt as though he was dissipating into a cloud.  The music moved through him with such ease, and he felt like some luminous being, moving against and with the other luminous being of Glade, enjoying both the space and tension between themselves, as well as the friction of cloth on cloth or leather as they brushed up against one another.

Some unknown amount of time later, the set drew to a close amid the cheers of their fellow dancers, and Michael and Glade drifted from the dance floor, hand in hand, out past the guard and into the hallway.

Michael found it difficult to stop dancing, swaying gently from side to side and rocking his weight back and forth even as they made their way over to the bank of elevators.  Glade laughing at him was all he needed in terms of encouragement.  He got the impression that Glade himself wasn't entirely sober, and he felt in good company -- comfortable, like how he used to feel when they smoked together.

They made their way to the elevators and stood with a tired looking canine suiter and a few other up-late furries, waiting.

Glade leaned in against his arm and tugged him down a little closer, murmuring, ``Your room okay?''

Michael nodded.  The whole room had agreed to let private liaisons be allowed, and so anyone who was there and not already in the middle of something should agree to clear out if Michael needed.

The ride up was uneventful, and likewise opening the door into an empty room.  Alexis was probably still dancing with Corrin, and Bomber was probably hovering around the edges of the dance, unsure of where he belonged.

Michael slipped into the room with Glade, then bent down to offer a kiss, falling back into old habits with the drink and pot filling him with warmth.  Glade leaned up to meet the kiss, but quickly took Michael's lower lip between his own and bit down on it.  He tugged carefully downward until Michael's face was level with his own before letting up on the bite.  ``You going to be a good pet tonight?''

Michael sucked his lower lip into his mouth and searched briefly for the taste of blood before nodding bashfully, ``I'm going to be a good pet.''

``Strip, then,'' Glade ordered imperiously.  ``And get your paws on.''

Michael hesitated, swaying a little on his feet.  Glade reached behind his back and extracted a small riding crop from his back pocket, simply holding it at his side.

Michael got the hint, and slipped over to where his bag lay next to the bed, fishing out his paws: gloves of dark brown faux fur.  He moved back to where Glade stood and carefully slipped out of his shirt and tugged his jeans and underwear off, standing exposed and erect in front of Glade. He shivered slightly in the air-conditioned room, though at least half of that was due to his excitement.

``Now me,'' Glade ordered quietly, holding his arms out.

``Yes mistr-'' Michael began, before realizing his mistake.  He winced as Glade raised the crop, then braced himself and held still.  There was a quick crack and an almost satisfying sting against the left cheek of his buttocks.

``You will call me Dom Glade, little pet,'' he purred.  ``No more slip-ups.''

``Yes\ldots{}Dom Glade,'' Michael whispered.  The strike had hurt initially, but with his body buzzing in its high, the sting was quickly turning into the familiar pleasant sensation they had experimented with so long ago.

Glade held his arms out and let the naked Michael slip the leather jacket off, then lifted his arms for Michael to lift his shirt.  There was something intimate about undressing his former partner, even having been ordered to do so, and he took his time, being mindful of the crop.

Beneath his shirt, Glade was bare, no binder or anything.  There were just two well-healed scars, each curving gently beneath his nipples, where the mastectomy had taken place.  Michael brushed his hands, fuzzy in their paws, softly down over his ex's chest, wonderingly.  There was so much more body hair than he had remembered, more than some of his roommates here at the con, come to think of it.

``There you go, little roo,'' Glade murmured, sounding pleased.  ``You're halfway there.  Kneel to do the rest.''

Michael nodded and obediently lowered himself to his knees, reaching up with his paws to work on unfastening the button of Glade's jeans, fumbling partly because of the fake fur and partly out of nerves and excitement.  Glade wore boxers -- though he always had -- which slipped part way off his hips as his jeans were carefully tugged lower.

Michael reached his fur covered hands up to rest just above the wasteband of Glade's pants and underwear, uncertainty growing within him.  He finally smoothly slid his hands down, taking the garments along with them to free his ex from his pants.  He hadn't been sure what to expect, seeing that Glade had opted for top surgery, but found himself confronted with the neatly trimmed crotch that still felt familiar to after all these years.

Glade chuckled quietly above him, drawing the tongue of his crop up along Michael's back to tease gently across his shoulders.  ``Expecting something different, little pet?''

Michael flushed and drew his hands lightly up over Glade's legs once more, the fur of the gloves brushing through the hair of his ex's body.  ``I\ldots{}don't know what I was expecting.''

Glade tapped the leather tongue of the crop gently against the back of Michael's head, ``I'm comfortable how I am.  I can present how I like, and little pets can still worship me.''

His cheeks still red, Michael nodded and swallowed, carefully rehearsing in his arousal- and drug-addled mind what he was going to say next.  ``May I worship you, Dom Glade?''

Glade walked slowly around Michael as he sat, kneeling and aroused on the floor.  He seemed intent on drawing the moment out and letting Michael stew.  The tongue of the crop kept tapping and prodding, as though it were inspecting all the ways in which his body had changed over the years.  The process of waiting had that flavor of delightful agony that Michael knew Glade was keen on.

Finally, Glade relented and sat back on the edge of the bed behind Michael, tapping him gently on the shoulder with the crop before leaning back onto one of his hands.  ``There's a dam in one of the pockets of my coat.  Get that, and you may worship me.''

Michael tried not to appear too eager as he crawled over to the crumpled jacket and tugged out the plastic-wrapped dental dam.  Aside from a few instances of almost fooling around, like that morning, he had been mostly abstinent throughout the last five years, and he lept at the chance to service his old owner as he used to (with that bit of latex in between, this time -- they weren't fluid-bonded anymore).  It might be the alcohol and pot buzzing through him, but he felt right, in his place.

Glade kept his noises primarily to purrs and growls, huskier than Michael remembered.  Even so, the act maintained its familiarity to him: the long teasing licks, the shorter feathery ones, lazily spelling his name out in cursive against the latex of the dam before delving a little more adventurously between the labia of his former -- and once more -- lover.  His hands, still stuffed in their paws, alternated between gentle brushings and firmer pets along Glade's legs, showing his adoration as he worshipped the best way he knew how.

He read his partner's body as best he could, finding all the spots that led to the reactions he craved.  He would focus there, then drift his attention elsewhere, not letting any one spot get played out.  Despite the years intervening, he still felt as though he knew Glade's body thoroughly.

``H-huff,'' Glade breathed with a stiff shudder.  ``Mmn, such a good little pet.''

Michael relaxed back onto his heels, peering up along Glade's more masculine body, eager to receive the praise.

``You did well, roo,'' Glade growled, hefting himself up further onto the bed.  ``Come up here by me, there's one more thing I want you to do, and I know you deserve it.''

Michael nodded shyly and stood to his feet, feeling the blood flow freely through his cramped legs.  He moved around to the side of the bed before climbing in, stretching out alongside his ex.

Glade leaned in closer and bit gently at the lobe of his ear, whispering quietly while he was there, ``I want you to paw, just one more time for me. I want to see you get off.''

Michael blushed and nodded, still shivering at the bite to his ear.  ``Yes\ldots{}yes, Dom Glade.''

He moved to slip one of his hands out of the paw mitts, only to feel the sharp crack of the crop against his thigh.

``But leave those on.''

Michael swallowed.  He knew he'd make a mess of the paws, that was inevitable.  He also knew how to clean them, though, and so after a moment, he nodded and rolled onto his back.

His erection hadn't let up since Glade had first gotten his attention with the questions on the dance floor, and by now, he felt an aching need for release.  The fur of the paws was dry and coarse against his stiff shaft, and though he usually required lube for masturbation, it seemed to feel just right to curl the clumsy fingers loosely around his cock and stroke along it gently.

It didn't take much, really.  The tickling of the fur and the occasional squeeze around the base of his cock as he stroked was enough to get him closer and closer to his orgasm.  What finally did it, though, was that last bit of mental stimulation when Glade leaned in close against him and nuzzled up to his ear, murmuring, ``You are just such. A good. Boy.''

His heavy breaths were cut short with a quiet whimper and he gripped tightly around the base of his shaft with his fur-covered hand and felt the rush of pleasure wash over him, felt the first few spurts of seed land on his front, and the rest dribble down over the brown fur of his paw.

``God, I missed that,'' Glade cooed as Michael settled back down onto the bed.

``Nnnf.''

Glade grinned and gave a gentle kiss to Michael's cheek before levering himself up out of bed.  ``Thank you, little pet.  Now, if you'll excuse me, I've got some other parties to go to.''

``Huh?  But\ldots{}'' Michael began.

``Hush, you did good.''

Michael leaned up onto one elbow, watching Glade tug his boxers and pants back on, then hunt for his shirt.  ``What\ldots{}what was that?  For us, I mean.''

Glade tugged his t-shirt back over his head and stood, regarding Michael for a moment.  ``Closure,'' he said simply.

``And where do we go from here?''

``I don't know, roo, I really don't.  I just feel like we're in a better place from where we left off before.''

Michael nodded.

His head still spun.

\secdiv

There was an electric-mechanical click as the lock on the door activated, and Michael jolted upright in bed, rushing to cover himself with his hands as he sat up.  He must've drifted off once Glade had slipped out of the room to head to his party.  He was still wearing the paws, even.

Bomber slipped quietly into the room, saw Michael in his messy and furry state, and smiled bashfully, turning away to face the wall.  ``Need a moment?''

Michael shook the paws off of his hands quickly and ducked over the edge of the bed to snag his underwear, slipping them on quickly, ``Just\ldots{}ah, just woke up.  You're fine.''

Bomber laughed and slid further into the room, slipping out of his canvas jacket and sitting down on the bed.  ``Hope I didnt interrupt, thought you were just sleeping.''

``I probably was, at that,'' Michael mumbled, rubbing his hands over his face, before reaching for his shirt to wipe up his spilled cum.

The two sat in awkward silence for a minute or so before Bomber asked, ``Good evening, then?''

Michael let out a breath, more forcefully than he had intended.  ``Yeah.  Glade came over.  Bit of\ldots{}bit of the old days, I guess.''

Bomber nodded and fiddled with one of his fingernails.

``Sorry,'' Michael offered.  ``Maybe a bit much information.''

``It's okay,'' Bomber responded.  ``Just wondering what he means to you.''

Sensing the undercurrent of meaning, Michael reached a hand over to rest on Bomber's knee.  ``We broke up, a long time ago. I don't think that's going to change.''  He took a deep breath before continuing, ``I know you like me, Bomber, and I know I've been distant, but I just don't really know where my head is anymore.  Glade meant enough to me that I don't know what to do after that ended.''

``I can't really say I know how you feel,'' the mouse replied hesitantly.  ``I've never been in a situation like that.  I don't want to push you or anything, I just like you, I guess.''

Michael nodded, silent.

The two sat for a while longer, touching and keeping contact.

Finally, Bomber asked, ``Think you guys will hook up again?''

Michael thought for a moment, then shrugged, ``Probably not.  Not in the same way we did before, certainly, but it's good to have contact open again.''

Bomber looked down and nodded.

Michael laughed and leaned over to hug both arms around his friend, ``Hey, don't worry, whatever happens happens, not leaving my friends behind at all.''
