I woke with a start.  The music was stopped, but my computer's monitor was still on, the simply displaying the time in one corner.  What passed as a screen saver for me.  I was cold and thirsty, and the only thing near by was the half-full beer bottle.  I grabbed at it and held onto it for a moment before deciding against it.  I needed water.  At least the bottle, by the slight chill, told me I hadn't been asleep too long.

I climbed clumsily over the sleeping form in my bed and stumbled to my desk to grab my travel mug, slipping out of my room and pulling the cable-lock between the door jam and door so that I wouldn't be locked out.  Shuffling down the hall toward the drinking fountain, I brushed my rumpled clothes out and tugged my shirt down over my pants absent mindedly and somehow still self-consciously to hide the slight tent there.  Morning wood strikes, even at twelve thirty at night.

It wasn't until I was rinsing the coffee taste from my mug that the rest of the evening came back to me.  Holy crap, I thought.  There was another person in my bed.  And it was a girl!  My ears reddened at the thought, then reddened further as I felt my erection, that traitor, subside now that I was more awake.  I was still too tired to think the whole thing through, but not too tired to be embarassed about it; hopefully Kris hadn't noticed.

I downed a glass of water and filled my mug again before heading back to my room, slipping quietly into my room once more and letting the door shut as quietly as possible.  Kris was still breathing heavily from my bed.  I shuffled toward the sound as I struggled to see in the dark.  Questing fingers finding the fabric of my sheets, I sat myself down on the edge of the bed and took another sip of water.

``Mm, Cor,'' Kris slurred and reached out a hand, only to whack me in the side.  She pulled herself around closer to me and blinked at me sleepy.  ``Tha' water?'' she mumbled.

I nodded and took one last sip before sacrificing the rest of the mug to She Who Likely Had Cotton Mouth Pretty Bad.

I shook myself some.  I was already thinking in terms of endearment.

Kris propped herself up on one elbow as she slurped at the water noisily, getting halfway through it before coughing violently.  I took the cup from her before she spilled the rest on my bed and patted her between the shoulders, ``Swallowing, s'one of those key skills,'' I murmurred.

She punched me feebly in the side before finishing her coughing fit and scooting up behind me some, half-curling around my lower back, keeping her head propped up on her fist.  ``Dork.''

``Mm,'' I agreed.

She seemed to tense up as she woke up a little more, leaning away from me a little cautiously, ``Sure you're okay with earlier?''

``No,'' I said, shaking my head and reaching around behind her to lean back onto my hands, effectively trapping her where she was.  ``Not sure,'' I added.  ``Not yet.''

Kris nodded and folded her arm in and down like origami, resting her head on her bicep.  ``Lemme know when you are.''  She added quietly, ``Or if you aren't.''

We stayed quiet for a few minutes.

``It,'' I began, then paused.  ``I mean, I liked it, and that's why I'm not sure.''  I sounded stupid and trite to myself, like I was quoting lines from a movie.  I shrugged it off.

``Mm.''

I sat up a little and pushed at her side a little, ``Scoot, I want to lay down.''

Kris wiggled herself back across the bed until she was near the wall and I was struck again by how narrow the beds were.  I hoped my body wouldn't make too much of an ass out of me in such close quarters.  I stretched myself out along the bed again anyway, facing the girl --- girl! --- who had kissed me, and I had kissed back.  She smiled sleepily and lifted her arm, holding the covers for me and looking for all the world like a stoned parody of Batman spreading one of his wings.

I shifted myself a little closer toward her and gratefully let her drape the covers over me.  Her hand dropped over my side and she gave a feeble sort of tug, a pained `c'mere' look on her face.  I giggled a little and scooted in a little closer, resting my hand on her side, just above the waistband of her pants.  This wasn't satisfactory, I guess, because she pulled at me a little more forcibly, straightening her legs out as she tugged herself up to my front.  I gave in and let my arm slip down around her back.

I had closed my eyes at some point, but opened them again when I felt her nuzzling her face in against my own questioningly.  I paused only for a second before responding to the advances, finding her lips with my own easily in the dark.

We shared delicate, exploratory kisses for a while as I tried to banish the thought that the feeling of her breasts against my front was a constant reminder of her gender and my previously stated preference.  The thoughts were still whirling in my head, the reminders of homosexuality battling with the desires for closeness with the one who was here with me now.

The kisses moved past that exploratory phase filled with smooching and pecking and into decidedly more intimate `real' kisses, as I'd called them in the past.  Kris still tasted a little like smoke, but it was a smaller part of the whole, just one chord in the whole flavor of her.  I was marveling the differences between this act as I had shared it with the two boyfriends I'd had and Kris when she slipped back from me.  She rearranged herself, slipping her left arm up under the pillows while her right tightened around me.  I hugged onto her a little more in return.

``I'm tired, Cor,'' She mumbled.

``'Kay.''

``And we're rushing.''

I tilted my head against the pillows some.

Kris rolled around after a second or two to spoon back against me once more, ``You were trembling.''

I kept my arm loosely around her while she got comfortable and forced myself to relax.  I found myself surprisingly tense.  ``Oh.  Sorry.''

``Mm.  We'll figure things out tomorrow.  Sleep now.''
