I saw my mom off shortly before we were supposed to gather for our first hall meeting.  She cried as she hugged me and kissed at my cheeks, whispering those same worries to me one last time before she went back to her car.  I suppose the reality that I had just moved away from home hadn't set in yet, but I was admittedly a little glad to see her go.  I was starting to feel like her pessimism was dragging me down and I was eager to get into life at college.

I had just enough time shift my basket of clothes to the floor and get my sheets onto the bed before Mark started hollering at the head of the hall, calling all the guys out of their rooms for the first meet and greet.

``Alright guys, for those who don't know or forgot, I'm your RA, Mark.  I'm supposed to read this big spiel to you, but I can sum it up to you pretty quickly.  Come to me if you've got problems with each other, with school, or with your room, but not for help with your love life.  The code to the bathroom is ninteen eleven, and we'll come up with a cleaning rotation later this weekend.  No candles, no incense, no smoking, no drinking, no drugs, take it easy on the loud music, and respect your roommate.  Basically what I'm saying is have fun, y'all are cool, but be nice to each other and don't burn the building down.''


We all laughed and went down the hall, giving our names, majors, and room numbers.

``Well, since that whole thing was supposed to take us an hour and a half and it took five minutes, why don't y'all just mingle for a bit, okay?  I'm serious, get to know each other, 'cause you've got six months to go here and you're stuck where you are.  No sneaking back to your room.''  As if to provide a role-model for us, he socked the closest guy on the shoulder and started in to introducing himself to him in depth.

We all stood around awkwardly for a bit before loosening up and starting to actually talk with each other.  There was one other music major, Eric, and two art majors, Joseph and Jamen, and the four of us somehow wound up clumped together amongst the crowd of thirty two guys.

``So,'' ventured Jamen.  ``You two are majoring in burger flipping, and Joseph and I have telemarketing?''

We laughed a little shyly and nodded.  ``I guess that's how it goes,'' I said.  ``So.. what kind of art do you guys do?''

``Painting and graphic design,'' Jamen said.

``Comic book type stuff and graphic design,'' Joseph said, adding, ``Graphic design is about the only way to make any money in the business, so it seems like every art major is also in graphic design.''

Eric nodded.  ``Sorta the same with music, except with education.''

``You an ed major, too?'' I asked.  Eric nodded.  ``I just kinda tacked it on when my parents complained that I'd never make any money.''

``Yeah, my parents got on my case about that, too,'' Eric chuckled.  ``No such thing as professional choirs anymore.  What instrument do you play?  Or are you voice?''

``Trumpet.  Pretty standard stuff.''

And so it went.  We introduced ourselves to the other guys on the hall, but after half an hour or so of that, we wound up sitting against the wall, two of us on each side of the hall, facing each other and talking about random things, mostly about going to what was mostly an agricultural school for a liberal arts degree.
