Jamen showed up at my dad's apartment fairly early that morning.  We had planned on the drive taking quite a while, and since the room was registered in my name, I wanted to make sure I didn't leave anyone waiting just because I had gotten bogged down in traffic somewhere between the Springs and Denver.  So I wound up waking up at around seven thirty that morning and puttered around, useless until I had my two cups of coffee, and by the time Jamen knocked an hour later, I was packed, showered, and ready to go.

My dad was up, but his girlfriend was still asleep, so he greeted my friend and offered him a cup of coffee as well --- such addictions ran in the family --- before we made our way out into the cold.  I was lugging a duffle filled half way with a set of clothes, a pair of swim trunks in case there was a hot tub, and some additional snow gear; my skis and a spare pair of snow blades were in the car just in case anyone else decided they wanted to go skiing as well.  Jamen got to carry the cooler, another styrofoam deal, that my dad had filled.  There was a bag of ice, a whole chicken, a bag of spices and salt for the chicken, a handful of potatoes, a quart of milk, and a can of frozen juice in the cooler.  Materials enough for me to cook dinner for the night we would be up there.  Taped to the top of the cooler was a hastily penned recipe for the chicken from my dad, a scaled down version of the recipe he used for the Thanksgiving turkey.  `Be Safe!' was scrawled along the bottom edge of the note, and Jamen smiled, reading it as we lifted it into the trunk of the car with my skis.

We left a quiet Colorado Springs in silence, both of us savoring our individual travel mugs of coffee, each laden with cream and sugar.  Jamen must've had to wake up at at least five thirty to make the drive to my place and leave his car there, so we were each more focused on waking up than anything else.  But by the time we hit the highway, we were both starting to warm up.

``So what all do we have planned for this whole trip?''  Jamen asked, slouched down in my passenger seat, head poking up from the depths of his anorak.

``Oh, I dunno,'' I mumbled.  ``Probably get there mid afternoon, walk around for a bit.  I'll make some dinner and we can just hang out at the condo and do whatever one does at parties, I guess.  Dunno about tomorrow.  I brought my skis, in case anyone else wants to go out, and I've got an extra pair, too.  We'll figure it out, I guess.''

He laughed and sipped more at his coffee, ``Well, sounds cool, I guess.  Don't suppose anyone brought anything to drink for the party?''

``Not to my knowledge, no.  Sorry.  I don't think any of us are of age, and I dunno if anyone has progressive enough parents to get booze that way.''

``Well, your dad gave you that beer, didn't he?  Over break?''

I grinned, ``Yeah, but I'm not sure I can picture him supplying five minors with alcohol.''

``True, I guess.''  A minute or so passed before he continued, ``Well, I brought an eight I've been saving all break.''

``Really?  Wow.  Kris will be happy, at least.  And Thomas.''

``Mm.  I couldn't do anything with it at home other than, like, eat it straight, which is gross.  Been pretty much stuck at home with parents and siblings.''

``Ooh, yeah, I suppose that does make it a little hard to smoke up,'' I laughed.  ``So do you have more than just the sister you mentioned a while ago?''

``Yeah, two sisters and one brother.''  He shrugged and sipped his coffee, ``Two boys, two girls.  I'm the oldest of everyone.''

``Oh, wow.''  I shook my head, ``I have a step sister, but I don't really know her all that well.  Only child otherwise.''

Jamen laughed ruefully, ``I wish I was an only child, sometimes.  I don't mind my brother and sisters all that much, but it was kind of a pain growing up.''

``Yeah?  How so?''

He shrugged, buried himself deeper in his coat, and mumbled a reply, ``Brother found me out, outed me to my parents.''

``Oh.  Jesus...''

``Yeah.  I just about kicked his ass for that one.''

``Wow, yeah, I probably would've done the same.''

He shrugged.  ``He took after all the religious stuff my parents fed us all a lot more than I did, I guess.  He's probably even more gung-ho about it than they are.''

I shook my head and tried to imagine a family like that.  ``Not sure I get the whole religion thing.''

Jamen laughed, ``I thought I did for a while, but when I sort of dropped out of the whole thing, I realized that no one really does, not even the pastor, not the congregation, not my family.  I thought I could see it as sort of a framework or something, like a way to view the rest of the world, but then all sorts of weird stuff contradicts that, and no one else seems to see it that way.  At least not down in Alamosa.''

``Never been down that far south,'' I admitted, gently steering the conversation to a happier topic.  ``Looked it up online, though.  Seems like a pretty small town.''

``Definitely.  Just kind of an old mining town that managed to stick around after the mining died down.  It's something of a tourist attraction, too, for the sand dunes, and there's a little college there, too.''

``Wanted to go somewhere away from parents but still in Colorado?''

``Yeah, definitely.  It was a little more expensive, which my parents like to remind me of, but they're rich enough.''

``Ah, alright.''  I thought for a moment, ``So you're the oldest...  Think your brother and sisters will go to college, too?''

``My brother and one sister might, but I'm sure my parents can afford to send them about anywhere.''

I nodded and we talked for a bit about the troubles my mom and step dad were going through, about how the early 2000s didn't seem to be doing all that well in general when it came to the economy.  It seemed like there was crisis after crisis in various financial sectors.  The conversation petered out and turned towards food when we each decided that neither of us knew enough about the economy to offer anything other than generalized observations on it.

We were making surprisingly good time, considering the weather, so we stopped in at an IHOP in a southern suburb of Denver to use the restroom and grab a quick breakfast before we made the climb up out of the plains and into the mountains.  Over pancakes and hashbrowns, we laughed over inane stories and planned out the trip a little further.  Jamen didn't ski, but said the would be willing to try the snow blades --- skis that were about two and a half feet long, much easier to learn on than full-sized skis --- if more people planned on going out on the slopes the next day.  We figured that we could check out late in the morning and get a few hours in on either side of lunch, then just toss the skis back in the car and head back home without having to worry about deadlines.

On our way once more, we talked little as we watched the Denver metro area thin out, climbing our way up out of town on I-70.  We listened to the CD of jazzy rock from Japan that Kris had burned for me, the only non-classical CD I had in the center console collection.  By the time we made our way past Genesee, the last outlier business district of Denver, we were settling into the rhythm of the drive.  Traffic started to slow down as a whole once the cloudy sky started to spit a light scattering of wet snow down onto the road.

``So how do you think this next semester will work out?'' Jamen asked, breaking the conversational silence.

I shrugged, ``Alright.  I don't think I have any difficult classes, or anything.  Need to get a job, though.''

He nodded, watching out the passenger side window.  ``Me either.  Come up with any ideas of where you'd get a job?''

``On campus, I imagine.  Maybe one of the dorms or something.  I think I'm too late for work study, though, so it'll have to be an hourly thing.''

``Work study's a bitch to get, I hear.  If you work in the kitchens, I bet you can get free food all the time, though.''

I laughed, ``Probably.  Then I can bring you and Thomas back some fries for when you all get the munchies.''

Jamen smiled at me innocently.  ``I wouldn't dare ask.''

``I would, too.''  I grinned, ``Anything to get you guys to quit going to Waffle House.  That stuff's pretty gross.''

``Aw, come on!'' he pleaded.  ``Just think, getting just totally blasted and walking over to the Waffle House where everything's funny, eating waffles made soggy by way too much syrup.  Fuckin' delicious, man.''

``Oh, God,'' I chuckled, shaking my head.  ``Don't even talk about it.  Gonna make me sick.''

``The butter that's not even butter,'' he grinned.  ``Grease coating the floors, the booths, the tables, the stools...''

I made gagging noises.  Jamen laughed.

``Whatever, man,'' he shrugged.  ``You just don't know how to live.''

``What, you think I should work at Waffle House so I can get you guys a discount?''

``There's an idea!''

``I think I'd shoot myself, sorry.  Kill myself in the deep fryer.''

``Ouch.  Yeah, stick with the dorms.  Besides, that walk would suck to make every day.  Just for serving stoner after stoner, homeless guy after homeless guy.''

``Mmhm.  Besides, I bet the dorms would be better at working around my class schedule.  Also, no night shifts, so I can still get sleep and hang out with people.''

``Sounds good,'' Jamen nodded, shrugging himself out of his jacket, what with the car being very warm by now.

I nodded, and we drove on.  Traffic continued to slow dow until we were going little more than thirty five.  I was glad for our head start now, since it would probably be snowing up on Berthoud Pass.

``Think you'll head back home for summer?'' Jamen asked.

I thought for a moment, ``Dunno, haven't really thought about it, to be honest.  I guess it depends on whether or not I get a job out in Fort Collins.  If I do and I can work over the summer, I guess I'll look for a place.''

``Totally should,'' he said, sitting up straighter.  ``We should get a place with Eric and Joseph or something.  Maybe Thomas, too, who knows.''

``Given it much thought, then?''

``Well, yeah.  This break's sucked, to be honest.  I don't think I really want to go back down there to live for more than a week, like during spring break.''  He pulled a face and shook his head, ``Gonna try and get a place up there no matter what, even if I just rent a room from someone else.''

``That's a pretty good idea, though.  I'd be up for it.  I mean, I love my family, but I'm sick of driving back and forth between two homes.  It'd be cool to have just one home to live in.''

Jamen laughed, ``Can't say I've ever experienced that.  You'd be up for maybe looking into moving into a place with a couple of people, then?''

``Why not?  I'm sure it'd be cheaper than the dorms.  They're crazy expensive.  And hell, I bet I could live with you, Joseph and Eric, and I know I can get along with Thomas.  What sort of place were you thinking?''

``Well, there's some apartments that people have been suggesting.  They've got some four bedroom places on two levels with a kitchen and main area.  Or we could rent a house.  There's a girl in one of my classes that's renting a three bedroom place in town.  It's the ground floor of a house, with a four bedroom place downstairs.  Something like that would be cool.''

I nodded, surprised at how excited I was at the prospect.  ``Sounds nice, yeah.  I'd really dig doing something like that, actually.''

We made our way up Berthoud pass discussing the details of how that might work.  Who would likely do the most cooking in that group (me), who would the the loudest (Joseph with his computer games), where we should look for a house (north of campus).  We laughed over what rules we should have regarding parties, girlfriends and boyfriends, and chores around the house.  By the time we crested the pass, where the road divided the small ski area of Berthoud in half, it was nearing eleven thirty.  With about half an hour of drive ahead of us, we were right on schedule for our noon check in at the resort hotel.  We spent the rest of the drive being excited at each other over the party, the coming semester, and the prospect of moving out north.
