%%%%%
\chapter*{Ioan Balan\#Tracker — 2305}

Ioan Balan awoke to an urgent message.

Ey didn't really like these, the sensorium messages. Ey liked paper messages. Ey mostly just liked paper. Ey was always accruing more. Paper and pens. Eir friends thought it creepy. Paper messages, or those rich messages that came attached to paper, played on its surface, or even messed with eir sensorium. To have one that just barged in on eir vision and endocrine system like this made em quite anxious. This one included a tiny jolt of adrenaline as an alert. Waking up with that jolt to have a partial sensory takeover just felt rude.

The benefit was that ey didn't have to get out of bed to deal with it.

The opacity on the message was turned up quite high, so that even in eir dark room, with eir eyes closed (and heart still pounding), ey could see the fox. A bipedal fox dressed quite sharply. It was sitting on a fairly plain wooden chair, situated in an empty room. The room had wood floors the same color as the chair, some very light wood, like hickory or pine. The walls were concrete where they weren't glass. Outside the glass was a sere shortgrass prairie, a cloudy day.

The combination of the fox's white fur, glistening and iridescent, combined with the room and landscape was all painfully pomo. Ey didn't consider eirself much of a pomophobe, but this was\ldots{}intense.

\emph{``Hi Mx Balan,''} the fox was saying. \emph{``I have a proposition for you.''}

Ioan grunted. The message was recorded, thank goodness. No interaction

\emph{``My name is Dear, Also, The Tree Was Felled, or just Dear, and I'm a member of the Ode clade. I'm an artist-''} Ioan rolled eir eyes. Ey could tell it didn't like the word. \emph{``-and performer. I'm not just telling you this to, ah, toot my own horn, I believe the phrase is, but just to underline the fact that I'm woefully unprepared for the situation at hand.''}

The fox smiled, looking tired. \emph{``I need some help finding someone,''} it continued. \emph{``Someone that doesn't want to be found. It's personally important, but also potentially damaging to the image of our entire clade.''}

Ioan furrowed eir brow.

\emph{``The person has information, a name, that ey have supposedly shared. We --- the other members of my clade and I --- don't precisely know if they actually did, unfortunately, we just have word from others close to the clade that someone knew and said The Name.''}

The fox shook it's head, ears flopping from side to side. \emph{``I'm sorry, I'm getting sidetracked by details. I try to be prepared for conversations and messages like this, but I'm a little worked up, excited, I guess. Can we meet?''} It listed some coordinates. \emph{``Even if only to talk. Even if you're not interested, I'd still like to meet you. You seem neat.''}

The message ended.

Ioan lay in bed, thinking. It was still about an hour before ey had to get up, and ey was loath to start the day before ey had to. Ey tried eir best to sleep for another ten minutes, at least, but eir mind kept slipping back to Dear's request.

\emph{Why me?} ey asked the backs of eir closed eyelids. \emph{Why hire a writer who fancied eirself a historian as a PI?}

With still a half hour to go before ey had to be up, Ioan slipped out of bed, stood, and stretched. The least ey could do was get a shower and some coffee. If there were any reason that the founders of the system had included sensoria in the works it must have been for those.

Those done and clothes donned --- ey knew ey could never out-natty the fox, so the usual faux-academia garb it was --- ey penned Dear a short note with a time. If it was day in that sim, or even late afternoon, it should get the note before dinner or bed.

\emph{Besides,} ey thought. \emph{Maybe it will get the fox to start sending notes this way in the future.}

No luck. Less than thirty seconds later, Ioan received a sensorium ping of acknowledgement, and a shiver up eir spine to go along with it.

Ey forked and sent \#c1494bf out to the meeting. Meanwhile, ey'd get some food.
