\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

Founded in 2115 CE (nine years prior to systime 0), the construct containing uploaded personalities commonly known as the System has exploded in population to an estimated twenty-seven billion individuals with countless more instances forked from those core identities. A world that is stable, beyond scarcity, and beyond even death, appeals to a great many people, and through incentives provided by political entities phys-side, transition from physical to uploaded life has been made as smooth as possible. The transition of religions and spirituality from life on Earth to the System has been less than seamless, however. We intend to explore the incidence and applicability of a wide array of generalized religious beliefs as they occur in societies built of immortal individuals, comparing them against their mortal roots on Earth. Through this survey we hope to hope to divine what aspects of spiritual life are bound more firmly to physicality and readily apparent mortality with an eye towards avoiding supercessionist language.

\hypertarget{the-elevation-of-unknown-things}{%
\section*{The Elevation of Unknown Things}\label{the-elevation-of-unknown-things}}
\addcontentsline{toc}{section}{The Elevation of Unknown Things}

What happens when mortality fails? What happens when what was once miraculous is now quotidian? What becomes up the beliefs we hold in the face of fundamental shifts in our reality?

With the advent of the technology required to upload one's consciousness, our lifespans are limited by the lifespan of the hardware on which we run. Our immortality may be only a functional one, but that does not change the fact that it redefines many of the foundations of the religions of the world --- and, indeed, much that we take on faith; the instance artist Dear, Also, The Tree That Was Felled put it succinctly, ``{[}To simply cease existing{]} is just cessation, and I do not care whether or not there is anything beyond that cessation. That is for the prophets and poets to worry about''.\footnote{Bălan (clade). systime 202. \emph{An Expanded History of Our World}. The Simien Fang School of Art and Design Press.} We know (or at least strongly suspect) that there is nothing after the cessation of an instance. There is no experience of death, there is simply the end of memories
