\hypertarget{ioan-bux103lan-2325}{%
\chapter{Ioan Bălan — 2325}\label{ioan-bux103lan-2325}}

The first thing that Ioan did when ey arrived before that low-slung house, there among countless acres of rolling buffalo grass, was laugh.

The prairie was much as ey remembered. Grass tickled at eir lower calves even through the socks and slacks, clouds threatened rain as they always did, and wind tugged at eir hair in all the very same ways as it first had however many years ago now — was it really twenty? And yet the house! Banners were hung about in deepest black, streamers running from pole to pole in a welcoming path, guiding visitors up to the house. This was lit about with flames of all sizes. Tea-lights scattered among the dandelions, elaborate candelabras set upon tables, braziers set upon tripods, wall sconces set beneath the cantilevered roof. A glow painting the grass beside the house suggested a bonfire out back.

And there, the largest banner of them all draped from that roof shouted in stately capitals: ``HAPPY DEATH DAY''.

Still shaking eir head, ey walked up along the streamer-lined path up toward the house. When the threshold was crossed, a soft chime sounded from within and outside the house.

Ioan need not have looked hard for Dear, for the fox was already sprinting around the corner of the house. Fox\emph{es}, ey realized, for as it ran, it forked off copies of itself of all sorts: that iridescent fox ey remembered, yes, but also scampering fennecs no larger than a double-handful, a few grinning copies of the Michelle Hadje of its past, and even a shoulder-high lumbering beast with eyes that crackled with a light of their own.

Dear — the real Dear — was easy to pick out, for it was dressed in mourners garb. A black suit, almost-but-not-quite masculine, with its eyes hidden by a gauzy black, almost-but-not-quite feminine veil.

One by one, the various forks quit, and Dear, Also, The Tree That Was Felled skidded to an unceremonious stop in front of the academic.

\emph{``Ioan! Mx Ioan Bălan! It has been too long! I have missed you.''} The fox held out a paw.

Ioan bypassed this and went straight for the hug. ``Dear, this is patently ridiculous.''

The laughter against eir ear was musical as the hug was returned. \emph{``I hold no patent on the ridiculous. It is precisely as ridiculous as it needs to be. Come! Come around back. You are early, and that is perfectly fine, but folks will want to say hi.''}

Following after the fox and laughing at the way the occasional non-anthropomorphized fennec would blip into being, scamper into the grass with a (frankly rather horrifying) screech, and disappear, Ioan chatted with Dear.

The fox was short on speech after the greeting, eventually hushing em. \emph{``We'll all talk together.''}

``Ioan! Goodness!''

Ey smiled. ``Codrin, you're looking well.''

What similarities the two had borne early on had long since started to blur. Codrin had started out, as a matter of absent-mindedness, an identical copy of Ioan. While Dear could fork out all the unexpected shapes it wanted, Ioan had never mastered the art. Time changes much, however, and eir up-tree fork had deviated in style from Ioan's stolid adherence to form. Codrin's hair had long-since grown past Ioan's hastily combed look, and now resembled an artfully tousled mop. Eir face, too, had changed, adopting a roundness that suited eir features well. The usual warm-colored sarong and tunic, however, had been replaced with clothes as funereal as Dear's.

Matching, Ioan realized. They were a triad now, Codrin, Dear, and Dear's partner, and ey supposed there was no reason that the three of them shouldn't match on their so-called death day.

There were hugs all around, and Ioan hid eir secret smile at the uncanny act of hugging one's own fork, however far they had diverged.

``How are you three? Excited?''

``Nervous is more like it.'' Dear's partner laughed. ``At least, I am. I can't speak for Codrin, but Dear hasn't shut up about this for months.''

The fox looked quite proud of itself. \emph{``Guilty.''}

Ioan looked to Codrin, who shrugged. ``I play the moderate, as always. I'm nervous and excited in equal parts. The nervousness comes from the irreversibility, and the excitement from the inevitability.''

\emph{``Ey has a way with words, as always. I have been unable to be nervous, even about the irreversibility.''}

``A new project, then?'' Ioan hazarded.

It smiled wryly. \emph{"You know me well. Yes, I cannot seem to think of anything else. Fewer things in life than we imagine are truly irreversible. Time is the one that everyone thinks of, and whenever they name some other process in life that seems irreversible, it really boils down to the ways in which it is bound by time. Breathing? Digestion? Aging? Death? All time-bound aspects that only bear the semblance of irreversibility.}

\emph{And yet we have short-circuited so much of that here. We have found ways to take time and set aside some of the constraints that it puts on those processes. Breathing, digestion, and aging are all optional, and death, as we must know, is something that must be chosen. Even then, a true death remains elusive. Perhaps we quit and merge down tree, but is that death? Perhaps all of our instances quit, but even this lacks some of the savor that a true death contains."}

``You're declaiming again.''

Dear stuck its tongue out at its partner, a gesture that bordered on cute on that vulpine face. Its partner laughed.

\emph{``It has already been established that I am excited. Permit me this!''} After a laughing pause, it continued. \emph{"Now, however, we have been permitted the wonder and curiosity that drives so many images of the afterlife. Now, we get as close as ever to} knowing \emph{that an afterlife exist, and ghosts will speak to us from beyond the heavens."}

``For a time,'' Codrin said.

\emph{``For a time, and even that carries with it the irreversibility of time.''}

The ideas touched on some subconscious musing that Ioan had carried with emself ever since the choice to remain had been made, and the group settled into a silence broken only by the crackling of logs on the bonfire. Ey didn't know what the others were thinking, there in the flickering light, but for em, the weight of that decision settled at last on em, and eir thoughts scattered before the implications.

Ey had made eir own irreversible choice, and while ey knew that ey could technically reverse it up until that final point of no return this evening, ey knew that ey would not.

``Ioan?''

Ey realized that the triad were staring at them. Ey shook eir head to dispel the rumination. ``Sorry. Yes?''

``Where is May Then My Name?'' Dear's partner asked.

``Here.'' Four heads turned to the watch the skunk, similar to Dear in so many ways but for species, padded around the corner. She smiled apologetically and bowed. ``Sorry I am late.''

Dear brightened and stepped quickly to the skunk, part of its own clade, and, once the bow completed, hugged her. \emph{``My dear, a pleasure as always.''}

Ioan waited for Dear to release May Then My Name Die With Me before getting eir own hug. After, she looped her arm through eirs, letting em play the escort and settling into a familiar pattern of constant touch.

``Glad you could make it,'' Dear's partner said.

``Of course! Would not miss it for the world. Besides, I am one of the honored guests, right?''

Codrin smiled. ``We've only invited honored guests.''

\emph{``Of course! And here come more.''}

For the next hour, the chime of arrival was nearly constant as guests upon guests arrived. Much of the Ode Clade showed, though Ioan noted that some of the more conservative members were absent, grudges remaining even to this day. Michelle Hadje herself, the root instance, was notably absent, and a tug of still-unprocessed emotions pulled at the insides of eir chest.

Ioan had only met her once before, shortly before this whole plan had been set into motion. She was unfailingly kind, though if madness rode the whole of the Ode Clade, it seemed to affect her deeper than the rest, and she was often taken by long silences, sometimes in the middle of sentences. During these, she lost coherence, her form rippling and changing, waves of skunk rolling down her form, followed by equally tumultuous waves of her usual human self. These spells would last anywhere from a few seconds to a few minutes, and even after they were quelled and the conversation resumed, afterimages of mephitidine muzzle and ears would ghost suddenly into place and just as quickly disappear.

After that visit, Ioan had asked Dear about them. Its features darkened and it had averted its gaze. \emph{``We all have our ways of dealing with loss. She could seek change if she wanted, but\ldots{}''}

It was rare for the fox to leave the end of a sentence unsaid, but Ioan could not think of a way to ask it to continue.

While every guest was noteworthy in their own way, a few names stood out to em. Dear's sibling instance, Serene; Sustained And Sustaining, arrived, a mad grin on her face as she ran directly at Dear and tackled it, the two foxes wrestling briefly on the ground before standing up and dusting themselves off again, both laughing.

``I can't believe you're going to destroy this place, you asshole. I spent weeks on the grass alone!''

Dear grinned lopsidedly. \emph{``It is not yours anymore, however, and I am a sucker for grand gestures.''}

``Some gesture!''

\emph{``Asshole, remember?''}

Serene had arrived with her and Dear's down-tree instance, That Which Lives Is Forever Praiseworthy, or Praiseworthy for short. The entire clade, all one hundred of them, had each taken for their names a line from a long poem, the shortest of which was What Right Have I, and the longest The Only Time I Know My True Name Is When I Dream, a jumble of syllables often shortened to just True Name. Both were present.

Ioan was surprised by a guest who arrived late in the evening when the champagne and wine were already flowing. Simien Fang, the head of an institute that both Dear and Ioan had worked for at times in the past, made an appearance his appearance in classic understated style. He was dressed in all black, but only when viewed head on. He had apparently made an agreement with Dear to allow the occupants of the sim's vision to be modified such that when viewed out of the corner of the eye, his outfit flashed in a whirlwind of phosphene colors. Not only that, but his normally calm features distorted into a devilish grin, no matter the expression seen directly.

The party rolled on inevitably.

A sudden peal of thunder, louder than any Ioan had ever heard, brought silence in its wake.

\emph{``It is time! It is time! Please gather around the fire!''} Excitement filled Dear's voice, though Ioan thought ey could detect a hint of nervousness that had not been there before.

The fox forked off several copies, all wide-eyed and feral-grinned, who helped to herd the hundred-and-change guests into a loose ring around the bonfire before quitting.

Ioan and May Then My Name took up places about a third of the way around the fire from Dear and its partners, the better to see without flames in the way.

The triad stepped forward, and the circle closed behind them. Each of them forked in turn, the forks bowed, and disappeared.

The weight of inevitability began to crest as midnight reared its head.

No speech was forthcoming, but the three within the circle began to sing.

\begin{quote}
Should old acquaintance be forgot\\
and never brought to mind?
\end{quote}

Something about their posture forbid everyone else from joining in just yet.

\begin{quote}
Should old acquaintance be forgot\\
and auld lang syne?
\end{quote}

Ioan realized that ey was crying, that many in the circle were crying, and without any signal, all within the circle burst into the chorus.

\begin{quote}
For auld lang syne, my dear,\\
for auld lang syne.\\
We'll take a cup of kindness yet,\\
For auld lang--
\end{quote}

Before the final note of the song could be sung, Dear gave a jaunty salute, bowed with a flourish, and quit along with its partner and Codrin Bălan. The landscape around them crumbled into voxels, and those voxels joined together by powers of two, and with a soft chime, all the members of the party were shunted off to wherever they called home.

Ioan stumbled and fell to eir knees on the parquet of eir entryway, May Then My Name standing, defiant against the change in scenery, in air and light and gravity, beside em.

``What an asshole,'' she laughed.
