\hypertarget{ioan-bux103lan-2325}{%
\chapter{Ioan Bălan—2325}\label{ioan-bux103lan-2325}}

Ioan and May Then My Name let the intoxication of the night cling to them a while longer while they sat on the balcony of Ioan's house, overlooking that perpetually lilac-scented yard, and talked. They talked of the party, of the modern house on the prairie, of Dear and the contradiction of formal intensity and playfulness that it seemed to embody. The conversation wound down, and then the two sat in silence. It did not seem time yet to snap sobriety into being.

It had taken Ioan a few days to get used to the skunk's affectionate nature. When she first moved in as the intensity of the project began to ramp up, it had taken em by surprised, and ey had needed to have a series of awkward conversations discussing boundaries and intentions.

Now, as she slouched against eir side on that bench swing and ey settled eir arm around her, he asked, ``What is the story behind your fork? Or your stanza?''

``Mm?''

``Well, Dear said that it and Serene were forked when Praiseworthy wanted to explore an interest in instances and sims. Is there something like that which led to\ldots to whatever your down-tree instance is forking?'' Ey supposed that, were ey sober, ey might have better luck dredging up the lines from the stanza. Something about true names and god.

May Then My Name shrugged, shoulder shifting against Ioan's side. ``In the early days, I---Michelle, that is---did not have much direction to her forking. Forks were created at need essentially to handle the increased workload.''

``Were the early days busy?''

``Very busy. We were one of the first, you know, and there were a lot of details that needed to be seen to before this place became what it is today.''

Ioan nodded. ``Dear said that Michelle had campaigned to include sensoria in the system.''

``Yes, though that word is something of an elision that has become shorthand for experiences rather than thoughts.'' Her voice was soft, though it still held the careful articulation of one who has realized that they are not sober. "We were not beings of pure thought, there were still experiences, but there was no guarantee that they would be shared. It was chaotic, as you might imagine from a set of unique individuals trying to dream the same dream.

``This was back in the early days, you understand, before the System had become a dumping ground for the world's excess population. We were all starry-eyed dreamers, and so were the engineers phys-side. Hard problems remain hard, however, and it kept getting deprioritized. Michelle and the rest of the Council of Eight provided arguments for the means by which we have consensual sensoria, as well as additional sensorium tools such as the messages.''

Ioan restrained the impulse to bristle at this. The Ode clade was notorious for their fondness for sensorium messages, those sensations and images that barged in on one's senses. Ey found them unnerving. Instead, ey said, ``Just how much of the early System did your clade influence.''

May Then My Name's laugh was musical. ``I am sure we have lost count. The first lines of each stanza quickly picked up interests of their own---they were in much better communication back then---and each picked up a project of their own, and whenever a new project would come along, they would petition the rest of the clade for the use of a line for a long-running fork. Everything was much more expensive back then, and we would sometimes have to pool our reputation.''

``What was your stanza's project?''

``We lost the idea that the whole stanza would be working on similar projects after a while, so they are not as tightly connected any more. The first line of mine, though, The Only Time I Know My True Name Is When I Dream---True Name---was instrumental in the secession of the System.''

Ioan blinked, startled. ``I had no idea. That early?''

``That was before we started using systime, yes.''

-\{``Two centuries ago? I thought Dear said Michelle uploaded after Secession.''\}(This whole bit is a continuity error)

She shrugged noncommittally, then rested her head back on Ioan's shoulder. The alcohol of the night still dogged em, but

``And the reason for your fork?''

``To feel.''

``To feel?''

``To feel. True Name kept spinning off instances to work on such concrete things, I think she forgot how to feel. Emotions became distant out of habit. Touch became a distraction. I was to become her anchor. We would merge every few months after that, though we have settled on once a decade, of late. We will merge once this project is finished.''

``You haven't diverged too far?'' Ioan asked.

``We try not to,'' the skunk murmured. ``That is why I am acting as coordinator. It is a familiar role.''

Ioan nodded. ``Close enough to Secession, I suppose.''

Another moment of silence. The academic permitted some of the drunkenness from the evening to drift away, allowing him to think more clearly. May Then My Name relaxed further against eir side, and ey suspected she was not far away from sleep. Tomorrow, the work would begin in earnest, so ey was tempted to let her sleep, but a question nagged at him.

``May?''

``I like it when you call me that.''

``It's a good name.'' Ioan grinned. ``I had a question, though. How much do you remember from back then?''

She sat bolt upright, wrenching at eir shoulder. ``What did you say? Sorry.''

Ey reclaimed eir arm, rubbing at the shoulder. ``It's okay. How much do you remember from the start of the System?''

``You, my dear, are a fucking genius.'' She was on her feet now, pacing back and forth in front of the bench swing. She paused mid-pace to lean down and bump her nose against Ioan's forehead; her form of a kiss. ``Fucking genius.''

Given that she appeared to have sobered up, Ioan allowed emself to do the same. ``What do you mean?'' ey asked.

``I want to modify the project scope. Can I tell you a secret?'' She was talking quickly now.

``Yes, of course.''

``I want to modify the project and add in an early history of the system, of Secession. Do you think you would be up for adding that in?''

Ioan frowned. ``If can I fork for it, I suppose.''

May Then My Name laughed. ``You are talking to an Odist, of course you can fucking fork.''

``Alright, alright. Then what's your secret?''

``I want to write an early history of the system to parallel the current. They are very similar, you know, but it has been two hundred years. We are well past history, and doubtless there are histories already written. Yes, I remember. Of course I do. I remember the secession, I remember uploading, I remember getting lost, I remember everything. The all the great and terrible things that we did. We could write a history, but that is all already there. There are paper trails and journals and everything phys-side already knows about us, but--''

Ioan's eyes went wide as ey picked up on her idea. ``You want to write a mythology.''

She clapped and bounced excitedly on her feet. ``Yes! Yes, a mythology. I know I have mentioned them before, and we had talked about incorporating that aspect with Dear and Codrin. The history is important, and perhaps we can write that too, but now is not the time for only history. Now is the time for--''

``Stories.''

In a decidedly Dear-like move, the skunk forked several times over, crowding the balcony before the bench swing with copies of herself, all of which had the same expression of glee. They quit quickly, and May Then My Name leaned forward to give Ioan a handful more of those nose-dot kisses. ``You get it!''

``I worked with Dear, you nut. Of course I get stories.'' Ey laughed and reached up to grab her around the waist and haul her back onto the swing beside em.

How different she was than Dear! Individuation is born in the decades and centuries. Ey would never have thought to be so physical with the fox, but as she laughed and slumped back against eir side, ey realized ey had long since fallen into the habit of physicality, of touch. Of, ey realized, feeling.
